### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@aa35be435d61ee276c974f92800736cda9c27428 🚀

%!TEX TS-program = xelatex
\documentclass[11pt]{article}

\usepackage[english]{babel}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage[scaled]{helvet}
\usepackage[scaled]{inconsolata}

\usepackage{lastpage}

\usepackage{setspace}

\usepackage{ccicons}

\usepackage[hang,flushmargin]{footmisc}

\usepackage{geometry}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}

\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\makeatletter
\newcounter{tableno}
\newenvironment{tablenos:no-prefix-table-caption}{
  \caption@ifcompatibility{}{
    \let\oldthetable\thetable
    \let\oldtheHtable\theHtable
    \renewcommand{\thetable}{tableno:\thetableno}
    \renewcommand{\theHtable}{tableno:\thetableno}
    \stepcounter{tableno}
    \captionsetup{labelformat=empty}
  }
}{
  \caption@ifcompatibility{}{
    \captionsetup{labelformat=default}
    \let\thetable\oldthetable
    \let\theHtable\oldtheHtable
    \addtocounter{table}{-1}
  }
}
\makeatother

\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\let\PBS=\PreserveBackslash

\usepackage[breaklinks=true]{hyperref}
\hypersetup{colorlinks,%
citecolor=blue,%
filecolor=blue,%
linkcolor=blue,%
urlcolor=blue}
\usepackage{url}

\usepackage{caption}
\setcounter{secnumdepth}{0}
\usepackage{cleveref}

\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

\usepackage{longtable}
\usepackage{booktabs}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

\pagestyle{plain}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\doublespacing

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
using markdown and github actions}
\vskip 5em

%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}\quad %
Peregrin\,Took%
%
\,\textsuperscript{3,4}\quad %
Merriadoc\,Brandybuck%
%
\,\textsuperscript{5,4,‡}

\textsuperscript{1}\,Université de
Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
Sciences\quad \textsuperscript{3}\,Inn of the Prancing
Pony\quad \textsuperscript{4}\,Fellowship of the
Ring\quad \textsuperscript{5}\,Green Dragon Inn

\textsuperscript{‡}\,These authors contributed equally to the work\\

\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\

\vfill
This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
Last revision: \emph{\today}

\clearpage
\thispagestyle{empty}

\vfill

        {\bfseries Purpose:}\,This template provides a series of scripts
to render a markdown document into an interactive website and a series
of PDFs.\\%
        {\bfseries Motivation:}\,It makes collaborating on text with
GitHub easier, and means that we never need to think about the
output.\\%
        {\bfseries Internals:}\,GitHub actions and a series of python
scritpts. The markdown is handled with \texttt{pandoc}.\\%

\vfill

\clearpage
\linenumbers
\pagestyle{normal}

\hypertarget{intro}{%
\section{Intro}\label{intro}}

Having a general solution for inferring \emph{potential} interactions
(despite the unavailability of interaction data) could be the catalyst
for significant breakthroughs in our ability to start thinking about
species interaction networks over large spatial scales. In a recent
overview of the field of ecological network prediction, Strydom \emph{et
al.} (2021) identified two challenges of interest to the prediction of
interactions at large scales. First, there is a relative scarcity of
relevant data in most places globally -- paradoxically, this restricts
our ability to infer interactions to locations where inference is
perhaps the least required; second, accurate predictions often demand
accurate predictors, and the lack of methods that can leverage small
amount of data is a serious impediment to our predictive ability
globally.

Following the definition of Dunne (2006), a metaweb is a network
analogue to the regional species pool; specifically, it is an inventory
of all \emph{potential} interactions between species from a spatially
delimited area (and so captures the \(\gamma\) diversity of
interactions). The metaweb is, therefore, \emph{not} a prediction of the
food web at a specific locale within the spatial area it covers, and
will have a different structure (notably by having a larger connectance;
see \emph{e.g.} Wood \emph{et al.} 2015). These local food webs (which
captures the \(\alpha\) diversity of interactions) are a subset of the
metaweb's species and interactions, and have been called ``metaweb
realizations'' (Poisot \emph{et al.} 2015). Differences between local
food web and their metaweb are due to chance, species abundance and
co-occurrence, local environmental conditions, and local distribution of
functional traits, among others.

Because the metaweb represents the joint effect of functional,
phylogenetic, and macroecological processes (Morales-Castilla \emph{et
al.} 2015), it holds valuable ecological information. Specifically, it
is the ``upper bounds'' on what the composition of the local networks
can be (see \emph{e.g.} McLeod \emph{et al.} 2021). These local
networks, in turn, can be reconstructed given appropriate knowledge of
local species composition, providing information on structure of food
webs at finer spatial scales. This has been done for example for
tree-galler-parasitoid systems (Gravel \emph{et al.} 2018), fish trophic
interactions (Albouy \emph{et al.} 2019), tetrapod trophic interactions
(O'Connor \emph{et al.} 2020), and crop-pest networks (Grünig \emph{et
al.} 2020). Whereas the original metaweb definition, and indeed most
past uses of metawebs, was based on the presence/absence of
interactions, we focus on \emph{probabilistic} metawebs where
interactions are represented as the chance of success of a Bernoulli
trial (see \emph{e.g.} Poisot \emph{et al.} 2016); therefore, not only
does our method recommend interactions that may exist, it gives each
interaction a score, allowing us to properly weigh them.

Yet, owing to the inherent plasticity of interactions, there have been
documented instances of food webs undergoing rapid collapse/recovery
cycles over short periods of time (Pedersen \emph{et al.} 2017). The
embedding of a network, in a sense, embeds its macro-evolutionary
history, especially as RDPG captures ecological signal (Dalla Riva \&
Stouffer 2016); at this point, it is important to recall that a metaweb
is intended as a catalogue of all potential interactions, which should
then be filtered (Morales-Castilla \emph{et al.} 2015). In practice (and
in this instance) the reconstructed metaweb will predict interactions
that are plausible based on the species' evolutionary history, however
some interactions would/would not be realized due to human impact.

Dallas \emph{et al.} (2017) suggested that most links in ecological
networks may be cryptic, \emph{i.e.} uncommon or otherwise hard to
observe. This argument essentially echoes Jordano (2016): the sampling
of ecological interactions is difficult because it requires first the
joint observation of two species, and then the observation of their
interaction. In addition, it is generally expected that weak or rare
links would be more common in networks (Csermely 2004), compared to
strong, persistent links; this is notably the case in food chains,
wherein many weaker links are key to the stability of a system (Neutel
\emph{et al.} 2002). In the light of these observations, the results in
fig.~\ref{fig:inflation} are not particularly surprising: we expect to
see a surge in these low-probability interactions under a model that has
a good predictive accuracy. Because the predictions we generate are by
design probabilistic, then one can weigh these rare links appropriately.
In a sense, that most ecological interactions are elusive can call for a
slightly different approach to sampling: once the common interactions
are documented, the effort required in documenting each rare interaction
may increase exponentially. Recent proposals suggest that machine
learning algorithms, in these situations, can act as data generators
(Hoffmann \emph{et al.} 2019): in this perspective, high quality
observational data can be supplemented with synthetic data coming from
predictive models, which increases the volume of information available
for inference. Indeed, Strydom \emph{et al.} (2021) suggested that
knowing the metaweb may render the prediction of local networks easier,
because it fixes an ``upper bound'' on which interactions can exist;
indeed, with a probabilistic metaweb, we can consider that the metaweb
represents an aggregation of informative priors on the interactions.

As Herbert (1965) rightfully pointed out, ``{[}y{]}ou can't draw neat
lines around planet-wide problems''; in this regard, our approach (and
indeed, any inference of a metaweb at large scales) must contend with
several interesting and interwoven families of problems. The first is
the limit of the metaweb to embed and transfer. If the initial metaweb
is too narrow in scope, notably from a taxonomic point of view, the
chances of finding another area with enough related species to make a
reliable inference decreases; this would likely be indicated by large
confidence intervals during ancestral character estimation, but the lack
of well documented metawebs is currently preventing the development of
more concrete guidelines. The question of phylogenetic relatedness and
dispersal is notably true if the metaweb is assembled in an area with
mostly endemic species, and as with every predictive algorithm, there is
room for the application of our best ecological judgement. Conversely,
the metaweb should be reliably filled, which assumes that the \(S^2\)
interactions in a pool of \(S\) species have been examined, either
through literature surveys or expert elicitation. Supp. Mat. 1 provides
some guidance as to the type of sampling effort that should be
prioritized. While RDPG was able to maintain very high predictive power
when interactions were missing, the addition of false positive
interactions was immediately detected; this suggests that it may be
appropriate to err on the side of ``too many'' interactions when
constructing the initial metaweb to be transferred. The second series of
problems are related to determining which area should be used to infer
the new metaweb in, as this determines the species pool that must be
used.

In our application, we focused on the mammals of Canada. The upside of
this approach is that information at the country level is likely to be
required by policy makers and stakeholders for their biodiversity
assessment, as each country tends to set goals at the national level
(Buxton \emph{et al.} 2021) for which quantitative instruments are
designed (Turak \emph{et al.} 2017), with specific strategies often
enacted at smaller scales (Ray \emph{et al.} 2021). And yet, we do not
really have a satisfying answer to the question of ``where does a food
web stop?''; the current most satisfying solutions involve examining the
spatial consistency of network area relationships (see \emph{e.g.}
Galiana \emph{et al.} 2018, 2019, 2021; Fortin \emph{et al.} 2021),
which is of course impossible in the absence of enough information about
the network itself. This suggests that an \emph{a posteriori} refinement
of the results may be required, based on a downscaling of the metaweb.
The final family of problems relates less to the availability of data or
quantitative tools, and more to the praxis of spatial ecology. Operating
under the context of national divisions, in large parts of the world,
reflects nothing more than the legacy of settler colonialism. Indeed,
the use of ecological data is not an apolitical act (Nost \& Goldstein
2021), as data infrastructures tend to be designed to answer questions
within national boundaries, and their use both draws upon and reinforces
territorial statecraft; as per Machen \& Nost (2021), this is
particularly true when the output of ``algorithmic thinking''
(\emph{e.g.} relying on machine learning to generate knowledge) can be
re-used for governance (\emph{e.g.} enacting conservation decisions at
the national scale). We therefore recognize that methods such as we
propose operate under the framework that contributed to the ongoing
biodiversity crisis (Adam 2014), reinforced environmental injustice
(Choudry 2013; Domínguez \& Luoma 2020), and on Turtle Island
especially, should be replaced by Indigenous principles of land
management (Eichhorn \emph{et al.} 2019; No'kmaq \emph{et al.} 2021). As
we see AI/ML being increasingly mobilized to generate knowledge that is
lacking for conservation decisions (\emph{e.g.} Lamba \emph{et al.}
2019; Mosebo Fernandes \emph{et al.} 2020), our discussion of these
tools need to go beyond the technical, and into the governance
consequences they can have.

\textbf{Acknowledgements:} We acknowledge that this study was conducted
on land within the traditional unceded territory of the Saint Lawrence
Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak
nations. TP, TS, DC, and LP received funding from the Canadian Institue
for Ecology \& Evolution. FB is funded by the Institute for Data
Valorization (IVADO). TS, SB, and TP are funded by a donation from the
Courtois Foundation. CB was awarded a Mitacs Elevate Fellowship no.
IT12391, in partnership with fRI Research, and also acknowledges funding
from Alberta Innovates and the Forest Resources Improvement Association
of Alberta. M-JF acknowledges funding from NSERC Discovery Grant and
NSERC CRC. RR is funded by New Zealand's Biological Heritage Ngā Koiora
Tuku Iho National Science Challenge, administered by New Zealand
Ministry of Business, Innovation, and Employment. BM is funded by the
NSERC Alexander Graham Bell Canada Graduate Scholarship and the FRQNT
master's scholarship. LP acknowledges funding from NSERC Discovery Grant
(NSERC RGPIN-2019-05771). TP acknowledges financial support from NSERC
through the Discovery Grants and Discovery Accelerator Supplement
programs.

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Adam2014EleTre}{}%
Adam, R. (2014). \emph{Elephant treaties: The Colonial legacy of the
biodiversity crisis}. UPNE.

\leavevmode\hypertarget{ref-Albouy2019MarFis}{}%
Albouy, C., Archambault, P., Appeltans, W., Araújo, M.B., Beauchesne,
D., Cazelles, K., \emph{et al.} (2019). The marine fish food web is
globally connected. \emph{Nature Ecology \& Evolution}, 3, 1153--1161.

\leavevmode\hypertarget{ref-Buxton2021KeyInf}{}%
Buxton, R.T., Bennett, J.R., Reid, A.J., Shulman, C., Cooke, S.J.,
Francis, C.M., \emph{et al.} (2021). Key information needs to move from
knowledge to action for biodiversity conservation in Canada.
\emph{Biological Conservation}, 256, 108983.

\leavevmode\hypertarget{ref-Choudry2013SavBio}{}%
Choudry, A. (2013). Saving biodiversity, for whom and for what?
Conservation NGOs, complicity, colonialism and conquest in an era of
capitalist globalization. In: \emph{NGOization: Complicity,
contradictions and prospects}. Bloomsbury Publishing, pp. 24--44.

\leavevmode\hypertarget{ref-Csermely2004StrLin}{}%
Csermely, P. (2004). Strong links are important, but weak links
stabilize them. \emph{Trends in Biochemical Sciences}, 29, 331--334.

\leavevmode\hypertarget{ref-DallaRiva2016ExpEvo}{}%
Dalla Riva, G.V. \& Stouffer, D.B. (2016). Exploring the evolutionary
signature of food webs' backbones using functional traits. \emph{Oikos},
125, 446--456.

\leavevmode\hypertarget{ref-Dallas2017PreCry}{}%
Dallas, T., Park, A.W. \& Drake, J.M. (2017). Predicting cryptic links
in host-parasite networks. \emph{PLOS Computational Biology}, 13,
e1005557.

\leavevmode\hypertarget{ref-Dominguez2020DecCon}{}%
Domínguez, L. \& Luoma, C. (2020). Decolonising Conservation Policy: How
Colonial Land and Conservation Ideologies Persist and Perpetuate
Indigenous Injustices at the Expense of the Environment. \emph{Land}, 9,
65.

\leavevmode\hypertarget{ref-Dunne2006NetStr}{}%
Dunne, J.A. (2006). The Network Structure of Food Webs. In:
\emph{Ecological networks: Linking structure and dynamics} (eds. Dunne,
J.A. \& Pascual, M.). Oxford University Press, pp. 27--86.

\leavevmode\hypertarget{ref-Eichhorn2019SteDec}{}%
Eichhorn, M.P., Baker, K. \& Griffiths, M. (2019). Steps towards
decolonising biogeography. \emph{Frontiers of Biogeography}, 12, 1--7.

\leavevmode\hypertarget{ref-Fortin2021NetEco}{}%
Fortin, M.-J., Dale, M.R.T. \& Brimacombe, C. (2021). Network ecology in
dynamic landscapes. \emph{Proceedings of the Royal Society B: Biological
Sciences}, 288, rspb.2020.1889, 20201889.

\leavevmode\hypertarget{ref-Galiana2021SpaSca}{}%
Galiana, N., Barros, C., Braga, J., Ficetola, G.F., Maiorano, L.,
Thuiller, W., \emph{et al.} (2021). The spatial scaling of food web
structure across European biogeographical regions. \emph{Ecography},
n/a.

\leavevmode\hypertarget{ref-Galiana2019GeoVar}{}%
Galiana, N., Hawkins, B.A. \& Montoya, J.M. (2019). The geographical
variation of network structure is scale dependent: Understanding the
biotic specialization of hostparasitoid networks. \emph{Ecography}, 42,
1175--1187.

\leavevmode\hypertarget{ref-Galiana2018SpaSca}{}%
Galiana, N., Lurgi, M., Claramunt-López, B., Fortin, M.-J., Leroux, S.,
Cazelles, K., \emph{et al.} (2018). The spatial scaling of species
interaction networks. \emph{Nature Ecology \& Evolution}, 2, 782--790.

\leavevmode\hypertarget{ref-Gravel2018BriElt}{}%
Gravel, D., Baiser, B., Dunne, J.A., Kopelke, J.-P., Martinez, N.D.,
Nyman, T., \emph{et al.} (2018). Bringing Elton and Grinnell together: A
quantitative framework to represent the biogeography of ecological
interaction networks. \emph{Ecography}, 0.

\leavevmode\hypertarget{ref-Grunig2020CroFor}{}%
Grünig, M., Mazzi, D., Calanca, P., Karger, D.N. \& Pellissier, L.
(2020). Crop and forest pest metawebs shift towards increased linkage
and suitability overlap under climate change. \emph{Communications
Biology}, 3, 1--10.

\leavevmode\hypertarget{ref-Herbert1965Dun}{}%
Herbert, F. (1965). \emph{Dune}. 1st edn. Chilton Book Company,
Philadelphia.

\leavevmode\hypertarget{ref-Hoffmann2019MacLea}{}%
Hoffmann, J., Bar-Sinai, Y., Lee, L.M., Andrejevic, J., Mishra, S.,
Rubinstein, S.M., \emph{et al.} (2019). Machine learning in a
data-limited regime: Augmenting experiments with synthetic data uncovers
order in crumpled sheets. \emph{Science Advances}, 5, eaau6792.

\leavevmode\hypertarget{ref-Jordano2016SamNet}{}%
Jordano, P. (2016). Sampling networks of ecological interactions.
\emph{Functional Ecology}, 30, 1883--1893.

\leavevmode\hypertarget{ref-Lamba2019DeeLea}{}%
Lamba, A., Cassey, P., Segaran, R.R. \& Koh, L.P. (2019). Deep learning
for environmental conservation. \emph{Current Biology}, 29, R977--R982.

\leavevmode\hypertarget{ref-Machen2021ThiAlg}{}%
Machen, R. \& Nost, E. (2021). Thinking algorithmically: The making of
hegemonic knowledge in climate governance. \emph{Transactions of the
Institute of British Geographers}, 46, 555--569.

\leavevmode\hypertarget{ref-McLeod2021SamAsy}{}%
McLeod, A., Leroux, S.J., Gravel, D., Chu, C., Cirtwill, A.R., Fortin,
M.-J., \emph{et al.} (2021). Sampling and asymptotic network properties
of spatial multi-trophic networks. \emph{Oikos}, n/a.

\leavevmode\hypertarget{ref-Morales-Castilla2015InfBio}{}%
Morales-Castilla, I., Matias, M.G., Gravel, D. \& Araújo, M.B. (2015).
Inferring biotic interactions from proxies. \emph{Trends in Ecology \&
Evolution}, 30, 347--356.

\leavevmode\hypertarget{ref-MoseboFernandes2020MacLea}{}%
Mosebo Fernandes, A.C., Quintero Gonzalez, R., Lenihan-Clarke, M.A.,
Leslie Trotter, E.F. \& Jokar Arsanjani, J. (2020). Machine Learning for
Conservation Planning in a Changing Climate. \emph{Sustainability}, 12,
7657.

\leavevmode\hypertarget{ref-Neutel2002StaRea}{}%
Neutel, A.-M., Heesterbeek, J.A.P. \& de Ruiter, P.C. (2002). Stability
in Real Food Webs: Weak Links in Long Loops. \emph{Science}, 296,
1120--1123.

\leavevmode\hypertarget{ref-Nokmaq2021AwaSle}{}%
No'kmaq, M., Marshall, A., Beazley, K.F., Hum, J., joudry, shalan,
Papadopoulos, A., \emph{et al.} (2021). {``Awakening the sleeping
giant''}: Re-Indigenization principles for transforming biodiversity
conservation in Canada and beyond. \emph{FACETS}, 6, 839--869.

\leavevmode\hypertarget{ref-Nost2021PolEco}{}%
Nost, E. \& Goldstein, J.E. (2021). A political ecology of data.
\emph{Environment and Planning E: Nature and Space}, 25148486211043503.

\leavevmode\hypertarget{ref-OConnor2020UnvFoo}{}%
O'Connor, L.M.J., Pollock, L.J., Braga, J., Ficetola, G.F., Maiorano,
L., Martinez-Almoyna, C., \emph{et al.} (2020). Unveiling the food webs
of tetrapods across Europe through the prism of the Eltonian niche.
\emph{Journal of Biogeography}, 47, 181--192.

\leavevmode\hypertarget{ref-Pedersen2017SigCol}{}%
Pedersen, E.J., Thompson, P.L., Ball, R.A., Fortin, M.-J., Gouhier,
T.C., Link, H., \emph{et al.} (2017). Signatures of the collapse and
incipient recovery of an overexploited marine ecosystem. \emph{Royal
Society Open Science}, 4, 170215.

\leavevmode\hypertarget{ref-Poisot2016StrPro}{}%
Poisot, T., Cirtwill, A.R., Cazelles, K., Gravel, D., Fortin, M.-J. \&
Stouffer, D.B. (2016). The structure of probabilistic networks.
\emph{Methods in Ecology and Evolution}, 7, 303--312.

\leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%
Poisot, T., Stouffer, D.B. \& Gravel, D. (2015). Beyond species: Why
ecological interaction networks vary through space and time.
\emph{Oikos}, 124, 243--251.

\leavevmode\hypertarget{ref-Ray2021BioCri}{}%
Ray, J.C., Grimm, J. \& Olive, A. (2021). The biodiversity crisis in
Canada: Failures and challenges of federal and sub-national strategic
and legal frameworks. \emph{FACETS}, 6, 1044--1068.

\leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
Desjardins-Proulx, P., \emph{et al.} (2021). A roadmap towards
predicting species interaction networks (across space and time).
\emph{Philosophical Transactions of the Royal Society B: Biological
Sciences}, 376, 20210063.

\leavevmode\hypertarget{ref-Turak2017UsiEss}{}%
Turak, E., Brazill-Boast, J., Cooney, T., Drielsma, M., DelaCruz, J.,
Dunkerley, G., \emph{et al.} (2017). Using the essential biodiversity
variables framework to measure biodiversity change at national scale.
\emph{Biological Conservation}, SI:Measures of biodiversity, 213,
264--271.

\leavevmode\hypertarget{ref-Wood2015EffSpa}{}%
Wood, S.A., Russell, R., Hanson, D., Williams, R.J. \& Dunne, J.A.
(2015). Effects of spatial scale of sampling on food web structure.
\emph{Ecology and Evolution}, 5, 3769--3782.

\end{CSLReferences}

\end{document}

### 2022-01-12 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@aa35be435d61ee276c974f92800736cda9c27428 🚀

--- 2022-01-12 draft.tex
@@
 %!TEX TS-program = xelatex
-\documentclass[11pt]{article}
+\documentclass[10pt,oneside]{article}
+\usepackage[fontsize=9pt]{scrextend}
 
@@
 \newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}
 
-\usepackage{lineno}
-\usepackage[nolists,noheads]{endfloat}
+\geometry{includemp,
+            letterpaper,
+            top=2.4cm,
+            bottom=2.4cm,
+            left=1.0cm,
+            right=1.0cm,
+            marginparwidth=5cm,
+            marginparsep=1.0cm}
+
+\usepackage[singlelinecheck=off]{caption}
+
+\captionsetup{
+  font={small},
+  labelfont={bf},
+  format=plain,
+  labelsep=quad
+}
+
+\usepackage{floatrow}
+
+\floatsetup[figure]{margins=hangright,
+              facing=no,
+              capposition=beside,
+              capbesideposition={center,outside},
+              floatwidth=\textwidth}
+
+% \floatsetup[table]{margins=hangright,
+%              facing=no,
+%              capposition=beside,
+%              capbesideposition={center,outside},
+%              floatwidth=\textwidth}
 
@@
 
-\tolerance=1
-\emergencystretch=\maxdimen
-\hyphenpenalty=10000
-\hbadness=10000
+\setcounter{secnumdepth}{5}
 
-\doublespacing
+\usepackage{titlesec}
+
+\titleformat{\section}[block]
+{\normalfont\large\sffamily}
+{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}
+
+\titleformat{\subsection}[runin]
+{\normalfont\fontseries{b}\selectfont\filright\sffamily}
+{\thesubsection.}{.5em}{}
+
+\titleformat{\subsubsection}[runin]
+{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}
+
+\fancypagestyle{firstpage}
+{
+   \fancyhf{}
+   \renewcommand{\headrulewidth}{0pt}
+   \fancyfoot[R]{\footnotesize\ccby}
+   \fancyfoot[L]{\footnotesize\sffamily\today}
+}
 
@@
 }
+
+\usepackage{tikz}
 \begin{document}
-\raggedright
-\thispagestyle{empty}
-{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
-using markdown and github actions}
-\vskip 5em
+\tikz [remember picture, overlay] %
+\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
+\pagestyle{normal}
+\thispagestyle{firstpage}
 
+\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}
+
+\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
+manuscripts using markdown and github actions}}}
+
+\medskip
+\begin{flushleft}
+{\small
 %
@@
 %
-\,\textsuperscript{1,2,‡}\quad %
+\,\textsuperscript{1,2,‡}, %
 Peregrin\,Took%
 %
-\,\textsuperscript{3,4}\quad %
+\,\textsuperscript{3,4}, %
 Merriadoc\,Brandybuck%
@@
 \,\textsuperscript{5,4,‡}
-
-\textsuperscript{1}\,Université de
-Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
-Sciences\quad \textsuperscript{3}\,Inn of the Prancing
-Pony\quad \textsuperscript{4}\,Fellowship of the
-Ring\quad \textsuperscript{5}\,Green Dragon Inn
-
+\vskip 1em
+\textsuperscript{1}\,Université de Montréal; \textsuperscript{2}\,Québec
+Centre for Biodiversity Sciences; \textsuperscript{3}\,Inn of the
+Prancing Pony; \textsuperscript{4}\,Fellowship of the
+Ring; \textsuperscript{5}\,Green Dragon Inn\\
 \textsuperscript{‡}\,These authors contributed equally to the work\\
-
+\vskip 1em
 \textbf{Correspondance to:}\\
 Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
+}
+\end{flushleft}
 
-\vfill
-This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
-Last revision: \emph{\today}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
+\noindent
 
-\clearpage
-\thispagestyle{empty}
-
-\vfill
+\marginpar{\vskip 1em\flushright
+{\small{\bfseries Keywords}:\par
+pandoc\\pandoc-crossref\\github actions\\}
+}
 
@@
 
-\vfill
-
-\clearpage
-\linenumbers
-\pagestyle{normal}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
 

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@6a3d63a69884a8ea48876819447b1319412eace5 🚀

@@
 \thispagestyle{empty}
-{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
-using markdown and github actions}
+{\Large\bfseries\sffamily Predicting metawebs: graph embeddings can help
+alleviate spatial data deficiencies}
 \vskip 5em
@@
 %
+\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
+%
+\,\textsuperscript{1,2,‡}\quad %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
 %
-\,\textsuperscript{1,2,‡}\quad %
-Peregrin\,Took%
-%
-\,\textsuperscript{3,4}\quad %
-Merriadoc\,Brandybuck%
-%
-\,\textsuperscript{5,4,‡}
+\,\textsuperscript{1,2,‡}
 
-\textsuperscript{1}\,Université de
-Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
-Sciences\quad \textsuperscript{3}\,Inn of the Prancing
-Pony\quad \textsuperscript{4}\,Fellowship of the
-Ring\quad \textsuperscript{5}\,Green Dragon Inn
+\textsuperscript{1}\,Département de Sciences Biologiques, Université de
+Montréal, Montréal, Canada\quad \textsuperscript{2}\,Quebec Centre for
+Biodiversity Science, Montréal, Canada
 
@@
 
-        {\bfseries Purpose:}\,This template provides a series of scripts
-to render a markdown document into an interactive website and a series
-of PDFs.\\%
-        {\bfseries Motivation:}\,It makes collaborating on text with
-GitHub easier, and means that we never need to think about the
-output.\\%
-        {\bfseries Internals:}\,GitHub actions and a series of python
-scritpts. The markdown is handled with \texttt{pandoc}.\\%
+\begin{enumerate}
+    \itemMetawebs, i.e.~networks of potential interactions within a
+species pool, are a powerful abstraction to understand how large-scales
+species interaction networks are structured.%
+    \itemBecause metawebs are typically expressed at large spatial and
+taxonomic scales, assembling them is a tedious and costly process;
+predictive methods can help circumvent the limitations in data
+deficiencies, by providing `draft' metawebs.%
+    \itemOne way to improve the predictive ability is to maximize the
+information used for prediction, by using graph embeddings rather than
+the list of species interactions. Graph embedding is an emerging field
+in machine learning that holds great potential for ecoloigcal problems.%
+    \itemIn this perspective, we outline how the challenges associated
+with infering metawebs line-up with the advantages of graph embeddings;
+furthermore, because metawebs are inherently spatial objects, we discuss
+how the choice of the species pool has consequences on the reconstructed
+network, but also embeds hypotheses about which human-made boundaries
+are ecologically meaningful.%
+\end{enumerate}
 
@@
 \pagestyle{normal}
-
-\hypertarget{intro}{%
-\section{Intro}\label{intro}}
 
@@
 spatial consistency of network area relationships (see \emph{e.g.}
-Galiana \emph{et al.} 2018, 2019, 2021; Fortin \emph{et al.} 2021),
+Galiana \emph{et al.} 2018, 2019, 2021; \textbf{Fortin2021NetEco?}),
 which is of course impossible in the absence of enough information about
@@
 
-\leavevmode\hypertarget{ref-Fortin2021NetEco}{}%
-Fortin, M.-J., Dale, M.R.T. \& Brimacombe, C. (2021). Network ecology in
-dynamic landscapes. \emph{Proceedings of the Royal Society B: Biological
-Sciences}, 288, rspb.2020.1889, 20201889.
-
 \leavevmode\hypertarget{ref-Galiana2021SpaSca}{}%
@@
 variation of network structure is scale dependent: Understanding the
-biotic specialization of hostparasitoid networks. \emph{Ecography}, 42,
-1175--1187.
+biotic specialization of host--parasitoid networks. \emph{Ecography},
+42, 1175--1187.
 
@@
 O'Connor, L.M.J., Pollock, L.J., Braga, J., Ficetola, G.F., Maiorano,
-L., Martinez-Almoyna, C., \emph{et al.} (2020). Unveiling the food webs
+L., Martinez‐Almoyna, C., \emph{et al.} (2020). Unveiling the food webs
 of tetrapods across Europe through the prism of the Eltonian niche.

### 2022-01-12 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@6a3d63a69884a8ea48876819447b1319412eace5 🚀

@@
 
-\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
-manuscripts using markdown and github actions}}}
+\noindent {\LARGE \textbf{\textsf{Predicting metawebs: graph embeddings
+can help alleviate spatial data deficiencies}}}
 
@@
 %
+\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
+%
+\,\textsuperscript{1,2,‡}, %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
 %
-\,\textsuperscript{1,2,‡}, %
-Peregrin\,Took%
-%
-\,\textsuperscript{3,4}, %
-Merriadoc\,Brandybuck%
-%
-\,\textsuperscript{5,4,‡}
+\,\textsuperscript{1,2,‡}
 \vskip 1em
-\textsuperscript{1}\,Université de Montréal; \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences; \textsuperscript{3}\,Inn of the
-Prancing Pony; \textsuperscript{4}\,Fellowship of the
-Ring; \textsuperscript{5}\,Green Dragon Inn\\
+\textsuperscript{1}\,Département de Sciences Biologiques, Université de
+Montréal, Montréal, Canada; \textsuperscript{2}\,Quebec Centre for
+Biodiversity Science, Montréal, Canada\\
 \textsuperscript{‡}\,These authors contributed equally to the work\\
@@
 \vskip 2em
-
-\hypertarget{intro}{%
-\section{Intro}\label{intro}}
 

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@d28b8b3c89251398e36e6b7d499d0f6d253e4e4b 🚀

@@
 species interaction networks over large spatial scales. In a recent
-overview of the field of ecological network prediction, Strydom \emph{et
-al.} (2021) identified two challenges of interest to the prediction of
+overview of the field of ecological network prediction, Strydom et al.
+(2021) identified two challenges of interest to the prediction of
 interactions at large scales. First, there is a relative scarcity of
@@
 will have a different structure (notably by having a larger connectance;
-see \emph{e.g.} Wood \emph{et al.} 2015). These local food webs (which
+see \emph{e.g.} Wood et al., 2015). These local food webs (which
 captures the \(\alpha\) diversity of interactions) are a subset of the
 metaweb's species and interactions, and have been called ``metaweb
-realizations'' (Poisot \emph{et al.} 2015). Differences between local
-food web and their metaweb are due to chance, species abundance and
+realizations'' (Poisot et al., 2015). Differences between local food web
+and their metaweb are due to chance, species abundance and
 co-occurrence, local environmental conditions, and local distribution of
@@
 Because the metaweb represents the joint effect of functional,
-phylogenetic, and macroecological processes (Morales-Castilla \emph{et
-al.} 2015), it holds valuable ecological information. Specifically, it
-is the ``upper bounds'' on what the composition of the local networks
-can be (see \emph{e.g.} McLeod \emph{et al.} 2021). These local
-networks, in turn, can be reconstructed given appropriate knowledge of
-local species composition, providing information on structure of food
-webs at finer spatial scales. This has been done for example for
-tree-galler-parasitoid systems (Gravel \emph{et al.} 2018), fish trophic
-interactions (Albouy \emph{et al.} 2019), tetrapod trophic interactions
-(O'Connor \emph{et al.} 2020), and crop-pest networks (Grünig \emph{et
-al.} 2020). Whereas the original metaweb definition, and indeed most
-past uses of metawebs, was based on the presence/absence of
-interactions, we focus on \emph{probabilistic} metawebs where
-interactions are represented as the chance of success of a Bernoulli
-trial (see \emph{e.g.} Poisot \emph{et al.} 2016); therefore, not only
-does our method recommend interactions that may exist, it gives each
-interaction a score, allowing us to properly weigh them.
+phylogenetic, and macroecological processes (Morales-Castilla et al.,
+2015), it holds valuable ecological information. Specifically, it is the
+``upper bounds'' on what the composition of the local networks can be
+(see \emph{e.g.} McLeod et al., 2021). These local networks, in turn,
+can be reconstructed given appropriate knowledge of local species
+composition, providing information on structure of food webs at finer
+spatial scales. This has been done for example for
+tree-galler-parasitoid systems (Gravel et al., 2018), fish trophic
+interactions (Albouy et al., 2019), tetrapod trophic interactions
+(O'Connor et al., 2020), and crop-pest networks (Grünig et al., 2020).
+Whereas the original metaweb definition, and indeed most past uses of
+metawebs, was based on the presence/absence of interactions, we focus on
+\emph{probabilistic} metawebs where interactions are represented as the
+chance of success of a Bernoulli trial (see \emph{e.g.} Poisot et al.,
+2016); therefore, not only does our method recommend interactions that
+may exist, it gives each interaction a score, allowing us to properly
+weigh them.
 
@@
 documented instances of food webs undergoing rapid collapse/recovery
-cycles over short periods of time (Pedersen \emph{et al.} 2017). The
-embedding of a network, in a sense, embeds its macro-evolutionary
-history, especially as RDPG captures ecological signal (Dalla Riva \&
-Stouffer 2016); at this point, it is important to recall that a metaweb
-is intended as a catalogue of all potential interactions, which should
-then be filtered (Morales-Castilla \emph{et al.} 2015). In practice (and
-in this instance) the reconstructed metaweb will predict interactions
-that are plausible based on the species' evolutionary history, however
-some interactions would/would not be realized due to human impact.
+cycles over short periods of time (Pedersen et al., 2017). The embedding
+of a network, in a sense, embeds its macro-evolutionary history,
+especially as RDPG captures ecological signal (Dalla Riva \& Stouffer,
+2016); at this point, it is important to recall that a metaweb is
+intended as a catalogue of all potential interactions, which should then
+be filtered (Morales-Castilla et al., 2015). In practice (and in this
+instance) the reconstructed metaweb will predict interactions that are
+plausible based on the species' evolutionary history, however some
+interactions would/would not be realized due to human impact.
 
-Dallas \emph{et al.} (2017) suggested that most links in ecological
-networks may be cryptic, \emph{i.e.} uncommon or otherwise hard to
-observe. This argument essentially echoes Jordano (2016): the sampling
-of ecological interactions is difficult because it requires first the
-joint observation of two species, and then the observation of their
+Dallas et al. (2017) suggested that most links in ecological networks
+may be cryptic, \emph{i.e.} uncommon or otherwise hard to observe. This
+argument essentially echoes Jordano (2016): the sampling of ecological
+interactions is difficult because it requires first the joint
+observation of two species, and then the observation of their
 interaction. In addition, it is generally expected that weak or rare
-links would be more common in networks (Csermely 2004), compared to
+links would be more common in networks (Csermely, 2004), compared to
 strong, persistent links; this is notably the case in food chains,
 wherein many weaker links are key to the stability of a system (Neutel
-\emph{et al.} 2002). In the light of these observations, the results in
+et al., 2002). In the light of these observations, the results in
 fig.~\ref{fig:inflation} are not particularly surprising: we expect to
@@
 learning algorithms, in these situations, can act as data generators
-(Hoffmann \emph{et al.} 2019): in this perspective, high quality
-observational data can be supplemented with synthetic data coming from
-predictive models, which increases the volume of information available
-for inference. Indeed, Strydom \emph{et al.} (2021) suggested that
-knowing the metaweb may render the prediction of local networks easier,
-because it fixes an ``upper bound'' on which interactions can exist;
-indeed, with a probabilistic metaweb, we can consider that the metaweb
-represents an aggregation of informative priors on the interactions.
+(Hoffmann et al., 2019): in this perspective, high quality observational
+data can be supplemented with synthetic data coming from predictive
+models, which increases the volume of information available for
+inference. Indeed, Strydom et al. (2021) suggested that knowing the
+metaweb may render the prediction of local networks easier, because it
+fixes an ``upper bound'' on which interactions can exist; indeed, with a
+probabilistic metaweb, we can consider that the metaweb represents an
+aggregation of informative priors on the interactions.
 
@@
 assessment, as each country tends to set goals at the national level
-(Buxton \emph{et al.} 2021) for which quantitative instruments are
-designed (Turak \emph{et al.} 2017), with specific strategies often
-enacted at smaller scales (Ray \emph{et al.} 2021). And yet, we do not
-really have a satisfying answer to the question of ``where does a food
-web stop?''; the current most satisfying solutions involve examining the
-spatial consistency of network area relationships (see \emph{e.g.}
-Galiana \emph{et al.} 2018, 2019, 2021; \textbf{Fortin2021NetEco?}),
-which is of course impossible in the absence of enough information about
-the network itself. This suggests that an \emph{a posteriori} refinement
-of the results may be required, based on a downscaling of the metaweb.
-The final family of problems relates less to the availability of data or
-quantitative tools, and more to the praxis of spatial ecology. Operating
-under the context of national divisions, in large parts of the world,
-reflects nothing more than the legacy of settler colonialism. Indeed,
-the use of ecological data is not an apolitical act (Nost \& Goldstein
-2021), as data infrastructures tend to be designed to answer questions
-within national boundaries, and their use both draws upon and reinforces
-territorial statecraft; as per Machen \& Nost (2021), this is
-particularly true when the output of ``algorithmic thinking''
-(\emph{e.g.} relying on machine learning to generate knowledge) can be
-re-used for governance (\emph{e.g.} enacting conservation decisions at
-the national scale). We therefore recognize that methods such as we
-propose operate under the framework that contributed to the ongoing
-biodiversity crisis (Adam 2014), reinforced environmental injustice
-(Choudry 2013; Domínguez \& Luoma 2020), and on Turtle Island
-especially, should be replaced by Indigenous principles of land
-management (Eichhorn \emph{et al.} 2019; No'kmaq \emph{et al.} 2021). As
-we see AI/ML being increasingly mobilized to generate knowledge that is
-lacking for conservation decisions (\emph{e.g.} Lamba \emph{et al.}
-2019; Mosebo Fernandes \emph{et al.} 2020), our discussion of these
+(Buxton et al., 2021) for which quantitative instruments are designed
+(Turak et al., 2017), with specific strategies often enacted at smaller
+scales (Ray et al., 2021). And yet, we do not really have a satisfying
+answer to the question of ``where does a food web stop?''; the current
+most satisfying solutions involve examining the spatial consistency of
+network area relationships (see \emph{e.g.} Galiana et al., 2018, 2019,
+2021; \textbf{Fortin2021NetEco?}), which is of course impossible in the
+absence of enough information about the network itself. This suggests
+that an \emph{a posteriori} refinement of the results may be required,
+based on a downscaling of the metaweb. The final family of problems
+relates less to the availability of data or quantitative tools, and more
+to the praxis of spatial ecology. Operating under the context of
+national divisions, in large parts of the world, reflects nothing more
+than the legacy of settler colonialism. Indeed, the use of ecological
+data is not an apolitical act (Nost \& Goldstein, 2021), as data
+infrastructures tend to be designed to answer questions within national
+boundaries, and their use both draws upon and reinforces territorial
+statecraft; as per Machen \& Nost (2021), this is particularly true when
+the output of ``algorithmic thinking'' (\emph{e.g.} relying on machine
+learning to generate knowledge) can be re-used for governance
+(\emph{e.g.} enacting conservation decisions at the national scale). We
+therefore recognize that methods such as we propose operate under the
+framework that contributed to the ongoing biodiversity crisis (Adam,
+2014), reinforced environmental injustice (Choudry, 2013; Domínguez \&
+Luoma, 2020), and on Turtle Island especially, should be replaced by
+Indigenous principles of land management (Eichhorn et al., 2019; No'kmaq
+et al., 2021). As we see AI/ML being increasingly mobilized to generate
+knowledge that is lacking for conservation decisions (\emph{e.g.} Lamba
+et al., 2019; Mosebo Fernandes et al., 2020), our discussion of these
 tools need to go beyond the technical, and into the governance
@@
 \leavevmode\hypertarget{ref-Albouy2019MarFis}{}%
-Albouy, C., Archambault, P., Appeltans, W., Araújo, M.B., Beauchesne,
-D., Cazelles, K., \emph{et al.} (2019). The marine fish food web is
-globally connected. \emph{Nature Ecology \& Evolution}, 3, 1153--1161.
+Albouy, C., Archambault, P., Appeltans, W., Araújo, M. B., Beauchesne,
+D., Cazelles, K., Cirtwill, A. R., Fortin, M.-J., Galiana, N., Leroux,
+S. J., Pellissier, L., Poisot, T., Stouffer, D. B., Wood, S. A., \&
+Gravel, D. (2019). The marine fish food web is globally connected.
+\emph{Nature Ecology \& Evolution}, \emph{3}(8, 8), 1153--1161.
+\url{https://doi.org/10.1038/s41559-019-0950-y}
 
 \leavevmode\hypertarget{ref-Buxton2021KeyInf}{}%
-Buxton, R.T., Bennett, J.R., Reid, A.J., Shulman, C., Cooke, S.J.,
-Francis, C.M., \emph{et al.} (2021). Key information needs to move from
+Buxton, R. T., Bennett, J. R., Reid, A. J., Shulman, C., Cooke, S. J.,
+Francis, C. M., Nyboer, E. A., Pritchard, G., Binley, A. D., Avery-Gomm,
+S., Ban, N. C., Beazley, K. F., Bennett, E., Blight, L. K., Bortolotti,
+L. E., Camfield, A. F., Gadallah, F., Jacob, A. L., Naujokaitis-Lewis,
+I., \ldots{} Smith, P. A. (2021). Key information needs to move from
 knowledge to action for biodiversity conservation in Canada.
-\emph{Biological Conservation}, 256, 108983.
+\emph{Biological Conservation}, \emph{256}, 108983.
+\url{https://doi.org/10.1016/j.biocon.2021.108983}
 
@@
 Conservation NGOs, complicity, colonialism and conquest in an era of
-capitalist globalization. In: \emph{NGOization: Complicity,
-contradictions and prospects}. Bloomsbury Publishing, pp. 24--44.
+capitalist globalization. In \emph{NGOization: Complicity,
+contradictions and prospects} (pp. 24--44). Bloomsbury Publishing.
 
@@
 Csermely, P. (2004). Strong links are important, but weak links
-stabilize them. \emph{Trends in Biochemical Sciences}, 29, 331--334.
+stabilize them. \emph{Trends in Biochemical Sciences}, \emph{29}(7),
+331--334. \url{https://doi.org/10.1016/j.tibs.2004.05.004}
 
 \leavevmode\hypertarget{ref-DallaRiva2016ExpEvo}{}%
-Dalla Riva, G.V. \& Stouffer, D.B. (2016). Exploring the evolutionary
+Dalla Riva, G. V., \& Stouffer, D. B. (2016). Exploring the evolutionary
 signature of food webs' backbones using functional traits. \emph{Oikos},
-125, 446--456.
+\emph{125}(4), 446--456. \url{https://doi.org/10.1111/oik.02305}
 
 \leavevmode\hypertarget{ref-Dallas2017PreCry}{}%
-Dallas, T., Park, A.W. \& Drake, J.M. (2017). Predicting cryptic links
-in host-parasite networks. \emph{PLOS Computational Biology}, 13,
-e1005557.
+Dallas, T., Park, A. W., \& Drake, J. M. (2017). Predicting cryptic
+links in host-parasite networks. \emph{PLOS Computational Biology},
+\emph{13}(5), e1005557.
+\url{https://doi.org/10.1371/journal.pcbi.1005557}
 
 \leavevmode\hypertarget{ref-Dominguez2020DecCon}{}%
-Domínguez, L. \& Luoma, C. (2020). Decolonising Conservation Policy: How
-Colonial Land and Conservation Ideologies Persist and Perpetuate
-Indigenous Injustices at the Expense of the Environment. \emph{Land}, 9,
-65.
+Domínguez, L., \& Luoma, C. (2020). Decolonising Conservation Policy:
+How Colonial Land and Conservation Ideologies Persist and Perpetuate
+Indigenous Injustices at the Expense of the Environment. \emph{Land},
+\emph{9}(3, 3), 65. \url{https://doi.org/10.3390/land9030065}
 
 \leavevmode\hypertarget{ref-Dunne2006NetStr}{}%
-Dunne, J.A. (2006). The Network Structure of Food Webs. In:
-\emph{Ecological networks: Linking structure and dynamics} (eds. Dunne,
-J.A. \& Pascual, M.). Oxford University Press, pp. 27--86.
+Dunne, J. A. (2006). The Network Structure of Food Webs. In J. A. Dunne
+\& M. Pascual (Eds.), \emph{Ecological networks: Linking structure and
+dynamics} (pp. 27--86). Oxford University Press.
 
 \leavevmode\hypertarget{ref-Eichhorn2019SteDec}{}%
-Eichhorn, M.P., Baker, K. \& Griffiths, M. (2019). Steps towards
-decolonising biogeography. \emph{Frontiers of Biogeography}, 12, 1--7.
+Eichhorn, M. P., Baker, K., \& Griffiths, M. (2019). Steps towards
+decolonising biogeography. \emph{Frontiers of Biogeography},
+\emph{12}(1), 1--7. \url{https://doi.org/10.21425/F5FBG44795}
 
 \leavevmode\hypertarget{ref-Galiana2021SpaSca}{}%
-Galiana, N., Barros, C., Braga, J., Ficetola, G.F., Maiorano, L.,
-Thuiller, W., \emph{et al.} (2021). The spatial scaling of food web
-structure across European biogeographical regions. \emph{Ecography},
-n/a.
+Galiana, N., Barros, C., Braga, J., Ficetola, G. F., Maiorano, L.,
+Thuiller, W., Montoya, J. M., \& Lurgi, M. (2021). The spatial scaling
+of food web structure across European biogeographical regions.
+\emph{Ecography}, \emph{n/a}(n/a).
+\url{https://doi.org/10.1111/ecog.05229}
 
 \leavevmode\hypertarget{ref-Galiana2019GeoVar}{}%
-Galiana, N., Hawkins, B.A. \& Montoya, J.M. (2019). The geographical
+Galiana, N., Hawkins, B. A., \& Montoya, J. M. (2019). The geographical
 variation of network structure is scale dependent: Understanding the
 biotic specialization of host--parasitoid networks. \emph{Ecography},
-42, 1175--1187.
+\emph{42}(6), 1175--1187. \url{https://doi.org/10.1111/ecog.03684}
 
@@
 Galiana, N., Lurgi, M., Claramunt-López, B., Fortin, M.-J., Leroux, S.,
-Cazelles, K., \emph{et al.} (2018). The spatial scaling of species
-interaction networks. \emph{Nature Ecology \& Evolution}, 2, 782--790.
+Cazelles, K., Gravel, D., \& Montoya, J. M. (2018). The spatial scaling
+of species interaction networks. \emph{Nature Ecology \& Evolution},
+\emph{2}(5), 782--790. \url{https://doi.org/10.1038/s41559-018-0517-3}
 
 \leavevmode\hypertarget{ref-Gravel2018BriElt}{}%
-Gravel, D., Baiser, B., Dunne, J.A., Kopelke, J.-P., Martinez, N.D.,
-Nyman, T., \emph{et al.} (2018). Bringing Elton and Grinnell together: A
+Gravel, D., Baiser, B., Dunne, J. A., Kopelke, J.-P., Martinez, N. D.,
+Nyman, T., Poisot, T., Stouffer, D. B., Tylianakis, J. M., Wood, S. A.,
+\& Roslin, T. (2018). Bringing Elton and Grinnell together: A
 quantitative framework to represent the biogeography of ecological
-interaction networks. \emph{Ecography}, 0.
+interaction networks. \emph{Ecography}, \emph{0}(0).
+\url{https://doi.org/10.1111/ecog.04006}
 
 \leavevmode\hypertarget{ref-Grunig2020CroFor}{}%
-Grünig, M., Mazzi, D., Calanca, P., Karger, D.N. \& Pellissier, L.
+Grünig, M., Mazzi, D., Calanca, P., Karger, D. N., \& Pellissier, L.
 (2020). Crop and forest pest metawebs shift towards increased linkage
 and suitability overlap under climate change. \emph{Communications
-Biology}, 3, 1--10.
+Biology}, \emph{3}(1, 1), 1--10.
+\url{https://doi.org/10.1038/s42003-020-0962-9}
 
 \leavevmode\hypertarget{ref-Herbert1965Dun}{}%
-Herbert, F. (1965). \emph{Dune}. 1st edn. Chilton Book Company,
-Philadelphia.
+Herbert, F. (1965). \emph{Dune} (1st ed.). Chilton Book Company.
 
 \leavevmode\hypertarget{ref-Hoffmann2019MacLea}{}%
-Hoffmann, J., Bar-Sinai, Y., Lee, L.M., Andrejevic, J., Mishra, S.,
-Rubinstein, S.M., \emph{et al.} (2019). Machine learning in a
+Hoffmann, J., Bar-Sinai, Y., Lee, L. M., Andrejevic, J., Mishra, S.,
+Rubinstein, S. M., \& Rycroft, C. H. (2019). Machine learning in a
 data-limited regime: Augmenting experiments with synthetic data uncovers
-order in crumpled sheets. \emph{Science Advances}, 5, eaau6792.
+order in crumpled sheets. \emph{Science Advances}, \emph{5}(4),
+eaau6792. \url{https://doi.org/10.1126/sciadv.aau6792}
 
@@
 Jordano, P. (2016). Sampling networks of ecological interactions.
-\emph{Functional Ecology}, 30, 1883--1893.
+\emph{Functional Ecology}, \emph{30}(12), 1883--1893.
+\url{https://doi.org/10.1111/1365-2435.12763}
 
 \leavevmode\hypertarget{ref-Lamba2019DeeLea}{}%
-Lamba, A., Cassey, P., Segaran, R.R. \& Koh, L.P. (2019). Deep learning
-for environmental conservation. \emph{Current Biology}, 29, R977--R982.
+Lamba, A., Cassey, P., Segaran, R. R., \& Koh, L. P. (2019). Deep
+learning for environmental conservation. \emph{Current Biology},
+\emph{29}(19), R977--R982.
+\url{https://doi.org/10.1016/j.cub.2019.08.016}
 
 \leavevmode\hypertarget{ref-Machen2021ThiAlg}{}%
-Machen, R. \& Nost, E. (2021). Thinking algorithmically: The making of
+Machen, R., \& Nost, E. (2021). Thinking algorithmically: The making of
 hegemonic knowledge in climate governance. \emph{Transactions of the
-Institute of British Geographers}, 46, 555--569.
+Institute of British Geographers}, \emph{46}(3), 555--569.
+\url{https://doi.org/10.1111/tran.12441}
 
 \leavevmode\hypertarget{ref-McLeod2021SamAsy}{}%
-McLeod, A., Leroux, S.J., Gravel, D., Chu, C., Cirtwill, A.R., Fortin,
-M.-J., \emph{et al.} (2021). Sampling and asymptotic network properties
-of spatial multi-trophic networks. \emph{Oikos}, n/a.
+McLeod, A., Leroux, S. J., Gravel, D., Chu, C., Cirtwill, A. R., Fortin,
+M.-J., Galiana, N., Poisot, T., \& Wood, S. A. (2021). Sampling and
+asymptotic network properties of spatial multi-trophic networks.
+\emph{Oikos}, \emph{n/a}(n/a). \url{https://doi.org/10.1111/oik.08650}
 
 \leavevmode\hypertarget{ref-Morales-Castilla2015InfBio}{}%
-Morales-Castilla, I., Matias, M.G., Gravel, D. \& Araújo, M.B. (2015).
-Inferring biotic interactions from proxies. \emph{Trends in Ecology \&
-Evolution}, 30, 347--356.
+Morales-Castilla, I., Matias, M. G., Gravel, D., \& Araújo, M. B.
+(2015). Inferring biotic interactions from proxies. \emph{Trends in
+Ecology \& Evolution}, \emph{30}(6), 347--356.
+\url{https://doi.org/10.1016/j.tree.2015.03.014}
 
 \leavevmode\hypertarget{ref-MoseboFernandes2020MacLea}{}%
-Mosebo Fernandes, A.C., Quintero Gonzalez, R., Lenihan-Clarke, M.A.,
-Leslie Trotter, E.F. \& Jokar Arsanjani, J. (2020). Machine Learning for
-Conservation Planning in a Changing Climate. \emph{Sustainability}, 12,
-7657.
+Mosebo Fernandes, A. C., Quintero Gonzalez, R., Lenihan-Clarke, M. A.,
+Leslie Trotter, E. F., \& Jokar Arsanjani, J. (2020). Machine Learning
+for Conservation Planning in a Changing Climate. \emph{Sustainability},
+\emph{12}(18, 18), 7657. \url{https://doi.org/10.3390/su12187657}
 
 \leavevmode\hypertarget{ref-Neutel2002StaRea}{}%
-Neutel, A.-M., Heesterbeek, J.A.P. \& de Ruiter, P.C. (2002). Stability
-in Real Food Webs: Weak Links in Long Loops. \emph{Science}, 296,
-1120--1123.
+Neutel, A.-M., Heesterbeek, J. A. P., \& de Ruiter, P. C. (2002).
+Stability in Real Food Webs: Weak Links in Long Loops. \emph{Science},
+\emph{296}(5570), 1120--1123.
+\url{https://doi.org/10.1126/science.1068326}
 
 \leavevmode\hypertarget{ref-Nokmaq2021AwaSle}{}%
-No'kmaq, M., Marshall, A., Beazley, K.F., Hum, J., joudry, shalan,
-Papadopoulos, A., \emph{et al.} (2021). {``Awakening the sleeping
-giant''}: Re-Indigenization principles for transforming biodiversity
-conservation in Canada and beyond. \emph{FACETS}, 6, 839--869.
+No'kmaq, M., Marshall, A., Beazley, K. F., Hum, J., joudry, shalan,
+Papadopoulos, A., Pictou, S., Rabesca, J., Young, L., \& Zurba, M.
+(2021). {``Awakening the sleeping giant''}: Re-Indigenization principles
+for transforming biodiversity conservation in Canada and beyond.
+\emph{FACETS}, \emph{6}(1), 839--869.
 
 \leavevmode\hypertarget{ref-Nost2021PolEco}{}%
-Nost, E. \& Goldstein, J.E. (2021). A political ecology of data.
+Nost, E., \& Goldstein, J. E. (2021). A political ecology of data.
 \emph{Environment and Planning E: Nature and Space}, 25148486211043503.
+\url{https://doi.org/10.1177/25148486211043503}
 
 \leavevmode\hypertarget{ref-OConnor2020UnvFoo}{}%
-O'Connor, L.M.J., Pollock, L.J., Braga, J., Ficetola, G.F., Maiorano,
-L., Martinez‐Almoyna, C., \emph{et al.} (2020). Unveiling the food webs
-of tetrapods across Europe through the prism of the Eltonian niche.
-\emph{Journal of Biogeography}, 47, 181--192.
+O'Connor, L. M. J., Pollock, L. J., Braga, J., Ficetola, G. F.,
+Maiorano, L., Martinez‐Almoyna, C., Montemaggiori, A., Ohlmann, M., \&
+Thuiller, W. (2020). Unveiling the food webs of tetrapods across Europe
+through the prism of the Eltonian niche. \emph{Journal of Biogeography},
+\emph{47}(1), 181--192. \url{https://doi.org/10.1111/jbi.13773}
 
 \leavevmode\hypertarget{ref-Pedersen2017SigCol}{}%
-Pedersen, E.J., Thompson, P.L., Ball, R.A., Fortin, M.-J., Gouhier,
-T.C., Link, H., \emph{et al.} (2017). Signatures of the collapse and
-incipient recovery of an overexploited marine ecosystem. \emph{Royal
-Society Open Science}, 4, 170215.
+Pedersen, E. J., Thompson, P. L., Ball, R. A., Fortin, M.-J., Gouhier,
+T. C., Link, H., Moritz, C., Nenzen, H., Stanley, R. R. E., Taranu, Z.
+E., Gonzalez, A., Guichard, F., \& Pepin, P. (2017). Signatures of the
+collapse and incipient recovery of an overexploited marine ecosystem.
+\emph{Royal Society Open Science}, \emph{4}(7), 170215.
+\url{https://doi.org/10.1098/rsos.170215}
 
 \leavevmode\hypertarget{ref-Poisot2016StrPro}{}%
-Poisot, T., Cirtwill, A.R., Cazelles, K., Gravel, D., Fortin, M.-J. \&
-Stouffer, D.B. (2016). The structure of probabilistic networks.
-\emph{Methods in Ecology and Evolution}, 7, 303--312.
+Poisot, T., Cirtwill, A. R., Cazelles, K., Gravel, D., Fortin, M.-J., \&
+Stouffer, D. B. (2016). The structure of probabilistic networks.
+\emph{Methods in Ecology and Evolution}, \emph{7}(3), 303--312.
+\url{https://doi.org/10.1111/2041-210X.12468}
 
 \leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%
-Poisot, T., Stouffer, D.B. \& Gravel, D. (2015). Beyond species: Why
+Poisot, T., Stouffer, D. B., \& Gravel, D. (2015). Beyond species: Why
 ecological interaction networks vary through space and time.
-\emph{Oikos}, 124, 243--251.
+\emph{Oikos}, \emph{124}(3), 243--251.
+\url{https://doi.org/10.1111/oik.01719}
 
 \leavevmode\hypertarget{ref-Ray2021BioCri}{}%
-Ray, J.C., Grimm, J. \& Olive, A. (2021). The biodiversity crisis in
+Ray, J. C., Grimm, J., \& Olive, A. (2021). The biodiversity crisis in
 Canada: Failures and challenges of federal and sub-national strategic
-and legal frameworks. \emph{FACETS}, 6, 1044--1068.
+and legal frameworks. \emph{FACETS}, \emph{6}, 1044--1068.
+\url{https://doi.org/10.1139/facets-2020-0075}
 
 \leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
-Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
-Desjardins-Proulx, P., \emph{et al.} (2021). A roadmap towards
-predicting species interaction networks (across space and time).
+Strydom, T., Catchen, M. D., Banville, F., Caron, D., Dansereau, G.,
+Desjardins-Proulx, P., Forero-Muñoz, N. R., Higino, G., Mercier, B.,
+Gonzalez, A., Gravel, D., Pollock, L., \& Poisot, T. (2021). A roadmap
+towards predicting species interaction networks (across space and time).
 \emph{Philosophical Transactions of the Royal Society B: Biological
-Sciences}, 376, 20210063.
+Sciences}, \emph{376}(1837), 20210063.
+\url{https://doi.org/10.1098/rstb.2021.0063}
 
@@
 Turak, E., Brazill-Boast, J., Cooney, T., Drielsma, M., DelaCruz, J.,
-Dunkerley, G., \emph{et al.} (2017). Using the essential biodiversity
-variables framework to measure biodiversity change at national scale.
-\emph{Biological Conservation}, SI:Measures of biodiversity, 213,
-264--271.
+Dunkerley, G., Fernandez, M., Ferrier, S., Gill, M., Jones, H., Koen,
+T., Leys, J., McGeoch, M., Mihoub, J.-B., Scanes, P., Schmeller, D., \&
+Williams, K. (2017). Using the essential biodiversity variables
+framework to measure biodiversity change at national scale.
+\emph{Biological Conservation}, \emph{213}, 264--271.
+\url{https://doi.org/10.1016/j.biocon.2016.08.019}
 
 \leavevmode\hypertarget{ref-Wood2015EffSpa}{}%
-Wood, S.A., Russell, R., Hanson, D., Williams, R.J. \& Dunne, J.A.
+Wood, S. A., Russell, R., Hanson, D., Williams, R. J., \& Dunne, J. A.
 (2015). Effects of spatial scale of sampling on food web structure.
-\emph{Ecology and Evolution}, 5, 3769--3782.
+\emph{Ecology and Evolution}, \emph{5}(17), 3769--3782.
+\url{https://doi.org/10.1002/ece3.1640}
 

### 2022-01-12 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@d28b8b3c89251398e36e6b7d499d0f6d253e4e4b 🚀

@@
 {\small{\bfseries Keywords}:\par
-pandoc\\pandoc-crossref\\github actions\\}
+ecological networks\\network embedding\\transfer learning\\network
+macroecology\\}
 }

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@e0a1165d0847969b43135297d89dacdc6dda7a11 🚀

@@
 
+\hypertarget{the-metaweb-is-an-inherently-probabilistic-object}{%
+\section{The metaweb is an inherently probabilistic
+object}\label{the-metaweb-is-an-inherently-probabilistic-object}}
+
 Yet, owing to the inherent plasticity of interactions, there have been
@@
 aggregation of informative priors on the interactions.
+
+\hypertarget{graph-embedding-offers-promises-the-inference-of-potential-interactions}{%
+\section{Graph embedding offers promises the inference of potential
+interactions}\label{graph-embedding-offers-promises-the-inference-of-potential-interactions}}
+
+\hypertarget{the-metaweb-embeds-hypotheses-about-which-spatial-boundaries-are-meaningful}{%
+\section{The metaweb embeds hypotheses about which spatial boundaries
+are
+meaningful}\label{the-metaweb-embeds-hypotheses-about-which-spatial-boundaries-are-meaningful}}
 

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@dd5b75b2340b0fe071253c8809c060f062871007 🚀

@@
 \begin{enumerate}
-    \itemMetawebs, i.e.~networks of potential interactions within a
+    \item Metawebs, i.e.~networks of potential interactions within a
 species pool, are a powerful abstraction to understand how large-scales
 species interaction networks are structured.%
-    \itemBecause metawebs are typically expressed at large spatial and
+    \item Because metawebs are typically expressed at large spatial and
 taxonomic scales, assembling them is a tedious and costly process;
@@
 deficiencies, by providing `draft' metawebs.%
-    \itemOne way to improve the predictive ability is to maximize the
+    \item One way to improve the predictive ability is to maximize the
 information used for prediction, by using graph embeddings rather than
@@
 in machine learning that holds great potential for ecoloigcal problems.%
-    \itemIn this perspective, we outline how the challenges associated
+    \item In this perspective, we outline how the challenges associated
 with infering metawebs line-up with the advantages of graph embeddings;

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@cad17d0c61090808efb3000abea680b23ff70b42 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@410f3a3ee07f1121afa8ff608dd9335ab4169044 🚀

@@
 
+Graph embedding is a varied family of machine learning techniques aiming
+to transform nodes and edges into a vector space, usually of a lower
+dimension, whilst maximally retaining key properties of the graph.
+Ecological networks are an interesting candidate for the widespread
+application of embeddings, as they tend to posess a shared sstructural
+backbone (Mora et al., 2018), which hints at structural invariants that
+can be revealed a lower dimensions. Indeed, previous work by
+(\textbf{Eklof2013DimEco?}) suggests that food webs are inherently
+low-dimensional objects, and can be adequately represented with less
+than ten dimensions.
+
 \hypertarget{the-metaweb-embeds-hypotheses-about-which-spatial-boundaries-are-meaningful}{%
@@
 programs.
+
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
 
@@
 
+\leavevmode\hypertarget{ref-Mora2018IdeCom}{}%
+Mora, B. B., Gravel, D., Gilarranz, L. J., Poisot, T., \& Stouffer, D.
+B. (2018). Identifying a common backbone of interactions underlying food
+webs from different ecosystems. \emph{Nature Communications},
+\emph{9}(1), 2603. \url{https://doi.org/10.1038/s41467-018-05056-0}
+
 \leavevmode\hypertarget{ref-Morales-Castilla2015InfBio}{}%

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@163eb539dcb188f582e97cd285727488ed612c1e 🚀

@@
 
+The popularity of graph embedding techniques in machine learning is
+rather intuitive: while graphs are discrete objects, machine learning
+techniques tend to handle continuous data better. Therefore, bringing a
+discrete graph into a continuous vector space opens up a broader variety
+of predictive algorithms.
+
+\begin{longtable}[]{@{}lll@{}}
+\toprule
+Method & Embedded object & Reference\tabularnewline
+\midrule
+\endhead
+DeepWalk & graph walk & Perozzi et al. (2014)\tabularnewline
+node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
+\bottomrule
+\end{longtable}
+
 \hypertarget{the-metaweb-embeds-hypotheses-about-which-spatial-boundaries-are-meaningful}{%
@@
 
+\leavevmode\hypertarget{ref-Grover2016NodSca}{}%
+Grover, A., \& Leskovec, J. (2016). Node2vec: Scalable Feature Learning
+for Networks. \emph{Proceedings of the 22nd ACM SIGKDD International
+Conference on Knowledge Discovery and Data Mining}, 855--864.
+\url{https://doi.org/10.1145/2939672.2939754}
+
 \leavevmode\hypertarget{ref-Grunig2020CroFor}{}%
@@
 
+\leavevmode\hypertarget{ref-Perozzi2014DeeOnl}{}%
+Perozzi, B., Al-Rfou, R., \& Skiena, S. (2014). DeepWalk: Online
+learning of social representations. \emph{Proceedings of the 20th ACM
+SIGKDD International Conference on Knowledge Discovery and Data Mining},
+701--710. \url{https://doi.org/10.1145/2623330.2623732}
+
 \leavevmode\hypertarget{ref-Poisot2016StrPro}{}%

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@0de5f26cf496d1a6a2c7f84605472734d9ca3027 🚀

@@
 node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
+graph2vec & sub-graph embedding & Narayanan et al. (2017)\tabularnewline
 \bottomrule
@@
 
+\leavevmode\hypertarget{ref-Narayanan2017GraLea}{}%
+Narayanan, A., Chandramohan, M., Venkatesan, R., Chen, L., Liu, Y., \&
+Jaiswal, S. (2017, July 17). \emph{Graph2vec: Learning Distributed
+Representations of Graphs}. \url{http://arxiv.org/abs/1707.05005}
+
 \leavevmode\hypertarget{ref-Neutel2002StaRea}{}%

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@376cc0382d84569713c4264a73c30f1f8c81ca15 🚀

@@
 backbone (Mora et al., 2018), which hints at structural invariants that
-can be revealed a lower dimensions. Indeed, previous work by
-(\textbf{Eklof2013DimEco?}) suggests that food webs are inherently
-low-dimensional objects, and can be adequately represented with less
-than ten dimensions.
+can be revealed a lower dimensions. Indeed, previous work by Eklöf et
+al. (2013) suggests that food webs are inherently low-dimensional
+objects, and can be adequately represented with less than ten
+dimensions.
 
@@
 \emph{12}(1), 1--7. \url{https://doi.org/10.21425/F5FBG44795}
+
+\leavevmode\hypertarget{ref-Eklof2013DimEco}{}%
+Eklöf, A., Jacob, U., Kopp, J., Bosch, J., Castro-Urgal, R., Chacoff, N.
+P., Dalsgaard, B., de Sassi, C., Galetti, M., Guimarães, P. R.,
+Lomáscolo, S. B., Martín González, A. M., Pizo, M. A., Rader, R.,
+Rodrigo, A., Tylianakis, J. M., Vázquez, D. P., \& Allesina, S. (2013).
+The dimensionality of ecological networks. \emph{Ecology Letters},
+\emph{16}(5), 577--583. \url{https://doi.org/10.1111/ele.12081}
 

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@699c8756b24d696b38e4476ceb811a802c5c49e5 🚀

@@
 
-\hypertarget{graph-embedding-offers-promises-the-inference-of-potential-interactions}{%
-\section{Graph embedding offers promises the inference of potential
-interactions}\label{graph-embedding-offers-promises-the-inference-of-potential-interactions}}
+\hypertarget{graph-embedding-offers-promises-for-the-inference-of-potential-interactions}{%
+\section{Graph embedding offers promises for the inference of potential
+interactions}\label{graph-embedding-offers-promises-for-the-inference-of-potential-interactions}}
 
@@
 graph2vec & sub-graph embedding & Narayanan et al. (2017)\tabularnewline
+SDNE & nodes through auto-encoding & Wang et al. (2016)\tabularnewline
 \bottomrule
@@
 
+\leavevmode\hypertarget{ref-Wang2016StrDee}{}%
+Wang, D., Cui, P., \& Zhu, W. (2016). Structural Deep Network Embedding.
+\emph{Proceedings of the 22nd ACM SIGKDD International Conference on
+Knowledge Discovery and Data Mining}, 1225--1234.
+\url{https://doi.org/10.1145/2939672.2939753}
+
 \leavevmode\hypertarget{ref-Wood2015EffSpa}{}%

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@d40d6d0710dd8c097b5a8838037bd0b10591c046 🚀

@@
 to transform nodes and edges into a vector space, usually of a lower
-dimension, whilst maximally retaining key properties of the graph.
-Ecological networks are an interesting candidate for the widespread
-application of embeddings, as they tend to posess a shared sstructural
-backbone (Mora et al., 2018), which hints at structural invariants that
-can be revealed a lower dimensions. Indeed, previous work by Eklöf et
-al. (2013) suggests that food webs are inherently low-dimensional
-objects, and can be adequately represented with less than ten
-dimensions.
+dimension, whilst maximally retaining key properties of the graph (Yan
+et al., 2005). Ecological networks are an interesting candidate for the
+widespread application of embeddings, as they tend to posess a shared
+sstructural backbone (Mora et al., 2018), which hints at structural
+invariants that can be revealed a lower dimensions. Indeed, previous
+work by Eklöf et al. (2013) suggests that food webs are inherently
+low-dimensional objects, and can be adequately represented with less
+than ten dimensions.
 
@@
 \toprule
-Method & Embedded object & Reference\tabularnewline
+Method & Embedding approach & Reference\tabularnewline
 \midrule
@@
 DeepWalk & graph walk & Perozzi et al. (2014)\tabularnewline
+FastEmbed & graph through PCA/SVD analogue & Ramasamy \& Madhow
+(2015)\tabularnewline
+LINE & nodes through statistical divergence & Tang et al.
+(2015)\tabularnewline
+SDNE & nodes through auto-encoding & Wang et al. (2016)\tabularnewline
 node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
 graph2vec & sub-graph embedding & Narayanan et al. (2017)\tabularnewline
-SDNE & nodes through auto-encoding & Wang et al. (2016)\tabularnewline
+HARP & nodes through a meta-strategy & Chen et al. (2017)\tabularnewline
 \bottomrule
@@
 \url{https://doi.org/10.1016/j.biocon.2021.108983}
+
+\leavevmode\hypertarget{ref-Chen2017HarHie}{}%
+Chen, H., Perozzi, B., Hu, Y., \& Skiena, S. (2017, November 16).
+\emph{HARP: Hierarchical Representation Learning for Networks}.
+\url{http://arxiv.org/abs/1706.07845}
 
@@
 
+\leavevmode\hypertarget{ref-Ramasamy2015ComSpe}{}%
+Ramasamy, D., \& Madhow, U. (2015). Compressive spectral embedding:
+Sidestepping the SVD. In C. Cortes, N. Lawrence, D. Lee, M. Sugiyama, \&
+R. Garnett (Eds.), \emph{Advances in neural information processing
+systems} (Vol. 28). Curran Associates, Inc.
+\url{https://proceedings.neurips.cc/paper/2015/file/4f6ffe13a5d75b2d6a3923922b3922e5-Paper.pdf}
+
 \leavevmode\hypertarget{ref-Ray2021BioCri}{}%
@@
 \url{https://doi.org/10.1098/rstb.2021.0063}
+
+\leavevmode\hypertarget{ref-Tang2015LinLar}{}%
+Tang, J., Qu, M., Wang, M., Zhang, M., Yan, J., \& Mei, Q. (2015). LINE:
+Large-scale Information Network Embedding. \emph{Proceedings of the 24th
+International Conference on World Wide Web}, 1067--1077.
+\url{https://doi.org/10.1145/2736277.2741093}
 
@@
 
+\leavevmode\hypertarget{ref-Yan2005GraEmb}{}%
+Yan, S., Xu, D., Zhang, B., \& Zhang, H.-J. (2005). Graph embedding: A
+general framework for dimensionality reduction. \emph{2005 IEEE Computer
+Society Conference on Computer Vision and Pattern Recognition
+(CVPR'05)}, \emph{2}, 830--837 vol. 2.
+\url{https://doi.org/10.1109/CVPR.2005.170}
+
 \end{CSLReferences}

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@b54934cfcadbcbed63871af5a22f9b3a617069ac 🚀

@@
 \endhead
+RDPG & graphs through SVD & Young \& Scheinerman (2007)\tabularnewline
+tSNE & nodes through statistical divergence & Hinton \& Roweis
+(2002)\tabularnewline
 DeepWalk & graph walk & Perozzi et al. (2014)\tabularnewline
@@
 (2015)\tabularnewline
-SDNE & nodes through auto-encoding & Wang et al. (2016)\tabularnewline
+SDNE & nodes through auto-encoding & D. Wang et al.
+(2016)\tabularnewline
 node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
@@
 HARP & nodes through a meta-strategy & Chen et al. (2017)\tabularnewline
+Joint methods & multiple graphs & S. Wang et al. (2021)\tabularnewline
 \bottomrule
@@
 
+\leavevmode\hypertarget{ref-Hinton2002StoNei}{}%
+Hinton, G., \& Roweis, S. T. (2002). Stochastic neighbor embedding.
+\emph{NIPS}, \emph{15}, 833--840.
+
 \leavevmode\hypertarget{ref-Hoffmann2019MacLea}{}%
@@
 
+\leavevmode\hypertarget{ref-Wang2021JoiEmb}{}%
+Wang, S., Arroyo, J., Vogelstein, J. T., \& Priebe, C. E. (2021). Joint
+Embedding of Graphs. \emph{IEEE Transactions on Pattern Analysis and
+Machine Intelligence}, \emph{43}(4), 1324--1336.
+\url{https://doi.org/10.1109/TPAMI.2019.2948619}
+
 \leavevmode\hypertarget{ref-Wood2015EffSpa}{}%
@@
 
+\leavevmode\hypertarget{ref-Young2007RanDot}{}%
+Young, S. J., \& Scheinerman, E. R. (2007). Random Dot Product Graph
+Models for Social Networks. In A. Bonato \& F. R. K. Chung (Eds.),
+\emph{Algorithms and Models for the Web-Graph} (pp. 138--149). Springer.
+\url{https://doi.org/10.1007/978-3-540-77004-6_11}
+
 \end{CSLReferences}

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@88e2dcdd5543b53a5899feea2eec4da34f7b286b 🚀

@@
 
-\begin{longtable}[]{@{}lll@{}}
+\begin{longtable}[]{@{}llll@{}}
 \toprule
-Method & Embedding approach & Reference\tabularnewline
+Method & Embedding approach & Reference & Ecological
+application\tabularnewline
 \midrule
 \endhead
-RDPG & graphs through SVD & Young \& Scheinerman (2007)\tabularnewline
-tSNE & nodes through statistical divergence & Hinton \& Roweis
-(2002)\tabularnewline
-DeepWalk & graph walk & Perozzi et al. (2014)\tabularnewline
-FastEmbed & graph through PCA/SVD analogue & Ramasamy \& Madhow
-(2015)\tabularnewline
-LINE & nodes through statistical divergence & Tang et al.
-(2015)\tabularnewline
-SDNE & nodes through auto-encoding & D. Wang et al.
-(2016)\tabularnewline
-node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
-graph2vec & sub-graph embedding & Narayanan et al. (2017)\tabularnewline
-HARP & nodes through a meta-strategy & Chen et al. (2017)\tabularnewline
-Joint methods & multiple graphs & S. Wang et al. (2021)\tabularnewline
+RDPG & graphs through SVD & Young \& Scheinerman (2007) & Wardeh et al.
+(2021)\tabularnewline
+tSNE & nodes through statistical divergence & Hinton \& Roweis (2002)
+&\tabularnewline
+DeepWalk & graph walk & Perozzi et al. (2014) &\tabularnewline
+FastEmbed & graph through PCA/SVD analogue & Ramasamy \& Madhow (2015)
+&\tabularnewline
+LINE & nodes through statistical divergence & Tang et al. (2015)
+&\tabularnewline
+SDNE & nodes through auto-encoding & D. Wang et al. (2016)
+&\tabularnewline
+node2vec & node embedding & Grover \& Leskovec (2016) &\tabularnewline
+graph2vec & sub-graph embedding & Narayanan et al. (2017)
+&\tabularnewline
+HARP & nodes through a meta-strategy & Chen et al. (2017)
+&\tabularnewline
+Joint methods & multiple graphs & S. Wang et al. (2021) &\tabularnewline
 \bottomrule
@@
 
+\leavevmode\hypertarget{ref-Wardeh2021PreMam}{}%
+Wardeh, M., Baylis, M., \& Blagrove, M. S. C. (2021). Predicting
+mammalian hosts in which novel coronaviruses can be generated.
+\emph{Nature Communications}, \emph{12}(1, 1), 780.
+\url{https://doi.org/10.1038/s41467-021-21034-5}
+
 \leavevmode\hypertarget{ref-Wood2015EffSpa}{}%

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@3e666f58ad67a514231fb4cb5f195ef5d3a55b80 🚀

@@
 \toprule
-Method & Embedding approach & Reference & Ecological
-application\tabularnewline
+\begin{minipage}[b]{0.10\columnwidth}\raggedright
+Method\strut
+\end{minipage} & \begin{minipage}[b]{0.28\columnwidth}\raggedright
+Embedding approach\strut
+\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\raggedright
+Reference\strut
+\end{minipage} & \begin{minipage}[b]{0.35\columnwidth}\raggedright
+Species interactions application\strut
+\end{minipage}\tabularnewline
 \midrule
 \endhead
-RDPG & graphs through SVD & Young \& Scheinerman (2007) & Wardeh et al.
-(2021)\tabularnewline
-tSNE & nodes through statistical divergence & Hinton \& Roweis (2002)
-&\tabularnewline
-DeepWalk & graph walk & Perozzi et al. (2014) &\tabularnewline
-FastEmbed & graph through PCA/SVD analogue & Ramasamy \& Madhow (2015)
-&\tabularnewline
-LINE & nodes through statistical divergence & Tang et al. (2015)
-&\tabularnewline
-SDNE & nodes through auto-encoding & D. Wang et al. (2016)
-&\tabularnewline
-node2vec & node embedding & Grover \& Leskovec (2016) &\tabularnewline
-graph2vec & sub-graph embedding & Narayanan et al. (2017)
-&\tabularnewline
-HARP & nodes through a meta-strategy & Chen et al. (2017)
-&\tabularnewline
-Joint methods & multiple graphs & S. Wang et al. (2021) &\tabularnewline
+\begin{minipage}[t]{0.10\columnwidth}\raggedright
+RDPG\strut
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+graphs through SVD\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+Young \& Scheinerman (2007)\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+Poisot et al. (2021)\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.10\columnwidth}\raggedright
+tSNE\strut
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+nodes through statistical divergence\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+Hinton \& Roweis (2002)\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+Cieslak et al. (2020) -- statistical interactions\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.10\columnwidth}\raggedright
+DeepWalk\strut
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+graph walk\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+Perozzi et al. (2014)\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+Wardeh et al. (2021)\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.10\columnwidth}\raggedright
+FastEmbed\strut
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+graph through PCA/SVD analogue\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+Ramasamy \& Madhow (2015)\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.10\columnwidth}\raggedright
+LINE\strut
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+nodes through statistical divergence\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+Tang et al. (2015)\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.10\columnwidth}\raggedright
+SDNE\strut
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+nodes through auto-encoding\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+D. Wang et al. (2016)\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.10\columnwidth}\raggedright
+node2vec\strut
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+node embedding\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+Grover \& Leskovec (2016)\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.10\columnwidth}\raggedright
+graph2vec\strut
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+sub-graph embedding\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+Narayanan et al. (2017)\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.10\columnwidth}\raggedright
+DMSE\strut
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+joint node embedding\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+D. Chen et al. (2017)\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+D. Chen et al. (2017) -- joint SDMs\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.10\columnwidth}\raggedright
+HARP\strut
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+nodes through a meta-strategy\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+H. Chen et al. (2017)\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.10\columnwidth}\raggedright
+Joint methods\strut
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+multiple graphs\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+S. Wang et al. (2021)\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
 \bottomrule
@@
 
+\leavevmode\hypertarget{ref-Chen2017DeeMul}{}%
+Chen, D., Xue, Y., Fink, D., Chen, S., \& Gomes, C. P. (2017).
+\emph{Deep Multi-species Embedding}. 3639--3646.
+\url{https://www.ijcai.org/proceedings/2017/509}
+
 \leavevmode\hypertarget{ref-Chen2017HarHie}{}%
@@
 contradictions and prospects} (pp. 24--44). Bloomsbury Publishing.
+
+\leavevmode\hypertarget{ref-Cieslak2020TdiSto}{}%
+Cieslak, M. C., Castelfranco, A. M., Roncalli, V., Lenz, P. H., \&
+Hartline, D. K. (2020). T-Distributed Stochastic Neighbor Embedding
+(t-SNE): A tool for eco-physiological transcriptomic analysis.
+\emph{Marine Genomics}, \emph{51}, 100723.
+\url{https://doi.org/10.1016/j.margen.2019.100723}
 
@@
 
+\leavevmode\hypertarget{ref-Poisot2021ImpMam}{}%
+Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M. J., Becker, D.
+J., Albery, G. F., Gibb, R. J., Seifert, S. N., \& Carlson, C. J. (2021,
+May 31). \emph{Imputing the mammalian virome with linear filtering and
+singular value decomposition}. \url{http://arxiv.org/abs/2105.14973}
+
 \leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@b956cdfb8cb77c73f025396391c1980c59c62c0c 🚀

@@
 low-dimensional objects, and can be adequately represented with less
-than ten dimensions.
+than ten dimensions. Simulation results by Botella et al. (2022) suggest
+that there is no best method to identify architectural similarities
+between networks, and that multiple approaches need to be tested and
+compared to the network descriptor of interest.
 
-The popularity of graph embedding techniques in machine learning is
-rather intuitive: while graphs are discrete objects, machine learning
-techniques tend to handle continuous data better. Therefore, bringing a
-discrete graph into a continuous vector space opens up a broader variety
-of predictive algorithms.
+But the popularity of graph embedding techniques in machine learning is
+rather more intuitive than the search for structural invariants: while
+graphs are discrete objects, machine learning techniques tend to handle
+continuous data better. Therefore, bringing a discrete graph into a
+continuous vector space opens up a broader variety of predictive
+algorithms.
 
@@
 \url{https://doi.org/10.1038/s41559-019-0950-y}
+
+\leavevmode\hypertarget{ref-Botella2022AppGra}{}%
+Botella, C., Dray, S., Matias, C., Miele, V., \& Thuiller, W. (2022). An
+appraisal of graph embeddings for comparing trophic network
+architectures. \emph{Methods in Ecology and Evolution}, \emph{13}(1),
+203--216. \url{https://doi.org/10.1111/2041-210X.13738}
 

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@35ed676dc3d5028bcf31c7ccadbe6861b05f6533 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@55d137a3b4bd365029a55a2fe7c121a2a01e1dbf 🚀

@@
 
+\hypertarget{tbl:methods}{}
 \begin{longtable}[]{@{}llll@{}}
+\caption{\label{tbl:methods}Overview of some common graph embedding
+approaches, by time of publication, alongside examples of their use in
+the prediction of species interactions. Surprisingly, these methods have
+not yet been used routinely to predict species interactions; most of the
+examples we identified were either statistical associations, or
+analogues to joint species distribution models. \(^a\): statistical
+interactions; \(^b\): joint-SDM-like approach.}\tabularnewline
 \toprule
-\begin{minipage}[b]{0.10\columnwidth}\raggedright
+\begin{minipage}[b]{0.11\columnwidth}\raggedright
 Method\strut
+\end{minipage} & \begin{minipage}[b]{0.32\columnwidth}\raggedright
+Embedding approach\strut
+\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedright
+Reference\strut
 \end{minipage} & \begin{minipage}[b]{0.28\columnwidth}\raggedright
+Species interactions application\strut
+\end{minipage}\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{0.11\columnwidth}\raggedright
+Method\strut
+\end{minipage} & \begin{minipage}[b]{0.32\columnwidth}\raggedright
 Embedding approach\strut
-\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedright
 Reference\strut
-\end{minipage} & \begin{minipage}[b]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{0.28\columnwidth}\raggedright
 Species interactions application\strut
@@
 \endhead
-\begin{minipage}[t]{0.10\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 RDPG\strut
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+graphs through SVD\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+Young \& Scheinerman (2007)\strut
 \end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
-graphs through SVD\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
-Young \& Scheinerman (2007)\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 Poisot et al. (2021)\strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.10\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 tSNE\strut
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+nodes through statistical divergence\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+Hinton \& Roweis (2002)\strut
 \end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
-nodes through statistical divergence\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
-Hinton \& Roweis (2002)\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
-Cieslak et al. (2020) -- statistical interactions\strut
+Cieslak et al. (2020) \(^a\)\strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.10\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 DeepWalk\strut
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+graph walk\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+Perozzi et al. (2014)\strut
 \end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
-graph walk\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
-Perozzi et al. (2014)\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 Wardeh et al. (2021)\strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.10\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 FastEmbed\strut
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+graph through PCA/SVD analogue\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+Ramasamy \& Madhow (2015)\strut
 \end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
-graph through PCA/SVD analogue\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
-Ramasamy \& Madhow (2015)\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.10\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 LINE\strut
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+nodes through statistical divergence\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+Tang et al. (2015)\strut
 \end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
-nodes through statistical divergence\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
-Tang et al. (2015)\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.10\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 SDNE\strut
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+nodes through auto-encoding\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+D. Wang et al. (2016)\strut
 \end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
-nodes through auto-encoding\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
-D. Wang et al. (2016)\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.10\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 node2vec\strut
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+node embedding\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+Grover \& Leskovec (2016)\strut
 \end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
-node embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
-Grover \& Leskovec (2016)\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.10\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 graph2vec\strut
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+sub-graph embedding\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+Narayanan et al. (2017)\strut
 \end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
-sub-graph embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
-Narayanan et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.10\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 DMSE\strut
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+joint node embedding\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+D. Chen et al. (2017)\strut
 \end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
-joint node embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
-D. Chen et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
-D. Chen et al. (2017) -- joint SDMs\strut
+D. Chen et al. (2017) \(^b\)\strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.10\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 HARP\strut
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+nodes through a meta-strategy\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+H. Chen et al. (2017)\strut
 \end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
-nodes through a meta-strategy\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
-H. Chen et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.10\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
+GraphKKE\strut
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+graph embedding\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+Melnyk et al. (2020)\strut
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+Melnyk et al. (2020) \(^a\)\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 Joint methods\strut
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+multiple graphs\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+S. Wang et al. (2021)\strut
 \end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
-multiple graphs\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
-S. Wang et al. (2021)\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 \strut
@@
 
+\leavevmode\hypertarget{ref-Melnyk2020GraGra}{}%
+Melnyk, K., Klus, S., Montavon, G., \& Conrad, T. O. F. (2020).
+GraphKKE: Graph Kernel Koopman embedding for human microbiome analysis.
+\emph{Applied Network Science}, \emph{5}(1), 96.
+\url{https://doi.org/10.1007/s41109-020-00339-2}
+
 \leavevmode\hypertarget{ref-Mora2018IdeCom}{}%

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@87f717c2b1cd34f55b3125064f042bb5f54eacd4 🚀

@@
 for significant breakthroughs in our ability to start thinking about
-species interaction networks over large spatial scales. In a recent
-overview of the field of ecological network prediction, Strydom et al.
-(2021) identified two challenges of interest to the prediction of
-interactions at large scales. First, there is a relative scarcity of
-relevant data in most places globally -- paradoxically, this restricts
-our ability to infer interactions to locations where inference is
-perhaps the least required; second, accurate predictions often demand
-accurate predictors, and the lack of methods that can leverage small
-amount of data is a serious impediment to our predictive ability
-globally.
+species interaction networks over large spatial scales (Hortal et al.,
+2015). In a recent overview of the field of ecological network
+prediction, Strydom et al. (2021) identified two challenges of interest
+to the prediction of interactions at large scales. First, there is a
+relative scarcity of relevant data in most places globally --
+paradoxically, this restricts our ability to infer interactions to
+locations where inference is perhaps the least required; second,
+accurate predictions often demand accurate predictors, and the lack of
+methods that can leverage small amount of data is a serious impediment
+to our predictive ability globally.
 
@@
 
+\leavevmode\hypertarget{ref-Hortal2015SevSho}{}%
+Hortal, J., de Bello, F., Diniz-Filho, J. A. F., Lewinsohn, T. M., Lobo,
+J. M., \& Ladle, R. J. (2015). Seven Shortfalls that Beset Large-Scale
+Knowledge of Biodiversity. \emph{Annual Review of Ecology, Evolution,
+and Systematics}, \emph{46}(1), 523--549.
+\url{https://doi.org/10.1146/annurev-ecolsys-112414-054400}
+
 \leavevmode\hypertarget{ref-Jordano2016SamNet}{}%

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@d5be554ad64f81d3840b29c4bb9c457dba9390f3 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@3adfc073e4ab7f6b5e548dbbab00543f961bbcca 🚀

@@
 \hypertarget{tbl:methods}{}
-\begin{longtable}[]{@{}llll@{}}
+\begin{longtable}[]{@{}llrr@{}}
 \caption{\label{tbl:methods}Overview of some common graph embedding
@@
 Embedding approach\strut
-\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedleft
 Reference\strut
-\end{minipage} & \begin{minipage}[b]{0.28\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{0.28\columnwidth}\raggedleft
 Species interactions application\strut
@@
 graphs through SVD\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
 Young \& Scheinerman (2007)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
 Poisot et al. (2021)\strut
@@
 nodes through statistical divergence\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
 Hinton \& Roweis (2002)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
 Cieslak et al. (2020) \(^a\)\strut
@@
 graph walk\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
 Perozzi et al. (2014)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
 Wardeh et al. (2021)\strut
@@
 graph through PCA/SVD analogue\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
 Ramasamy \& Madhow (2015)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
 \strut
@@
 nodes through statistical divergence\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
 Tang et al. (2015)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
 \strut
@@
 nodes through auto-encoding\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
 D. Wang et al. (2016)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
 \strut
@@
 node embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
 Grover \& Leskovec (2016)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
 \strut
@@
 sub-graph embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
 Narayanan et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
 \strut
@@
 joint node embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
 D. Chen et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
 D. Chen et al. (2017) \(^b\)\strut
@@
 nodes through a meta-strategy\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
 H. Chen et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
 \strut
@@
 graph embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
 Melnyk et al. (2020)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
 Melnyk et al. (2020) \(^a\)\strut
@@
 multiple graphs\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
 S. Wang et al. (2021)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
 \strut
@@
 \end{longtable}
+
+\textbf{TK} Transfer + embedding graf
 
@@
 As Herbert (1965) rightfully pointed out, ``{[}y{]}ou can't draw neat
-lines around planet-wide problems''; in this regard, our approach (and
-indeed, any inference of a metaweb at large scales) must contend with
-several interesting and interwoven families of problems. The first is
-the limit of the metaweb to embed and transfer. If the initial metaweb
-is too narrow in scope, notably from a taxonomic point of view, the
-chances of finding another area with enough related species to make a
-reliable inference decreases; this would likely be indicated by large
-confidence intervals during ancestral character estimation, but the lack
-of well documented metawebs is currently preventing the development of
-more concrete guidelines. The question of phylogenetic relatedness and
-dispersal is notably true if the metaweb is assembled in an area with
-mostly endemic species, and as with every predictive algorithm, there is
-room for the application of our best ecological judgement. Conversely,
-the metaweb should be reliably filled, which assumes that the \(S^2\)
-interactions in a pool of \(S\) species have been examined, either
-through literature surveys or expert elicitation. Supp. Mat. 1 provides
-some guidance as to the type of sampling effort that should be
-prioritized. While RDPG was able to maintain very high predictive power
-when interactions were missing, the addition of false positive
-interactions was immediately detected; this suggests that it may be
-appropriate to err on the side of ``too many'' interactions when
-constructing the initial metaweb to be transferred. The second series of
-problems are related to determining which area should be used to infer
-the new metaweb in, as this determines the species pool that must be
-used.
+lines around planet-wide problems''; in this regard, any inference of a
+metaweb at large scales must contend with several interesting and
+interwoven families of problems.
 
-In our application, we focused on the mammals of Canada. The upside of
-this approach is that information at the country level is likely to be
-required by policy makers and stakeholders for their biodiversity
-assessment, as each country tends to set goals at the national level
-(Buxton et al., 2021) for which quantitative instruments are designed
-(Turak et al., 2017), with specific strategies often enacted at smaller
-scales (Ray et al., 2021). And yet, we do not really have a satisfying
-answer to the question of ``where does a food web stop?''; the current
-most satisfying solutions involve examining the spatial consistency of
-network area relationships (see \emph{e.g.} Galiana et al., 2018, 2019,
-2021; \textbf{Fortin2021NetEco?}), which is of course impossible in the
-absence of enough information about the network itself. This suggests
-that an \emph{a posteriori} refinement of the results may be required,
-based on a downscaling of the metaweb. The final family of problems
-relates less to the availability of data or quantitative tools, and more
-to the praxis of spatial ecology. Operating under the context of
-national divisions, in large parts of the world, reflects nothing more
-than the legacy of settler colonialism. Indeed, the use of ecological
-data is not an apolitical act (Nost \& Goldstein, 2021), as data
-infrastructures tend to be designed to answer questions within national
-boundaries, and their use both draws upon and reinforces territorial
-statecraft; as per Machen \& Nost (2021), this is particularly true when
-the output of ``algorithmic thinking'' (\emph{e.g.} relying on machine
-learning to generate knowledge) can be re-used for governance
-(\emph{e.g.} enacting conservation decisions at the national scale). We
-therefore recognize that methods such as we propose operate under the
-framework that contributed to the ongoing biodiversity crisis (Adam,
-2014), reinforced environmental injustice (Choudry, 2013; Domínguez \&
-Luoma, 2020), and on Turtle Island especially, should be replaced by
-Indigenous principles of land management (Eichhorn et al., 2019; No'kmaq
-et al., 2021). As we see AI/ML being increasingly mobilized to generate
-knowledge that is lacking for conservation decisions (\emph{e.g.} Lamba
-et al., 2019; Mosebo Fernandes et al., 2020), our discussion of these
-tools need to go beyond the technical, and into the governance
-consequences they can have.
+The first is the spatial and taxonomic limit of the metaweb to embed and
+transfer. If the initial metaweb is too narrow in scope, notably from a
+taxonomic point of view, the chances of finding another area with enough
+related species (through phylogenetic relatedness or similarity of
+functional traits) to make a reliable inference decreases; this would
+likely be indicated by large confidence intervals during estimation of
+the values in the low-rank space, but the lack of well documented
+metawebs is currently preventing the development of more concrete
+guidelines. The question of phylogenetic relatedness and dispersal is
+notably true if the metaweb is assembled in an area with mostly endemic
+species, and as with every predictive algorithm, there is room for the
+application of our best ecological judgement. Conversely, the metaweb
+should be reliably filled, which assumes that the \(S^2\) interactions
+in a pool of \(S\) species have been examined, either through literature
+surveys or expert elicitation.
+
+\textbf{TK} Supp. Mat. 1 provides some guidance as to the type of
+sampling effort that should be prioritized. While RDPG was able to
+maintain very high predictive power when interactions were missing, the
+addition of false positive interactions was immediately detected; this
+suggests that it may be appropriate to err on the side of ``too many''
+interactions when constructing the initial metaweb to be transferred.
+
+The second series of problems are related to determining which area
+should be used to infer the new metaweb in, as this determines the
+species pool that must be used.
+
+\textbf{TK} In our application, we focused on the mammals of Canada. The
+upside of this approach is that information at the country level is
+likely to be required by policy makers and stakeholders for their
+biodiversity assessment, as each country tends to set goals at the
+national level (Buxton et al., 2021) for which quantitative instruments
+are designed (Turak et al., 2017), with specific strategies often
+enacted at smaller scales (Ray et al., 2021). And yet, we do not really
+have a satisfying answer to the question of ``where does a food web
+stop?''; the current most satisfying solutions involve examining the
+spatial consistency of network area relationships (Fortin et al., 2021;
+see \emph{e.g.} Galiana et al., 2018, 2019, 2021), which is of course
+impossible in the absence of enough information about the network
+itself. This suggests that an \emph{a posteriori} refinement of the
+results may be required, based on a downscaling of the metaweb.
+
+The final family of problems relates less to the availability of data or
+quantitative tools, and more to the praxis of spatial ecology. Operating
+under the context of national divisions, in large parts of the world,
+reflects nothing more than the legacy of settler colonialism. Indeed,
+the use of ecological data is not an apolitical act (Nost \& Goldstein,
+2021), as data infrastructures tend to be designed to answer questions
+within national boundaries, and their use both draws upon and reinforces
+territorial statecraft; as per Machen \& Nost (2021), this is
+particularly true when the output of ``algorithmic thinking''
+(\emph{e.g.} relying on machine learning to generate knowledge) can be
+re-used for governance (\emph{e.g.} enacting conservation decisions at
+the national scale). We therefore recognize that methods such as we
+propose operate under the framework that contributed to the ongoing
+biodiversity crisis (Adam, 2014), reinforced environmental injustice
+(Choudry, 2013; Domínguez \& Luoma, 2020), and on Turtle Island
+especially, should be replaced by Indigenous principles of land
+management (Eichhorn et al., 2019; No'kmaq et al., 2021). As we see
+AI/ML being increasingly mobilized to generate knowledge that is lacking
+for conservation decisions (\emph{e.g.} Lamba et al., 2019; Mosebo
+Fernandes et al., 2020), our discussion of these tools need to go beyond
+the technical, and into the governance consequences they can have.
 
@@
 \emph{16}(5), 577--583. \url{https://doi.org/10.1111/ele.12081}
+
+\leavevmode\hypertarget{ref-Fortin2021NetEco}{}%
+Fortin, M.-J., Dale, M. R. T., \& Brimacombe, C. (2021). Network ecology
+in dynamic landscapes. \emph{Proceedings of the Royal Society B:
+Biological Sciences}, \emph{288}(1949), rspb.2020.1889, 20201889.
+\url{https://doi.org/10.1098/rspb.2020.1889}
 

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@43d0f0111ac6b747baa7fd465a604a6ff369e8a3 🚀

@@
 
-\hypertarget{the-metaweb-embeds-hypotheses-about-which-spatial-boundaries-are-meaningful}{%
-\section{The metaweb embeds hypotheses about which spatial boundaries
-are
-meaningful}\label{the-metaweb-embeds-hypotheses-about-which-spatial-boundaries-are-meaningful}}
+\hypertarget{the-metaweb-embeds-strong-ecological-hypotheses}{%
+\section{The metaweb embeds strong ecological
+hypotheses}\label{the-metaweb-embeds-strong-ecological-hypotheses}}
 

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@57a65aa6914e2f823b146cdbf46ea7d5075553ee 🚀

@@
 2015). In a recent overview of the field of ecological network
-prediction, Strydom et al. (2021) identified two challenges of interest
-to the prediction of interactions at large scales. First, there is a
-relative scarcity of relevant data in most places globally --
+prediction, Strydom, Catchen, et al. (2021) identified two challenges of
+interest to the prediction of interactions at large scales. First, there
+is a relative scarcity of relevant data in most places globally --
 paradoxically, this restricts our ability to infer interactions to
@@
 models, which increases the volume of information available for
-inference. Indeed, Strydom et al. (2021) suggested that knowing the
-metaweb may render the prediction of local networks easier, because it
-fixes an ``upper bound'' on which interactions can exist; indeed, with a
-probabilistic metaweb, we can consider that the metaweb represents an
-aggregation of informative priors on the interactions.
+inference. Indeed, Strydom, Catchen, et al. (2021) suggested that
+knowing the metaweb may render the prediction of local networks easier,
+because it fixes an ``upper bound'' on which interactions can exist;
+indeed, with a probabilistic metaweb, we can consider that the metaweb
+represents an aggregation of informative priors on the interactions.
+
+\begin{figure}
+\hypertarget{fig:embedding}{%
+\centering
+\includegraphics{figures/conceptual_embedding.jpg}
+\caption{Overview of the embedding process. A network (\emph{A}),
+possibbly represented as its adjacency matrix (\emph{B}), is converted
+into a lower-dimensional object (\emph{C}) where nodes, subgraphs, or
+edges have specific values (see tbl.~\ref{tbl:methods}). For the
+purposes of prediction, this low-dimensional object encodes feature
+vectors for \emph{e.g.} the nodes. Embedding also allows to visualize
+the structure in the data differently (\emph{D}), much like with a
+principal component analysis.}\label{fig:embedding}
+}
+\end{figure}
 
@@
 
-Graph embedding is a varied family of machine learning techniques aiming
-to transform nodes and edges into a vector space, usually of a lower
-dimension, whilst maximally retaining key properties of the graph (Yan
-et al., 2005). Ecological networks are an interesting candidate for the
-widespread application of embeddings, as they tend to posess a shared
-sstructural backbone (Mora et al., 2018), which hints at structural
-invariants that can be revealed a lower dimensions. Indeed, previous
-work by Eklöf et al. (2013) suggests that food webs are inherently
-low-dimensional objects, and can be adequately represented with less
-than ten dimensions. Simulation results by Botella et al. (2022) suggest
-that there is no best method to identify architectural similarities
-between networks, and that multiple approaches need to be tested and
-compared to the network descriptor of interest.
-
-But the popularity of graph embedding techniques in machine learning is
-rather more intuitive than the search for structural invariants: while
-graphs are discrete objects, machine learning techniques tend to handle
-continuous data better. Therefore, bringing a discrete graph into a
-continuous vector space opens up a broader variety of predictive
-algorithms.
+Graph embedding fig.~\ref{fig:embedding} is a varied family of machine
+learning techniques aiming to transform nodes and edges into a vector
+space (Arsov \& Mirceva, 2019), usually of a lower dimension, whilst
+maximally retaining key properties of the graph (Yan et al., 2005).
+Ecological networks are an interesting candidate for the widespread
+application of embeddings, as they tend to posess a shared sstructural
+backbone (Mora et al., 2018), which hints at structural invariants that
+can be revealed a lower dimensions. Indeed, previous work by Eklöf et
+al. (2013) suggests that food webs are inherently low-dimensional
+objects, and can be adequately represented with less than ten
+dimensions. Simulation results by Botella et al. (2022) suggest that
+there is no best method to identify architectural similarities between
+networks, and that multiple approaches need to be tested and compared to
+the network descriptor of interest. This matches with previous, more
+general results on graph embedding, which suggest that embedding
+algorithm choice matters for the results (Goyal \& Ferrara, 2018).
 
@@
 
+But the popularity of graph embedding techniques in machine learning is
+rather more intuitive than the search for structural invariants: while
+graphs are discrete objects, machine learning techniques tend to handle
+continuous data better. Therefore, bringing a sparse graph into a
+continuous, dense vector space (Xu, 2020) opens up a broader variety of
+predictive algorithms.
+
 \textbf{TK} Transfer + embedding graf
+
+\begin{figure}
+\hypertarget{fig:prediction}{%
+\centering
+\includegraphics{figures/conceptual_predictions.jpg}
+\caption{From a low-dimensional figure vector (see
+fig.~\ref{fig:embedding}), it is possible to develop predictive
+approaches. Nodes in an ecological network are species, for which we can
+leverage phylogenetic relatedness (\emph{e.g.} Strydom, Bouskila, et
+al., 2021) or functional traits to fill the values of additional species
+we would like to project in this space (here, I, J, K, and L) from the
+embedding of known species (here, A, B, C, and D). Because embeddings
+can be projected back to a graph, this allows to reconstruct a network
+with these new species. This approach constitutes an instance of
+transfer learning.}\label{fig:prediction}
+}
+\end{figure}
 
@@
 
+\leavevmode\hypertarget{ref-Arsov2019NetEmb}{}%
+Arsov, N., \& Mirceva, G. (2019, November 26). \emph{Network Embedding:
+An Overview}. \url{http://arxiv.org/abs/1911.11726}
+
 \leavevmode\hypertarget{ref-Botella2022AppGra}{}%
@@
 \emph{2}(5), 782--790. \url{https://doi.org/10.1038/s41559-018-0517-3}
+
+\leavevmode\hypertarget{ref-Goyal2018GraEmb}{}%
+Goyal, P., \& Ferrara, E. (2018). Graph embedding techniques,
+applications, and performance: A survey. \emph{Knowledge-Based Systems},
+\emph{151}, 78--94. \url{https://doi.org/10.1016/j.knosys.2018.03.022}
 
@@
 
+\leavevmode\hypertarget{ref-Strydom2021FooWeb}{}%
+Strydom, T., Bouskila, S., Banville, F., Barros, C., Caron, D., Farrell,
+M. J., Fortin, M.-J., Hemming, V., Mercier, B., Pollock, L., Runghen,
+R., Riva, G. V. D., \& Poisot, T. (2021). \emph{Food web reconstruction
+through phylogenetic transfer of low-rank network representation}.
+\url{https://doi.org/10.32942/osf.io/y7sdz}
+
 \leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
@@
 
+\leavevmode\hypertarget{ref-Xu2020UndGra}{}%
+Xu, M. (2020, December 14). \emph{Understanding graph embedding methods
+and their applications}. \url{http://arxiv.org/abs/2012.08019}
+
 \leavevmode\hypertarget{ref-Yan2005GraEmb}{}%

### 2022-01-12 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@57a65aa6914e2f823b146cdbf46ea7d5075553ee 🚀

@@
 
+\leavevmode\hypertarget{ref-Goyal2018GraEmb}{}%
+Goyal, P., \& Ferrara, E. (2018). Graph embedding techniques,
+applications, and performance: A survey. \emph{Knowledge-Based Systems},
+\emph{151}, 78--94. \url{https://doi.org/10.1016/j.knosys.2018.03.022}
+
 \leavevmode\hypertarget{ref-Gravel2018BriElt}{}%
@@
 \url{https://doi.org/10.1139/facets-2020-0075}
+
+\leavevmode\hypertarget{ref-Strydom2021FooWeb}{}%
+Strydom, T., Bouskila, S., Banville, F., Barros, C., Caron, D., Farrell,
+M. J., Fortin, M.-J., Hemming, V., Mercier, B., Pollock, L., Runghen,
+R., Riva, G. V. D., \& Poisot, T. (2021). \emph{Food web reconstruction
+through phylogenetic transfer of low-rank network representation}.
+\url{https://doi.org/10.32942/osf.io/y7sdz}
 

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@f29fae06131c59d66d14617bddb35706086827df 🚀

@@
 
+Rather than directly predicting biological rules (see \emph{e.g.}
+Pichler et al., 2020 for an overview), which may be confounded by the
+sparse nature of graph data, learning embeddings works in the
+low-dimensional space that maximizes information about the network
+structure.
+
 \begin{figure}
@@
 
+\leavevmode\hypertarget{ref-Pichler2020MacLea}{}%
+Pichler, M., Boreux, V., Klein, A.-M., Schleuning, M., \& Hartig, F.
+(2020). Machine learning algorithms to infer trait-matching and predict
+species interactions in ecological networks. \emph{Methods in Ecology
+and Evolution}, \emph{11}(2), 281--293.
+\url{https://doi.org/10.1111/2041-210X.13329}
+
 \leavevmode\hypertarget{ref-Poisot2016StrPro}{}%

### 2022-01-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@c657de18ad684416b0b89818c774a1182ba26cb3 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@fc4007332ca73f80d568a723c3e6ea57be742c28 🚀

@@
 \thispagestyle{empty}
-{\Large\bfseries\sffamily Predicting metawebs: graph embeddings can help
-alleviate spatial data deficiencies}
+{\Large\bfseries\sffamily Predicting metawebs: transfer of graph
+embeddings can help alleviate spatial data deficiencies}
 \vskip 5em
@@
 \centering
-\includegraphics{figures/conceptual_predictions.jpg}
-\caption{From a low-dimensional figure vector (see
+\includegraphics{figures/conceptual_prediction.jpg}
+\caption{From a low-dimensional feature vector (see
 fig.~\ref{fig:embedding}), it is possible to develop predictive

### 2022-01-13 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@c657de18ad684416b0b89818c774a1182ba26cb3 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@fc4007332ca73f80d568a723c3e6ea57be742c28 🚀

@@
 
-\noindent {\LARGE \textbf{\textsf{Predicting metawebs: graph embeddings
-can help alleviate spatial data deficiencies}}}
+\noindent {\LARGE \textbf{\textsf{Predicting metawebs: transfer of graph
+embeddings can help alleviate spatial data deficiencies}}}
 

### 2022-01-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@0688247d1354ca4f0fd4214e851dd5f46c103a9e 🚀

@@
 
-Having a general solution for inferring \emph{potential} interactions
-(despite the unavailability of interaction data) could be the catalyst
+Being able to infer \emph{potential} interactions could be the catalyst
 for significant breakthroughs in our ability to start thinking about
@@
 methods that can leverage small amount of data is a serious impediment
-to our predictive ability globally.
+to our global predictive ability. In most places, our most reliable
+biodiversity knowledge is that of a species pool: through the analysis
+of databases like GBIF or IUCN, it is possible to establish a list of
+species in a region of interest; but establishing the interactions
+between these species is difficult.
 
-Following the definition of Dunne (2006), a metaweb is a network
-analogue to the regional species pool; specifically, it is an inventory
-of all \emph{potential} interactions between species from a spatially
-delimited area (and so captures the \(\gamma\) diversity of
-interactions). The metaweb is, therefore, \emph{not} a prediction of the
-food web at a specific locale within the spatial area it covers, and
-will have a different structure (notably by having a larger connectance;
-see \emph{e.g.} Wood et al., 2015). These local food webs (which
-captures the \(\alpha\) diversity of interactions) are a subset of the
-metaweb's species and interactions, and have been called ``metaweb
-realizations'' (Poisot et al., 2015). Differences between local food web
-and their metaweb are due to chance, species abundance and
-co-occurrence, local environmental conditions, and local distribution of
-functional traits, among others.
+Following the definition of Dunne (2006), a metaweb is the ecological
+network analogue to the species pool; specifically, it iventories
+\emph{potential} interactions between species from a spatially delimited
+area (and so captures the \(\gamma\) diversity of interactions). The
+metaweb is not a prediction of the network at a specific point within
+the spatial area it covers: it will have a different structure, notably
+by having a larger connectance (see \emph{e.g.} Wood et al., 2015), from
+any of these local networks. These local networks (capturing the
+\(\alpha\) diversity of interactions) are a subset of the metaweb's
+species and interactions, and have been called ``metaweb realizations''
+(Poisot et al., 2015). Differences between local networks and their
+metawebs are due to chance, species abundance and co-occurrence, local
+environmental conditions, and local distribution of functional traits,
+among others.
 
@@
 ``upper bounds'' on what the composition of the local networks can be
-(see \emph{e.g.} McLeod et al., 2021). These local networks, in turn,
-can be reconstructed given appropriate knowledge of local species
-composition, providing information on structure of food webs at finer
-spatial scales. This has been done for example for
-tree-galler-parasitoid systems (Gravel et al., 2018), fish trophic
-interactions (Albouy et al., 2019), tetrapod trophic interactions
-(O'Connor et al., 2020), and crop-pest networks (Grünig et al., 2020).
-Whereas the original metaweb definition, and indeed most past uses of
-metawebs, was based on the presence/absence of interactions, we focus on
-\emph{probabilistic} metawebs where interactions are represented as the
-chance of success of a Bernoulli trial (see \emph{e.g.} Poisot et al.,
-2016); therefore, not only does our method recommend interactions that
-may exist, it gives each interaction a score, allowing us to properly
-weigh them.
+(see \emph{e.g.} McLeod et al., 2021). These local networks may be
+reconstructed given appropriate knowledge of local species composition,
+providing information on structure of food webs at finer spatial scales.
+This has been done for example for tree-galler-parasitoid systems
+(Gravel et al., 2018), fish trophic interactions (Albouy et al., 2019),
+tetrapod trophic interactions (O'Connor et al., 2020), and crop-pest
+networks (Grünig et al., 2020). In this contribution, we highlight the
+\emph{probabilistic} nature of metawebs, discuss how a family of machine
+learning tools (graph embeddings and transfer learning) can be used to
+overcome data limitations to metaweb inference, and highlight how the
+use of metawebs introduces important questions for the field of network
+ecology.
 
@@
 
-Yet, owing to the inherent plasticity of interactions, there have been
+Dallas et al. (2017) suggested that most links in ecological networks
+are cryptic, \emph{i.e.} uncommon or hard to observe. This argument
+echoes Jordano (2016): sampling ecological interactions is difficult
+because it requires first the joint observation of two species, and then
+the observation of their interaction. In addition, it is generally
+expected that weak or rare links would be more common in networks
+(Csermely, 2004), compared to strong, persistent links; this is notably
+the case in food chains, wherein many weaker links are key to the
+stability of a system (Neutel et al., 2002). In the light of these
+observations, we expect to see an over-representation of low-probability
+interactions under a model that accurately predicts interaction
+probabilities. Yet the original metaweb definition, and indeed most past
+uses of metawebs, was based on the presence/absence of interactions.
+Moving towards \emph{probabilistic} metawebs, by represent interactions
+as Bernoulli events (see \emph{e.g.} Poisot et al., 2016), offers the
+opportunity to weigh these rare interactions appropriately. The inherent
+plasticity of interactions is important to capture: there have been
 documented instances of food webs undergoing rapid collapse/recovery
-cycles over short periods of time (Pedersen et al., 2017). The embedding
-of a network, in a sense, embeds its macro-evolutionary history,
-especially as RDPG captures ecological signal (Dalla Riva \& Stouffer,
-2016); at this point, it is important to recall that a metaweb is
-intended as a catalogue of all potential interactions, which should then
-be filtered (Morales-Castilla et al., 2015). In practice (and in this
-instance) the reconstructed metaweb will predict interactions that are
-plausible based on the species' evolutionary history, however some
-interactions would/would not be realized due to human impact.
+cycles over short periods of time (\emph{e.g.} Pedersen et al., 2017).
+These considerations emphasize why metaweb predictions should focus on
+quantitative (preferentially probabilistic) predictions; this should
+constrain the suite of appropriate models.
 
-Dallas et al. (2017) suggested that most links in ecological networks
-may be cryptic, \emph{i.e.} uncommon or otherwise hard to observe. This
-argument essentially echoes Jordano (2016): the sampling of ecological
-interactions is difficult because it requires first the joint
-observation of two species, and then the observation of their
-interaction. In addition, it is generally expected that weak or rare
-links would be more common in networks (Csermely, 2004), compared to
-strong, persistent links; this is notably the case in food chains,
-wherein many weaker links are key to the stability of a system (Neutel
-et al., 2002). In the light of these observations, the results in
-fig.~\ref{fig:inflation} are not particularly surprising: we expect to
-see a surge in these low-probability interactions under a model that has
-a good predictive accuracy. Because the predictions we generate are by
-design probabilistic, then one can weigh these rare links appropriately.
-In a sense, that most ecological interactions are elusive can call for a
-slightly different approach to sampling: once the common interactions
-are documented, the effort required in documenting each rare interaction
-may increase exponentially. Recent proposals suggest that machine
-learning algorithms, in these situations, can act as data generators
-(Hoffmann et al., 2019): in this perspective, high quality observational
-data can be supplemented with synthetic data coming from predictive
-models, which increases the volume of information available for
-inference. Indeed, Strydom, Catchen, et al. (2021) suggested that
-knowing the metaweb may render the prediction of local networks easier,
-because it fixes an ``upper bound'' on which interactions can exist;
-indeed, with a probabilistic metaweb, we can consider that the metaweb
-represents an aggregation of informative priors on the interactions.
+Yet it is important to recall that a metaweb is intended as a catalogue
+of all potential interactions, which is then filtered (Morales-Castilla
+et al., 2015). In a sense, that most ecological interactions are elusive
+can call for a slightly different approach to sampling: once the common
+interactions are documented, the effort required in documenting each
+rare interaction will increase exponentially, and will do so for each
+undocumented interaction. Recent proposals suggest that machine learning
+algorithms, in these situations, can act as data generators (Hoffmann et
+al., 2019): high quality observational data can generate the core rules
+underpinning the network structure, and be supplemented with synthetic
+data coming from predictive models, increasing the volume of information
+available for inference. Indeed, Strydom, Catchen, et al. (2021)
+suggested that knowing the metaweb may render the prediction of local
+networks easier, because it fixes an ``upper bound'' on which
+interactions can exist. A probabilistic metaweb represents an
+aggregation of informative priors on the interactions, an elusive
+information with the potential to boost our predictive ability
+(\textbf{Bartomeus2016ComFra?}).
 
@@
 structure.
+
+The embedding of a network, in a sense, embeds its macro-evolutionary
+history, especially as RDPG captures ecological signal (Dalla Riva \&
+Stouffer, 2016); at this point,
 

### 2022-01-13 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@0688247d1354ca4f0fd4214e851dd5f46c103a9e 🚀

@@
 methods that can leverage small amount of data is a serious impediment
-to our predictive ability globally.
-
-Following the definition of Dunne (2006), a metaweb is a network
-analogue to the regional species pool; specifically, it is an inventory
-of all \emph{potential} interactions between species from a spatially
-delimited area (and so captures the \(\gamma\) diversity of
-interactions). The metaweb is, therefore, \emph{not} a prediction of the
-food web at a specific locale within the spatial area it covers, and
-will have a different structure (notably by having a larger connectance;
-see \emph{e.g.} Wood et al., 2015). These local food webs (which
-captures the \(\alpha\) diversity of interactions) are a subset of the
-metaweb's species and interactions, and have been called ``metaweb
-realizations'' (Poisot et al., 2015). Differences between local food web
-and their metaweb are due to chance, species abundance and
-co-occurrence, local environmental conditions, and local distribution of
-functional traits, among others.
+to our global predictive ability. In most places, our most reliable
+biodiversity knowledge is that of a species pool: through the analysis
+of databases like GBIF or IUCN, it is possible to establish a list of
+species in a region of interest; but establishing the interactions
+between these species is difficult.
+
+Following the definition of Dunne (2006), a metaweb is the ecological
+network analogue to the species pool; specifically, it iventories
+\emph{potential} interactions between species from a spatially delimited
+area (and so captures the \(\gamma\) diversity of interactions). The
+metaweb is not a prediction of the network at a specific point within
+the spatial area it covers: it will have a different structure, notably
+by having a larger connectance (see \emph{e.g.} Wood et al., 2015), from
+any of these local networks. These local networks (capturing the
+\(\alpha\) diversity of interactions) are a subset of the metaweb's
+species and interactions, and have been called ``metaweb realizations''
+(Poisot et al., 2015). Differences between local networks and their
+metawebs are due to chance, species abundance and co-occurrence, local
+environmental conditions, and local distribution of functional traits,
+among others.
 
@@
 
-Yet, owing to the inherent plasticity of interactions, there have been
+Dallas et al. (2017) suggested that most links in ecological networks
+are cryptic, \emph{i.e.} uncommon or hard to observe. This argument
+echoes Jordano (2016): sampling ecological interactions is difficult
+because it requires first the joint observation of two species, and then
+the observation of their interaction. In addition, it is generally
+expected that weak or rare links would be more common in networks
+(Csermely, 2004), compared to strong, persistent links; this is notably
+the case in food chains, wherein many weaker links are key to the
+stability of a system (Neutel et al., 2002). In the light of these
+observations, we expect to see an over-representation of low-probability
+interactions under a model that accurately predicts interaction
+probabilities. Yet the original metaweb definition, and indeed most past
+uses of metawebs, was based on the presence/absence of interactions.
+Moving towards \emph{probabilistic} metawebs, by represent interactions
+as Bernoulli events (see \emph{e.g.} Poisot et al., 2016), offers the
+opportunity to weigh these rare interactions appropriately. The inherent
+plasticity of interactions is important to capture: there have been
 documented instances of food webs undergoing rapid collapse/recovery
-cycles over short periods of time (Pedersen et al., 2017). The embedding
-of a network, in a sense, embeds its macro-evolutionary history,
-especially as RDPG captures ecological signal (Dalla Riva \& Stouffer,
-2016); at this point, it is important to recall that a metaweb is
-intended as a catalogue of all potential interactions, which should then
-be filtered (Morales-Castilla et al., 2015). In practice (and in this
-instance) the reconstructed metaweb will predict interactions that are
-plausible based on the species' evolutionary history, however some
-interactions would/would not be realized due to human impact.
-
-Dallas et al. (2017) suggested that most links in ecological networks
-may be cryptic, \emph{i.e.} uncommon or otherwise hard to observe. This
-argument essentially echoes Jordano (2016): the sampling of ecological
-interactions is difficult because it requires first the joint
-observation of two species, and then the observation of their
-interaction. In addition, it is generally expected that weak or rare
-links would be more common in networks (Csermely, 2004), compared to
-strong, persistent links; this is notably the case in food chains,
-wherein many weaker links are key to the stability of a system (Neutel
-et al., 2002). In the light of these observations, the results in
-fig.~\ref{fig:inflation} are not particularly surprising: we expect to
-see a surge in these low-probability interactions under a model that has
-a good predictive accuracy. Because the predictions we generate are by
-design probabilistic, then one can weigh these rare links appropriately.
-In a sense, that most ecological interactions are elusive can call for a
-slightly different approach to sampling: once the common interactions
-are documented, the effort required in documenting each rare interaction
-may increase exponentially. Recent proposals suggest that machine
-learning algorithms, in these situations, can act as data generators
-(Hoffmann et al., 2019): in this perspective, high quality observational
-data can be supplemented with synthetic data coming from predictive
-models, which increases the volume of information available for
-inference. Indeed, Strydom, Catchen, et al. (2021) suggested that
-knowing the metaweb may render the prediction of local networks easier,
-because it fixes an ``upper bound'' on which interactions can exist;
-indeed, with a probabilistic metaweb, we can consider that the metaweb
-represents an aggregation of informative priors on the interactions.
+cycles over short periods of time (\emph{e.g.} Pedersen et al., 2017).
+These considerations emphasize why metaweb predictions should focus on
+quantitative (preferentially probabilistic) predictions; this should
+constrain the suite of appropriate models.
+
+Yet it is important to recall that a metaweb is intended as a catalogue
+of all potential interactions, which is then filtered (Morales-Castilla
+et al., 2015). In a sense, that most ecological interactions are elusive
+can call for a slightly different approach to sampling: once the common
+interactions are documented, the effort required in documenting each
+rare interaction will increase exponentially, and will do so for each
+undocumented interaction. Recent proposals suggest that machine learning
+algorithms, in these situations, can act as data generators (Hoffmann et
+al., 2019): high quality observational data can generate the core rules
+underpinning the network structure, and be supplemented with synthetic
+data coming from predictive models, increasing the volume of information
+available for inference. Indeed, Strydom, Catchen, et al. (2021)
+suggested that knowing the metaweb may render the prediction of local
+networks easier, because it fixes an ``upper bound'' on which
+interactions can exist. A probabilistic metaweb represents an
+aggregation of informative priors on the interactions, an elusive
+information with the potential to boost our predictive ability
+(\textbf{Bartomeus2016ComFra?}).
 

### 2022-01-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@4bfaaf1811e3805832d8dc15ed1acbedf6ef893b 🚀

@@
 general results on graph embedding, which suggest that embedding
-algorithm choice matters for the results (Goyal \& Ferrara, 2018).
+algorithm choice matters for the results (Goyal \& Ferrara, 2018). In
+tbl.~\ref{tbl:methods}, we present a selection of common graph
+embeddings methods, alongside examples of their use to predict species
+interactions (when they have been used this way).
 
@@
 \toprule
-\begin{minipage}[b]{0.11\columnwidth}\raggedright
+\begin{minipage}[b]{0.13\columnwidth}\raggedright
 Method\strut
-\end{minipage} & \begin{minipage}[b]{0.32\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{0.35\columnwidth}\raggedright
 Embedding approach\strut
-\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[b]{0.19\columnwidth}\raggedleft
 Reference\strut
-\end{minipage} & \begin{minipage}[b]{0.28\columnwidth}\raggedleft
-Species interactions application\strut
+\end{minipage} & \begin{minipage}[b]{0.22\columnwidth}\raggedleft
+Application\strut
 \end{minipage}\tabularnewline
@@
 \endhead
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
+\begin{minipage}[t]{0.13\columnwidth}\raggedright
+tSNE\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+nodes through statistical divergence\strut
+\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+Hinton \& Roweis (2002)\strut
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+Cieslak et al. (2020) \(^a\)\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.13\columnwidth}\raggedright
 RDPG\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
-graphs through SVD\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+graph through SVD\strut
+\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
 Young \& Scheinerman (2007)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
 Poisot et al. (2021)\strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-tSNE\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+\begin{minipage}[t]{0.13\columnwidth}\raggedright
+DeepWalk\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+graph walk\strut
+\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+Perozzi et al. (2014)\strut
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+Wardeh et al. (2021)\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.13\columnwidth}\raggedright
+FastEmbed\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+graph through PCA/SVD analogue\strut
+\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+Ramasamy \& Madhow (2015)\strut
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.13\columnwidth}\raggedright
+LINE\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 nodes through statistical divergence\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
-Hinton \& Roweis (2002)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
-Cieslak et al. (2020) \(^a\)\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-DeepWalk\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
-graph walk\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
-Perozzi et al. (2014)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
-Wardeh et al. (2021)\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-FastEmbed\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
-graph through PCA/SVD analogue\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
-Ramasamy \& Madhow (2015)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+Tang et al. (2015)\strut
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-LINE\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
-nodes through statistical divergence\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
-Tang et al. (2015)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
+\begin{minipage}[t]{0.13\columnwidth}\raggedright
+SDNE\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+nodes through auto-encoding\strut
+\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+D. Wang et al. (2016)\strut
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-SDNE\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
-nodes through auto-encoding\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
-D. Wang et al. (2016)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
+\begin{minipage}[t]{0.13\columnwidth}\raggedright
+node2vec\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+nodes embedding\strut
+\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+Grover \& Leskovec (2016)\strut
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-node2vec\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
-node embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
-Grover \& Leskovec (2016)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
+\begin{minipage}[t]{0.13\columnwidth}\raggedright
+graph2vec\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+sub-graph embedding\strut
+\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+Narayanan et al. (2017)\strut
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-graph2vec\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
-sub-graph embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
-Narayanan et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
+\begin{minipage}[t]{0.13\columnwidth}\raggedright
+DMSE\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+joint nodes embedding\strut
+\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+D. Chen et al. (2017)\strut
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+D. Chen et al. (2017) \(^b\)\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.13\columnwidth}\raggedright
+HARP\strut
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+nodes through a meta-strategy\strut
+\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+H. Chen et al. (2017)\strut
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-DMSE\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
-joint node embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
-D. Chen et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
-D. Chen et al. (2017) \(^b\)\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-HARP\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
-nodes through a meta-strategy\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
-H. Chen et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
+\begin{minipage}[t]{0.13\columnwidth}\raggedright
 GraphKKE\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 graph embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
 Melnyk et al. (2020)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
 Melnyk et al. (2020) \(^a\)\strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
+\begin{minipage}[t]{0.13\columnwidth}\raggedright
 Joint methods\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 multiple graphs\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
 S. Wang et al. (2021)\strut
-\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
 \strut
@@
 
-But the popularity of graph embedding techniques in machine learning is
-rather more intuitive than the search for structural invariants: while
-graphs are discrete objects, machine learning techniques tend to handle
-continuous data better. Therefore, bringing a sparse graph into a
-continuous, dense vector space (Xu, 2020) opens up a broader variety of
-predictive algorithms.
-
-\textbf{TK} Transfer + embedding graf
-
-Rather than directly predicting biological rules (see \emph{e.g.}
-Pichler et al., 2020 for an overview), which may be confounded by the
-sparse nature of graph data, learning embeddings works in the
-low-dimensional space that maximizes information about the network
-structure.
-
-The embedding of a network, in a sense, embeds its macro-evolutionary
-history, especially as RDPG captures ecological signal (Dalla Riva \&
-Stouffer, 2016); at this point,
+The popularity of graph embedding techniques in machine learning is more
+prosaic than the search for structural invariants: graphs are discrete
+objects, and machine learning techniques tend to handle continuous data
+better. Bringing a sparse graph into a continuous, dense vector space
+(Xu, 2020) opens up a broader variety of predictive algorithms, notably
+of the sort that are able to predict events as probabilities (Murphy,
+2022). Furthermore, the projection of the graph itself is a
+representation that can be learned; Runghen et al. (2021), for example,
+used a neural network to learn the embedding of a network in which not
+all interactions were known, based on nodes metadata. This example has
+many parallels in ecology see \ref{fig:prediction}, in which node
+metadata can be given by phylogeny or functional traits. Rather than
+directly predicting biological rules (see \emph{e.g.} Pichler et al.,
+2020 for an overview), which may be confounded by the sparse nature of
+graph data, learning embeddings works in the low-dimensional space that
+maximizes information about the network structure. This approach is
+further justified by the observation, for example, that the
+macro-evolutionary history of a network is adequately represented by
+some graph embeddings (RDPG; see Dalla Riva \& Stouffer, 2016).
 
@@
 
+\leavevmode\hypertarget{ref-Murphy2022ProMac}{}%
+Murphy, K. P. (2022). \emph{Probabilistic machine learning: An
+introduction}. MIT Press. \href{https://probml.ai}{probml.ai}
+
 \leavevmode\hypertarget{ref-Narayanan2017GraLea}{}%
@@
 \url{https://doi.org/10.1139/facets-2020-0075}
+
+\leavevmode\hypertarget{ref-Runghen2021ExpNod}{}%
+Runghen, R., Stouffer, D. B., \& Dalla Riva, G. V. (2021).
+\emph{Exploiting node metadata to predict interactions in large networks
+using graph embedding and neural networks}.
+\url{https://doi.org/10.1101/2021.06.10.447991}
 

### 2022-01-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@a5e9b5b3ede822d2a31bca4179f8d471ca9b4a58 🚀

@@
 information with the potential to boost our predictive ability
-(\textbf{Bartomeus2016ComFra?}).
+(Bartomeus et al., 2016).
 
@@
 
+\leavevmode\hypertarget{ref-Bartomeus2016ComFra}{}%
+Bartomeus, I., Gravel, D., Tylianakis, J. M., Aizen, M. A., Dickie, I.
+A., \& Bernard-Verdier, M. (2016). A common framework for identifying
+linkage rules across different types of interactions. \emph{Functional
+Ecology}, \emph{30}(12), 1894--1903.
+\url{http://onlinelibrary.wiley.com/doi/10.1111/1365-2435.12666/full}
+
 \leavevmode\hypertarget{ref-Botella2022AppGra}{}%

### 2022-01-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@8da19da65b247ecf582d2d2538cadaede0352ed1 🚀

@@
 
-As Herbert (1965) rightfully pointed out, ``{[}y{]}ou can't draw neat
-lines around planet-wide problems''; in this regard, any inference of a
-metaweb at large scales must contend with several interesting and
-interwoven families of problems.
+The goal of metaweb inference is to provide information about the
+interactions between species at a large spatial scale. But as Herbert
+(1965) rightfully pointed out, ``{[}y{]}ou can't draw neat lines around
+planet-wide problems''; any inference of a metaweb at large scales must
+contend with several novel, and interwoven, families of problems.
 
@@
 likely be indicated by large confidence intervals during estimation of
-the values in the low-rank space, but the lack of well documented
-metawebs is currently preventing the development of more concrete
-guidelines. The question of phylogenetic relatedness and dispersal is
-notably true if the metaweb is assembled in an area with mostly endemic
-species, and as with every predictive algorithm, there is room for the
-application of our best ecological judgement. Conversely, the metaweb
-should be reliably filled, which assumes that the \(S^2\) interactions
-in a pool of \(S\) species have been examined, either through literature
-surveys or expert elicitation.
-
-\textbf{TK} Supp. Mat. 1 provides some guidance as to the type of
-sampling effort that should be prioritized. While RDPG was able to
-maintain very high predictive power when interactions were missing, the
-addition of false positive interactions was immediately detected; this
-suggests that it may be appropriate to err on the side of ``too many''
-interactions when constructing the initial metaweb to be transferred.
+the values in the low-rank space, or by non-overlapping trait
+distributions in the known and unknown species. The lack of well
+documented metawebs is currently preventing the development of more
+concrete guidelines. The question of phylogenetic relatedness and
+dispersal is notably true if the metaweb is assembled in an area with
+mostly endemic species, and as with every predictive algorithm, there is
+room for the application of our best ecological judgement.
 
@@
 should be used to infer the new metaweb in, as this determines the
-species pool that must be used.
-
-\textbf{TK} In our application, we focused on the mammals of Canada. The
+species pool that must be used. Metawebs can be constructed by assigning
+interactions in a list of species within geographic boundaries. The
 upside of this approach is that information at the country level is
-likely to be required by policy makers and stakeholders for their
-biodiversity assessment, as each country tends to set goals at the
-national level (Buxton et al., 2021) for which quantitative instruments
-are designed (Turak et al., 2017), with specific strategies often
-enacted at smaller scales (Ray et al., 2021). And yet, we do not really
-have a satisfying answer to the question of ``where does a food web
-stop?''; the current most satisfying solutions involve examining the
-spatial consistency of network area relationships (Fortin et al., 2021;
-see \emph{e.g.} Galiana et al., 2018, 2019, 2021), which is of course
-impossible in the absence of enough information about the network
-itself. This suggests that an \emph{a posteriori} refinement of the
-results may be required, based on a downscaling of the metaweb.
-
-The final family of problems relates less to the availability of data or
-quantitative tools, and more to the praxis of spatial ecology. Operating
-under the context of national divisions, in large parts of the world,
-reflects nothing more than the legacy of settler colonialism. Indeed,
-the use of ecological data is not an apolitical act (Nost \& Goldstein,
-2021), as data infrastructures tend to be designed to answer questions
-within national boundaries, and their use both draws upon and reinforces
+likely to be required for biodiversity assessments, as countries set
+goals at the national level (Buxton et al., 2021), and as quantitative
+instruments are designed to work at these scales (Turak et al., 2017);
+specific strategies are often enacted at smaller scales, nested within a
+specific country (Ray et al., 2021). But there is no guarantee that
+these boundaries are meaningful. In fact, we do not have a satisfying
+answer to the question of ``where does a food web stop?''; the most
+promising solutions involve examining the spatial consistency of network
+area relationships (Fortin et al., 2021; see \emph{e.g.} Galiana et al.,
+2018, 2019, 2021), which is impossible in the absence of enough
+information about the network itself. This suggests that infered metaweb
+should be futher downscaled to allow \emph{a posteriori} analyses.
+
+The final family of problems relates less to ecological concepts and
+more to the praxis of ecological research. Operating under the context
+of national divisions, in large parts of the world, reflects nothing
+more than the legacy of settler colonialism. Indeed, the use of
+ecological data is not an apolitical act (Nost \& Goldstein, 2021), as
+data infrastructures tend to be designed to answer questions within
+national boundaries, and their use both draws upon and reinforces
 territorial statecraft; as per Machen \& Nost (2021), this is
@@
 re-used for governance (\emph{e.g.} enacting conservation decisions at
-the national scale). We therefore recognize that methods such as we
-propose operate under the framework that contributed to the ongoing
-biodiversity crisis (Adam, 2014), reinforced environmental injustice
-(Choudry, 2013; Domínguez \& Luoma, 2020), and on Turtle Island
-especially, should be replaced by Indigenous principles of land
-management (Eichhorn et al., 2019; No'kmaq et al., 2021). As we see
-AI/ML being increasingly mobilized to generate knowledge that is lacking
-for conservation decisions (\emph{e.g.} Lamba et al., 2019; Mosebo
-Fernandes et al., 2020), our discussion of these tools need to go beyond
-the technical, and into the governance consequences they can have.
+the national scale). We therefore recognize that predictive approaches
+deployed at the continental scale, no matter their intent, originate in
+the framework that contributed to the ongoing biodiversity crisis (Adam,
+2014), reinforced environmental injustice (Choudry, 2013; Domínguez \&
+Luoma, 2020), and on Turtle Island especially, should be replaced by
+Indigenous principles of land management (Eichhorn et al., 2019; No'kmaq
+et al., 2021). As we see AI/ML being increasingly mobilized to generate
+knowledge that is lacking for conservation decisions (\emph{e.g.} Lamba
+et al., 2019; Mosebo Fernandes et al., 2020), our discussion of these
+tools need to go beyond the technical, and into the governance
+consequences they can have.
 

### 2022-01-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@b4859b66321cb2a8375edc04f836d83e592252ff 🚀

@@
 
-\hypertarget{the-metaweb-embeds-strong-ecological-hypotheses}{%
-\section{The metaweb embeds strong ecological
-hypotheses}\label{the-metaweb-embeds-strong-ecological-hypotheses}}
+\hypertarget{the-metaweb-embeds-ecological-hypotheses-and-practices}{%
+\section{The metaweb embeds ecological hypotheses and
+practices}\label{the-metaweb-embeds-ecological-hypotheses-and-practices}}
 

### 2022-01-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@09cee1e9c0d55662cb8b757f5df57699662d9a2e 🚀

@@
 Following the definition of Dunne (2006), a metaweb is the ecological
-network analogue to the species pool; specifically, it iventories
-\emph{potential} interactions between species from a spatially delimited
+network analogue to the species pool; specifically, it inventories
+\emph{potential} interactions between species for a spatially delimited
 area (and so captures the \(\gamma\) diversity of interactions). The
@@
 \centering
-\includegraphics{figures/conceptual_embedding.jpg}
+\includegraphics{figures/conceptual_embedding.png}
 \caption{Overview of the embedding process. A network (\emph{A}),
@@
 \centering
-\includegraphics{figures/conceptual_prediction.jpg}
+\includegraphics{figures/conceptual_prediction.png}
 \caption{From a low-dimensional feature vector (see

### 2022-01-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@6166c2549c61ce3da71f45b9eebf407f2b9230d5 🚀

@@
 the spatial area it covers: it will have a different structure, notably
-by having a larger connectance (see \emph{e.g.} Wood et al., 2015), from
-any of these local networks. These local networks (capturing the
-\(\alpha\) diversity of interactions) are a subset of the metaweb's
-species and interactions, and have been called ``metaweb realizations''
-(Poisot et al., 2015). Differences between local networks and their
-metawebs are due to chance, species abundance and co-occurrence, local
-environmental conditions, and local distribution of functional traits,
-among others.
+by having a larger connectance (see \emph{e.g.} Wood et al., 2015) and
+complexity (see \emph{e.g.} Galiana et al., 2022), from any of these
+local networks. These local networks (capturing the \(\alpha\) diversity
+of interactions) are a subset of the metaweb's species and interactions,
+and have been called ``metaweb realizations'' (Poisot et al., 2015).
+Differences between local networks and their metawebs are due to chance,
+species abundance and co-occurrence, local environmental conditions, and
+local distribution of functional traits, among others.
 
@@
 ``upper bounds'' on what the composition of the local networks can be
-(see \emph{e.g.} McLeod et al., 2021). These local networks may be
-reconstructed given appropriate knowledge of local species composition,
-providing information on structure of food webs at finer spatial scales.
-This has been done for example for tree-galler-parasitoid systems
-(Gravel et al., 2018), fish trophic interactions (Albouy et al., 2019),
-tetrapod trophic interactions (O'Connor et al., 2020), and crop-pest
-networks (Grünig et al., 2020). In this contribution, we highlight the
-\emph{probabilistic} nature of metawebs, discuss how a family of machine
-learning tools (graph embeddings and transfer learning) can be used to
-overcome data limitations to metaweb inference, and highlight how the
-use of metawebs introduces important questions for the field of network
-ecology.
+(see \emph{e.g.} McLeod et al., 2021); this information can help
+evaluate the ability of ecological assemblages to withstand the effects
+of, for example, climate change (Fricke et al., 2022). These local
+networks may be reconstructed given appropriate knowledge of local
+species composition, providing information on structure of food webs at
+finer spatial scales. This has been done for example for
+tree-galler-parasitoid systems (Gravel et al., 2018), fish trophic
+interactions (Albouy et al., 2019), tetrapod trophic interactions
+(O'Connor et al., 2020), and crop-pest networks (Grünig et al., 2020).
+In this contribution, we highlight the \emph{probabilistic} nature of
+metawebs, discuss how a family of machine learning tools (graph
+embeddings and transfer learning) can be used to overcome data
+limitations to metaweb inference, and highlight how the use of metawebs
+introduces important questions for the field of network ecology.
 
@@
 
+\leavevmode\hypertarget{ref-Fricke2022EffDef}{}%
+Fricke, E. C., Ordonez, A., Rogers, H. S., \& Svenning, J.-C. (2022).
+The effects of defaunation on plants' capacity to track climate change.
+\emph{Science}.
+\url{https://www.science.org/doi/abs/10.1126/science.abk3510}
+
 \leavevmode\hypertarget{ref-Galiana2021SpaSca}{}%
@@
 \emph{42}(6), 1175--1187. \url{https://doi.org/10.1111/ecog.03684}
+
+\leavevmode\hypertarget{ref-Galiana2022EcoNet}{}%
+Galiana, N., Lurgi, M., Bastazini, V. A. G., Bosch, J., Cagnolo, L.,
+Cazelles, K., Claramunt-López, B., Emer, C., Fortin, M.-J., Grass, I.,
+Hernández-Castellano, C., Jauker, F., Leroux, S. J., McCann, K., McLeod,
+A. M., Montoya, D., Mulder, C., Osorio-Canadas, S., Reverté, S.,
+\ldots{} Montoya, J. M. (2022). Ecological network complexity scales
+with area. \emph{Nature Ecology \& Evolution}, 1--8.
+\url{https://doi.org/10.1038/s41559-021-01644-4}
 

### 2022-01-15 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@b126c68309ef23dd542c6e4aab525cfb6b98b32a 🚀

@@
 species abundance and co-occurrence, local environmental conditions, and
-local distribution of functional traits, among others.
+local distribution of functional traits, among others. Yet, recent
+results by Saravia et al. (2021) strongly suggest that the local
+realizations only respond weakly to local conditions: instead, they
+reflect constraints inherited by the structure of their metaweb. This
+establishes the metaweb structure as the core goal of predictive network
+ecology, as it is a required information to accurately produce
+downscaled, local predictions.
 
@@
 
+\leavevmode\hypertarget{ref-Saravia2021EcoNet}{}%
+Saravia, L. A., Marina, T. I., Kristensen, N. P., De Troch, M., \& Momo,
+F. R. (2021). Ecological network assembly: How the regional metaweb
+influences local food webs. \emph{Journal of Animal Ecology},
+\emph{n/a}(n/a). \url{https://doi.org/10.1111/1365-2656.13652}
+
 \leavevmode\hypertarget{ref-Strydom2021FooWeb}{}%

### 2022-01-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@d02a7d6914473de70559174e284da8ec696ee1ca 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@bc2a1c88fcd2e4d7cf6f074fd89d176be6591fca 🚀

@@
 the list of species interactions. Graph embedding is an emerging field
-in machine learning that holds great potential for ecoloigcal problems.%
+in machine learning that holds great potential for ecological problems.%
     \item In this perspective, we outline how the challenges associated
@@
 Ecological networks are an interesting candidate for the widespread
-application of embeddings, as they tend to posess a shared sstructural
+application of embeddings, as they tend to possess a shared structural
 backbone (Mora et al., 2018), which hints at structural invariants that
@@
 2018, 2019, 2021), which is impossible in the absence of enough
-information about the network itself. This suggests that infered metaweb
-should be futher downscaled to allow \emph{a posteriori} analyses.
+information about the network itself. This suggests that inferred
+metaweb should be further downscaled to allow \emph{a posteriori}
+analyses.
 

### 2022-02-08 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@4d28c3d0586ee51f57656245ff4035561ea746ac 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@056d2ea48feb5fa0c34dec6d1acd591bb0714bd6 🚀

@@
 \,\textsuperscript{1,2,‡}\quad %
+\href{https://orcid.org/0000-0003-0193-5441}{Salomé\,Bouskila}%
+%
+\,\textsuperscript{1,‡}\quad %
+\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
+%
+\,\textsuperscript{1,3,2}\quad %
+\href{https://orcid.org/0000-0003-4036-977X}{Ceres\,Barros}%
+%
+\,\textsuperscript{4}\quad %
+\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
+%
+\,\textsuperscript{5,2}\quad %
+\href{https://orcid.org/0000-0003-0452-6993}{Maxwell J\,Farrell}%
+%
+\,\textsuperscript{6}\quad %
+\href{https://orcid.org/0000-0002-9935-1366}{Marie-Josée\,Fortin}%
+%
+\,\textsuperscript{6}\quad %
+\href{https://orcid.org/0000-0003-3220-6161}{Victoria\,Hemming}%
+%
+\,\textsuperscript{7}\quad %
+\href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
+%
+\,\textsuperscript{3,2}\quad %
+\href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
+%
+\,\textsuperscript{5,2}\quad %
+\href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
+%
+\,\textsuperscript{8}\quad %
+\href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
+%
+\,\textsuperscript{9}\quad %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
@@
 Montréal, Montréal, Canada\quad \textsuperscript{2}\,Quebec Centre for
-Biodiversity Science, Montréal, Canada
+Biodiversity Science, Montréal,
+Canada\quad \textsuperscript{3}\,Département de Biologie, Université de
+Sherbrooke, Sherbrooke, Canada\quad \textsuperscript{4}\,Department of
+Forest Resources Management, University of British Columbia, Vancouver,
+B.C., Canada\quad \textsuperscript{5}\,Department of Biology, McGill
+University, Montréal, Canada\quad \textsuperscript{6}\,Department of
+Ecology \& Evolutionary Biology, University of Toronto, Toronto,
+Canada\quad \textsuperscript{7}\,Department of Forest and Conservation
+Sciences, University of British Columbia, Vancouver,
+Canada\quad \textsuperscript{8}\,Centre for Integrative Ecology, School
+of Biological Sciences, University of Canterbury, Canterbury, New
+Zealand\quad \textsuperscript{9}\,School of Mathematics and Statistics,
+University of Canterbury, Canterbury, New Zealand
 
@@
 Following the definition of Dunne (2006), a metaweb is the ecological
-network analogue to the species pool; specifically, it inventories
+network analogue to the species pool; specifically, it inventories all
 \emph{potential} interactions between species for a spatially delimited
@@
 complexity (see \emph{e.g.} Galiana et al., 2022), from any of these
-local networks. These local networks (capturing the \(\alpha\) diversity
-of interactions) are a subset of the metaweb's species and interactions,
-and have been called ``metaweb realizations'' (Poisot et al., 2015).
-Differences between local networks and their metawebs are due to chance,
-species abundance and co-occurrence, local environmental conditions, and
-local distribution of functional traits, among others. Yet, recent
-results by Saravia et al. (2021) strongly suggest that the local
-realizations only respond weakly to local conditions: instead, they
-reflect constraints inherited by the structure of their metaweb. This
-establishes the metaweb structure as the core goal of predictive network
-ecology, as it is a required information to accurately produce
-downscaled, local predictions.
+local networks. These local networks (which capture the \(\alpha\)
+diversity of interactions) are a subset of the metaweb's species and
+their interactions, and have been called ``metaweb realizations''
+(Poisot et al., 2015). Differences between local networks and their
+metawebs are due to chance, species abundance and co-occurrence, local
+environmental conditions, and local distribution of functional traits,
+among others. Yet, recent results by Saravia et al. (2021) strongly
+suggest that the local realizations only respond weakly to local
+conditions: instead, they reflect constraints inherited by the structure
+of their metaweb. This establishes the metaweb structure as the core
+goal of predictive network ecology, as it is a required information to
+accurately produce downscaled, local predictions.
 
@@
 2015), it holds valuable ecological information. Specifically, it is the
-``upper bounds'' on what the composition of the local networks can be
-(see \emph{e.g.} McLeod et al., 2021); this information can help
-evaluate the ability of ecological assemblages to withstand the effects
-of, for example, climate change (Fricke et al., 2022). These local
-networks may be reconstructed given appropriate knowledge of local
-species composition, providing information on structure of food webs at
-finer spatial scales. This has been done for example for
-tree-galler-parasitoid systems (Gravel et al., 2018), fish trophic
-interactions (Albouy et al., 2019), tetrapod trophic interactions
-(O'Connor et al., 2020), and crop-pest networks (Grünig et al., 2020).
-In this contribution, we highlight the \emph{probabilistic} nature of
-metawebs, discuss how a family of machine learning tools (graph
-embeddings and transfer learning) can be used to overcome data
-limitations to metaweb inference, and highlight how the use of metawebs
-introduces important questions for the field of network ecology.
+``upper bounds'' on what the composition of the local networks, given
+the local species pool, can be (see \emph{e.g.} McLeod et al., 2021);
+this information can help evaluate the ability of ecological assemblages
+to withstand the effects of, for example, climate change (Fricke et al.,
+2022). These local networks may be reconstructed given an appropriate
+knowledge of local species composition and provide information on the
+structure of food webs at finer spatial scales. This has been done for
+example for tree-galler-parasitoid systems (Gravel et al., 2018), fish
+trophic interactions (Albouy et al., 2019), tetrapod trophic
+interactions (O'Connor et al., 2020; \textbf{Braga2019SpaAna?}), and
+crop-pest networks (Grünig et al., 2020). In this contribution, we
+highlight the power in viewing (and constructing) metawebs as
+\emph{probabilistic} objects in the context of rare interactions,
+discuss how a family of machine learning tools (graph embeddings and
+transfer learning) can be used to overcome data limitations to metaweb
+inference, and highlight how the use of metawebs introduces important
+questions for the field of network ecology.
 
@@
 
-Dallas et al. (2017) suggested that most links in ecological networks
-are cryptic, \emph{i.e.} uncommon or hard to observe. This argument
-echoes Jordano (2016): sampling ecological interactions is difficult
-because it requires first the joint observation of two species, and then
-the observation of their interaction. In addition, it is generally
-expected that weak or rare links would be more common in networks
-(Csermely, 2004), compared to strong, persistent links; this is notably
-the case in food chains, wherein many weaker links are key to the
-stability of a system (Neutel et al., 2002). In the light of these
+Treating interactions probabilistic (as opposed to binary) is a more
+nuanced and realistic way to represent interactions. Dallas et al.
+(2017) suggested that most links in ecological networks are cryptic,
+\emph{i.e.} uncommon or hard to observe. This argument echoes Jordano
+(2016): sampling ecological interactions is difficult because it
+requires first the joint observation of two species, and then the
+observation of their interaction. In addition, it is generally expected
+that weak or rare links to be more prevalent in networks than common or
+rare links (Csermely, 2004), compared to strong, persistent links; this
+is notably the case in food chains, wherein many weaker links are key to
+the stability of a system (Neutel et al., 2002). In the light of these
 observations, we expect to see an over-representation of low-probability
@@
 uses of metawebs, was based on the presence/absence of interactions.
-Moving towards \emph{probabilistic} metawebs, by represent interactions
-as Bernoulli events (see \emph{e.g.} Poisot et al., 2016), offers the
-opportunity to weigh these rare interactions appropriately. The inherent
-plasticity of interactions is important to capture: there have been
-documented instances of food webs undergoing rapid collapse/recovery
-cycles over short periods of time (\emph{e.g.} Pedersen et al., 2017).
-These considerations emphasize why metaweb predictions should focus on
-quantitative (preferentially probabilistic) predictions; this should
-constrain the suite of appropriate models.
+Moving towards \emph{probabilistic} metawebs, by representing
+interactions as Bernoulli events (see \emph{e.g.} Poisot et al., 2016),
+offers the opportunity to weigh these rare interactions appropriately.
+The inherent plasticity of interactions is important to capture: there
+have been documented instances of food webs undergoing rapid
+collapse/recovery cycles over short periods of time (\emph{e.g.}
+Pedersen et al., 2017). These considerations emphasize why metaweb
+predictions should focus on quantitative (preferentially probabilistic)
+predictions; this should constrain the suite of appropriate models.
 
@@
 interactions are documented, the effort required in documenting each
-rare interaction will increase exponentially, and will do so for each
-undocumented interaction. Recent proposals suggest that machine learning
-algorithms, in these situations, can act as data generators (Hoffmann et
-al., 2019): high quality observational data can generate the core rules
-underpinning the network structure, and be supplemented with synthetic
-data coming from predictive models, increasing the volume of information
-available for inference. Indeed, Strydom, Catchen, et al. (2021)
-suggested that knowing the metaweb may render the prediction of local
-networks easier, because it fixes an ``upper bound'' on which
-interactions can exist. A probabilistic metaweb represents an
-aggregation of informative priors on the interactions, an elusive
-information with the potential to boost our predictive ability
-(Bartomeus et al., 2016).
+rare interaction will increase exponentially. Recent proposals suggest
+that machine learning algorithms, in these situations, can act as data
+generators (Hoffmann et al., 2019): high quality observational data can
+generate the core rules underpinning the network structure, and be
+supplemented with synthetic data coming from predictive models,
+increasing the volume of information available for inference. Indeed,
+Strydom, Catchen, et al. (2021) suggested that knowing the metaweb may
+render the prediction of local networks easier, because it fixes an
+``upper bound'' on which interactions can exist. In this context a
+probabilistic metaweb represents an aggregation of informative priors on
+the interactions, elusive information with the potential to boost our
+predictive ability (Bartomeus et al., 2016).
 
@@
 \caption{Overview of the embedding process. A network (\emph{A}),
-possibbly represented as its adjacency matrix (\emph{B}), is converted
+possibly represented as its adjacency matrix (\emph{B}), is converted
 into a lower-dimensional object (\emph{C}) where nodes, subgraphs, or
@@
 
-Graph embedding fig.~\ref{fig:embedding} is a varied family of machine
+Graph embedding (fig.~\ref{fig:embedding}) is a varied family of machine
 learning techniques aiming to transform nodes and edges into a vector
@@
 backbone (Mora et al., 2018), which hints at structural invariants that
-can be revealed a lower dimensions. Indeed, previous work by Eklöf et
-al. (2013) suggests that food webs are inherently low-dimensional
-objects, and can be adequately represented with less than ten
-dimensions. Simulation results by Botella et al. (2022) suggest that
-there is no best method to identify architectural similarities between
-networks, and that multiple approaches need to be tested and compared to
-the network descriptor of interest. This matches with previous, more
-general results on graph embedding, which suggest that embedding
-algorithm choice matters for the results (Goyal \& Ferrara, 2018). In
-tbl.~\ref{tbl:methods}, we present a selection of common graph
-embeddings methods, alongside examples of their use to predict species
-interactions (when they have been used this way).
+can be revealed at lower dimensions. Indeed, food webs are inherently
+low-dimensional objects, and can be adequately represented with less
+than ten dimensions (Eklöf et al., 2013; \textbf{Braga2019SpaAna?}).
+Simulation results by Botella et al. (2022) suggest that there is no
+best method to identify architectural similarities between networks, and
+that multiple approaches need to be tested and compared to the network
+descriptor of interest. This matches previous, more general results on
+graph embedding, which suggest that the choice of embedding algorithm
+matters for the results (Goyal \& Ferrara, 2018). In
+tbl.~\ref{tbl:methods}, we present a selection of common graph embedding
+methods, alongside examples of their use to predict species
+interactions.
 
@@
 approaches, by time of publication, alongside examples of their use in
-the prediction of species interactions. Surprisingly, these methods have
-not yet been used routinely to predict species interactions; most of the
-examples we identified were either statistical associations, or
-analogues to joint species distribution models. \(^a\): statistical
-interactions; \(^b\): joint-SDM-like approach.}\tabularnewline
+the prediction of species interactions. These methods have not yet been
+routinely used to predict species interactions; most examples that we
+identified were either statistical associations, or analogues to joint
+species distribution models. \(^a\): statistical interactions; \(^b\):
+joint-SDM-like approach.}\tabularnewline
 \toprule
-\begin{minipage}[b]{0.13\columnwidth}\raggedright
+\begin{minipage}[b]{0.11\columnwidth}\raggedright
 Method\strut
-\end{minipage} & \begin{minipage}[b]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{0.31\columnwidth}\raggedright
 Embedding approach\strut
-\end{minipage} & \begin{minipage}[b]{0.19\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[b]{0.17\columnwidth}\raggedleft
 Reference\strut
-\end{minipage} & \begin{minipage}[b]{0.22\columnwidth}\raggedleft
-Application\strut
+\end{minipage} & \begin{minipage}[b]{0.30\columnwidth}\raggedleft
+Application in species interactions\strut
 \end{minipage}\tabularnewline
@@
 \toprule
-\begin{minipage}[b]{0.13\columnwidth}\raggedright
+\begin{minipage}[b]{0.11\columnwidth}\raggedright
 Method\strut
-\end{minipage} & \begin{minipage}[b]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{0.31\columnwidth}\raggedright
 Embedding approach\strut
-\end{minipage} & \begin{minipage}[b]{0.19\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[b]{0.17\columnwidth}\raggedleft
 Reference\strut
-\end{minipage} & \begin{minipage}[b]{0.22\columnwidth}\raggedleft
-Application\strut
+\end{minipage} & \begin{minipage}[b]{0.30\columnwidth}\raggedleft
+Application in species interactions\strut
 \end{minipage}\tabularnewline
@@
 \endhead
-\begin{minipage}[t]{0.13\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 tSNE\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
 nodes through statistical divergence\strut
-\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
 Hinton \& Roweis (2002)\strut
-\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
 Cieslak et al. (2020) \(^a\)\strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.13\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 RDPG\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
 graph through SVD\strut
-\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
 Young \& Scheinerman (2007)\strut
-\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
 Poisot et al. (2021)\strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.13\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 DeepWalk\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
 graph walk\strut
-\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
 Perozzi et al. (2014)\strut
-\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
 Wardeh et al. (2021)\strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.13\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 FastEmbed\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
 graph through PCA/SVD analogue\strut
-\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
 Ramasamy \& Madhow (2015)\strut
-\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.13\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 LINE\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
 nodes through statistical divergence\strut
-\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
 Tang et al. (2015)\strut
-\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.13\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 SDNE\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
 nodes through auto-encoding\strut
-\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
 D. Wang et al. (2016)\strut
-\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.13\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 node2vec\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
 nodes embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
 Grover \& Leskovec (2016)\strut
-\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.13\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 graph2vec\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
 sub-graph embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
 Narayanan et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.13\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 DMSE\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
 joint nodes embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
 D. Chen et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
 D. Chen et al. (2017) \(^b\)\strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.13\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 HARP\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
 nodes through a meta-strategy\strut
-\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
 H. Chen et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.13\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 GraphKKE\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
 graph embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
 Melnyk et al. (2020)\strut
-\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
 Melnyk et al. (2020) \(^a\)\strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.13\columnwidth}\raggedright
+\begin{minipage}[t]{0.11\columnwidth}\raggedright
 Joint methods\strut
-\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
 multiple graphs\strut
-\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
 S. Wang et al. (2021)\strut
-\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
 \strut
@@
 all interactions were known, based on nodes metadata. This example has
-many parallels in ecology see \ref{fig:prediction}, in which node
+many parallels in ecology (see fig.~\ref{fig:prediction}), in which node
 metadata can be given by phylogeny or functional traits. Rather than
@@
 
-The first is the spatial and taxonomic limit of the metaweb to embed and
+The first is the taxonomic and spatial limit of the metaweb to embed and
 transfer. If the initial metaweb is too narrow in scope, notably from a
@@
 dispersal is notably true if the metaweb is assembled in an area with
-mostly endemic species, and as with every predictive algorithm, there is
-room for the application of our best ecological judgement.
+mostly endemic species (\emph{i.e.} potentially limited
+phylogenetic/species overlap), and as with every predictive algorithm,
+there is room for the application of our best ecological judgement.
 
@@
 information about the network itself. This suggests that inferred
-metaweb should be further downscaled to allow \emph{a posteriori}
+metawebs should be further downscaled to allow for \emph{a posteriori}
 analyses.
@@
 data infrastructures tend to be designed to answer questions within
-national boundaries, and their use both draws upon and reinforces
+national boundaries, and their use often draws upon and reinforces
 territorial statecraft; as per Machen \& Nost (2021), this is
@@
 2014), reinforced environmental injustice (Choudry, 2013; Domínguez \&
-Luoma, 2020), and on Turtle Island especially, should be replaced by
+Luoma, 2020), and \emph{e.g.} as on Turtle Island, should be replaced by
 Indigenous principles of land management (Eichhorn et al., 2019; No'kmaq
-et al., 2021). As we see AI/ML being increasingly mobilized to generate
-knowledge that is lacking for conservation decisions (\emph{e.g.} Lamba
-et al., 2019; Mosebo Fernandes et al., 2020), our discussion of these
-tools need to go beyond the technical, and into the governance
-consequences they can have.
+et al., 2021). As we see artificial intelligence/machine learning being
+increasingly mobilized to generate knowledge that is lacking for
+conservation decisions (\emph{e.g.} Lamba et al., 2019; Mosebo Fernandes
+et al., 2020), our discussion of these tools need to go beyond the
+technical, and into the governance consequences they can have.
 
@@
 Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak
-nations. TP, TS, DC, and LP received funding from the Canadian Institue
+nations. TP, TS, DC, and LP received funding from the Canadian Institute
 for Ecology \& Evolution. FB is funded by the Institute for Data

### 2022-02-08 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@4d28c3d0586ee51f57656245ff4035561ea746ac 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@056d2ea48feb5fa0c34dec6d1acd591bb0714bd6 🚀

@@
 \,\textsuperscript{1,2,‡}, %
+\href{https://orcid.org/0000-0003-0193-5441}{Salomé\,Bouskila}%
+%
+\,\textsuperscript{1,‡}, %
+\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
+%
+\,\textsuperscript{1,3,2}, %
+\href{https://orcid.org/0000-0003-4036-977X}{Ceres\,Barros}%
+%
+\,\textsuperscript{4}, %
+\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
+%
+\,\textsuperscript{5,2}, %
+\href{https://orcid.org/0000-0003-0452-6993}{Maxwell J\,Farrell}%
+%
+\,\textsuperscript{6}, %
+\href{https://orcid.org/0000-0002-9935-1366}{Marie-Josée\,Fortin}%
+%
+\,\textsuperscript{6}, %
+\href{https://orcid.org/0000-0003-3220-6161}{Victoria\,Hemming}%
+%
+\,\textsuperscript{7}, %
+\href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
+%
+\,\textsuperscript{3,2}, %
+\href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
+%
+\,\textsuperscript{5,2}, %
+\href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
+%
+\,\textsuperscript{8}, %
+\href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
+%
+\,\textsuperscript{9}, %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
@@
 Montréal, Montréal, Canada; \textsuperscript{2}\,Quebec Centre for
-Biodiversity Science, Montréal, Canada\\
+Biodiversity Science, Montréal, Canada; \textsuperscript{3}\,Département
+de Biologie, Université de Sherbrooke, Sherbrooke,
+Canada; \textsuperscript{4}\,Department of Forest Resources Management,
+University of British Columbia, Vancouver, B.C.,
+Canada; \textsuperscript{5}\,Department of Biology, McGill University,
+Montréal, Canada; \textsuperscript{6}\,Department of Ecology \&
+Evolutionary Biology, University of Toronto, Toronto,
+Canada; \textsuperscript{7}\,Department of Forest and Conservation
+Sciences, University of British Columbia, Vancouver,
+Canada; \textsuperscript{8}\,Centre for Integrative Ecology, School of
+Biological Sciences, University of Canterbury, Canterbury, New
+Zealand; \textsuperscript{9}\,School of Mathematics and Statistics,
+University of Canterbury, Canterbury, New Zealand\\
 \textsuperscript{‡}\,These authors contributed equally to the work\\

### 2022-02-09 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@e56623fbe278bf9e6b31b7a9183dc8d59cf0db2f 🚀

@@
 species interaction networks over large spatial scales (Hortal et al.,
-2015). In a recent overview of the field of ecological network
-prediction, Strydom, Catchen, et al. (2021) identified two challenges of
-interest to the prediction of interactions at large scales. First, there
-is a relative scarcity of relevant data in most places globally --
-paradoxically, this restricts our ability to infer interactions to
-locations where inference is perhaps the least required; second,
-accurate predictions often demand accurate predictors, and the lack of
-methods that can leverage small amount of data is a serious impediment
-to our global predictive ability. In most places, our most reliable
-biodiversity knowledge is that of a species pool: through the analysis
-of databases like GBIF or IUCN, it is possible to establish a list of
-species in a region of interest; but establishing the interactions
-between these species is difficult.
+2015). Understanding species interactions holds enormous potential to
+not only understand and more rapidly learn about species interactions
+and metawebs, but also how changes in management of a single species may
+impact non-target species. In a recent overview of the field of
+ecological network prediction, Strydom, Catchen, et al. (2021)
+identified two challenges of interest to the prediction of interactions
+at large scales. First, there is a relative scarcity of relevant data in
+most places globally -- paradoxically, this restricts our ability to
+infer interactions to locations where inference is perhaps the least
+required (and still leaves us unable to address regions without data);
+second, accurate predictions often demand accurate predictors, and the
+lack of methods that can leverage small amount of data is a serious
+impediment to our global predictive ability. In most places, our most
+reliable biodiversity knowledge is that of a species pool: through the
+analysis of databases like GBIF or IUCN, it is possible to establish a
+list of species in a region of interest; but establishing the
+interactions between these species is difficult.
 
@@
 \caption{Overview of the embedding process. A network (\emph{A}),
-possibly represented as its adjacency matrix (\emph{B}), is converted
-into a lower-dimensional object (\emph{C}) where nodes, subgraphs, or
-edges have specific values (see tbl.~\ref{tbl:methods}). For the
-purposes of prediction, this low-dimensional object encodes feature
-vectors for \emph{e.g.} the nodes. Embedding also allows to visualize
-the structure in the data differently (\emph{D}), much like with a
-principal component analysis.}\label{fig:embedding}
+represented as its adjacency matrix (\emph{B}), is converted into a
+lower-dimensional object (\emph{C}) where nodes, subgraphs, or edges
+have specific values (see tbl.~\ref{tbl:methods}). For the purposes of
+prediction, this low-dimensional object encodes feature vectors for
+\emph{e.g.} the nodes. Embedding also allows to visualize the structure
+in the data differently (\emph{D}), much like with a principal component
+analysis.}\label{fig:embedding}
 }
@@
 embedding of known species (here, A, B, C, and D). Because embeddings
-can be projected back to a graph, this allows to reconstruct a network
-with these new species. This approach constitutes an instance of
+can be projected back to a graph, this allows us to reconstruct a
+network with these new species. This approach constitutes an instance of
 transfer learning.}\label{fig:prediction}
@@
 
-The second series of problems are related to determining which area
-should be used to infer the new metaweb in, as this determines the
-species pool that must be used. Metawebs can be constructed by assigning
-interactions in a list of species within geographic boundaries. The
-upside of this approach is that information at the country level is
-likely to be required for biodiversity assessments, as countries set
-goals at the national level (Buxton et al., 2021), and as quantitative
-instruments are designed to work at these scales (Turak et al., 2017);
-specific strategies are often enacted at smaller scales, nested within a
-specific country (Ray et al., 2021). But there is no guarantee that
-these boundaries are meaningful. In fact, we do not have a satisfying
-answer to the question of ``where does a food web stop?''; the most
-promising solutions involve examining the spatial consistency of network
-area relationships (Fortin et al., 2021; see \emph{e.g.} Galiana et al.,
+The second series of problems relate to determining which area should be
+used to infer the new metaweb in, as this determines the species pool
+that must be used. Metawebs can be constructed by assigning interactions
+in a list of species within geographic boundaries. The upside of this
+approach is that information at the country level is likely to be
+required for biodiversity assessments, as countries set goals at the
+national level (Buxton et al., 2021), and as quantitative instruments
+are designed to work at these scales (Turak et al., 2017); specific
+strategies are often enacted at smaller scales, nested within a specific
+country (Ray et al., 2021). But there is no guarantee that these
+boundaries are meaningful. In fact, we do not have a satisfying answer
+to the question of ``where does a food web stop?''; the most promising
+solutions involve examining the spatial consistency of network area
+relationships (Fortin et al., 2021; see \emph{e.g.} Galiana et al.,
 2018, 2019, 2021), which is impossible in the absence of enough
@@
 national boundaries, and their use often draws upon and reinforces
-territorial statecraft; as per Machen \& Nost (2021), this is
+territorial statecraft. As per Machen \& Nost (2021), this is
 particularly true when the output of ``algorithmic thinking''

### 2022-02-09 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@d1bacbaa6836b261a3f037391dd7be5340e75d5f 🚀

@@
 most places globally -- paradoxically, this restricts our ability to
-infer interactions to locations where inference is perhaps the least
-required (and still leaves us unable to address regions without data);
-second, accurate predictions often demand accurate predictors, and the
-lack of methods that can leverage small amount of data is a serious
-impediment to our global predictive ability. In most places, our most
-reliable biodiversity knowledge is that of a species pool: through the
-analysis of databases like GBIF or IUCN, it is possible to establish a
-list of species in a region of interest; but establishing the
-interactions between these species is difficult.
+infer interactions for locations where inference is perhaps the least
+required (and leaves us unable to make inference in regions without
+interaction data); second, accurate predictions often demand accurate
+predictors, and the lack of methods that can leverage small amount of
+\emph{accurate} data is a serious impediment to our global predictive
+ability. In most places, our most reliable biodiversity knowledge is
+that of a species pool (\emph{i.e.} a set of potentially interacting
+species in a given area): through the analysis of databases like GBIF or
+IUCN, it is possible to construct a list of species in a region of
+interest; but inferring the potential interactions between these species
+is difficult.
 
@@
 trophic interactions (Albouy et al., 2019), tetrapod trophic
-interactions (O'Connor et al., 2020; \textbf{Braga2019SpaAna?}), and
-crop-pest networks (Grünig et al., 2020). In this contribution, we
-highlight the power in viewing (and constructing) metawebs as
-\emph{probabilistic} objects in the context of rare interactions,
-discuss how a family of machine learning tools (graph embeddings and
-transfer learning) can be used to overcome data limitations to metaweb
-inference, and highlight how the use of metawebs introduces important
-questions for the field of network ecology.
+interactions (Braga et al., 2019; O'Connor et al., 2020), and crop-pest
+networks (Grünig et al., 2020). In this contribution, we highlight the
+power in viewing (and constructing) metawebs as \emph{probabilistic}
+objects in the context of rare interactions, discuss how a family of
+machine learning tools (graph embeddings and transfer learning) can be
+used to overcome data limitations to metaweb inference, and highlight
+how the use of metawebs introduces important questions for the field of
+network ecology.
 
@@
 application of embeddings, as they tend to possess a shared structural
-backbone (Mora et al., 2018), which hints at structural invariants that
-can be revealed at lower dimensions. Indeed, food webs are inherently
-low-dimensional objects, and can be adequately represented with less
-than ten dimensions (Eklöf et al., 2013; \textbf{Braga2019SpaAna?}).
-Simulation results by Botella et al. (2022) suggest that there is no
-best method to identify architectural similarities between networks, and
-that multiple approaches need to be tested and compared to the network
-descriptor of interest. This matches previous, more general results on
-graph embedding, which suggest that the choice of embedding algorithm
-matters for the results (Goyal \& Ferrara, 2018). In
+backbone (Bramon Mora et al., 2018), which hints at structural
+invariants that can be revealed at lower dimensions. Indeed, food webs
+are inherently low-dimensional objects, and can be adequately
+represented with less than ten dimensions (Braga et al., 2019; Eklöf et
+al., 2013). Simulation results by Botella et al. (2022) suggest that
+there is no best method to identify architectural similarities between
+networks, and that multiple approaches need to be tested and compared to
+the network descriptor of interest. This matches previous, more general
+results on graph embedding, which suggest that the choice of embedding
+algorithm matters for the results (Goyal \& Ferrara, 2018). In
 tbl.~\ref{tbl:methods}, we present a selection of common graph embedding
@@
 Method\strut
-\end{minipage} & \begin{minipage}[b]{0.31\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{0.30\columnwidth}\raggedright
 Embedding approach\strut
-\end{minipage} & \begin{minipage}[b]{0.17\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedleft
 Reference\strut
-\end{minipage} & \begin{minipage}[b]{0.30\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[b]{0.32\columnwidth}\raggedleft
 Application in species interactions\strut
@@
 tSNE\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
 nodes through statistical divergence\strut
-\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
 Hinton \& Roweis (2002)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
 Cieslak et al. (2020) \(^a\)\strut
@@
 RDPG\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
 graph through SVD\strut
-\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
 Young \& Scheinerman (2007)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
-Poisot et al. (2021)\strut
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
+Poisot et al. (2021); Dalla Riva \& Stouffer (2016)\strut
 \end{minipage}\tabularnewline
@@
 DeepWalk\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
 graph walk\strut
-\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
 Perozzi et al. (2014)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
 Wardeh et al. (2021)\strut
@@
 FastEmbed\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
 graph through PCA/SVD analogue\strut
-\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
 Ramasamy \& Madhow (2015)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
 \strut
@@
 LINE\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
 nodes through statistical divergence\strut
-\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
 Tang et al. (2015)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
 \strut
@@
 SDNE\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
 nodes through auto-encoding\strut
-\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
 D. Wang et al. (2016)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
 \strut
@@
 node2vec\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
 nodes embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
 Grover \& Leskovec (2016)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
 \strut
@@
 graph2vec\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
 sub-graph embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
 Narayanan et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
 \strut
@@
 DMSE\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
 joint nodes embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
 D. Chen et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
 D. Chen et al. (2017) \(^b\)\strut
@@
 HARP\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
 nodes through a meta-strategy\strut
-\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
 H. Chen et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
 \strut
@@
 GraphKKE\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
 graph embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
 Melnyk et al. (2020)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
 Melnyk et al. (2020) \(^a\)\strut
@@
 Joint methods\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
 multiple graphs\strut
-\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
 S. Wang et al. (2021)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
 \strut
@@
 the values in the low-rank space, or by non-overlapping trait
-distributions in the known and unknown species. The lack of well
-documented metawebs is currently preventing the development of more
-concrete guidelines. The question of phylogenetic relatedness and
-dispersal is notably true if the metaweb is assembled in an area with
-mostly endemic species (\emph{i.e.} potentially limited
-phylogenetic/species overlap), and as with every predictive algorithm,
-there is room for the application of our best ecological judgement.
+distributions in the known and unknown species. Alternatively a metaweb
+is too large (taxonomically), then the resulting embeddings would have
+interactions relative to taxonomic groups that not present in the new
+location, resulting in the potential under or over estimation of the
+strength of new predicted interactions. The lack of well documented
+metawebs is currently preventing the development of more concrete
+guidelines. The question of phylogenetic relatedness and dispersal is
+notably true if the metaweb is assembled in an area with mostly endemic
+species (\emph{e.g.} a system that has undergone recent radiation and
+might not have an analogous system with which to draw knowledge from),
+and as with every predictive algorithm, there is room for the
+application of our best ecological judgement.
 
@@
 of national divisions, in large parts of the world, reflects nothing
-more than the legacy of settler colonialism. Indeed, the use of
-ecological data is not an apolitical act (Nost \& Goldstein, 2021), as
-data infrastructures tend to be designed to answer questions within
-national boundaries, and their use often draws upon and reinforces
-territorial statecraft. As per Machen \& Nost (2021), this is
+more than the legacy of settler colonialism, which not only drive a
+disparity in available ecological data, but can entrench said biases
+with the machine learning models that make predictions with them.
+Indeed, the use of ecological data is not an apolitical act (Nost \&
+Goldstein, 2021), as data infrastructures tend to be designed to answer
+questions within national boundaries, and their use often draws upon and
+reinforces territorial statecraft. As per Machen \& Nost (2021), this is
 particularly true when the output of ``algorithmic thinking''
@@
 Ecology}, \emph{30}(12), 1894--1903.
-\url{http://onlinelibrary.wiley.com/doi/10.1111/1365-2435.12666/full}
 
@@
 203--216. \url{https://doi.org/10.1111/2041-210X.13738}
+
+\leavevmode\hypertarget{ref-Braga2019SpaAna}{}%
+Braga, J., Pollock, L. J., Barros, C., Galiana, N., Montoya, J. M.,
+Gravel, D., Maiorano, L., Montemaggiori, A., Ficetola, G. F., Dray, S.,
+\& Thuiller, W. (2019). Spatial analyses of multi-trophic terrestrial
+vertebrate assemblages in Europe. \emph{Global Ecology and
+Biogeography}, \emph{28}(11), 1636--1648.
+\url{https://doi.org/10.1111/geb.12981}
+
+\leavevmode\hypertarget{ref-BramonMora2018IdeCom}{}%
+Bramon Mora, B., Gravel, D., Gilarranz, L. J., Poisot, T., \& Stouffer,
+D. B. (2018). Identifying a common backbone of interactions underlying
+food webs from different ecosystems. \emph{Nature Communications},
+\emph{9}(1), 2603. \url{https://doi.org/10.1038/s41467-018-05056-0}
 
@@
 \emph{Deep Multi-species Embedding}. 3639--3646.
-\url{https://www.ijcai.org/proceedings/2017/509}
 
@@
 \emph{Science}.
-\url{https://www.science.org/doi/abs/10.1126/science.abk3510}
 
@@
 variation of network structure is scale dependent: Understanding the
-biotic specialization of host--parasitoid networks. \emph{Ecography},
+biotic specialization of hostparasitoid networks. \emph{Ecography},
 \emph{42}(6), 1175--1187. \url{https://doi.org/10.1111/ecog.03684}
@@
 
-\leavevmode\hypertarget{ref-Mora2018IdeCom}{}%
-Mora, B. B., Gravel, D., Gilarranz, L. J., Poisot, T., \& Stouffer, D.
-B. (2018). Identifying a common backbone of interactions underlying food
-webs from different ecosystems. \emph{Nature Communications},
-\emph{9}(1), 2603. \url{https://doi.org/10.1038/s41467-018-05056-0}
-
 \leavevmode\hypertarget{ref-Morales-Castilla2015InfBio}{}%
@@
 Murphy, K. P. (2022). \emph{Probabilistic machine learning: An
-introduction}. MIT Press. \href{https://probml.ai}{probml.ai}
+introduction}. MIT Press.
 
@@
 O'Connor, L. M. J., Pollock, L. J., Braga, J., Ficetola, G. F.,
-Maiorano, L., Martinez‐Almoyna, C., Montemaggiori, A., Ohlmann, M., \&
+Maiorano, L., Martinez-Almoyna, C., Montemaggiori, A., Ohlmann, M., \&
 Thuiller, W. (2020). Unveiling the food webs of tetrapods across Europe
@@
 systems} (Vol. 28). Curran Associates, Inc.
-\url{https://proceedings.neurips.cc/paper/2015/file/4f6ffe13a5d75b2d6a3923922b3922e5-Paper.pdf}
 

### 2022-02-09 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@62da9aa2b821626f52e55b3868081990db7a95fe 🚀

@@
 conservation decisions (\emph{e.g.} Lamba et al., 2019; Mosebo Fernandes
-et al., 2020), our discussion of these tools need to go beyond the
-technical, and into the governance consequences they can have.
+et al., 2020) and drive policy decisions (Weiskopf et al., 2022), our
+discussion of these tools need to go beyond the technical, and into the
+governance consequences they can have.
 
@@
 
+\leavevmode\hypertarget{ref-Weiskopf2022IncUpt}{}%
+Weiskopf, S. R., Harmáčková, Z. V., Johnson, C. G., Londoño-Murcia, M.
+C., Miller, B. W., Myers, B. J. E., Pereira, L., Arce-Plata, M. I.,
+Blanchard, J. L., Ferrier, S., Fulton, E. A., Harfoot, M., Isbell, F.,
+Johnson, J. A., Mori, A. S., Weng, E., \& Rosa, I. M. D. (2022).
+Increasing the uptake of ecological model results in policy decisions to
+improve biodiversity outcomes. \emph{Environmental Modelling \&
+Software}, \emph{149}, 105318.
+\url{https://doi.org/10.1016/j.envsoft.2022.105318}
+
 \leavevmode\hypertarget{ref-Wood2015EffSpa}{}%

### 2022-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@b2a921ac18259d59b0857d010a78dd5becdffac1 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@c4b9061048722bb9329fc7030e9ed36fac70400b 🚀

@@
 The popularity of graph embedding techniques in machine learning is more
-prosaic than the search for structural invariants: graphs are discrete
-objects, and machine learning techniques tend to handle continuous data
-better. Bringing a sparse graph into a continuous, dense vector space
-(Xu, 2020) opens up a broader variety of predictive algorithms, notably
-of the sort that are able to predict events as probabilities (Murphy,
-2022). Furthermore, the projection of the graph itself is a
-representation that can be learned; Runghen et al. (2021), for example,
-used a neural network to learn the embedding of a network in which not
-all interactions were known, based on nodes metadata. This example has
-many parallels in ecology (see fig.~\ref{fig:prediction}), in which node
+than the search for structural invariants: graphs are discrete objects,
+and machine learning techniques tend to handle continuous data better.
+Bringing a sparse graph into a continuous, dense vector space (Xu, 2020)
+opens up a broader variety of predictive algorithms, notably of the sort
+that are able to predict events as probabilities (Murphy, 2022).
+Furthermore, the projection of the graph itself is a representation that
+can be learned; Runghen et al. (2021), for example, used a neural
+network to learn the embedding of a network in which not all
+interactions were known, based on nodes metadata. This example has many
+parallels in ecology (see fig.~\ref{fig:prediction}), in which node
 metadata can be given by phylogeny or functional traits. Rather than
@@
 through the Discovery Grants and Discovery Accelerator Supplement
-programs.
+programs. MJF is supported by an NSERC PDF and an RBC Post-Doctoral
+Fellowship
 

### 2022-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@1a3b0a9b61ccf8f7b3eeb8e7fe1fafcecb1c8056 🚀

@@
     \item In this perspective, we outline how the challenges associated
-with infering metawebs line-up with the advantages of graph embeddings;
+with inferring metawebs line-up with the advantages of graph embeddings;
 furthermore, because metawebs are inherently spatial objects, we discuss

### 2022-02-11 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@b4399a5a1602cc5d454dbfc0b5cabcdfa5c29ced 🚀

@@
 
+\textbf{Conflict of interest:} The authors have no conflict interests to
+disclose
+
+\textbf{Authors' contributions:} TS, and TP conceived the ideas
+discussed in the manuscript. All authors contributed to writing and
+editing the manuscript.
+
+\textbf{Data availability:} There is no data associated with this
+manuscript.
+
 \hypertarget{references}{%

### 2022-06-18 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@506bc1d784de934764c8930b355a97ca76bf72b2 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@a96092b77ff5073ad066e801b83b0b46226f9a7f 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@a8599f92e7684e7f5aa8cbbacbf5433ffb071768 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@117ac6d708db764dee6f23f4aa7b357f4c88fc51 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@1ae0189d3cedf179e3b39cad8719776eccbbb86a 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@b8ffddb

@@
 
+\DeclareDelayedFloatFlavour*{longtable}{table}
+
 \pagestyle{plain}
@@
 \thispagestyle{empty}
-{\Large\bfseries\sffamily Predicting metawebs: transfer of graph
-embeddings can help alleviate spatial data deficiencies}
+{\Large\bfseries\sffamily The prediction of species interaction networks
+is facilitated by graph embedding and transfer learning despite data
+limitations}
 \vskip 5em

### 2022-06-18 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@8490e4857ccfb0f5bc050bd7c16f5b52dbe68c83 🚀

@@
 
-Treating interactions probabilistic (as opposed to binary) is a more
-nuanced and realistic way to represent interactions. Dallas et al.
-(2017) suggested that most links in ecological networks are cryptic,
+Treating interactions as probabilistic (as opposed to binary) events is
+a more nuanced and realistic way to represent them. Dallas et al. (2017)
+suggested that most links in ecological networks are cryptic,
 \emph{i.e.} uncommon or hard to observe. This argument echoes Jordano
@@
 methods, alongside examples of their use to predict species
-interactions.
+interactions; most of these methods rely either on linear algebra, or on
+pseudo-random walks on graphs.
+
+One prominent family of approaches we do not discuss in the present
+manuscript is Graph Neural Networks (GNN; \textbf{Zhou2020GraNeu?}); GNN
+are, in a sense, a method to embed a graph into a dense subspace, but
+belong to the family of deep learning methods, which has its own set of
+practices (see \emph{e.g.} \textbf{Goodfellow2016DeeLea?}). An important
+issue with methods based on deep learning is that because their
+parameter space is immense, the sample size of the data fed into them
+must be similarly large (typically thousands of instances). This is a
+requirement for the model to converge correctly during training, but
+this assumption is unlikely to be met given the size of datasets about
+currently available metawebs (or single time/location species
+interaction networks). This data volume requirement is mostly absent
+from the techniques we list below. Furthermore, GNN still have some
+challenges related to their shallow structure, and concerns related to
+scalability (see \textbf{Gupta2021GraNeu?} for a review), which are
+mostly absent from the methods listed in tbl.~\ref{tbl:methods}.
+Assuming that the uptake of next-generation biomonitoring techniques
+does indeed deliver larger datasets on species interactions
+(\textbf{Bohan2017NexGlo?}), there is a potential for GNN to become an
+applicable embedding/predictive technique in the coming years.
 
@@
 macro-evolutionary history of a network is adequately represented by
-some graph embeddings (RDPG; see Dalla Riva \& Stouffer, 2016).
+some graph embeddings (RDPG; see Dalla Riva \& Stouffer, 2016). In a
+recent publication, Strydom, Bouskila, et al. (2021) have used an
+embedding (based on RDPG) to project a metaweb of trophic interactions
+between European mammals, and transfered this information to mammals of
+Canada by using the phylogenetic distance between related clades to
+infer the values in the latent sub-space into which the metaweb was
+projected. By performing the RDPG step on re-constructed value, this
+approach yields a probabilistic trophic metaweb for mammals of Canada
+based on knowledge of European species, despite a limited (\(\approx\)
+5\%) taxonomic overlap.
+
+Graph embeddings \emph{can} serve as a dimensionality reduction method.
+For example, RDPG (Strydom, Bouskila, et al., 2021) and t-SVD (Poisot et
+al., 2021) typically embed networks using fewer dimensions than the
+original network (the original network has as many dimensions as
+species, and as many informative dimensions as trophically unique
+species; Strydom, Dalla Riva, et al., 2021). But this is not
+necessarilly the case -- indeed, one may perform a PCA (a special case
+of SVD) to project the raw data into a subspace that improves the
+efficacy of t-SNE (\textbf{Maaten2009LeaPar?}). There are many
+dimensionality reductions (\textbf{Anowar2021ConEmp?}) that can be
+applied to an embedded network should the need for dimensionality
+reduction (for example for data visualisation) arise. In brief, many
+graph embeddings \emph{can} serve as dimensionality reduction steps, but
+not all do, neither do all dimensionality reduction methods provide
+adequate graph embedding capacities.
 
@@
 planet-wide problems''; any inference of a metaweb at large scales must
-contend with several novel, and interwoven, families of problems.
-
-The first is the taxonomic and spatial limit of the metaweb to embed and
-transfer. If the initial metaweb is too narrow in scope, notably from a
-taxonomic point of view, the chances of finding another area with enough
-related species (through phylogenetic relatedness or similarity of
-functional traits) to make a reliable inference decreases; this would
-likely be indicated by large confidence intervals during estimation of
-the values in the low-rank space, or by non-overlapping trait
-distributions in the known and unknown species. Alternatively a metaweb
-is too large (taxonomically), then the resulting embeddings would have
-interactions relative to taxonomic groups that not present in the new
-location, resulting in the potential under or over estimation of the
-strength of new predicted interactions. The lack of well documented
+contend with several novel, and interwoven, families of problems. In
+this section, we list some of the most pressing research priorities
+(\emph{i.e.} problems that can be adressed with subsequent data analysis
+or simulations), as well as issues related to the application of these
+methods at the science-policy interface.
+
+The first open research problem is the taxonomic and spatial limit of
+the metaweb to embed and transfer. If the initial metaweb is too narrow
+in scope, notably from a taxonomic point of view, the chances of finding
+another area with enough related species (through phylogenetic
+relatedness or similarity of functional traits) to make a reliable
+inference decreases; this would likely be indicated by large confidence
+intervals during estimation of the values in the low-rank space, meaning
+that the representation of the original graph is difficult to transfer
+to the new problem. In addition, other problems can arise due to
+non-overlapping trait distributions in the known and unknown species.
+Alternatively a metaweb is too large (taxonomically), then the resulting
+embeddings would need to represent interactions between taxonomic groups
+that are not present in the new location. This would lead to a much
+higher variance in the starting dataset, and to under-dispersal in the
+target dataset, resulting in the potential under or over estimation of
+the strength of new predicted interactions. The lack of well documented
 metawebs is currently preventing the development of more concrete
@@
 and as with every predictive algorithm, there is room for the
-application of our best ecological judgement.
+application of our best ecological judgement. Because this problem
+relates to dispersal of species in the geographic or phylogenetic space,
+it can certainly be approached through assessing the performance of
+embedding transfer in simulated starting/target species pools.
 
@@
 metawebs should be further downscaled to allow for \emph{a posteriori}
-analyses.
-
-The final family of problems relates less to ecological concepts and
-more to the praxis of ecological research. Operating under the context
-of national divisions, in large parts of the world, reflects nothing
-more than the legacy of settler colonialism, which not only drive a
-disparity in available ecological data, but can entrench said biases
-with the machine learning models that make predictions with them.
+analyses. The methodology for metaweb downscaling is currently limited,
+and it is likely that the sustained effort to characterize the spatial
+dependency of food web structure will lead to more prescriptive
+guidelines about the need for prediction downscaling.
+
+The final family of problems relates less to ecological methods than to
+the praxis of ecological research. Operating under the context of
+national divisions, in large parts of the world, reflects nothing more
+than the legacy of settler colonialism, which drives a disparity in
+available ecological data. Applying any embedding to biased data does
+not debias them, but instead embeds these very same biases, propagating
+them to the machine learning models using embeddings tomake predictions.
 Indeed, the use of ecological data is not an apolitical act (Nost \&
 Goldstein, 2021), as data infrastructures tend to be designed to answer
-questions within national boundaries, and their use often draws upon and
+questions within national boundaries (therefore placing contingencies on
+what is available to be embedded), and their use often draws upon and
 reinforces territorial statecraft. As per Machen \& Nost (2021), this is
@@
 re-used for governance (\emph{e.g.} enacting conservation decisions at
-the national scale). We therefore recognize that predictive approaches
-deployed at the continental scale, no matter their intent, originate in
-the framework that contributed to the ongoing biodiversity crisis (Adam,
-2014), reinforced environmental injustice (Choudry, 2013; Domínguez \&
-Luoma, 2020), and \emph{e.g.} as on Turtle Island, should be replaced by
-Indigenous principles of land management (Eichhorn et al., 2019; No'kmaq
-et al., 2021). As we see artificial intelligence/machine learning being
-increasingly mobilized to generate knowledge that is lacking for
+the national scale). As information on species interaction networks
+structure is increasingly leveraged as a tool to guide conservation
+actions (see \emph{e.g.} recent discussions for food-web based
+conservation; \textbf{Eero2021UseFoo?}; \textbf{NamanFooWeb?};
+\textbf{Stier2017IntExp?}), the need to appraise and correct biases that
+are unwittingly propagated to algorithms when embedded from the original
+data is paramount. Predictive approaches deployed at the continental
+scale, no matter their intent, originate in the framework that
+contributed to the ongoing biodiversity crisis (Adam, 2014) and
+reinforced environmental injustice (Choudry, 2013; Domínguez \& Luoma,
+2020). Particularly on Turtle Island and other territories that were
+traditionally stewarded by Indigenous people, these approaches should be
+replaced (or at least guided and framed) by Indigenous principles of
+land management (Eichhorn et al., 2019; No'kmaq et al., 2021), as part
+of an ``algorithm-in-the-loop'' approach. Human-algorithm interactions
+are notoriously difficult and can yield adverse effect
+(\textbf{Green2019DisInt?}; \textbf{Stevenson2021AlgRis?}), suggesting
+the need to systematically study them for the specific purpose of
+biodiversity governance, as well as to improve the algorithmic literacy
+of decision makers. As we see artificial intelligence/machine learning
+being increasingly mobilized to generate knowledge that is lacking for
 conservation decisions (\emph{e.g.} Lamba et al., 2019; Mosebo Fernandes
 et al., 2020) and drive policy decisions (Weiskopf et al., 2022), our
-discussion of these tools need to go beyond the technical, and into the
-governance consequences they can have.
+discussion of these tools need to go beyond the technical and
+statistical, and into the governance consequences they can have.
 
@@
 
+\leavevmode\hypertarget{ref-Strydom2021SvdEnt}{}%
+Strydom, T., Dalla Riva, G. V., \& Poisot, T. (2021). SVD Entropy
+Reveals the High Complexity of Ecological Networks. \emph{Frontiers in
+Ecology and Evolution}, \emph{9}.
+\url{https://doi.org/10.3389/fevo.2021.623141}
+
 \leavevmode\hypertarget{ref-Tang2015LinLar}{}%

### 2022-06-18 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@506bc1d784de934764c8930b355a97ca76bf72b2 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@117ac6d708db764dee6f23f4aa7b357f4c88fc51 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@927d35eef5774873802855faec618cb24ccddc30 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@8490e4857ccfb0f5bc050bd7c16f5b52dbe68c83 🚀

@@
 
-\noindent {\LARGE \textbf{\textsf{Predicting metawebs: transfer of graph
-embeddings can help alleviate spatial data deficiencies}}}
+\noindent {\LARGE \textbf{\textsf{The prediction of species interaction
+networks is facilitated by graph embedding and transfer learning despite
+data limitations}}}
 

### 2022-06-19 code/demo.jl
illustration figure done, need to work on text

@@ -1,0 +1,56 @@
+# Graph embedding demo
+using EcologicalNetworks
+using CairoMakie
+using LinearAlgebra
+
+# Load a series of bipartite networks
+ids = getfield.(filter(n -> contains("Hadfield")(n.Reference), web_of_life()), :ID)
+N = [convert(BipartiteNetwork, web_of_life(n)) for n in ids]
+
+# Get the metaweb
+M = reduce(∪, N)
+
+# Co-occurrence matrix
+C = zeros(Int64, size(M))
+for n in N
+    i = indexin(species(n; dims=1), species(M; dims=1))
+    j = indexin(species(n; dims=2), species(M; dims=2))
+    C[i, j] .+= 1
+end
+
+# Check the loss due to the embedding
+rnk = collect(1:121)
+L2 = [sum((adjacency(M) - prod(rdpg(M, r))) .^ 2) for r in rnk]
+
+# Plot layout
+fig = Figure(resolution=(800, 550))
+ax1 = Axis(fig[1, 1], xlabel="Rank", ylabel="L2 loss", title="A", titlealign=:left)
+ax2 = Axis(fig[1, 2], xlabel="Dimension 1 (left-subspace)", ylabel="Dimension 2 (left-subspace)", title="B", titlealign=:left)
+ax3 = Axis(fig[2, 1], xlabel="Predicted weight", ylabel="Density", title="C", titlealign=:left)
+ax4 = Axis(fig[2, 2], xlabel="Dimension 1 (left-subspace)", ylabel="Number of hosts", title="D", titlealign=:left)
+fig
+
+# Plot of rank vs. L2
+lines!(ax1, rnk, L2)
+fig
+
+# Values of co-oc vs. non-co-oc. interactions at rank 25
+L, R = rdpg(M, 25)
+
+noc = density!(ax3, (L*R)[findall(iszero.(C))]; normalization=:probability)
+pos = density!(ax3, (L*R)[findall(adjacency(M))]; normalization=:probability)
+neg = density!(ax3, (L*R)[findall(iszero.(adjacency(M)) .& .~iszero.(C))]; normalization=:probability)
+axislegend(ax3, [pos, neg, noc], ["Interactions", "Non-interactions", "No co-occurence"])
+fig
+
+# Representation of the network on axis 1
+
+para = scatter!(ax2, L[:, 1], L[:, 2])
+host = scatter!(ax2, R'[:, 1], R'[:, 2])
[…]

### 2022-06-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@7ebad97c94abdd8e51790494ddfc38f9c4abf9d4 🚀

@@
 
-\hypertarget{the-metaweb-embeds-ecological-hypotheses-and-practices}{%
-\section{The metaweb embeds ecological hypotheses and
-practices}\label{the-metaweb-embeds-ecological-hypotheses-and-practices}}
+\hypertarget{an-illustration-of-metaweb-embedding}{%
+\section{An illustration of metaweb
+embedding}\label{an-illustration-of-metaweb-embedding}}
+
+In this section, we illustrate the embedding of a collection of
+bipartite networks collected by \textbf{REF}, using truncated Singular
+Value Decomposition (t-SVD). The code to reproduce this example (as a
+Jupyter notebook) is available as supplementary material. The resulting
+(binary) metaweb \(\mathcal{M}\) has 2131 interactions between 206
+parasites and 121 hosts (the same metaweb was used for the illustration
+of interaction inference through deep learning in Strydom, Catchen, et
+al., 2021), and its adjacency matrix has full rank (\emph{i.e.} it
+represents a space with 121 dimensions). All analyses were done using
+Julia (Bezanson et al., 2017) version 1.7.2, \emph{Makie.jl}
+(\textbf{Danisch2021MakJl?}), and \emph{EcologicalNetworks.jl} (Poisot
+et al., 2019).
+
+\hypertarget{the-metaweb-embeds-both-ecological-hypotheses-and-practices}{%
+\section{The metaweb embeds both ecological hypotheses and
+practices}\label{the-metaweb-embeds-both-ecological-hypotheses-and-practices}}
 
@@
 
+\leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
+Bezanson, J., Edelman, A., Karpinski, S., \& Shah, V. (2017). Julia: A
+Fresh Approach to Numerical Computing. \emph{SIAM Review}, \emph{59}(1),
+65--98. \url{https://doi.org/10.1137/141000671}
+
 \leavevmode\hypertarget{ref-Botella2022AppGra}{}%
@@
 
+\leavevmode\hypertarget{ref-Poisot2019EcoJl}{}%
+Poisot, T., Belisle, Z., Hoebeke, L., Stock, M., \& Szefer, P. (2019).
+EcologicalNetworks.jl - analysing ecological networks. \emph{Ecography}.
+\url{https://doi.org/10.1111/ecog.04310}
+
 \leavevmode\hypertarget{ref-Poisot2016StrPro}{}%

### 2022-06-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@7d1f33e481bf1cda2e0b88f5b79db035106f84c9 🚀

@@
 One prominent family of approaches we do not discuss in the present
-manuscript is Graph Neural Networks (GNN; \textbf{Zhou2020GraNeu?}); GNN
-are, in a sense, a method to embed a graph into a dense subspace, but
-belong to the family of deep learning methods, which has its own set of
-practices (see \emph{e.g.} \textbf{Goodfellow2016DeeLea?}). An important
-issue with methods based on deep learning is that because their
-parameter space is immense, the sample size of the data fed into them
-must be similarly large (typically thousands of instances). This is a
+manuscript is Graph Neural Networks (GNN; Zhou et al., 2020); GNN are,
+in a sense, a method to embed a graph into a dense subspace, but belong
+to the family of deep learning methods, which has its own set of
+practices (see \emph{e.g.} Goodfellow et al., 2016). An important issue
+with methods based on deep learning is that because their parameter
+space is immense, the sample size of the data fed into them must be
+similarly large (typically thousands of instances). This is a
 requirement for the model to converge correctly during training, but
@@
 challenges related to their shallow structure, and concerns related to
-scalability (see \textbf{Gupta2021GraNeu?} for a review), which are
-mostly absent from the methods listed in tbl.~\ref{tbl:methods}.
-Assuming that the uptake of next-generation biomonitoring techniques
-does indeed deliver larger datasets on species interactions
-(\textbf{Bohan2017NexGlo?}), there is a potential for GNN to become an
-applicable embedding/predictive technique in the coming years.
+scalability (see Gupta et al., 2021 for a review), which are mostly
+absent from the methods listed in tbl.~\ref{tbl:methods}. Assuming that
+the uptake of next-generation biomonitoring techniques does indeed
+deliver larger datasets on species interactions (Bohan et al., 2017),
+there is a potential for GNN to become an applicable
+embedding/predictive technique in the coming years.
 
@@
 of SVD) to project the raw data into a subspace that improves the
-efficacy of t-SNE (\textbf{Maaten2009LeaPar?}). There are many
-dimensionality reductions (\textbf{Anowar2021ConEmp?}) that can be
-applied to an embedded network should the need for dimensionality
-reduction (for example for data visualisation) arise. In brief, many
-graph embeddings \emph{can} serve as dimensionality reduction steps, but
-not all do, neither do all dimensionality reduction methods provide
-adequate graph embedding capacities.
+efficacy of t-SNE (Maaten, 2009). There are many dimensionality
+reductions (Anowar et al., 2021) that can be applied to an embedded
+network should the need for dimensionality reduction (for example for
+data visualisation) arise. In brief, many graph embeddings \emph{can}
+serve as dimensionality reduction steps, but not all do, neither do all
+dimensionality reduction methods provide adequate graph embedding
+capacities.
 
@@
 represents a space with 121 dimensions). All analyses were done using
-Julia (Bezanson et al., 2017) version 1.7.2, \emph{Makie.jl}
-(\textbf{Danisch2021MakJl?}), and \emph{EcologicalNetworks.jl} (Poisot
-et al., 2019).
+Julia (Bezanson et al., 2017) version 1.7.2, \emph{Makie.jl} (Danisch \&
+Krumbiegel, 2021), and \emph{EcologicalNetworks.jl} (Poisot et al.,
+2019).
 
@@
 actions (see \emph{e.g.} recent discussions for food-web based
-conservation; \textbf{Eero2021UseFoo?}; \textbf{NamanFooWeb?};
-\textbf{Stier2017IntExp?}), the need to appraise and correct biases that
-are unwittingly propagated to algorithms when embedded from the original
-data is paramount. Predictive approaches deployed at the continental
-scale, no matter their intent, originate in the framework that
-contributed to the ongoing biodiversity crisis (Adam, 2014) and
-reinforced environmental injustice (Choudry, 2013; Domínguez \& Luoma,
-2020). Particularly on Turtle Island and other territories that were
-traditionally stewarded by Indigenous people, these approaches should be
-replaced (or at least guided and framed) by Indigenous principles of
-land management (Eichhorn et al., 2019; No'kmaq et al., 2021), as part
-of an ``algorithm-in-the-loop'' approach. Human-algorithm interactions
-are notoriously difficult and can yield adverse effect
-(\textbf{Green2019DisInt?}; \textbf{Stevenson2021AlgRis?}), suggesting
-the need to systematically study them for the specific purpose of
-biodiversity governance, as well as to improve the algorithmic literacy
-of decision makers. As we see artificial intelligence/machine learning
-being increasingly mobilized to generate knowledge that is lacking for
-conservation decisions (\emph{e.g.} Lamba et al., 2019; Mosebo Fernandes
-et al., 2020) and drive policy decisions (Weiskopf et al., 2022), our
-discussion of these tools need to go beyond the technical and
-statistical, and into the governance consequences they can have.
+conservation; Eero et al., 2021; Naman et al., 2022; Stier et al.,
+2017), the need to appraise and correct biases that are unwittingly
+propagated to algorithms when embedded from the original data is
+paramount. Predictive approaches deployed at the continental scale, no
+matter their intent, originate in the framework that contributed to the
+ongoing biodiversity crisis (Adam, 2014) and reinforced environmental
+injustice (Choudry, 2013; Domínguez \& Luoma, 2020). Particularly on
+Turtle Island and other territories that were traditionally stewarded by
+Indigenous people, these approaches should be replaced (or at least
+guided and framed) by Indigenous principles of land management (Eichhorn
+et al., 2019; No'kmaq et al., 2021), as part of an
+``algorithm-in-the-loop'' approach. Human-algorithm interactions are
+notoriously difficult and can yield adverse effect (Green \& Chen, 2019;
+Stevenson \& Doleac, 2021), suggesting the need to systematically study
+them for the specific purpose of biodiversity governance, as well as to
+improve the algorithmic literacy of decision makers. As we see
+artificial intelligence/machine learning being increasingly mobilized to
+generate knowledge that is lacking for conservation decisions
+(\emph{e.g.} Lamba et al., 2019; Mosebo Fernandes et al., 2020) and
+drive policy decisions (Weiskopf et al., 2022), our discussion of these
+tools need to go beyond the technical and statistical, and into the
+governance consequences they can have.
 
@@
 
+\leavevmode\hypertarget{ref-Anowar2021ConEmp}{}%
+Anowar, F., Sadaoui, S., \& Selim, B. (2021). Conceptual and empirical
+comparison of dimensionality reduction algorithms (PCA, KPCA, LDA, MDS,
+SVD, LLE, ISOMAP, LE, ICA, t-SNE). \emph{Computer Science Review},
+\emph{40}, 100378. \url{https://doi.org/10.1016/j.cosrev.2021.100378}
+
 \leavevmode\hypertarget{ref-Arsov2019NetEmb}{}%
-Arsov, N., \& Mirceva, G. (2019, November 26). \emph{Network Embedding:
-An Overview}. \url{http://arxiv.org/abs/1911.11726}
+Arsov, N., \& Mirceva, G. (2019). \emph{Network Embedding: An Overview}.
+\url{http://arxiv.org/abs/1911.11726}
 
@@
 Ecology}, \emph{30}(12), 1894--1903.
+\url{http://onlinelibrary.wiley.com/doi/10.1111/1365-2435.12666/full}
 
@@
 65--98. \url{https://doi.org/10.1137/141000671}
+
+\leavevmode\hypertarget{ref-Bohan2017NexGlo}{}%
+Bohan, D. A., Vacher, C., Tamaddoni-Nezhad, A., Raybould, A., Dumbrell,
+A. J., \& Woodward, G. (2017). Next-Generation Global Biomonitoring:
+Large-scale, Automated Reconstruction of Ecological Networks.
+\emph{Trends in Ecology \& Evolution}.
+\url{https://doi.org/10.1016/j.tree.2017.03.001}
 
@@
 \emph{Deep Multi-species Embedding}. 3639--3646.
+\url{https://www.ijcai.org/proceedings/2017/509}
 
 \leavevmode\hypertarget{ref-Chen2017HarHie}{}%
-Chen, H., Perozzi, B., Hu, Y., \& Skiena, S. (2017, November 16).
-\emph{HARP: Hierarchical Representation Learning for Networks}.
+Chen, H., Perozzi, B., Hu, Y., \& Skiena, S. (2017). \emph{HARP:
+Hierarchical Representation Learning for Networks}.
 \url{http://arxiv.org/abs/1706.07845}
@@
 
+\leavevmode\hypertarget{ref-Danisch2021MakJl}{}%
+Danisch, S., \& Krumbiegel, J. (2021). Makie.jl: Flexible
+high-performance data visualization for Julia. \emph{Journal of Open
+Source Software}, \emph{6}(65), 3349.
+\url{https://doi.org/10.21105/joss.03349}
+
 \leavevmode\hypertarget{ref-Dominguez2020DecCon}{}%
@@
 dynamics} (pp. 27--86). Oxford University Press.
+
+\leavevmode\hypertarget{ref-Eero2021UseFoo}{}%
+Eero, M., Dierking, J., Humborg, C., Undeman, E., MacKenzie, B. R.,
+Ojaveer, H., Salo, T., \& Köster, F. W. (2021). Use of food web
+knowledge in environmental conservation and management of living
+resources in the Baltic Sea. \emph{ICES Journal of Marine Science},
+\emph{78}(8), 2645--2663. \url{https://doi.org/10.1093/icesjms/fsab145}
 
@@
 \emph{Science}.
+\url{https://www.science.org/doi/abs/10.1126/science.abk3510}
 
@@
 variation of network structure is scale dependent: Understanding the
-biotic specialization of hostparasitoid networks. \emph{Ecography},
+biotic specialization of host--parasitoid networks. \emph{Ecography},
 \emph{42}(6), 1175--1187. \url{https://doi.org/10.1111/ecog.03684}
@@
 
+\leavevmode\hypertarget{ref-Goodfellow2016DeeLea}{}%
+Goodfellow, I., Bengio, Y., \& Courville, A. (2016). \emph{Deep
+learning}. MIT Press.
+
 \leavevmode\hypertarget{ref-Goyal2018GraEmb}{}%
@@
 
+\leavevmode\hypertarget{ref-Green2019DisInt}{}%
+Green, B., \& Chen, Y. (2019). Disparate Interactions: An
+Algorithm-in-the-Loop Analysis of Fairness in Risk Assessments.
+\emph{Proceedings of the Conference on Fairness, Accountability, and
+Transparency}, 90--99. \url{https://doi.org/10.1145/3287560.3287563}
+
 \leavevmode\hypertarget{ref-Grover2016NodSca}{}%
@@
 
+\leavevmode\hypertarget{ref-Gupta2021GraNeu}{}%
+Gupta, A., Matta, P., \& Pant, B. (2021). Graph neural network: Current
+state of Art, challenges and applications. \emph{Materials Today:
+Proceedings}, \emph{46}, 10927--10932.
+\url{https://doi.org/10.1016/j.matpr.2021.01.950}
+
 \leavevmode\hypertarget{ref-Herbert1965Dun}{}%
@@
 
+\leavevmode\hypertarget{ref-Maaten2009LeaPar}{}%
+Maaten, L. van der. (2009). Learning a Parametric Embedding by
+Preserving Local Structure. \emph{Proceedings of the Twelth
+International Conference on Artificial Intelligence and Statistics},
+384--391. \url{https://proceedings.mlr.press/v5/maaten09a.html}
+
 \leavevmode\hypertarget{ref-Machen2021ThiAlg}{}%
@@
 Murphy, K. P. (2022). \emph{Probabilistic machine learning: An
-introduction}. MIT Press.
+introduction}. MIT Press. \href{https://probml.ai}{probml.ai}
+
+\leavevmode\hypertarget{ref-Naman2022FooWeb}{}%
+Naman, S. M., White, S. M., Bellmore, J. R., McHugh, P. A., Kaylor, M.
+J., Baxter, C. V., Danehy, R. J., Naiman, R. J., \& Puls, A. L. (2022).
+Food web perspectives and methods for riverine fish conservation.
+\emph{WIREs Water}, \emph{n/a}(n/a), e1590.
+\url{https://doi.org/10.1002/wat2.1590}
 
@@
 Narayanan, A., Chandramohan, M., Venkatesan, R., Chen, L., Liu, Y., \&
-Jaiswal, S. (2017, July 17). \emph{Graph2vec: Learning Distributed
+Jaiswal, S. (2017). \emph{Graph2vec: Learning Distributed
 Representations of Graphs}. \url{http://arxiv.org/abs/1707.05005}
@@
 O'Connor, L. M. J., Pollock, L. J., Braga, J., Ficetola, G. F.,
-Maiorano, L., Martinez-Almoyna, C., Montemaggiori, A., Ohlmann, M., \&
+Maiorano, L., Martinez‐Almoyna, C., Montemaggiori, A., Ohlmann, M., \&
 Thuiller, W. (2020). Unveiling the food webs of tetrapods across Europe
@@
 Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M. J., Becker, D.
-J., Albery, G. F., Gibb, R. J., Seifert, S. N., \& Carlson, C. J. (2021,
-May 31). \emph{Imputing the mammalian virome with linear filtering and
+J., Albery, G. F., Gibb, R. J., Seifert, S. N., \& Carlson, C. J.
+(2021). \emph{Imputing the mammalian virome with linear filtering and
 singular value decomposition}. \url{http://arxiv.org/abs/2105.14973}
@@
 systems} (Vol. 28). Curran Associates, Inc.
+\url{https://proceedings.neurips.cc/paper/2015/file/4f6ffe13a5d75b2d6a3923922b3922e5-Paper.pdf}
 
@@
 \emph{n/a}(n/a). \url{https://doi.org/10.1111/1365-2656.13652}
+
+\leavevmode\hypertarget{ref-Stevenson2021AlgRis}{}%
+Stevenson, M. T., \& Doleac, J. L. (2021). \emph{Algorithmic Risk
+Assessment in the Hands of Humans} {[}SSRN Scholarly Paper{]}.
+\url{https://doi.org/10.2139/ssrn.3489440}
+
+\leavevmode\hypertarget{ref-Stier2017IntExp}{}%
+Stier, A. C., Samhouri, J. F., Gray, S., Martone, R. G., Mach, M. E.,
+Halpern, B. S., Kappel, C. V., Scarborough, C., \& Levin, P. S. (2017).
+Integrating Expert Perceptions into Food Web Conservation and
+Management. \emph{Conservation Letters}, \emph{10}(1), 67--76.
+\url{https://doi.org/10.1111/conl.12245}
 
@@
 \leavevmode\hypertarget{ref-Xu2020UndGra}{}%
-Xu, M. (2020, December 14). \emph{Understanding graph embedding methods
-and their applications}. \url{http://arxiv.org/abs/2012.08019}
+Xu, M. (2020). \emph{Understanding graph embedding methods and their
+applications}. \url{http://arxiv.org/abs/2012.08019}
 
@@
 
+\leavevmode\hypertarget{ref-Zhou2020GraNeu}{}%
+Zhou, J., Cui, G., Hu, S., Zhang, Z., Yang, C., Liu, Z., Wang, L., Li,
+C., \& Sun, M. (2020). Graph neural networks: A review of methods and
+applications. \emph{AI Open}, \emph{1}, 57--81.
+\url{https://doi.org/10.1016/j.aiopen.2021.01.001}
+
 \end{CSLReferences}

### 2022-06-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@310f967569bdb5586a7ac6164381b396cdf9b018 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@efa3002ff699cea610b13aa6ab46808ff5d81068 🚀

@@
 \centering
-\includegraphics{figures/conceptual_embedding.png}
+\includegraphics{figures/conceptual_2.png}
 \caption{Overview of the embedding process. A network (\emph{A}),
@@
 in the data differently (\emph{D}), much like with a principal component
-analysis.}\label{fig:embedding}
+analysis. From a low-dimensional feature vector , it is possible to
+develop predictive approaches. Nodes in an ecological network are
+species, for which we can leverage phylogenetic relatedness (\emph{e.g.}
+Strydom, Bouskila, et al., 2021) or functional traits to fill the values
+of additional species we would like to project in this space (here, I,
+J, K, and L) from the embedding of known species (here, A, B, C, and D).
+Because embeddings can be projected back to a graph, this allows us to
+reconstruct a network with these new species. This approach constitutes
+an instance of transfer learning.}\label{fig:embedding}
 }
@@
 
-\begin{figure}
-\hypertarget{fig:prediction}{%
-\centering
-\includegraphics{figures/conceptual_prediction.png}
-\caption{From a low-dimensional feature vector (see
-fig.~\ref{fig:embedding}), it is possible to develop predictive
-approaches. Nodes in an ecological network are species, for which we can
-leverage phylogenetic relatedness (\emph{e.g.} Strydom, Bouskila, et
-al., 2021) or functional traits to fill the values of additional species
-we would like to project in this space (here, I, J, K, and L) from the
-embedding of known species (here, A, B, C, and D). Because embeddings
-can be projected back to a graph, this allows us to reconstruct a
-network with these new species. This approach constitutes an instance of
-transfer learning.}\label{fig:prediction}
-}
-\end{figure}
-
 \hypertarget{an-illustration-of-metaweb-embedding}{%
@@
 2019).
+
+fig.~\ref{fig:illustration}
+
+\begin{figure}
+\hypertarget{fig:illustration}{%
+\centering
+\includegraphics{figures/illustration.png}
+\caption{Need to add text here}\label{fig:illustration}
+}
+\end{figure}
 

### 2022-06-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@0f66ee4a6a10c3a41eedcd0cac4e2acbeb6aa798 🚀

@@
 master's scholarship. LP acknowledges funding from NSERC Discovery Grant
-(NSERC RGPIN-2019-05771). TP acknowledges financial support from NSERC
-through the Discovery Grants and Discovery Accelerator Supplement
-programs. MJF is supported by an NSERC PDF and an RBC Post-Doctoral
-Fellowship
+(NSERC RGPIN-2019-05771). TP acknowledges financial support from the
+Fondation Courtois, and NSERC through the Discovery Grants and Discovery
+Accelerator Supplement programs. MJF is supported by an NSERC PDF and an
+RBC Post-Doctoral Fellowship.
 

### 2022-06-19 code/demo.jl
new figs

@@ -25,7 +25,7 @@ L2 = [sum((adjacency(M) - prod(rdpg(M, r))) .^ 2) for r in rnk]
 # Plot layout
 fig = Figure(resolution=(800, 550))
 ax1 = Axis(fig[1, 1], xlabel="Rank", ylabel="L2 loss", title="A", titlealign=:left)
-ax2 = Axis(fig[1, 2], xlabel="Dimension 1 (left-subspace)", ylabel="Dimension 2 (left-subspace)", title="B", titlealign=:left)
+ax2 = Axis(fig[1, 2], xlabel="Dimension 1", ylabel="Dimension 2", title="B", titlealign=:left)
 ax3 = Axis(fig[2, 1], xlabel="Predicted weight", ylabel="Density", title="C", titlealign=:left)
 ax4 = Axis(fig[2, 2], xlabel="Dimension 1 (left-subspace)", ylabel="Number of hosts", title="D", titlealign=:left)
 fig

### 2022-06-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@0bc03c93ecf191a0dfc81ea9f4129b7b144260df 🚀

@@
 \caption{Overview of the embedding process. A network (\emph{A}),
-represented as its adjacency matrix (\emph{B}), is converted into a
-lower-dimensional object (\emph{C}) where nodes, subgraphs, or edges
-have specific values (see tbl.~\ref{tbl:methods}). For the purposes of
+represented here as its adjacency matrix, is converted into a
+lower-dimensional object (\emph{B}) where nodes, subgraphs, or edges
+have specific values (see tbl.~\ref{tbl:methods} for an overview of
+methods and their use for species interactions). For the purposes of
 prediction, this low-dimensional object encodes feature vectors for
 \emph{e.g.} the nodes. Embedding also allows to visualize the structure
-in the data differently (\emph{D}), much like with a principal component
-analysis. From a low-dimensional feature vector , it is possible to
-develop predictive approaches. Nodes in an ecological network are
-species, for which we can leverage phylogenetic relatedness (\emph{e.g.}
-Strydom, Bouskila, et al., 2021) or functional traits to fill the values
-of additional species we would like to project in this space (here, I,
-J, K, and L) from the embedding of known species (here, A, B, C, and D).
-Because embeddings can be projected back to a graph, this allows us to
-reconstruct a network with these new species. This approach constitutes
-an instance of transfer learning.}\label{fig:embedding}
+in the data differently (see fig.~\ref{fig:illustration}), much like
+with a principal component analysis. From a low-dimensional feature
+vector, it is possible to develop predictive approaches. Nodes in an
+ecological network are usually species (\textbf{C}), for which we can
+leverage phylogenetic relatedness (\emph{e.g.}
+\textbf{Strydom2022FooWeb?}) or functional traits to fill the values of
+additional species we would like to project in this space (here for
+nodes I, J, K, and L) from the embedding of known species (here, nodes
+A, B, C, and D). Because embeddings can be projected back to a graph,
+this allows us to reconstruct a network with these new species
+(\textbf{D}). This entire cycle constitutes an instance of transfer
+learning, where the transfered information is the representation of
+graph \textbf{A} through its embedding.}\label{fig:embedding}
 }
@@
 interactions were known, based on nodes metadata. This example has many
-parallels in ecology (see fig.~\ref{fig:prediction}), in which node
-metadata can be given by phylogeny or functional traits. Rather than
-directly predicting biological rules (see \emph{e.g.} Pichler et al.,
-2020 for an overview), which may be confounded by the sparse nature of
-graph data, learning embeddings works in the low-dimensional space that
-maximizes information about the network structure. This approach is
+parallels in ecology (see fig.~\ref{fig:embedding} \textbf{C}), in which
+node metadata can be given by phylogeny or functional traits. Rather
+than directly predicting biological rules (see \emph{e.g.} Pichler et
+al., 2020 for an overview), which may be confounded by the sparse nature
+of graph data, learning embeddings works in the low-dimensional space
+that maximizes information about the network structure. This approach is
 further justified by the observation, for example, that the
@@
 some graph embeddings (RDPG; see Dalla Riva \& Stouffer, 2016). In a
-recent publication, Strydom, Bouskila, et al. (2021) have used an
-embedding (based on RDPG) to project a metaweb of trophic interactions
-between European mammals, and transfered this information to mammals of
-Canada by using the phylogenetic distance between related clades to
-infer the values in the latent sub-space into which the metaweb was
-projected. By performing the RDPG step on re-constructed value, this
-approach yields a probabilistic trophic metaweb for mammals of Canada
-based on knowledge of European species, despite a limited (\(\approx\)
-5\%) taxonomic overlap.
+recent publication, (\textbf{Strydom2022FooWeb?}) have used an embedding
+(based on RDPG) to project a metaweb of trophic interactions between
+European mammals, and transfered this information to mammals of Canada
+by using the phylogenetic distance between related clades to infer the
+values in the latent sub-space into which the metaweb was projected. By
+performing the RDPG step on re-constructed value, this approach yields a
+probabilistic trophic metaweb for mammals of Canada based on knowledge
+of European species, despite a limited (\(\approx\) 5\%) taxonomic
+overlap.
 
 Graph embeddings \emph{can} serve as a dimensionality reduction method.
-For example, RDPG (Strydom, Bouskila, et al., 2021) and t-SVD (Poisot et
+For example, RDPG (\textbf{Strydom2022FooWeb?}) and t-SVD (Poisot et
 al., 2021) typically embed networks using fewer dimensions than the
@@
 dimensionality reduction methods provide adequate graph embedding
-capacities.
+capacities. In the next section (and fig.~\ref{fig:illustration}), we
+show how the amount of dimensionality reduction can affect the quality
+of the embedding.
 
@@
 In this section, we illustrate the embedding of a collection of
-bipartite networks collected by \textbf{REF}, using truncated Singular
-Value Decomposition (t-SVD). The code to reproduce this example (as a
-Jupyter notebook) is available as supplementary material. The resulting
-(binary) metaweb \(\mathcal{M}\) has 2131 interactions between 206
-parasites and 121 hosts (the same metaweb was used for the illustration
-of interaction inference through deep learning in Strydom, Catchen, et
-al., 2021), and its adjacency matrix has full rank (\emph{i.e.} it
-represents a space with 121 dimensions). All analyses were done using
-Julia (Bezanson et al., 2017) version 1.7.2, \emph{Makie.jl} (Danisch \&
-Krumbiegel, 2021), and \emph{EcologicalNetworks.jl} (Poisot et al.,
-2019).
-
-fig.~\ref{fig:illustration}
+bipartite networks collected by Hadfield et al. (2014), using truncated
+Singular Value Decomposition (t-SVD) and RDPG (see
+\textbf{Strydom2022FooWeb?} for the full details). Briefly, an RDPG
+decomposes a network into two subspaces (left and right), which are
+matrices that when multiplied give an approximation of the original
+network. The code to reproduce this example is available as
+supplementary material (note, for the sake of comparison, that Strydom,
+Catchen, et al., 2021 have an example using embedding through PCA
+followed by prediction using a deep neural network on the same dataset).
+The resulting (binary) metaweb \(\mathcal{M}\) has 2131 interactions
+between 206 parasites and 121 hosts, and its adjacency matrix has full
+rank (\emph{i.e.} it represents a space with 121 dimensions). All
+analyses were done using Julia (Bezanson et al., 2017) version 1.7.2,
+\emph{Makie.jl} (Danisch \& Krumbiegel, 2021), and
+\emph{EcologicalNetworks.jl} (Poisot et al., 2019).
 
@@
 \includegraphics{figures/illustration.png}
-\caption{Need to add text here}\label{fig:illustration}
+\caption{Illustration of an embedding for an host-parasite metaweb,
+using Random Dot Product Graphs. \textbf{A}, decrease in approximation
+error as the number of dimensions in the subspaces increases.
+\textbf{B}, position of hosts and parasites in the first two dimensions
+of their respective subspaces. \textbf{C}, predicted interaction weight
+from the RDPG based on the status of the species pair in the metaweb.
+\textbf{D}, relationship between the position on the first dimension and
+parasite generalism.}\label{fig:illustration}
 }
 \end{figure}
+
+The embedding of the metaweb holds several pieces of information
+(fig.~\ref{fig:illustration}). In panel \textbf{A}, we show that the
+\(L_2\) loss (\emph{i.e.} the sum of squared errors) between the
+empirical and reconstructed metaweb decreases when number of dimensions
+(rank) of the subspace increases, with a point of inflection around 25
+dimensions. As discussed by Runghen et al. (2021), there is often a
+trade-off between the number of dimensions to use (more dimensions are
+more computationally demanding) and the quality of the representation.
+In this instance, accepting \(L_2 = 500\) as an approximation of the
+network means that the error for every position in the metaweb is
+\(\approx \left(500/(206\times 121)\right)^{1/2}\). In \textbf{B}, we
+show the positions of hosts and parasites on the first two dimensions of
+the left and right subspaces. Note that these values largely skew
+negative, because the first dimensions capture the coarse structure of
+the network: most pairs of species do not interact, and therefore have
+negative values. In \textbf{C}, we show the predicted weight
+(\emph{i.e.} the result of the multiplication of the RDGP subspaces at a
+rank of 25) as a function of whether the interactions are observed,
+not-observed, or unknown due to lack of co-occurence. This reveals that
+the obserbed interactions have higher predicted weights, although there
+is some overlap; the usual approach to identify possible interactions
+based on this information would be a thresholding analysis, which is
+outside the scope of this manuscript (and is done in the papers cited in
+this illustration). Note that the values are not bound to the unit
+interval, which emphasizes the need for either scaling or clamping
+(although thresholding analyses are insensitive to this choice).
+Finally, in \textbf{D}, we show that the embedding, as it captures
+structural information about the network, holds ecological information;
+indeed, the position of the parasite on the first dimension of the left
+sub-space is a linear predictor of its number of hosts.
 
@@
 
+\leavevmode\hypertarget{ref-Hadfield2014TalTwo}{}%
+Hadfield, J. D., Krasnov, B. R., Poulin, R., \& Nakagawa, S. (2014). A
+Tale of Two Phylogenies: Comparative Analyses of Ecological
+Interactions. \emph{The American Naturalist}, \emph{183}(2), 174--187.
+\url{https://doi.org/10.1086/674445}
+
 \leavevmode\hypertarget{ref-Herbert1965Dun}{}%
@@
 \url{https://doi.org/10.1111/conl.12245}
-
-\leavevmode\hypertarget{ref-Strydom2021FooWeb}{}%
-Strydom, T., Bouskila, S., Banville, F., Barros, C., Caron, D., Farrell,
-M. J., Fortin, M.-J., Hemming, V., Mercier, B., Pollock, L., Runghen,
-R., Riva, G. V. D., \& Poisot, T. (2021). \emph{Food web reconstruction
-through phylogenetic transfer of low-rank network representation}.
-\url{https://doi.org/10.32942/osf.io/y7sdz}
 

### 2022-06-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@e08ecc2032f88252bc68360880c8d8160202cdba 🚀

@@
 \thispagestyle{empty}
-{\Large\bfseries\sffamily The prediction of species interaction networks
-is facilitated by graph embedding and transfer learning despite data
-limitations}
+{\Large\bfseries\sffamily Graph embedding and transfer learning can help
+predict species interaction networks despite data limitations}
 \vskip 5em

### 2022-06-19 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@e08ecc2032f88252bc68360880c8d8160202cdba 🚀

@@
 
-\noindent {\LARGE \textbf{\textsf{The prediction of species interaction
-networks is facilitated by graph embedding and transfer learning despite
-data limitations}}}
+\noindent {\LARGE \textbf{\textsf{Graph embedding and transfer learning
+can help predict species interaction networks despite data
+limitations}}}
 

### 2022-06-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@3b65ca139ef26a20c1cacfb5d00881f916148bae 🚀

@@
 ecological network are usually species (\textbf{C}), for which we can
-leverage phylogenetic relatedness (\emph{e.g.}
-\textbf{Strydom2022FooWeb?}) or functional traits to fill the values of
-additional species we would like to project in this space (here for
-nodes I, J, K, and L) from the embedding of known species (here, nodes
-A, B, C, and D). Because embeddings can be projected back to a graph,
-this allows us to reconstruct a network with these new species
-(\textbf{D}). This entire cycle constitutes an instance of transfer
-learning, where the transfered information is the representation of
-graph \textbf{A} through its embedding.}\label{fig:embedding}
+leverage phylogenetic relatedness (\emph{e.g.} Strydom et al., 2022) or
+functional traits to fill the values of additional species we would like
+to project in this space (here for nodes I, J, K, and L) from the
+embedding of known species (here, nodes A, B, C, and D). Because
+embeddings can be projected back to a graph, this allows us to
+reconstruct a network with these new species (\textbf{D}). This entire
+cycle constitutes an instance of transfer learning, where the transfered
+information is the representation of graph \textbf{A} through its
+embedding.}\label{fig:embedding}
 }
@@
 some graph embeddings (RDPG; see Dalla Riva \& Stouffer, 2016). In a
-recent publication, (\textbf{Strydom2022FooWeb?}) have used an embedding
-(based on RDPG) to project a metaweb of trophic interactions between
-European mammals, and transfered this information to mammals of Canada
-by using the phylogenetic distance between related clades to infer the
-values in the latent sub-space into which the metaweb was projected. By
-performing the RDPG step on re-constructed value, this approach yields a
+recent publication, Strydom et al. (2022) have used an embedding (based
+on RDPG) to project a metaweb of trophic interactions between European
+mammals, and transfered this information to mammals of Canada by using
+the phylogenetic distance between related clades to infer the values in
+the latent sub-space into which the metaweb was projected. By performing
+the RDPG step on re-constructed value, this approach yields a
 probabilistic trophic metaweb for mammals of Canada based on knowledge
@@
 Graph embeddings \emph{can} serve as a dimensionality reduction method.
-For example, RDPG (\textbf{Strydom2022FooWeb?}) and t-SVD (Poisot et
-al., 2021) typically embed networks using fewer dimensions than the
-original network (the original network has as many dimensions as
-species, and as many informative dimensions as trophically unique
-species; Strydom, Dalla Riva, et al., 2021). But this is not
-necessarilly the case -- indeed, one may perform a PCA (a special case
-of SVD) to project the raw data into a subspace that improves the
-efficacy of t-SNE (Maaten, 2009). There are many dimensionality
-reductions (Anowar et al., 2021) that can be applied to an embedded
-network should the need for dimensionality reduction (for example for
-data visualisation) arise. In brief, many graph embeddings \emph{can}
-serve as dimensionality reduction steps, but not all do, neither do all
-dimensionality reduction methods provide adequate graph embedding
-capacities. In the next section (and fig.~\ref{fig:illustration}), we
-show how the amount of dimensionality reduction can affect the quality
-of the embedding.
+For example, RDPG (Strydom et al., 2022) and t-SVD (Poisot et al., 2021)
+typically embed networks using fewer dimensions than the original
+network (the original network has as many dimensions as species, and as
+many informative dimensions as trophically unique species; Strydom,
+Dalla Riva, et al., 2021). But this is not necessarilly the case --
+indeed, one may perform a PCA (a special case of SVD) to project the raw
+data into a subspace that improves the efficacy of t-SNE (Maaten, 2009).
+There are many dimensionality reductions (Anowar et al., 2021) that can
+be applied to an embedded network should the need for dimensionality
+reduction (for example for data visualisation) arise. In brief, many
+graph embeddings \emph{can} serve as dimensionality reduction steps, but
+not all do, neither do all dimensionality reduction methods provide
+adequate graph embedding capacities. In the next section (and
+fig.~\ref{fig:illustration}), we show how the amount of dimensionality
+reduction can affect the quality of the embedding.
 
@@
 bipartite networks collected by Hadfield et al. (2014), using truncated
-Singular Value Decomposition (t-SVD) and RDPG (see
-\textbf{Strydom2022FooWeb?} for the full details). Briefly, an RDPG
-decomposes a network into two subspaces (left and right), which are
-matrices that when multiplied give an approximation of the original
-network. The code to reproduce this example is available as
-supplementary material (note, for the sake of comparison, that Strydom,
-Catchen, et al., 2021 have an example using embedding through PCA
-followed by prediction using a deep neural network on the same dataset).
-The resulting (binary) metaweb \(\mathcal{M}\) has 2131 interactions
-between 206 parasites and 121 hosts, and its adjacency matrix has full
-rank (\emph{i.e.} it represents a space with 121 dimensions). All
-analyses were done using Julia (Bezanson et al., 2017) version 1.7.2,
-\emph{Makie.jl} (Danisch \& Krumbiegel, 2021), and
+Singular Value Decomposition (t-SVD) and RDPG (see Strydom et al., 2022
+for the full details). Briefly, an RDPG decomposes a network into two
+subspaces (left and right), which are matrices that when multiplied give
+an approximation of the original network. The code to reproduce this
+example is available as supplementary material (note, for the sake of
+comparison, that Strydom, Catchen, et al., 2021 have an example using
+embedding through PCA followed by prediction using a deep neural network
+on the same dataset). The resulting (binary) metaweb \(\mathcal{M}\) has
+2131 interactions between 206 parasites and 121 hosts, and its adjacency
+matrix has full rank (\emph{i.e.} it represents a space with 121
+dimensions). All analyses were done using Julia (Bezanson et al., 2017)
+version 1.7.2, \emph{Makie.jl} (Danisch \& Krumbiegel, 2021), and
 \emph{EcologicalNetworks.jl} (Poisot et al., 2019).
@@
 
+\leavevmode\hypertarget{ref-Strydom2022FooWeb}{}%
+Strydom, T., Bouskila, S., Banville, F., Barros, C., Caron, D., Farrell,
+M. J., Fortin, M.-J., Hemming, V., Mercier, B., Pollock, L. J., Runghen,
+R., Dalla Riva, G. V., \& Poisot, T. (2022). Food web reconstruction
+through phylogenetic transfer of low-rank network representation.
+\emph{Methods in Ecology and Evolution}, \emph{n/a}(n/a).
+\url{https://doi.org/10.1111/2041-210X.13835}
+
 \leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%

### 2022-06-19 code/demo.jl
reproducible notebook

@@ -1,16 +1,28 @@
-# Graph embedding demo
+# # Demonstration of  graph embedding using RDPG
+
 using EcologicalNetworks
 using CairoMakie
 using LinearAlgebra
 
-# Load a series of bipartite networks
+# The first step is to load a series of bipartite quantitative networks between
+# hosts and parasites, coming from the Hadfield et al. paper on host-parasite
+# phylogenetic structure.
+
 ids = getfield.(filter(n -> contains("Hadfield")(n.Reference), web_of_life()), :ID)
+
+# We convert these networks to binary bipartite networks, in order to make the
+# metaweb aggregation easier.
+
 N = [convert(BipartiteNetwork, web_of_life(n)) for n in ids]
 
-# Get the metaweb
+# Transforming the array of networks into a metaweb is done through the union
+# operation:
+
 M = reduce(∪, N)
 
-# Co-occurrence matrix
+# In order to identify the pairs of species that have never been observed
+# together, we use the following loop to create a co-occurence matrix:
+
 C = zeros(Int64, size(M))
 for n in N
     i = indexin(species(n; dims=1), species(M; dims=1))
@@ -18,11 +30,9 @@ for n in N
     C[i, j] .+= 1
 end
 
-# Check the loss due to the embedding
-rnk = collect(1:121)
-L2 = [sum((adjacency(M) - prod(rdpg(M, r))) .^ 2) for r in rnk]
+# Before moving forward with the results, we will setup the multi-panel figure
+# used in main text:
 
-# Plot layout
 fig = Figure(resolution=(800, 550))
 ax1 = Axis(fig[1, 1], xlabel="Rank", ylabel="L2 loss", title="A", titlealign=:left)
 ax2 = Axis(fig[1, 2], xlabel="Dimension 1", ylabel="Dimension 2", title="B", titlealign=:left)
@@ -30,27 +40,86 @@ ax3 = Axis(fig[2, 1], xlabel="Predicted weight", ylabel="Density", title="C", ti
 ax4 = Axis(fig[2, 2], xlabel="Dimension 1 (left-subspace)", ylabel="Number of hosts", title="D", titlealign=:left)
 fig
 
-# Plot of rank vs. L2
-lines!(ax1, rnk, L2)
+# The first thing we want to do is measure the L2 loss (the sum of squared
+# errors) as a function of the rank.  The rank of the metaweb is at most the
+# number of species on its least species-rich side:
+
+rank(adjacency(M))
+
+# The following list comprehension will perform the RDPG embedding for each rank
[…]

### 2022-06-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@1d38a4d0137defc303e636439c8f51544298a89c 🚀

@@
 \begin{enumerate}
-    \item Metawebs, i.e.~networks of potential interactions within a
-species pool, are a powerful abstraction to understand how large-scales
-species interaction networks are structured.%
+    \item Metawebs, (networks of potential interactions within a species
+pool) are a powerful abstraction to understand how large-scale species
+interaction networks are structured.%
     \item Because metawebs are typically expressed at large spatial and
@@
 deficiencies, by providing `draft' metawebs.%
-    \item One way to improve the predictive ability is to maximize the
-information used for prediction, by using graph embeddings rather than
-the list of species interactions. Graph embedding is an emerging field
-in machine learning that holds great potential for ecological problems.%
+    \item One way to improve our ability to predict metawebs is to
+maximize available information by using graph embeddings, instead of the
+list of species interactions. Graph embedding is an emerging field in
+machine learning that holds great potential for ecological problems.%
     \item In this perspective, we outline how the challenges associated
 with inferring metawebs line-up with the advantages of graph embeddings;
-furthermore, because metawebs are inherently spatial objects, we discuss
-how the choice of the species pool has consequences on the reconstructed
-network, but also embeds hypotheses about which human-made boundaries
-are ecologically meaningful.%
+as well as discuss how the choice of the species pool has consequences
+on the reconstructed network, but also embeds hypotheses about which
+human-made boundaries are ecologically meaningful.%
 \end{enumerate}
@@
 
-Being able to infer \emph{potential} interactions could be the catalyst
-for significant breakthroughs in our ability to start thinking about
-species interaction networks over large spatial scales (Hortal et al.,
-2015). Understanding species interactions holds enormous potential to
-not only understand and more rapidly learn about species interactions
-and metawebs, but also how changes in management of a single species may
+Being able to infer \emph{potential} interactions could serve as a
+significant breakthrough in our ability to start thinking about species
+interaction networks over large spatial scales (Hortal et al., 2015).
+Understanding species interactions holds enormous potential to not only
+understand and more rapidly learn about species interactions and
+metawebs, but also how changes in management of a single species may
 impact non-target species. In a recent overview of the field of
@@
 required (and leaves us unable to make inference in regions without
-interaction data); second, accurate predictions often demand accurate
-predictors, and the lack of methods that can leverage small amount of
-\emph{accurate} data is a serious impediment to our global predictive
+interaction data); second, accurate predictors are important for
+accurate predictions, and the lack of methods that can leverage a small
+amount of \emph{accurate} data is a serious impediment to our predictive
 ability. In most places, our most reliable biodiversity knowledge is
@@
 diversity of interactions) are a subset of the metaweb's species and
-their interactions, and have been called ``metaweb realizations''
+realized interactions, and have been called ``metaweb realizations''
 (Poisot et al., 2015). Differences between local networks and their
@@
 among others. Yet, recent results by Saravia et al. (2021) strongly
-suggest that the local realizations only respond weakly to local
-conditions: instead, they reflect constraints inherited by the structure
-of their metaweb. This establishes the metaweb structure as the core
-goal of predictive network ecology, as it is a required information to
-accurately produce downscaled, local predictions.
+suggest that the local (metaweb) realizations only respond weakly to
+local conditions: instead, they reflect constraints inherited by the
+structure of their metaweb. This establishes the metaweb structure as
+the core goal of predictive network ecology, as it is a required
+information to accurately produce downscaled, local predictions.
 
@@
 phylogenetic, and macroecological processes (Morales-Castilla et al.,
-2015), it holds valuable ecological information. Specifically, it is the
-``upper bounds'' on what the composition of the local networks, given
-the local species pool, can be (see \emph{e.g.} McLeod et al., 2021);
-this information can help evaluate the ability of ecological assemblages
-to withstand the effects of, for example, climate change (Fricke et al.,
-2022). These local networks may be reconstructed given an appropriate
-knowledge of local species composition and provide information on the
-structure of food webs at finer spatial scales. This has been done for
-example for tree-galler-parasitoid systems (Gravel et al., 2018), fish
-trophic interactions (Albouy et al., 2019), tetrapod trophic
-interactions (Braga et al., 2019; O'Connor et al., 2020), and crop-pest
-networks (Grünig et al., 2020). In this contribution, we highlight the
-power in viewing (and constructing) metawebs as \emph{probabilistic}
-objects in the context of rare interactions, discuss how a family of
-machine learning tools (graph embeddings and transfer learning) can be
-used to overcome data limitations to metaweb inference, and highlight
-how the use of metawebs introduces important questions for the field of
-network ecology.
-
-\hypertarget{the-metaweb-is-an-inherently-probabilistic-object}{%
-\section{The metaweb is an inherently probabilistic
-object}\label{the-metaweb-is-an-inherently-probabilistic-object}}
+2015), it holds valuable ecological information. Specifically, it
+represents the ``upper bounds'' on what the composition of the local
+networks, given a local species pool, can be (see \emph{e.g.} McLeod et
+al., 2021); this information can help evaluate the ability of ecological
+assemblages to withstand the effects of, for example, climate change
+(Fricke et al., 2022). These local networks may be reconstructed given
+an appropriate knowledge of local species composition and provide
+information on the structure of food webs at finer spatial scales. This
+has been done for example for tree-galler-parasitoid systems (Gravel et
+al., 2018), fish trophic interactions (Albouy et al., 2019), tetrapod
+trophic interactions (Braga et al., 2019; O'Connor et al., 2020), and
+crop-pest networks (Grünig et al., 2020). In this contribution, we
+highlight the power in viewing (and constructing) metawebs as
+\emph{probabilistic} objects in the context of rare interactions,
+discuss how a family of machine learning tools (graph embeddings and
+transfer learning) can be used to overcome data limitations to metaweb
+inference, and highlight how the use of metawebs introduces important
+questions for the field of network ecology.
+
+\hypertarget{a-metaweb-is-an-inherently-probabilistic-object}{%
+\section{A metaweb is an inherently probabilistic
+object}\label{a-metaweb-is-an-inherently-probabilistic-object}}
 
@@
 observation of their interaction. In addition, it is generally expected
-that weak or rare links to be more prevalent in networks than common or
-rare links (Csermely, 2004), compared to strong, persistent links; this
-is notably the case in food chains, wherein many weaker links are key to
-the stability of a system (Neutel et al., 2002). In the light of these
-observations, we expect to see an over-representation of low-probability
-interactions under a model that accurately predicts interaction
-probabilities. Yet the original metaweb definition, and indeed most past
-uses of metawebs, was based on the presence/absence of interactions.
-Moving towards \emph{probabilistic} metawebs, by representing
-interactions as Bernoulli events (see \emph{e.g.} Poisot et al., 2016),
-offers the opportunity to weigh these rare interactions appropriately.
-The inherent plasticity of interactions is important to capture: there
-have been documented instances of food webs undergoing rapid
-collapse/recovery cycles over short periods of time (\emph{e.g.}
+weak or rare links to be more prevalent in networks than common or
+strong links (Csermely, 2004), compared to strong, persistent links;
+this is notably the case in food chains, wherein many weaker links are
+key to the stability of a system (Neutel et al., 2002). In the light of
+these observations, we expect to see an over-representation of
+low-probability (rare) interactions under a model that accurately
+predicts interaction probabilities. Yet the original metaweb definition,
+and indeed most past uses of metawebs, was based on the presence/absence
+of interactions. Moving towards \emph{probabilistic} metawebs, by
+representing interactions as Bernoulli events (see \emph{e.g.} Poisot et
+al., 2016), offers the opportunity to weigh these rare interactions
+appropriately. The inherent plasticity of interactions is important to
+capture: there have been documented instances of food webs undergoing
+rapid collapse/recovery cycles over short periods of time (\emph{e.g.}
 Pedersen et al., 2017). These considerations emphasize why metaweb
 predictions should focus on quantitative (preferentially probabilistic)
-predictions; this should constrain the suite of appropriate models.
-
-Yet it is important to recall that a metaweb is intended as a catalogue
-of all potential interactions, which is then filtered (Morales-Castilla
-et al., 2015). In a sense, that most ecological interactions are elusive
-can call for a slightly different approach to sampling: once the common
-interactions are documented, the effort required in documenting each
-rare interaction will increase exponentially. Recent proposals suggest
-that machine learning algorithms, in these situations, can act as data
-generators (Hoffmann et al., 2019): high quality observational data can
-generate the core rules underpinning the network structure, and be
-supplemented with synthetic data coming from predictive models,
-increasing the volume of information available for inference. Indeed,
-Strydom, Catchen, et al. (2021) suggested that knowing the metaweb may
-render the prediction of local networks easier, because it fixes an
-``upper bound'' on which interactions can exist. In this context a
-probabilistic metaweb represents an aggregation of informative priors on
-the interactions, elusive information with the potential to boost our
-predictive ability (Bartomeus et al., 2016).
+predictions, and this should constrain the suite of appropriate models
+used to predict them.
+
+It is important to recall that a metaweb is intended as a catalogue of
+all potential interactions, which is then filtered for a given
+application (Morales-Castilla et al., 2015). In a sense, that most
+ecological interactions are elusive can call for a slightly different
+approach to sampling: once the common interactions are documented, the
+effort required in documenting each rare interaction will increase
+exponentially. Recent proposals suggest that machine learning
+algorithms, in these situations, can act as data generators (Hoffmann et
+al., 2019): high quality observational data can generate the core rules
+underpinning the network structure, and be supplemented with synthetic
+data coming from predictive models, increasing the volume of information
+available for inference. Indeed, Strydom, Catchen, et al. (2021)
+suggested that knowing the metaweb may render the prediction of local
+networks easier, because it fixes an ``upper bound'' on which
+interactions can exist. In this context, a probabilistic metaweb
+represents an aggregation of informative priors on the interactions,
+elusive information with the potential to boost our predictive ability
+(Bartomeus et al., 2016).
 
@@
 \includegraphics{figures/conceptual_2.png}
-\caption{Overview of the embedding process. A network (\emph{A}),
+\caption{Overview of the embedding process. A network (\textbf{A}),
 represented here as its adjacency matrix, is converted into a
-lower-dimensional object (\emph{B}) where nodes, subgraphs, or edges
+lower-dimensional object (\textbf{B}) where nodes, subgraphs, or edges
 have specific values (see tbl.~\ref{tbl:methods} for an overview of
@@
 
-Graph embedding (fig.~\ref{fig:embedding}) is a varied family of machine
-learning techniques aiming to transform nodes and edges into a vector
-space (Arsov \& Mirceva, 2019), usually of a lower dimension, whilst
-maximally retaining key properties of the graph (Yan et al., 2005).
-Ecological networks are an interesting candidate for the widespread
-application of embeddings, as they tend to possess a shared structural
-backbone (Bramon Mora et al., 2018), which hints at structural
-invariants that can be revealed at lower dimensions. Indeed, food webs
-are inherently low-dimensional objects, and can be adequately
-represented with less than ten dimensions (Braga et al., 2019; Eklöf et
-al., 2013). Simulation results by Botella et al. (2022) suggest that
-there is no best method to identify architectural similarities between
-networks, and that multiple approaches need to be tested and compared to
-the network descriptor of interest. This matches previous, more general
-results on graph embedding, which suggest that the choice of embedding
-algorithm matters for the results (Goyal \& Ferrara, 2018). In
-tbl.~\ref{tbl:methods}, we present a selection of common graph embedding
-methods, alongside examples of their use to predict species
-interactions; most of these methods rely either on linear algebra, or on
-pseudo-random walks on graphs.
+Graph (or Network) embedding (fig.~\ref{fig:embedding}) is a family of
+machine learning techniques, whose main task is to learn a mapping
+function from a discrete graph to a continuous domain (Arsov \& Mirceva,
+2019; Chami et al., 2022). Their main goal is to learn a low dimensional
+vector representations for the nodes of the graph (embeddings), such
+that key properties of the graph (e.g.~local or global structures) are
+retained in the embedding space(Yan et al., 2005). Ecological networks
+are an interesting candidate for the widespread application of
+embeddings, as they tend to possess a shared structural backbone (Bramon
+Mora et al., 2018), which hints at structural invariants that can be
+revealed at lower dimensions. Indeed, food webs are inherently
+low-dimensional objects, and can be adequately represented with less
+than ten dimensions (Braga et al., 2019; Eklöf et al., 2013). Simulation
+results by Botella et al. (2022) suggest that there is no best method to
+identify architectural similarities between networks, and that multiple
+approaches need to be tested and compared to the network descriptor of
+interest. This matches previous, more general results on graph
+embedding, which suggest that the choice of embedding algorithm matters
+for the results (Goyal \& Ferrara, 2018). In tbl.~\ref{tbl:methods}, we
+present a selection of common graph and node embedding methods,
+alongside examples of their use to predict species interactions; most of
+these methods rely either on linear algebra, or on pseudo-random walks
+on graphs.
 
 One prominent family of approaches we do not discuss in the present
-manuscript is Graph Neural Networks (GNN; Zhou et al., 2020); GNN are,
+manuscript is Graph Neural Networks (GNN; Zhou et al., 2020). GNN are,
 in a sense, a method to embed a graph into a dense subspace, but belong
@@
 practices (see \emph{e.g.} Goodfellow et al., 2016). An important issue
-with methods based on deep learning is that because their parameter
+with methods based on deep learning is that, because their parameter
 space is immense, the sample size of the data fed into them must be
@@
 requirement for the model to converge correctly during training, but
-this assumption is unlikely to be met given the size of datasets about
-currently available metawebs (or single time/location species
+this assumption is unlikely to be met given the size of datasets
+currently available for metawebs (or single time/location species
 interaction networks). This data volume requirement is mostly absent
@@
 \hypertarget{tbl:methods}{}
-\begin{longtable}[]{@{}llrr@{}}
+\begin{longtable}[]{@{}lllll@{}}
 \caption{\label{tbl:methods}Overview of some common graph embedding
-approaches, by time of publication, alongside examples of their use in
-the prediction of species interactions. These methods have not yet been
-routinely used to predict species interactions; most examples that we
-identified were either statistical associations, or analogues to joint
-species distribution models. \(^a\): statistical interactions; \(^b\):
-joint-SDM-like approach.}\tabularnewline
+approaches, by type of embedded objects, alongside examples of their use
+in the prediction of species interactions. These methods have not yet
+been routinely used to predict species interactions; most examples that
+we identified were either statistical associations, or analogues to
+joint species distribution models. \(^a\): statistical interactions;
+\(^b\): joint-SDM-like approach. Note that the row for PCA also applies
+to kernel/probabilistic PCA, which are variations on the more general
+method of SVD. Note further that tSNE has been included because it is
+frequently used to embed graphs, including of species
+associations/interactions, despite not being strictly speaking, a graph
+embedding technique (see \emph{e.g.} Chami et al., 2022)}\tabularnewline
 \toprule
-\begin{minipage}[b]{0.11\columnwidth}\raggedright
+\begin{minipage}[b]{0.09\columnwidth}\raggedright
 Method\strut
-\end{minipage} & \begin{minipage}[b]{0.30\columnwidth}\raggedright
-Embedding approach\strut
-\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\raggedright
+Object\strut
+\end{minipage} & \begin{minipage}[b]{0.23\columnwidth}\raggedright
+Technique\strut
+\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
 Reference\strut
-\end{minipage} & \begin{minipage}[b]{0.32\columnwidth}\raggedleft
-Application in species interactions\strut
+\end{minipage} & \begin{minipage}[b]{0.29\columnwidth}\raggedright
+Application\strut
 \end{minipage}\tabularnewline
@@
 \toprule
-\begin{minipage}[b]{0.11\columnwidth}\raggedright
+\begin{minipage}[b]{0.09\columnwidth}\raggedright
 Method\strut
-\end{minipage} & \begin{minipage}[b]{0.30\columnwidth}\raggedright
-Embedding approach\strut
-\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\raggedright
+Object\strut
+\end{minipage} & \begin{minipage}[b]{0.23\columnwidth}\raggedright
+Technique\strut
+\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
 Reference\strut
-\end{minipage} & \begin{minipage}[b]{0.32\columnwidth}\raggedleft
-Application in species interactions\strut
+\end{minipage} & \begin{minipage}[b]{0.29\columnwidth}\raggedright
+Application\strut
 \end{minipage}\tabularnewline
@@
 \endhead
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
+\begin{minipage}[t]{0.09\columnwidth}\raggedright
 tSNE\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-nodes through statistical divergence\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
+nodes\strut
+\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
+statistical divergence\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
 Hinton \& Roweis (2002)\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
-Cieslak et al. (2020) \(^a\)\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+Gibb et al. (2021); Cieslak et al. (2020) \(^a\)\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.09\columnwidth}\raggedright
+LINE\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
+nodes\strut
+\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
+stochastic gradient descent\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+Tang et al. (2015)\strut
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.09\columnwidth}\raggedright
+SDNE\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
+nodes\strut
+\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
+gradient descent\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+D. Wang et al. (2016)\strut
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.09\columnwidth}\raggedright
+node2vec\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
+nodes\strut
+\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
+stochastic gradient descent\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+Grover \& Leskovec (2016)\strut
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.09\columnwidth}\raggedright
+HARP\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
+nodes\strut
+\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
+meta-strategy\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+H. Chen et al. (2017)\strut
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.09\columnwidth}\raggedright
+DMSE\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
+joint nodes\strut
+\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
+deep neural network\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+D. Chen et al. (2017)\strut
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+D. Chen et al. (2017) \(^b\)\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.09\columnwidth}\raggedright
+graph2vec\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
+sub-graph\strut
+\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
+skipgram network\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+Narayanan et al. (2017)\strut
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.09\columnwidth}\raggedright
 RDPG\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-graph through SVD\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
+graph\strut
+\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
+SVD\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
 Young \& Scheinerman (2007)\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
 Poisot et al. (2021); Dalla Riva \& Stouffer (2016)\strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
+\begin{minipage}[t]{0.09\columnwidth}\raggedright
+GLEE\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
+graph\strut
+\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
+Laplacian eigenmap\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+(\textbf{Torres2020GleGeo?})\strut
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.09\columnwidth}\raggedright
 DeepWalk\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-graph walk\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
+graph\strut
+\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
+stochastic gradient descent\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
 Perozzi et al. (2014)\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
 Wardeh et al. (2021)\strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
+\begin{minipage}[t]{0.09\columnwidth}\raggedright
+GraphKKE\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
+graph\strut
+\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
+stochastic differential equation\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+Melnyk et al. (2020)\strut
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+Melnyk et al. (2020) \(^a\)\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.09\columnwidth}\raggedright
 FastEmbed\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-graph through PCA/SVD analogue\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
+graph\strut
+\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
+eigen decomposition\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
 Ramasamy \& Madhow (2015)\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-LINE\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-nodes through statistical divergence\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
-Tang et al. (2015)\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-SDNE\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-nodes through auto-encoding\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
-D. Wang et al. (2016)\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-node2vec\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-nodes embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
-Grover \& Leskovec (2016)\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-graph2vec\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-sub-graph embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
-Narayanan et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-DMSE\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-joint nodes embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
-D. Chen et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
-D. Chen et al. (2017) \(^b\)\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-HARP\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-nodes through a meta-strategy\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
-H. Chen et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
-GraphKKE\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-graph embedding\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
-Melnyk et al. (2020)\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
-Melnyk et al. (2020) \(^a\)\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.11\columnwidth}\raggedright
+\begin{minipage}[t]{0.09\columnwidth}\raggedright
+PCA\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
+graph\strut
+\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
+eigen decomposition\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+(\textbf{S2013GraEmb?})\strut
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+Strydom, Catchen, et al. (2021)\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.09\columnwidth}\raggedright
 Joint methods\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
 multiple graphs\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
+multiple strategies\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
 S. Wang et al. (2021)\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedleft
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
 \strut
@@
 network to learn the embedding of a network in which not all
-interactions were known, based on nodes metadata. This example has many
-parallels in ecology (see fig.~\ref{fig:embedding} \textbf{C}), in which
-node metadata can be given by phylogeny or functional traits. Rather
-than directly predicting biological rules (see \emph{e.g.} Pichler et
-al., 2020 for an overview), which may be confounded by the sparse nature
-of graph data, learning embeddings works in the low-dimensional space
-that maximizes information about the network structure. This approach is
-further justified by the observation, for example, that the
-macro-evolutionary history of a network is adequately represented by
-some graph embeddings (RDPG; see Dalla Riva \& Stouffer, 2016). In a
-recent publication, Strydom et al. (2022) have used an embedding (based
-on RDPG) to project a metaweb of trophic interactions between European
-mammals, and transfered this information to mammals of Canada by using
-the phylogenetic distance between related clades to infer the values in
-the latent sub-space into which the metaweb was projected. By performing
-the RDPG step on re-constructed value, this approach yields a
-probabilistic trophic metaweb for mammals of Canada based on knowledge
-of European species, despite a limited (\(\approx\) 5\%) taxonomic
-overlap.
+interactions were known, based on the nodes' metadata. This example has
+many parallels in ecology (see fig.~\ref{fig:embedding} \textbf{C}), in
+which node metadata can be given by phylogeny or functional traits.
+Rather than directly predicting biological rules (see \emph{e.g.}
+Pichler et al., 2020 for an overview), which may be confounded by the
+sparse nature of graph data, learning embeddings works in the
+low-dimensional space that maximizes information about the network
+structure. This approach is further justified by the observation, for
+example, that the macro-evolutionary history of a network is adequately
+represented by some graph embeddings (Random dot product graphs (RDPG);
+see Dalla Riva \& Stouffer, 2016). In a recent publication, Strydom et
+al. (2022) have used an embedding (based on RDPG) to project a metaweb
+of trophic interactions between European mammals, and transferred this
+information to mammals of Canada, using the phylogenetic distance
+between related clades to infer the values in the latent sub-space into
+which the European metaweb was projected. By performing the RDPG step on
+re-constructed values, this approach yields a probabilistic trophic
+metaweb for mammals of Canada based on knowledge of European species,
+despite a limited (\(\approx\) 5\%) taxonomic overlap.
 
 Graph embeddings \emph{can} serve as a dimensionality reduction method.
-For example, RDPG (Strydom et al., 2022) and t-SVD (Poisot et al., 2021)
-typically embed networks using fewer dimensions than the original
-network (the original network has as many dimensions as species, and as
-many informative dimensions as trophically unique species; Strydom,
-Dalla Riva, et al., 2021). But this is not necessarilly the case --
-indeed, one may perform a PCA (a special case of SVD) to project the raw
-data into a subspace that improves the efficacy of t-SNE (Maaten, 2009).
-There are many dimensionality reductions (Anowar et al., 2021) that can
-be applied to an embedded network should the need for dimensionality
-reduction (for example for data visualisation) arise. In brief, many
-graph embeddings \emph{can} serve as dimensionality reduction steps, but
-not all do, neither do all dimensionality reduction methods provide
-adequate graph embedding capacities. In the next section (and
-fig.~\ref{fig:illustration}), we show how the amount of dimensionality
-reduction can affect the quality of the embedding.
+For example, RDPG (Strydom et al., 2022) and t-SVD (truncated Singular
+Value Decomposition; Poisot et al., 2021) typically embed networks using
+fewer dimensions than the original network (the original network has as
+many dimensions as species, and as many informative dimensions as
+trophically unique species; Strydom, Dalla Riva, et al., 2021). But this
+is not necessarily the case -- indeed, one may perform a PCA (a special
+case of SVD) to project the raw data into a subspace that improves the
+efficacy of t-SNE (t-distributed stochastic neighbor embedding; Maaten,
+2009). There are many dimensionality reductions (Anowar et al., 2021)
+that can be applied to an embedded network should the need for
+dimensionality reduction (for example for data visualisation) arise. In
+brief, many graph embeddings \emph{can} serve as dimensionality
+reduction steps, but not all do, neither do all dimensionality reduction
+methods provide adequate graph embedding capacities. In the next section
+(and fig.~\ref{fig:illustration}), we show how the amount of
+dimensionality reduction can affect the quality of the embedding.
 
@@
 In this section, we illustrate the embedding of a collection of
-bipartite networks collected by Hadfield et al. (2014), using truncated
-Singular Value Decomposition (t-SVD) and RDPG (see Strydom et al., 2022
-for the full details). Briefly, an RDPG decomposes a network into two
-subspaces (left and right), which are matrices that when multiplied give
-an approximation of the original network. The code to reproduce this
-example is available as supplementary material (note, for the sake of
-comparison, that Strydom, Catchen, et al., 2021 have an example using
-embedding through PCA followed by prediction using a deep neural network
-on the same dataset). The resulting (binary) metaweb \(\mathcal{M}\) has
-2131 interactions between 206 parasites and 121 hosts, and its adjacency
-matrix has full rank (\emph{i.e.} it represents a space with 121
-dimensions). All analyses were done using Julia (Bezanson et al., 2017)
-version 1.7.2, \emph{Makie.jl} (Danisch \& Krumbiegel, 2021), and
+bipartite networks collected by Hadfield et al. (2014), using t-SVD and
+RDPG (see Strydom et al., 2022 for the full details). Briefly, an RDPG
+decomposes a network into two subspaces (left and right), which are
+matrices that when multiplied give an approximation of the original
+network. The code to reproduce this example is available as
+supplementary material (note, for the sake of comparison, that Strydom,
+Catchen, et al., 2021 have an example using embedding through PCA
+followed by prediction using a deep neural network on the same dataset).
+The resulting (binary) metaweb \(\mathcal{M}\) has 2131 interactions
+between 206 parasites and 121 hosts, and its adjacency matrix has full
+rank (\emph{i.e.} it represents a space with 121 dimensions). All
+analyses were done using Julia (Bezanson et al., 2017) version 1.7.2,
+\emph{Makie.jl} (Danisch \& Krumbiegel, 2021), and
 \emph{EcologicalNetworks.jl} (Poisot et al., 2019).
@@
 \(L_2\) loss (\emph{i.e.} the sum of squared errors) between the
-empirical and reconstructed metaweb decreases when number of dimensions
-(rank) of the subspace increases, with a point of inflection around 25
-dimensions. As discussed by Runghen et al. (2021), there is often a
-trade-off between the number of dimensions to use (more dimensions are
-more computationally demanding) and the quality of the representation.
-In this instance, accepting \(L_2 = 500\) as an approximation of the
-network means that the error for every position in the metaweb is
-\(\approx \left(500/(206\times 121)\right)^{1/2}\). In \textbf{B}, we
-show the positions of hosts and parasites on the first two dimensions of
-the left and right subspaces. Note that these values largely skew
-negative, because the first dimensions capture the coarse structure of
-the network: most pairs of species do not interact, and therefore have
-negative values. In \textbf{C}, we show the predicted weight
-(\emph{i.e.} the result of the multiplication of the RDGP subspaces at a
-rank of 25) as a function of whether the interactions are observed,
-not-observed, or unknown due to lack of co-occurence. This reveals that
-the obserbed interactions have higher predicted weights, although there
-is some overlap; the usual approach to identify possible interactions
-based on this information would be a thresholding analysis, which is
-outside the scope of this manuscript (and is done in the papers cited in
-this illustration). Note that the values are not bound to the unit
-interval, which emphasizes the need for either scaling or clamping
+empirical and reconstructed metaweb decreases when the number of
+dimensions (rank) of the subspace increases, with an inflection point
+around 25 dimensions. As discussed by Runghen et al. (2021), there is
+often a trade-off between the number of dimensions to use (more
+dimensions are more computationally demanding) and the quality of the
+representation. In this instance, accepting \(L_2 = 500\) as an
+approximation of the network means that the error for every position in
+the metaweb is \(\approx \left(500/(206\times 121)\right)^{1/2}\). In
+fig.~\ref{fig:illustration}, panel \textbf{B}, we show the positions of
+hosts and parasites on the first two dimensions of the left and right
+subspaces. Note that these values largely skew negative, because the
+first dimensions capture the coarse structure of the network: most pairs
+of species do not interact, and therefore have negative values. In
+fig.~\ref{fig:illustration}, panel \textbf{C}, we show the predicted
+weight (\emph{i.e.} the result of the multiplication of the RDGP
+subspaces at a rank of 25) as a function of whether the interactions are
+observed, not-observed, or unknown due to lack of co-occurrence. This
+reveals that the observed interactions have higher predicted weights,
+although there is some overlap; the usual approach to identify potential
+interactions based on this information would be a thresholding analysis,
+which is outside the scope of this manuscript (and is done in the papers
+cited in this illustration). Note that the values are not bound to the
+unit interval, which emphasizes the need for either scaling or clamping
 (although thresholding analyses are insensitive to this choice).
-Finally, in \textbf{D}, we show that the embedding, as it captures
-structural information about the network, holds ecological information;
-indeed, the position of the parasite on the first dimension of the left
-sub-space is a linear predictor of its number of hosts.
+Finally, in fig.~\ref{fig:illustration}, panel \textbf{D}, we show that
+the embedding, as it captures structural information about the network,
+holds ecological information; indeed, the position of the parasite on
+the first dimension of the left sub-space is a linear predictor of its
+number of hosts.
 
@@
 that the representation of the original graph is difficult to transfer
-to the new problem. In addition, other problems can arise due to
-non-overlapping trait distributions in the known and unknown species.
-Alternatively a metaweb is too large (taxonomically), then the resulting
-embeddings would need to represent interactions between taxonomic groups
-that are not present in the new location. This would lead to a much
-higher variance in the starting dataset, and to under-dispersal in the
-target dataset, resulting in the potential under or over estimation of
-the strength of new predicted interactions. The lack of well documented
-metawebs is currently preventing the development of more concrete
-guidelines. The question of phylogenetic relatedness and dispersal is
-notably true if the metaweb is assembled in an area with mostly endemic
-species (\emph{e.g.} a system that has undergone recent radiation and
-might not have an analogous system with which to draw knowledge from),
-and as with every predictive algorithm, there is room for the
-application of our best ecological judgement. Because this problem
-relates to dispersal of species in the geographic or phylogenetic space,
-it can certainly be approached through assessing the performance of
-embedding transfer in simulated starting/target species pools.
+to the new problem. Alternatively, if the initial metaweb is too large
+(taxonomically), then the resulting embeddings would need to represent
+interactions between taxonomic groups that are not present in the new
+location. This would lead to a much higher variance in the starting
+dataset, and to under-dispersion in the target dataset, resulting in the
+potential under or over estimation of the strength of new predicted
+interactions. The lack of well documented metawebs is currently
+preventing the development of more concrete guidelines. The question of
+phylogenetic relatedness and distribution is notably relevant if the
+metaweb is assembled in an area with mostly endemic species (\emph{e.g.}
+a system that has undergone recent radiation or that has remained in
+isolation for a long period of time might not have an analogous system
+with which to draw knowledge from), and as with every predictive
+algorithm, there is room for the application of our best ecological
+judgement. Because this problem relates to distribution of species in
+the geographic or phylogenetic space, it can certainly be approached
+through assessing the performance of embedding transfer in simulated
+starting/target species pools.
 
@@
 approach is that information at the country level is likely to be
-required for biodiversity assessments, as countries set goals at the
-national level (Buxton et al., 2021), and as quantitative instruments
-are designed to work at these scales (Turak et al., 2017); specific
-strategies are often enacted at smaller scales, nested within a specific
-country (Ray et al., 2021). But there is no guarantee that these
-boundaries are meaningful. In fact, we do not have a satisfying answer
-to the question of ``where does a food web stop?''; the most promising
-solutions involve examining the spatial consistency of network area
-relationships (Fortin et al., 2021; see \emph{e.g.} Galiana et al.,
+required for biodiversity assessments, as countries set conservation
+goals at the national level (Buxton et al., 2021), and as quantitative
+instruments are designed to work at these scales (Turak et al., 2017);
+specific strategies are often enacted at smaller scales, nested within a
+specific country (Ray et al., 2021). But there is no guarantee that
+these boundaries are meaningful. In fact, we do not have a satisfying
+answer to the question of ``where does a food web stop?''; the most
+promising solutions involve examining the spatial consistency of network
+area relationships (Fortin et al., 2021; see \emph{e.g.} Galiana et al.,
 2018, 2019, 2021), which is impossible in the absence of enough
@@
 not debias them, but instead embeds these very same biases, propagating
-them to the machine learning models using embeddings tomake predictions.
-Indeed, the use of ecological data is not an apolitical act (Nost \&
-Goldstein, 2021), as data infrastructures tend to be designed to answer
-questions within national boundaries (therefore placing contingencies on
-what is available to be embedded), and their use often draws upon and
-reinforces territorial statecraft. As per Machen \& Nost (2021), this is
-particularly true when the output of ``algorithmic thinking''
-(\emph{e.g.} relying on machine learning to generate knowledge) can be
-re-used for governance (\emph{e.g.} enacting conservation decisions at
-the national scale). As information on species interaction networks
-structure is increasingly leveraged as a tool to guide conservation
-actions (see \emph{e.g.} recent discussions for food-web based
-conservation; Eero et al., 2021; Naman et al., 2022; Stier et al.,
-2017), the need to appraise and correct biases that are unwittingly
-propagated to algorithms when embedded from the original data is
-paramount. Predictive approaches deployed at the continental scale, no
-matter their intent, originate in the framework that contributed to the
-ongoing biodiversity crisis (Adam, 2014) and reinforced environmental
-injustice (Choudry, 2013; Domínguez \& Luoma, 2020). Particularly on
-Turtle Island and other territories that were traditionally stewarded by
-Indigenous people, these approaches should be replaced (or at least
-guided and framed) by Indigenous principles of land management (Eichhorn
-et al., 2019; No'kmaq et al., 2021), as part of an
-``algorithm-in-the-loop'' approach. Human-algorithm interactions are
-notoriously difficult and can yield adverse effect (Green \& Chen, 2019;
-Stevenson \& Doleac, 2021), suggesting the need to systematically study
-them for the specific purpose of biodiversity governance, as well as to
-improve the algorithmic literacy of decision makers. As we see
+them to the machine learning models using embeddings to make
+predictions. Indeed, the use of ecological data is not an apolitical act
+(Nost \& Goldstein, 2021), as data infrastructures tend to be designed
+to answer questions within national boundaries (therefore placing
+contingencies on what is available to be embedded), and their use often
+draws upon and reinforces territorial statecraft. As per Machen \& Nost
+(2021), this is particularly true when the output of ``algorithmic
+thinking'' (\emph{e.g.} relying on machine learning to generate
+knowledge) can be re-used for governance (\emph{e.g.} enacting
+conservation decisions at the national scale). As information on species
+interaction networks structure is increasingly leveraged as a tool to
+guide conservation actions (see \emph{e.g.} recent discussions for
+food-web based conservation; Eero et al., 2021; Naman et al., 2022;
+Stier et al., 2017), the need to appraise and correct biases that are
+unwittingly propagated to algorithms when embedded from the original
+data is paramount. Predictive approaches deployed at the continental
+scale, no matter their intent, originate in the framework that
+contributed to the ongoing biodiversity crisis (Adam, 2014) and
+reinforced environmental injustice (Choudry, 2013; Domínguez \& Luoma,
+2020). Particularly on Turtle Island and other territories that were
+traditionally stewarded by Indigenous people, these approaches should be
+replaced (or at least guided and framed) by Indigenous principles of
+land management (Eichhorn et al., 2019; No'kmaq et al., 2021), as part
+of an ``algorithm-in-the-loop'' approach. Human-algorithm interactions
+are notoriously difficult and can yield adverse effect (Green \& Chen,
+2019; Stevenson \& Doleac, 2021), suggesting the need to systematically
+study them for the specific purpose of biodiversity governance, as well
+as to improve the algorithmic literacy of decision makers. As we see
 artificial intelligence/machine learning being increasingly mobilized to
@@
 
+\leavevmode\hypertarget{ref-Chami2022MacLea}{}%
+Chami, I., Abu-El-Haija, S., Perozzi, B., Ré, C., \& Murphy, K. (2022).
+Machine Learning on Graphs: A Model and Comprehensive Taxonomy.
+\emph{Journal of Machine Learning Research}, \emph{23}(89), 1--64.
+\url{http://jmlr.org/papers/v23/20-852.html}
+
 \leavevmode\hypertarget{ref-Chen2017DeeMul}{}%
@@
 \emph{2}(5), 782--790. \url{https://doi.org/10.1038/s41559-018-0517-3}
+
+\leavevmode\hypertarget{ref-Gibb2021DatPro}{}%
+Gibb, R., Albery, G. F., Becker, D. J., Brierley, L., Connor, R.,
+Dallas, T. A., Eskew, E. A., Farrell, M. J., Rasmussen, A. L., Ryan, S.
+J., Sweeny, A., Carlson, C. J., \& Poisot, T. (2021). Data
+Proliferation, Reconciliation, and Synthesis in Viral Ecology.
+\emph{BioScience}, \emph{71}(11), 1148--1156.
+\url{https://doi.org/10.1093/biosci/biab080}
 

### 2022-06-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@fe5dd17f2ca4d62088143ccf25a9c06eb0123d28 🚀

@@
 that key properties of the graph (e.g.~local or global structures) are
-retained in the embedding space(Yan et al., 2005). Ecological networks
+retained in the embedding space (Yan et al., 2005). Ecological networks
 are an interesting candidate for the widespread application of

### 2022-06-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@d4a5cee100420e126780c4c1afe18f7b5484f993 🚀

@@
 \end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-(\textbf{Torres2020GleGeo?})\strut
+Torres et al. (2020)\strut
 \end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
@@
 \end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-(\textbf{S2013GraEmb?})\strut
+S \& Surendran (2013)\strut
 \end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
@@
 
+\leavevmode\hypertarget{ref-S2013GraEmb}{}%
+S, N. S., \& Surendran, S. (2013). Graph Embedding and Dimensionality
+Reduction - A Survey. \emph{International Journal of Computer Science \&
+Engineering Technology}, \emph{4}(1).
+\url{https://www.semanticscholar.org/paper/Graph-Embedding-and-Dimensionality-Reduction-A-Surendran/3f413d591e4b2b876e033eeb9390e232ad4826ca}
+
 \leavevmode\hypertarget{ref-Saravia2021EcoNet}{}%
@@
 Stevenson, M. T., \& Doleac, J. L. (2021). \emph{Algorithmic Risk
-Assessment in the Hands of Humans} {[}SSRN Scholarly Paper{]}.
+Assessment in the Hands of Humans} (SSRN Scholarly Paper No. 3489440).
 \url{https://doi.org/10.2139/ssrn.3489440}
@@
 \url{https://doi.org/10.1145/2736277.2741093}
+
+\leavevmode\hypertarget{ref-Torres2020GleGeo}{}%
+Torres, L., Chan, K. S., \& Eliassi-Rad, T. (2020). GLEE: Geometric
+Laplacian Eigenmap Embedding. \emph{Journal of Complex Networks},
+\emph{8}(2), cnaa007. \url{https://doi.org/10.1093/comnet/cnaa007}
 

### 2022-09-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@16217d2fa569fdf41fb11fee129c94289230ab70 🚀

@@
 effort required in documenting each rare interaction will increase
-exponentially. Recent proposals suggest that machine learning
-algorithms, in these situations, can act as data generators (Hoffmann et
-al., 2019): high quality observational data can generate the core rules
-underpinning the network structure, and be supplemented with synthetic
-data coming from predictive models, increasing the volume of information
-available for inference. Indeed, Strydom, Catchen, et al. (2021)
-suggested that knowing the metaweb may render the prediction of local
-networks easier, because it fixes an ``upper bound'' on which
+exponentially. Recent proposals suggest that machine learning algorithms
+can also act as data generators (Hoffmann et al., 2019): high quality
+observational data can be used to infer core rules underpinning network
+structure, and be supplemented with synthetic data coming from
+predictive models trained on them, thereby increasing the volume of
+information available for analysis. Indeed, Strydom, Catchen, et al.
+(2021) suggested that knowing the metaweb may render the prediction of
+local networks easier, because it fixes an ``upper bound'' on which
 interactions can exist. In this context, a probabilistic metaweb

### 2022-09-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@f6666497809251353fa4cf0043de56f532cc817b 🚀

@@
 are an interesting candidate for the widespread application of
-embeddings, as they tend to possess a shared structural backbone (Bramon
-Mora et al., 2018), which hints at structural invariants that can be
-revealed at lower dimensions. Indeed, food webs are inherently
-low-dimensional objects, and can be adequately represented with less
-than ten dimensions (Braga et al., 2019; Eklöf et al., 2013). Simulation
-results by Botella et al. (2022) suggest that there is no best method to
-identify architectural similarities between networks, and that multiple
-approaches need to be tested and compared to the network descriptor of
-interest. This matches previous, more general results on graph
-embedding, which suggest that the choice of embedding algorithm matters
-for the results (Goyal \& Ferrara, 2018). In tbl.~\ref{tbl:methods}, we
-present a selection of common graph and node embedding methods,
-alongside examples of their use to predict species interactions; most of
-these methods rely either on linear algebra, or on pseudo-random walks
-on graphs.
+embeddings, as they tend to possess a shared structural backbone (see
+\emph{e.g.} Bramon Mora et al., 2018 for food webs), which hints at
+structural invariants in empirical data; assuming that these structural
+invariants are indeed widespread, they would dominate the structure of
+networks, and therefore be adequately captured by the first (lower)
+dimensions of an embedding, without the need to measure derived aspects
+of their structure (\emph{e.g.} motifs, paths, modularity, \ldots).
+
+Indeed, food webs are inherently low-dimensional objects, and can be
+adequately represented with less than ten dimensions (Braga et al.,
+2019; Eklöf et al., 2013). Simulation results by Botella et al. (2022)
+suggest that there is no best method to identify architectural
+similarities between networks, and that multiple approaches need to be
+tested and compared to the network descriptor of interest. This matches
+previous, more general results on graph embedding, which suggest that
+different embedding algorithms yield different network embeddings (Goyal
+\& Ferrara, 2018), calling for a careful selection of the
+problem-specific approach to use. In tbl.~\ref{tbl:methods}, we present
+a selection of common graph and node embedding methods, alongside
+examples of their use to predict species interactions; most of these
+methods rely either on linear algebra, or on pseudo-random walks on
+graphs.
 

### 2022-09-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@5dd3632ebad73129d6d692b071900fe366ba949e 🚀

@@
 joint species distribution models. \(^a\): statistical interactions;
-\(^b\): joint-SDM-like approach. Note that the row for PCA also applies
-to kernel/probabilistic PCA, which are variations on the more general
+\(^b\): joint-SDM-like approach. Given the need to evaluate different
+methods on a problem-specific basis, the fact that a lot of methods have
+not been used on network problems is an opportunity for benchmarking and
+method development. Note that the row for PCA also applies to
+kernel/probabilistic PCA, which are variations on the more general
 method of SVD. Note further that tSNE has been included because it is
@@
 many parallels in ecology (see fig.~\ref{fig:embedding} \textbf{C}), in
-which node metadata can be given by phylogeny or functional traits.
+which node metadata can be represented by phylogeny, abundance, or
+functional traits. Using phylogeny as a source of information assumes
+(or strives to capture) the action of evolutionary processes on network
+structure, which at least for food webs have been well documented
+\textbf{TK REF}; similarly, the use of functional traits assumes that
+interactions can be infered from the knowledge of trait-matching rules,
+which is similarly well supported in the empirical literature \textbf{TK
+REF}. Relating this information to an embedding rather than a list of
+networks measures would allow to capture their effect on the more
+fundamental aspects of network structure; conversely, the absence of a
+phylogenetic or functional signal may suggest that evolutionary/trait
+processes are not strong drivers of network structure, therefore opening
+a new way to perform hypothesis testing.
+
 Rather than directly predicting biological rules (see \emph{e.g.}

### 2022-09-28 code/demo.jl
📈 update on fig2/3

@@ -158,7 +158,7 @@ size(L)
 # dimension). We will approximate the network at the previously identified rank,
 # and call it P:
 
-P = L * R
+P = clamp.(L * R, 0., 1.)
 
 # With this matrix, we can start looking at the weight given for (i) positive
 # interactions, (ii) interactions that are never observed but for which the
@@ -207,16 +207,24 @@ figure2a = Axis(
 )
 figure2b = Axis(
     figure2[1, 2];
-    xlabel = "Dimension 1 (right-subspace)",
-    ylabel = "Body mass (grams)",
-    yscale = log10,
+    ylabel = "Dimension 1 (right-subspace)",
+    xlabel = "Body mass (grams)",
+    xscale = log10,
     title = "B",
     titlealign = :left,
 )
 figure2c = Axis(
-    figure2[2, 1:2];
-    ylabel = "Dimension 1 (right-subspace)",
+    figure2[1, 3];
+    ylabel = "Number of parasites",
+    xlabel = "Body mass (grams)",
+    xscale = log10,
     title = "C",
+    titlealign = :left,
+)
+figure2d = Axis(
+    figure2[2, 1:3];
+    ylabel = "Dimension 1 (right-subspace)",
+    title = "D",
     titlealign = :left,
     xticklabelrotation = π / 4,
 )
@@ -241,12 +249,14 @@ vidx = filter(!isnothing, indexin(species(M; dims = 2), pantheria.MSW05_Binomial
 rodents = pantheria[vidx, :]
 species_index = indexin(rodents.MSW05_Binomial, species(M; dims = 2))
 rodents.dim1 = R[1, species_index]
+rodents.prich = [degree(M)[k] for k in rodents.MSW05_Binomial]
 
 @select!(
     rodents,
     :species = :MSW05_Binomial,
     :family = :MSW05_Family,
     :dimension = :dim1,
+    :parasites = :prich,
     :bodymass = $(Symbol("5-1_AdultBodyMass_g"))
 )
 
@@ -256,7 +266,7 @@ rodents = @orderby(rodents, :family)
 # do not appear on the boxplots):
 
 rainclouds!(
-    figure2c,
+    figure2d,
     rodents.family,
     rodents.dimension;
     plot_boxplots = true,
@@ -281,8 +291,18 @@ current_figure()
 
 scatter!(
     figure2b,
-    rodents.dimension,
-    rodents.bodymass;
+    rodents.bodymass,
[…]

### 2022-09-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@133195b5572b35c48fcc87e35a1dd3894494a8ec 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@0c903b9b810520a82beb4ec474a4befef4adb03f 🚀

@@
 low-probability (rare) interactions under a model that accurately
-predicts interaction probabilities. Yet the original metaweb definition,
-and indeed most past uses of metawebs, was based on the presence/absence
-of interactions. Moving towards \emph{probabilistic} metawebs, by
-representing interactions as Bernoulli events (see \emph{e.g.} Poisot et
-al., 2016), offers the opportunity to weigh these rare interactions
-appropriately. The inherent plasticity of interactions is important to
-capture: there have been documented instances of food webs undergoing
-rapid collapse/recovery cycles over short periods of time (\emph{e.g.}
-Pedersen et al., 2017). These considerations emphasize why metaweb
-predictions should focus on quantitative (preferentially probabilistic)
-predictions, and this should constrain the suite of appropriate models
-used to predict them.
+predicts interaction probabilities.
+
+Yet the original metaweb definition, and indeed most past uses of
+metawebs, was based on the presence/absence of interactions. Moving
+towards \emph{probabilistic} metawebs, by representing interactions as
+Bernoulli events (see \emph{e.g.} Poisot et al., 2016), offers the
+opportunity to weigh these rare interactions appropriately. The inherent
+plasticity of interactions is important to capture: there have been
+documented instances of food webs undergoing rapid collapse/recovery
+cycles over short periods of time (\emph{e.g.} Pedersen et al., 2017).
+Furthermore, because the structure of the metaweb cannot be known in
+advance, it is important to rely on predictive tools that do not assume
+a specific network topology for link prediction (Gaucher et al., 2021),
+but are able to work on generalizations of the network. These
+considerations emphasize why metaweb predictions should focus on
+quantitative (preferentially probabilistic) predictions, and this should
+constrain the suite of appropriate models used to predict them.
 
 It is important to recall that a metaweb is intended as a catalogue of
-all potential interactions, which is then filtered for a given
-application (Morales-Castilla et al., 2015). In a sense, that most
-ecological interactions are elusive can call for a slightly different
-approach to sampling: once the common interactions are documented, the
-effort required in documenting each rare interaction will increase
-exponentially. Recent proposals suggest that machine learning algorithms
-can also act as data generators (Hoffmann et al., 2019): high quality
-observational data can be used to infer core rules underpinning network
-structure, and be supplemented with synthetic data coming from
-predictive models trained on them, thereby increasing the volume of
-information available for analysis. Indeed, Strydom, Catchen, et al.
-(2021) suggested that knowing the metaweb may render the prediction of
-local networks easier, because it fixes an ``upper bound'' on which
-interactions can exist. In this context, a probabilistic metaweb
-represents an aggregation of informative priors on the interactions,
-elusive information with the potential to boost our predictive ability
+all potential (feasible) interactions, which is then filtered for a
+given application (Morales-Castilla et al., 2015). It is therefore
+important to separate the interactions that happen ``almost surely''
+(repeated observational data), ``almost never'' (repeated lack of
+evidence \emph{or} evidence that the link is forbidden through
+\emph{e.g.} trait mis-match), and interactions with a probability that
+lays somewhere in between. In a sense, that most ecological interactions
+are elusive can call for a slightly different approach to sampling: once
+the common interactions are documented, the effort required in
+documenting each rare interaction will increase exponentially (Jordano,
+2016). Recent proposals in other fields emphasize the idea that machine
+learning algorithms can also act as data generators (Hoffmann et al.,
+2019): high quality observational data can be used to infer core rules
+underpinning network structure, and be supplemented with synthetic data
+coming from predictive models trained on them, thereby increasing the
+volume of information available for analysis. Indeed, Strydom, Catchen,
+et al. (2021) suggested that knowing the metaweb may render the
+prediction of local networks easier, because it fixes an ``upper bound''
+on which interactions can exist. In this context, a probabilistic
+metaweb represents an aggregation of informative priors on the
+biological feasibility of interactions, which is usually hard to obtain
+yet has possibly the most potential to boost our predictive ability
 (Bartomeus et al., 2016).
@@
 \begin{figure}
-\hypertarget{fig:illustration}{%
+\hypertarget{fig:illustration1}{%
 \centering
-\includegraphics{figures/illustration.png}
-\caption{Illustration of an embedding for an host-parasite metaweb,
-using Random Dot Product Graphs. \textbf{A}, decrease in approximation
-error as the number of dimensions in the subspaces increases.
-\textbf{B}, position of hosts and parasites in the first two dimensions
-of their respective subspaces. \textbf{C}, predicted interaction weight
-from the RDPG based on the status of the species pair in the metaweb.
-\textbf{D}, relationship between the position on the first dimension and
-parasite generalism.}\label{fig:illustration}
+\includegraphics{figures/illustration-part1.png}
+\caption{Validation of an embedding for a host-parasite metaweb, using
+Random Dot Product Graphs. \textbf{A}, decrease in approximation error
+as the number of dimensions in the subspaces increases. \textbf{B},
+increase in cumulative variance explained as the number of ranks
+considered increases; in \textbf{A} and \textbf{B}, the dot represents
+the point of inflexion in the curve (at rank 39) estimated using the
+finite differences method. \textbf{C}, position of hosts and parasites
+in the space of latent variables on the first and second dimensions of
+their respective subspaces (the results have been clamped to the unit
+interval). \textbf{D}, predicted interaction weight from the RDPG based
+on the status of the species pair in the
+metaweb.}\label{fig:illustration1}
 }
@@
 
-The embedding of the metaweb holds several pieces of information
-(fig.~\ref{fig:illustration}). In panel \textbf{A}, we show that the
-\(L_2\) loss (\emph{i.e.} the sum of squared errors) between the
-empirical and reconstructed metaweb decreases when the number of
-dimensions (rank) of the subspace increases, with an inflection point
-around 25 dimensions. As discussed by Runghen et al. (2021), there is
-often a trade-off between the number of dimensions to use (more
-dimensions are more computationally demanding) and the quality of the
-representation. In this instance, accepting \(L_2 = 500\) as an
-approximation of the network means that the error for every position in
-the metaweb is \(\approx \left(500/(206\times 121)\right)^{1/2}\). In
-fig.~\ref{fig:illustration}, panel \textbf{B}, we show the positions of
-hosts and parasites on the first two dimensions of the left and right
-subspaces. Note that these values largely skew negative, because the
-first dimensions capture the coarse structure of the network: most pairs
-of species do not interact, and therefore have negative values. In
-fig.~\ref{fig:illustration}, panel \textbf{C}, we show the predicted
-weight (\emph{i.e.} the result of the multiplication of the RDGP
-subspaces at a rank of 25) as a function of whether the interactions are
-observed, not-observed, or unknown due to lack of co-occurrence. This
-reveals that the observed interactions have higher predicted weights,
-although there is some overlap; the usual approach to identify potential
-interactions based on this information would be a thresholding analysis,
-which is outside the scope of this manuscript (and is done in the papers
-cited in this illustration). Note that the values are not bound to the
-unit interval, which emphasizes the need for either scaling or clamping
-(although thresholding analyses are insensitive to this choice).
-Finally, in fig.~\ref{fig:illustration}, panel \textbf{D}, we show that
-the embedding, as it captures structural information about the network,
-holds ecological information; indeed, the position of the parasite on
-the first dimension of the left sub-space is a linear predictor of its
-number of hosts.
+In fig.~\ref{fig:illustration1}, we focus on some statistical checks of
+the embedding. In panel \textbf{A}, we show that the averaged \(L_2\)
+loss (\emph{i.e.} the sum of squared errors) between the empirical and
+reconstructed metaweb decreases when the number of dimensions (rank) of
+the subspace increases, with an inflection at 39 dimensions (out of 120
+initially) according to the finite differences method. As discussed by
+Runghen et al. (2021), there is often a trade-off between the number of
+dimensions to use (more dimensions are more computationally demanding)
+and the quality of the representation. In panel \textbf{B}, we show the
+increase in cumulative variance explained at each rank, and visualize
+that using 39 ranks explains about 70\% of the variance in the empirical
+metaweb. This is a different information from the \(L_2\) loss (which is
+averaged across interactions), as it works on the eigenvalues of the
+embedding, and therefore captures higher-level features of the network.
+In panel \textbf{C}, we show positions of hosts and parasites on the
+first two dimensions of the left and right subspaces. Note that these
+values largely skew negative, because the first dimensions capture the
+coarse structure of the network: most pairs of species do not interact,
+and therefore have negative values. Finally in panel \textbf{D}, we show
+the predicted weight (\emph{i.e.} the result of the multiplication of
+the RDGP subspaces at a rank of 25) as a function of whether the
+interactions are observed, not-observed, or unknown due to lack of
+co-occurrence. This reveals that the observed interactions have higher
+predicted weights, although there is some overlap; the usual approach to
+identify potential interactions based on this information would be a
+thresholding analysis, which is outside the scope of this manuscript
+(and is done in the papers cited in this illustration). Because the
+values returned from RDPG are not bound to the unit interval, we
+performed a clamping of the weights to the unit space, showing a
+one-inflation in documented interaction, and a zero-inflation in other
+species pairs. This last figure crosses from the statistical into the
+ecological, by showing that species pairs with no documented
+co-occurrence have weights that are not distinguishable from species
+pairs with no documented interactions, suggesting that (as befits a
+host-parasite model) the ability to interact is a strong predictor of
+co-occurrence.
+
+\begin{figure}
+\hypertarget{fig:illustration2}{%
+\centering
+\includegraphics{figures/illustration-part2.png}
+\caption{Ecological analysis of an embedding for a host-parasite
+metaweb, using Random Dot Product Graphs. \textbf{A}, relationship
+between the number of parasites and position along the first axis of the
+right-subspace for all hosts, showing that the embedding captures
+elements of network structure at the species scale. \textbf{B}, weak
+relationship between the body mass of hosts (in grams) and the position
+alongside the same dimension. \textbf{C}, weak relationship between
+bodymass of hosts and parasite richness. \textbf{D}, distribution of
+positions alongside the same axis for hosts grouped by taxonomic
+family.}\label{fig:illustration2}
+}
+\end{figure}
+
+As the results of fig.~\ref{fig:illustration1} show that we can extract
+an embedding of the metaweb that captures enough variance to be
+relevant, in fig.~\ref{fig:illustration2}, we relate the values of
+latent variables for hosts to different ecologically-relevant data. In
+panel \textbf{A}, we show that host with a higher value on the first
+dimension have fewer parasites. This relates to the body size of hosts
+in the \emph{PanTHERIA} database (Jones et al., 2009), as shown in panel
+\textbf{B}: interestingly, the position on the first axis is only weakly
+correlated to body mass of the host; this matches well establihed
+results showing that body size/mass is not always a direct predictor of
+parasite richness in terrestrial mammals (Morand \& Poulin, 1998), a
+result we observe in panel \textbf{C}. Finally, in panel \textbf{D}, we
+can see how different taxonomic families occupy different positions on
+the first axis, with \emph{e.g.} Sciuridae being biased towards higher
+values. These results show how we can look for ecological informations
+in the output of network embeddings, which can further be refined into
+the selection of predictors for transfer learning.
 
@@
 
+\leavevmode\hypertarget{ref-Gaucher2021OutDet}{}%
+Gaucher, S., Klopp, O., \& Robin, G. (2021). Outlier detection in
+networks with missing links. \emph{Computational Statistics \& Data
+Analysis}, \emph{164}, 107308.
+\url{https://doi.org/10.1016/j.csda.2021.107308}
+
 \leavevmode\hypertarget{ref-Gibb2021DatPro}{}%
@@
 
+\leavevmode\hypertarget{ref-Jones2009PanSpe}{}%
+Jones, K. E., Bielby, J., Cardillo, M., Fritz, S. A., O'Dell, J., Orme,
+C. D. L., Safi, K., Sechrest, W., Boakes, E. H., Carbone, C., Connolly,
+C., Cutts, M. J., Foster, J. K., Grenyer, R., Habib, M., Plaster, C. A.,
+Price, S. A., Rigby, E. A., Rist, J., \ldots{} Purvis, A. (2009).
+PanTHERIA: A species‐level database of life history, ecology, and
+geography of extant and recently extinct mammals: Ecological Archives
+E090‐184. \emph{Ecology}, \emph{90}(9), 2648--2648.
+\url{https://doi.org/10.1890/08-1494.1}
+
 \leavevmode\hypertarget{ref-Jordano2016SamNet}{}%
@@
 \url{https://doi.org/10.1016/j.tree.2015.03.014}
+
+\leavevmode\hypertarget{ref-Morand1998DenBod}{}%
+Morand, S., \& Poulin, R. (1998). Density, body mass and parasite
+species richness of terrestrial mammals. \emph{Evolutionary Ecology},
+\emph{12}(6), 717--727. \url{https://doi.org/10.1023/A:1006537600093}
 

### 2022-09-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@5c6d9d4823f8bd4aab92c025a087e9b2f96261ef 🚀

@@
 methods rely either on linear algebra, or on pseudo-random walks on
-graphs.
+graphs. All forms of embeddings presented in the table share the common
+property of summarizing their objects into (sets of) dense feature
+vectors, that capture the overall network structure, pairwise
+information on nodes, and emergent aspects of the network, in a
+compressed way (\emph{i.e.} with some information loss, as we later
+discuss in the illustration). Node embeddings tend to focus on
+maintaining pairwise relationships, while graph embeddings focus on
+maintaining the network structure. Nevertheless, some graph embedding
+techniques (like RDPG, see \emph{e.g.} Wu et al., 2021) will provide
+usable node-level embeddings.
 
@@
 
+Before moving further, it is important to clarify the epistemic status
+of node values derived from embeddings: specifically, they are
+\emph{not} functional traits, and therefore should not be discussed in
+terms of effects or responses. As per the framework of Malaterre et al.
+(2019), these values neither derive from, nor result in, changes in
+organismal fitness, and should therefore not be used to quantify
+\emph{e.g.} functional diversity. This holds true even when there are
+correlations between latent values and functional traits: although these
+enable an ecological discussion of how traits condition the structure of
+the network, the existence of a statistical relationship does not
+elevate the latent values to the status of functional traits.
+
 Rather than directly predicting biological rules (see \emph{e.g.}
@@
 matrices that when multiplied give an approximation of the original
-network. The code to reproduce this example is available as
-supplementary material (note, for the sake of comparison, that Strydom,
-Catchen, et al., 2021 have an example using embedding through PCA
-followed by prediction using a deep neural network on the same dataset).
-The resulting (binary) metaweb \(\mathcal{M}\) has 2131 interactions
-between 206 parasites and 121 hosts, and its adjacency matrix has full
-rank (\emph{i.e.} it represents a space with 121 dimensions). All
-analyses were done using Julia (Bezanson et al., 2017) version 1.7.2,
-\emph{Makie.jl} (Danisch \& Krumbiegel, 2021), and
+network. RDPG has the particularly desirable properties of being a graph
+embedding technique that produces relevant node-level feature vectors,
+and provides good approximations of graphs with varied structures
+(Athreya et al., 2017). The code to reproduce this example is available
+as supplementary material (note, for the sake of comparison, that
+Strydom, Catchen, et al., 2021 have an example using embedding through
+PCA followed by prediction using a deep neural network on the same
+dataset). The resulting (binary) metaweb \(\mathcal{M}\) has 2131
+interactions between 206 parasites and 121 hosts, and its adjacency
+matrix has full rank (\emph{i.e.} it represents a space with 121
+dimensions). All analyses were done using Julia (Bezanson et al., 2017)
+version 1.7.2, \emph{Makie.jl} (Danisch \& Krumbiegel, 2021), and
 \emph{EcologicalNetworks.jl} (Poisot et al., 2019).
@@
 
+\leavevmode\hypertarget{ref-Athreya2017StaInf}{}%
+Athreya, A., Fishkind, D. E., Levin, K., Lyzinski, V., Park, Y., Qin,
+Y., Sussman, D. L., Tang, M., Vogelstein, J. T., \& Priebe, C. E.
+(2017). \emph{Statistical inference on random dot product graphs: A
+survey} (No. arXiv:1709.05454). arXiv.
+\url{http://arxiv.org/abs/1709.05454}
+
 \leavevmode\hypertarget{ref-Bartomeus2016ComFra}{}%
@@
 
+\leavevmode\hypertarget{ref-Malaterre2019FunDiv}{}%
+Malaterre, C., Dussault, A. C., Mermans, E., Barker, G., Beisner, B. E.,
+Bouchard, F., Desjardins, E., Handa, I. T., Kembel, S. W., Lajoie, G.,
+Maris, V., Munson, A. D., Odenbaugh, J., Poisot, T., Shapiro, B. J., \&
+Suttle, C. A. (2019). Functional Diversity: An Epistemic Roadmap.
+\emph{BioScience}, \emph{69}(10), 800--811.
+\url{https://doi.org/10.1093/biosci/biz089}
+
 \leavevmode\hypertarget{ref-McLeod2021SamAsy}{}%
@@
 
+\leavevmode\hypertarget{ref-Wu2021MaxPos}{}%
+Wu, D., Palmer, D. R., \& Deford, D. R. (2021). \emph{Maximum a
+Posteriori Inference of Random Dot Product Graphs via Conic Programming}
+(No. arXiv:2101.02180). arXiv. \url{http://arxiv.org/abs/2101.02180}
+
 \leavevmode\hypertarget{ref-Xu2020UndGra}{}%

### 2022-09-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@168624837233208b10ef2af8dac807174a1c4161 🚀

@@
 and machine learning techniques tend to handle continuous data better.
-Bringing a sparse graph into a continuous, dense vector space (Xu, 2020)
+Bringing a sparse graph into a continuous, dense vector space (Xu, 2021)
 opens up a broader variety of predictive algorithms, notably of the sort
@@
 
-\leavevmode\hypertarget{ref-Xu2020UndGra}{}%
-Xu, M. (2020). \emph{Understanding graph embedding methods and their
-applications}. \url{http://arxiv.org/abs/2012.08019}
+\leavevmode\hypertarget{ref-Xu2021UndGra}{}%
+Xu, M. (2021). Understanding Graph Embedding Methods and Their
+Applications. \emph{SIAM Review}, \emph{63}(4), 825--853.
+\url{https://doi.org/10.1137/20M1386062}
 

### 2022-09-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@ed328b81b016bdf01ad11d064b84c1e85fce1f14 🚀

@@
 that of a species pool (\emph{i.e.} a set of potentially interacting
-species in a given area): through the analysis of databases like GBIF or
-IUCN, it is possible to construct a list of species in a region of
-interest; but inferring the potential interactions between these species
-is difficult.
+species in a given area): through the analysis of databases like the
+Global Biodiversity Information Facility (GBIF) or the International
+Union for the Conservation of Nature (IUCN), it is possible to construct
+a list of species in a region of interest; but inferring the potential
+interactions between these species is difficult.
 
@@
 environmental conditions, and local distribution of functional traits,
-among others. Yet, recent results by Saravia et al. (2021) strongly
-suggest that the local (metaweb) realizations only respond weakly to
-local conditions: instead, they reflect constraints inherited by the
-structure of their metaweb. This establishes the metaweb structure as
-the core goal of predictive network ecology, as it is a required
-information to accurately produce downscaled, local predictions.
+among others. Specifically, although co-occurrence can be driven by
+interactions (Cazelles et al., 2016), co-occurrence alone is not a
+predictor of interactions (Blanchet et al., 2020; Thurman et al., 2019),
+and therefore lack of co-occurrence cannot be used to rule out lack of a
+feasible interaction. Yet, recent results by Saravia et al. (2021)
+strongly suggest that the local (metaweb) realizations only respond
+weakly to local conditions: instead, they reflect constraints inherited
+by the structure of their metaweb. This establishes the metaweb
+structure as the core goal of predictive network ecology, as it is a
+required information to accurately produce downscaled, local
+predictions.
 
@@
 \includegraphics{figures/conceptual_2.png}
-\caption{Overview of the embedding process. A network (\textbf{A}),
-represented here as its adjacency matrix, is converted into a
-lower-dimensional object (\textbf{B}) where nodes, subgraphs, or edges
-have specific values (see tbl.~\ref{tbl:methods} for an overview of
-methods and their use for species interactions). For the purposes of
+\caption{Overview of the embedding and transfer process. A network
+(\textbf{A}), represented here as its adjacency matrix, is converted
+into a lower-dimensional object (\textbf{B}) where nodes, subgraphs, or
+edges have specific values (see tbl.~\ref{tbl:methods} for an overview
+of methods and their use for species interactions). For the purposes of
 prediction, this low-dimensional object encodes feature vectors for
@@
 we identified were either statistical associations, or analogues to
-joint species distribution models. \(^a\): statistical interactions;
-\(^b\): joint-SDM-like approach. Given the need to evaluate different
-methods on a problem-specific basis, the fact that a lot of methods have
-not been used on network problems is an opportunity for benchmarking and
-method development. Note that the row for PCA also applies to
-kernel/probabilistic PCA, which are variations on the more general
-method of SVD. Note further that tSNE has been included because it is
-frequently used to embed graphs, including of species
+joint species distribution models. \(^a\): application is concerned with
+\emph{statistical} interactions, which are not necessarilly direct
+biotic interactions; \(^b\):application is concerned with joint-SDM-like
+approach, which is also very close to statistical associations as
+opposed to direct biotic interactions. Given the need to evaluate
+different methods on a problem-specific basis, the fact that a lot of
+methods have not been used on network problems is an opportunity for
+benchmarking and method development. Note that the row for PCA also
+applies to kernel/probabilistic PCA, which are variations on the more
+general method of SVD. Note further that tSNE has been included because
+it is frequently used to embed graphs, including of species
 associations/interactions, despite not being strictly speaking, a graph
@@
 (or strives to capture) the action of evolutionary processes on network
-structure, which at least for food webs have been well documented
-\textbf{TK REF}; similarly, the use of functional traits assumes that
-interactions can be infered from the knowledge of trait-matching rules,
-which is similarly well supported in the empirical literature \textbf{TK
-REF}. Relating this information to an embedding rather than a list of
-networks measures would allow to capture their effect on the more
-fundamental aspects of network structure; conversely, the absence of a
-phylogenetic or functional signal may suggest that evolutionary/trait
-processes are not strong drivers of network structure, therefore opening
-a new way to perform hypothesis testing.
+structure, which at least for food webs have been well documented (Dalla
+Riva \& Stouffer, 2016; Stouffer et al., 2012; Stouffer et al., 2007);
+similarly, the use of functional traits assumes that interactions can be
+infered from the knowledge of trait-matching rules, which is similarly
+well supported in the empirical literature (Bartomeus, 2013; Bartomeus
+et al., 2016; Gravel et al., 2013). Relating this information to an
+embedding rather than a list of networks measures would allow to capture
+their effect on the more fundamental aspects of network structure;
+conversely, the absence of a phylogenetic or functional signal may
+suggest that evolutionary/trait processes are not strong drivers of
+network structure, therefore opening a new way to perform hypothesis
+testing.
 
@@
 
-As the results of fig.~\ref{fig:illustration1} show that we can extract
-an embedding of the metaweb that captures enough variance to be
-relevant, in fig.~\ref{fig:illustration2}, we relate the values of
-latent variables for hosts to different ecologically-relevant data. In
-panel \textbf{A}, we show that host with a higher value on the first
-dimension have fewer parasites. This relates to the body size of hosts
-in the \emph{PanTHERIA} database (Jones et al., 2009), as shown in panel
-\textbf{B}: interestingly, the position on the first axis is only weakly
-correlated to body mass of the host; this matches well establihed
+The results of fig.~\ref{fig:illustration1} show that we can extract an
+embedding of the metaweb that captures enough variance to be relevant;
+specifically, this is true both of \(L_2\) loss (indicating that RDPG is
+able to capture pairwise processes) and the cumulative variance
+explained (indicating that RDPG is able to capture network-level
+structure). Therefore, in fig.~\ref{fig:illustration2}, we relate the
+values of latent variables for hosts to different ecologically-relevant
+data. In panel \textbf{A}, we show that host with a higher value on the
+first dimension have fewer parasites. This relates to the body size of
+hosts in the \emph{PanTHERIA} database (Jones et al., 2009), as shown in
+panel \textbf{B}: interestingly, the position on the first axis is only
+weakly correlated to body mass of the host; this matches well establihed
 results showing that body size/mass is not always a direct predictor of
@@
 
+\leavevmode\hypertarget{ref-Bartomeus2013UndLin}{}%
+Bartomeus, I. (2013). Understanding linkage rules in plant-pollinator
+networks by using hierarchical models that incorporate pollinator
+detectability and plant traits. \emph{PloS One}, \emph{8}(7), e69200.
+\url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0069200}
+
 \leavevmode\hypertarget{ref-Bartomeus2016ComFra}{}%
@@
 65--98. \url{https://doi.org/10.1137/141000671}
+
+\leavevmode\hypertarget{ref-Blanchet2020CooNot}{}%
+Blanchet, F. G., Cazelles, K., \& Gravel, D. (2020). Co-occurrence is
+not evidence of ecological interactions. \emph{Ecology Letters}.
 
@@
 
+\leavevmode\hypertarget{ref-Cazelles2016TheSpe}{}%
+Cazelles, K., Araújo, M. B., Mouquet, N., \& Gravel, D. (2016). A theory
+for species co-occurrence in interaction networks. \emph{Theoretical
+Ecology}, \emph{9}(1), 39--48.
+\url{https://doi.org/10.1007/s12080-015-0281-9}
+
 \leavevmode\hypertarget{ref-Chami2022MacLea}{}%
@@
 \url{https://doi.org/10.1111/ecog.04006}
+
+\leavevmode\hypertarget{ref-Gravel2013InfFoo}{}%
+Gravel, D., Poisot, T., Albouy, C., Velez, L., \& Mouillot, D. (2013).
+Inferring food web structure from predator-prey body size relationships.
+\emph{Methods in Ecology and Evolution}, \emph{4}(11), 1083--1090.
+\url{https://doi.org/10.1111/2041-210X.12103}
 
@@
 
+\leavevmode\hypertarget{ref-Stouffer2007EviExi}{}%
+Stouffer, D. B., Camacho, J., Jiang, W., \& Nunes Amaral, L. A. (2007).
+Evidence for the existence of a robust pattern of prey selection in food
+webs. \emph{Proceedings of the Royal Society B: Biological Sciences},
+\emph{274}(1621), 1931--1940.
+\url{https://doi.org/10.1098/rspb.2007.0571}
+
+\leavevmode\hypertarget{ref-Stouffer2012EvoCon}{}%
+Stouffer, D. B., Sales-Pardo, M., Sirer, M. I., \& Bascompte, J. (2012).
+Evolutionary Conservation of Species' Roles in Food Webs.
+\emph{Science}, \emph{335}(6075), 1489--1492.
+\url{https://doi.org/10.1126/science.1216556}
+
 \leavevmode\hypertarget{ref-Strydom2022FooWeb}{}%
@@
 \url{https://doi.org/10.1145/2736277.2741093}
+
+\leavevmode\hypertarget{ref-Thurman2019TesLin}{}%
+Thurman, L. L., Barner, A. K., Garcia, T. S., \& Chestnut, T. (2019).
+Testing the link between species interactions and co-occurrence in a
+trophic network. \emph{Ecography}, \emph{0}.
+\url{https://doi.org/10.1111/ecog.04360}
 

### 2022-10-04 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@cf472ac989d9ea38d7b0478bf6f18ab7ef8564f8 🚀

@@
 similarly, the use of functional traits assumes that interactions can be
-infered from the knowledge of trait-matching rules, which is similarly
+inferred from the knowledge of trait-matching rules, which is similarly
 well supported in the empirical literature (Bartomeus, 2013; Bartomeus

### 2022-10-04 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@cfc35072323c390515c168da89a05baaa02a78d6 🚀

@@
 reconstruct a network with these new species (\textbf{D}). This entire
-cycle constitutes an instance of transfer learning, where the transfered
-information is the representation of graph \textbf{A} through its
-embedding.}\label{fig:embedding}
+cycle constitutes an instance of transfer learning, where the
+transferred information is the representation of graph \textbf{A}
+through its embedding.}\label{fig:embedding}
 }

### 2022-10-07 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@b94b98480a69f18125786f9872154aebb77f4413 🚀

--- 2022-10-04 draft.tex
@@
 \includegraphics{figures/conceptual_2.png}
-\caption{Overview of the embedding and transfer process. A network
-(\textbf{A}), represented here as its adjacency matrix, is converted
-into a lower-dimensional object (\textbf{B}) where nodes, subgraphs, or
-edges have specific values (see tbl.~\ref{tbl:methods} for an overview
-of methods and their use for species interactions). For the purposes of
-prediction, this low-dimensional object encodes feature vectors for
-\emph{e.g.} the nodes. Embedding also allows to visualize the structure
-in the data differently (see fig.~\ref{fig:illustration}), much like
-with a principal component analysis. From a low-dimensional feature
-vector, it is possible to develop predictive approaches. Nodes in an
-ecological network are usually species (\textbf{C}), for which we can
-leverage phylogenetic relatedness (\emph{e.g.} Strydom et al., 2022) or
-functional traits to fill the values of additional species we would like
-to project in this space (here for nodes I, J, K, and L) from the
-embedding of known species (here, nodes A, B, C, and D). Because
-embeddings can be projected back to a graph, this allows us to
-reconstruct a network with these new species (\textbf{D}). This entire
-cycle constitutes an instance of transfer learning, where the transfered
-information is the representation of graph \textbf{A} through its
-embedding.}\label{fig:embedding}
+\caption{The embedding process (\textbf{A}) can help to identify links
+(interactions) that may have been missed within the current sample
+(community, \textbf{B}), while transfer learning (\textbf{D}) allows for
+predicting links (interactions) for species external to the original
+sample as well as within sample links (\textbf{F}). Transfer learning
+allows for the prediction links (interactions) when novel species
+(\textbf{C}) are included in the sample by learning using other relevant
+predictors (e.g.~traits) in conjunction with the known interactions to
+infer latent values (\textbf{E}). Within this context the predicted
+networks as well as the ecological predictors used (green boxes) are
+products that can be quantified through field measurements, whereas the
+embedded as well as imputed matrices are representative of
+\textbf{TK}}\label{fig:embedding}
 }

### 2023-01-24 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@32377dfbc750a8864f2ea754d587f4308f4fb1f0 🚀

--- 2022-10-07 draft.tex
@@
 \usepackage{lastpage}
+
+\usepackage{gensymb}
 
@@
 \setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
  {% don't indent paragraphs
@@
 
-\DeclareDelayedFloatFlavour*{longtable}{table}
-
 \pagestyle{plain}
@@
 %
-\,\textsuperscript{1,3,2}\quad %
+\,\textsuperscript{1,2,3}\quad %
 \href{https://orcid.org/0000-0003-4036-977X}{Ceres\,Barros}%
@@
 %
-\,\textsuperscript{5,2}\quad %
+\,\textsuperscript{2,5}\quad %
 \href{https://orcid.org/0000-0003-0452-6993}{Maxwell J\,Farrell}%
@@
 %
-\,\textsuperscript{3,2}\quad %
+\,\textsuperscript{2,3}\quad %
 \href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
 %
-\,\textsuperscript{5,2}\quad %
+\,\textsuperscript{2,5}\quad %
 \href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
@@
 
-\textsuperscript{‡}\,These authors contributed equally to the work\\
+\textsuperscript{‡}\,Equal contributions\\
 
@@
 \vfill
-This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
-Last revision: \emph{\today}
-
-\clearpage
-\thispagestyle{empty}
-
-\vfill
 
 \begin{enumerate}
-    \item Metawebs, (networks of potential interactions within a species
+    \itemMetawebs, (networks of potential interactions within a species
 pool) are a powerful abstraction to understand how large-scale species
 interaction networks are structured.%
-    \item Because metawebs are typically expressed at large spatial and
+    \itemBecause metawebs are typically expressed at large spatial and
 taxonomic scales, assembling them is a tedious and costly process;
@@
 deficiencies, by providing `draft' metawebs.%
-    \item One way to improve our ability to predict metawebs is to
+    \itemOne way to improve our ability to predict metawebs is to
 maximize available information by using graph embeddings, instead of the
@@
 machine learning that holds great potential for ecological problems.%
-    \item In this perspective, we outline how the challenges associated
+    \itemIn this perspective, we outline how the challenges associated
 with inferring metawebs line-up with the advantages of graph embeddings;
@@
 \end{enumerate}
+
+\vfill
+This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
+Last revision: \emph{\today}
+
+\clearpage
+\thispagestyle{empty}
+
+\vfill
 
@@
 One prominent family of approaches we do not discuss in the present
-manuscript is Graph Neural Networks (GNN; Zhou et al., 2020). GNN are,
-in a sense, a method to embed a graph into a dense subspace, but belong
-to the family of deep learning methods, which has its own set of
+manuscript is Graph Neural Networks {[}GNN; Zhou et al. (2020){]}. GNN
+are, in a sense, a method to embed a graph into a dense subspace, but
+belong to the family of deep learning methods, which has its own set of
 practices (see \emph{e.g.} Goodfellow et al., 2016). An important issue
@@
 \hypertarget{tbl:methods}{}
-\begin{longtable}[]{@{}lllll@{}}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1083}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1250}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2667}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1667}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3333}}@{}}
 \caption{\label{tbl:methods}Overview of some common graph embedding
@@
 embedding technique (see \emph{e.g.} Chami et al., 2022)}\tabularnewline
-\toprule
-\begin{minipage}[b]{0.09\columnwidth}\raggedright
-Method\strut
-\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\raggedright
-Object\strut
-\end{minipage} & \begin{minipage}[b]{0.23\columnwidth}\raggedright
-Technique\strut
-\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
-Reference\strut
-\end{minipage} & \begin{minipage}[b]{0.29\columnwidth}\raggedright
-Application\strut
-\end{minipage}\tabularnewline
-\midrule
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedright
+Method
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Object
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Technique
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Reference
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Application
+\end{minipage} \\
+\midrule()
 \endfirsthead
-\toprule
-\begin{minipage}[b]{0.09\columnwidth}\raggedright
-Method\strut
-\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\raggedright
-Object\strut
-\end{minipage} & \begin{minipage}[b]{0.23\columnwidth}\raggedright
-Technique\strut
-\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
-Reference\strut
-\end{minipage} & \begin{minipage}[b]{0.29\columnwidth}\raggedright
-Application\strut
-\end{minipage}\tabularnewline
-\midrule
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedright
+Method
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Object
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Technique
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Reference
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Application
+\end{minipage} \\
+\midrule()
 \endhead
-\begin{minipage}[t]{0.09\columnwidth}\raggedright
-tSNE\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
-nodes\strut
-\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
-statistical divergence\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-Hinton \& Roweis (2002)\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
-Gibb et al. (2021); Cieslak et al. (2020) \(^a\)\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.09\columnwidth}\raggedright
-LINE\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
-nodes\strut
-\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
-stochastic gradient descent\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-Tang et al. (2015)\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.09\columnwidth}\raggedright
-SDNE\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
-nodes\strut
-\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
-gradient descent\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-D. Wang et al. (2016)\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.09\columnwidth}\raggedright
-node2vec\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
-nodes\strut
-\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
-stochastic gradient descent\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-Grover \& Leskovec (2016)\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.09\columnwidth}\raggedright
-HARP\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
-nodes\strut
-\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
-meta-strategy\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-H. Chen et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.09\columnwidth}\raggedright
-DMSE\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
-joint nodes\strut
-\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
-deep neural network\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-D. Chen et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
-D. Chen et al. (2017) \(^b\)\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.09\columnwidth}\raggedright
-graph2vec\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
-sub-graph\strut
-\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
-skipgram network\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-Narayanan et al. (2017)\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.09\columnwidth}\raggedright
-RDPG\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
-graph\strut
-\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
-SVD\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-Young \& Scheinerman (2007)\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
-Poisot et al. (2021); Dalla Riva \& Stouffer (2016)\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.09\columnwidth}\raggedright
-GLEE\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
-graph\strut
-\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
-Laplacian eigenmap\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-Torres et al. (2020)\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.09\columnwidth}\raggedright
-DeepWalk\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
-graph\strut
-\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
-stochastic gradient descent\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-Perozzi et al. (2014)\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
-Wardeh et al. (2021)\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.09\columnwidth}\raggedright
-GraphKKE\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
-graph\strut
-\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
-stochastic differential equation\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-Melnyk et al. (2020)\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
-Melnyk et al. (2020) \(^a\)\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.09\columnwidth}\raggedright
-FastEmbed\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
-graph\strut
-\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
-eigen decomposition\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-Ramasamy \& Madhow (2015)\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.09\columnwidth}\raggedright
-PCA\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
-graph\strut
-\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
-eigen decomposition\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-S \& Surendran (2013)\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
-Strydom, Catchen, et al. (2021)\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.09\columnwidth}\raggedright
-Joint methods\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
-multiple graphs\strut
-\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
-multiple strategies\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-S. Wang et al. (2021)\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\bottomrule
+tSNE & nodes & statistical divergence & Hinton \& Roweis (2002) & Gibb
+et al. (2021); Cieslak et al. (2020) \(^a\) \\
+LINE & nodes & stochastic gradient descent & Tang et al. (2015) & \\
+SDNE & nodes & gradient descent & D. Wang et al. (2016) & \\
+node2vec & nodes & stochastic gradient descent & Grover \& Leskovec
+(2016) & \\
+HARP & nodes & meta-strategy & H. Chen et al. (2017) & \\
+DMSE & joint nodes & deep neural network & D. Chen et al. (2017) & D.
+Chen et al. (2017) \(^b\) \\
+graph2vec & sub-graph & skipgram network & Narayanan et al. (2017) & \\
+RDPG & graph & SVD & Young \& Scheinerman (2007) & Poisot et al. (2021);
+Dalla Riva \& Stouffer (2016) \\
+GLEE & graph & Laplacian eigenmap & Torres et al. (2020) & \\
+DeepWalk & graph & stochastic gradient descent & Perozzi et al. (2014) &
+Wardeh et al. (2021) \\
+GraphKKE & graph & stochastic differential equation & Melnyk et al.
+(2020) & Melnyk et al. (2020) \(^a\) \\
+FastEmbed & graph & eigen decomposition & Ramasamy \& Madhow (2015) & \\
+PCA & graph & eigen decomposition & S \& Surendran (2013) & Strydom,
+Catchen, et al. (2021) \\
+Joint methods & multiple graphs & multiple strategies & S. Wang et al.
+(2021) & \\
+\bottomrule()
 \end{longtable}
@@
 example, that the macro-evolutionary history of a network is adequately
-represented by some graph embeddings (Random dot product graphs (RDPG);
-see Dalla Riva \& Stouffer, 2016). In a recent publication, Strydom et
-al. (2022) have used an embedding (based on RDPG) to project a metaweb
-of trophic interactions between European mammals, and transferred this
-information to mammals of Canada, using the phylogenetic distance
-between related clades to infer the values in the latent sub-space into
-which the European metaweb was projected. By performing the RDPG step on
-re-constructed values, this approach yields a probabilistic trophic
-metaweb for mammals of Canada based on knowledge of European species,
-despite a limited (\(\approx\) 5\%) taxonomic overlap.
+represented by some graph embeddings {[}Random dot product graphs
+(RDPG); see Dalla Riva \& Stouffer (2016){]}. In a recent publication,
+Strydom et al. (2022) have used an embedding (based on RDPG) to project
+a metaweb of trophic interactions between European mammals, and
+transferred this information to mammals of Canada, using the
+phylogenetic distance between related clades to infer the values in the
+latent sub-space into which the European metaweb was projected. By
+performing the RDPG step on re-constructed values, this approach yields
+a probabilistic trophic metaweb for mammals of Canada based on knowledge
+of European species, despite a limited (\(\approx\) 5\%) taxonomic
+overlap.
 
 Graph embeddings \emph{can} serve as a dimensionality reduction method.
-For example, RDPG (Strydom et al., 2022) and t-SVD (truncated Singular
-Value Decomposition; Poisot et al., 2021) typically embed networks using
-fewer dimensions than the original network (the original network has as
-many dimensions as species, and as many informative dimensions as
-trophically unique species; Strydom, Dalla Riva, et al., 2021). But this
-is not necessarily the case -- indeed, one may perform a PCA (a special
-case of SVD) to project the raw data into a subspace that improves the
-efficacy of t-SNE (t-distributed stochastic neighbor embedding; Maaten,
-2009). There are many dimensionality reductions (Anowar et al., 2021)
-that can be applied to an embedded network should the need for
-dimensionality reduction (for example for data visualisation) arise. In
-brief, many graph embeddings \emph{can} serve as dimensionality
-reduction steps, but not all do, neither do all dimensionality reduction
-methods provide adequate graph embedding capacities. In the next section
-(and fig.~\ref{fig:illustration}), we show how the amount of
-dimensionality reduction can affect the quality of the embedding.
+For example, RDPG (Strydom et al., 2022) and t-SVD {[}truncated Singular
+Value Decomposition; Poisot et al. (2021){]} typically embed networks
+using fewer dimensions than the original network {[}the original network
+has as many dimensions as species, and as many informative dimensions as
+trophically unique species; Strydom, Dalla Riva, et al. (2021){]}. But
+this is not necessarily the case -- indeed, one may perform a PCA (a
+special case of SVD) to project the raw data into a subspace that
+improves the efficacy of t-SNE {[}t-distributed stochastic neighbor
+embedding; Maaten (2009){]}. There are many dimensionality reductions
+(Anowar et al., 2021) that can be applied to an embedded network should
+the need for dimensionality reduction (for example for data
+visualisation) arise. In brief, many graph embeddings \emph{can} serve
+as dimensionality reduction steps, but not all do, neither do all
+dimensionality reduction methods provide adequate graph embedding
+capacities. In the next section (and fig.~\ref{fig:illustration}), we
+show how the amount of dimensionality reduction can affect the quality
+of the embedding.
 
@@
 interaction networks structure is increasingly leveraged as a tool to
-guide conservation actions (see \emph{e.g.} recent discussions for
-food-web based conservation; Eero et al., 2021; Naman et al., 2022;
-Stier et al., 2017), the need to appraise and correct biases that are
+guide conservation actions {[}see \emph{e.g.} recent discussions for
+food-web based conservation; Eero et al. (2021); Naman et al. (2022);
+Stier et al. (2017){]}, the need to appraise and correct biases that are
 unwittingly propagated to algorithms when embedded from the original
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Adam2014EleTre}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Adam2014EleTre}{}}%
 Adam, R. (2014). \emph{Elephant treaties: The Colonial legacy of the
@@
 
-\leavevmode\hypertarget{ref-Albouy2019MarFis}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Albouy2019MarFis}{}}%
 Albouy, C., Archambault, P., Appeltans, W., Araújo, M. B., Beauchesne,
@@
 
-\leavevmode\hypertarget{ref-Anowar2021ConEmp}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Anowar2021ConEmp}{}}%
 Anowar, F., Sadaoui, S., \& Selim, B. (2021). Conceptual and empirical
@@
 
-\leavevmode\hypertarget{ref-Arsov2019NetEmb}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Arsov2019NetEmb}{}}%
 Arsov, N., \& Mirceva, G. (2019). \emph{Network Embedding: An Overview}.
@@
 
-\leavevmode\hypertarget{ref-Athreya2017StaInf}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Athreya2017StaInf}{}}%
 Athreya, A., Fishkind, D. E., Levin, K., Lyzinski, V., Park, Y., Qin,
@@
 
-\leavevmode\hypertarget{ref-Bartomeus2013UndLin}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Bartomeus2013UndLin}{}}%
 Bartomeus, I. (2013). Understanding linkage rules in plant-pollinator
@@
 
-\leavevmode\hypertarget{ref-Bartomeus2016ComFra}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Bartomeus2016ComFra}{}}%
 Bartomeus, I., Gravel, D., Tylianakis, J. M., Aizen, M. A., Dickie, I.
@@
 
-\leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Bezanson2017JulFre}{}}%
 Bezanson, J., Edelman, A., Karpinski, S., \& Shah, V. (2017). Julia: A
@@
 
-\leavevmode\hypertarget{ref-Blanchet2020CooNot}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Blanchet2020CooNot}{}}%
 Blanchet, F. G., Cazelles, K., \& Gravel, D. (2020). Co-occurrence is
@@
 
-\leavevmode\hypertarget{ref-Bohan2017NexGlo}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Bohan2017NexGlo}{}}%
 Bohan, D. A., Vacher, C., Tamaddoni-Nezhad, A., Raybould, A., Dumbrell,
@@
 
-\leavevmode\hypertarget{ref-Botella2022AppGra}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Botella2022AppGra}{}}%
 Botella, C., Dray, S., Matias, C., Miele, V., \& Thuiller, W. (2022). An
@@
 
-\leavevmode\hypertarget{ref-Braga2019SpaAna}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Braga2019SpaAna}{}}%
 Braga, J., Pollock, L. J., Barros, C., Galiana, N., Montoya, J. M.,
@@
 
-\leavevmode\hypertarget{ref-BramonMora2018IdeCom}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-BramonMora2018IdeCom}{}}%
 Bramon Mora, B., Gravel, D., Gilarranz, L. J., Poisot, T., \& Stouffer,
@@
 
-\leavevmode\hypertarget{ref-Buxton2021KeyInf}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Buxton2021KeyInf}{}}%
 Buxton, R. T., Bennett, J. R., Reid, A. J., Shulman, C., Cooke, S. J.,
@@
 
-\leavevmode\hypertarget{ref-Cazelles2016TheSpe}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Cazelles2016TheSpe}{}}%
 Cazelles, K., Araújo, M. B., Mouquet, N., \& Gravel, D. (2016). A theory
@@
 
-\leavevmode\hypertarget{ref-Chami2022MacLea}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Chami2022MacLea}{}}%
 Chami, I., Abu-El-Haija, S., Perozzi, B., Ré, C., \& Murphy, K. (2022).
@@
 
-\leavevmode\hypertarget{ref-Chen2017DeeMul}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Chen2017DeeMul}{}}%
 Chen, D., Xue, Y., Fink, D., Chen, S., \& Gomes, C. P. (2017).
@@
 
-\leavevmode\hypertarget{ref-Chen2017HarHie}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Chen2017HarHie}{}}%
 Chen, H., Perozzi, B., Hu, Y., \& Skiena, S. (2017). \emph{HARP:
@@
 
-\leavevmode\hypertarget{ref-Choudry2013SavBio}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Choudry2013SavBio}{}}%
 Choudry, A. (2013). Saving biodiversity, for whom and for what?
@@
 
-\leavevmode\hypertarget{ref-Cieslak2020TdiSto}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Cieslak2020TdiSto}{}}%
 Cieslak, M. C., Castelfranco, A. M., Roncalli, V., Lenz, P. H., \&
@@
 
-\leavevmode\hypertarget{ref-Csermely2004StrLin}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Csermely2004StrLin}{}}%
 Csermely, P. (2004). Strong links are important, but weak links
@@
 
-\leavevmode\hypertarget{ref-DallaRiva2016ExpEvo}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-DallaRiva2016ExpEvo}{}}%
 Dalla Riva, G. V., \& Stouffer, D. B. (2016). Exploring the evolutionary
@@
 
-\leavevmode\hypertarget{ref-Dallas2017PreCry}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Dallas2017PreCry}{}}%
 Dallas, T., Park, A. W., \& Drake, J. M. (2017). Predicting cryptic
@@
 
-\leavevmode\hypertarget{ref-Danisch2021MakJl}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Danisch2021MakJl}{}}%
 Danisch, S., \& Krumbiegel, J. (2021). Makie.jl: Flexible
@@
 
-\leavevmode\hypertarget{ref-Dominguez2020DecCon}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Dominguez2020DecCon}{}}%
 Domínguez, L., \& Luoma, C. (2020). Decolonising Conservation Policy:
@@
 
-\leavevmode\hypertarget{ref-Dunne2006NetStr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Dunne2006NetStr}{}}%
 Dunne, J. A. (2006). The Network Structure of Food Webs. In J. A. Dunne
@@
 
-\leavevmode\hypertarget{ref-Eero2021UseFoo}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Eero2021UseFoo}{}}%
 Eero, M., Dierking, J., Humborg, C., Undeman, E., MacKenzie, B. R.,
@@
 
-\leavevmode\hypertarget{ref-Eichhorn2019SteDec}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Eichhorn2019SteDec}{}}%
 Eichhorn, M. P., Baker, K., \& Griffiths, M. (2019). Steps towards
@@
 
-\leavevmode\hypertarget{ref-Eklof2013DimEco}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Eklof2013DimEco}{}}%
 Eklöf, A., Jacob, U., Kopp, J., Bosch, J., Castro-Urgal, R., Chacoff, N.
@@
 
-\leavevmode\hypertarget{ref-Fortin2021NetEco}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Fortin2021NetEco}{}}%
 Fortin, M.-J., Dale, M. R. T., \& Brimacombe, C. (2021). Network ecology
@@
 
-\leavevmode\hypertarget{ref-Fricke2022EffDef}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Fricke2022EffDef}{}}%
 Fricke, E. C., Ordonez, A., Rogers, H. S., \& Svenning, J.-C. (2022).
@@
 
-\leavevmode\hypertarget{ref-Galiana2021SpaSca}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Galiana2021SpaSca}{}}%
 Galiana, N., Barros, C., Braga, J., Ficetola, G. F., Maiorano, L.,
@@
 
-\leavevmode\hypertarget{ref-Galiana2019GeoVar}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Galiana2019GeoVar}{}}%
 Galiana, N., Hawkins, B. A., \& Montoya, J. M. (2019). The geographical
@@
 
-\leavevmode\hypertarget{ref-Galiana2022EcoNet}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Galiana2022EcoNet}{}}%
 Galiana, N., Lurgi, M., Bastazini, V. A. G., Bosch, J., Cagnolo, L.,
@@
 
-\leavevmode\hypertarget{ref-Galiana2018SpaSca}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Galiana2018SpaSca}{}}%
 Galiana, N., Lurgi, M., Claramunt-López, B., Fortin, M.-J., Leroux, S.,
@@
 
-\leavevmode\hypertarget{ref-Gaucher2021OutDet}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Gaucher2021OutDet}{}}%
 Gaucher, S., Klopp, O., \& Robin, G. (2021). Outlier detection in
@@
 
-\leavevmode\hypertarget{ref-Gibb2021DatPro}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Gibb2021DatPro}{}}%
 Gibb, R., Albery, G. F., Becker, D. J., Brierley, L., Connor, R.,
@@
 
-\leavevmode\hypertarget{ref-Goodfellow2016DeeLea}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Goodfellow2016DeeLea}{}}%
 Goodfellow, I., Bengio, Y., \& Courville, A. (2016). \emph{Deep
@@
 
-\leavevmode\hypertarget{ref-Goyal2018GraEmb}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Goyal2018GraEmb}{}}%
 Goyal, P., \& Ferrara, E. (2018). Graph embedding techniques,
@@
 
-\leavevmode\hypertarget{ref-Gravel2018BriElt}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Gravel2018BriElt}{}}%
 Gravel, D., Baiser, B., Dunne, J. A., Kopelke, J.-P., Martinez, N. D.,
@@
 
-\leavevmode\hypertarget{ref-Gravel2013InfFoo}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Gravel2013InfFoo}{}}%
 Gravel, D., Poisot, T., Albouy, C., Velez, L., \& Mouillot, D. (2013).
@@
 
-\leavevmode\hypertarget{ref-Green2019DisInt}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Green2019DisInt}{}}%
 Green, B., \& Chen, Y. (2019). Disparate Interactions: An
@@
 
-\leavevmode\hypertarget{ref-Grover2016NodSca}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Grover2016NodSca}{}}%
 Grover, A., \& Leskovec, J. (2016). Node2vec: Scalable Feature Learning
@@
 
-\leavevmode\hypertarget{ref-Grunig2020CroFor}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Grunig2020CroFor}{}}%
 Grünig, M., Mazzi, D., Calanca, P., Karger, D. N., \& Pellissier, L.
@@
 
-\leavevmode\hypertarget{ref-Gupta2021GraNeu}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Gupta2021GraNeu}{}}%
 Gupta, A., Matta, P., \& Pant, B. (2021). Graph neural network: Current
@@
 
-\leavevmode\hypertarget{ref-Hadfield2014TalTwo}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Hadfield2014TalTwo}{}}%
 Hadfield, J. D., Krasnov, B. R., Poulin, R., \& Nakagawa, S. (2014). A
@@
 
-\leavevmode\hypertarget{ref-Herbert1965Dun}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Herbert1965Dun}{}}%
 Herbert, F. (1965). \emph{Dune} (1st ed.). Chilton Book Company.
 
-\leavevmode\hypertarget{ref-Hinton2002StoNei}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Hinton2002StoNei}{}}%
 Hinton, G., \& Roweis, S. T. (2002). Stochastic neighbor embedding.
@@
 
-\leavevmode\hypertarget{ref-Hoffmann2019MacLea}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Hoffmann2019MacLea}{}}%
 Hoffmann, J., Bar-Sinai, Y., Lee, L. M., Andrejevic, J., Mishra, S.,
@@
 
-\leavevmode\hypertarget{ref-Hortal2015SevSho}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Hortal2015SevSho}{}}%
 Hortal, J., de Bello, F., Diniz-Filho, J. A. F., Lewinsohn, T. M., Lobo,
@@
 
-\leavevmode\hypertarget{ref-Jones2009PanSpe}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Jones2009PanSpe}{}}%
 Jones, K. E., Bielby, J., Cardillo, M., Fritz, S. A., O'Dell, J., Orme,
@@
 
-\leavevmode\hypertarget{ref-Jordano2016SamNet}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Jordano2016SamNet}{}}%
 Jordano, P. (2016). Sampling networks of ecological interactions.
@@
 
-\leavevmode\hypertarget{ref-Lamba2019DeeLea}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Lamba2019DeeLea}{}}%
 Lamba, A., Cassey, P., Segaran, R. R., \& Koh, L. P. (2019). Deep
@@
 
-\leavevmode\hypertarget{ref-Maaten2009LeaPar}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Maaten2009LeaPar}{}}%
 Maaten, L. van der. (2009). Learning a Parametric Embedding by
@@
 
-\leavevmode\hypertarget{ref-Machen2021ThiAlg}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Machen2021ThiAlg}{}}%
 Machen, R., \& Nost, E. (2021). Thinking algorithmically: The making of
@@
 
-\leavevmode\hypertarget{ref-Malaterre2019FunDiv}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Malaterre2019FunDiv}{}}%
 Malaterre, C., Dussault, A. C., Mermans, E., Barker, G., Beisner, B. E.,
@@
 
-\leavevmode\hypertarget{ref-McLeod2021SamAsy}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-McLeod2021SamAsy}{}}%
 McLeod, A., Leroux, S. J., Gravel, D., Chu, C., Cirtwill, A. R., Fortin,
@@
 
-\leavevmode\hypertarget{ref-Melnyk2020GraGra}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Melnyk2020GraGra}{}}%
 Melnyk, K., Klus, S., Montavon, G., \& Conrad, T. O. F. (2020).
@@
 
-\leavevmode\hypertarget{ref-Morales-Castilla2015InfBio}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Morales-Castilla2015InfBio}{}}%
 Morales-Castilla, I., Matias, M. G., Gravel, D., \& Araújo, M. B.
@@
 
-\leavevmode\hypertarget{ref-Morand1998DenBod}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Morand1998DenBod}{}}%
 Morand, S., \& Poulin, R. (1998). Density, body mass and parasite
@@
 
-\leavevmode\hypertarget{ref-MoseboFernandes2020MacLea}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-MoseboFernandes2020MacLea}{}}%
 Mosebo Fernandes, A. C., Quintero Gonzalez, R., Lenihan-Clarke, M. A.,
@@
 
-\leavevmode\hypertarget{ref-Murphy2022ProMac}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Murphy2022ProMac}{}}%
 Murphy, K. P. (2022). \emph{Probabilistic machine learning: An
@@
 
-\leavevmode\hypertarget{ref-Naman2022FooWeb}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Naman2022FooWeb}{}}%
 Naman, S. M., White, S. M., Bellmore, J. R., McHugh, P. A., Kaylor, M.
@@
 
-\leavevmode\hypertarget{ref-Narayanan2017GraLea}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Narayanan2017GraLea}{}}%
 Narayanan, A., Chandramohan, M., Venkatesan, R., Chen, L., Liu, Y., \&
@@
 
-\leavevmode\hypertarget{ref-Neutel2002StaRea}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Neutel2002StaRea}{}}%
 Neutel, A.-M., Heesterbeek, J. A. P., \& de Ruiter, P. C. (2002).
@@
 
-\leavevmode\hypertarget{ref-Nokmaq2021AwaSle}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Nokmaq2021AwaSle}{}}%
 No'kmaq, M., Marshall, A., Beazley, K. F., Hum, J., joudry, shalan,
@@
 
-\leavevmode\hypertarget{ref-Nost2021PolEco}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Nost2021PolEco}{}}%
 Nost, E., \& Goldstein, J. E. (2021). A political ecology of data.
@@
 
-\leavevmode\hypertarget{ref-OConnor2020UnvFoo}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-OConnor2020UnvFoo}{}}%
 O'Connor, L. M. J., Pollock, L. J., Braga, J., Ficetola, G. F.,
@@
 
-\leavevmode\hypertarget{ref-Pedersen2017SigCol}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Pedersen2017SigCol}{}}%
 Pedersen, E. J., Thompson, P. L., Ball, R. A., Fortin, M.-J., Gouhier,
@@
 
-\leavevmode\hypertarget{ref-Perozzi2014DeeOnl}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Perozzi2014DeeOnl}{}}%
 Perozzi, B., Al-Rfou, R., \& Skiena, S. (2014). DeepWalk: Online
@@
 
-\leavevmode\hypertarget{ref-Pichler2020MacLea}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Pichler2020MacLea}{}}%
 Pichler, M., Boreux, V., Klein, A.-M., Schleuning, M., \& Hartig, F.
@@
 
-\leavevmode\hypertarget{ref-Poisot2019EcoJl}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Poisot2019EcoJl}{}}%
 Poisot, T., Belisle, Z., Hoebeke, L., Stock, M., \& Szefer, P. (2019).
@@
 
-\leavevmode\hypertarget{ref-Poisot2016StrPro}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Poisot2016StrPro}{}}%
 Poisot, T., Cirtwill, A. R., Cazelles, K., Gravel, D., Fortin, M.-J., \&
@@
 
-\leavevmode\hypertarget{ref-Poisot2021ImpMam}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Poisot2021ImpMam}{}}%
 Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M. J., Becker, D.
@@
 
-\leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Poisot2015SpeWhy}{}}%
 Poisot, T., Stouffer, D. B., \& Gravel, D. (2015). Beyond species: Why
@@
 
-\leavevmode\hypertarget{ref-Ramasamy2015ComSpe}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Ramasamy2015ComSpe}{}}%
 Ramasamy, D., \& Madhow, U. (2015). Compressive spectral embedding:
@@
 
-\leavevmode\hypertarget{ref-Ray2021BioCri}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Ray2021BioCri}{}}%
 Ray, J. C., Grimm, J., \& Olive, A. (2021). The biodiversity crisis in
@@
 
-\leavevmode\hypertarget{ref-Runghen2021ExpNod}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Runghen2021ExpNod}{}}%
 Runghen, R., Stouffer, D. B., \& Dalla Riva, G. V. (2021).
@@
 
-\leavevmode\hypertarget{ref-S2013GraEmb}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-S2013GraEmb}{}}%
 S, N. S., \& Surendran, S. (2013). Graph Embedding and Dimensionality
@@
 
-\leavevmode\hypertarget{ref-Saravia2021EcoNet}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Saravia2021EcoNet}{}}%
 Saravia, L. A., Marina, T. I., Kristensen, N. P., De Troch, M., \& Momo,
@@
 
-\leavevmode\hypertarget{ref-Stevenson2021AlgRis}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Stevenson2021AlgRis}{}}%
 Stevenson, M. T., \& Doleac, J. L. (2021). \emph{Algorithmic Risk
@@
 
-\leavevmode\hypertarget{ref-Stier2017IntExp}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Stier2017IntExp}{}}%
 Stier, A. C., Samhouri, J. F., Gray, S., Martone, R. G., Mach, M. E.,
@@
 
-\leavevmode\hypertarget{ref-Stouffer2007EviExi}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2007EviExi}{}}%
 Stouffer, D. B., Camacho, J., Jiang, W., \& Nunes Amaral, L. A. (2007).
@@
 
-\leavevmode\hypertarget{ref-Stouffer2012EvoCon}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2012EvoCon}{}}%
 Stouffer, D. B., Sales-Pardo, M., Sirer, M. I., \& Bascompte, J. (2012).
@@
 
-\leavevmode\hypertarget{ref-Strydom2022FooWeb}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Strydom2022FooWeb}{}}%
 Strydom, T., Bouskila, S., Banville, F., Barros, C., Caron, D., Farrell,
@@
 
-\leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021RoaPre}{}}%
 Strydom, T., Catchen, M. D., Banville, F., Caron, D., Dansereau, G.,
@@
 
-\leavevmode\hypertarget{ref-Strydom2021SvdEnt}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021SvdEnt}{}}%
 Strydom, T., Dalla Riva, G. V., \& Poisot, T. (2021). SVD Entropy
@@
 
-\leavevmode\hypertarget{ref-Tang2015LinLar}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Tang2015LinLar}{}}%
 Tang, J., Qu, M., Wang, M., Zhang, M., Yan, J., \& Mei, Q. (2015). LINE:
@@
 
-\leavevmode\hypertarget{ref-Thurman2019TesLin}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Thurman2019TesLin}{}}%
 Thurman, L. L., Barner, A. K., Garcia, T. S., \& Chestnut, T. (2019).
@@
 
-\leavevmode\hypertarget{ref-Torres2020GleGeo}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Torres2020GleGeo}{}}%
 Torres, L., Chan, K. S., \& Eliassi-Rad, T. (2020). GLEE: Geometric
@@
 
-\leavevmode\hypertarget{ref-Turak2017UsiEss}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Turak2017UsiEss}{}}%
 Turak, E., Brazill-Boast, J., Cooney, T., Drielsma, M., DelaCruz, J.,
@@
 
-\leavevmode\hypertarget{ref-Wang2016StrDee}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Wang2016StrDee}{}}%
 Wang, D., Cui, P., \& Zhu, W. (2016). Structural Deep Network Embedding.
@@
 
-\leavevmode\hypertarget{ref-Wang2021JoiEmb}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Wang2021JoiEmb}{}}%
 Wang, S., Arroyo, J., Vogelstein, J. T., \& Priebe, C. E. (2021). Joint
@@
 
-\leavevmode\hypertarget{ref-Wardeh2021PreMam}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Wardeh2021PreMam}{}}%
 Wardeh, M., Baylis, M., \& Blagrove, M. S. C. (2021). Predicting
@@
 
-\leavevmode\hypertarget{ref-Weiskopf2022IncUpt}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Weiskopf2022IncUpt}{}}%
 Weiskopf, S. R., Harmáčková, Z. V., Johnson, C. G., Londoño-Murcia, M.
@@
 
-\leavevmode\hypertarget{ref-Wood2015EffSpa}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Wood2015EffSpa}{}}%
 Wood, S. A., Russell, R., Hanson, D., Williams, R. J., \& Dunne, J. A.
@@
 
-\leavevmode\hypertarget{ref-Wu2021MaxPos}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Wu2021MaxPos}{}}%
 Wu, D., Palmer, D. R., \& Deford, D. R. (2021). \emph{Maximum a
@@
 
-\leavevmode\hypertarget{ref-Xu2021UndGra}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Xu2021UndGra}{}}%
 Xu, M. (2021). Understanding Graph Embedding Methods and Their
@@
 
-\leavevmode\hypertarget{ref-Yan2005GraEmb}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Yan2005GraEmb}{}}%
 Yan, S., Xu, D., Zhang, B., \& Zhang, H.-J. (2005). Graph embedding: A
@@
 
-\leavevmode\hypertarget{ref-Young2007RanDot}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Young2007RanDot}{}}%
 Young, S. J., \& Scheinerman, E. R. (2007). Random Dot Product Graph
@@
 
-\leavevmode\hypertarget{ref-Zhou2020GraNeu}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Zhou2020GraNeu}{}}%
 Zhou, J., Cui, G., Hu, S., Zhang, Z., Yang, C., Liu, Z., Wang, L., Li,

### 2023-01-24 Strydom_et_al_2023_graph_embedding_preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@32377dfbc750a8864f2ea754d587f4308f4fb1f0 🚀

--- 2023-01-24 Strydom_et_al_2023_graph_embedding_draft.tex
@@
 \newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}
-
-\usepackage{lineno}
-\usepackage[nolists,noheads]{endfloat}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}
+
+\geometry{includemp,
+            letterpaper,
+            top=2.4cm,
+            bottom=2.4cm,
+            left=1.0cm,
+            right=1.0cm,
+            marginparwidth=5cm,
+            marginparsep=1.0cm}
+
+\usepackage[singlelinecheck=off]{caption}
+
+\captionsetup{
+  font={small},
+  labelfont={bf},
+  format=plain,
+  labelsep=quad
+}
+
+\usepackage{floatrow}
+
+\floatsetup[figure]{margins=hangright,
+              facing=no,
+              capposition=beside,
+              capbesideposition={center,outside},
+              floatwidth=\textwidth}
+
+% \floatsetup[table]{margins=hangright,
+%              facing=no,
+%              capposition=beside,
+%              capbesideposition={center,outside},
+%              floatwidth=\textwidth}
 
@@
 
-\tolerance=1
-\emergencystretch=\maxdimen
-\hyphenpenalty=10000
-\hbadness=10000
-
-\doublespacing
+\setcounter{secnumdepth}{5}
+
+\usepackage{titlesec}
+
+\titleformat{\section}[block]
+{\normalfont\large\sffamily}
+{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}
+
+\titleformat{\subsection}[runin]
+{\normalfont\fontseries{b}\selectfont\filright\sffamily}
+{\thesubsection.}{.5em}{}
+
+\titleformat{\subsubsection}[runin]
+{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}
+
+\fancypagestyle{firstpage}
+{
+   \fancyhf{}
+   \renewcommand{\headrulewidth}{0pt}
+   \fancyfoot[R]{\footnotesize\ccby}
+   \fancyfoot[L]{\footnotesize\sffamily\today}
+}
 
@@
 }
+
+\usepackage{tikz}
 \begin{document}
-\raggedright
-\thispagestyle{empty}
-{\Large\bfseries\sffamily Graph embedding and transfer learning can help
-predict species interaction networks despite data limitations}
-\vskip 5em
-
+\tikz [remember picture, overlay] %
+\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
+\pagestyle{normal}
+\thispagestyle{firstpage}
+
+\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}
+
+\noindent {\LARGE \textbf{\textsf{Graph embedding and transfer learning
+can help predict species interaction networks despite data
+limitations}}}
+
+\medskip
+\begin{flushleft}
+{\small
 %
@@
 %
-\,\textsuperscript{1,2,‡}\quad %
+\,\textsuperscript{1,2,‡}, %
 \href{https://orcid.org/0000-0003-0193-5441}{Salomé\,Bouskila}%
 %
-\,\textsuperscript{1,‡}\quad %
+\,\textsuperscript{1,‡}, %
 \href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
 %
-\,\textsuperscript{1,2,3}\quad %
+\,\textsuperscript{1,2,3}, %
 \href{https://orcid.org/0000-0003-4036-977X}{Ceres\,Barros}%
 %
-\,\textsuperscript{4}\quad %
+\,\textsuperscript{4}, %
 \href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
 %
-\,\textsuperscript{2,5}\quad %
+\,\textsuperscript{2,5}, %
 \href{https://orcid.org/0000-0003-0452-6993}{Maxwell J\,Farrell}%
 %
-\,\textsuperscript{6}\quad %
+\,\textsuperscript{6}, %
 \href{https://orcid.org/0000-0002-9935-1366}{Marie-Josée\,Fortin}%
 %
-\,\textsuperscript{6}\quad %
+\,\textsuperscript{6}, %
 \href{https://orcid.org/0000-0003-3220-6161}{Victoria\,Hemming}%
 %
-\,\textsuperscript{7}\quad %
+\,\textsuperscript{7}, %
 \href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
 %
-\,\textsuperscript{2,3}\quad %
+\,\textsuperscript{2,3}, %
 \href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
 %
-\,\textsuperscript{2,5}\quad %
+\,\textsuperscript{2,5}, %
 \href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
 %
-\,\textsuperscript{8}\quad %
+\,\textsuperscript{8}, %
 \href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
 %
-\,\textsuperscript{9}\quad %
+\,\textsuperscript{9}, %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
@@
 \,\textsuperscript{1,2,‡}
-
+\vskip 1em
 \textsuperscript{1}\,Département de Sciences Biologiques, Université de
-Montréal, Montréal, Canada\quad \textsuperscript{2}\,Quebec Centre for
-Biodiversity Science, Montréal,
-Canada\quad \textsuperscript{3}\,Département de Biologie, Université de
-Sherbrooke, Sherbrooke, Canada\quad \textsuperscript{4}\,Department of
-Forest Resources Management, University of British Columbia, Vancouver,
-B.C., Canada\quad \textsuperscript{5}\,Department of Biology, McGill
-University, Montréal, Canada\quad \textsuperscript{6}\,Department of
-Ecology \& Evolutionary Biology, University of Toronto, Toronto,
-Canada\quad \textsuperscript{7}\,Department of Forest and Conservation
+Montréal, Montréal, Canada; \textsuperscript{2}\,Quebec Centre for
+Biodiversity Science, Montréal, Canada; \textsuperscript{3}\,Département
+de Biologie, Université de Sherbrooke, Sherbrooke,
+Canada; \textsuperscript{4}\,Department of Forest Resources Management,
+University of British Columbia, Vancouver, B.C.,
+Canada; \textsuperscript{5}\,Department of Biology, McGill University,
+Montréal, Canada; \textsuperscript{6}\,Department of Ecology \&
+Evolutionary Biology, University of Toronto, Toronto,
+Canada; \textsuperscript{7}\,Department of Forest and Conservation
 Sciences, University of British Columbia, Vancouver,
-Canada\quad \textsuperscript{8}\,Centre for Integrative Ecology, School
-of Biological Sciences, University of Canterbury, Canterbury, New
-Zealand\quad \textsuperscript{9}\,School of Mathematics and Statistics,
-University of Canterbury, Canterbury, New Zealand
-
+Canada; \textsuperscript{8}\,Centre for Integrative Ecology, School of
+Biological Sciences, University of Canterbury, Canterbury, New
+Zealand; \textsuperscript{9}\,School of Mathematics and Statistics,
+University of Canterbury, Canterbury, New Zealand\\
 \textsuperscript{‡}\,Equal contributions\\
-
+\vskip 1em
 \textbf{Correspondance to:}\\
 Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
-
-\vfill
+}
+\end{flushleft}
+
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
+\noindent
+
+\marginpar{\vskip 1em\flushright
+{\small{\bfseries Keywords}:\par
+ecological networks\\network embedding\\transfer learning\\network
+macroecology\\}
+}
 
@@
 
-\vfill
-This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
-Last revision: \emph{\today}
-
-\clearpage
-\thispagestyle{empty}
-
-\vfill
-
-\vfill
-
-\clearpage
-\linenumbers
-\pagestyle{normal}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
 

### 2023-01-24 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@82ac41a1e8ba572b95aabaf0d231ab73f1c01a50 🚀

@@
 dependency of food web structure will lead to more prescriptive
-guidelines about the need for prediction downscaling.
+guidelines about the need for prediction downscaling. Recent results by
+(\textbf{Martins2022GloReg?}) suggest that networks are shaped within
+eco-regions, with abrupt structural transitions from an eco-region to
+the next. Should this trend hold generally, this would provide an
+ecologically-relevant scale at which metawebs can be downscaled and
+predicted.
 
@@
 unwittingly propagated to algorithms when embedded from the original
-data is paramount. Predictive approaches deployed at the continental
-scale, no matter their intent, originate in the framework that
-contributed to the ongoing biodiversity crisis (Adam, 2014) and
+data is paramount. These considerations are even more urgent in the
+specific context of biodiversity data, as long-term colonial legacies
+still shape taxonomic composition to this day
+(\textbf{Lenzner2022NatAli?}; \textbf{Raja2022ColSha?}), and where much
+shorter-term changes in taxonomic and genetic richness emerged as a
+consequence of environmental racism. (\textbf{Schmidt2022SysRac?}).
+
+Predictive approaches, regardless of the scale at which they are
+deployed and the intent of their deployment, originate in the framework
+that contributed to the ongoing biodiversity crisis (Adam, 2014) and
 reinforced environmental injustice (Choudry, 2013; Domínguez \& Luoma,

### 2023-01-24 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@769f8d08213a74eb01c156b8aa2c72a1600175b0 🚀

@@
 structure, which at least for food webs have been well documented (Dalla
-Riva \& Stouffer, 2016; Stouffer et al., 2012; Stouffer et al., 2007);
-similarly, the use of functional traits assumes that interactions can be
-inferred from the knowledge of trait-matching rules, which is similarly
-well supported in the empirical literature (Bartomeus, 2013; Bartomeus
-et al., 2016; Gravel et al., 2013). Relating this information to an
-embedding rather than a list of networks measures would allow to capture
-their effect on the more fundamental aspects of network structure;
-conversely, the absence of a phylogenetic or functional signal may
-suggest that evolutionary/trait processes are not strong drivers of
-network structure, therefore opening a new way to perform hypothesis
-testing.
+Riva \& Stouffer, 2016; Stouffer et al., 2012;
+\textbf{Stouffer2007EviExi?}); similarly, the use of functional traits
+assumes that interactions can be inferred from the knowledge of
+trait-matching rules, which is similarly well supported in the empirical
+literature (Bartomeus, 2013; Bartomeus et al., 2016;
+\textbf{Gravel2013InfFoo?}). Relating this information to an embedding
+rather than a list of networks measures would allow to capture their
+effect on the more fundamental aspects of network structure; conversely,
+the absence of a phylogenetic or functional signal may suggest that
+evolutionary/trait processes are not strong drivers of network
+structure, therefore opening a new way to perform hypothesis testing.
 
@@
 guidelines about the need for prediction downscaling. Recent results by
-(\textbf{Martins2022GloReg?}) suggest that networks are shaped within
+Martins et al. (2022) suggest that networks are shaped within
 eco-regions, with abrupt structural transitions from an eco-region to
@@
 specific context of biodiversity data, as long-term colonial legacies
-still shape taxonomic composition to this day
-(\textbf{Lenzner2022NatAli?}; \textbf{Raja2022ColSha?}), and where much
-shorter-term changes in taxonomic and genetic richness emerged as a
-consequence of environmental racism. (\textbf{Schmidt2022SysRac?}).
+still shape taxonomic composition to this day (Lenzner et al., 2022;
+Raja, 2022), and where much shorter-term changes in taxonomic and
+genetic richness emerged as a consequence of environmental racism.
+(Schmidt \& Garroway, 2022).
 
@@
 Gravel, D. (2019). The marine fish food web is globally connected.
-\emph{Nature Ecology \& Evolution}, \emph{3}(8, 8), 1153--1161.
+\emph{Nature Ecology \& Evolution}, \emph{3}(8), 1153--1161.
 \url{https://doi.org/10.1038/s41559-019-0950-y}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Arsov2019NetEmb}{}}%
-Arsov, N., \& Mirceva, G. (2019). \emph{Network Embedding: An Overview}.
-\url{http://arxiv.org/abs/1911.11726}
+Arsov, N., \& Mirceva, G. (2019). Network Embedding: An Overview.
+\emph{arXiv:1911.11726 {[}Cs, Stat{]}}.
+\url{https://arxiv.org/abs/1911.11726}
 
@@
 survey} (No. arXiv:1709.05454). arXiv.
-\url{http://arxiv.org/abs/1709.05454}
+\url{https://arxiv.org/abs/1709.05454}
 
@@
 detectability and plant traits. \emph{PloS One}, \emph{8}(7), e69200.
-\url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0069200}
 
@@
 Ecology}, \emph{30}(12), 1894--1903.
-\url{http://onlinelibrary.wiley.com/doi/10.1111/1365-2435.12666/full}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Bezanson2017JulFre}{}}%
-Bezanson, J., Edelman, A., Karpinski, S., \& Shah, V. (2017). Julia: A
-Fresh Approach to Numerical Computing. \emph{SIAM Review}, \emph{59}(1),
-65--98. \url{https://doi.org/10.1137/141000671}
+Bezanson, J., Edelman, A., Karpinski, S., \& Shah, V. B. (2017). Julia:
+A Fresh Approach to Numerical Computing. \emph{SIAM Review},
+\emph{59}(1), 65--98. \url{https://doi.org/10.1137/141000671}
 
@@
 \emph{Journal of Machine Learning Research}, \emph{23}(89), 1--64.
-\url{http://jmlr.org/papers/v23/20-852.html}
 
@@
 \emph{Deep Multi-species Embedding}. 3639--3646.
-\url{https://www.ijcai.org/proceedings/2017/509}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Chen2017HarHie}{}}%
-Chen, H., Perozzi, B., Hu, Y., \& Skiena, S. (2017). \emph{HARP:
-Hierarchical Representation Learning for Networks}.
-\url{http://arxiv.org/abs/1706.07845}
+Chen, H., Perozzi, B., Hu, Y., \& Skiena, S. (2017). HARP: Hierarchical
+Representation Learning for Networks. \emph{arXiv:1706.07845 {[}Cs{]}}.
+\url{https://arxiv.org/abs/1706.07845}
 
@@
 Indigenous Injustices at the Expense of the Environment. \emph{Land},
-\emph{9}(3, 3), 65. \url{https://doi.org/10.3390/land9030065}
+\emph{9}(3), 65. \url{https://doi.org/10.3390/land9030065}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gravel2013InfFoo}{}}%
-Gravel, D., Poisot, T., Albouy, C., Velez, L., \& Mouillot, D. (2013).
-Inferring food web structure from predator-prey body size relationships.
-\emph{Methods in Ecology and Evolution}, \emph{4}(11), 1083--1090.
-\url{https://doi.org/10.1111/2041-210X.12103}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Green2019DisInt}{}}%
@@
 and suitability overlap under climate change. \emph{Communications
-Biology}, \emph{3}(1, 1), 1--10.
+Biology}, \emph{3}(1), 1--10.
 \url{https://doi.org/10.1038/s42003-020-0962-9}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Herbert1965Dun}{}}%
-Herbert, F. (1965). \emph{Dune} (1st ed.). Chilton Book Company.
+Herbert, F. (1965). \emph{Dune} (First). Chilton Book Company.
 
@@
 Price, S. A., Rigby, E. A., Rist, J., \ldots{} Purvis, A. (2009).
-PanTHERIA: A species‐level database of life history, ecology, and
+PanTHERIA: A species-level database of life history, ecology, and
 geography of extant and recently extinct mammals: Ecological Archives
-E090‐184. \emph{Ecology}, \emph{90}(9), 2648--2648.
+E090-184. \emph{Ecology}, \emph{90}(9), 2648--2648.
 \url{https://doi.org/10.1890/08-1494.1}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Lenzner2022NatAli}{}}%
+Lenzner, B., Latombe, G., Schertler, A., Seebens, H., Yang, Q., Winter,
+M., Weigelt, P., van Kleunen, M., Pyšek, P., Pergl, J., Kreft, H.,
+Dawson, W., Dullinger, S., \& Essl, F. (2022). Naturalized alien floras
+still carry the legacy of European colonialism. \emph{Nature Ecology \&
+Evolution}, 1--10. \url{https://doi.org/10.1038/s41559-022-01865-1}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Maaten2009LeaPar}{}}%
@@
 International Conference on Artificial Intelligence and Statistics},
-384--391. \url{https://proceedings.mlr.press/v5/maaten09a.html}
+384--391.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Martins2022GloReg}{}}%
+Martins, L. P., Stouffer, D. B., Blendinger, P. G., Böhning-Gaese, K.,
+Buitrón-Jurado, G., Correia, M., Costa, J. M., Dehling, D. M., Donatti,
+C. I., Emer, C., Galetti, M., Heleno, R., Jordano, P., Menezes, Í.,
+Morante-Filho, J. C., Muñoz, M. C., Neuschulz, E. L., Pizo, M. A.,
+Quitián, M., \ldots{} Tylianakis, J. M. (2022). Global and regional
+ecological boundaries explain abrupt spatial discontinuities in avian
+frugivory interactions. \emph{Nature Communications}, \emph{13}(1),
+6943. \url{https://doi.org/10.1038/s41467-022-34355-w}
+
 \leavevmode\vadjust pre{\hypertarget{ref-McLeod2021SamAsy}{}}%
@@
 for Conservation Planning in a Changing Climate. \emph{Sustainability},
-\emph{12}(18, 18), 7657. \url{https://doi.org/10.3390/su12187657}
+\emph{12}(18), 7657. \url{https://doi.org/10.3390/su12187657}
 
@@
 Narayanan, A., Chandramohan, M., Venkatesan, R., Chen, L., Liu, Y., \&
-Jaiswal, S. (2017). \emph{Graph2vec: Learning Distributed
-Representations of Graphs}. \url{http://arxiv.org/abs/1707.05005}
+Jaiswal, S. (2017). Graph2vec: Learning Distributed Representations of
+Graphs. \emph{arXiv:1707.05005 {[}Cs{]}}.
+\url{https://arxiv.org/abs/1707.05005}
 
@@
 J., Albery, G. F., Gibb, R. J., Seifert, S. N., \& Carlson, C. J.
-(2021). \emph{Imputing the mammalian virome with linear filtering and
-singular value decomposition}. \url{http://arxiv.org/abs/2105.14973}
+(2021). Imputing the mammalian virome with linear filtering and singular
+value decomposition. \emph{arXiv:2105.14973 {[}q-Bio{]}}.
+\url{https://arxiv.org/abs/2105.14973}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Raja2022ColSha}{}}%
+Raja, N. B. (2022). Colonialism shaped today's biodiversity.
+\emph{Nature Ecology \& Evolution}, 1--2.
+\url{https://doi.org/10.1038/s41559-022-01903-y}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Ramasamy2015ComSpe}{}}%
@@
 Engineering Technology}, \emph{4}(1).
-\url{https://www.semanticscholar.org/paper/Graph-Embedding-and-Dimensionality-Reduction-A-Surendran/3f413d591e4b2b876e033eeb9390e232ad4826ca}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Schmidt2022SysRac}{}}%
+Schmidt, C., \& Garroway, C. J. (2022). Systemic racism alters wildlife
+genetic diversity. \emph{Proceedings of the National Academy of
+Sciences}, \emph{119}(43), e2102860119.
+\url{https://doi.org/10.1073/pnas.2102860119}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Stevenson2021AlgRis}{}}%
 Stevenson, M. T., \& Doleac, J. L. (2021). \emph{Algorithmic Risk
-Assessment in the Hands of Humans} (SSRN Scholarly Paper No. 3489440).
-\url{https://doi.org/10.2139/ssrn.3489440}
+Assessment in the Hands of Humans} (\{\{SSRN Scholarly Paper\}\} No.
+3489440). \url{https://doi.org/10.2139/ssrn.3489440}
 
@@
 \url{https://doi.org/10.1111/conl.12245}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2007EviExi}{}}%
-Stouffer, D. B., Camacho, J., Jiang, W., \& Nunes Amaral, L. A. (2007).
-Evidence for the existence of a robust pattern of prey selection in food
-webs. \emph{Proceedings of the Royal Society B: Biological Sciences},
-\emph{274}(1621), 1931--1940.
-\url{https://doi.org/10.1098/rspb.2007.0571}
 
@@
 Testing the link between species interactions and co-occurrence in a
-trophic network. \emph{Ecography}, \emph{0}.
+trophic network. \emph{Ecography}, \emph{0}(ja).
 \url{https://doi.org/10.1111/ecog.04360}
@@
 mammalian hosts in which novel coronaviruses can be generated.
-\emph{Nature Communications}, \emph{12}(1, 1), 780.
+\emph{Nature Communications}, \emph{12}(1), 780.
 \url{https://doi.org/10.1038/s41467-021-21034-5}
@@
 Posteriori Inference of Random Dot Product Graphs via Conic Programming}
-(No. arXiv:2101.02180). arXiv. \url{http://arxiv.org/abs/2101.02180}
+(No. arXiv:2101.02180). arXiv. \url{https://arxiv.org/abs/2101.02180}
 

### 2023-01-24 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@2a1f16b72dc7d9c83e6211b0433d8904ab134298 🚀

@@
 \begin{enumerate}
-    \itemMetawebs, (networks of potential interactions within a species
+    \item Metawebs, (networks of potential interactions within a species
 pool) are a powerful abstraction to understand how large-scale species
 interaction networks are structured.%
-    \itemBecause metawebs are typically expressed at large spatial and
+    \item Because metawebs are typically expressed at large spatial and
 taxonomic scales, assembling them is a tedious and costly process;
@@
 deficiencies, by providing `draft' metawebs.%
-    \itemOne way to improve our ability to predict metawebs is to
+    \item One way to improve our ability to predict metawebs is to
 maximize available information by using graph embeddings, instead of the
@@
 machine learning that holds great potential for ecological problems.%
-    \itemIn this perspective, we outline how the challenges associated
+    \item In this perspective, we outline how the challenges associated
 with inferring metawebs line-up with the advantages of graph embeddings;

### 2023-01-25 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@026f64e8b2ee9a7eeddbf48f484c413be77d2a4e 🚀

@@
 %
-\,\textsuperscript{1,‡}\quad %
+\,\textsuperscript{1}\quad %
 \href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
@@
 \caption{The embedding process (\textbf{A}) can help to identify links
-(interactions) that may have been missed within the current sample
-(community, \textbf{B}), while transfer learning (\textbf{D}) allows for
-predicting links (interactions) for species external to the original
-sample as well as within sample links (\textbf{F}). Transfer learning
+(interactions) that may have been missed within the original community
+(represented by the orange dashed lines, \textbf{B}). Transfer learning
 allows for the prediction links (interactions) when novel species
-(\textbf{C}) are included in the sample by learning using other relevant
-predictors (e.g.~traits) in conjunction with the known interactions to
-infer latent values (\textbf{E}). Within this context the predicted
-networks as well as the ecological predictors used (green boxes) are
-products that can be quantified through field measurements, whereas the
-embedded as well as imputed matrices are representative of
-\textbf{TK}}\label{fig:embedding}
+(\textbf{C}) are included alongside the original community (\textbf{D}).
+This is achieved by learning using other relevant predictors
+(\emph{e.g.} traits) in conjunction with the known interactions to infer
+latent values (\textbf{E}). Ultimately this allows us to predict links
+(interactions) for species external to the original sample as well as
+within sample links (\textbf{F}). Within this context the predicted (and
+original) networks as well as the ecological predictors used (green
+boxes) are products that can be quantified through field measurements,
+whereas the embedded as well as imputed matrices are representative of a
+decomposition of the interaction networks}\label{fig:embedding}
 }

### 2023-01-25 Strydom_et_al_2023_graph_embedding_preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@026f64e8b2ee9a7eeddbf48f484c413be77d2a4e 🚀

@@
 %
-\,\textsuperscript{1,‡}, %
+\,\textsuperscript{1}, %
 \href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%

### 2023-01-25 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@c1b6843af19aa07ac594d30f93b6f812201d80f0 🚀

@@
 boxes) are products that can be quantified through field measurements,
-whereas the embedded as well as imputed matrices are representative of a
-decomposition of the interaction networks}\label{fig:embedding}
+whereas the embedded as well as imputed matrices (purple box) are
+representative of a decomposition of the interaction
+networks}\label{fig:embedding}
 }

### 2023-01-25 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@347a9937e2eb5fc9f006894aadc63420e927d746 🚀

@@
 al., 2018), fish trophic interactions (Albouy et al., 2019), tetrapod
-trophic interactions (Braga et al., 2019; O'Connor et al., 2020), and
+trophic interactions (J. Braga et al., 2019; O'Connor et al., 2020), and
 crop-pest networks (Grünig et al., 2020). In this contribution, we
@@
 \emph{e.g.} trait mis-match), and interactions with a probability that
-lays somewhere in between. In a sense, that most ecological interactions
-are elusive can call for a slightly different approach to sampling: once
-the common interactions are documented, the effort required in
-documenting each rare interaction will increase exponentially (Jordano,
-2016). Recent proposals in other fields emphasize the idea that machine
-learning algorithms can also act as data generators (Hoffmann et al.,
-2019): high quality observational data can be used to infer core rules
+lays somewhere in between (Catchen et al., 2023). In a sense, that most
+ecological interactions are elusive can call for a slightly different
+approach to sampling: once the common interactions are documented, the
+effort required in documenting each rare interaction will increase
+exponentially (Jordano, 2016). Recent proposals in other fields relying
+on machine learning approaches emphasize the idea that algorithms meant
+to predict, through the assumption that they approximate the process
+generating the data, can also act as data generators (Hoffmann et al.,
+2019). High quality observational data can be used to infer core rules
 underpinning network structure, and be supplemented with synthetic data
@@
 yet has possibly the most potential to boost our predictive ability
-(Bartomeus et al., 2016).
+(Bartomeus, 2013; Bartomeus et al., 2016). This would represent a
+departure from simple rules expressed at the network scale (\emph{e.g.}
+Williams \& Martinez, 2000) to a view of network prediction based on
+learning the rules that underpin interactions \emph{and} their
+variability (Gupta et al., 2022).
 
@@
 machine learning techniques, whose main task is to learn a mapping
-function from a discrete graph to a continuous domain (Arsov \& Mirceva,
-2019; Chami et al., 2022). Their main goal is to learn a low dimensional
-vector representations for the nodes of the graph (embeddings), such
-that key properties of the graph (e.g.~local or global structures) are
-retained in the embedding space (Yan et al., 2005). Ecological networks
-are an interesting candidate for the widespread application of
-embeddings, as they tend to possess a shared structural backbone (see
-\emph{e.g.} Bramon Mora et al., 2018 for food webs), which hints at
-structural invariants in empirical data; assuming that these structural
-invariants are indeed widespread, they would dominate the structure of
-networks, and therefore be adequately captured by the first (lower)
-dimensions of an embedding, without the need to measure derived aspects
-of their structure (\emph{e.g.} motifs, paths, modularity, \ldots).
+function from a discrete graph to a continuous domain (Chami et al.,
+2022; \textbf{arsov\_network\_2019?}). Their main goal is to learn a low
+dimensional vector representations of the graph (embeddings), such that
+its key properties (\emph{e.g.} local or global structures) are retained
+in the embedding space (Yan et al., 2005). The embedding space may, but
+will not necessarily, have lower dimensionality than the graph.
+Ecological networks are promising candidates for the routine application
+of embeddings, as they tend to possess a shared structural backbone (see
+\emph{e.g.} Bramon Mora et al., 2018), which hints at structural
+invariants in empirical data. Assuming that these structural invariants
+are common enough, they would dominate the structure of networks, and
+therefore be adequately captured by the first (lower) dimensions of an
+embedding, without the need to measure derived aspects of their
+structure (\emph{e.g.} motifs, paths, modularity, \ldots).
 
 Indeed, food webs are inherently low-dimensional objects, and can be
-adequately represented with less than ten dimensions (Braga et al.,
-2019; Eklöf et al., 2013). Simulation results by Botella et al. (2022)
-suggest that there is no best method to identify architectural
-similarities between networks, and that multiple approaches need to be
-tested and compared to the network descriptor of interest. This matches
-previous, more general results on graph embedding, which suggest that
-different embedding algorithms yield different network embeddings (Goyal
-\& Ferrara, 2018), calling for a careful selection of the
-problem-specific approach to use. In tbl.~\ref{tbl:methods}, we present
-a selection of common graph and node embedding methods, alongside
-examples of their use to predict species interactions; most of these
-methods rely either on linear algebra, or on pseudo-random walks on
-graphs. All forms of embeddings presented in the table share the common
-property of summarizing their objects into (sets of) dense feature
-vectors, that capture the overall network structure, pairwise
-information on nodes, and emergent aspects of the network, in a
-compressed way (\emph{i.e.} with some information loss, as we later
-discuss in the illustration). Node embeddings tend to focus on
-maintaining pairwise relationships, while graph embeddings focus on
-maintaining the network structure. Nevertheless, some graph embedding
-techniques (like RDPG, see \emph{e.g.} Wu et al., 2021) will provide
-usable node-level embeddings.
+adequately represented with less than ten dimensions (J. Braga et al.,
+2019; M. P. Braga et al., 2021; Eklöf et al., 2013). Simulation results
+by Botella et al. (2022) suggests that there is no dominant method to
+identify architectural similarities between networks: multiple
+approaches need to be tested and compared to the network descriptor of
+interest on a problem-specific basis. This matches previous results on
+graph embedding, wherein different embedding algorithms yield different
+network embeddings (Goyal \& Ferrara, 2018), calling for a careful
+selection of the problem-specific approach to use. In
+tbl.~\ref{tbl:methods}, we present a selection of common graph and node
+embedding methods, alongside examples of their use to predict
+interactions or statistical associations between species. These methods
+rely largely on linear algebra or pseudo-random walks on graphs. All
+forms of embeddings presented in the table share the common property of
+summarizing their objects into (sets of) dense feature vectors, that
+capture the overall network structure, pairwise information on nodes,
+and emergent aspects of the network, in a compressed way (\emph{i.e.}
+with some information loss, as we later discuss in the illustration).
+Node embeddings tend to focus on maintaining pairwise relationships
+(\emph{i.e.} species interactions), while graph embeddings focus on
+maintaining the network structure (\emph{i.e.} emergent properties).
+Nevertheless, some graph embedding techniques (like RDPG, see
+\emph{e.g.} Wu et al., 2021) will provide high-quality node-level
+embeddings while also preserving network structure.
 
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1083}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1250}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2667}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1667}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3333}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1016}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1172}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2500}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1875}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3438}}@{}}
 \caption{\label{tbl:methods}Overview of some common graph embedding
@@
 \endhead
-tSNE & nodes & statistical divergence & Hinton \& Roweis (2002) & Gibb
-et al. (2021); Cieslak et al. (2020) \(^a\) \\
+tSNE & nodes & statistical divergence & Hinton \& Roweis (2002) &
+Cieslak et al. (2020) \(^a\) Gibb et al. (2021) \\
 LINE & nodes & stochastic gradient descent & Tang et al. (2015) & \\
@@
 graph2vec & sub-graph & skipgram network & Narayanan et al. (2017) & \\
-RDPG & graph & SVD & Young \& Scheinerman (2007) & Poisot et al. (2021);
-Dalla Riva \& Stouffer (2016) \\
+RDPG & graph & SVD & Young \& Scheinerman (2007) & Dalla Riva \&
+Stouffer (2016); Poisot et al. (2021) \\
 GLEE & graph & Laplacian eigenmap & Torres et al. (2020) & \\
@@
 FastEmbed & graph & eigen decomposition & Ramasamy \& Madhow (2015) & \\
-PCA & graph & eigen decomposition & S \& Surendran (2013) & Strydom,
-Catchen, et al. (2021) \\
+PCA & graph & eigen decomposition & Surendran (2013) & Strydom, Catchen,
+et al. (2021) \\
 Joint methods & multiple graphs & multiple strategies & S. Wang et al.
@@
 (or strives to capture) the action of evolutionary processes on network
-structure, which at least for food webs have been well documented (Dalla
-Riva \& Stouffer, 2016; Stouffer et al., 2012;
-\textbf{Stouffer2007EviExi?}); similarly, the use of functional traits
-assumes that interactions can be inferred from the knowledge of
-trait-matching rules, which is similarly well supported in the empirical
-literature (Bartomeus, 2013; Bartomeus et al., 2016;
-\textbf{Gravel2013InfFoo?}). Relating this information to an embedding
-rather than a list of networks measures would allow to capture their
-effect on the more fundamental aspects of network structure; conversely,
-the absence of a phylogenetic or functional signal may suggest that
-evolutionary/trait processes are not strong drivers of network
-structure, therefore opening a new way to perform hypothesis testing.
+structure, which at least for food webs have been well documented (M. P.
+Braga et al., 2021; Dalla Riva \& Stouffer, 2016; Eklöf \& Stouffer,
+2016; Stouffer et al., 2012; Stouffer et al., 2007); similarly, the use
+of functional traits assumes that interactions can be inferred from the
+knowledge of trait-matching rules, which is similarly well supported in
+the empirical literature (Bartomeus, 2013; Bartomeus et al., 2016;
+Goebel et al., 2023; Gravel et al., 2013). Relating this information to
+an embedding rather than a list of networks measures would allow to
+capture their effect on the more fundamental aspects of network
+structure; conversely, the absence of a phylogenetic or functional
+signal may suggest that evolutionary/trait processes are not strong
+drivers of network structure, therefore opening a new way to perform
+hypothesis testing.
 
@@
 (2019), these values neither derive from, nor result in, changes in
-organismal fitness, and should therefore not be used to quantify
+organismal performance, and should therefore not be used to quantify
 \emph{e.g.} functional diversity. This holds true even when there are
@@
 bipartite networks collected by Hadfield et al. (2014), using t-SVD and
-RDPG (see Strydom et al., 2022 for the full details). Briefly, an RDPG
-decomposes a network into two subspaces (left and right), which are
-matrices that when multiplied give an approximation of the original
-network. RDPG has the particularly desirable properties of being a graph
-embedding technique that produces relevant node-level feature vectors,
-and provides good approximations of graphs with varied structures
-(Athreya et al., 2017). The code to reproduce this example is available
-as supplementary material (note, for the sake of comparison, that
-Strydom, Catchen, et al., 2021 have an example using embedding through
-PCA followed by prediction using a deep neural network on the same
-dataset). The resulting (binary) metaweb \(\mathcal{M}\) has 2131
+RDPG. Briefly, an RDPG decomposes a network into two subspaces (left and
+right), which are matrices that when multiplied give an approximation of
+the original network. RDPG has the particularly desirable properties of
+being a graph embedding technique that produces relevant node-level
+feature vectors, and provides good approximations of graphs with varied
+structures (Athreya et al., 2017). The code to reproduce this example is
+available as supplementary material (note, for the sake of comparison,
+that Strydom, Catchen, et al., 2021 have an example using embedding
+through PCA followed by prediction using a deep neural network on the
+same dataset). The resulting (binary) metaweb \(\mathcal{M}\) has 2131
 interactions between 206 parasites and 121 hosts, and its adjacency
@@
 the predicted weight (\emph{i.e.} the result of the multiplication of
-the RDGP subspaces at a rank of 25) as a function of whether the
+the RDGP subspaces at a rank of 39) as a function of whether the
 interactions are observed, not-observed, or unknown due to lack of
@@
 performed a clamping of the weights to the unit space, showing a
-one-inflation in documented interaction, and a zero-inflation in other
+one-inflation in documented interactions, and a zero-inflation in other
 species pairs. This last figure crosses from the statistical into the
@@
 
-The first open research problem is the taxonomic and spatial limit of
-the metaweb to embed and transfer. If the initial metaweb is too narrow
-in scope, notably from a taxonomic point of view, the chances of finding
-another area with enough related species (through phylogenetic
-relatedness or similarity of functional traits) to make a reliable
-inference decreases; this would likely be indicated by large confidence
-intervals during estimation of the values in the low-rank space, meaning
-that the representation of the original graph is difficult to transfer
-to the new problem. Alternatively, if the initial metaweb is too large
-(taxonomically), then the resulting embeddings would need to represent
-interactions between taxonomic groups that are not present in the new
-location. This would lead to a much higher variance in the starting
-dataset, and to under-dispersion in the target dataset, resulting in the
-potential under or over estimation of the strength of new predicted
-interactions. The lack of well documented metawebs is currently
-preventing the development of more concrete guidelines. The question of
-phylogenetic relatedness and distribution is notably relevant if the
-metaweb is assembled in an area with mostly endemic species (\emph{e.g.}
-a system that has undergone recent radiation or that has remained in
-isolation for a long period of time might not have an analogous system
-with which to draw knowledge from), and as with every predictive
-algorithm, there is room for the application of our best ecological
-judgement. Because this problem relates to distribution of species in
-the geographic or phylogenetic space, it can certainly be approached
-through assessing the performance of embedding transfer in simulated
-starting/target species pools.
-
-The second series of problems relate to determining which area should be
-used to infer the new metaweb in, as this determines the species pool
-that must be used. Metawebs can be constructed by assigning interactions
-in a list of species within geographic boundaries. The upside of this
-approach is that information at the country level is likely to be
-required for biodiversity assessments, as countries set conservation
-goals at the national level (Buxton et al., 2021), and as quantitative
-instruments are designed to work at these scales (Turak et al., 2017);
-specific strategies are often enacted at smaller scales, nested within a
-specific country (Ray et al., 2021). But there is no guarantee that
-these boundaries are meaningful. In fact, we do not have a satisfying
-answer to the question of ``where does a food web stop?''; the most
-promising solutions involve examining the spatial consistency of network
-area relationships (Fortin et al., 2021; see \emph{e.g.} Galiana et al.,
-2018, 2019, 2021), which is impossible in the absence of enough
-information about the network itself. This suggests that inferred
-metawebs should be further downscaled to allow for \emph{a posteriori}
-analyses. The methodology for metaweb downscaling is currently limited,
-and it is likely that the sustained effort to characterize the spatial
-dependency of food web structure will lead to more prescriptive
-guidelines about the need for prediction downscaling. Recent results by
-Martins et al. (2022) suggest that networks are shaped within
-eco-regions, with abrupt structural transitions from an eco-region to
-the next. Should this trend hold generally, this would provide an
-ecologically-relevant scale at which metawebs can be downscaled and
-predicted.
-
-The final family of problems relates less to ecological methods than to
-the praxis of ecological research. Operating under the context of
-national divisions, in large parts of the world, reflects nothing more
-than the legacy of settler colonialism, which drives a disparity in
-available ecological data. Applying any embedding to biased data does
-not debias them, but instead embeds these very same biases, propagating
-them to the machine learning models using embeddings to make
-predictions. Indeed, the use of ecological data is not an apolitical act
-(Nost \& Goldstein, 2021), as data infrastructures tend to be designed
-to answer questions within national boundaries (therefore placing
-contingencies on what is available to be embedded), and their use often
-draws upon and reinforces territorial statecraft. As per Machen \& Nost
-(2021), this is particularly true when the output of ``algorithmic
-thinking'' (\emph{e.g.} relying on machine learning to generate
-knowledge) can be re-used for governance (\emph{e.g.} enacting
-conservation decisions at the national scale). As information on species
-interaction networks structure is increasingly leveraged as a tool to
-guide conservation actions {[}see \emph{e.g.} recent discussions for
-food-web based conservation; Eero et al. (2021); Naman et al. (2022);
-Stier et al. (2017){]}, the need to appraise and correct biases that are
-unwittingly propagated to algorithms when embedded from the original
-data is paramount. These considerations are even more urgent in the
-specific context of biodiversity data, as long-term colonial legacies
-still shape taxonomic composition to this day (Lenzner et al., 2022;
-Raja, 2022), and where much shorter-term changes in taxonomic and
-genetic richness emerged as a consequence of environmental racism.
-(Schmidt \& Garroway, 2022).
+\hypertarget{identifying-the-properties-of-the-network-to-embed}{%
+\subsection{Identifying the properties of the network to
+embed}\label{identifying-the-properties-of-the-network-to-embed}}
+
+If the initial metaweb is too narrow in scope, notably from a taxonomic
+point of view, the chances of finding another area with enough related
+species (through phylogenetic relatedness or similarity of functional
+traits) to make a reliable inference decreases; this would likely be
+indicated by large confidence intervals during estimation of the values
+in the low-rank space, meaning that the representation of the original
+graph is difficult to transfer to the new problem. Alternatively, if the
+initial metaweb is too large (taxonomically), then the resulting
+embeddings would need to represent interactions between taxonomic groups
+that are not present in the new location. This would lead to a much
+higher variance in the starting dataset, and to under-dispersion in the
+target dataset, resulting in the potential under or over estimation of
+the strength of new predicted interactions. The lack of well documented
+metawebs is currently preventing the development of more concrete
+guidelines. The question of phylogenetic relatedness and distribution is
+notably relevant if the metaweb is assembled in an area with mostly
+endemic species (\emph{e.g.} a system that has undergone recent
+radiation or that has remained in isolation for a long period of time
+might not have an analogous system with which to draw knowledge from),
+and as with every predictive algorithm, there is room for the
+application of our best ecological judgement. Because this problem
+relates to distribution of species in the geographic or phylogenetic
+space, it can certainly be approached through assessing the performance
+of embedding transfer in simulated starting/target species pools.
+
+\hypertarget{identifying-the-scope-of-the-prediction-to-perform}{%
+\subsection{Identifying the scope of the prediction to
+perform}\label{identifying-the-scope-of-the-prediction-to-perform}}
+
+The area used to infer the new metaweb in determines the species pool
+that must be used to perform this embedding. Metawebs can be constructed
+by assigning interactions in a list of species within geographic
+boundaries. The upside of this approach is that information at the
+country level is likely to be required for biodiversity assessments, as
+countries set conservation goals at the national level (Buxton et al.,
+2021), and as quantitative instruments are designed to work at these
+scales (\textbf{turak\_measuring\_2017?}); specific strategies are often
+enacted at smaller scales, nested within a specific country (Ray et al.,
+2021). But there is no guarantee that these boundaries are meaningful.
+In fact, we do not have a satisfying answer to the question of ``where
+does an ecological network stop?''. Recent results by Martins et al.
+(2022) suggest that networks are shaped within eco-regions, with abrupt
+structural transitions from an eco-region to the next. Should this trend
+hold generally, this would provide an ecologically-relevant scale at
+which metawebs can be downscaled and predicted. Other solutions leverage
+network-area relationships to identify areas in which networks are
+structurally similar (see \emph{e.g.} Fortin et al., 2021; Galiana et
+al., 2022, 2018), which requires ample pre-existing information about
+the network. This suggests that inferred metawebs should be further
+downscaled to allow for \emph{a posteriori} analyses; Llewelyn et al.
+(2022) provide compelling evidence for the fact that when a place is
+rich in endemic species, even at smaller spatial scales, the transfer of
+information about interactions becomes more challenging, re-emphasizing
+the need to identify guidelines for when and where network predictions
+can be mapped.
+
+\hypertarget{minding-legacies-shaping-ecological-datasets}{%
+\subsection{Minding legacies shaping ecological
+datasets}\label{minding-legacies-shaping-ecological-datasets}}
+
+Operating under the context of national divisions, in large parts of the
+world, reflects nothing more than the legacy of settler colonialism,
+which drives a disparity in available ecological data. Applying any
+embedding to biased data does not debias them, but instead embeds these
+very same biases, propagating them to the machine learning models using
+embeddings to make predictions. Indeed, the use of ecological data
+itself is not an apolitical act (Nost \& Goldstein, 2021), as data
+infrastructures tend to be designed to answer questions within national
+boundaries (therefore placing contingencies on what is available to be
+embedded). Furthermore, their use often draws upon, and reinforces,
+territorial statecraft (see \emph{e.g.} Barrett, 2005). As per Machen \&
+Nost (2021), these biases are particularly important to consider when
+the output of ``algorithmic thinking'' (\emph{i.e.} relying on machine
+learning to generate knowledge or as a substitute to human
+decision-making) can be re-purposed for governance (\emph{e.g.} enacting
+conservation decisions on the basis of model prediction). As information
+on species interaction networks structure is increasingly leveraged as a
+tool to guide conservation actions (see \emph{e.g.} Eero et al., 2021;
+Naman et al., 2022; Stier et al., 2017), the need to appraise and
+correct biases that are unwittingly propagated to algorithms when
+embedded from the original data is paramount. These considerations are
+even more urgent in the specific context of biodiversity data, as
+long-term colonial legacies still shape taxonomic composition to this
+day (Lenzner et al., 2022; Raja, 2022), and where much shorter-term
+changes in taxonomic and genetic richness of wildlife emerged through
+environmental racism (Schmidt \& Garroway, 2022).
+
+\hypertarget{conclusion-metaweb-prediction-in-context}{%
+\section{Conclusion: metaweb prediction in
+context}\label{conclusion-metaweb-prediction-in-context}}
 
@@
 reinforced environmental injustice (Choudry, 2013; Domínguez \& Luoma,
-2020). Particularly on Turtle Island and other territories that were
-traditionally stewarded by Indigenous people, these approaches should be
-replaced (or at least guided and framed) by Indigenous principles of
-land management (Eichhorn et al., 2019; No'kmaq et al., 2021), as part
-of an ``algorithm-in-the-loop'' approach. Human-algorithm interactions
-are notoriously difficult and can yield adverse effect (Green \& Chen,
-2019; Stevenson \& Doleac, 2021), suggesting the need to systematically
-study them for the specific purpose of biodiversity governance, as well
-as to improve the algorithmic literacy of decision makers. As we see
-artificial intelligence/machine learning being increasingly mobilized to
-generate knowledge that is lacking for conservation decisions
-(\emph{e.g.} Lamba et al., 2019; Mosebo Fernandes et al., 2020) and
-drive policy decisions (Weiskopf et al., 2022), our discussion of these
-tools need to go beyond the technical and statistical, and into the
-governance consequences they can have.
+2020). The risk of embedding this legacy in our models is great,
+especially when the impact of this legacy on species pools is being
+increasingly documented. This problem can be addressed by re-framing the
+way we interact with models, especially in the context where these
+models are intended to support conservation actions. Particularly on
+territories that were traditionally stewarded by Indigenous people,
+these approaches should be replaced (or at least guided and framed) by
+Indigenous principles of land management (Eichhorn et al., 2019; No'kmaq
+et al., 2021), as part of an ``algorithm-in-the-loop'' approach.
+Human-algorithm interactions are notoriously difficult and can yield
+adverse effect (Green \& Chen, 2019; Stevenson \& Doleac, 2021),
+suggesting the need to systematically study them for the specific
+purpose of biodiversity governance, as well as to improve the
+algorithmic literacy of decision makers. As we see artificial
+intelligence/machine learning being increasingly mobilized to generate
+knowledge that is lacking for conservation decisions (\emph{e.g.} Lamba
+et al., 2019; Mosebo Fernandes et al., 2020) and drive policy decisions
+(Weiskopf et al., 2022), our discussion of these tools need to go beyond
+the technical and statistical, and into the governance consequences they
+can have.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Adam2014EleTre}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Adam2014Elephant}{}}%
 Adam, R. (2014). \emph{Elephant treaties: The Colonial legacy of the
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Albouy2019MarFis}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Albouy2019Marine}{}}%
 Albouy, C., Archambault, P., Appeltans, W., Araújo, M. B., Beauchesne,
@@
 Gravel, D. (2019). The marine fish food web is globally connected.
-\emph{Nature Ecology \& Evolution}, \emph{3}(8), 1153--1161.
+\emph{Nature Ecology \& Evolution}, \emph{3}(8, 8), 1153--1161.
 \url{https://doi.org/10.1038/s41559-019-0950-y}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Anowar2021ConEmp}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Anowar2021Conceptual}{}}%
 Anowar, F., Sadaoui, S., \& Selim, B. (2021). Conceptual and empirical
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Arsov2019NetEmb}{}}%
-Arsov, N., \& Mirceva, G. (2019). Network Embedding: An Overview.
-\emph{arXiv:1911.11726 {[}Cs, Stat{]}}.
-\url{https://arxiv.org/abs/1911.11726}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Athreya2017StaInf}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Athreya2017Statistical}{}}%
 Athreya, A., Fishkind, D. E., Levin, K., Lyzinski, V., Park, Y., Qin,
@@
 survey} (No. arXiv:1709.05454). arXiv.
-\url{https://arxiv.org/abs/1709.05454}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bartomeus2013UndLin}{}}%
+\url{http://arxiv.org/abs/1709.05454}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Barrett2005Environment}{}}%
+Barrett, S. (2005). \emph{Environment and Statecraft: The Strategy of
+Environmental Treaty-Making} (1st ed.). Oxford University PressOxford.
+\url{https://doi.org/10.1093/0199286094.001.0001}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bartomeus2013Understanding}{}}%
 Bartomeus, I. (2013). Understanding linkage rules in plant-pollinator
@@
 detectability and plant traits. \emph{PloS One}, \emph{8}(7), e69200.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bartomeus2016ComFra}{}}%
+\url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0069200}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bartomeus2016Common}{}}%
 Bartomeus, I., Gravel, D., Tylianakis, J. M., Aizen, M. A., Dickie, I.
@@
 Ecology}, \emph{30}(12), 1894--1903.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bezanson2017JulFre}{}}%
+\url{http://onlinelibrary.wiley.com/doi/10.1111/1365-2435.12666/full}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bezanson2017Julia}{}}%
 Bezanson, J., Edelman, A., Karpinski, S., \& Shah, V. B. (2017). Julia:
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Blanchet2020CooNot}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Blanchet2020Cooccurrence}{}}%
 Blanchet, F. G., Cazelles, K., \& Gravel, D. (2020). Co-occurrence is
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Bohan2017NexGlo}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Bohan2017Nextgeneration}{}}%
 Bohan, D. A., Vacher, C., Tamaddoni-Nezhad, A., Raybould, A., Dumbrell,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Botella2022AppGra}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Botella2022Appraisal}{}}%
 Botella, C., Dray, S., Matias, C., Miele, V., \& Thuiller, W. (2022). An
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Braga2019SpaAna}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Braga2019Spatial}{}}%
 Braga, J., Pollock, L. J., Barros, C., Galiana, N., Montoya, J. M.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-BramonMora2018IdeCom}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Braga2021Phylogenetic}{}}%
+Braga, M. P., Janz, N., Nylin, S., Ronquist, F., \& Landis, M. J.
+(2021). Phylogenetic reconstruction of ancestral ecological networks
+through time for pierid butterflies and their host plants. \emph{Ecology
+Letters}, \emph{n/a}(n/a). \url{https://doi.org/10.1111/ele.13842}
+
+\leavevmode\vadjust pre{\hypertarget{ref-BramonMora2018Identifying}{}}%
 Bramon Mora, B., Gravel, D., Gilarranz, L. J., Poisot, T., \& Stouffer,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Buxton2021KeyInf}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Buxton2021Key}{}}%
 Buxton, R. T., Bennett, J. R., Reid, A. J., Shulman, C., Cooke, S. J.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Cazelles2016TheSpe}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Catchen2023Missing}{}}%
+Catchen, M., Poisot, T., Pollock, L., \& Gonzalez, A. (2023). \emph{The
+missing link: Discerning true from false negatives when sampling species
+interaction networks} (Preprint No. 4929). EcoEvoRXiV.
+\url{https://doi.org/10.32942/X2DW22}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Cazelles2016Theory}{}}%
 Cazelles, K., Araújo, M. B., Mouquet, N., \& Gravel, D. (2016). A theory
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Chami2022MacLea}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Chami2022Machine}{}}%
 Chami, I., Abu-El-Haija, S., Perozzi, B., Ré, C., \& Murphy, K. (2022).
@@
 \emph{Journal of Machine Learning Research}, \emph{23}(89), 1--64.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Chen2017DeeMul}{}}%
+\url{http://jmlr.org/papers/v23/20-852.html}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Chen2017Deep}{}}%
 Chen, D., Xue, Y., Fink, D., Chen, S., \& Gomes, C. P. (2017).
 \emph{Deep Multi-species Embedding}. 3639--3646.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Chen2017HarHie}{}}%
-Chen, H., Perozzi, B., Hu, Y., \& Skiena, S. (2017). HARP: Hierarchical
-Representation Learning for Networks. \emph{arXiv:1706.07845 {[}Cs{]}}.
-\url{https://arxiv.org/abs/1706.07845}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Choudry2013SavBio}{}}%
+\url{https://www.ijcai.org/proceedings/2017/509}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Chen2017Harp}{}}%
+Chen, H., Perozzi, B., Hu, Y., \& Skiena, S. (2017). \emph{HARP:
+Hierarchical Representation Learning for Networks}.
+\url{http://arxiv.org/abs/1706.07845}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Choudry2013Saving}{}}%
 Choudry, A. (2013). Saving biodiversity, for whom and for what?
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Cieslak2020TdiSto}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Cieslak2020Tdistributed}{}}%
 Cieslak, M. C., Castelfranco, A. M., Roncalli, V., Lenz, P. H., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Csermely2004StrLin}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Csermely2004Strong}{}}%
 Csermely, P. (2004). Strong links are important, but weak links
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-DallaRiva2016ExpEvo}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-DallaRiva2016Exploring}{}}%
 Dalla Riva, G. V., \& Stouffer, D. B. (2016). Exploring the evolutionary
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dallas2017PreCry}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Dallas2017Predicting}{}}%
 Dallas, T., Park, A. W., \& Drake, J. M. (2017). Predicting cryptic
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Danisch2021MakJl}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Danisch2021Makie}{}}%
 Danisch, S., \& Krumbiegel, J. (2021). Makie.jl: Flexible
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dominguez2020DecCon}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Dominguez2020Decolonising}{}}%
 Domínguez, L., \& Luoma, C. (2020). Decolonising Conservation Policy:
@@
 Indigenous Injustices at the Expense of the Environment. \emph{Land},
-\emph{9}(3), 65. \url{https://doi.org/10.3390/land9030065}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dunne2006NetStr}{}}%
+\emph{9}(3, 3), 65. \url{https://doi.org/10.3390/land9030065}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dunne2006Network}{}}%
 Dunne, J. A. (2006). The Network Structure of Food Webs. In J. A. Dunne
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Eero2021UseFoo}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Eero2021Use}{}}%
 Eero, M., Dierking, J., Humborg, C., Undeman, E., MacKenzie, B. R.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Eichhorn2019SteDec}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Eichhorn2019Steps}{}}%
 Eichhorn, M. P., Baker, K., \& Griffiths, M. (2019). Steps towards
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Eklof2013DimEco}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Eklof2013Dimensionality}{}}%
 Eklöf, A., Jacob, U., Kopp, J., Bosch, J., Castro-Urgal, R., Chacoff, N.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Fortin2021NetEco}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Eklof2016Phylogenetic}{}}%
+Eklöf, A., \& Stouffer, D. B. (2016). The phylogenetic component of food
+web structure and intervality. \emph{Theoretical Ecology}, \emph{9}(1),
+107--115. \url{https://doi.org/10.1007/s12080-015-0273-9}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fortin2021Network}{}}%
 Fortin, M.-J., Dale, M. R. T., \& Brimacombe, C. (2021). Network ecology
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Fricke2022EffDef}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Fricke2022Effects}{}}%
 Fricke, E. C., Ordonez, A., Rogers, H. S., \& Svenning, J.-C. (2022).
@@
 \emph{Science}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Galiana2021SpaSca}{}}%
-Galiana, N., Barros, C., Braga, J., Ficetola, G. F., Maiorano, L.,
-Thuiller, W., Montoya, J. M., \& Lurgi, M. (2021). The spatial scaling
-of food web structure across European biogeographical regions.
-\emph{Ecography}, \emph{n/a}(n/a).
-\url{https://doi.org/10.1111/ecog.05229}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Galiana2019GeoVar}{}}%
-Galiana, N., Hawkins, B. A., \& Montoya, J. M. (2019). The geographical
-variation of network structure is scale dependent: Understanding the
-biotic specialization of hostparasitoid networks. \emph{Ecography},
-\emph{42}(6), 1175--1187. \url{https://doi.org/10.1111/ecog.03684}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Galiana2022EcoNet}{}}%
+\url{https://www.science.org/doi/abs/10.1126/science.abk3510}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Galiana2022Ecological}{}}%
 Galiana, N., Lurgi, M., Bastazini, V. A. G., Bosch, J., Cagnolo, L.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Galiana2018SpaSca}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Galiana2018Spatial}{}}%
 Galiana, N., Lurgi, M., Claramunt-López, B., Fortin, M.-J., Leroux, S.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gaucher2021OutDet}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Gaucher2021Outlier}{}}%
 Gaucher, S., Klopp, O., \& Robin, G. (2021). Outlier detection in
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gibb2021DatPro}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Gibb2021Data}{}}%
 Gibb, R., Albery, G. F., Becker, D. J., Brierley, L., Connor, R.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Goodfellow2016DeeLea}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Goebel2023Body}{}}%
+Goebel, L. G. A., Vitorino, B. D., Frota, A. V. B., \& Santos-Filho, M.
+dos. (2023). Body mass determines the role of mammal species in a
+frugivore-large fruit interaction network in a Neotropical savanna.
+\emph{Journal of Tropical Ecology}, \emph{39}, e12.
+\url{https://doi.org/10.1017/S0266467422000505}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Goodfellow2016Deep}{}}%
 Goodfellow, I., Bengio, Y., \& Courville, A. (2016). \emph{Deep
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Goyal2018GraEmb}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Goyal2018Graph}{}}%
 Goyal, P., \& Ferrara, E. (2018). Graph embedding techniques,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gravel2018BriElt}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Gravel2018Bringing}{}}%
 Gravel, D., Baiser, B., Dunne, J. A., Kopelke, J.-P., Martinez, N. D.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Green2019DisInt}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Gravel2013Inferring}{}}%
+Gravel, D., Poisot, T., Albouy, C., Velez, L., \& Mouillot, D. (2013).
+Inferring food web structure from predator-prey body size relationships.
+\emph{Methods in Ecology and Evolution}, \emph{4}(11), 1083--1090.
+\url{https://doi.org/10.1111/2041-210X.12103}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Green2019Disparate}{}}%
 Green, B., \& Chen, Y. (2019). Disparate Interactions: An
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Grover2016NodSca}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Grover2016Node2vec}{}}%
 Grover, A., \& Leskovec, J. (2016). Node2vec: Scalable Feature Learning
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Grunig2020CroFor}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Grunig2020Crop}{}}%
 Grünig, M., Mazzi, D., Calanca, P., Karger, D. N., \& Pellissier, L.
@@
 and suitability overlap under climate change. \emph{Communications
-Biology}, \emph{3}(1), 1--10.
+Biology}, \emph{3}(1, 1), 1--10.
 \url{https://doi.org/10.1038/s42003-020-0962-9}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gupta2021GraNeu}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Gupta2022Simultaneously}{}}%
+Gupta, A., Furrer, R., \& Petchey, O. L. (2022). Simultaneously
+estimating food web connectance and structure with uncertainty.
+\emph{Ecology and Evolution}, \emph{12}(3), e8643.
+\url{https://doi.org/10.1002/ece3.8643}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Gupta2021Graph}{}}%
 Gupta, A., Matta, P., \& Pant, B. (2021). Graph neural network: Current
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hadfield2014TalTwo}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Hadfield2014Tale}{}}%
 Hadfield, J. D., Krasnov, B. R., Poulin, R., \& Nakagawa, S. (2014). A
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Herbert1965Dun}{}}%
-Herbert, F. (1965). \emph{Dune} (First). Chilton Book Company.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hinton2002StoNei}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Herbert1965Dune}{}}%
+Herbert, F. (1965). \emph{Dune} (1st ed.). Chilton Book Company.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hinton2002Stochastic}{}}%
 Hinton, G., \& Roweis, S. T. (2002). Stochastic neighbor embedding.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hoffmann2019MacLea}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Hoffmann2019Machine}{}}%
 Hoffmann, J., Bar-Sinai, Y., Lee, L. M., Andrejevic, J., Mishra, S.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hortal2015SevSho}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Hortal2015Seven}{}}%
 Hortal, J., de Bello, F., Diniz-Filho, J. A. F., Lewinsohn, T. M., Lobo,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Jones2009PanSpe}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Jones2009Pantheria}{}}%
 Jones, K. E., Bielby, J., Cardillo, M., Fritz, S. A., O'Dell, J., Orme,
@@
 Price, S. A., Rigby, E. A., Rist, J., \ldots{} Purvis, A. (2009).
-PanTHERIA: A species-level database of life history, ecology, and
+PanTHERIA: A species‐level database of life history, ecology, and
 geography of extant and recently extinct mammals: Ecological Archives
-E090-184. \emph{Ecology}, \emph{90}(9), 2648--2648.
+E090‐184. \emph{Ecology}, \emph{90}(9), 2648--2648.
 \url{https://doi.org/10.1890/08-1494.1}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Jordano2016SamNet}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Jordano2016Sampling}{}}%
 Jordano, P. (2016). Sampling networks of ecological interactions.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Lamba2019DeeLea}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Lamba2019Deep}{}}%
 Lamba, A., Cassey, P., Segaran, R. R., \& Koh, L. P. (2019). Deep
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Lenzner2022NatAli}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Lenzner2022Naturalized}{}}%
 Lenzner, B., Latombe, G., Schertler, A., Seebens, H., Yang, Q., Winter,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Maaten2009LeaPar}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Llewelyn2022Predicting}{}}%
+Llewelyn, J., Strona, G., Dickman, C. R., Greenville, A. C., Wardle, G.
+M., Lee, M. S. Y., Doherty, S., Shabani, F., Saltré, F., \& Bradshaw, C.
+J. A. (2022). \emph{Predicting predator-prey interactions in terrestrial
+endotherms using random forest} {[}Preprint{]}. Ecology.
+\url{https://doi.org/10.1101/2022.09.02.506446}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Maaten2009Learning}{}}%
 Maaten, L. van der. (2009). Learning a Parametric Embedding by
@@
 International Conference on Artificial Intelligence and Statistics},
-384--391.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Machen2021ThiAlg}{}}%
+384--391. \url{https://proceedings.mlr.press/v5/maaten09a.html}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Machen2021Thinking}{}}%
 Machen, R., \& Nost, E. (2021). Thinking algorithmically: The making of
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Malaterre2019FunDiv}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Malaterre2019Functional}{}}%
 Malaterre, C., Dussault, A. C., Mermans, E., Barker, G., Beisner, B. E.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Martins2022GloReg}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Martins2022Global}{}}%
 Martins, L. P., Stouffer, D. B., Blendinger, P. G., Böhning-Gaese, K.,
@@
 ecological boundaries explain abrupt spatial discontinuities in avian
-frugivory interactions. \emph{Nature Communications}, \emph{13}(1),
+frugivory interactions. \emph{Nature Communications}, \emph{13}(1, 1),
 6943. \url{https://doi.org/10.1038/s41467-022-34355-w}
 
-\leavevmode\vadjust pre{\hypertarget{ref-McLeod2021SamAsy}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-McLeod2021Sampling}{}}%
 McLeod, A., Leroux, S. J., Gravel, D., Chu, C., Cirtwill, A. R., Fortin,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Melnyk2020GraGra}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Melnyk2020Graphkke}{}}%
 Melnyk, K., Klus, S., Montavon, G., \& Conrad, T. O. F. (2020).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Morales-Castilla2015InfBio}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Morales-Castilla2015Inferring}{}}%
 Morales-Castilla, I., Matias, M. G., Gravel, D., \& Araújo, M. B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Morand1998DenBod}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Morand1998Density}{}}%
 Morand, S., \& Poulin, R. (1998). Density, body mass and parasite
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-MoseboFernandes2020MacLea}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-MoseboFernandes2020Machine}{}}%
 Mosebo Fernandes, A. C., Quintero Gonzalez, R., Lenihan-Clarke, M. A.,
@@
 for Conservation Planning in a Changing Climate. \emph{Sustainability},
-\emph{12}(18), 7657. \url{https://doi.org/10.3390/su12187657}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Murphy2022ProMac}{}}%
+\emph{12}(18, 18), 7657. \url{https://doi.org/10.3390/su12187657}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Murphy2022Probabilistic}{}}%
 Murphy, K. P. (2022). \emph{Probabilistic machine learning: An
-introduction}. MIT Press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Naman2022FooWeb}{}}%
+introduction}. MIT Press. \href{https://probml.ai}{probml.ai}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Naman2022Food}{}}%
 Naman, S. M., White, S. M., Bellmore, J. R., McHugh, P. A., Kaylor, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Narayanan2017GraLea}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Narayanan2017Graph2vec}{}}%
 Narayanan, A., Chandramohan, M., Venkatesan, R., Chen, L., Liu, Y., \&
-Jaiswal, S. (2017). Graph2vec: Learning Distributed Representations of
-Graphs. \emph{arXiv:1707.05005 {[}Cs{]}}.
-\url{https://arxiv.org/abs/1707.05005}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Neutel2002StaRea}{}}%
+Jaiswal, S. (2017). \emph{Graph2vec: Learning Distributed
+Representations of Graphs}. \url{http://arxiv.org/abs/1707.05005}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Neutel2002Stability}{}}%
 Neutel, A.-M., Heesterbeek, J. A. P., \& de Ruiter, P. C. (2002).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Nokmaq2021AwaSle}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Nokmaq2021Awakening}{}}%
 No'kmaq, M., Marshall, A., Beazley, K. F., Hum, J., joudry, shalan,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Nost2021PolEco}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Nost2021Political}{}}%
 Nost, E., \& Goldstein, J. E. (2021). A political ecology of data.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-OConnor2020UnvFoo}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-OConnor2020Unveiling}{}}%
 O'Connor, L. M. J., Pollock, L. J., Braga, J., Ficetola, G. F.,
-Maiorano, L., Martinez-Almoyna, C., Montemaggiori, A., Ohlmann, M., \&
+Maiorano, L., Martinez‐Almoyna, C., Montemaggiori, A., Ohlmann, M., \&
 Thuiller, W. (2020). Unveiling the food webs of tetrapods across Europe
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pedersen2017SigCol}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Pedersen2017Signatures}{}}%
 Pedersen, E. J., Thompson, P. L., Ball, R. A., Fortin, M.-J., Gouhier,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Perozzi2014DeeOnl}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Perozzi2014Deepwalk}{}}%
 Perozzi, B., Al-Rfou, R., \& Skiena, S. (2014). DeepWalk: Online
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pichler2020MacLea}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Pichler2020Machine}{}}%
 Pichler, M., Boreux, V., Klein, A.-M., Schleuning, M., \& Hartig, F.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Poisot2019EcoJl}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Poisot2019Ecologicalnetworks}{}}%
 Poisot, T., Belisle, Z., Hoebeke, L., Stock, M., \& Szefer, P. (2019).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Poisot2016StrPro}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Poisot2016Structure}{}}%
 Poisot, T., Cirtwill, A. R., Cazelles, K., Gravel, D., Fortin, M.-J., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Poisot2021ImpMam}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Poisot2021Imputing}{}}%
 Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M. J., Becker, D.
 J., Albery, G. F., Gibb, R. J., Seifert, S. N., \& Carlson, C. J.
-(2021). Imputing the mammalian virome with linear filtering and singular
-value decomposition. \emph{arXiv:2105.14973 {[}q-Bio{]}}.
-\url{https://arxiv.org/abs/2105.14973}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Poisot2015SpeWhy}{}}%
+(2021). \emph{Imputing the mammalian virome with linear filtering and
+singular value decomposition}. \url{http://arxiv.org/abs/2105.14973}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Poisot2015Species}{}}%
 Poisot, T., Stouffer, D. B., \& Gravel, D. (2015). Beyond species: Why
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Raja2022ColSha}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Raja2022Colonialism}{}}%
 Raja, N. B. (2022). Colonialism shaped today's biodiversity.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ramasamy2015ComSpe}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Ramasamy2015Compressive}{}}%
 Ramasamy, D., \& Madhow, U. (2015). Compressive spectral embedding:
@@
 systems} (Vol. 28). Curran Associates, Inc.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ray2021BioCri}{}}%
+\url{https://proceedings.neurips.cc/paper/2015/file/4f6ffe13a5d75b2d6a3923922b3922e5-Paper.pdf}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Ray2021Biodiversity}{}}%
 Ray, J. C., Grimm, J., \& Olive, A. (2021). The biodiversity crisis in
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Runghen2021ExpNod}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Runghen2021Exploiting}{}}%
 Runghen, R., Stouffer, D. B., \& Dalla Riva, G. V. (2021).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-S2013GraEmb}{}}%
-S, N. S., \& Surendran, S. (2013). Graph Embedding and Dimensionality
-Reduction - A Survey. \emph{International Journal of Computer Science \&
-Engineering Technology}, \emph{4}(1).
-
-\leavevmode\vadjust pre{\hypertarget{ref-Saravia2021EcoNet}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Saravia2021Ecological}{}}%
 Saravia, L. A., Marina, T. I., Kristensen, N. P., De Troch, M., \& Momo,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Schmidt2022SysRac}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Schmidt2022Systemic}{}}%
 Schmidt, C., \& Garroway, C. J. (2022). Systemic racism alters wildlife
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Stevenson2021AlgRis}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Stevenson2021Algorithmic}{}}%
 Stevenson, M. T., \& Doleac, J. L. (2021). \emph{Algorithmic Risk
-Assessment in the Hands of Humans} (\{\{SSRN Scholarly Paper\}\} No.
-3489440). \url{https://doi.org/10.2139/ssrn.3489440}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Stier2017IntExp}{}}%
+Assessment in the Hands of Humans} (SSRN Scholarly Paper No. 3489440).
+\url{https://doi.org/10.2139/ssrn.3489440}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Stier2017Integrating}{}}%
 Stier, A. C., Samhouri, J. F., Gray, S., Martone, R. G., Mach, M. E.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2012EvoCon}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2007Evidence}{}}%
+Stouffer, D. B., Camacho, J., Jiang, W., \& Nunes Amaral, L. A. (2007).
+Evidence for the existence of a robust pattern of prey selection in food
+webs. \emph{Proceedings of the Royal Society B: Biological Sciences},
+\emph{274}(1621), 1931--1940.
+\url{https://doi.org/10.1098/rspb.2007.0571}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2012Evolutionary}{}}%
 Stouffer, D. B., Sales-Pardo, M., Sirer, M. I., \& Bascompte, J. (2012).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Strydom2022FooWeb}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Strydom2022Food}{}}%
 Strydom, T., Bouskila, S., Banville, F., Barros, C., Caron, D., Farrell,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021RoaPre}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021Roadmap}{}}%
 Strydom, T., Catchen, M. D., Banville, F., Caron, D., Dansereau, G.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021SvdEnt}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021Svd}{}}%
 Strydom, T., Dalla Riva, G. V., \& Poisot, T. (2021). SVD Entropy
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Tang2015LinLar}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Surendran2013Graph}{}}%
+Surendran, S. (2013). Graph Embedding and Dimensionality Reduction - A
+Survey. \emph{International Journal of Computer Science \& Engineering
+Technology}, \emph{4}(1).
+\url{https://www.semanticscholar.org/paper/Graph-Embedding-and-Dimensionality-Reduction-A-Surendran/3f413d591e4b2b876e033eeb9390e232ad4826ca}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Tang2015Line}{}}%
 Tang, J., Qu, M., Wang, M., Zhang, M., Yan, J., \& Mei, Q. (2015). LINE:
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Thurman2019TesLin}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Thurman2019Testing}{}}%
 Thurman, L. L., Barner, A. K., Garcia, T. S., \& Chestnut, T. (2019).
 Testing the link between species interactions and co-occurrence in a
-trophic network. \emph{Ecography}, \emph{0}(ja).
+trophic network. \emph{Ecography}, \emph{0}.
 \url{https://doi.org/10.1111/ecog.04360}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Torres2020GleGeo}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Torres2020Glee}{}}%
 Torres, L., Chan, K. S., \& Eliassi-Rad, T. (2020). GLEE: Geometric
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Turak2017UsiEss}{}}%
-Turak, E., Brazill-Boast, J., Cooney, T., Drielsma, M., DelaCruz, J.,
-Dunkerley, G., Fernandez, M., Ferrier, S., Gill, M., Jones, H., Koen,
-T., Leys, J., McGeoch, M., Mihoub, J.-B., Scanes, P., Schmeller, D., \&
-Williams, K. (2017). Using the essential biodiversity variables
-framework to measure biodiversity change at national scale.
-\emph{Biological Conservation}, \emph{213}, 264--271.
-\url{https://doi.org/10.1016/j.biocon.2016.08.019}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wang2016StrDee}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Wang2016Structural}{}}%
 Wang, D., Cui, P., \& Zhu, W. (2016). Structural Deep Network Embedding.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wang2021JoiEmb}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Wang2021Joint}{}}%
 Wang, S., Arroyo, J., Vogelstein, J. T., \& Priebe, C. E. (2021). Joint
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wardeh2021PreMam}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Wardeh2021Predicting}{}}%
 Wardeh, M., Baylis, M., \& Blagrove, M. S. C. (2021). Predicting
 mammalian hosts in which novel coronaviruses can be generated.
-\emph{Nature Communications}, \emph{12}(1), 780.
+\emph{Nature Communications}, \emph{12}(1, 1), 780.
 \url{https://doi.org/10.1038/s41467-021-21034-5}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Weiskopf2022IncUpt}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Weiskopf2022Increasing}{}}%
 Weiskopf, S. R., Harmáčková, Z. V., Johnson, C. G., Londoño-Murcia, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wood2015EffSpa}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Williams2000Simple}{}}%
+Williams, R. J., \& Martinez, N. D. (2000). Simple rules yield complex
+food webs. \emph{Nature}, \emph{404}(6774), 180--183.
+\url{https://doi.org/10.1038/35004572}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wood2015Effects}{}}%
 Wood, S. A., Russell, R., Hanson, D., Williams, R. J., \& Dunne, J. A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wu2021MaxPos}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Wu2021Maximum}{}}%
 Wu, D., Palmer, D. R., \& Deford, D. R. (2021). \emph{Maximum a
 Posteriori Inference of Random Dot Product Graphs via Conic Programming}
-(No. arXiv:2101.02180). arXiv. \url{https://arxiv.org/abs/2101.02180}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Xu2021UndGra}{}}%
+(No. arXiv:2101.02180). arXiv. \url{http://arxiv.org/abs/2101.02180}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Xu2021Understanding}{}}%
 Xu, M. (2021). Understanding Graph Embedding Methods and Their
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Yan2005GraEmb}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Yan2005Graph}{}}%
 Yan, S., Xu, D., Zhang, B., \& Zhang, H.-J. (2005). Graph embedding: A
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Young2007RanDot}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Young2007Random}{}}%
 Young, S. J., \& Scheinerman, E. R. (2007). Random Dot Product Graph
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Zhou2020GraNeu}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Zhou2020Graph}{}}%
 Zhou, J., Cui, G., Hu, S., Zhang, Z., Yang, C., Liu, Z., Wang, L., Li,

### 2023-01-25 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@2c05016c09f13e610bf21955d0b2f421bbcf7424 🚀

@@
 machine learning techniques, whose main task is to learn a mapping
-function from a discrete graph to a continuous domain (Chami et al.,
-2022; \textbf{arsov\_network\_2019?}). Their main goal is to learn a low
-dimensional vector representations of the graph (embeddings), such that
-its key properties (\emph{e.g.} local or global structures) are retained
-in the embedding space (Yan et al., 2005). The embedding space may, but
-will not necessarily, have lower dimensionality than the graph.
-Ecological networks are promising candidates for the routine application
-of embeddings, as they tend to possess a shared structural backbone (see
+function from a discrete graph to a continuous domain (Arsov \& Mirceva,
+2019; Chami et al., 2022). Their main goal is to learn a low dimensional
+vector representations of the graph (embeddings), such that its key
+properties (\emph{e.g.} local or global structures) are retained in the
+embedding space (Yan et al., 2005). The embedding space may, but will
+not necessarily, have lower dimensionality than the graph. Ecological
+networks are promising candidates for the routine application of
+embeddings, as they tend to possess a shared structural backbone (see
 \emph{e.g.} Bramon Mora et al., 2018), which hints at structural
@@
 dimensionality reduction methods provide adequate graph embedding
-capacities. In the next section (and fig.~\ref{fig:illustration}), we
-show how the amount of dimensionality reduction can affect the quality
-of the embedding.
+capacities. In the next section (and fig.~\ref{fig:embedding}), we show
+how the amount of dimensionality reduction can affect the quality of the
+embedding.
 
@@
 2021), and as quantitative instruments are designed to work at these
-scales (\textbf{turak\_measuring\_2017?}); specific strategies are often
-enacted at smaller scales, nested within a specific country (Ray et al.,
-2021). But there is no guarantee that these boundaries are meaningful.
-In fact, we do not have a satisfying answer to the question of ``where
-does an ecological network stop?''. Recent results by Martins et al.
-(2022) suggest that networks are shaped within eco-regions, with abrupt
+scales (Turak et al., 2017); specific strategies are often enacted at
+smaller scales, nested within a specific country (Ray et al., 2021). But
+there is no guarantee that these boundaries are meaningful. In fact, we
+do not have a satisfying answer to the question of ``where does an
+ecological network stop?''. Recent results by Martins et al. (2022)
+suggest that networks are shaped within eco-regions, with abrupt
 structural transitions from an eco-region to the next. Should this trend
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Arsov2019Network}{}}%
+Arsov, N., \& Mirceva, G. (2019). \emph{Network Embedding: An Overview}.
+\url{http://arxiv.org/abs/1911.11726}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Athreya2017Statistical}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Turak2017Using}{}}%
+Turak, E., Brazill-Boast, J., Cooney, T., Drielsma, M., DelaCruz, J.,
+Dunkerley, G., Fernandez, M., Ferrier, S., Gill, M., Jones, H., Koen,
+T., Leys, J., McGeoch, M., Mihoub, J.-B., Scanes, P., Schmeller, D., \&
+Williams, K. (2017). Using the essential biodiversity variables
+framework to measure biodiversity change at national scale.
+\emph{Biological Conservation}, \emph{213}, 264--271.
+\url{https://doi.org/10.1016/j.biocon.2016.08.019}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Wang2016Structural}{}}%

### 2023-01-25 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@c8046a43af1b6d14c4cec3f47386c267b9ce35c5 🚀

@@
 most places globally -- paradoxically, this restricts our ability to
-infer interactions for locations where inference is perhaps the least
-required (and leaves us unable to make inference in regions without
-interaction data); second, accurate predictors are important for
-accurate predictions, and the lack of methods that can leverage a small
-amount of \emph{accurate} data is a serious impediment to our predictive
-ability. In most places, our most reliable biodiversity knowledge is
-that of a species pool (\emph{i.e.} a set of potentially interacting
-species in a given area): through the analysis of databases like the
-Global Biodiversity Information Facility (GBIF) or the International
-Union for the Conservation of Nature (IUCN), it is possible to construct
-a list of species in a region of interest; but inferring the potential
-interactions between these species is difficult.
+infer interactions to locations where inference is perhaps the least
+required (and leaves us unable to make inference in data scarce
+regions); second, accurate predictors are important for accurate
+predictions, and the lack of methods that can leverage a small amount of
+\emph{accurate} data is a serious impediment to our predictive ability.
+In most places, our most reliable biodiversity knowledge is that of a
+species pool (\emph{i.e.} a set of potentially interacting species in a
+given area): through the analysis of databases like the Global
+Biodiversity Information Facility (GBIF) or the International Union for
+the Conservation of Nature (IUCN), it is possible to construct a list of
+species for a region of interest; however inferring the potential
+interactions between these species still remains a challenge.
 
@@
 area (and so captures the \(\gamma\) diversity of interactions). The
-metaweb is not a prediction of the network at a specific point within
-the spatial area it covers: it will have a different structure, notably
-by having a larger connectance (see \emph{e.g.} Wood et al., 2015) and
-complexity (see \emph{e.g.} Galiana et al., 2022), from any of these
-local networks. These local networks (which capture the \(\alpha\)
+metaweb itself is not a prediction of the network at a specific point
+within the spatial area it covers: it will have a different structure,
+notably by having a larger connectance (see \emph{e.g.} Wood et al.,
+2015) and complexity (see \emph{e.g.} Galiana et al., 2022), from any of
+these local networks. These local networks (which capture the \(\alpha\)
 diversity of interactions) are a subset of the metaweb's species and
@@
 crop-pest networks (Grünig et al., 2020). In this contribution, we
-highlight the power in viewing (and constructing) metawebs as
+highlight the power of viewing (and constructing) metawebs as
 \emph{probabilistic} objects in the context of rare interactions,
@@
 observation of their interaction. In addition, it is generally expected
-weak or rare links to be more prevalent in networks than common or
-strong links (Csermely, 2004), compared to strong, persistent links;
+that weak or rare links will be more prevalent in networks than common
+or strong links (Csermely, 2004), compared to strong, persistent links;
 this is notably the case in food chains, wherein many weaker links are
@@
 quantitative (preferentially probabilistic) predictions, and this should
-constrain the suite of appropriate models used to predict them.
+constrain the suite of models that are appropriate for prediction.
 
@@
 (interactions) that may have been missed within the original community
-(represented by the orange dashed lines, \textbf{B}). Transfer learning
-allows for the prediction links (interactions) when novel species
-(\textbf{C}) are included alongside the original community (\textbf{D}).
-This is achieved by learning using other relevant predictors
+(represented by the orange dashed arrows, \textbf{B}). Transfer learning
+(\textbf{D}) allows for the prediction links (interactions) even when
+novel species (\textbf{C}) are included alongside the original
+community. This is achieved by learning using other relevant predictors
 (\emph{e.g.} traits) in conjunction with the known interactions to infer
 latent values (\textbf{E}). Ultimately this allows us to predict links
-(interactions) for species external to the original sample as well as
-within sample links (\textbf{F}). Within this context the predicted (and
-original) networks as well as the ecological predictors used (green
-boxes) are products that can be quantified through field measurements,
-whereas the embedded as well as imputed matrices (purple box) are
-representative of a decomposition of the interaction
-networks}\label{fig:embedding}
+(interactions) for species external from the original sample (blue
+dashed arrows) as well as missing within sample links (\textbf{F}).
+Within this context the predicted (and original) networks as well as the
+ecological predictors used (green boxes) are products that can be
+quantified through measurements in the field, whereas the embedded as
+well as imputed matrices (purple box) are representative of a
+decomposition of the interaction matrices onto the embedding
+space}\label{fig:embedding}
 }
@@
 the need for dimensionality reduction (for example for data
-visualisation) arise. In brief, many graph embeddings \emph{can} serve
+visualization) arise. In brief, many graph embeddings \emph{can} serve
 as dimensionality reduction steps, but not all do, neither do all
@@
 relationship between the body mass of hosts (in grams) and the position
-alongside the same dimension. \textbf{C}, weak relationship between
-bodymass of hosts and parasite richness. \textbf{D}, distribution of
+alongside the same dimension. \textbf{C}, weak relationship between body
+mass of hosts and parasite richness. \textbf{D}, distribution of
 positions alongside the same axis for hosts grouped by taxonomic
@@
 panel \textbf{B}: interestingly, the position on the first axis is only
-weakly correlated to body mass of the host; this matches well establihed
-results showing that body size/mass is not always a direct predictor of
-parasite richness in terrestrial mammals (Morand \& Poulin, 1998), a
-result we observe in panel \textbf{C}. Finally, in panel \textbf{D}, we
-can see how different taxonomic families occupy different positions on
-the first axis, with \emph{e.g.} Sciuridae being biased towards higher
-values. These results show how we can look for ecological informations
-in the output of network embeddings, which can further be refined into
-the selection of predictors for transfer learning.
+weakly correlated to body mass of the host; this matches well
+established results showing that body size/mass is not always a direct
+predictor of parasite richness in terrestrial mammals (Morand \& Poulin,
+1998), a result we observe in panel \textbf{C}. Finally, in panel
+\textbf{D}, we can see how different taxonomic families occupy different
+positions on the first axis, with \emph{e.g.} Sciuridae being biased
+towards higher values. These results show how we can look for ecological
+informations in the output of network embeddings, which can further be
+refined into the selection of predictors for transfer learning.
 
@@
 this section, we list some of the most pressing research priorities
-(\emph{i.e.} problems that can be adressed with subsequent data analysis
-or simulations), as well as issues related to the application of these
-methods at the science-policy interface.
+(\emph{i.e.} problems that can be addressed with subsequent data
+analysis or simulations), as well as issues related to the application
+of these methods at the science-policy interface.
 

### 2023-01-26 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@a5efe396f635fafb5ba5f2ef1440b056bf76d3a7 🚀

@@
 
-Being able to infer \emph{potential} interactions could serve as a
-significant breakthrough in our ability to start thinking about species
+The ability to infer \emph{potential} interactions could serve as a
+significant breakthrough in our ability to conceptualize species
 interaction networks over large spatial scales (Hortal et al., 2015).
-Understanding species interactions holds enormous potential to not only
-understand and more rapidly learn about species interactions and
-metawebs, but also how changes in management of a single species may
-impact non-target species. In a recent overview of the field of
-ecological network prediction, Strydom, Catchen, et al. (2021)
-identified two challenges of interest to the prediction of interactions
-at large scales. First, there is a relative scarcity of relevant data in
-most places globally -- paradoxically, this restricts our ability to
-infer interactions to locations where inference is perhaps the least
-required (and leaves us unable to make inference in data scarce
-regions); second, accurate predictors are important for accurate
-predictions, and the lack of methods that can leverage a small amount of
-\emph{accurate} data is a serious impediment to our predictive ability.
-In most places, our most reliable biodiversity knowledge is that of a
-species pool (\emph{i.e.} a set of potentially interacting species in a
-given area): through the analysis of databases like the Global
-Biodiversity Information Facility (GBIF) or the International Union for
-the Conservation of Nature (IUCN), it is possible to construct a list of
-species for a region of interest; however inferring the potential
-interactions between these species still remains a challenge.
+Robust inferences would not only boost our understanding of the
+structure of species interaction networks, but also increase the amount
+of information that can be used for biodiversity management. In a recent
+overview of the field of ecological network prediction, Strydom,
+Catchen, et al. (2021) identified two challenges of interest to the
+prediction of interactions at large scales. First, there is a relative
+scarcity of relevant data in most places globally -- paradoxically, this
+restricts our ability to infer interactions to locations where inference
+is perhaps the least required (and leaves us unable to make inference in
+data scarce regions); second, accurate predictors are important for
+accurate predictions, and the lack of methods that can leverage a small
+amount of \emph{accurate} data is a serious impediment to our predictive
+ability. In most places, our most reliable biodiversity knowledge is
+that of a species pool (\emph{i.e.} a set of potentially interacting
+species in a given area): through the analysis of databases like the
+Global Biodiversity Information Facility (GBIF) or the International
+Union for the Conservation of Nature (IUCN), it is possible to construct
+a list of species for a region of interest; however inferring the
+potential interactions between these species still remains a challenge.
 
@@
 
+\hypertarget{ecological-networks-are-good-candidates-for-embedding}{%
+\subsection{Ecological networks are good candidates for
+embedding}\label{ecological-networks-are-good-candidates-for-embedding}}
+
 Indeed, food webs are inherently low-dimensional objects, and can be
@@
 embeddings while also preserving network structure.
+
+\hypertarget{graph-embeddings-produce-novel-latent-variables-to-predict-interactions}{%
+\subsection{Graph embeddings produce novel latent variables to predict
+interactions}\label{graph-embeddings-produce-novel-latent-variables-to-predict-interactions}}
+
+Before moving further, it is important to clarify the epistemic status
+of node values derived from embeddings: specifically, they are
+\emph{not} functional traits, and therefore should not be discussed in
+terms of effects or responses. As per the framework of Malaterre et al.
+(2019), these values neither derive from, nor result in, changes in
+organismal performance, and should therefore not be used to quantify
+\emph{e.g.} functional diversity. This holds true even when there are
+correlations between latent values and functional traits: although these
+enable an ecological discussion of how traits condition the structure of
+the network, the existence of a statistical relationship does not
+elevate the latent values to the status of functional traits.
+
+Rather than directly predicting biological rules (see \emph{e.g.}
+Pichler et al., 2020 for an overview), which may be confounded by the
+sparse nature of graph data, learning embeddings works in the
+low-dimensional space that maximizes information about the network
+structure. This approach is further justified by the observation, for
+example, that the macro-evolutionary history of a network is adequately
+represented by some graph embeddings {[}Random dot product graphs
+(RDPG); see Dalla Riva \& Stouffer (2016){]}. In a recent publication,
+Strydom et al. (2022) have used an embedding (based on RDPG) to project
+a metaweb of trophic interactions between European mammals, and
+transferred this information to mammals of Canada, using the
+phylogenetic distance between related clades to infer the values in the
+latent sub-space into which the European metaweb was projected. By
+performing the RDPG step on re-constructed values, this approach yields
+a probabilistic trophic metaweb for mammals of Canada based on knowledge
+of European species, despite a limited (\(\approx\) 5\%) taxonomic
+overlap.
+
+Graph embeddings \emph{can} serve as a dimensionality reduction method.
+For example, RDPG (Strydom et al., 2022) and t-SVD {[}truncated Singular
+Value Decomposition; Poisot et al. (2021){]} typically embed networks
+using fewer dimensions than the original network {[}the original network
+has as many dimensions as species, and as many informative dimensions as
+trophically unique species; Strydom, Dalla Riva, et al. (2021){]}. But
+this is not necessarily the case -- indeed, one may perform a PCA (a
+special case of SVD) to project the raw data into a subspace that
+improves the efficacy of t-SNE {[}t-distributed stochastic neighbor
+embedding; Maaten (2009){]}. There are many dimensionality reductions
+(Anowar et al., 2021) that can be applied to an embedded network should
+the need for dimensionality reduction (for example for data
+visualization) arise. In brief, many graph embeddings \emph{can} serve
+as dimensionality reduction steps, but not all do, neither do all
+dimensionality reduction methods provide adequate graph embedding
+capacities. In the next section (and fig.~\ref{fig:embedding}), we show
+how the amount of dimensionality reduction can affect the quality of the
+embedding.
+
+\hypertarget{graph-embedding-has-been-under-used-in-the-prediction-of-species-interactions}{%
+\subsection{Graph embedding has been under-used in the prediction of
+species
+interactions}\label{graph-embedding-has-been-under-used-in-the-prediction-of-species-interactions}}
 
@@
 
-Before moving further, it is important to clarify the epistemic status
-of node values derived from embeddings: specifically, they are
-\emph{not} functional traits, and therefore should not be discussed in
-terms of effects or responses. As per the framework of Malaterre et al.
-(2019), these values neither derive from, nor result in, changes in
-organismal performance, and should therefore not be used to quantify
-\emph{e.g.} functional diversity. This holds true even when there are
-correlations between latent values and functional traits: although these
-enable an ecological discussion of how traits condition the structure of
-the network, the existence of a statistical relationship does not
-elevate the latent values to the status of functional traits.
-
-Rather than directly predicting biological rules (see \emph{e.g.}
-Pichler et al., 2020 for an overview), which may be confounded by the
-sparse nature of graph data, learning embeddings works in the
-low-dimensional space that maximizes information about the network
-structure. This approach is further justified by the observation, for
-example, that the macro-evolutionary history of a network is adequately
-represented by some graph embeddings {[}Random dot product graphs
-(RDPG); see Dalla Riva \& Stouffer (2016){]}. In a recent publication,
-Strydom et al. (2022) have used an embedding (based on RDPG) to project
-a metaweb of trophic interactions between European mammals, and
-transferred this information to mammals of Canada, using the
-phylogenetic distance between related clades to infer the values in the
-latent sub-space into which the European metaweb was projected. By
-performing the RDPG step on re-constructed values, this approach yields
-a probabilistic trophic metaweb for mammals of Canada based on knowledge
-of European species, despite a limited (\(\approx\) 5\%) taxonomic
-overlap.
-
-Graph embeddings \emph{can} serve as a dimensionality reduction method.
-For example, RDPG (Strydom et al., 2022) and t-SVD {[}truncated Singular
-Value Decomposition; Poisot et al. (2021){]} typically embed networks
-using fewer dimensions than the original network {[}the original network
-has as many dimensions as species, and as many informative dimensions as
-trophically unique species; Strydom, Dalla Riva, et al. (2021){]}. But
-this is not necessarily the case -- indeed, one may perform a PCA (a
-special case of SVD) to project the raw data into a subspace that
-improves the efficacy of t-SNE {[}t-distributed stochastic neighbor
-embedding; Maaten (2009){]}. There are many dimensionality reductions
-(Anowar et al., 2021) that can be applied to an embedded network should
-the need for dimensionality reduction (for example for data
-visualization) arise. In brief, many graph embeddings \emph{can} serve
-as dimensionality reduction steps, but not all do, neither do all
-dimensionality reduction methods provide adequate graph embedding
-capacities. In the next section (and fig.~\ref{fig:embedding}), we show
-how the amount of dimensionality reduction can affect the quality of the
-embedding.
-
 \hypertarget{an-illustration-of-metaweb-embedding}{%
@@
 
-\hypertarget{the-metaweb-embeds-both-ecological-hypotheses-and-practices}{%
-\section{The metaweb embeds both ecological hypotheses and
-practices}\label{the-metaweb-embeds-both-ecological-hypotheses-and-practices}}
-
-The goal of metaweb inference is to provide information about the
-interactions between species at a large spatial scale. But as Herbert
-(1965) rightfully pointed out, ``{[}y{]}ou can't draw neat lines around
-planet-wide problems''; any inference of a metaweb at large scales must
-contend with several novel, and interwoven, families of problems. In
-this section, we list some of the most pressing research priorities
-(\emph{i.e.} problems that can be addressed with subsequent data
-analysis or simulations), as well as issues related to the application
-of these methods at the science-policy interface.
+\hypertarget{the-metaweb-merges-ecological-hypotheses-and-practices}{%
+\section{The metaweb merges ecological hypotheses and
+practices}\label{the-metaweb-merges-ecological-hypotheses-and-practices}}
+
+Metaweb inference seeks to provide information about the interactions
+between species at a large spatial scale, typically a scale large enough
+to be considered of biogeographic relevance (indeed, many of the
+examples covered in the introduction span areas larger than a country,
+some of them global). But as Herbert (1965) rightfully pointed out,
+``{[}y{]}ou can't draw neat lines around planet-wide problems''; any
+inference of a metaweb must therefore contend with several novel,
+interwoven, families of problems. In this section, we outline three that
+we think are particularly important, and can discuss how they may
+addressed with subsequent data analysis or simulations, and how they
+emerge in the specific context of using embeddings; some of these issues
+are related to the application of these methods at the science-policy
+interface.
 
@@
 species (through phylogenetic relatedness or similarity of functional
-traits) to make a reliable inference decreases; this would likely be
-indicated by large confidence intervals during estimation of the values
-in the low-rank space, meaning that the representation of the original
-graph is difficult to transfer to the new problem. Alternatively, if the
-initial metaweb is too large (taxonomically), then the resulting
-embeddings would need to represent interactions between taxonomic groups
-that are not present in the new location. This would lead to a much
-higher variance in the starting dataset, and to under-dispersion in the
-target dataset, resulting in the potential under or over estimation of
-the strength of new predicted interactions. The lack of well documented
-metawebs is currently preventing the development of more concrete
-guidelines. The question of phylogenetic relatedness and distribution is
-notably relevant if the metaweb is assembled in an area with mostly
-endemic species (\emph{e.g.} a system that has undergone recent
-radiation or that has remained in isolation for a long period of time
-might not have an analogous system with which to draw knowledge from),
-and as with every predictive algorithm, there is room for the
+traits) to make a reliable inference decreases. This is because transfer
+requires similarity (fig.~\ref{fig:embedding}). A diagnostic for the
+lack of similar species would likely be large confidence intervals
+during estimation of the values in the low-rank space. In other words,
+the representation of the original graph is difficult to transfer to the
+new problem. Alternatively, if the initial metaweb is too large
+(taxonomically), then the resulting embeddings would need to represent
+interactions between taxonomic groups that are not present in the new
+location. This would lead to a much higher variance in the starting
+dataset, and to under-dispersion in the target dataset, resulting in the
+potential under or over estimation of the strength of new predicted
+interactions. Llewelyn et al. (2022) provide compelling evidence for
+these situations by showing that, even at small spatial scales, the
+transfer of information about interactions becomes more challenging when
+areas rich with endemic species are considered. The lack of well
+documented metawebs is currently preventing the development of more
+concrete guidelines. The question of phylogenetic relatedness and
+distribution is notably relevant if the metaweb is assembled in an area
+with mostly endemic species (\emph{e.g.} a system that has undergone
+recent radiation or that has remained in isolation for a long period of
+time might not have an analogous system with which to draw knowledge
+from), and as with every predictive algorithm, there is room for the
 application of our best ecological judgement. Because this problem
@@
 
-The area used to infer the new metaweb in determines the species pool
-that must be used to perform this embedding. Metawebs can be constructed
-by assigning interactions in a list of species within geographic
-boundaries. The upside of this approach is that information at the
-country level is likely to be required for biodiversity assessments, as
-countries set conservation goals at the national level (Buxton et al.,
-2021), and as quantitative instruments are designed to work at these
-scales (Turak et al., 2017); specific strategies are often enacted at
-smaller scales, nested within a specific country (Ray et al., 2021). But
-there is no guarantee that these boundaries are meaningful. In fact, we
-do not have a satisfying answer to the question of ``where does an
-ecological network stop?''. Recent results by Martins et al. (2022)
-suggest that networks are shaped within eco-regions, with abrupt
-structural transitions from an eco-region to the next. Should this trend
-hold generally, this would provide an ecologically-relevant scale at
-which metawebs can be downscaled and predicted. Other solutions leverage
-network-area relationships to identify areas in which networks are
-structurally similar (see \emph{e.g.} Fortin et al., 2021; Galiana et
-al., 2022, 2018), which requires ample pre-existing information about
-the network. This suggests that inferred metawebs should be further
-downscaled to allow for \emph{a posteriori} analyses; Llewelyn et al.
-(2022) provide compelling evidence for the fact that when a place is
-rich in endemic species, even at smaller spatial scales, the transfer of
-information about interactions becomes more challenging, re-emphasizing
-the need to identify guidelines for when and where network predictions
-can be mapped.
+The area for which we seek to predict the metaweb should determine the
+species pool on which the embedding is performed. Metawebs can be
+constructed by assigning interactions in a list of species within
+geographic boundaries. The upside of this approach is that information
+relevant for the construction of this dataset is likely to exist, as
+countries usually set conservation goals at the national level (Buxton
+et al., 2021), and as quantitative instruments are consequently designed
+to work at these scales (Turak et al., 2017); specific strategies are
+often enacted at smaller scales, nested within a specific country (Ray
+et al., 2021). But there is no guarantee that these boundaries are
+meaningful. In fact, we do not have a satisfying answer to the question
+of ``where does an ecological network stop?'', the answer to which would
+dictate the spatial span to embed/predict. Recent results by Martins et
+al. (2022) suggest that networks are shaped within eco-regions, with
+abrupt structural transitions from an eco-region to the next. Should
+this trend hold generally, this would provide an ecologically-relevant
+scale at which metawebs can be downscaled and predicted. Other solutions
+could leverage network-area relationships to identify areas in which
+networks are structurally similar (see \emph{e.g.} Fortin et al., 2021;
+Galiana et al., 2022, 2018). Both of these solutions requires ample
+pre-existing information about the network in space. Nevertheless, the
+inclusion of species for which we have data but that are not in the
+right spatial extent\emph{may} improve the performance of approaches
+based on embedding and transfer, \emph{if} they increase the similarity
+between the target and destination network. This proposal can
+specifically be evaluated by adding nodes to the network to embed, and
+evaluating the performance of predictive models (see \emph{e.g.}
+Llewelyn et al., 2022).
 
@@
 
-Operating under the context of national divisions, in large parts of the
-world, reflects nothing more than the legacy of settler colonialism,
-which drives a disparity in available ecological data. Applying any
-embedding to biased data does not debias them, but instead embeds these
-very same biases, propagating them to the machine learning models using
-embeddings to make predictions. Indeed, the use of ecological data
-itself is not an apolitical act (Nost \& Goldstein, 2021), as data
-infrastructures tend to be designed to answer questions within national
-boundaries (therefore placing contingencies on what is available to be
-embedded). Furthermore, their use often draws upon, and reinforces,
-territorial statecraft (see \emph{e.g.} Barrett, 2005). As per Machen \&
-Nost (2021), these biases are particularly important to consider when
-the output of ``algorithmic thinking'' (\emph{i.e.} relying on machine
-learning to generate knowledge or as a substitute to human
-decision-making) can be re-purposed for governance (\emph{e.g.} enacting
-conservation decisions on the basis of model prediction). As information
-on species interaction networks structure is increasingly leveraged as a
-tool to guide conservation actions (see \emph{e.g.} Eero et al., 2021;
-Naman et al., 2022; Stier et al., 2017), the need to appraise and
-correct biases that are unwittingly propagated to algorithms when
-embedded from the original data is paramount. These considerations are
-even more urgent in the specific context of biodiversity data, as
-long-term colonial legacies still shape taxonomic composition to this
-day (Lenzner et al., 2022; Raja, 2022), and where much shorter-term
-changes in taxonomic and genetic richness of wildlife emerged through
-environmental racism (Schmidt \& Garroway, 2022).
-
-\hypertarget{conclusion-metaweb-prediction-in-context}{%
-\section{Conclusion: metaweb prediction in
-context}\label{conclusion-metaweb-prediction-in-context}}
-
-Predictive approaches, regardless of the scale at which they are
-deployed and the intent of their deployment, originate in the framework
-that contributed to the ongoing biodiversity crisis (Adam, 2014) and
-reinforced environmental injustice (Choudry, 2013; Domínguez \& Luoma,
-2020). The risk of embedding this legacy in our models is great,
-especially when the impact of this legacy on species pools is being
-increasingly documented. This problem can be addressed by re-framing the
-way we interact with models, especially in the context where these
-models are intended to support conservation actions. Particularly on
-territories that were traditionally stewarded by Indigenous people,
-these approaches should be replaced (or at least guided and framed) by
-Indigenous principles of land management (Eichhorn et al., 2019; No'kmaq
-et al., 2021), as part of an ``algorithm-in-the-loop'' approach.
+In large parts of the world, geographic boundaries only reflect the
+legacy of settler colonialism, which drives global disparity in capacity
+to collect and publish ecological data. Applying any embedding to biased
+data does not debias them, but rather embeds these biases, propagating
+them to the models using embeddings to make predictions. Furthermore,
+the use of ecological data itself is not an apolitical act (Nost \&
+Goldstein, 2021): data infrastructures tend to be designed to answer
+questions within national boundaries (therefore placing contingencies on
+what is available to be embedded), their use often drawing upon, and
+reinforcing, territorial statecraft (see \emph{e.g.} Barrett, 2005). As
+per Machen \& Nost (2021), these biases are particularly important to
+consider when knowledge generated algorithmically is used to supplement
+or replace human decision-making, especially for governance (\emph{e.g.}
+enacting conservation decisions on the basis of model prediction). As
+information on networks is increasingly leveraged for conservation
+actions (see \emph{e.g.} Eero et al., 2021; Naman et al., 2022; Stier et
+al., 2017), the need to appraise and correct biases that are unwittingly
+propagated to algorithms when embedded from the original data is
+immense. These considerations are even more urgent in the specific
+context of biodiversity data. Long-term colonial legacies still shape
+taxonomic composition to this day (Lenzner et al., 2022; Raja, 2022),
+and much shorter-term changes in taxonomic and genetic richness of
+wildlife emerged through environmental racism (Schmidt \& Garroway,
+2022). These considerations mean that ``the set of species found at a
+place'' is not only a response to ecological processes, and therefore
+there may exist forcing on the interactions between these species.
+
+\hypertarget{conclusion-metawebs-predictions-and-people}{%
+\section{Conclusion: metawebs, predictions, and
+people}\label{conclusion-metawebs-predictions-and-people}}
+
+Predictive approaches in ecology, regardless of the scale at which they
+are deployed and the intent of their deployment, originate in the
+framework that contributed to the ongoing biodiversity crisis (Adam,
+2014) and reinforced environmental injustice (Choudry, 2013; Domínguez
+\& Luoma, 2020). The risk of embedding this legacy in our models is
+real, especially when the impact of this legacy on species pools is
+being increasingly documented. This problem can be addressed by
+re-framing the way we interact with models, especially when models are
+intended to support conservation actions. Particularly on territories
+that were traditionally stewarded by Indigenous people, we must
+interrogate how predictive approaches and the biases that underpin them
+can be put to task in accompanying Indigenous principles of land
+management (Eichhorn et al., 2019; No'kmaq et al., 2021). The discussion
+of ``algorithm-in-the-loop'' approaches that is now pervasive in the
+machine learning community provides examples of why this is important.
 Human-algorithm interactions are notoriously difficult and can yield
@@
 suggesting the need to systematically study them for the specific
-purpose of biodiversity governance, as well as to improve the
-algorithmic literacy of decision makers. As we see artificial
-intelligence/machine learning being increasingly mobilized to generate
-knowledge that is lacking for conservation decisions (\emph{e.g.} Lamba
-et al., 2019; Mosebo Fernandes et al., 2020) and drive policy decisions
-(Weiskopf et al., 2022), our discussion of these tools need to go beyond
-the technical and statistical, and into the governance consequences they
-can have.
+purpose of, here, biodiversity governance. Improving the algorithmic
+literacy of decision makers is part of the solution (\emph{e.g.} Lamba
+et al., 2019; Mosebo Fernandes et al., 2020), as we can reasonably
+expect that model outputs will be increasingly used to drive policy
+decisions (Weiskopf et al., 2022). Our discussion of these approaches
+need to go beyond the technical and statistical, and into the governance
+consequences they can have. To embed data also embeds historical and
+contemporary biases that acted on these data, both because they shaped
+the ecological processes generating them, and the global processes
+leading to their measurement and publication. For a domain as vast as
+species interaction networks, these biases exist at multiple scales
+along the way, and a challenge for prediction is not only to develop (or
+adopt) new quantitative tools, but to assess the behavior of these tools
+in the proper context.
 

### 2023-01-26 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@41a86090a2b482457cb251048e354194819eea58 🚀

@@
 
+\hypertarget{graph-embeddings-produce-latent-variables-but-not-traits}{%
+\subsection{Graph embeddings produce latent variables (but not
+traits)}\label{graph-embeddings-produce-latent-variables-but-not-traits}}
+
+Before moving further, it is important to clarify the epistemic status
+of node values derived from embeddings: specifically, they are
+\emph{not} functional traits, and therefore should not be discussed in
+terms of effects or responses. As per the framework of Malaterre et al.
+(2019), these values neither derive from, nor result in, changes in
+organismal performance, and should therefore not be used to quantify
+\emph{e.g.} functional diversity. This holds true even when there are
+correlations between latent values and functional traits: although these
+enable an ecological discussion of how traits condition the structure of
+the network, the existence of a statistical relationship does not
+elevate the latent values to the status of functional traits.
+
+Rather than directly predicting biological rules (see \emph{e.g.}
+Pichler et al., 2020 for an overview), which may be confounded by the
+sparse nature of graph data, learning embeddings works in the
+low-dimensional space that maximizes information about the network
+structure. This approach is further justified by the observation, for
+example, that the macro-evolutionary history of a network is adequately
+represented by some graph embeddings {[}Random dot product graphs
+(RDPG); see Dalla Riva \& Stouffer (2016){]}. In a recent publication,
+Strydom et al. (2022) have used an embedding (based on RDPG) to project
+a metaweb of trophic interactions between European mammals, and
+transferred this information to mammals of Canada, using the
+phylogenetic distance between related clades to infer the values in the
+latent sub-space into which the European metaweb was projected. By
+performing the RDPG step on re-constructed values, this approach yields
+a probabilistic trophic metaweb for mammals of Canada based on knowledge
+of European species, despite a limited (\(\approx\) 5\%) taxonomic
+overlap, and illustrates how the values derived from an embedding can be
+used for prediction without being ``traits'' of the species they
+represent.
+
 \hypertarget{ecological-networks-are-good-candidates-for-embedding}{%
@@
 embeddings while also preserving network structure.
-
-\hypertarget{graph-embeddings-produce-novel-latent-variables-to-predict-interactions}{%
-\subsection{Graph embeddings produce novel latent variables to predict
-interactions}\label{graph-embeddings-produce-novel-latent-variables-to-predict-interactions}}
-
-Before moving further, it is important to clarify the epistemic status
-of node values derived from embeddings: specifically, they are
-\emph{not} functional traits, and therefore should not be discussed in
-terms of effects or responses. As per the framework of Malaterre et al.
-(2019), these values neither derive from, nor result in, changes in
-organismal performance, and should therefore not be used to quantify
-\emph{e.g.} functional diversity. This holds true even when there are
-correlations between latent values and functional traits: although these
-enable an ecological discussion of how traits condition the structure of
-the network, the existence of a statistical relationship does not
-elevate the latent values to the status of functional traits.
-
-Rather than directly predicting biological rules (see \emph{e.g.}
-Pichler et al., 2020 for an overview), which may be confounded by the
-sparse nature of graph data, learning embeddings works in the
-low-dimensional space that maximizes information about the network
-structure. This approach is further justified by the observation, for
-example, that the macro-evolutionary history of a network is adequately
-represented by some graph embeddings {[}Random dot product graphs
-(RDPG); see Dalla Riva \& Stouffer (2016){]}. In a recent publication,
-Strydom et al. (2022) have used an embedding (based on RDPG) to project
-a metaweb of trophic interactions between European mammals, and
-transferred this information to mammals of Canada, using the
-phylogenetic distance between related clades to infer the values in the
-latent sub-space into which the European metaweb was projected. By
-performing the RDPG step on re-constructed values, this approach yields
-a probabilistic trophic metaweb for mammals of Canada based on knowledge
-of European species, despite a limited (\(\approx\) 5\%) taxonomic
-overlap.
 

### 2023-01-26 reviews/compile.sh
add script to compile responses

@@ -1,0 +1,1 @@
+find . -type f -name "*.md" -exec bash -c 'pandoc {} -o {}.pdf --template=../.assets/templates/responses.tex' \;

### 2023-01-30 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@3032c689da6f52ef691456e9389c596b3e43be49 🚀

@@
 {\Large\bfseries\sffamily Graph embedding and transfer learning can help
-predict species interaction networks despite data limitations}
+predict potential species interaction networks despite data limitations}
 \vskip 5em
@@
 predictive methods can help circumvent the limitations in data
-deficiencies, by providing `draft' metawebs.%
+deficiencies, by providing a `first approximation' of metawebs.%
     \item One way to improve our ability to predict metawebs is to
-maximize available information by using graph embeddings, instead of the
-list of species interactions. Graph embedding is an emerging field in
-machine learning that holds great potential for ecological problems.%
-    \item In this perspective, we outline how the challenges associated
-with inferring metawebs line-up with the advantages of graph embeddings;
-as well as discuss how the choice of the species pool has consequences
-on the reconstructed network, but also embeds hypotheses about which
-human-made boundaries are ecologically meaningful.%
+maximize available information by using graph embeddings, as opposed to
+an exhaustive list of species interactions. Graph embedding is an
+emerging field in machine learning that holds great potential for
+ecological problems.%
+    \item Here, we outline how the challenges associated with inferring
+metawebs line-up with the advantages of graph embeddings; followed by a
+discussion as to how the choice of the species pool has consequences on
+the reconstructed network, specifically as to the role of human-made (or
+arbitrarily assigned) boundaries and how these my influence ecological
+hypotheses.%
 \end{enumerate}
@@
 interaction networks over large spatial scales (Hortal et al., 2015).
-Robust inferences would not only boost our understanding of the
+Reliable inferences would not only boost our understanding of the
 structure of species interaction networks, but also increase the amount
@@
 prediction of interactions at large scales. First, there is a relative
-scarcity of relevant data in most places globally -- paradoxically, this
-restricts our ability to infer interactions to locations where inference
-is perhaps the least required (and leaves us unable to make inference in
-data scarce regions); second, accurate predictors are important for
-accurate predictions, and the lack of methods that can leverage a small
-amount of \emph{accurate} data is a serious impediment to our predictive
-ability. In most places, our most reliable biodiversity knowledge is
-that of a species pool (\emph{i.e.} a set of potentially interacting
-species in a given area): through the analysis of databases like the
-Global Biodiversity Information Facility (GBIF) or the International
-Union for the Conservation of Nature (IUCN), it is possible to construct
-a list of species for a region of interest; however inferring the
-potential interactions between these species still remains a challenge.
+scarcity of relevant data in most places globally -- restricting the
+inference of interactions to locations where least required (and leaves
+us unable to make inference in data scarce regions); second, accurate
+predictors are important for accurate predictions, and the lack of
+methods that can leverage a small amount of \emph{accurate} data is a
+serious impediment to our predictive ability. In most places, our most
+reliable biodiversity knowledge is that of a species pool where a set of
+potentially interacting species in a given area could occur: through the
+analysis of databases like the Global Biodiversity Information Facility
+(GBIF) or the International Union for the Conservation of Nature (IUCN),
+it is possible to construct a list of species for a region of interest;
+however inferring the potential interactions between these species still
+remains a challenge.
 
@@
 area (and so captures the \(\gamma\) diversity of interactions). The
-metaweb itself is not a prediction of the network at a specific point
-within the spatial area it covers: it will have a different structure,
-notably by having a larger connectance (see \emph{e.g.} Wood et al.,
-2015) and complexity (see \emph{e.g.} Galiana et al., 2022), from any of
-these local networks. These local networks (which capture the \(\alpha\)
-diversity of interactions) are a subset of the metaweb's species and
-realized interactions, and have been called ``metaweb realizations''
-(Poisot et al., 2015). Differences between local networks and their
-metawebs are due to chance, species abundance and co-occurrence, local
-environmental conditions, and local distribution of functional traits,
-among others. Specifically, although co-occurrence can be driven by
-interactions (Cazelles et al., 2016), co-occurrence alone is not a
-predictor of interactions (Blanchet et al., 2020; Thurman et al., 2019),
-and therefore lack of co-occurrence cannot be used to rule out lack of a
-feasible interaction. Yet, recent results by Saravia et al. (2021)
-strongly suggest that the local (metaweb) realizations only respond
-weakly to local conditions: instead, they reflect constraints inherited
-by the structure of their metaweb. This establishes the metaweb
-structure as the core goal of predictive network ecology, as it is a
-required information to accurately produce downscaled, local
+metaweb itself is not a prediction of local networks at specific
+locations within the spatial area it covers: it will have a different
+structure, notably by having a larger connectance (see \emph{e.g.} Wood
+et al., 2015) and complexity (see \emph{e.g.} Galiana et al., 2022),
+from any of these local networks. These local networks (which capture
+the \(\alpha\) diversity of interactions) are a subset of the metaweb's
+species and realized interactions, and have been called ``metaweb
+realizations'' (Poisot et al., 2015). Differences between local networks
+and their metawebs are due to chance, species abundance and
+co-occurrence, local environmental conditions, and local distribution of
+functional traits, among others. Specifically, although co-occurrence
+can be driven by interactions (Cazelles et al., 2016), co-occurrence
+alone is not a predictor of interactions (Blanchet et al., 2020; Thurman
+et al., 2019), and therefore lack of co-occurrence cannot be used to
+rule out lack of a feasible interaction. Yet, recent results by Saravia
+et al. (2021) strongly suggested that the local (metaweb) realizations
+only respond weakly to local conditions: instead, they reflect
+constraints inherited by the structure of their metaweb. This sets up
+the core goal of predictive network ecology as the prediction of metaweb
+structure, as it is required to accurately produce downscaled, local
 predictions.
@@
 highlight the power of viewing (and constructing) metawebs as
-\emph{probabilistic} objects in the context of rare interactions,
-discuss how a family of machine learning tools (graph embeddings and
-transfer learning) can be used to overcome data limitations to metaweb
-inference, and highlight how the use of metawebs introduces important
-questions for the field of network ecology.
+\emph{probabilistic} objects in the context of low-probability
+interactions, discuss how a family of machine learning tools (graph
+embeddings and transfer learning) can be used to overcome data
+limitations to metaweb inference, and highlight how the use of metawebs
+introduces important questions for the field of network ecology.
 
@@
 these observations, we expect to see an over-representation of
-low-probability (rare) interactions under a model that accurately
-predicts interaction probabilities.
+low-probability (hereafter rare) interactions under a model that
+accurately predicts interaction probabilities.
 
@@
 
-Graph (or Network) embedding (fig.~\ref{fig:embedding}) is a family of
+Graph (or network) embedding (fig.~\ref{fig:embedding}) is a family of
 machine learning techniques, whose main task is to learn a mapping
@@
 of node values derived from embeddings: specifically, they are
-\emph{not} functional traits, and therefore should not be discussed in
+\emph{not} functional traits, and therefore should not be interpreted in
 terms of effects or responses. As per the framework of Malaterre et al.
@@
 
-Indeed, food webs are inherently low-dimensional objects, and can be
-adequately represented with less than ten dimensions (J. Braga et al.,
-2019; M. P. Braga et al., 2021; Eklöf et al., 2013). Simulation results
-by Botella et al. (2022) suggests that there is no dominant method to
-identify architectural similarities between networks: multiple
-approaches need to be tested and compared to the network descriptor of
-interest on a problem-specific basis. This matches previous results on
-graph embedding, wherein different embedding algorithms yield different
+Food webs are inherently low-dimensional objects, and can be adequately
+represented with less than ten dimensions (J. Braga et al., 2019; M. P.
+Braga et al., 2021; Eklöf et al., 2013). Simulation results by Botella
+et al. (2022) suggested that there is no dominant method to identify
+architectural similarities between networks: multiple approaches need to
+be tested and compared to the network descriptor of interest on a
+problem-specific basis. This matches previous results on graph
+embedding, wherein different embedding algorithms yield different
 network embeddings (Goyal \& Ferrara, 2018), calling for a careful
@@
 rely largely on linear algebra or pseudo-random walks on graphs. All
-forms of embeddings presented in the table share the common property of
-summarizing their objects into (sets of) dense feature vectors, that
-capture the overall network structure, pairwise information on nodes,
-and emergent aspects of the network, in a compressed way (\emph{i.e.}
-with some information loss, as we later discuss in the illustration).
-Node embeddings tend to focus on maintaining pairwise relationships
-(\emph{i.e.} species interactions), while graph embeddings focus on
-maintaining the network structure (\emph{i.e.} emergent properties).
-Nevertheless, some graph embedding techniques (like RDPG, see
-\emph{e.g.} Wu et al., 2021) will provide high-quality node-level
-embeddings while also preserving network structure.
+forms of embeddings presented in tbl.~\ref{tbl:methods} share the common
+property of summarizing their objects into (sets of) dense feature
+vectors, that capture the overall network structure, pairwise
+information on nodes, and emergent aspects of the network, in a
+compressed way (\emph{i.e.} with some information loss, as we later
+discuss in the illustration). Node embeddings tend to focus on
+maintaining pairwise relationships (\emph{i.e.} species interactions),
+while graph embeddings focus on maintaining the network structure
+(\emph{i.e.} emergent properties). Nevertheless, some graph embedding
+techniques (like RDPG, see \emph{e.g.} Wu et al., 2021) will provide
+high-quality node-level embeddings while also preserving network
+structure.
 
@@
 embedding of the metaweb that captures enough variance to be relevant;
-specifically, this is true both of \(L_2\) loss (indicating that RDPG is
-able to capture pairwise processes) and the cumulative variance
+specifically, this is true for both \(L_2\) loss (indicating that RDPG
+is able to capture pairwise processes) and the cumulative variance
 explained (indicating that RDPG is able to capture network-level
@@
 potential under or over estimation of the strength of new predicted
-interactions. Llewelyn et al. (2022) provide compelling evidence for
+interactions. Llewelyn et al. (2022) provided compelling evidence for
 these situations by showing that, even at small spatial scales, the
@@
 constructed by assigning interactions in a list of species within
-geographic boundaries. The upside of this approach is that information
+specific regions. The upside of this approach is that information
 relevant for the construction of this dataset is likely to exist, as
@@
 often enacted at smaller scales, nested within a specific country (Ray
-et al., 2021). But there is no guarantee that these boundaries are
-meaningful. In fact, we do not have a satisfying answer to the question
-of ``where does an ecological network stop?'', the answer to which would
-dictate the spatial span to embed/predict. Recent results by Martins et
-al. (2022) suggest that networks are shaped within eco-regions, with
-abrupt structural transitions from an eco-region to the next. Should
-this trend hold generally, this would provide an ecologically-relevant
-scale at which metawebs can be downscaled and predicted. Other solutions
-could leverage network-area relationships to identify areas in which
-networks are structurally similar (see \emph{e.g.} Fortin et al., 2021;
-Galiana et al., 2022, 2018). Both of these solutions requires ample
-pre-existing information about the network in space. Nevertheless, the
-inclusion of species for which we have data but that are not in the
-right spatial extent\emph{may} improve the performance of approaches
-based on embedding and transfer, \emph{if} they increase the similarity
-between the target and destination network. This proposal can
-specifically be evaluated by adding nodes to the network to embed, and
-evaluating the performance of predictive models (see \emph{e.g.}
-Llewelyn et al., 2022).
+et al., 2021). But there is no guarantee that these arbitrary boundaries
+are meaningful. In fact, we do not have a satisfying answer to the
+question of ``where does an ecological network stop?'', the answer to
+which would dictate the spatial span to embed/predict. Recent results by
+Martins et al. (2022) suggested that networks are shaped within
+eco-regions, with abrupt structural transitions from an eco-region to
+the next. Should this trend hold generally, this would provide an
+ecologically-relevant scale at which metawebs can be downscaled and
+predicted. Other solutions could leverage network-area relationships to
+identify areas in which networks are structurally similar (see
+\emph{e.g.} Fortin et al., 2021; Galiana et al., 2022, 2018). Both of
+these solutions requires ample pre-existing information about the
+network in space. Nevertheless, the inclusion of species for which we
+have data but that are not in the right spatial extent\emph{may} improve
+the performance of approaches based on embedding and transfer, \emph{if}
+they increase the similarity between the target and destination network.
+This proposal can specifically be evaluated by adding nodes to the
+network to embed, and evaluating the performance of predictive models
+(see \emph{e.g.} Llewelyn et al., 2022).
 
@@
 
-In large parts of the world, geographic boundaries only reflect the
-legacy of settler colonialism, which drives global disparity in capacity
-to collect and publish ecological data. Applying any embedding to biased
-data does not debias them, but rather embeds these biases, propagating
-them to the models using embeddings to make predictions. Furthermore,
-the use of ecological data itself is not an apolitical act (Nost \&
-Goldstein, 2021): data infrastructures tend to be designed to answer
-questions within national boundaries (therefore placing contingencies on
-what is available to be embedded), their use often drawing upon, and
-reinforcing, territorial statecraft (see \emph{e.g.} Barrett, 2005). As
-per Machen \& Nost (2021), these biases are particularly important to
-consider when knowledge generated algorithmically is used to supplement
-or replace human decision-making, especially for governance (\emph{e.g.}
-enacting conservation decisions on the basis of model prediction). As
-information on networks is increasingly leveraged for conservation
-actions (see \emph{e.g.} Eero et al., 2021; Naman et al., 2022; Stier et
-al., 2017), the need to appraise and correct biases that are unwittingly
-propagated to algorithms when embedded from the original data is
-immense. These considerations are even more urgent in the specific
-context of biodiversity data. Long-term colonial legacies still shape
-taxonomic composition to this day (Lenzner et al., 2022; Raja, 2022),
-and much shorter-term changes in taxonomic and genetic richness of
-wildlife emerged through environmental racism (Schmidt \& Garroway,
-2022). These considerations mean that ``the set of species found at a
-place'' is not only a response to ecological processes, and therefore
-there may exist forcing on the interactions between these species.
+In large parts of the world, boundaries that delineate geographic
+regions are merely a reflection the legacy of settler colonialism, which
+drives global disparity in capacity to collect and publish ecological
+data. Applying any embedding to biased data does not debias them, but
+rather embeds these biases, propagating them to the models using
+embeddings to make predictions. Furthermore, the use of ecological data
+itself is not an apolitical act (Nost \& Goldstein, 2021): data
+infrastructures tend to be designed to answer questions within national
+boundaries (therefore placing contingencies on what is available to be
+embedded), their use often drawing upon, and reinforcing, territorial
+statecraft (see \emph{e.g.} Barrett, 2005). As per Machen \& Nost
+(2021), these biases are particularly important to consider when
+knowledge generated algorithmically is used to supplement or replace
+human decision-making, especially for governance (\emph{e.g.} enacting
+conservation decisions on the basis of model prediction). As information
+on networks is increasingly leveraged for conservation actions (see
+\emph{e.g.} Eero et al., 2021; Naman et al., 2022; Stier et al., 2017),
+the need to appraise and correct biases that are unwittingly propagated
+to algorithms when embedded from the original data is immense. These
+considerations are even more urgent in the specific context of
+biodiversity data. Long-term colonial legacies still shape taxonomic
+composition to this day (Lenzner et al., 2022; Raja, 2022), and much
+shorter-term changes in taxonomic and genetic richness of wildlife
+emerged through environmental racism (Schmidt \& Garroway, 2022). These
+considerations mean that ``the set of species found at a place'' is not
+only a response to ecological processes, and therefore there may exist
+forcing on the interactions between these species.
 

### 2023-01-30 Strydom_et_al_2023_graph_embedding_preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@3032c689da6f52ef691456e9389c596b3e43be49 🚀

@@
 \noindent {\LARGE \textbf{\textsf{Graph embedding and transfer learning
-can help predict species interaction networks despite data
+can help predict potential species interaction networks despite data
 limitations}}}

### 2023-01-31 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@d617ee537b1f749c11b972569a02582eedf50247 🚀

@@
 \begin{enumerate}
-    \item Metawebs, (networks of potential interactions within a species
+    \item Metawebs (networks of potential interactions within a species
 pool) are a powerful abstraction to understand how large-scale species
@@
 predictive methods can help circumvent the limitations in data
-deficiencies, by providing a `first approximation' of metawebs.%
+deficiencies, by providing a first approximation of metawebs.%
     \item One way to improve our ability to predict metawebs is to
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1016}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1172}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2500}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1875}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3438}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0660}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0761}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1624}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1218}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.5736}}@{}}
 \caption{\label{tbl:methods}Overview of some common graph embedding
@@
 tSNE & nodes & statistical divergence & Hinton \& Roweis (2002) &
-Cieslak et al. (2020) \(^a\) Gibb et al. (2021) \\
+{[}species-environment responses \(^a\); Cieslak et al. (2020){]}
+{[}host-virus network representation; Gibb et al. (2021){]} \\
 LINE & nodes & stochastic gradient descent & Tang et al. (2015) & \\
@@
 HARP & nodes & meta-strategy & H. Chen et al. (2017) & \\
-DMSE & joint nodes & deep neural network & D. Chen et al. (2017) & D.
-Chen et al. (2017) \(^b\) \\
+DMSE & joint nodes & deep neural network & D. Chen et al. (2017) &
+{[}species-environment interactions \(^b\); D. Chen et al. (2017){]} \\
 graph2vec & sub-graph & skipgram network & Narayanan et al. (2017) & \\
-RDPG & graph & SVD & Young \& Scheinerman (2007) & Dalla Riva \&
-Stouffer (2016); Poisot et al. (2021) \\
+RDPG & graph & SVD & Young \& Scheinerman (2007) & {[}trophic
+interactions; Dalla Riva \& Stouffer (2016){]} {[}host-virus network
+prediction; Poisot et al. (2021){]} \\
 GLEE & graph & Laplacian eigenmap & Torres et al. (2020) & \\
 DeepWalk & graph & stochastic gradient descent & Perozzi et al. (2014) &
-Wardeh et al. (2021) \\
+{[}host-virus interactions; Wardeh et al. (2021){]} \\
 GraphKKE & graph & stochastic differential equation & Melnyk et al.
-(2020) & Melnyk et al. (2020) \(^a\) \\
+(2020) & {[}microbiote species associations \(^a\); Melnyk et al.
+(2020){]} \\
 FastEmbed & graph & eigen decomposition & Ramasamy \& Madhow (2015) & \\
-PCA & graph & eigen decomposition & Surendran (2013) & Strydom, Catchen,
-et al. (2021) \\
+PCA & graph & eigen decomposition & Surendran (2013) & {[}host-parasite
+interactions; Strydom, Catchen, et al. (2021){]} \\
 Joint methods & multiple graphs & multiple strategies & S. Wang et al.

### 2023-01-31 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@2964e56d1c5b8415fd783a8ab2eae6e33c54e1a6 🚀

@@
 tSNE & nodes & statistical divergence & Hinton \& Roweis (2002) &
-{[}species-environment responses \(^a\); Cieslak et al. (2020){]}
-{[}host-virus network representation; Gibb et al. (2021){]} \\
+(Cieslak et al., 2020, species-environment responses \(^a\)) (Gibb et
+al., 2021, host-virus network representation) \\
 LINE & nodes & stochastic gradient descent & Tang et al. (2015) & \\
@@
 HARP & nodes & meta-strategy & H. Chen et al. (2017) & \\
-DMSE & joint nodes & deep neural network & D. Chen et al. (2017) &
-{[}species-environment interactions \(^b\); D. Chen et al. (2017){]} \\
+DMSE & joint nodes & deep neural network & D. Chen et al. (2017) & (D.
+Chen et al., 2017, species-environment interactions \(^b\)) \\
 graph2vec & sub-graph & skipgram network & Narayanan et al. (2017) & \\
-RDPG & graph & SVD & Young \& Scheinerman (2007) & {[}trophic
-interactions; Dalla Riva \& Stouffer (2016){]} {[}host-virus network
-prediction; Poisot et al. (2021){]} \\
+RDPG & graph & SVD & Young \& Scheinerman (2007) & (Dalla Riva \&
+Stouffer, 2016, trophic interactions) (Poisot et al., 2021, host-virus
+network prediction) \\
 GLEE & graph & Laplacian eigenmap & Torres et al. (2020) & \\
 DeepWalk & graph & stochastic gradient descent & Perozzi et al. (2014) &
-{[}host-virus interactions; Wardeh et al. (2021){]} \\
+(Wardeh et al., 2021, host-virus interactions) \\
 GraphKKE & graph & stochastic differential equation & Melnyk et al.
-(2020) & {[}microbiote species associations \(^a\); Melnyk et al.
-(2020){]} \\
+(2020) & (Melnyk et al., 2020, microbiote species associations
+\(^a\)) \\
 FastEmbed & graph & eigen decomposition & Ramasamy \& Madhow (2015) & \\
-PCA & graph & eigen decomposition & Surendran (2013) & {[}host-parasite
-interactions; Strydom, Catchen, et al. (2021){]} \\
+PCA & graph & eigen decomposition & Surendran (2013) & (Strydom,
+Catchen, et al., 2021, host-parasite interactions) \\
 Joint methods & multiple graphs & multiple strategies & S. Wang et al.

### 2023-01-31 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@771317a3716ac0d55a20b4d8398e9866760ad3f4 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@fb8d110628b0a1dd021f89530054474415ba9ba0 🚀

@@
 the \(\alpha\) diversity of interactions) are a subset of the metaweb's
-species and realized interactions, and have been called ``metaweb
+species and its realized interactions, and have been called ``metaweb
 realizations'' (Poisot et al., 2015). Differences between local networks
@@
 alone is not a predictor of interactions (Blanchet et al., 2020; Thurman
-et al., 2019), and therefore lack of co-occurrence cannot be used to
-rule out lack of a feasible interaction. Yet, recent results by Saravia
-et al. (2021) strongly suggested that the local (metaweb) realizations
-only respond weakly to local conditions: instead, they reflect
-constraints inherited by the structure of their metaweb. This sets up
-the core goal of predictive network ecology as the prediction of metaweb
-structure, as it is required to accurately produce downscaled, local
-predictions.
+et al., 2019), and therefore the lack of co-occurrence cannot be used to
+infer the lack of a feasible interaction. Yet, recent results by Saravia
+et al. (2021) strongly suggested that local (metaweb) realizations only
+respond weakly to local conditions: instead, they reflect constraints
+inherited by the structure of their metaweb. This sets up the core goal
+of predictive network ecology as the prediction of metaweb structure, as
+it is required to accurately produce downscaled, local predictions.
 
@@
 a more nuanced and realistic way to represent them. Dallas et al. (2017)
-suggested that most links in ecological networks are cryptic,
-\emph{i.e.} uncommon or hard to observe. This argument echoes Jordano
-(2016): sampling ecological interactions is difficult because it
+suggested that most interactions (links) in ecological networks are
+cryptic, \emph{i.e.} uncommon or hard to observe. This argument echoes
+Jordano (2016): sampling ecological interactions is difficult because it
 requires first the joint observation of two species, and then the
 observation of their interaction. In addition, it is generally expected
-that weak or rare links will be more prevalent in networks than common
-or strong links (Csermely, 2004), compared to strong, persistent links;
-this is notably the case in food chains, wherein many weaker links are
-key to the stability of a system (Neutel et al., 2002). In the light of
-these observations, we expect to see an over-representation of
-low-probability (hereafter rare) interactions under a model that
-accurately predicts interaction probabilities.
-
-Yet the original metaweb definition, and indeed most past uses of
-metawebs, was based on the presence/absence of interactions. Moving
+that weak or rare interactions will be more prevalent in networks than
+common or strong interactions (Csermely, 2004), compared to strong,
+persistent interactions; this is notably the case in food chains,
+wherein many weaker interactions are key to the stability of a system
+(Neutel et al., 2002). In the light of these observations, we expect to
+see an over-representation of low-probability (hereafter rare)
+interactions under a model that accurately predicts interaction
+probabilities. Although defining an interaction as `rare' is perhaps not
+as straight forward as one may assume (rare in the context of likelihood
+of occurrence or the context of biologically plausible?) but for the
+context of the discussion in this manuscript the core idea is that
+construction of probabilistic networks affords us the nuance of
+capturing this inherit variability of interaction occurrence.
+
+Critically, the original metaweb definition, and indeed most past uses
+of metawebs, was based on the presence/absence of interactions. Moving
 towards \emph{probabilistic} metawebs, by representing interactions as
@@
 biological feasibility of interactions, which is usually hard to obtain
-yet has possibly the most potential to boost our predictive ability
-(Bartomeus, 2013; Bartomeus et al., 2016). This would represent a
-departure from simple rules expressed at the network scale (\emph{e.g.}
-Williams \& Martinez, 2000) to a view of network prediction based on
-learning the rules that underpin interactions \emph{and} their
+yet has possibly the most potential to boost our predictive ability of
+local networks (Bartomeus, 2013; Bartomeus et al., 2016). This would
+represent a departure from simple rules expressed at the network scale
+(\emph{e.g.} Williams \& Martinez, 2000) to a view of network prediction
+based on learning the rules that underpin interactions \emph{and} their
 variability (Gupta et al., 2022).
@@
 
-\hypertarget{graph-embeddings-produce-latent-variables-but-not-traits}{%
-\subsection{Graph embeddings produce latent variables (but not
-traits)}\label{graph-embeddings-produce-latent-variables-but-not-traits}}
+\hypertarget{graph-embedding-produces-latent-variables-but-not-traits}{%
+\subsection{Graph embedding produces latent variables (but not
+traits)}\label{graph-embedding-produces-latent-variables-but-not-traits}}
 
@@
 phylogenetic distance between related clades to infer the values in the
-latent sub-space into which the European metaweb was projected. By
+latent subspace into which the European metaweb was projected. By
 performing the RDPG step on re-constructed values, this approach yields
@@
 has as many dimensions as species, and as many informative dimensions as
-trophically unique species; Strydom, Dalla Riva, et al. (2021){]}. But
-this is not necessarily the case -- indeed, one may perform a PCA (a
-special case of SVD) to project the raw data into a subspace that
+trophically unique species; Strydom, Dalla Riva, et al. (2021){]}.
+However, this is not necessarily the case -- indeed, one may perform a
+PCA (a special case of SVD) to project the raw data into a subspace that
 improves the efficacy of t-SNE {[}t-distributed stochastic neighbor
@@
 deliver larger datasets on species interactions (Bohan et al., 2017),
-there is a potential for GNN to become an applicable
+there is nevertheless the potential for GNN to become an applicable
 embedding/predictive technique in the coming years.
@@
 associations/interactions, despite not being strictly speaking, a graph
-embedding technique (see \emph{e.g.} Chami et al., 2022)}\tabularnewline
+embedding technique (see \emph{e.g.} Chami et al.,
+2022).}\tabularnewline
 \toprule()
@@
 GraphKKE & graph & stochastic differential equation & Melnyk et al.
-(2020) & (Melnyk et al., 2020, microbiote species associations
+(2020) & (Melnyk et al., 2020, microbiome species associations
 \(^a\)) \\
@@
 Goebel et al., 2023; Gravel et al., 2013). Relating this information to
-an embedding rather than a list of networks measures would allow to
+an embedding rather than a list of network measures would allow to
 capture their effect on the more fundamental aspects of network
@@
 interactions are observed, not-observed, or unknown due to lack of
-co-occurrence. This reveals that the observed interactions have higher
-predicted weights, although there is some overlap; the usual approach to
-identify potential interactions based on this information would be a
-thresholding analysis, which is outside the scope of this manuscript
-(and is done in the papers cited in this illustration). Because the
-values returned from RDPG are not bound to the unit interval, we
-performed a clamping of the weights to the unit space, showing a
-one-inflation in documented interactions, and a zero-inflation in other
-species pairs. This last figure crosses from the statistical into the
-ecological, by showing that species pairs with no documented
-co-occurrence have weights that are not distinguishable from species
-pairs with no documented interactions, suggesting that (as befits a
-host-parasite model) the ability to interact is a strong predictor of
-co-occurrence.
+co-occurrence in the original dataset. This reveals that the observed
+interactions have higher predicted weights, although there is some
+overlap; the usual approach to identify potential interactions based on
+this information would be a thresholding analysis, which is outside the
+scope of this manuscript (and is done in the papers cited in this
+illustration). Because the values returned from RDPG are not bound to
+the unit interval, we performed a clamping of the weights to the unit
+space, showing a one-inflation in documented interactions, and a
+zero-inflation in other species pairs. This last figure crosses from the
+statistical into the ecological, by showing that species pairs with no
+documented co-occurrence have weights that are not distinguishable from
+species pairs with no documented interactions, suggesting that (as
+befits a host-parasite model) the ability to interact is a strong
+predictor of co-occurrence.
 
@@
 often enacted at smaller scales, nested within a specific country (Ray
-et al., 2021). But there is no guarantee that these arbitrary boundaries
-are meaningful. In fact, we do not have a satisfying answer to the
-question of ``where does an ecological network stop?'', the answer to
-which would dictate the spatial span to embed/predict. Recent results by
-Martins et al. (2022) suggested that networks are shaped within
-eco-regions, with abrupt structural transitions from an eco-region to
-the next. Should this trend hold generally, this would provide an
-ecologically-relevant scale at which metawebs can be downscaled and
-predicted. Other solutions could leverage network-area relationships to
-identify areas in which networks are structurally similar (see
-\emph{e.g.} Fortin et al., 2021; Galiana et al., 2022, 2018). Both of
-these solutions requires ample pre-existing information about the
-network in space. Nevertheless, the inclusion of species for which we
-have data but that are not in the right spatial extent\emph{may} improve
-the performance of approaches based on embedding and transfer, \emph{if}
-they increase the similarity between the target and destination network.
-This proposal can specifically be evaluated by adding nodes to the
-network to embed, and evaluating the performance of predictive models
-(see \emph{e.g.} Llewelyn et al., 2022).
+et al., 2021). However, there is no guarantee that these arbitrary
+boundaries are meaningful. In fact, we do not have a satisfying answer
+to the question of ``where does an ecological network stop?'', the
+answer to which would dictate the spatial span to embed/predict. Recent
+results by Martins et al. (2022) suggested that networks are shaped
+within eco-regions, with abrupt structural transitions from an
+eco-region to the next. Should this trend hold generally, this would
+provide an ecologically-relevant scale at which metawebs can be
+downscaled and predicted. Other solutions could leverage network-area
+relationships to identify areas in which networks are structurally
+similar (see \emph{e.g.} Fortin et al., 2021; Galiana et al., 2022,
+2018). Both of these solutions require ample pre-existing information
+about the network in space. Nevertheless, the inclusion of species for
+which we have data but that are not in the right spatial extent
+\emph{may} improve the performance of approaches based on embedding and
+transfer, \emph{if} they increase the similarity between the target and
+destination network. This proposal can specifically be evaluated by
+adding nodes to the network to embed, and assessing the performance of
+predictive models (see \emph{e.g.} Llewelyn et al., 2022).
 
@@
 shorter-term changes in taxonomic and genetic richness of wildlife
-emerged through environmental racism (Schmidt \& Garroway, 2022). These
-considerations mean that ``the set of species found at a place'' is not
-only a response to ecological processes, and therefore there may exist
-forcing on the interactions between these species.
+emerged through environmental racism (Schmidt \& Garroway, 2022). Thus,
+the set of species found at a specific location is not only as the
+result of a response to ecological processes separate from human
+influence, but also the result of human-environment interaction as well
+as the result legislative/political histories.
 
@@
 Human-algorithm interactions are notoriously difficult and can yield
-adverse effect (Green \& Chen, 2019; Stevenson \& Doleac, 2021),
+adverse effects (Green \& Chen, 2019; Stevenson \& Doleac, 2021),
 suggesting the need to systematically study them for the specific
@@
 
-\textbf{Conflict of interest:} The authors have no conflict interests to
-disclose
+\textbf{Conflict of interest:} The authors have no conflict of interests
+to disclose
 

### 2023-01-31 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@056496e780c73ebc88e57c6540b8eb43cd84cf64 🚀

@@
 interactions under a model that accurately predicts interaction
-probabilities. Although defining an interaction as `rare' is perhaps not
-as straight forward as one may assume (rare in the context of likelihood
-of occurrence or the context of biologically plausible?) but for the
-context of the discussion in this manuscript the core idea is that
-construction of probabilistic networks affords us the nuance of
-capturing this inherit variability of interaction occurrence.
-
-Critically, the original metaweb definition, and indeed most past uses
-of metawebs, was based on the presence/absence of interactions. Moving
+probabilities.
+
+Yet, the original metaweb definition, and indeed most past uses of
+metawebs, was based on the presence/absence of interactions. Moving
 towards \emph{probabilistic} metawebs, by representing interactions as

### 2023-08-11 index.qmd
move to quarto

---
title: Graph embedding and transfer learning can help predict potential species interaction networks despite data limitations
authors:
  - name: Tanya Strydom
    affiliation:
        - ref: udem
        - ref: qcbs
    orcid: 0000-0001-6067-1349
    email: tanya.strydom@umontreal.ca
  - name: Salomé Bouskila
    affiliation:
        - ref: udem
    roles: writing
    corresponding: false
    orcid: 0000-0003-0193-5441
    email: salome.bouskila@umontreal.ca
  - name: Francis Banville
    affiliation:
        - ref: udem
        - ref: qcbs
        - ref: udes
    orcid: 0000-0001-9051-0597
    email: francis.banville@umontreal.ca
  - name: Ceres Barros
    affiliation:
        - Department of Forest Resources Management, University of British Columbia, Vancouver, B.C., Canada
    orcid: 0000-0003-4036-977X
    email: cbarros@mail.ubc.ca
affiliations:
    - id: udem
      name: Département de Sciences Biologiques, Université de Montréal, Montréal, Canada
    - id: qcbs
      name: Québec Centre for Biodiversity Science, Montréal, Canada
    - id: udes
      name: Département de Biologie, Université de Sherbrooke, Sherbrooke, Canada
bibliography: references.bib
---

The ability to infer *potential* interactions could serve as a significant
breakthrough in our ability to conceptualize species interaction networks over
large spatial scales [@Hortal2015Seven]. Reliable inferences would not only
boost our understanding of the structure of species interaction networks, but
also increase the amount of information that can be used for biodiversity
management. In a recent overview of the field of ecological network prediction,
@Strydom2021Roadmap identified two challenges of interest to the prediction of
interactions at large scales. First, there is a relative scarcity of relevant
data in most places globally -- which, due to the limitations in most predictive
methods, restricts the ability to infer interactions to locations where it is
least required (*i.e.* regions where we already have interaction data) leaving
us unable to make inference in data scarce regions (where we most need it);
second, accurate predictors are important for accurate predictions, and the lack
of methods that can leverage a small amount of *accurate* data is a serious
impediment to our predictive ability. In most places, our most reliable
biodiversity knowledge is that of a species pool where a set of potentially
interacting species in a given area could occur: through the analysis of
databases like the Global Biodiversity Information Facility (GBIF) or the
International Union for the Conservation of Nature (IUCN), it is possible to
construct a list of species for a region of interest; however inferring the
potential interactions between these species still remains a challenge.

Following the definition of @Dunne2006Network, a metaweb is the ecological
network analogue to the species pool; specifically, it inventories all
*potential* interactions between species for a spatially delimited area (and so
captures the $\gamma$ diversity of interactions). The metaweb itself is not a
prediction of local networks at specific locations within the spatial area it
covers: it will have a different structure, notably by having a larger
connectance [see *e.g.* @Wood2015Effects] and complexity [see *e.g.*
@Galiana2022Ecological], than any of these local networks. These local networks
(which capture the $\alpha$ diversity of interactions) are a subset of the
metaweb's species and its realized interactions, and have been called "metaweb
realizations" [@Poisot2015Species]. Differences between local networks and their
metawebs are due to chance, species abundance and co-occurrence, local
environmental conditions, and local distribution of functional traits, among
others. Specifically, although co-occurrence can be driven by interactions
[@Cazelles2016Theory], co-occurrence alone is not a predictor of interactions
[@Blanchet2020Cooccurrence; @Thurman2019Testing], and therefore the lack of
co-occurrence cannot be used to infer the lack of a feasible interaction. Yet,
recent results by @Saravia2021Ecological strongly suggested that local (metaweb)
realizations only respond weakly to local conditions: instead, they reflect
constraints inherited by the structure of their metaweb. This sets up the core
goal of predictive network ecology as the prediction of metaweb structure, as it
is required to accurately produce downscaled, local predictions.

Because the metaweb represents the joint effect of functional, phylogenetic, and
macroecological processes [@Morales-Castilla2015Inferring], it holds valuable
ecological information. Specifically, it represents the "upper bounds" on what
the composition of the local networks, given a local species pool, can be [see
*e.g.* @McLeod2021Sampling]; this information can help evaluate the ability of
ecological assemblages to withstand the effects of, for example, climate change
[@Fricke2022Effects]. These local networks may be reconstructed given an
appropriate knowledge of local species composition and provide information on
the structure of food webs at finer spatial scales. This has been done for
example for tree-galler-parasitoid systems [@Gravel2018Bringing], fish trophic
interactions [@Albouy2019Marine], tetrapod trophic interactions
[@Braga2019Spatial; @OConnor2020Unveiling], and crop-pest networks
[@Grunig2020Crop]. In this contribution, we highlight the power of viewing (and
constructing) metawebs as *probabilistic* objects in the context of
low-probability interactions, discuss how a family of machine learning tools
(graph embeddings and transfer learning) can be used to overcome data
limitations to metaweb inference, and highlight how the use of metawebs
introduces important questions for the field of network ecology.

# A metaweb is an inherently probabilistic object

Treating interactions as probabilistic (as opposed to binary) events is a more
nuanced and realistic way to represent them. @Dallas2017Predicting suggested
that most interactions (links) in ecological networks are cryptic, *i.e.*
uncommon or hard to observe. This argument echoes @Jordano2016Sampling: sampling
ecological interactions is difficult because it requires first the joint
observation of two species, and then the observation of their interaction. In
addition, it is generally expected that weak or rare interactions will be more
prevalent in networks than common or strong interactions [@Csermely2004Strong],
compared to strong, persistent interactions; this is notably the case in food
chains, wherein many weaker interactions are key to the stability of a system
[@Neutel2002Stability]. In the light of these observations, we expect to see an
over-representation of low-probability (hereafter rare) interactions under a
model that accurately predicts interaction probabilities.

Yet, the original metaweb definition, and indeed most past uses of
metawebs, was based on the presence/absence of interactions. Moving towards
*probabilistic* metawebs, by representing interactions as Bernoulli events [see
*e.g.* @Poisot2016Structure], offers the opportunity to weigh these rare
interactions appropriately. The inherent plasticity of interactions is important
to capture: there have been documented instances of food webs undergoing rapid
collapse/recovery cycles over short periods of time [*e.g.*
@Pedersen2017Signatures]. Furthermore, because the structure of the metaweb
cannot be known in advance, it is important to rely on predictive tools that do
not assume a specific network topology for link prediction
[@Gaucher2021Outlier], but are able to work on generalizations of the network.
These considerations emphasize why metaweb predictions should focus on
quantitative (preferentially probabilistic) predictions, and this should
constrain the suite of models that are appropriate for prediction.

It is important to recall that a metaweb is intended as a catalogue of all
potential (feasible) interactions, which is then filtered for a given
application [@Morales-Castilla2015Inferring]. It is therefore important to
separate the interactions that happen "almost surely" (repeated observational
data), "almost never" (repeated lack of evidence *or* evidence that the link is
forbidden through *e.g.* trait mis-match), and interactions with a probability
that lays somewhere in between [@Catchen2023Missing]. In a sense, that most
ecological interactions are elusive can call for a slightly different approach
to sampling: once the common interactions are documented, the effort required in
documenting each rare interaction will increase exponentially
[@Jordano2016Sampling]. Recent proposals in other fields relying on machine
learning approaches emphasize the idea that algorithms meant to predict, through
the assumption that they approximate the process generating the data, can also
act as data generators [@Hoffmann2019Machine]. High quality observational data
can be used to infer core rules underpinning network structure, and be
supplemented with synthetic data coming from predictive models trained on them,
thereby increasing the volume of information available for analysis. Indeed,
@Strydom2021Roadmap suggested that knowing the metaweb may render the prediction
of local networks easier, because it fixes an "upper bound" on which
interactions can exist. In this context, a probabilistic metaweb represents an
aggregation of informative priors on the biological feasibility of interactions,
which is usually hard to obtain yet has possibly the most potential to boost our
predictive ability of local networks [@Bartomeus2013Understanding;
@Bartomeus2016Common]. This would represent a departure from simple rules
expressed at the network scale [*e.g.* @Williams2000Simple] to a view of network
prediction based on learning the rules that underpin interactions *and* their
variability [@Gupta2022Simultaneously].

![The embedding process (**A**) can help to identify links (interactions) that
may have been missed within the original community (represented by the orange
dashed arrows, **B**). Transfer learning (**D**) allows for the prediction links
(interactions) even when novel species (**C**) are included alongside the
original community. This is achieved by learning using other relevant predictors
(*e.g.* traits) in conjunction with the known interactions to infer latent
values (**E**). Ultimately this allows us to predict links (interactions) for
species external from the original sample (blue dashed arrows) as well as
missing within sample links (**F**). Within this context the predicted (and
original) networks as well as the ecological predictors used (green boxes) are
products that can be quantified through measurements in the field, whereas the
embedded as well as imputed matrices (purple box) are representative of a
decomposition of the interaction matrices onto the embedding
space](figures/conceptual_2.png){#fig:embedding}

# Graph embedding offers promises for the inference of potential interactions

Graph (or network) embedding (@fig:embedding) is a family of machine learning
techniques, whose main task is to learn a mapping function from a discrete graph
to a continuous domain [@Arsov2019Network; @Chami2022Machine]. Their main goal
is to learn a low dimensional vector representation of the graph (embeddings),
such that its key properties (*e.g.* local or global structures) are retained in
the embedding space [@Yan2005Graph]. The embedding space may, but will not
necessarily, have lower dimensionality than the graph. Ecological networks are
promising candidates for the routine application of embeddings, as they tend to
possess a shared structural backbone [see *e.g.* @BramonMora2018Identifying],
which hints at structural invariants in empirical data. Assuming that these
structural invariants are common enough, they would dominate the structure of
networks, and therefore be adequately captured by the first (lower) dimensions
of an embedding, without the need to measure derived aspects of their structure
(*e.g.* motifs, paths, modularity, ...).

## Graph embedding produces latent variables (but not traits)

Before moving further, it is important to clarify the epistemic status of node
values derived from embeddings: specifically, they are *not* functional traits,
and therefore should not be interpreted in terms of effects or responses. As per
the framework of @Malaterre2019Functional, these values neither derive from, nor
result in, changes in organismal performance, and should therefore not be used
to quantify *e.g.* functional diversity. This holds true even when there are
correlations between latent values and functional traits: although these enable
an ecological discussion of how traits condition the structure of the network,
the existence of a statistical relationship does not elevate the latent values
to the status of functional traits.

Rather than directly predicting biological rules [see *e.g.* @Pichler2020Machine
for an overview], which may be confounded by the sparse nature of graph data,
learning embeddings works in the low-dimensional space that maximizes
information about the network structure. This approach is further justified by
the observation, for example, that the macro-evolutionary history of a network
is adequately represented by some graph embeddings [Random dot product graphs
(RDPG); see @DallaRiva2016Exploring]. In a recent publication, @Strydom2022Food
have used an embedding (based on RDPG) to project a metaweb of trophic
interactions between European mammals, and transferred this information to
mammals of Canada, using the phylogenetic distance between related clades to
infer the values in the latent subspace into which the European metaweb was
projected. By performing the RDPG step on re-constructed values, this approach
yields a probabilistic trophic metaweb for mammals of Canada based on knowledge
of European species, despite a limited ($\approx$ 5%) taxonomic overlap, and
illustrates how the values derived from an embedding can be used for prediction
without being "traits" of the species they represent.

## Ecological networks are good candidates for embedding

Food webs are inherently low-dimensional objects, and can be adequately
represented with less than ten dimensions [@Braga2021Phylogenetic;
@Eklof2013Dimensionality; @Braga2019Spatial]. Simulation results by
@Botella2022Appraisal suggested that there is no dominant method to identify
architectural similarities between networks: multiple approaches need to be
tested and compared to the network descriptor of interest on a problem-specific
basis. This matches previous results on graph embedding, wherein different
embedding algorithms yield different network embeddings [@Goyal2018Graph],
calling for a careful selection of the problem-specific approach to use. In
@tbl:methods, we present a selection of common graph and node embedding methods,
alongside examples of their use to predict interactions or statistical
associations between species. These methods rely largely on linear algebra or
pseudo-random walks on graphs. All forms of embeddings presented in @tbl:methods
share the common property of summarizing their objects into (sets of) dense
feature vectors, that capture the overall network structure, pairwise
information on nodes, and emergent aspects of the network, in a compressed way
(*i.e.* with some information loss, as we later discuss in the illustration).
Node embeddings tend to focus on maintaining pairwise relationships (*i.e.*
species interactions), while graph embeddings focus on maintaining the network
structure (*i.e.* emergent properties). Nevertheless, some graph embedding
techniques [like RDPG, see *e.g.* @Wu2021Maximum] will provide high-quality
node-level embeddings while also preserving network structure.

::: {#box-gnn .callout-note}
## Graph Neural Networks {#box-gnn}

One prominent family of approaches we do not discuss in the present manuscript
is Graph Neural Networks [GNN; @Zhou2020Graph]. GNN are, in a sense, a method to
embed a graph into a dense subspace, but belong to the family of deep learning
methods, which has its own set of practices [see *e.g.* @Goodfellow2016Deep]. An
important issue with methods based on deep learning is that, because their
parameter space is immense, the sample size of the data fed into them must be
similarly large (typically thousands of instances). This is a requirement for
the model to converge correctly during training, but this assumption is unlikely
to be met given the size of datasets currently available for metawebs (or single
time/location species interaction networks). This data volume requirement is
mostly absent from the techniques we list below. Furthermore, GNN still have
some challenges related to their shallow structure, and concerns related to
scalability [see @Gupta2021Graph for a review], which are mostly absent from the
methods listed in @tbl:methods. Assuming that the uptake of next-generation
biomonitoring techniques does indeed deliver larger datasets on species
interactions [@Bohan2017Nextgeneration], there is nevertheless the potential for
GNN to become an applicable embedding/predictive technique in the coming years.
:::

Graph embeddings *can* serve as a dimensionality reduction method. For example,
RDPG [@Strydom2022Food] and t-SVD [truncated Singular Value Decomposition;
@Poisot2021Imputing] typically embed networks using fewer dimensions than the
original network [the original network has as many dimensions as species, and as
many informative dimensions as trophically unique species; @Strydom2021Svd].
However, this is not necessarily the case -- indeed, one may perform a PCA (a
special case of SVD) to project the raw data into a subspace that improves the
efficacy of t-SNE [t-distributed stochastic neighbor embedding;
@Maaten2009Learning]. There are many dimensionality reductions
[@Anowar2021Conceptual] that can be applied to an embedded network should the
need for dimensionality reduction (for example for data visualization) arise. In
brief, many graph embeddings *can* serve as dimensionality reduction steps, but
not all do, neither do all dimensionality reduction methods provide adequate
graph embedding capacities. In the next section (and @fig:embedding), we show
how the amount of dimensionality reduction can affect the quality of the
embedding.

| Method        | Object          | Technique                        | Reference                | Application                                                                                                       |
| ------------- | --------------- | -------------------------------- | ------------------------ | ----------------------------------------------------------------------------------------------------------------- |
| tSNE          | nodes           | statistical divergence           | @Hinton2002Stochastic    | [@Cieslak2020Tdistributed, species-environment responses $^a$] [@Gibb2021Data, host-virus network representation] |
| LINE          | nodes           | stochastic gradient descent      | @Tang2015Line            |                                                                                                                   |
| SDNE          | nodes           | gradient descent                 | @Wang2016Structural      |                                                                                                                   |
| node2vec      | nodes           | stochastic gradient descent      | @Grover2016Node2vec      |                                                                                                                   |
| HARP          | nodes           | meta-strategy                    | @Chen2017Harp            |                                                                                                                   |
| DMSE          | joint nodes     | deep neural network              | @Chen2017Deep            | [@Chen2017Deep, species-environment interactions $^b$]                                                            |
| graph2vec     | sub-graph       | skipgram network                 | @Narayanan2017Graph2vec  |                                                                                                                   |
| RDPG          | graph           | SVD                              | @Young2007Random         | [@DallaRiva2016Exploring, trophic interactions] [@Poisot2021Imputing, host-virus network prediction]              |
| GLEE          | graph           | Laplacian eigenmap               | @Torres2020Glee          |                                                                                                                   |
| DeepWalk      | graph           | stochastic gradient descent      | @Perozzi2014Deepwalk     | [@Wardeh2021Predicting, host-virus interactions]                                                                  |
| GraphKKE      | graph           | stochastic differential equation | @Melnyk2020Graphkke      | [@Melnyk2020Graphkke, microbiome species associations $^a$]                                                       |
| FastEmbed     | graph           | eigen decomposition              | @Ramasamy2015Compressive |                                                                                                                   |
| PCA           | graph           | eigen decomposition              | @Surendran2013Graph      | [@Strydom2021Roadmap, host-parasite interactions]                                                                 |
| Joint methods | multiple graphs | multiple strategies              | @Wang2021Joint           |                                                                                                                   |

: Overview of some common graph embedding approaches, by type of embedded
objects, alongside examples of their use in the prediction of species
interactions. These methods have not yet been routinely used to predict species
interactions; most examples that we identified were either statistical
associations, or analogues to joint species distribution models. $^a$:
application is concerned with *statistical* interactions, which are not
necessarilly direct biotic interactions; $^b$:application is concerned with
joint-SDM-like approach, which is also very close to statistical associations as
opposed to direct biotic interactions. Given the need to evaluate different
methods on a problem-specific basis, the fact that a lot of methods have not
been used on network problems is an opportunity for benchmarking and method
development. Note that the row for PCA also applies to kernel/probabilistic PCA,
which are variations on the more general method of SVD. Note further that tSNE
has been included because it is frequently used to embed graphs, including of
species associations/interactions, despite not being strictly speaking, a graph
embedding technique [see *e.g.* @Chami2022Machine]. {#tbl:methods}

The popularity of graph embedding techniques in machine learning is more than
the search for structural invariants: graphs are discrete objects, and machine
learning techniques tend to handle continuous data better. Bringing a sparse
graph into a continuous, dense vector space [@Xu2021Understanding] opens up a
broader variety of predictive algorithms, notably of the sort that are able to
predict events as probabilities [@Murphy2022Probabilistic]. Furthermore, the
projection of the graph itself is a representation that can be learned;
@Runghen2021Exploiting, for example, used a neural network to learn the
embedding of a network in which not all interactions were known, based on the
nodes' metadata. This example has many parallels in ecology (see @fig:embedding
**C**), in which node metadata can be represented by phylogeny, abundance, or
functional traits. Using phylogeny as a source of information assumes (or
strives to capture) the action of evolutionary processes on network structure,
which at least for food webs have been well documented [@Braga2021Phylogenetic;
@DallaRiva2016Exploring; @Eklof2016Phylogenetic; @Stouffer2007Evidence;
@Stouffer2012Evolutionary]; similarly, the use of functional traits assumes that
interactions can be inferred from the knowledge of trait-matching rules, which
is similarly well supported in the empirical literature
[@Bartomeus2013Understanding; @Bartomeus2016Common; @Goebel2023Body;
@Gravel2013Inferring]. Relating this information to an embedding rather than a
list of network measures would allow to capture their effect on the more
fundamental aspects of network structure; conversely, the absence of a
phylogenetic or functional signal may suggest that evolutionary/trait processes
are not strong drivers of network structure, therefore opening a new way to
perform hypothesis testing.

# An illustration of metaweb embedding

In this section, we illustrate the embedding of a collection of bipartite
networks collected by @Hadfield2014Tale, using t-SVD and RDPG. Briefly, an RDPG
decomposes a network into two subspaces (left and right), which are matrices
that when multiplied give an approximation of the original network. RDPG has the
particularly desirable properties of being a graph embedding technique that
produces relevant node-level feature vectors, and provides good approximations
of graphs with varied structures [@Athreya2017Statistical]. The code to
reproduce this example is available as supplementary material [note, for the
sake of comparison, that @Strydom2021Roadmap have an example using embedding
through PCA followed by prediction using a deep neural network on the same
dataset]. The resulting (binary) metaweb $\mathcal{M}$ has 2131 interactions
between 206 parasites and 121 hosts, and its adjacency matrix has full rank
(*i.e.* it represents a space with 121 dimensions). All analyses were done using
Julia [@Bezanson2017Julia] version 1.7.2, *Makie.jl* [@Danisch2021Makie], and
*EcologicalNetworks.jl* [@Poisot2019Ecologicalnetworks].

![Validation of an embedding for a host-parasite metaweb, using Random Dot
Product Graphs. **A**, decrease in approximation error as the number of
dimensions in the subspaces increases. **B**, increase in cumulative variance
explained as the number of ranks considered increases; in **A** and **B**, the
dot represents the point of inflexion in the curve (at rank 39) estimated using
the finite differences method. **C**, position of hosts and parasites in the
space of latent variables on the first and second dimensions of their respective
subspaces (the results have been clamped to the unit interval). **D**, predicted
interaction weight from the RDPG based on the status of the species pair in the
metaweb.](figures/illustration-part1.png){#fig:illustration1}

In @fig:illustration1, we focus on some statistical checks of the embedding. In
panel **A**, we show that the averaged $L_2$ loss (*i.e.* the sum of squared
errors) between the empirical and reconstructed metaweb decreases when the
number of dimensions (rank) of the subspace increases, with an inflection at 39
dimensions (out of 120 initially) according to the finite differences method. As
discussed by @Runghen2021Exploiting, there is often a trade-off between the
number of dimensions to use (more dimensions are more computationally demanding)
and the quality of the representation. In panel **B**, we show the increase in
cumulative variance explained at each rank, and visualize that using 39 ranks
explains about 70% of the variance in the empirical metaweb. This is a different
information from the $L_2$ loss (which is averaged across interactions), as it
works on the eigenvalues of the embedding, and therefore captures higher-level
features of the network. In panel **C**, we show positions of hosts and
parasites on the first two dimensions of the left and right subspaces. Note that
these values largely skew negative, because the first dimensions capture the
coarse structure of the network: most pairs of species do not interact, and
therefore have negative values. Finally in panel **D**, we show the predicted
weight (*i.e.* the result of the multiplication of the RDGP subspaces at a rank
of 39) as a function of whether the interactions are observed, not-observed, or
unknown due to lack of co-occurrence in the original dataset. This reveals that
the observed interactions have higher predicted weights, although there is some
overlap; the usual approach to identify potential interactions based on this
information would be a thresholding analysis, which is outside the scope of this
manuscript (and is done in the papers cited in this illustration). Because the
values returned from RDPG are not bound to the unit interval, we performed a
clamping of the weights to the unit space, showing a one-inflation in documented
interactions, and a zero-inflation in other species pairs. This last figure
crosses from the statistical into the ecological, by showing that species pairs
with no documented co-occurrence have weights that are not distinguishable from
species pairs with no documented interactions, suggesting that (as befits a
host-parasite model) the ability to interact is a strong predictor of
co-occurrence.

![Ecological analysis of an embedding for a host-parasite metaweb, using Random
Dot Product Graphs. **A**, relationship between the number of parasites and
position along the first axis of the right-subspace for all hosts, showing that
the embedding captures elements of network structure at the species scale.
**B**, weak relationship between the body mass of hosts (in grams) and the
position alongside the same dimension. **C**, weak relationship between body
mass of hosts and parasite richness. **D**, distribution of positions alongside
the same axis for hosts grouped by taxonomic
family.](figures/illustration-part2.png){#fig:illustration2}

The results of @fig:illustration1 show that we can extract an embedding of the
metaweb that captures enough variance to be relevant; specifically, this is true
for both $L_2$ loss (indicating that RDPG is able to capture pairwise processes)
and the cumulative variance explained (indicating that RDPG is able to capture
network-level structure). Therefore, in @fig:illustration2, we relate the values
of latent variables for hosts to different ecologically-relevant data. In panel
**A**, we show that host with a higher value on the first dimension have fewer
parasites. This relates to the body size of hosts in the *PanTHERIA* database
[@Jones2009Pantheria], as shown in panel **B**: interestingly, the position on
the first axis is only weakly correlated to body mass of the host; this matches
well established results showing that body size/mass is not always a direct
predictor of parasite richness in terrestrial mammals [@Morand1998Density], a
result we observe in panel **C**. Finally, in panel **D**, we can see how
different taxonomic families occupy different positions on the first axis, with
*e.g.* Sciuridae being biased towards higher values. These results show how we
can look for ecological informations in the output of network embeddings, which
can further be refined into the selection of predictors for transfer learning.

# The metaweb merges ecological hypotheses and practices

Metaweb inference seeks to provide information about the interactions between
species at a large spatial scale, typically a scale large enough to be
considered of biogeographic relevance (indeed, many of the examples covered in
the introduction span areas larger than a country, some of them global). But as
@Herbert1965Dune rightfully pointed out, "[y]ou can't draw neat lines around
planet-wide problems"; any inference of a metaweb must therefore contend with
several novel, interwoven, families of problems. In this section, we outline
three that we think are particularly important, and can discuss how they may
addressed with subsequent data analysis or simulations, and how they emerge in
the specific context of using embeddings; some of these issues are related to
the application of these methods at the science-policy interface.

## Identifying the properties of the network to embed

If the initial metaweb is too narrow in scope, notably from a taxonomic point of
view, the chances of finding another area with enough related species (through
phylogenetic relatedness or similarity of functional traits) to make a reliable
inference decreases. This is because transfer requires similarity
(@fig:embedding). A diagnostic for the lack of similar species would likely be
large confidence intervals during estimation of the values in the low-rank
space. In other words, the representation of the original graph is difficult to
transfer to the new problem. Alternatively, if the initial metaweb is too large
(taxonomically), then the resulting embeddings would need to represent
interactions between taxonomic groups that are not present in the new location.
This would lead to a much higher variance in the starting dataset, and to
under-dispersion in the target dataset, resulting in the potential under or over
estimation of the strength of new predicted interactions.
@Llewelyn2022Predicting provided compelling evidence for these situations by
showing that, even at small spatial scales, the transfer of information about
interactions becomes more challenging when areas rich with endemic species are
considered. The lack of well documented metawebs is currently preventing the
development of more concrete guidelines. The question of phylogenetic
relatedness and distribution is notably relevant if the metaweb is assembled in
an area with mostly endemic species (*e.g.* a system that has undergone recent
radiation or that has remained in isolation for a long period of time might not
have an analogous system with which to draw knowledge from), and as with every
predictive algorithm, there is room for the application of our best ecological
judgement. Because this problem relates to distribution of species in the
geographic or phylogenetic space, it can certainly be approached through
assessing the performance of embedding transfer in simulated starting/target
species pools.

## Identifying the scope of the prediction to perform

The area for which we seek to predict the metaweb should determine the species
pool on which the embedding is performed. Metawebs can be constructed by
assigning interactions in a list of species within specific regions. The upside
of this approach is that information relevant for the construction of this
dataset is likely to exist, as countries usually set conservation goals at the
national level [@Buxton2021Key], and as quantitative instruments are
consequently designed to work at these scales [@Turak2017Using]; specific
strategies are often enacted at smaller scales, nested within a specific country
[@Ray2021Biodiversity]. However, there is no guarantee that these arbitrary
boundaries are meaningful. In fact, we do not have a satisfying answer to the
question of "where does an ecological network stop?", the answer to which would
dictate the spatial span to embed/predict. Recent results by @Martins2022Global
suggested that networks are shaped within eco-regions, with abrupt structural
transitions from an eco-region to the next. Should this trend hold generally,
this would provide an ecologically-relevant scale at which metawebs can be
downscaled and predicted. Other solutions could leverage network-area
relationships to identify areas in which networks are structurally similar [see
*e.g.* @Fortin2021Network; @Galiana2018Spatial; @Galiana2022Ecological]. Both of
these solutions require ample pre-existing information about the network in
space. Nevertheless, the inclusion of species for which we have data but that
are not in the right spatial extent *may* improve the performance of approaches
based on embedding and transfer, *if* they increase the similarity between the
target and destination network. This proposal can specifically be evaluated by
adding nodes to the network to embed, and assessing the performance of
predictive models [see *e.g.* @Llewelyn2022Predicting].

# Conclusion: metawebs, predictions, and people

Predictive approaches in ecology, regardless of the scale at which they are
deployed and the intent of their deployment, originate in the framework that
contributed to the ongoing biodiversity crisis [@Adam2014Elephant] and
reinforced environmental injustice [@Choudry2013Saving;
@Dominguez2020Decolonising]. The risk of embedding this legacy in our models is
real, especially when the impact of this legacy on species pools is being
increasingly documented. This problem can be addressed by re-framing the way we
interact with models, especially when models are intended to support
conservation actions. Particularly on territories that were traditionally
stewarded by Indigenous people, we must interrogate how predictive approaches
and the biases that underpin them can be put to task in accompanying Indigenous
principles of land management [@Eichhorn2019Steps; @Nokmaq2021Awakening]. The
discussion of "algorithm-in-the-loop" approaches that is now pervasive in the
machine learning community provides examples of why this is important.
Human-algorithm interactions are notoriously difficult and can yield adverse
effects [@Green2019Disparate; @Stevenson2021Algorithmic], suggesting the need to
systematically study them for the specific purpose of, here, biodiversity
governance. Improving the algorithmic literacy of decision makers is part of the
solution [*e.g.* @Lamba2019Deep; @MoseboFernandes2020Machine], as we can
reasonably expect that model outputs will be increasingly used to drive policy
decisions [@Weiskopf2022Increasing]. Our discussion of these approaches need to
go beyond the technical and statistical, and into the governance consequences
they can have. To embed data also embeds historical and contemporary biases that
acted on these data, both because they shaped the ecological processes
generating them, and the global processes leading to their measurement and
publication. For a domain as vast as species interaction networks, these biases
exist at multiple scales along the way, and a challenge for prediction is not
only to develop (or adopt) new quantitative tools, but to assess the behavior of
these tools in the proper context.

::: {#box-legacy .callout-note}
## Minding legacies shaping ecological datasets {#box-legacy}

In large parts of the world, boundaries that delineate geographic regions are
merely a reflection the legacy of settler colonialism, which drives global
disparity in capacity to collect and publish ecological data. Applying any
embedding to biased data does not debias them, but rather embeds these biases,
propagating them to the models using embeddings to make predictions.
Furthermore, the use of ecological data itself is not an apolitical act
[@Nost2021Political]: data infrastructures tend to be designed to answer
questions within national boundaries (therefore placing contingencies on what is
available to be embedded), their use often drawing upon, and reinforcing,
territorial statecraft [see *e.g.* @Barrett2005Environment]. As per
@Machen2021Thinking, these biases are particularly important to consider when
knowledge generated algorithmically is used to supplement or replace human
decision-making, especially for governance (*e.g.* enacting conservation
decisions on the basis of model prediction). As information on networks is
increasingly leveraged for conservation actions [see *e.g.* @Eero2021Use;
@Naman2022Food; @Stier2017Integrating], the need to appraise and correct biases
that are unwittingly propagated to algorithms when embedded from the original
data is immense. These considerations are even more urgent in the specific
context of biodiversity data. Long-term colonial legacies still shape taxonomic
composition to this day [@Lenzner2022Naturalized; @Raja2022Colonialism], and
much shorter-term changes in taxonomic and genetic richness of wildlife emerged
through environmental racism [@Schmidt2022Systemic]. Thus, the set of species
found at a specific location is not only as the result of a response to
ecological processes separate from human influence, but also the result of
human-environment interaction as well as the result legislative/political
histories.
:::

**Acknowledgements:** We acknowledge that this study was conducted on land
within the traditional unceded territory of the Saint Lawrence Iroquoian,
Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. TP, TS, DC,
and LP received funding from the Canadian Institute for Ecology & Evolution. FB
is funded by the Institute for Data Valorization (IVADO). TS, SB, and TP are
funded by a donation from the Courtois Foundation. CB was awarded a Mitacs
Elevate Fellowship no. IT12391, in partnership with fRI Research, and also
acknowledges funding from Alberta Innovates and the Forest Resources Improvement
Association of Alberta. M-JF acknowledges funding from NSERC Discovery Grant and
NSERC CRC. RR is funded by New Zealand’s Biological Heritage Ngā Koiora Tuku Iho
National Science Challenge, administered by New Zealand Ministry of Business,
Innovation, and Employment. BM is funded by the NSERC Alexander Graham Bell
Canada Graduate Scholarship and the FRQNT master’s scholarship. LP acknowledges
funding from NSERC Discovery Grant (NSERC RGPIN-2019-05771). TP acknowledges
financial support from the Fondation Courtois, and NSERC through the Discovery
Grants and Discovery Accelerator Supplement programs. MJF is supported by an
NSERC PDF and an RBC Post-Doctoral Fellowship.

**Conflict of interest:** The authors have no conflict of interests to disclose

**Authors' contributions:** TS, and TP conceived the ideas discussed in the
manuscript. All authors contributed to writing and editing the manuscript.

**Data availability:** There is no data associated with this manuscript.

# References

### 2023-08-11 index.qmd
update authors

@@
     affiliation:
-        - Department of Forest Resources Management, University of British Columbia, Vancouver, B.C., Canada
+        - ref: ubcforest
     orcid: 0000-0003-4036-977X
     email: cbarros@mail.ubc.ca
+  - name: Dominique Caron
+    affiliation:
+        - ref: mcgill
+        - ref: qcbs
+    orcid: 0000-0002-2151-6693
+    email: dominique.caron@mail.mcgill.ca
+  - name: Maxwell J. Farrell
+    affiliation:
+        - ref: uoft
+    orcid: 0000-0003-0452-6993
+    email: maxwell.farrell@utoronto.ca
+  - name: Marie-Josée Fortin
+    affiliation:
+        - ref: uoft
+    orcid: 0000-0002-9935-1366
+    email: mariejosee.fortin@utoronto.ca
+  - name: Victoria Hemming
+    affiliation:
+        - ref: ubccons
+    orcid: 0000-0003-3220-6161
+    email: victoria.hemming@ubc.ca
+  - name: Benjamin Mercier
+    affiliation:
+        - ref: udes
+        - ref: qcbs
+    orcid: 0000-0002-4104-9463
+    email: benjamin.b.mercier@usherbrooke.ca
+  - name: Laura J. Pollock
+    affiliation:
+        - ref: mcgill
+        - ref: qcbs
+    orcid: 0000-0002-6004-4027
+    email: laura.pollock@mcgill.ca
+  - name: Rogini Runghen
+    affiliation:
+        - ref: ucecology
+    orcid: 0000-0001-5785-8321
+    email: rogini.runghen@gmail.com
+  - name: Giulio V. Dalla Riva
+    affiliation:
+        - ref: ucmath
+    orcid: 0000-0002-3454-0633
+    email: giulio.dallariva@canterbury.ac.nz
+  - name: Timothée Poisot
+    affiliation:
+        - ref: udem
+        - ref: qcbs
+    orcid: 0000-0002-0735-5184
+    corresponding: true
+    email: timothee.poisot@umontreal.ca
 affiliations:
@@
       name: Département de Biologie, Université de Sherbrooke, Sherbrooke, Canada
+    - id: ubcforest
+      name: Department of Forest Resources Management, University of British Columbia, Vancouver, B.C., Canada
+    - id: mcgill
+      name: Department of Biology, McGill University, Montréal, Canada
+    - id: uoft
+      name: Department of Ecology & Evolutionary Biology, University of Toronto, Toronto, Canada
+    - id: ubccons
+      name: Department of Forest and Conservation Sciences, University of British Columbia, Vancouver, Canada
+    - id: ucecology
+      name: Department of Forest and Conservation Sciences, University of British Columbia, Vancouver, Canada
+    - id: ucmath
+      name: Department of Forest and Conservation Sciences, University of British Columbia, Vancouver, Canada
 bibliography: references.bib

### 2023-08-15 index.qmd
moved to quarto

@@
 
-The ability to infer *potential* interactions could serve as a significant
-breakthrough in our ability to conceptualize species interaction networks over
-large spatial scales [@Hortal2015Seven]. Reliable inferences would not only
-boost our understanding of the structure of species interaction networks, but
-also increase the amount of information that can be used for biodiversity
-management. In a recent overview of the field of ecological network prediction,
-@Strydom2021Roadmap identified two challenges of interest to the prediction of
-interactions at large scales. First, there is a relative scarcity of relevant
-data in most places globally -- which, due to the limitations in most predictive
-methods, restricts the ability to infer interactions to locations where it is
-least required (*i.e.* regions where we already have interaction data) leaving
-us unable to make inference in data scarce regions (where we most need it);
-second, accurate predictors are important for accurate predictions, and the lack
-of methods that can leverage a small amount of *accurate* data is a serious
-impediment to our predictive ability. In most places, our most reliable
-biodiversity knowledge is that of a species pool where a set of potentially
-interacting species in a given area could occur: through the analysis of
-databases like the Global Biodiversity Information Facility (GBIF) or the
-International Union for the Conservation of Nature (IUCN), it is possible to
-construct a list of species for a region of interest; however inferring the
-potential interactions between these species still remains a challenge.
+The ability to infer *potential* interactions could serve as a significant breakthrough in our ability to conceptualize species interaction networks over large spatial scales [@Hortal2015Seven].
+Reliable inferences would not only boost our understanding of the structure of species interaction networks, but also increase the amount of information that can be used for biodiversity management.
+In a recent overview of the field of ecological network prediction, @Strydom2021Roadmap identified two challenges of interest to the prediction of interactions at large scales.
+First, there is a relative scarcity of relevant data in most places globally -- which, due to the limitations in most predictive methods, restricts the ability to infer interactions to locations where it is least required (*i.e.* regions where we already have interaction data) leaving us unable to make inference in data scarce regions (where we most need it); second, accurate predictors are important for accurate predictions, and the lack of methods that can leverage a small amount of *accurate* data is a serious impediment to our predictive ability.
+In most places, our most reliable biodiversity knowledge is that of a species pool where a set of potentially interacting species in a given area could occur: through the analysis of databases like the Global Biodiversity Information Facility (GBIF) or the International Union for the Conservation of Nature (IUCN), it is possible to construct a list of species for a region of interest; however inferring the potential interactions between these species still remains a challenge.
 
-Following the definition of @Dunne2006Network, a metaweb is the ecological
-network analogue to the species pool; specifically, it inventories all
-*potential* interactions between species for a spatially delimited area (and so
-captures the $\gamma$ diversity of interactions). The metaweb itself is not a
-prediction of local networks at specific locations within the spatial area it
-covers: it will have a different structure, notably by having a larger
-connectance [see *e.g.* @Wood2015Effects] and complexity [see *e.g.*
-@Galiana2022Ecological], than any of these local networks. These local networks
-(which capture the $\alpha$ diversity of interactions) are a subset of the
-metaweb's species and its realized interactions, and have been called "metaweb
-realizations" [@Poisot2015Species]. Differences between local networks and their
-metawebs are due to chance, species abundance and co-occurrence, local
-environmental conditions, and local distribution of functional traits, among
-others. Specifically, although co-occurrence can be driven by interactions
-[@Cazelles2016Theory], co-occurrence alone is not a predictor of interactions
-[@Blanchet2020Cooccurrence; @Thurman2019Testing], and therefore the lack of
-co-occurrence cannot be used to infer the lack of a feasible interaction. Yet,
-recent results by @Saravia2021Ecological strongly suggested that local (metaweb)
-realizations only respond weakly to local conditions: instead, they reflect
-constraints inherited by the structure of their metaweb. This sets up the core
-goal of predictive network ecology as the prediction of metaweb structure, as it
-is required to accurately produce downscaled, local predictions.
+Following the definition of @Dunne2006Network, a metaweb is the ecological network analogue to the species pool; specifically, it inventories all *potential* interactions between species for a spatially delimited area (and so captures the $\gamma$ diversity of interactions).
+The metaweb itself is not a prediction of local networks at specific locations within the spatial area it covers: it will have a different structure, notably by having a larger connectance [see *e.g.* @Wood2015Effects] and complexity [see *e.g.* @Galiana2022Ecological], than any of these local networks.
+These local networks (which capture the $\alpha$ diversity of interactions) are a subset of the metaweb's species and its realized interactions, and have been called "metaweb realizations" [@Poisot2015Species].
+Differences between local networks and their metawebs are due to chance, species abundance and co-occurrence, local environmental conditions, and local distribution of functional traits, among others.
+Specifically, although co-occurrence can be driven by interactions [@Cazelles2016Theory], co-occurrence alone is not a predictor of interactions [@Blanchet2020Cooccurrence; @Thurman2019Testing], and therefore the lack of co-occurrence cannot be used to infer the lack of a feasible interaction.
+Yet, recent results by @Saravia2021Ecological strongly suggested that local (metaweb) realizations only respond weakly to local conditions: instead, they reflect constraints inherited by the structure of their metaweb.
+This sets up the core goal of predictive network ecology as the prediction of metaweb structure, as it is required to accurately produce downscaled, local predictions.
 
-Because the metaweb represents the joint effect of functional, phylogenetic, and
-macroecological processes [@Morales-Castilla2015Inferring], it holds valuable
-ecological information. Specifically, it represents the "upper bounds" on what
-the composition of the local networks, given a local species pool, can be [see
-*e.g.* @McLeod2021Sampling]; this information can help evaluate the ability of
-ecological assemblages to withstand the effects of, for example, climate change
-[@Fricke2022Effects]. These local networks may be reconstructed given an
-appropriate knowledge of local species composition and provide information on
-the structure of food webs at finer spatial scales. This has been done for
-example for tree-galler-parasitoid systems [@Gravel2018Bringing], fish trophic
-interactions [@Albouy2019Marine], tetrapod trophic interactions
-[@Braga2019Spatial; @OConnor2020Unveiling], and crop-pest networks
-[@Grunig2020Crop]. In this contribution, we highlight the power of viewing (and
-constructing) metawebs as *probabilistic* objects in the context of
-low-probability interactions, discuss how a family of machine learning tools
-(graph embeddings and transfer learning) can be used to overcome data
-limitations to metaweb inference, and highlight how the use of metawebs
-introduces important questions for the field of network ecology.
+Because the metaweb represents the joint effect of functional, phylogenetic, and macroecological processes [@Morales-Castilla2015Inferring], it holds valuable ecological information.
+Specifically, it represents the "upper bounds" on what the composition of the local networks, given a local species pool, can be [see *e.g.* @McLeod2021Sampling]; this information can help evaluate the ability of ecological assemblages to withstand the effects of, for example, climate change [@Fricke2022Effects].
+These local networks may be reconstructed given an appropriate knowledge of local species composition and provide information on the structure of food webs at finer spatial scales.
+This has been done for example for tree-galler-parasitoid systems [@Gravel2018Bringing], fish trophic interactions [@Albouy2019Marine], tetrapod trophic interactions [@Braga2019Spatial; @OConnor2020Unveiling], and crop-pest networks [@Grunig2020Crop].
+In this contribution, we highlight the power of viewing (and constructing) metawebs as *probabilistic* objects in the context of low-probability interactions, discuss how a family of machine learning tools (graph embeddings and transfer learning) can be used to overcome data limitations to metaweb inference, and highlight how the use of metawebs introduces important questions for the field of network ecology.
 
@@
 
-Treating interactions as probabilistic (as opposed to binary) events is a more
-nuanced and realistic way to represent them. @Dallas2017Predicting suggested
-that most interactions (links) in ecological networks are cryptic, *i.e.*
-uncommon or hard to observe. This argument echoes @Jordano2016Sampling: sampling
-ecological interactions is difficult because it requires first the joint
-observation of two species, and then the observation of their interaction. In
-addition, it is generally expected that weak or rare interactions will be more
-prevalent in networks than common or strong interactions [@Csermely2004Strong],
-compared to strong, persistent interactions; this is notably the case in food
-chains, wherein many weaker interactions are key to the stability of a system
-[@Neutel2002Stability]. In the light of these observations, we expect to see an
-over-representation of low-probability (hereafter rare) interactions under a
-model that accurately predicts interaction probabilities.
+Treating interactions as probabilistic (as opposed to binary) events is a more nuanced and realistic way to represent them.
+@Dallas2017Predicting suggested that most interactions (links) in ecological networks are cryptic, *i.e.* uncommon or hard to observe.
+This argument echoes @Jordano2016Sampling: sampling ecological interactions is difficult because it requires first the joint observation of two species, and then the observation of their interaction.
+In addition, it is generally expected that weak or rare interactions will be more prevalent in networks than common or strong interactions [@Csermely2004Strong], compared to strong, persistent interactions; this is notably the case in food chains, wherein many weaker interactions are key to the stability of a system [@Neutel2002Stability].
+In the light of these observations, we expect to see an over-representation of low-probability (hereafter rare) interactions under a model that accurately predicts interaction probabilities.
 
-Yet, the original metaweb definition, and indeed most past uses of
-metawebs, was based on the presence/absence of interactions. Moving towards
-*probabilistic* metawebs, by representing interactions as Bernoulli events [see
-*e.g.* @Poisot2016Structure], offers the opportunity to weigh these rare
-interactions appropriately. The inherent plasticity of interactions is important
-to capture: there have been documented instances of food webs undergoing rapid
-collapse/recovery cycles over short periods of time [*e.g.*
-@Pedersen2017Signatures]. Furthermore, because the structure of the metaweb
-cannot be known in advance, it is important to rely on predictive tools that do
-not assume a specific network topology for link prediction
-[@Gaucher2021Outlier], but are able to work on generalizations of the network.
-These considerations emphasize why metaweb predictions should focus on
-quantitative (preferentially probabilistic) predictions, and this should
-constrain the suite of models that are appropriate for prediction.
+Yet, the original metaweb definition, and indeed most past uses of metawebs, was based on the presence/absence of interactions.
+Moving towards *probabilistic* metawebs, by representing interactions as Bernoulli events [see *e.g.* @Poisot2016Structure], offers the opportunity to weigh these rare interactions appropriately.
+The inherent plasticity of interactions is important to capture: there have been documented instances of food webs undergoing rapid collapse/recovery cycles over short periods of time [*e.g.* @Pedersen2017Signatures].
+Furthermore, because the structure of the metaweb cannot be known in advance, it is important to rely on predictive tools that do not assume a specific network topology for link prediction [@Gaucher2021Outlier], but are able to work on generalizations of the network.
+These considerations emphasize why metaweb predictions should focus on quantitative (preferentially probabilistic) predictions, and this should constrain the suite of models that are appropriate for prediction.
 
-It is important to recall that a metaweb is intended as a catalogue of all
-potential (feasible) interactions, which is then filtered for a given
-application [@Morales-Castilla2015Inferring]. It is therefore important to
-separate the interactions that happen "almost surely" (repeated observational
-data), "almost never" (repeated lack of evidence *or* evidence that the link is
-forbidden through *e.g.* trait mis-match), and interactions with a probability
-that lays somewhere in between [@Catchen2023Missing]. In a sense, that most
-ecological interactions are elusive can call for a slightly different approach
-to sampling: once the common interactions are documented, the effort required in
-documenting each rare interaction will increase exponentially
-[@Jordano2016Sampling]. Recent proposals in other fields relying on machine
-learning approaches emphasize the idea that algorithms meant to predict, through
-the assumption that they approximate the process generating the data, can also
-act as data generators [@Hoffmann2019Machine]. High quality observational data
-can be used to infer core rules underpinning network structure, and be
-supplemented with synthetic data coming from predictive models trained on them,
-thereby increasing the volume of information available for analysis. Indeed,
-@Strydom2021Roadmap suggested that knowing the metaweb may render the prediction
-of local networks easier, because it fixes an "upper bound" on which
-interactions can exist. In this context, a probabilistic metaweb represents an
-aggregation of informative priors on the biological feasibility of interactions,
-which is usually hard to obtain yet has possibly the most potential to boost our
-predictive ability of local networks [@Bartomeus2013Understanding;
-@Bartomeus2016Common]. This would represent a departure from simple rules
-expressed at the network scale [*e.g.* @Williams2000Simple] to a view of network
-prediction based on learning the rules that underpin interactions *and* their
-variability [@Gupta2022Simultaneously].
+It is important to recall that a metaweb is intended as a catalogue of all potential (feasible) interactions, which is then filtered for a given application [@Morales-Castilla2015Inferring].
+It is therefore important to separate the interactions that happen "almost surely" (repeated observational data), "almost never" (repeated lack of evidence *or* evidence that the link is forbidden through *e.g.* trait mis-match), and interactions with a probability that lays somewhere in between [@Catchen2023Missing].
+In a sense, that most ecological interactions are elusive can call for a slightly different approach to sampling: once the common interactions are documented, the effort required in documenting each rare interaction will increase exponentially [@Jordano2016Sampling].
+Recent proposals in other fields relying on machine learning approaches emphasize the idea that algorithms meant to predict, through the assumption that they approximate the process generating the data, can also act as data generators [@Hoffmann2019Machine].
+High quality observational data can be used to infer core rules underpinning network structure, and be supplemented with synthetic data coming from predictive models trained on them, thereby increasing the volume of information available for analysis.
+Indeed, @Strydom2021Roadmap suggested that knowing the metaweb may render the prediction of local networks easier, because it fixes an "upper bound" on which interactions can exist.
+In this context, a probabilistic metaweb represents an aggregation of informative priors on the biological feasibility of interactions, which is usually hard to obtain yet has possibly the most potential to boost our predictive ability of local networks [@Bartomeus2013Understanding; @Bartomeus2016Common].
+This would represent a departure from simple rules expressed at the network scale [*e.g.* @Williams2000Simple] to a view of network prediction based on learning the rules that underpin interactions *and* their variability [@Gupta2022Simultaneously].
 
-![The embedding process (**A**) can help to identify links (interactions) that
-may have been missed within the original community (represented by the orange
-dashed arrows, **B**). Transfer learning (**D**) allows for the prediction links
-(interactions) even when novel species (**C**) are included alongside the
-original community. This is achieved by learning using other relevant predictors
-(*e.g.* traits) in conjunction with the known interactions to infer latent
-values (**E**). Ultimately this allows us to predict links (interactions) for
-species external from the original sample (blue dashed arrows) as well as
-missing within sample links (**F**). Within this context the predicted (and
-original) networks as well as the ecological predictors used (green boxes) are
-products that can be quantified through measurements in the field, whereas the
-embedded as well as imputed matrices (purple box) are representative of a
-decomposition of the interaction matrices onto the embedding
-space](figures/conceptual_2.png){#fig:embedding}
+![The embedding process (**A**) can help to identify links (interactions) that may have been missed within the original community (represented by the orange dashed arrows, **B**).
+Transfer learning (**D**) allows for the prediction links (interactions) even when novel species (**C**) are included alongside the original community.
+This is achieved by learning using other relevant predictors (*e.g.* traits) in conjunction with the known interactions to infer latent values (**E**).
+Ultimately this allows us to predict links (interactions) for species external from the original sample (blue dashed arrows) as well as missing within sample links (**F**).
+Within this context the predicted (and original) networks as well as the ecological predictors used (green boxes) are products that can be quantified through measurements in the field, whereas the embedded as well as imputed matrices (purple box) are representative of a decomposition of the interaction matrices onto the embedding space](figures/conceptual_2.png){#fig-embedding}
 
@@
 
-Graph (or network) embedding (@fig:embedding) is a family of machine learning
-techniques, whose main task is to learn a mapping function from a discrete graph
-to a continuous domain [@Arsov2019Network; @Chami2022Machine]. Their main goal
-is to learn a low dimensional vector representation of the graph (embeddings),
-such that its key properties (*e.g.* local or global structures) are retained in
-the embedding space [@Yan2005Graph]. The embedding space may, but will not
-necessarily, have lower dimensionality than the graph. Ecological networks are
-promising candidates for the routine application of embeddings, as they tend to
-possess a shared structural backbone [see *e.g.* @BramonMora2018Identifying],
-which hints at structural invariants in empirical data. Assuming that these
-structural invariants are common enough, they would dominate the structure of
-networks, and therefore be adequately captured by the first (lower) dimensions
-of an embedding, without the need to measure derived aspects of their structure
-(*e.g.* motifs, paths, modularity, ...).
+Graph (or network) embedding (@fig-embedding) is a family of machine learning techniques, whose main task is to learn a mapping function from a discrete graph to a continuous domain [@Arsov2019Network; @Chami2022Machine].
+Their main goal is to learn a low dimensional vector representation of the graph (embeddings), such that its key properties (*e.g.* local or global structures) are retained in the embedding space [@Yan2005Graph].
+The embedding space may, but will not necessarily, have lower dimensionality than the graph.
+Ecological networks are promising candidates for the routine application of embeddings, as they tend to possess a shared structural backbone [see *e.g.* @BramonMora2018Identifying], which hints at structural invariants in empirical data.
+Assuming that these structural invariants are common enough, they would dominate the structure of networks, and therefore be adequately captured by the first (lower) dimensions of an embedding, without the need to measure derived aspects of their structure (*e.g.* motifs, paths, modularity, ...).
 
@@
 
-Before moving further, it is important to clarify the epistemic status of node
-values derived from embeddings: specifically, they are *not* functional traits,
-and therefore should not be interpreted in terms of effects or responses. As per
-the framework of @Malaterre2019Functional, these values neither derive from, nor
-result in, changes in organismal performance, and should therefore not be used
-to quantify *e.g.* functional diversity. This holds true even when there are
-correlations between latent values and functional traits: although these enable
-an ecological discussion of how traits condition the structure of the network,
-the existence of a statistical relationship does not elevate the latent values
-to the status of functional traits.
+Before moving further, it is important to clarify the epistemic status of node values derived from embeddings: specifically, they are *not* functional traits, and therefore should not be interpreted in terms of effects or responses.
+As per the framework of @Malaterre2019Functional, these values neither derive from, nor result in, changes in organismal performance, and should therefore not be used to quantify *e.g.* functional diversity.
+This holds true even when there are correlations between latent values and functional traits: although these enable an ecological discussion of how traits condition the structure of the network, the existence of a statistical relationship does not elevate the latent values to the status of functional traits.
 
-Rather than directly predicting biological rules [see *e.g.* @Pichler2020Machine
-for an overview], which may be confounded by the sparse nature of graph data,
-learning embeddings works in the low-dimensional space that maximizes
-information about the network structure. This approach is further justified by
-the observation, for example, that the macro-evolutionary history of a network
-is adequately represented by some graph embeddings [Random dot product graphs
-(RDPG); see @DallaRiva2016Exploring]. In a recent publication, @Strydom2022Food
-have used an embedding (based on RDPG) to project a metaweb of trophic
-interactions between European mammals, and transferred this information to
-mammals of Canada, using the phylogenetic distance between related clades to
-infer the values in the latent subspace into which the European metaweb was
-projected. By performing the RDPG step on re-constructed values, this approach
-yields a probabilistic trophic metaweb for mammals of Canada based on knowledge
-of European species, despite a limited ($\approx$ 5%) taxonomic overlap, and
-illustrates how the values derived from an embedding can be used for prediction
-without being "traits" of the species they represent.
+Rather than directly predicting biological rules [see *e.g.* @Pichler2020Machine for an overview], which may be confounded by the sparse nature of graph data, learning embeddings works in the low-dimensional space that maximizes information about the network structure.
+This approach is further justified by the observation, for example, that the macro-evolutionary history of a network is adequately represented by some graph embeddings [Random dot product graphs (RDPG); see @DallaRiva2016Exploring].
+In a recent publication, @Strydom2022Food have used an embedding (based on RDPG) to project a metaweb of trophic interactions between European mammals, and transferred this information to mammals of Canada, using the phylogenetic distance between related clades to infer the values in the latent subspace into which the European metaweb was projected.
+By performing the RDPG step on re-constructed values, this approach yields a probabilistic trophic metaweb for mammals of Canada based on knowledge of European species, despite a limited ($\approx$ 5%) taxonomic overlap, and illustrates how the values derived from an embedding can be used for prediction without being "traits" of the species they represent.
 
@@
 
-Food webs are inherently low-dimensional objects, and can be adequately
-represented with less than ten dimensions [@Braga2021Phylogenetic;
-@Eklof2013Dimensionality; @Braga2019Spatial]. Simulation results by
-@Botella2022Appraisal suggested that there is no dominant method to identify
-architectural similarities between networks: multiple approaches need to be
-tested and compared to the network descriptor of interest on a problem-specific
-basis. This matches previous results on graph embedding, wherein different
-embedding algorithms yield different network embeddings [@Goyal2018Graph],
-calling for a careful selection of the problem-specific approach to use. In
-@tbl:methods, we present a selection of common graph and node embedding methods,
-alongside examples of their use to predict interactions or statistical
-associations between species. These methods rely largely on linear algebra or
-pseudo-random walks on graphs. All forms of embeddings presented in @tbl:methods
-share the common property of summarizing their objects into (sets of) dense
-feature vectors, that capture the overall network structure, pairwise
-information on nodes, and emergent aspects of the network, in a compressed way
-(*i.e.* with some information loss, as we later discuss in the illustration).
-Node embeddings tend to focus on maintaining pairwise relationships (*i.e.*
-species interactions), while graph embeddings focus on maintaining the network
-structure (*i.e.* emergent properties). Nevertheless, some graph embedding
-techniques [like RDPG, see *e.g.* @Wu2021Maximum] will provide high-quality
-node-level embeddings while also preserving network structure.
+Food webs are inherently low-dimensional objects, and can be adequately represented with less than ten dimensions [@Braga2021Phylogenetic; @Eklof2013Dimensionality; @Braga2019Spatial].
+Simulation results by @Botella2022Appraisal suggested that there is no dominant method to identify architectural similarities between networks: multiple approaches need to be tested and compared to the network descriptor of interest on a problem-specific basis.
+This matches previous results on graph embedding, wherein different embedding algorithms yield different network embeddings [@Goyal2018Graph], calling for a careful selection of the problem-specific approach to use.
+In @tbl-methods, we present a selection of common graph and node embedding methods, alongside examples of their use to predict interactions or statistical associations between species.
+These methods rely largely on linear algebra or pseudo-random walks on graphs.
+All forms of embeddings presented in @tbl-methods share the common property of summarizing their objects into (sets of) dense feature vectors, that capture the overall network structure, pairwise information on nodes, and emergent aspects of the network, in a compressed way (*i.e.* with some information loss, as we later discuss in the illustration).
+Node embeddings tend to focus on maintaining pairwise relationships (*i.e.* species interactions), while graph embeddings focus on maintaining the network structure (*i.e.* emergent properties).
+Nevertheless, some graph embedding techniques [like RDPG, see *e.g.* @Wu2021Maximum] will provide high-quality node-level embeddings while also preserving network structure.
 
 ::: {#box-gnn .callout-note}
-## Graph Neural Networks {#box-gnn}
+## Box 1 - Graph Neural Networks
 
-One prominent family of approaches we do not discuss in the present manuscript
-is Graph Neural Networks [GNN; @Zhou2020Graph]. GNN are, in a sense, a method to
-embed a graph into a dense subspace, but belong to the family of deep learning
-methods, which has its own set of practices [see *e.g.* @Goodfellow2016Deep]. An
-important issue with methods based on deep learning is that, because their
-parameter space is immense, the sample size of the data fed into them must be
-similarly large (typically thousands of instances). This is a requirement for
-the model to converge correctly during training, but this assumption is unlikely
-to be met given the size of datasets currently available for metawebs (or single
-time/location species interaction networks). This data volume requirement is
-mostly absent from the techniques we list below. Furthermore, GNN still have
-some challenges related to their shallow structure, and concerns related to
-scalability [see @Gupta2021Graph for a review], which are mostly absent from the
-methods listed in @tbl:methods. Assuming that the uptake of next-generation
-biomonitoring techniques does indeed deliver larger datasets on species
-interactions [@Bohan2017Nextgeneration], there is nevertheless the potential for
-GNN to become an applicable embedding/predictive technique in the coming years.
+One prominent family of approaches we do not discuss in the present manuscript is Graph Neural Networks [GNN; @Zhou2020Graph].
+GNN are, in a sense, a method to embed a graph into a dense subspace, but belong to the family of deep learning methods, which has its own set of practices [see *e.g.* @Goodfellow2016Deep].
+An important issue with methods based on deep learning is that, because their parameter space is immense, the sample size of the data fed into them must be similarly large (typically thousands of instances).
+This is a requirement for the model to converge correctly during training, but this assumption is unlikely to be met given the size of datasets currently available for metawebs (or single time/location species interaction networks).
+This data volume requirement is mostly absent from the techniques we list below.
+Furthermore, GNN still have some challenges related to their shallow structure, and concerns related to scalability [see @Gupta2021Graph for a review], which are mostly absent from the methods listed in @tbl-methods.
+Assuming that the uptake of next-generation biomonitoring techniques does indeed deliver larger datasets on species interactions [@Bohan2017Nextgeneration], there is nevertheless the potential for GNN to become an applicable embedding/predictive technique in the coming years.
 :::
 
-Graph embeddings *can* serve as a dimensionality reduction method. For example,
-RDPG [@Strydom2022Food] and t-SVD [truncated Singular Value Decomposition;
-@Poisot2021Imputing] typically embed networks using fewer dimensions than the
-original network [the original network has as many dimensions as species, and as
-many informative dimensions as trophically unique species; @Strydom2021Svd].
-However, this is not necessarily the case -- indeed, one may perform a PCA (a
-special case of SVD) to project the raw data into a subspace that improves the
-efficacy of t-SNE [t-distributed stochastic neighbor embedding;
-@Maaten2009Learning]. There are many dimensionality reductions
-[@Anowar2021Conceptual] that can be applied to an embedded network should the
-need for dimensionality reduction (for example for data visualization) arise. In
-brief, many graph embeddings *can* serve as dimensionality reduction steps, but
-not all do, neither do all dimensionality reduction methods provide adequate
-graph embedding capacities. In the next section (and @fig:embedding), we show
-how the amount of dimensionality reduction can affect the quality of the
-embedding.
+Graph embeddings *can* serve as a dimensionality reduction method.
+For example, RDPG [@Strydom2022Food] and t-SVD [truncated Singular Value Decomposition; @Poisot2021Imputing] typically embed networks using fewer dimensions than the original network [the original network has as many dimensions as species, and as many informative dimensions as trophically unique species; @Strydom2021Svd].
+However, this is not necessarily the case -- indeed, one may perform a PCA (a special case of SVD) to project the raw data into a subspace that improves the efficacy of t-SNE [t-distributed stochastic neighbor embedding; @Maaten2009Learning].
+There are many dimensionality reductions [@Anowar2021Conceptual] that can be applied to an embedded network should the need for dimensionality reduction (for example for data visualization) arise.
+In brief, many graph embeddings *can* serve as dimensionality reduction steps, but not all do, neither do all dimensionality reduction methods provide adequate graph embedding capacities.
+In the next section (and @fig-embedding), we show how the amount of dimensionality reduction can affect the quality of the embedding.
 
 | Method        | Object          | Technique                        | Reference                | Application                                                                                                       |
-| ------------- | --------------- | -------------------------------- | ------------------------ | ----------------------------------------------------------------------------------------------------------------- |
+|-------------|-------------|-------------|-------------|--------------------|
 | tSNE          | nodes           | statistical divergence           | @Hinton2002Stochastic    | [@Cieslak2020Tdistributed, species-environment responses $^a$] [@Gibb2021Data, host-virus network representation] |
@@
 
-: Overview of some common graph embedding approaches, by type of embedded
-objects, alongside examples of their use in the prediction of species
-interactions. These methods have not yet been routinely used to predict species
-interactions; most examples that we identified were either statistical
-associations, or analogues to joint species distribution models. $^a$:
-application is concerned with *statistical* interactions, which are not
-necessarilly direct biotic interactions; $^b$:application is concerned with
-joint-SDM-like approach, which is also very close to statistical associations as
-opposed to direct biotic interactions. Given the need to evaluate different
-methods on a problem-specific basis, the fact that a lot of methods have not
-been used on network problems is an opportunity for benchmarking and method
-development. Note that the row for PCA also applies to kernel/probabilistic PCA,
-which are variations on the more general method of SVD. Note further that tSNE
-has been included because it is frequently used to embed graphs, including of
-species associations/interactions, despite not being strictly speaking, a graph
-embedding technique [see *e.g.* @Chami2022Machine]. {#tbl:methods}
+: Overview of some common graph embedding approaches, by type of embedded objects, alongside examples of their use in the prediction of species interactions.
+These methods have not yet been routinely used to predict species interactions; most examples that we identified were either statistical associations, or analogues to joint species distribution models.
+$^a$: application is concerned with *statistical* interactions, which are not necessarilly direct biotic interactions; $^b$:application is concerned with joint-SDM-like approach, which is also very close to statistical associations as opposed to direct biotic interactions.
+Given the need to evaluate different methods on a problem-specific basis, the fact that a lot of methods have not been used on network problems is an opportunity for benchmarking and method development.
+Note that the row for PCA also applies to kernel/probabilistic PCA, which are variations on the more general method of SVD.
+Note further that tSNE has been included because it is frequently used to embed graphs, including of species associations/interactions, despite not being strictly speaking, a graph embedding technique [see *e.g.* @Chami2022Machine].
+{#tbl-methods}
 
-The popularity of graph embedding techniques in machine learning is more than
-the search for structural invariants: graphs are discrete objects, and machine
-learning techniques tend to handle continuous data better. Bringing a sparse
-graph into a continuous, dense vector space [@Xu2021Understanding] opens up a
-broader variety of predictive algorithms, notably of the sort that are able to
-predict events as probabilities [@Murphy2022Probabilistic]. Furthermore, the
-projection of the graph itself is a representation that can be learned;
-@Runghen2021Exploiting, for example, used a neural network to learn the
-embedding of a network in which not all interactions were known, based on the
-nodes' metadata. This example has many parallels in ecology (see @fig:embedding
-**C**), in which node metadata can be represented by phylogeny, abundance, or
-functional traits. Using phylogeny as a source of information assumes (or
-strives to capture) the action of evolutionary processes on network structure,
-which at least for food webs have been well documented [@Braga2021Phylogenetic;
-@DallaRiva2016Exploring; @Eklof2016Phylogenetic; @Stouffer2007Evidence;
-@Stouffer2012Evolutionary]; similarly, the use of functional traits assumes that
-interactions can be inferred from the knowledge of trait-matching rules, which
-is similarly well supported in the empirical literature
-[@Bartomeus2013Understanding; @Bartomeus2016Common; @Goebel2023Body;
-@Gravel2013Inferring]. Relating this information to an embedding rather than a
-list of network measures would allow to capture their effect on the more
-fundamental aspects of network structure; conversely, the absence of a
-phylogenetic or functional signal may suggest that evolutionary/trait processes
-are not strong drivers of network structure, therefore opening a new way to
-perform hypothesis testing.
+The popularity of graph embedding techniques in machine learning is more than the search for structural invariants: graphs are discrete objects, and machine learning techniques tend to handle continuous data better.
+Bringing a sparse graph into a continuous, dense vector space [@Xu2021Understanding] opens up a broader variety of predictive algorithms, notably of the sort that are able to predict events as probabilities [@Murphy2022Probabilistic].
+Furthermore, the projection of the graph itself is a representation that can be learned; @Runghen2021Exploiting, for example, used a neural network to learn the embedding of a network in which not all interactions were known, based on the nodes' metadata.
+This example has many parallels in ecology (see @fig-embedding **C**), in which node metadata can be represented by phylogeny, abundance, or functional traits.
+Using phylogeny as a source of information assumes (or strives to capture) the action of evolutionary processes on network structure, which at least for food webs have been well documented [@Braga2021Phylogenetic; @DallaRiva2016Exploring; @Eklof2016Phylogenetic; @Stouffer2007Evidence; @Stouffer2012Evolutionary]; similarly, the use of functional traits assumes that interactions can be inferred from the knowledge of trait-matching rules, which is similarly well supported in the empirical literature [@Bartomeus2013Understanding; @Bartomeus2016Common; @Goebel2023Body; @Gravel2013Inferring].
+Relating this information to an embedding rather than a list of network measures would allow to capture their effect on the more fundamental aspects of network structure; conversely, the absence of a phylogenetic or functional signal may suggest that evolutionary/trait processes are not strong drivers of network structure, therefore opening a new way to perform hypothesis testing.
 
@@
 
-In this section, we illustrate the embedding of a collection of bipartite
-networks collected by @Hadfield2014Tale, using t-SVD and RDPG. Briefly, an RDPG
-decomposes a network into two subspaces (left and right), which are matrices
-that when multiplied give an approximation of the original network. RDPG has the
-particularly desirable properties of being a graph embedding technique that
-produces relevant node-level feature vectors, and provides good approximations
-of graphs with varied structures [@Athreya2017Statistical]. The code to
-reproduce this example is available as supplementary material [note, for the
-sake of comparison, that @Strydom2021Roadmap have an example using embedding
-through PCA followed by prediction using a deep neural network on the same
-dataset]. The resulting (binary) metaweb $\mathcal{M}$ has 2131 interactions
-between 206 parasites and 121 hosts, and its adjacency matrix has full rank
-(*i.e.* it represents a space with 121 dimensions). All analyses were done using
-Julia [@Bezanson2017Julia] version 1.7.2, *Makie.jl* [@Danisch2021Makie], and
-*EcologicalNetworks.jl* [@Poisot2019Ecologicalnetworks].
+In this section, we illustrate the embedding of a collection of bipartite networks collected by @Hadfield2014Tale, using t-SVD and RDPG.
+Briefly, an RDPG decomposes a network into two subspaces (left and right), which are matrices that when multiplied give an approximation of the original network.
+RDPG has the particularly desirable properties of being a graph embedding technique that produces relevant node-level feature vectors, and provides good approximations of graphs with varied structures [@Athreya2017Statistical].
+The code to reproduce this example is available as supplementary material [note, for the sake of comparison, that @Strydom2021Roadmap have an example using embedding through PCA followed by prediction using a deep neural network on the same dataset].
+The resulting (binary) metaweb $\mathcal{M}$ has 2131 interactions between 206 parasites and 121 hosts, and its adjacency matrix has full rank (*i.e.* it represents a space with 121 dimensions).
+All analyses were done using Julia [@Bezanson2017Julia] version 1.7.2, *Makie.jl* [@Danisch2021Makie], and *EcologicalNetworks.jl* [@Poisot2019Ecologicalnetworks].
 
-![Validation of an embedding for a host-parasite metaweb, using Random Dot
-Product Graphs. **A**, decrease in approximation error as the number of
-dimensions in the subspaces increases. **B**, increase in cumulative variance
-explained as the number of ranks considered increases; in **A** and **B**, the
-dot represents the point of inflexion in the curve (at rank 39) estimated using
-the finite differences method. **C**, position of hosts and parasites in the
-space of latent variables on the first and second dimensions of their respective
-subspaces (the results have been clamped to the unit interval). **D**, predicted
-interaction weight from the RDPG based on the status of the species pair in the
-metaweb.](figures/illustration-part1.png){#fig:illustration1}
+{{< embed notebooks/SupplementaryMaterial.ipynb#fig-illustration-1 >}}
 
-In @fig:illustration1, we focus on some statistical checks of the embedding. In
-panel **A**, we show that the averaged $L_2$ loss (*i.e.* the sum of squared
-errors) between the empirical and reconstructed metaweb decreases when the
-number of dimensions (rank) of the subspace increases, with an inflection at 39
-dimensions (out of 120 initially) according to the finite differences method. As
-discussed by @Runghen2021Exploiting, there is often a trade-off between the
-number of dimensions to use (more dimensions are more computationally demanding)
-and the quality of the representation. In panel **B**, we show the increase in
-cumulative variance explained at each rank, and visualize that using 39 ranks
-explains about 70% of the variance in the empirical metaweb. This is a different
-information from the $L_2$ loss (which is averaged across interactions), as it
-works on the eigenvalues of the embedding, and therefore captures higher-level
-features of the network. In panel **C**, we show positions of hosts and
-parasites on the first two dimensions of the left and right subspaces. Note that
-these values largely skew negative, because the first dimensions capture the
-coarse structure of the network: most pairs of species do not interact, and
-therefore have negative values. Finally in panel **D**, we show the predicted
-weight (*i.e.* the result of the multiplication of the RDGP subspaces at a rank
-of 39) as a function of whether the interactions are observed, not-observed, or
-unknown due to lack of co-occurrence in the original dataset. This reveals that
-the observed interactions have higher predicted weights, although there is some
-overlap; the usual approach to identify potential interactions based on this
-information would be a thresholding analysis, which is outside the scope of this
-manuscript (and is done in the papers cited in this illustration). Because the
-values returned from RDPG are not bound to the unit interval, we performed a
-clamping of the weights to the unit space, showing a one-inflation in documented
-interactions, and a zero-inflation in other species pairs. This last figure
-crosses from the statistical into the ecological, by showing that species pairs
-with no documented co-occurrence have weights that are not distinguishable from
-species pairs with no documented interactions, suggesting that (as befits a
-host-parasite model) the ability to interact is a strong predictor of
-co-occurrence.
+In @fig-illustration-1, we focus on some statistical checks of the embedding.
+In panel **A**, we show that the averaged $L_2$ loss (*i.e.* the mean of squared errors) between the empirical and reconstructed metaweb decreases when the number of dimensions (rank) of the subspace increases, with an inflection at 39 dimensions (out of 120 initially) according to the finite differences method.
+As discussed by @Runghen2021Exploiting, there is often a trade-off between the number of dimensions to use (more dimensions are more computationally demanding) and the quality of the representation.
+In panel **B**, we show the increase in cumulative variance explained at each rank, and visualize that using 39 ranks explains about 70% of the variance in the empirical metaweb.
+This is a different information from the $L_2$ loss (which is averaged across interactions), as it works on the eigenvalues of the embedding, and therefore captures higher-level features of the network.
+In panel **C**, we show positions of hosts and parasites on the first two dimensions of the left and right subspaces.
+Note that these values largely skew negative, because the first dimensions capture the coarse structure of the network: most pairs of species do not interact, and therefore have negative values.
+Finally in panel **D**, we show the predicted weight (*i.e.* the result of the multiplication of the RDGP subspaces at a rank of 39) as a function of whether the interactions are observed, not-observed, or unknown due to lack of co-occurrence in the original dataset.
+This reveals that the observed interactions have higher predicted weights, although there is some overlap; the usual approach to identify potential interactions based on this information would be a thresholding analysis, which is outside the scope of this manuscript (and is done in the papers cited in this illustration).
+Because the values returned from RDPG are not bound to the unit interval, we performed a clamping of the weights to the unit space, showing a one-inflation in documented interactions, and a zero-inflation in other species pairs.
+This last figure crosses from the statistical into the ecological, by showing that species pairs with no documented co-occurrence have weights that are not distinguishable from species pairs with no documented interactions, suggesting that (as befits a host-parasite model) the ability to interact is a strong predictor of co-occurrence.
 
-![Ecological analysis of an embedding for a host-parasite metaweb, using Random
-Dot Product Graphs. **A**, relationship between the number of parasites and
-position along the first axis of the right-subspace for all hosts, showing that
-the embedding captures elements of network structure at the species scale.
-**B**, weak relationship between the body mass of hosts (in grams) and the
-position alongside the same dimension. **C**, weak relationship between body
-mass of hosts and parasite richness. **D**, distribution of positions alongside
-the same axis for hosts grouped by taxonomic
-family.](figures/illustration-part2.png){#fig:illustration2}
+{{< embed notebooks/SupplementaryMaterial.ipynb#fig-illustration-2 >}}
 
-The results of @fig:illustration1 show that we can extract an embedding of the
-metaweb that captures enough variance to be relevant; specifically, this is true
-for both $L_2$ loss (indicating that RDPG is able to capture pairwise processes)
-and the cumulative variance explained (indicating that RDPG is able to capture
-network-level structure). Therefore, in @fig:illustration2, we relate the values
-of latent variables for hosts to different ecologically-relevant data. In panel
-**A**, we show that host with a higher value on the first dimension have fewer
-parasites. This relates to the body size of hosts in the *PanTHERIA* database
-[@Jones2009Pantheria], as shown in panel **B**: interestingly, the position on
-the first axis is only weakly correlated to body mass of the host; this matches
-well established results showing that body size/mass is not always a direct
-predictor of parasite richness in terrestrial mammals [@Morand1998Density], a
-result we observe in panel **C**. Finally, in panel **D**, we can see how
-different taxonomic families occupy different positions on the first axis, with
-*e.g.* Sciuridae being biased towards higher values. These results show how we
-can look for ecological informations in the output of network embeddings, which
-can further be refined into the selection of predictors for transfer learning.
+The results of @fig-illustration-1 show that we can extract an embedding of the metaweb that captures enough variance to be relevant; specifically, this is true for both $L_2$ loss (indicating that RDPG is able to capture pairwise processes) and the cumulative variance explained (indicating that RDPG is able to capture network-level structure).
+Therefore, in @fig-illustration-2, we relate the values of latent variables for hosts to different ecologically-relevant data.
+In panel **A**, we show that host with a higher value on the first dimension have fewer parasites.
+This relates to the body size of hosts in the *PanTHERIA* database [@Jones2009Pantheria], as shown in panel **B**: interestingly, the position on the first axis is only weakly correlated to body mass of the host; this matches well established results showing that body size/mass is not always a direct predictor of parasite richness in terrestrial mammals [@Morand1998Density], a result we observe in panel **C**.
+Finally, in panel **D**, we can see how different taxonomic families occupy different positions on the first axis, with *e.g.* Sciuridae being biased towards higher values.
+These results show how we can look for ecological informations in the output of network embeddings, which can further be refined into the selection of predictors for transfer learning.
 
@@
 
-Metaweb inference seeks to provide information about the interactions between
-species at a large spatial scale, typically a scale large enough to be
-considered of biogeographic relevance (indeed, many of the examples covered in
-the introduction span areas larger than a country, some of them global). But as
-@Herbert1965Dune rightfully pointed out, "[y]ou can't draw neat lines around
-planet-wide problems"; any inference of a metaweb must therefore contend with
-several novel, interwoven, families of problems. In this section, we outline
-three that we think are particularly important, and can discuss how they may
-addressed with subsequent data analysis or simulations, and how they emerge in
-the specific context of using embeddings; some of these issues are related to
-the application of these methods at the science-policy interface.
+Metaweb inference seeks to provide information about the interactions between species at a large spatial scale, typically a scale large enough to be considered of biogeographic relevance (indeed, many of the examples covered in the introduction span areas larger than a country, some of them global).
+But as @Herbert1965Dune rightfully pointed out, "\[y\]ou can't draw neat lines around planet-wide problems"; any inference of a metaweb must therefore contend with several novel, interwoven, families of problems.
+In this section, we outline three that we think are particularly important, and can discuss how they may addressed with subsequent data analysis or simulations, and how they emerge in the specific context of using embeddings; some of these issues are related to the application of these methods at the science-policy interface.
+Adressing these considerations as part of the methodological discussion is particularly important, as the construction of metawebs can perpetuate legacies of biases in data (Box 2).
 
@@
 
-If the initial metaweb is too narrow in scope, notably from a taxonomic point of
-view, the chances of finding another area with enough related species (through
-phylogenetic relatedness or similarity of functional traits) to make a reliable
-inference decreases. This is because transfer requires similarity
-(@fig:embedding). A diagnostic for the lack of similar species would likely be
-large confidence intervals during estimation of the values in the low-rank
-space. In other words, the representation of the original graph is difficult to
-transfer to the new problem. Alternatively, if the initial metaweb is too large
-(taxonomically), then the resulting embeddings would need to represent
-interactions between taxonomic groups that are not present in the new location.
-This would lead to a much higher variance in the starting dataset, and to
-under-dispersion in the target dataset, resulting in the potential under or over
-estimation of the strength of new predicted interactions.
-@Llewelyn2022Predicting provided compelling evidence for these situations by
-showing that, even at small spatial scales, the transfer of information about
-interactions becomes more challenging when areas rich with endemic species are
-considered. The lack of well documented metawebs is currently preventing the
-development of more concrete guidelines. The question of phylogenetic
-relatedness and distribution is notably relevant if the metaweb is assembled in
-an area with mostly endemic species (*e.g.* a system that has undergone recent
-radiation or that has remained in isolation for a long period of time might not
-have an analogous system with which to draw knowledge from), and as with every
-predictive algorithm, there is room for the application of our best ecological
-judgement. Because this problem relates to distribution of species in the
-geographic or phylogenetic space, it can certainly be approached through
-assessing the performance of embedding transfer in simulated starting/target
-species pools.
+If the initial metaweb is too narrow in scope, notably from a taxonomic point of view, the chances of finding another area with enough related species (through phylogenetic relatedness or similarity of functional traits) to make a reliable inference decreases.
+This is because transfer requires similarity (@fig-embedding).
+A diagnostic for the lack of similar species would likely be large confidence intervals during estimation of the values in the low-rank space.
+In other words, the representation of the original graph is difficult to transfer to the new problem.
+Alternatively, if the initial metaweb is too large (taxonomically), then the resulting embeddings would need to represent interactions between taxonomic groups that are not present in the new location.
+This would lead to a much higher variance in the starting dataset, and to under-dispersion in the target dataset, resulting in the potential under or over estimation of the strength of new predicted interactions.
+@Llewelyn2022Predicting provided compelling evidence for these situations by showing that, even at small spatial scales, the transfer of information about interactions becomes more challenging when areas rich with endemic species are considered.
+The lack of well documented metawebs is currently preventing the development of more concrete guidelines.
+The question of phylogenetic relatedness and distribution is notably relevant if the metaweb is assembled in an area with mostly endemic species (*e.g.* a system that has undergone recent radiation or that has remained in isolation for a long period of time might not have an analogous system with which to draw knowledge from), and as with every predictive algorithm, there is room for the application of our best ecological judgement.
+Because this problem relates to distribution of species in the geographic or phylogenetic space, it can certainly be approached through assessing the performance of embedding transfer in simulated starting/target species pools.
 
@@
 
-The area for which we seek to predict the metaweb should determine the species
-pool on which the embedding is performed. Metawebs can be constructed by
-assigning interactions in a list of species within specific regions. The upside
-of this approach is that information relevant for the construction of this
-dataset is likely to exist, as countries usually set conservation goals at the
-national level [@Buxton2021Key], and as quantitative instruments are
-consequently designed to work at these scales [@Turak2017Using]; specific
-strategies are often enacted at smaller scales, nested within a specific country
-[@Ray2021Biodiversity]. However, there is no guarantee that these arbitrary
-boundaries are meaningful. In fact, we do not have a satisfying answer to the
-question of "where does an ecological network stop?", the answer to which would
-dictate the spatial span to embed/predict. Recent results by @Martins2022Global
-suggested that networks are shaped within eco-regions, with abrupt structural
-transitions from an eco-region to the next. Should this trend hold generally,
-this would provide an ecologically-relevant scale at which metawebs can be
-downscaled and predicted. Other solutions could leverage network-area
-relationships to identify areas in which networks are structurally similar [see
-*e.g.* @Fortin2021Network; @Galiana2018Spatial; @Galiana2022Ecological]. Both of
-these solutions require ample pre-existing information about the network in
-space. Nevertheless, the inclusion of species for which we have data but that
-are not in the right spatial extent *may* improve the performance of approaches
-based on embedding and transfer, *if* they increase the similarity between the
-target and destination network. This proposal can specifically be evaluated by
-adding nodes to the network to embed, and assessing the performance of
-predictive models [see *e.g.* @Llewelyn2022Predicting].
+The area for which we seek to predict the metaweb should determine the species pool on which the embedding is performed.
+Metawebs can be constructed by assigning interactions in a list of species within specific regions.
+The upside of this approach is that information relevant for the construction of this dataset is likely to exist, as countries usually set conservation goals at the national level [@Buxton2021Key], and as quantitative instruments are consequently designed to work at these scales [@Turak2017Using]; specific strategies are often enacted at smaller scales, nested within a specific country [@Ray2021Biodiversity].
+However, there is no guarantee that these arbitrary boundaries are meaningful.
+In fact, we do not have a satisfying answer to the question of "where does an ecological network stop?", the answer to which would dictate the spatial span to embed/predict.
+Recent results by @Martins2022Global suggested that networks are shaped within eco-regions, with abrupt structural transitions from an eco-region to the next.
+Should this trend hold generally, this would provide an ecologically-relevant scale at which metawebs can be downscaled and predicted.
+Other solutions could leverage network-area relationships to identify areas in which networks are structurally similar [see *e.g.* @Fortin2021Network; @Galiana2018Spatial; @Galiana2022Ecological].
+Both of these solutions require ample pre-existing information about the network in space.
+Nevertheless, the inclusion of species for which we have data but that are not in the right spatial extent *may* improve the performance of approaches based on embedding and transfer, *if* they increase the similarity between the target and destination network.
+This proposal can specifically be evaluated by adding nodes to the network to embed, and assessing the performance of predictive models [see *e.g.* @Llewelyn2022Predicting].
 
-# Conclusion: metawebs, predictions, and people
+# Conclusion
 
-Predictive approaches in ecology, regardless of the scale at which they are
-deployed and the intent of their deployment, originate in the framework that
-contributed to the ongoing biodiversity crisis [@Adam2014Elephant] and
-reinforced environmental injustice [@Choudry2013Saving;
-@Dominguez2020Decolonising]. The risk of embedding this legacy in our models is
-real, especially when the impact of this legacy on species pools is being
-increasingly documented. This problem can be addressed by re-framing the way we
-interact with models, especially when models are intended to support
-conservation actions. Particularly on territories that were traditionally
-stewarded by Indigenous people, we must interrogate how predictive approaches
-and the biases that underpin them can be put to task in accompanying Indigenous
-principles of land management [@Eichhorn2019Steps; @Nokmaq2021Awakening]. The
-discussion of "algorithm-in-the-loop" approaches that is now pervasive in the
-machine learning community provides examples of why this is important.
-Human-algorithm interactions are notoriously difficult and can yield adverse
-effects [@Green2019Disparate; @Stevenson2021Algorithmic], suggesting the need to
-systematically study them for the specific purpose of, here, biodiversity
-governance. Improving the algorithmic literacy of decision makers is part of the
-solution [*e.g.* @Lamba2019Deep; @MoseboFernandes2020Machine], as we can
-reasonably expect that model outputs will be increasingly used to drive policy
-decisions [@Weiskopf2022Increasing]. Our discussion of these approaches need to
-go beyond the technical and statistical, and into the governance consequences
-they can have. To embed data also embeds historical and contemporary biases that
-acted on these data, both because they shaped the ecological processes
-generating them, and the global processes leading to their measurement and
-publication. For a domain as vast as species interaction networks, these biases
-exist at multiple scales along the way, and a challenge for prediction is not
-only to develop (or adopt) new quantitative tools, but to assess the behavior of
-these tools in the proper context.
+Predictive approaches in ecology, regardless of the scale at which they are deployed and the intent of their deployment, originate in the framework that contributed to the ongoing biodiversity crisis [@Adam2014Elephant] and reinforced environmental injustice [@Choudry2013Saving; @Dominguez2020Decolonising].
+The risk of embedding this legacy in our models is real, especially when the impact of this legacy on species pools is being increasingly documented.
+This problem can be addressed by re-framing the way we interact with models, especially when models are intended to support conservation actions.
+Particularly on territories that were traditionally stewarded by Indigenous people, we must interrogate how predictive approaches and the biases that underpin them can be put to task in accompanying Indigenous principles of land management [@Eichhorn2019Steps; @Nokmaq2021Awakening].
+The discussion of "algorithm-in-the-loop" approaches that is now pervasive in the machine learning community provides examples of why this is important.
+Human-algorithm interactions are notoriously difficult and can yield adverse effects [@Green2019Disparate; @Stevenson2021Algorithmic], suggesting the need to systematically study them for the specific purpose of, here, biodiversity governance.
+Improving the algorithmic literacy of decision makers is part of the solution [*e.g.* @Lamba2019Deep; @MoseboFernandes2020Machine], as we can reasonably expect that model outputs will be increasingly used to drive policy decisions [@Weiskopf2022Increasing].
+Our discussion of these approaches need to go beyond the technical and statistical, and into the governance consequences they can have.
+To embed data also embeds historical and contemporary biases that acted on these data, both because they shaped the ecological processes generating them, and the global processes leading to their measurement and publication.
+For a domain as vast as species interaction networks, these biases exist at multiple scales along the way, and a challenge for prediction is not only to develop (or adopt) new quantitative tools, but to assess the behavior of these tools in the proper context.
 
-::: {#box-legacy .callout-note}
-## Minding legacies shaping ecological datasets {#box-legacy}
+::: {#sec-box-legacy .callout-note}
+## Box 2 - Minding legacies shaping ecological datasets
 
-In large parts of the world, boundaries that delineate geographic regions are
-merely a reflection the legacy of settler colonialism, which drives global
-disparity in capacity to collect and publish ecological data. Applying any
-embedding to biased data does not debias them, but rather embeds these biases,
-propagating them to the models using embeddings to make predictions.
-Furthermore, the use of ecological data itself is not an apolitical act
-[@Nost2021Political]: data infrastructures tend to be designed to answer
-questions within national boundaries (therefore placing contingencies on what is
-available to be embedded), their use often drawing upon, and reinforcing,
-territorial statecraft [see *e.g.* @Barrett2005Environment]. As per
-@Machen2021Thinking, these biases are particularly important to consider when
-knowledge generated algorithmically is used to supplement or replace human
-decision-making, especially for governance (*e.g.* enacting conservation
-decisions on the basis of model prediction). As information on networks is
-increasingly leveraged for conservation actions [see *e.g.* @Eero2021Use;
-@Naman2022Food; @Stier2017Integrating], the need to appraise and correct biases
-that are unwittingly propagated to algorithms when embedded from the original
-data is immense. These considerations are even more urgent in the specific
-context of biodiversity data. Long-term colonial legacies still shape taxonomic
-composition to this day [@Lenzner2022Naturalized; @Raja2022Colonialism], and
-much shorter-term changes in taxonomic and genetic richness of wildlife emerged
-through environmental racism [@Schmidt2022Systemic]. Thus, the set of species
-found at a specific location is not only as the result of a response to
-ecological processes separate from human influence, but also the result of
-human-environment interaction as well as the result legislative/political
-histories.
+In large parts of the world, boundaries that delineate geographic regions are merely a reflection the legacy of settler colonialism, which drives global disparity in capacity to collect and publish ecological data.
+Applying any embedding to biased data does not debias them, but rather embeds these biases, propagating them to the models using embeddings to make predictions.
+Furthermore, the use of ecological data itself is not an apolitical act [@Nost2021Political]: data infrastructures tend to be designed to answer questions within national boundaries (therefore placing contingencies on what is available to be embedded), their use often drawing upon, and reinforcing, territorial statecraft [see *e.g.* @Barrett2005Environment].
+As per @Machen2021Thinking, these biases are particularly important to consider when knowledge generated algorithmically is used to supplement or replace human decision-making, especially for governance (*e.g.* enacting conservation decisions on the basis of model prediction).
+As information on networks is increasingly leveraged for conservation actions [see *e.g.* @Eero2021Use; @Naman2022Food; @Stier2017Integrating], the need to appraise and correct biases that are unwittingly propagated to algorithms when embedded from the original data is immense.
+These considerations are even more urgent in the specific context of biodiversity data.
+Long-term colonial legacies still shape taxonomic composition to this day [@Lenzner2022Naturalized; @Raja2022Colonialism], and much shorter-term changes in taxonomic and genetic richness of wildlife emerged through environmental racism [@Schmidt2022Systemic].
+Thus, the set of species found at a specific location is not only as the result of a response to ecological processes separate from human influence, but also the result of human-environment interaction as well as the result legislative/political histories.
 :::
 
-**Acknowledgements:** We acknowledge that this study was conducted on land
-within the traditional unceded territory of the Saint Lawrence Iroquoian,
-Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. TP, TS, DC,
-and LP received funding from the Canadian Institute for Ecology & Evolution. FB
-is funded by the Institute for Data Valorization (IVADO). TS, SB, and TP are
-funded by a donation from the Courtois Foundation. CB was awarded a Mitacs
-Elevate Fellowship no. IT12391, in partnership with fRI Research, and also
-acknowledges funding from Alberta Innovates and the Forest Resources Improvement
-Association of Alberta. M-JF acknowledges funding from NSERC Discovery Grant and
-NSERC CRC. RR is funded by New Zealand’s Biological Heritage Ngā Koiora Tuku Iho
-National Science Challenge, administered by New Zealand Ministry of Business,
-Innovation, and Employment. BM is funded by the NSERC Alexander Graham Bell
-Canada Graduate Scholarship and the FRQNT master’s scholarship. LP acknowledges
-funding from NSERC Discovery Grant (NSERC RGPIN-2019-05771). TP acknowledges
-financial support from the Fondation Courtois, and NSERC through the Discovery
-Grants and Discovery Accelerator Supplement programs. MJF is supported by an
-NSERC PDF and an RBC Post-Doctoral Fellowship.
+**Acknowledgements:** We acknowledge that this study was conducted on land within the traditional unceded territory of the Saint Lawrence Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations.
+TP, TS, DC, and LP received funding from the Canadian Institute for Ecology & Evolution.
+FB is funded by the Institute for Data Valorization (IVADO).
+TS, SB, and TP are funded by a donation from the Courtois Foundation.
+CB was awarded a Mitacs Elevate Fellowship no.
+IT12391, in partnership with fRI Research, and also acknowledges funding from Alberta Innovates and the Forest Resources Improvement Association of Alberta.
+M-JF acknowledges funding from NSERC Discovery Grant and NSERC CRC.
+RR is funded by New Zealand's Biological Heritage Ngā Koiora Tuku Iho National Science Challenge, administered by New Zealand Ministry of Business, Innovation, and Employment.
+BM is funded by the NSERC Alexander Graham Bell Canada Graduate Scholarship and the FRQNT master's scholarship.
+LP acknowledges funding from NSERC Discovery Grant (NSERC RGPIN-2019-05771).
+TP acknowledges financial support from the Fondation Courtois, and NSERC through the Discovery Grants and Discovery Accelerator Supplement programs.
+MJF is supported by an NSERC PDF and an RBC Post-Doctoral Fellowship.
 
@@
 
-**Authors' contributions:** TS, and TP conceived the ideas discussed in the
-manuscript. All authors contributed to writing and editing the manuscript.
+**Authors' contributions:** TS, and TP conceived the ideas discussed in the manuscript. All authors contributed to writing and editing the manuscript.
 

### 2023-08-15 index.qmd
done

@@
 First, there is a relative scarcity of relevant data in most places globally -- which, due to the limitations in most predictive methods, restricts the ability to infer interactions to locations where it is least required (*i.e.* regions where we already have interaction data) leaving us unable to make inference in data scarce regions (where we most need it); second, accurate predictors are important for accurate predictions, and the lack of methods that can leverage a small amount of *accurate* data is a serious impediment to our predictive ability.
-In most places, our most reliable biodiversity knowledge is that of a species pool where a set of potentially interacting species in a given area could occur: through the analysis of databases like the Global Biodiversity Information Facility (GBIF) or the International Union for the Conservation of Nature (IUCN), it is possible to construct a list of species for a region of interest; however inferring the potential interactions between these species still remains a challenge.
+In this contribution, we highlight the power of viewing (and constructing) metawebs as *probabilistic* objects in the context of low-probability interactions, discuss how a family of machine learning tools (graph embeddings and transfer learning) can be used to overcome data limitations to metaweb inference, and highlight how the use of metawebs introduces important questions for the field of network ecology.
 
-Following the definition of @Dunne2006Network, a metaweb is the ecological network analogue to the species pool; specifically, it inventories all *potential* interactions between species for a spatially delimited area (and so captures the $\gamma$ diversity of interactions).
+In most places, our most reliable biodiversity knowledge is that of a species pool where a set of potentially interacting species in a given area could occur: through the analysis of databases like the Global Biodiversity Information Facility (GBIF) or the International Union for the Conservation of Nature (IUCN), it is possible to construct a list of species for a region of interest.
+Following the definition of @Dunne2006Network, a metaweb is the ecological network analogue to the species pool; specifically, it inventories all *potential* interactions between species for a spatially delimited area (and so captures the $\gamma$ diversity of interactions as per @Poisot2012Dissimilarity).
+However, inferring the potential interactions between these species still remains a challenge.
+And yet, because the metaweb represents the joint effect of functional, phylogenetic, and macroecological processes [@Morales-Castilla2015Inferring; @carlson2022; @morales-castilla2021], it holds valuable ecological information.
+Specifically, it represents the "upper bounds" on what the composition of the local networks, given a local species pool, can be [see *e.g.* @McLeod2021Sampling]; this information can help evaluate the ability of ecological assemblages to withstand the effects of, for example, climate change [@Fricke2022Effects].
+These local networks may be reconstructed given an appropriate knowledge of local species composition and provide information on the structure of networks at finer spatial scales.
+This has been done for example for tree-galler-parasitoid systems [@Gravel2018Bringing], fish trophic interactions [@Albouy2019Marine], tetrapod trophic interactions [@Braga2019Spatial; @OConnor2020Unveiling], and crop-pest networks [@Grunig2020Crop].
+
 The metaweb itself is not a prediction of local networks at specific locations within the spatial area it covers: it will have a different structure, notably by having a larger connectance [see *e.g.* @Wood2015Effects] and complexity [see *e.g.* @Galiana2022Ecological], than any of these local networks.
@@
 This sets up the core goal of predictive network ecology as the prediction of metaweb structure, as it is required to accurately produce downscaled, local predictions.
-
-Because the metaweb represents the joint effect of functional, phylogenetic, and macroecological processes [@Morales-Castilla2015Inferring], it holds valuable ecological information.
-Specifically, it represents the "upper bounds" on what the composition of the local networks, given a local species pool, can be [see *e.g.* @McLeod2021Sampling]; this information can help evaluate the ability of ecological assemblages to withstand the effects of, for example, climate change [@Fricke2022Effects].
-These local networks may be reconstructed given an appropriate knowledge of local species composition and provide information on the structure of food webs at finer spatial scales.
-This has been done for example for tree-galler-parasitoid systems [@Gravel2018Bringing], fish trophic interactions [@Albouy2019Marine], tetrapod trophic interactions [@Braga2019Spatial; @OConnor2020Unveiling], and crop-pest networks [@Grunig2020Crop].
-In this contribution, we highlight the power of viewing (and constructing) metawebs as *probabilistic* objects in the context of low-probability interactions, discuss how a family of machine learning tools (graph embeddings and transfer learning) can be used to overcome data limitations to metaweb inference, and highlight how the use of metawebs introduces important questions for the field of network ecology.
 
@@
 These considerations emphasize why metaweb predictions should focus on quantitative (preferentially probabilistic) predictions, and this should constrain the suite of models that are appropriate for prediction.
+Binary classifiers based on probabilities have an extremely robust methodology to validate them, and this applies naturally to the prediction of interactions [@poisot2023].
 
@@
 It is therefore important to separate the interactions that happen "almost surely" (repeated observational data), "almost never" (repeated lack of evidence *or* evidence that the link is forbidden through *e.g.* trait mis-match), and interactions with a probability that lays somewhere in between [@Catchen2023Missing].
+Although metawebs can (and in practice likely do) include false positives, these are statistically negligible compared to the false negatives.
+Furthermore, @Strydom2022Food shows that t-SVD embedding is extremely robust to (and able to detect) the presence of false positives.
 In a sense, that most ecological interactions are elusive can call for a slightly different approach to sampling: once the common interactions are documented, the effort required in documenting each rare interaction will increase exponentially [@Jordano2016Sampling].
@@
 
-Food webs are inherently low-dimensional objects, and can be adequately represented with less than ten dimensions [@Braga2021Phylogenetic; @Eklof2013Dimensionality; @Braga2019Spatial].
+Ecological networks are inherently low-dimensional objects, and can be adequately represented with less than ten dimensions [@Braga2021Phylogenetic; @Eklof2013Dimensionality; @Braga2019Spatial].
 Simulation results by @Botella2022Appraisal suggested that there is no dominant method to identify architectural similarities between networks: multiple approaches need to be tested and compared to the network descriptor of interest on a problem-specific basis.
 This matches previous results on graph embedding, wherein different embedding algorithms yield different network embeddings [@Goyal2018Graph], calling for a careful selection of the problem-specific approach to use.
+Additionally, @ghasemian2020 suggest that in some cases, nodes embeddings can be outperformed by other methods, re-inforcing the need to thoroughly select the appropriate data analysis technique.
 In @tbl-methods, we present a selection of common graph and node embedding methods, alongside examples of their use to predict interactions or statistical associations between species.
@@
 | Method        | Object          | Technique                        | Reference                | Application                                                                                                       |
-|-------------|-------------|-------------|-------------|--------------------|
+|---------------|---------------|---------------|---------------|---------------|
 | tSNE          | nodes           | statistical divergence           | @Hinton2002Stochastic    | [@Cieslak2020Tdistributed, species-environment responses $^a$] [@Gibb2021Data, host-virus network representation] |
@@
 This example has many parallels in ecology (see @fig-embedding **C**), in which node metadata can be represented by phylogeny, abundance, or functional traits.
-Using phylogeny as a source of information assumes (or strives to capture) the action of evolutionary processes on network structure, which at least for food webs have been well documented [@Braga2021Phylogenetic; @DallaRiva2016Exploring; @Eklof2016Phylogenetic; @Stouffer2007Evidence; @Stouffer2012Evolutionary]; similarly, the use of functional traits assumes that interactions can be inferred from the knowledge of trait-matching rules, which is similarly well supported in the empirical literature [@Bartomeus2013Understanding; @Bartomeus2016Common; @Goebel2023Body; @Gravel2013Inferring].
+Using phylogeny as a source of information assumes (or strives to capture) the action of evolutionary processes on network structure, which at least for networks have been well documented [@Braga2021Phylogenetic; @DallaRiva2016Exploring; @Eklof2016Phylogenetic; @Stouffer2007Evidence; @Stouffer2012Evolutionary]; similarly, the use of functional traits assumes that interactions can be inferred from the knowledge of trait-matching rules, which is similarly well supported in the empirical literature [@Bartomeus2013Understanding; @Bartomeus2016Common; @Goebel2023Body; @Gravel2013Inferring].
 Relating this information to an embedding rather than a list of network measures would allow to capture their effect on the more fundamental aspects of network structure; conversely, the absence of a phylogenetic or functional signal may suggest that evolutionary/trait processes are not strong drivers of network structure, therefore opening a new way to perform hypothesis testing.
@@
 Because the values returned from RDPG are not bound to the unit interval, we performed a clamping of the weights to the unit space, showing a one-inflation in documented interactions, and a zero-inflation in other species pairs.
-This last figure crosses from the statistical into the ecological, by showing that species pairs with no documented co-occurrence have weights that are not distinguishable from species pairs with no documented interactions, suggesting that (as befits a host-parasite model) the ability to interact is a strong predictor of co-occurrence.
+This last figure shows that species pairs with no documented co-occurrence have weights that are not distinguishable from species pairs with no documented interactions; in other words, looking at the embedding, species that do not co-occur are not easily distinguished from species that do not interact.
+This suggests that (as befits a host-parasite model) the ability to interact is a strong predictor of co-occurrence.
 
@@
 
-# Conclusion
+## Putting models in their context
 
@@
 For a domain as vast as species interaction networks, these biases exist at multiple scales along the way, and a challenge for prediction is not only to develop (or adopt) new quantitative tools, but to assess the behavior of these tools in the proper context.
+
+# Conclusion
+
+Although promising, the application of embeddings to metaweb prediction will require to address several challenges.
+First, there is a need to understand how to define a metaweb as a single, cohesive, unit of ecological organisation.
+This is likely to admit very different answers based on the specific taxonomic group, temporal and spatial resolution, and question being investigated.
+Second, there is a need to understand the scale at which these predictions are relevant.
+Although we have documented many cases of using embedding to fill gaps in the metaweb, these techniques can likely be brought into a spatial (and possibly temporal) context.
+The validation of these predictions will have to proceed jointly with empirical sampling of interactions, but also with the design of downsampling methods.
+Finally, there is a need for a greater understanding of how biases in the data propagate to the predictions.
+Because the volume of metawebs is currently low, and because graph embeddings have not been commonly applied, we anticipate that this discussion will take place organically in the coming years.
 

### 2023-09-02 index.qmd
wup

--- 2023-08-11 index.qmd
@@
     email: mariejosee.fortin@utoronto.ca
-  - name: Victoria Hemming
-    affiliation:
-        - ref: ubccons
-    orcid: 0000-0003-3220-6161
-    email: victoria.hemming@ubc.ca
   - name: Benjamin Mercier
@@
 within the traditional unceded territory of the Saint Lawrence Iroquoian,
-Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. TP, TS, DC,
-and LP received funding from the Canadian Institute for Ecology & Evolution. FB
+Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. We thank Victoria
+hemming for feedback on this manuscript. TP, TS, DC, and LP received funding from the Canadian Institute for Ecology & Evolution. FB
 is funded by the Institute for Data Valorization (IVADO). TS, SB, and TP are

### 2023-09-02 index.qmd

--- 2023-08-15 index.qmd
@@
 **Acknowledgements:** We acknowledge that this study was conducted on land within the traditional unceded territory of the Saint Lawrence Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations.
+We thank Victoria hemming for feedback on this manuscript.
 TP, TS, DC, and LP received funding from the Canadian Institute for Ecology & Evolution.

### 2023-09-02 index.qmd
ready

@@
 bibliography: references.bib
+abstract: |
+    - Metawebs (networks of potential interactions within a species pool) are a powerful abstraction to understand how large-scale species interaction networks are structured.
+    - Because metawebs are typically expressed at large spatial and taxonomic scales, assembling them is a tedious and costly process; predictive methods can help circumvent the limitations in data deficiencies, by providing a first approximation of metawebs."
+    - One way to improve our ability to predict metawebs is to maximize available information by using graph embeddings, as opposed to an exhaustive list of species interactions.
+Graph embedding is an emerging field in machine learning that holds great potential for ecological problems.
+    - Here, we outline how the challenges associated with inferring metawebs line-up with the advantages of graph embeddings; followed by a discussion as to how the choice of the species pool has consequences on the reconstructed network, specifically as to the role of human-made (or arbitrarily assigned) boundaries and how these may influence ecological hypotheses.
 ---
 
-The ability to infer *potential* interactions could serve as a significant breakthrough in our ability to conceptualize species interaction networks over large spatial scales [@Hortal2015Seven].
+The ability to infer potential biotic interactions could serve as a significant breakthrough in our ability to conceptualize networks over large spatial scales [@Hortal2015Seven].
 Reliable inferences would not only boost our understanding of the structure of species interaction networks, but also increase the amount of information that can be used for biodiversity management.
@@
 First, there is a relative scarcity of relevant data in most places globally -- which, due to the limitations in most predictive methods, restricts the ability to infer interactions to locations where it is least required (*i.e.* regions where we already have interaction data) leaving us unable to make inference in data scarce regions (where we most need it); second, accurate predictors are important for accurate predictions, and the lack of methods that can leverage a small amount of *accurate* data is a serious impediment to our predictive ability.
-In this contribution, we highlight the power of viewing (and constructing) metawebs as *probabilistic* objects in the context of low-probability interactions, discuss how a family of machine learning tools (graph embeddings and transfer learning) can be used to overcome data limitations to metaweb inference, and highlight how the use of metawebs introduces important questions for the field of network ecology.
+In this contribution, we (i) highlight the power of viewing (and constructing) metawebs as *probabilistic* objects in the context of low-probability interactions, (ii) discuss how a family of machine learning tools (graph embeddings and transfer learning) can be used to overcome data limitations to metaweb inference, and (iii) highlight how the use of metawebs introduces important questions for the field of network ecology.
 
@@
 However, inferring the potential interactions between these species still remains a challenge.
-And yet, because the metaweb represents the joint effect of functional, phylogenetic, and macroecological processes [@Morales-Castilla2015Inferring; @carlson2022; @morales-castilla2021], it holds valuable ecological information.
+And yet, the metaweb holds valuable ecological information: it represents the joint effect of functional, phylogenetic, and macroecological processes [@Morales-Castilla2015Inferring; @carlson2022; @morales-castilla2021].
 Specifically, it represents the "upper bounds" on what the composition of the local networks, given a local species pool, can be [see *e.g.* @McLeod2021Sampling]; this information can help evaluate the ability of ecological assemblages to withstand the effects of, for example, climate change [@Fricke2022Effects].
 These local networks may be reconstructed given an appropriate knowledge of local species composition and provide information on the structure of networks at finer spatial scales.
-This has been done for example for tree-galler-parasitoid systems [@Gravel2018Bringing], fish trophic interactions [@Albouy2019Marine], tetrapod trophic interactions [@Braga2019Spatial; @OConnor2020Unveiling], and crop-pest networks [@Grunig2020Crop].
+This has been done for example for tree-galler-parasitoid systems [@Gravel2018Bringing], fish trophic interactions [@Albouy2019Marine], terrestrial tetrapod trophic interactions [@Braga2019Spatial; @OConnor2020Unveiling], and crop-pest networks [@Grunig2020Crop].
 
 The metaweb itself is not a prediction of local networks at specific locations within the spatial area it covers: it will have a different structure, notably by having a larger connectance [see *e.g.* @Wood2015Effects] and complexity [see *e.g.* @Galiana2022Ecological], than any of these local networks.
-These local networks (which capture the $\alpha$ diversity of interactions) are a subset of the metaweb's species and its realized interactions, and have been called "metaweb realizations" [@Poisot2015Species].
+Local networks (which capture the $\alpha$ diversity of interactions) are a subset of the metaweb's species and its realized interactions, and have been called "metaweb realizations" [@Poisot2015Species].
 Differences between local networks and their metawebs are due to chance, species abundance and co-occurrence, local environmental conditions, and local distribution of functional traits, among others.
@@
 This argument echoes @Jordano2016Sampling: sampling ecological interactions is difficult because it requires first the joint observation of two species, and then the observation of their interaction.
-In addition, it is generally expected that weak or rare interactions will be more prevalent in networks than common or strong interactions [@Csermely2004Strong], compared to strong, persistent interactions; this is notably the case in food chains, wherein many weaker interactions are key to the stability of a system [@Neutel2002Stability].
+In addition, it is generally expected that weak or rare interactions will be more prevalent in networks than common or strong interactions [@Csermely2004Strong]; this is notably the case in food chains, wherein many weaker interactions are key to the stability of a system [@Neutel2002Stability].
 In the light of these observations, we expect to see an over-representation of low-probability (hereafter rare) interactions under a model that accurately predicts interaction probabilities.
@@
 The inherent plasticity of interactions is important to capture: there have been documented instances of food webs undergoing rapid collapse/recovery cycles over short periods of time [*e.g.* @Pedersen2017Signatures].
-Furthermore, because the structure of the metaweb cannot be known in advance, it is important to rely on predictive tools that do not assume a specific network topology for link prediction [@Gaucher2021Outlier], but are able to work on generalizations of the network.
+Furthermore, because the structure of the metaweb cannot be known in advance, it is important to rely on predictive tools that do not assume a specific network topology for link prediction [@Gaucher2021Outlier], but are able to work on generalizations of the network that capture statistical processes giving it its structure.
 These considerations emphasize why metaweb predictions should focus on quantitative (preferentially probabilistic) predictions, and this should constrain the suite of models that are appropriate for prediction.
@@
 Furthermore, @Strydom2022Food shows that t-SVD embedding is extremely robust to (and able to detect) the presence of false positives.
-In a sense, that most ecological interactions are elusive can call for a slightly different approach to sampling: once the common interactions are documented, the effort required in documenting each rare interaction will increase exponentially [@Jordano2016Sampling].
+In a sense, because most ecological interactions are elusive, we should consider the direct consequences this has on sampling: once the common interactions are documented, the effort required in documenting each rare interaction will increase exponentially [@Jordano2016Sampling].
 Recent proposals in other fields relying on machine learning approaches emphasize the idea that algorithms meant to predict, through the assumption that they approximate the process generating the data, can also act as data generators [@Hoffmann2019Machine].
@@
 ![The embedding process (**A**) can help to identify links (interactions) that may have been missed within the original community (represented by the orange dashed arrows, **B**).
-Transfer learning (**D**) allows for the prediction links (interactions) even when novel species (**C**) are included alongside the original community.
-This is achieved by learning using other relevant predictors (*e.g.* traits) in conjunction with the known interactions to infer latent values (**E**).
+Transfer learning (**D**) allows for the prediction of links (interactions) even when novel species (**C**) are included alongside the original community.
+This is achieved with other ecologically relevant predictors (*e.g.* traits) in conjunction with the known interactions to infer latent values (**E**).
 Ultimately this allows us to predict links (interactions) for species external from the original sample (blue dashed arrows) as well as missing within sample links (**F**).
-Within this context the predicted (and original) networks as well as the ecological predictors used (green boxes) are products that can be quantified through measurements in the field, whereas the embedded as well as imputed matrices (purple box) are representative of a decomposition of the interaction matrices onto the embedding space](figures/conceptual_2.png){#fig-embedding}
+Within this context the predicted (and original) networks as well as the ecological predictors used (green boxes) are products that can be quantified through measurements in the field, whereas the embedded as well as imputed matrices (purple box) are representative of a decomposition of the interaction matrices onto the embedding space]
+
+  [The embedding process (**A**) can help to identify links (interactions) that may have been missed within the original community (represented by the orange dashed arrows, **B**).
+Transfer learning (**D**) allows for the prediction of links (interactions) even when novel species (**C**) are included alongside the original community.
+This is achieved with other ecologically relevant predictors (*e.g.* traits) in conjunction with the known interactions to infer latent values (**E**).
+Ultimately this allows us to predict links (interactions) for species external from the original sample (blue dashed arrows) as well as missing within sample links (**F**).
+Within this context the predicted (and original) networks as well as the ecological predictors used (green boxes) are products that can be quantified through measurements in the field, whereas the embedded as well as imputed matrices (purple box) are representative of a decomposition of the interaction matrices onto the embedding space]: figures/conceptual_2.png {#fig-embedding}
 
@@
 |---------------|---------------|---------------|---------------|---------------|
-| tSNE          | nodes           | statistical divergence           | @Hinton2002Stochastic    | [@Cieslak2020Tdistributed, species-environment responses $^a$] [@Gibb2021Data, host-virus network representation] |
+| t-SNE         | nodes           | statistical divergence           | @Hinton2002Stochastic    | [@Cieslak2020Tdistributed, species-environment responses $^a$] [@Gibb2021Data, host-virus network representation] |
 | LINE          | nodes           | stochastic gradient descent      | @Tang2015Line            |                                                                                                                   |
@@
 $^a$: application is concerned with *statistical* interactions, which are not necessarilly direct biotic interactions; $^b$:application is concerned with joint-SDM-like approach, which is also very close to statistical associations as opposed to direct biotic interactions.
-Given the need to evaluate different methods on a problem-specific basis, the fact that a lot of methods have not been used on network problems is an opportunity for benchmarking and method development.
+Given the need to evaluate different methods on a problem-specific basis, the fact that many methods have not been used on network problems is an opportunity for benchmarking and method development.
 Note that the row for PCA also applies to kernel/probabilistic PCA, which are variations on the more general method of SVD.
-Note further that tSNE has been included because it is frequently used to embed graphs, including of species associations/interactions, despite not being strictly speaking, a graph embedding technique [see *e.g.* @Chami2022Machine].
+Note further that t-SNE has been included because it is frequently used to embed graphs, including of species associations/interactions, despite not being strictly speaking, a graph embedding technique [see *e.g.* @Chami2022Machine].
 {#tbl-methods}
@@
 In panel **B**, we show the increase in cumulative variance explained at each rank, and visualize that using 39 ranks explains about 70% of the variance in the empirical metaweb.
-This is a different information from the $L_2$ loss (which is averaged across interactions), as it works on the eigenvalues of the embedding, and therefore captures higher-level features of the network.
+This provides different information from the $L_2$ loss (which is averaged across interactions), as it works on the eigenvalues of the embedding, and therefore captures higher-level features of the network.
 In panel **C**, we show positions of hosts and parasites on the first two dimensions of the left and right subspaces.
@@
 Because the values returned from RDPG are not bound to the unit interval, we performed a clamping of the weights to the unit space, showing a one-inflation in documented interactions, and a zero-inflation in other species pairs.
-This last figure shows that species pairs with no documented co-occurrence have weights that are not distinguishable from species pairs with no documented interactions; in other words, looking at the embedding, species that do not co-occur are not easily distinguished from species that do not interact.
+Panel **D** specifically shows that species pairs with no documented co-occurrence have weights that are not distinguishable from species pairs with no documented interactions; in other words, looking at the embedding, species that do not co-occur are not easily distinguished from species that do not interact.
 This suggests that (as befits a host-parasite model) the ability to interact is a strong predictor of co-occurrence.
@@
 
-The results of @fig-illustration-1 show that we can extract an embedding of the metaweb that captures enough variance to be relevant; specifically, this is true for both $L_2$ loss (indicating that RDPG is able to capture pairwise processes) and the cumulative variance explained (indicating that RDPG is able to capture network-level structure).
-Therefore, in @fig-illustration-2, we relate the values of latent variables for hosts to different ecologically-relevant data.
+In @fig-illustration-2, we relate the values of latent variables for hosts to different ecologically-relevant data; we can perform this additional step, because the results presented in @fig-illustration-1 show that we can extract an embedding of the metaweb that captures enough variance to be relevant.
+Importantly, this is true for both $L_2$ loss (indicating that RDPG is able to capture pairwise processes) and the cumulative variance explained (indicating that RDPG is able to capture network-level structure), which suggests that these approaches may allow to predict interactions *and* network structure.
 In panel **A**, we show that host with a higher value on the first dimension have fewer parasites.
@@
 But as @Herbert1965Dune rightfully pointed out, "\[y\]ou can't draw neat lines around planet-wide problems"; any inference of a metaweb must therefore contend with several novel, interwoven, families of problems.
-In this section, we outline three that we think are particularly important, and can discuss how they may addressed with subsequent data analysis or simulations, and how they emerge in the specific context of using embeddings; some of these issues are related to the application of these methods at the science-policy interface.
+In this section, we outline three that we think are particularly important, and discuss how they may be addressed with subsequent data analysis or simulations, and how they emerge in the specific context of using embeddings; some of these issues are related to the application of these methods at the science-policy interface.
 Adressing these considerations as part of the methodological discussion is particularly important, as the construction of metawebs can perpetuate legacies of biases in data (Box 2).
@@
 
-If the initial metaweb is too narrow in scope, notably from a taxonomic point of view, the chances of finding another area with enough related species (through phylogenetic relatedness or similarity of functional traits) to make a reliable inference decreases.
+If the initial metaweb is too narrow in scope, notably from a taxonomic point of view, the chances decrease of finding another area with enough related species (through phylogenetic relatedness or similarity of functional traits) to make a reliable inference.
 This is because transfer requires similarity (@fig-embedding).
@@
 Our discussion of these approaches need to go beyond the technical and statistical, and into the governance consequences they can have.
-To embed data also embeds historical and contemporary biases that acted on these data, both because they shaped the ecological processes generating them, and the global processes leading to their measurement and publication.
+To embed data also embeds historical and contemporary biases that acted on these data, both because they shaped the ecological processes generating them (see Box 2), and the global processes leading to their measurement and publication.
 For a domain as vast as species interaction networks, these biases exist at multiple scales along the way, and a challenge for prediction is not only to develop (or adopt) new quantitative tools, but to assess the behavior of these tools in the proper context.
@@
 
-Although promising, the application of embeddings to metaweb prediction will require to address several challenges.
+Although promising, the application of embeddings to metaweb prediction still involved several challenges.
 First, there is a need to understand how to define a metaweb as a single, cohesive, unit of ecological organisation.
-This is likely to admit very different answers based on the specific taxonomic group, temporal and spatial resolution, and question being investigated.
+This is likely to have very different answers based on the specific taxonomic group, temporal and spatial resolution, and question being investigated.
 Second, there is a need to understand the scale at which these predictions are relevant.
@@
 
-In large parts of the world, boundaries that delineate geographic regions are merely a reflection the legacy of settler colonialism, which drives global disparity in capacity to collect and publish ecological data.
+In large parts of the world, boundaries that delineate geographic regions are a legacy of settler colonialism, which drives global disparity in capacity to collect and publish ecological data.
 Applying any embedding to biased data does not debias them, but rather embeds these biases, propagating them to the models using embeddings to make predictions.
@@
 Long-term colonial legacies still shape taxonomic composition to this day [@Lenzner2022Naturalized; @Raja2022Colonialism], and much shorter-term changes in taxonomic and genetic richness of wildlife emerged through environmental racism [@Schmidt2022Systemic].
-Thus, the set of species found at a specific location is not only as the result of a response to ecological processes separate from human influence, but also the result of human-environment interaction as well as the result legislative/political histories.
+Thus, the set of species found at a specific location is not only as the result of a response to ecological processes separate from human influence, but also the result of human-environment interaction as well as the results of legislative/political histories.
 :::
@@
 TS, SB, and TP are funded by a donation from the Courtois Foundation.
-CB was awarded a Mitacs Elevate Fellowship no.
-IT12391, in partnership with fRI Research, and also acknowledges funding from Alberta Innovates and the Forest Resources Improvement Association of Alberta.
 M-JF acknowledges funding from NSERC Discovery Grant and NSERC CRC.
@@
 
-**Authors' contributions:** TS, and TP conceived the ideas discussed in the manuscript. All authors contributed to writing and editing the manuscript.
+**Authors' contributions:** TS and TP conceived the ideas discussed in the manuscript. All authors contributed to writing and editing the manuscript.
 
-**Data availability:** There is no data associated with this manuscript.
+**Data availability:** The code to collect the data use in figures is distributed as part of the Supplementary Material.
 

### 2023-09-07 docs/_tex/index.tex
things

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Graph embedding and transfer learning can help predict potential species interaction networks despite data limitations},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Graph embedding and transfer learning can help predict potential
species interaction networks despite data limitations}
\author{Tanya Strydom \and Salomé Bouskila \and Francis
Banville \and Ceres Barros \and Dominique Caron \and Maxwell J.
Farrell \and Marie-Josée Fortin \and Victoria Hemming \and Benjamin
Mercier \and Laura J. Pollock \and Rogini Runghen \and Giulio V. Dalla
Riva \and Timothée Poisot}
\date{}

\begin{document}
\maketitle
The ability to infer \emph{potential} interactions could serve as a
significant breakthrough in our ability to conceptualize species
interaction networks over large spatial scales (Hortal et al. 2015).
Reliable inferences would not only boost our understanding of the
structure of species interaction networks, but also increase the amount
of information that can be used for biodiversity management. In a recent
overview of the field of ecological network prediction, Strydom et al.
(2021) identified two challenges of interest to the prediction of
interactions at large scales. First, there is a relative scarcity of
relevant data in most places globally -- which, due to the limitations
in most predictive methods, restricts the ability to infer interactions
to locations where it is least required (\emph{i.e.} regions where we
already have interaction data) leaving us unable to make inference in
data scarce regions (where we most need it); second, accurate predictors
are important for accurate predictions, and the lack of methods that can
leverage a small amount of \emph{accurate} data is a serious impediment
to our predictive ability. In this contribution, we highlight the power
of viewing (and constructing) metawebs as \emph{probabilistic} objects
in the context of low-probability interactions, discuss how a family of
machine learning tools (graph embeddings and transfer learning) can be
used to overcome data limitations to metaweb inference, and highlight
how the use of metawebs introduces important questions for the field of
network ecology.

In most places, our most reliable biodiversity knowledge is that of a
species pool where a set of potentially interacting species in a given
area could occur: through the analysis of databases like the Global
Biodiversity Information Facility (GBIF) or the International Union for
the Conservation of Nature (IUCN), it is possible to construct a list of
species for a region of interest. Following the definition of Dunne
(2006), a metaweb is the ecological network analogue to the species
pool; specifically, it inventories all \emph{potential} interactions
between species for a spatially delimited area (and so captures the
\(\gamma\) diversity of interactions as per Poisot et al. (2012)).
However, inferring the potential interactions between these species
still remains a challenge. And yet, because the metaweb represents the
joint effect of functional, phylogenetic, and macroecological processes
(Morales-Castilla et al. 2015; Carlson et al. 2022; Morales-Castilla et
al. 2021), it holds valuable ecological information. Specifically, it
represents the ``upper bounds'' on what the composition of the local
networks, given a local species pool, can be (see \emph{e.g.} McLeod et
al. 2021); this information can help evaluate the ability of ecological
assemblages to withstand the effects of, for example, climate change
(Fricke et al. 2022). These local networks may be reconstructed given an
appropriate knowledge of local species composition and provide
information on the structure of networks at finer spatial scales. This
has been done for example for tree-galler-parasitoid systems (Gravel et
al. 2018), fish trophic interactions (Albouy et al. 2019), tetrapod
trophic interactions (J. Braga et al. 2019; O'Connor et al. 2020), and
crop-pest networks (Grünig et al. 2020).

The metaweb itself is not a prediction of local networks at specific
locations within the spatial area it covers: it will have a different
structure, notably by having a larger connectance (see \emph{e.g.} Wood
et al. 2015) and complexity (see \emph{e.g.} Galiana et al. 2022), than
any of these local networks. These local networks (which capture the
\(\alpha\) diversity of interactions) are a subset of the metaweb's
species and its realized interactions, and have been called ``metaweb
realizations'' (Poisot, Stouffer, and Gravel 2015). Differences between
local networks and their metawebs are due to chance, species abundance
and co-occurrence, local environmental conditions, and local
distribution of functional traits, among others. Specifically, although
co-occurrence can be driven by interactions (Cazelles et al. 2016),
co-occurrence alone is not a predictor of interactions (Blanchet,
Cazelles, and Gravel 2020; Thurman et al. 2019), and therefore the lack
of co-occurrence cannot be used to infer the lack of a feasible
interaction. Yet, recent results by Saravia et al. (2021) strongly
suggested that local (metaweb) realizations only respond weakly to local
conditions: instead, they reflect constraints inherited by the structure
of their metaweb. This sets up the core goal of predictive network
ecology as the prediction of metaweb structure, as it is required to
accurately produce downscaled, local predictions.

\hypertarget{a-metaweb-is-an-inherently-probabilistic-object}{%
\section{A metaweb is an inherently probabilistic
object}\label{a-metaweb-is-an-inherently-probabilistic-object}}

Treating interactions as probabilistic (as opposed to binary) events is
a more nuanced and realistic way to represent them. Dallas, Park, and
Drake (2017) suggested that most interactions (links) in ecological
networks are cryptic, \emph{i.e.} uncommon or hard to observe. This
argument echoes Jordano (2016): sampling ecological interactions is
difficult because it requires first the joint observation of two
species, and then the observation of their interaction. In addition, it
is generally expected that weak or rare interactions will be more
prevalent in networks than common or strong interactions (Csermely
2004), compared to strong, persistent interactions; this is notably the
case in food chains, wherein many weaker interactions are key to the
stability of a system (Neutel, Heesterbeek, and de Ruiter 2002). In the
light of these observations, we expect to see an over-representation of
low-probability (hereafter rare) interactions under a model that
accurately predicts interaction probabilities.

Yet, the original metaweb definition, and indeed most past uses of
metawebs, was based on the presence/absence of interactions. Moving
towards \emph{probabilistic} metawebs, by representing interactions as
Bernoulli events (see \emph{e.g.} Poisot et al. 2016), offers the
opportunity to weigh these rare interactions appropriately. The inherent
plasticity of interactions is important to capture: there have been
documented instances of food webs undergoing rapid collapse/recovery
cycles over short periods of time (\emph{e.g.} Pedersen et al. 2017).
Furthermore, because the structure of the metaweb cannot be known in
advance, it is important to rely on predictive tools that do not assume
a specific network topology for link prediction (Gaucher, Klopp, and
Robin 2021), but are able to work on generalizations of the network.
These considerations emphasize why metaweb predictions should focus on
quantitative (preferentially probabilistic) predictions, and this should
constrain the suite of models that are appropriate for prediction.
Binary classifiers based on probabilities have an extremely robust
methodology to validate them, and this applies naturally to the
prediction of interactions (Poisot 2023).

It is important to recall that a metaweb is intended as a catalogue of
all potential (feasible) interactions, which is then filtered for a
given application (Morales-Castilla et al. 2015). It is therefore
important to separate the interactions that happen ``almost surely''
(repeated observational data), ``almost never'' (repeated lack of
evidence \emph{or} evidence that the link is forbidden through
\emph{e.g.} trait mis-match), and interactions with a probability that
lays somewhere in between (Catchen et al. 2023). Although metawebs can
(and in practice likely do) include false positives, these are
statistically negligible compared to the false negatives. Furthermore,
Strydom et al. (2022) shows that t-SVD embedding is extremely robust to
(and able to detect) the presence of false positives. In a sense, that
most ecological interactions are elusive can call for a slightly
different approach to sampling: once the common interactions are
documented, the effort required in documenting each rare interaction
will increase exponentially (Jordano 2016). Recent proposals in other
fields relying on machine learning approaches emphasize the idea that
algorithms meant to predict, through the assumption that they
approximate the process generating the data, can also act as data
generators (Hoffmann et al. 2019). High quality observational data can
be used to infer core rules underpinning network structure, and be
supplemented with synthetic data coming from predictive models trained
on them, thereby increasing the volume of information available for
analysis. Indeed, Strydom et al. (2021) suggested that knowing the
metaweb may render the prediction of local networks easier, because it
fixes an ``upper bound'' on which interactions can exist. In this
context, a probabilistic metaweb represents an aggregation of
informative priors on the biological feasibility of interactions, which
is usually hard to obtain yet has possibly the most potential to boost
our predictive ability of local networks (Bartomeus 2013; Bartomeus et
al. 2016). This would represent a departure from simple rules expressed
at the network scale (\emph{e.g.} Williams and Martinez 2000) to a view
of network prediction based on learning the rules that underpin
interactions \emph{and} their variability (Anubhav Gupta, Furrer, and
Petchey 2022).

\begin{figure}

{\centering \includegraphics{figures/conceptual_2.png}

}

\caption{\label{fig-embedding}The embedding process (\textbf{A}) can
help to identify links (interactions) that may have been missed within
the original community (represented by the orange dashed arrows,
\textbf{B}). Transfer learning (\textbf{D}) allows for the prediction
links (interactions) even when novel species (\textbf{C}) are included
alongside the original community. This is achieved by learning using
other relevant predictors (\emph{e.g.} traits) in conjunction with the
known interactions to infer latent values (\textbf{E}). Ultimately this
allows us to predict links (interactions) for species external from the
original sample (blue dashed arrows) as well as missing within sample
links (\textbf{F}). Within this context the predicted (and original)
networks as well as the ecological predictors used (green boxes) are
products that can be quantified through measurements in the field,
whereas the embedded as well as imputed matrices (purple box) are
representative of a decomposition of the interaction matrices onto the
embedding space}

\end{figure}

\hypertarget{graph-embedding-offers-promises-for-the-inference-of-potential-interactions}{%
\section{Graph embedding offers promises for the inference of potential
interactions}\label{graph-embedding-offers-promises-for-the-inference-of-potential-interactions}}

Graph (or network) embedding (Figure~\ref{fig-embedding}) is a family of
machine learning techniques, whose main task is to learn a mapping
function from a discrete graph to a continuous domain (Arsov and Mirceva
2019; Chami et al. 2022). Their main goal is to learn a low dimensional
vector representation of the graph (embeddings), such that its key
properties (\emph{e.g.} local or global structures) are retained in the
embedding space (Yan et al. 2005). The embedding space may, but will not
necessarily, have lower dimensionality than the graph. Ecological
networks are promising candidates for the routine application of
embeddings, as they tend to possess a shared structural backbone (see
\emph{e.g.} Bramon Mora et al. 2018), which hints at structural
invariants in empirical data. Assuming that these structural invariants
are common enough, they would dominate the structure of networks, and
therefore be adequately captured by the first (lower) dimensions of an
embedding, without the need to measure derived aspects of their
structure (\emph{e.g.} motifs, paths, modularity, \ldots).

\hypertarget{graph-embedding-produces-latent-variables-but-not-traits}{%
\subsection{Graph embedding produces latent variables (but not
traits)}\label{graph-embedding-produces-latent-variables-but-not-traits}}

Before moving further, it is important to clarify the epistemic status
of node values derived from embeddings: specifically, they are
\emph{not} functional traits, and therefore should not be interpreted in
terms of effects or responses. As per the framework of Malaterre et al.
(2019), these values neither derive from, nor result in, changes in
organismal performance, and should therefore not be used to quantify
\emph{e.g.} functional diversity. This holds true even when there are
correlations between latent values and functional traits: although these
enable an ecological discussion of how traits condition the structure of
the network, the existence of a statistical relationship does not
elevate the latent values to the status of functional traits.

Rather than directly predicting biological rules (see \emph{e.g.}
Pichler et al. 2020 for an overview), which may be confounded by the
sparse nature of graph data, learning embeddings works in the
low-dimensional space that maximizes information about the network
structure. This approach is further justified by the observation, for
example, that the macro-evolutionary history of a network is adequately
represented by some graph embeddings {[}Random dot product graphs
(RDPG); see Dalla Riva and Stouffer (2016){]}. In a recent publication,
Strydom et al. (2022) have used an embedding (based on RDPG) to project
a metaweb of trophic interactions between European mammals, and
transferred this information to mammals of Canada, using the
phylogenetic distance between related clades to infer the values in the
latent subspace into which the European metaweb was projected. By
performing the RDPG step on re-constructed values, this approach yields
a probabilistic trophic metaweb for mammals of Canada based on knowledge
of European species, despite a limited (\(\approx\) 5\%) taxonomic
overlap, and illustrates how the values derived from an embedding can be
used for prediction without being ``traits'' of the species they
represent.

\hypertarget{ecological-networks-are-good-candidates-for-embedding}{%
\subsection{Ecological networks are good candidates for
embedding}\label{ecological-networks-are-good-candidates-for-embedding}}

Ecological networks are inherently low-dimensional objects, and can be
adequately represented with less than ten dimensions (M. P. Braga et al.
2021; Eklöf et al. 2013; J. Braga et al. 2019). Simulation results by
Botella et al. (2022) suggested that there is no dominant method to
identify architectural similarities between networks: multiple
approaches need to be tested and compared to the network descriptor of
interest on a problem-specific basis. This matches previous results on
graph embedding, wherein different embedding algorithms yield different
network embeddings (Goyal and Ferrara 2018), calling for a careful
selection of the problem-specific approach to use. Additionally,
Ghasemian et al. (2020) suggest that in some cases, nodes embeddings can
be outperformed by other methods, re-inforcing the need to thoroughly
select the appropriate data analysis technique. In
Table~\ref{tbl-methods}, we present a selection of common graph and node
embedding methods, alongside examples of their use to predict
interactions or statistical associations between species. These methods
rely largely on linear algebra or pseudo-random walks on graphs. All
forms of embeddings presented in Table~\ref{tbl-methods} share the
common property of summarizing their objects into (sets of) dense
feature vectors, that capture the overall network structure, pairwise
information on nodes, and emergent aspects of the network, in a
compressed way (\emph{i.e.} with some information loss, as we later
discuss in the illustration). Node embeddings tend to focus on
maintaining pairwise relationships (\emph{i.e.} species interactions),
while graph embeddings focus on maintaining the network structure
(\emph{i.e.} emergent properties). Nevertheless, some graph embedding
techniques (like RDPG, see \emph{e.g.} Wu, Palmer, and Deford 2021) will
provide high-quality node-level embeddings while also preserving network
structure.

\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Box 1 - Graph Neural Networks}, colback=white, rightrule=.15mm, coltitle=black, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0, breakable, bottomtitle=1mm, titlerule=0mm, toptitle=1mm, arc=.35mm, toprule=.15mm, leftrule=.75mm, left=2mm, opacitybacktitle=0.6]

One prominent family of approaches we do not discuss in the present
manuscript is Graph Neural Networks {[}GNN; Zhou et al. (2020){]}. GNN
are, in a sense, a method to embed a graph into a dense subspace, but
belong to the family of deep learning methods, which has its own set of
practices (see \emph{e.g.} Goodfellow, Bengio, and Courville 2016). An
important issue with methods based on deep learning is that, because
their parameter space is immense, the sample size of the data fed into
them must be similarly large (typically thousands of instances). This is
a requirement for the model to converge correctly during training, but
this assumption is unlikely to be met given the size of datasets
currently available for metawebs (or single time/location species
interaction networks). This data volume requirement is mostly absent
from the techniques we list below. Furthermore, GNN still have some
challenges related to their shallow structure, and concerns related to
scalability (see Atika Gupta, Matta, and Pant 2021 for a review), which
are mostly absent from the methods listed in Table~\ref{tbl-methods}.
Assuming that the uptake of next-generation biomonitoring techniques
does indeed deliver larger datasets on species interactions (Bohan et
al. 2017), there is nevertheless the potential for GNN to become an
applicable embedding/predictive technique in the coming years.

\end{tcolorbox}

Graph embeddings \emph{can} serve as a dimensionality reduction method.
For example, RDPG (Strydom et al. 2022) and t-SVD {[}truncated Singular
Value Decomposition; Poisot et al. (2021){]} typically embed networks
using fewer dimensions than the original network {[}the original network
has as many dimensions as species, and as many informative dimensions as
trophically unique species; Strydom, Dalla Riva, and Poisot (2021){]}.
However, this is not necessarily the case -- indeed, one may perform a
PCA (a special case of SVD) to project the raw data into a subspace that
improves the efficacy of t-SNE {[}t-distributed stochastic neighbor
embedding; Maaten (2009){]}. There are many dimensionality reductions
(Anowar, Sadaoui, and Selim 2021) that can be applied to an embedded
network should the need for dimensionality reduction (for example for
data visualization) arise. In brief, many graph embeddings \emph{can}
serve as dimensionality reduction steps, but not all do, neither do all
dimensionality reduction methods provide adequate graph embedding
capacities. In the next section (and Figure~\ref{fig-embedding}), we
show how the amount of dimensionality reduction can affect the quality
of the embedding.

\hypertarget{tbl-methods}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}@{}}
\caption{\label{tbl-methods}Overview of some common graph embedding
approaches, by type of embedded objects, alongside examples of their use
in the prediction of species interactions. These methods have not yet
been routinely used to predict species interactions; most examples that
we identified were either statistical associations, or analogues to
joint species distribution models. \(^a\): application is concerned with
\emph{statistical} interactions, which are not necessarilly direct
biotic interactions; \(^b\):application is concerned with joint-SDM-like
approach, which is also very close to statistical associations as
opposed to direct biotic interactions. Given the need to evaluate
different methods on a problem-specific basis, the fact that a lot of
methods have not been used on network problems is an opportunity for
benchmarking and method development. Note that the row for PCA also
applies to kernel/probabilistic PCA, which are variations on the more
general method of SVD. Note further that tSNE has been included because
it is frequently used to embed graphs, including of species
associations/interactions, despite not being strictly speaking, a graph
embedding technique (see \emph{e.g.} Chami et al. 2022).}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Method
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Object
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Technique
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reference
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Application
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Method
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Object
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Technique
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reference
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Application
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
tSNE & nodes & statistical divergence & Hinton and Roweis (2002) &
(Cieslak et al. 2020, species-environment responses \(^a\)) (Gibb et al.
2021, host-virus network representation) \\
LINE & nodes & stochastic gradient descent & Tang et al. (2015) & \\
SDNE & nodes & gradient descent & D. Wang, Cui, and Zhu (2016) & \\
node2vec & nodes & stochastic gradient descent & Grover and Leskovec
(2016) & \\
HARP & nodes & meta-strategy & H. Chen et al. (2017) & \\
DMSE & joint nodes & deep neural network & D. Chen et al. (2017) & (D.
Chen et al. 2017, species-environment interactions \(^b\)) \\
graph2vec & sub-graph & skipgram network & Narayanan et al. (2017) & \\
RDPG & graph & SVD & Young and Scheinerman (2007) & (Dalla Riva and
Stouffer 2016, trophic interactions) (Poisot et al. 2021, host-virus
network prediction) \\
GLEE & graph & Laplacian eigenmap & Torres, Chan, and Eliassi-Rad (2020)
& \\
DeepWalk & graph & stochastic gradient descent & Perozzi, Al-Rfou, and
Skiena (2014) & (Wardeh, Baylis, and Blagrove 2021, host-virus
interactions) \\
GraphKKE & graph & stochastic differential equation & Melnyk et al.
(2020) & (Melnyk et al. 2020, microbiome species associations \(^a\)) \\
FastEmbed & graph & eigen decomposition & Ramasamy and Madhow (2015)
& \\
PCA & graph & eigen decomposition & Surendran (2013) & (Strydom et al.
2021, host-parasite interactions) \\
Joint methods & multiple graphs & multiple strategies & S. Wang et al.
(2021) & \\
\end{longtable}

The popularity of graph embedding techniques in machine learning is more
than the search for structural invariants: graphs are discrete objects,
and machine learning techniques tend to handle continuous data better.
Bringing a sparse graph into a continuous, dense vector space (Xu 2021)
opens up a broader variety of predictive algorithms, notably of the sort
that are able to predict events as probabilities (Murphy 2022).
Furthermore, the projection of the graph itself is a representation that
can be learned; Runghen, Stouffer, and Dalla Riva (2021), for example,
used a neural network to learn the embedding of a network in which not
all interactions were known, based on the nodes' metadata. This example
has many parallels in ecology (see Figure~\ref{fig-embedding}
\textbf{C}), in which node metadata can be represented by phylogeny,
abundance, or functional traits. Using phylogeny as a source of
information assumes (or strives to capture) the action of evolutionary
processes on network structure, which at least for networks have been
well documented (M. P. Braga et al. 2021; Dalla Riva and Stouffer 2016;
Eklöf and Stouffer 2016; D. B. Stouffer et al. 2007; D. B. Stouffer et
al. 2012); similarly, the use of functional traits assumes that
interactions can be inferred from the knowledge of trait-matching rules,
which is similarly well supported in the empirical literature (Bartomeus
2013; Bartomeus et al. 2016; Goebel et al. 2023; Gravel et al. 2013).
Relating this information to an embedding rather than a list of network
measures would allow to capture their effect on the more fundamental
aspects of network structure; conversely, the absence of a phylogenetic
or functional signal may suggest that evolutionary/trait processes are
not strong drivers of network structure, therefore opening a new way to
perform hypothesis testing.

\hypertarget{an-illustration-of-metaweb-embedding}{%
\section{An illustration of metaweb
embedding}\label{an-illustration-of-metaweb-embedding}}

In this section, we illustrate the embedding of a collection of
bipartite networks collected by Hadfield et al. (2014), using t-SVD and
RDPG. Briefly, an RDPG decomposes a network into two subspaces (left and
right), which are matrices that when multiplied give an approximation of
the original network. RDPG has the particularly desirable properties of
being a graph embedding technique that produces relevant node-level
feature vectors, and provides good approximations of graphs with varied
structures (Athreya et al. 2017). The code to reproduce this example is
available as supplementary material (note, for the sake of comparison,
that Strydom et al. 2021 have an example using embedding through PCA
followed by prediction using a deep neural network on the same dataset).
The resulting (binary) metaweb \(\mathcal{M}\) has 2131 interactions
between 206 parasites and 121 hosts, and its adjacency matrix has full
rank (\emph{i.e.} it represents a space with 121 dimensions). All
analyses were done using Julia (Bezanson et al. 2017) version 1.7.2,
\emph{Makie.jl} (Danisch and Krumbiegel 2021), and
\emph{EcologicalNetworks.jl} (Poisot et al. 2019).

\begin{figure}[H]

{\centering \includegraphics{index_files/figure-latex/fig-illustration-1-output-1.png}

}

\caption{\label{fig-illustration-1}Validation of an embedding for a
host-parasite metaweb, using Random Dot Product Graphs. \textbf{A},
decrease in approximation error as the number of dimensions in the
subspaces increases. \textbf{B}, increase in cumulative variance
explained as the number of ranks considered increases; in \textbf{A} and
\textbf{B}, the dot represents the point of inflexion in the curve (at
rank 39) estimated using the finite differences method. \textbf{C},
position of hosts and parasites in the space of latent variables on the
first and second dimensions of their respective subspaces (the results
have been clamped to the unit interval). \textbf{D}, predicted
interaction weight from the RDPG based on the status of the species pair
in the metaweb. Source:
\href{https://PoisotLab.github.io/ms_metaweb_perspectives/notebooks/SupplementaryMaterial-preview.html\#cell-fig-illustration-1}{Demonstration
of metaweb embedding using RDPG}}

\end{figure}

In Figure~\ref{fig-illustration-1}, we focus on some statistical checks
of the embedding. In panel \textbf{A}, we show that the averaged \(L_2\)
loss (\emph{i.e.} the mean of squared errors) between the empirical and
reconstructed metaweb decreases when the number of dimensions (rank) of
the subspace increases, with an inflection at 39 dimensions (out of 120
initially) according to the finite differences method. As discussed by
Runghen, Stouffer, and Dalla Riva (2021), there is often a trade-off
between the number of dimensions to use (more dimensions are more
computationally demanding) and the quality of the representation. In
panel \textbf{B}, we show the increase in cumulative variance explained
at each rank, and visualize that using 39 ranks explains about 70\% of
the variance in the empirical metaweb. This is a different information
from the \(L_2\) loss (which is averaged across interactions), as it
works on the eigenvalues of the embedding, and therefore captures
higher-level features of the network. In panel \textbf{C}, we show
positions of hosts and parasites on the first two dimensions of the left
and right subspaces. Note that these values largely skew negative,
because the first dimensions capture the coarse structure of the
network: most pairs of species do not interact, and therefore have
negative values. Finally in panel \textbf{D}, we show the predicted
weight (\emph{i.e.} the result of the multiplication of the RDGP
subspaces at a rank of 39) as a function of whether the interactions are
observed, not-observed, or unknown due to lack of co-occurrence in the
original dataset. This reveals that the observed interactions have
higher predicted weights, although there is some overlap; the usual
approach to identify potential interactions based on this information
would be a thresholding analysis, which is outside the scope of this
manuscript (and is done in the papers cited in this illustration).
Because the values returned from RDPG are not bound to the unit
interval, we performed a clamping of the weights to the unit space,
showing a one-inflation in documented interactions, and a zero-inflation
in other species pairs. This last figure shows that species pairs with
no documented co-occurrence have weights that are not distinguishable
from species pairs with no documented interactions; in other words,
looking at the embedding, species that do not co-occur are not easily
distinguished from species that do not interact. This suggests that (as
befits a host-parasite model) the ability to interact is a strong
predictor of co-occurrence.

\begin{figure}[H]

{\centering \includegraphics{index_files/figure-latex/fig-illustration-2-output-1.png}

}

\caption{\label{fig-illustration-2}Ecological analysis of an embedding
for a host-parasite metaweb, using Random Dot Product Graphs.
\textbf{A}, relationship between the number of parasites and position
along the first axis of the right-subspace for all hosts, showing that
the embedding captures elements of network structure at the species
scale. \textbf{B}, weak relationship between the body mass of hosts (in
grams) and the position alongside the same dimension. \textbf{C}, weak
relationship between body mass of hosts and parasite richness.
\textbf{D}, distribution of positions alongside the same axis for hosts
grouped by taxonomic family. Source:
\href{https://PoisotLab.github.io/ms_metaweb_perspectives/notebooks/SupplementaryMaterial-preview.html\#cell-fig-illustration-2}{Demonstration
of metaweb embedding using RDPG}}

\end{figure}

The results of Figure~\ref{fig-illustration-1} show that we can extract
an embedding of the metaweb that captures enough variance to be
relevant; specifically, this is true for both \(L_2\) loss (indicating
that RDPG is able to capture pairwise processes) and the cumulative
variance explained (indicating that RDPG is able to capture
network-level structure). Therefore, in Figure~\ref{fig-illustration-2},
we relate the values of latent variables for hosts to different
ecologically-relevant data. In panel \textbf{A}, we show that host with
a higher value on the first dimension have fewer parasites. This relates
to the body size of hosts in the \emph{PanTHERIA} database (Jones et al.
2009), as shown in panel \textbf{B}: interestingly, the position on the
first axis is only weakly correlated to body mass of the host; this
matches well established results showing that body size/mass is not
always a direct predictor of parasite richness in terrestrial mammals
(Morand and Poulin 1998), a result we observe in panel \textbf{C}.
Finally, in panel \textbf{D}, we can see how different taxonomic
families occupy different positions on the first axis, with \emph{e.g.}
Sciuridae being biased towards higher values. These results show how we
can look for ecological informations in the output of network
embeddings, which can further be refined into the selection of
predictors for transfer learning.

\hypertarget{the-metaweb-merges-ecological-hypotheses-and-practices}{%
\section{The metaweb merges ecological hypotheses and
practices}\label{the-metaweb-merges-ecological-hypotheses-and-practices}}

Metaweb inference seeks to provide information about the interactions
between species at a large spatial scale, typically a scale large enough
to be considered of biogeographic relevance (indeed, many of the
examples covered in the introduction span areas larger than a country,
some of them global). But as Herbert (1965) rightfully pointed out,
``{[}y{]}ou can't draw neat lines around planet-wide problems''; any
inference of a metaweb must therefore contend with several novel,
interwoven, families of problems. In this section, we outline three that
we think are particularly important, and can discuss how they may
addressed with subsequent data analysis or simulations, and how they
emerge in the specific context of using embeddings; some of these issues
are related to the application of these methods at the science-policy
interface. Adressing these considerations as part of the methodological
discussion is particularly important, as the construction of metawebs
can perpetuate legacies of biases in data (Box 2).

\hypertarget{identifying-the-properties-of-the-network-to-embed}{%
\subsection{Identifying the properties of the network to
embed}\label{identifying-the-properties-of-the-network-to-embed}}

If the initial metaweb is too narrow in scope, notably from a taxonomic
point of view, the chances of finding another area with enough related
species (through phylogenetic relatedness or similarity of functional
traits) to make a reliable inference decreases. This is because transfer
requires similarity (Figure~\ref{fig-embedding}). A diagnostic for the
lack of similar species would likely be large confidence intervals
during estimation of the values in the low-rank space. In other words,
the representation of the original graph is difficult to transfer to the
new problem. Alternatively, if the initial metaweb is too large
(taxonomically), then the resulting embeddings would need to represent
interactions between taxonomic groups that are not present in the new
location. This would lead to a much higher variance in the starting
dataset, and to under-dispersion in the target dataset, resulting in the
potential under or over estimation of the strength of new predicted
interactions. Llewelyn et al. (2022) provided compelling evidence for
these situations by showing that, even at small spatial scales, the
transfer of information about interactions becomes more challenging when
areas rich with endemic species are considered. The lack of well
documented metawebs is currently preventing the development of more
concrete guidelines. The question of phylogenetic relatedness and
distribution is notably relevant if the metaweb is assembled in an area
with mostly endemic species (\emph{e.g.} a system that has undergone
recent radiation or that has remained in isolation for a long period of
time might not have an analogous system with which to draw knowledge
from), and as with every predictive algorithm, there is room for the
application of our best ecological judgement. Because this problem
relates to distribution of species in the geographic or phylogenetic
space, it can certainly be approached through assessing the performance
of embedding transfer in simulated starting/target species pools.

\hypertarget{identifying-the-scope-of-the-prediction-to-perform}{%
\subsection{Identifying the scope of the prediction to
perform}\label{identifying-the-scope-of-the-prediction-to-perform}}

The area for which we seek to predict the metaweb should determine the
species pool on which the embedding is performed. Metawebs can be
constructed by assigning interactions in a list of species within
specific regions. The upside of this approach is that information
relevant for the construction of this dataset is likely to exist, as
countries usually set conservation goals at the national level (Buxton
et al. 2021), and as quantitative instruments are consequently designed
to work at these scales (Turak et al. 2017); specific strategies are
often enacted at smaller scales, nested within a specific country (Ray,
Grimm, and Olive 2021). However, there is no guarantee that these
arbitrary boundaries are meaningful. In fact, we do not have a
satisfying answer to the question of ``where does an ecological network
stop?'', the answer to which would dictate the spatial span to
embed/predict. Recent results by Martins et al. (2022) suggested that
networks are shaped within eco-regions, with abrupt structural
transitions from an eco-region to the next. Should this trend hold
generally, this would provide an ecologically-relevant scale at which
metawebs can be downscaled and predicted. Other solutions could leverage
network-area relationships to identify areas in which networks are
structurally similar (see \emph{e.g.} Fortin, Dale, and Brimacombe 2021;
Galiana et al. 2018, 2022). Both of these solutions require ample
pre-existing information about the network in space. Nevertheless, the
inclusion of species for which we have data but that are not in the
right spatial extent \emph{may} improve the performance of approaches
based on embedding and transfer, \emph{if} they increase the similarity
between the target and destination network. This proposal can
specifically be evaluated by adding nodes to the network to embed, and
assessing the performance of predictive models (see \emph{e.g.} Llewelyn
et al. 2022).

\hypertarget{putting-models-in-their-context}{%
\subsection{Putting models in their
context}\label{putting-models-in-their-context}}

Predictive approaches in ecology, regardless of the scale at which they
are deployed and the intent of their deployment, originate in the
framework that contributed to the ongoing biodiversity crisis (Adam
2014) and reinforced environmental injustice (Choudry 2013; Domínguez
and Luoma 2020). The risk of embedding this legacy in our models is
real, especially when the impact of this legacy on species pools is
being increasingly documented. This problem can be addressed by
re-framing the way we interact with models, especially when models are
intended to support conservation actions. Particularly on territories
that were traditionally stewarded by Indigenous people, we must
interrogate how predictive approaches and the biases that underpin them
can be put to task in accompanying Indigenous principles of land
management (Eichhorn, Baker, and Griffiths 2019; No'kmaq et al. 2021).
The discussion of ``algorithm-in-the-loop'' approaches that is now
pervasive in the machine learning community provides examples of why
this is important. Human-algorithm interactions are notoriously
difficult and can yield adverse effects (Green and Chen 2019; Stevenson
and Doleac 2021), suggesting the need to systematically study them for
the specific purpose of, here, biodiversity governance. Improving the
algorithmic literacy of decision makers is part of the solution
(\emph{e.g.} Lamba et al. 2019; Mosebo Fernandes et al. 2020), as we can
reasonably expect that model outputs will be increasingly used to drive
policy decisions (Weiskopf et al. 2022). Our discussion of these
approaches need to go beyond the technical and statistical, and into the
governance consequences they can have. To embed data also embeds
historical and contemporary biases that acted on these data, both
because they shaped the ecological processes generating them, and the
global processes leading to their measurement and publication. For a
domain as vast as species interaction networks, these biases exist at
multiple scales along the way, and a challenge for prediction is not
only to develop (or adopt) new quantitative tools, but to assess the
behavior of these tools in the proper context.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

Although promising, the application of embeddings to metaweb prediction
will require to address several challenges. First, there is a need to
understand how to define a metaweb as a single, cohesive, unit of
ecological organisation. This is likely to admit very different answers
based on the specific taxonomic group, temporal and spatial resolution,
and question being investigated. Second, there is a need to understand
the scale at which these predictions are relevant. Although we have
documented many cases of using embedding to fill gaps in the metaweb,
these techniques can likely be brought into a spatial (and possibly
temporal) context. The validation of these predictions will have to
proceed jointly with empirical sampling of interactions, but also with
the design of downsampling methods. Finally, there is a need for a
greater understanding of how biases in the data propagate to the
predictions. Because the volume of metawebs is currently low, and
because graph embeddings have not been commonly applied, we anticipate
that this discussion will take place organically in the coming years.

\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Box 2 - Minding legacies shaping ecological datasets}, colback=white, rightrule=.15mm, coltitle=black, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0, breakable, bottomtitle=1mm, titlerule=0mm, toptitle=1mm, arc=.35mm, toprule=.15mm, leftrule=.75mm, left=2mm, opacitybacktitle=0.6]

In large parts of the world, boundaries that delineate geographic
regions are merely a reflection the legacy of settler colonialism, which
drives global disparity in capacity to collect and publish ecological
data. Applying any embedding to biased data does not debias them, but
rather embeds these biases, propagating them to the models using
embeddings to make predictions. Furthermore, the use of ecological data
itself is not an apolitical act (Nost and Goldstein 2021): data
infrastructures tend to be designed to answer questions within national
boundaries (therefore placing contingencies on what is available to be
embedded), their use often drawing upon, and reinforcing, territorial
statecraft (see \emph{e.g.} Barrett 2005). As per Machen and Nost
(2021), these biases are particularly important to consider when
knowledge generated algorithmically is used to supplement or replace
human decision-making, especially for governance (\emph{e.g.} enacting
conservation decisions on the basis of model prediction). As information
on networks is increasingly leveraged for conservation actions (see
\emph{e.g.} Eero et al. 2021; Naman et al. 2022; Stier et al. 2017), the
need to appraise and correct biases that are unwittingly propagated to
algorithms when embedded from the original data is immense. These
considerations are even more urgent in the specific context of
biodiversity data. Long-term colonial legacies still shape taxonomic
composition to this day (Lenzner et al. 2022; Raja 2022), and much
shorter-term changes in taxonomic and genetic richness of wildlife
emerged through environmental racism (Schmidt and Garroway 2022). Thus,
the set of species found at a specific location is not only as the
result of a response to ecological processes separate from human
influence, but also the result of human-environment interaction as well
as the result legislative/political histories.

\end{tcolorbox}

\textbf{Acknowledgements:} We acknowledge that this study was conducted
on land within the traditional unceded territory of the Saint Lawrence
Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak
nations. TP, TS, DC, and LP received funding from the Canadian Institute
for Ecology \& Evolution. FB is funded by the Institute for Data
Valorization (IVADO). TS, SB, and TP are funded by a donation from the
Courtois Foundation. CB was awarded a Mitacs Elevate Fellowship no.
IT12391, in partnership with fRI Research, and also acknowledges funding
from Alberta Innovates and the Forest Resources Improvement Association
of Alberta. M-JF acknowledges funding from NSERC Discovery Grant and
NSERC CRC. RR is funded by New Zealand's Biological Heritage Ngā Koiora
Tuku Iho National Science Challenge, administered by New Zealand
Ministry of Business, Innovation, and Employment. BM is funded by the
NSERC Alexander Graham Bell Canada Graduate Scholarship and the FRQNT
master's scholarship. LP acknowledges funding from NSERC Discovery Grant
(NSERC RGPIN-2019-05771). TP acknowledges financial support from the
Fondation Courtois, and NSERC through the Discovery Grants and Discovery
Accelerator Supplement programs. MJF is supported by an NSERC PDF and an
RBC Post-Doctoral Fellowship.

\textbf{Conflict of interest:} The authors have no conflict of interests
to disclose

\textbf{Authors' contributions:} TS, and TP conceived the ideas
discussed in the manuscript. All authors contributed to writing and
editing the manuscript.

\textbf{Data availability:} There is no data associated with this
manuscript.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Adam2014Elephant}{}}%
Adam, Rachelle. 2014. \emph{Elephant Treaties: {The Colonial} Legacy of
the Biodiversity Crisis}. {UPNE}.

\leavevmode\vadjust pre{\hypertarget{ref-Albouy2019Marine}{}}%
Albouy, Camille, Philippe Archambault, Ward Appeltans, Miguel B. Araújo,
David Beauchesne, Kevin Cazelles, Alyssa R. Cirtwill, et al. 2019.
{``The Marine Fish Food Web Is Globally Connected.''} \emph{Nature
Ecology \& Evolution} 3 (8, 8): 1153--61.
\url{https://doi.org/10.1038/s41559-019-0950-y}.

\leavevmode\vadjust pre{\hypertarget{ref-Anowar2021Conceptual}{}}%
Anowar, Farzana, Samira Sadaoui, and Bassant Selim. 2021. {``Conceptual
and Empirical Comparison of Dimensionality Reduction Algorithms ({PCA},
{KPCA}, {LDA}, {MDS}, {SVD}, {LLE}, {ISOMAP}, {LE}, {ICA}, t-{SNE}).''}
\emph{Computer Science Review} 40 (May): 100378.
\url{https://doi.org/10.1016/j.cosrev.2021.100378}.

\leavevmode\vadjust pre{\hypertarget{ref-Arsov2019Network}{}}%
Arsov, Nino, and Georgina Mirceva. 2019. {``Network {Embedding}: {An
Overview}.''} \url{http://arxiv.org/abs/1911.11726}.

\leavevmode\vadjust pre{\hypertarget{ref-Athreya2017Statistical}{}}%
Athreya, Avanti, Donniell E. Fishkind, Keith Levin, Vince Lyzinski,
Youngser Park, Yichen Qin, Daniel L. Sussman, Minh Tang, Joshua T.
Vogelstein, and Carey E. Priebe. 2017. {``Statistical Inference on
Random Dot Product Graphs: A Survey.''} {arXiv}.
\url{http://arxiv.org/abs/1709.05454}.

\leavevmode\vadjust pre{\hypertarget{ref-Barrett2005Environment}{}}%
Barrett, Scott. 2005. \emph{Environment and {Statecraft}: {The Strategy}
of {Environmental Treaty-Making}}. 1st ed. {Oxford University
PressOxford}. \url{https://doi.org/10.1093/0199286094.001.0001}.

\leavevmode\vadjust pre{\hypertarget{ref-Bartomeus2013Understanding}{}}%
Bartomeus, Ignasi. 2013. {``Understanding Linkage Rules in
Plant-Pollinator Networks by Using Hierarchical Models That Incorporate
Pollinator Detectability and Plant Traits.''} \emph{PloS One} 8 (7):
e69200.
\url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0069200}.

\leavevmode\vadjust pre{\hypertarget{ref-Bartomeus2016Common}{}}%
Bartomeus, Ignasi, Dominique Gravel, Jason M. Tylianakis, Marcelo A.
Aizen, Ian A. Dickie, and Maud Bernard-Verdier. 2016. {``A Common
Framework for Identifying Linkage Rules Across Different Types of
Interactions.''} \emph{Functional Ecology} 30 (12): 1894--1903.
\url{http://onlinelibrary.wiley.com/doi/10.1111/1365-2435.12666/full}.

\leavevmode\vadjust pre{\hypertarget{ref-Bezanson2017Julia}{}}%
Bezanson, Jeff, Alan Edelman, Stefan Karpinski, and Viral B. Shah. 2017.
{``Julia: {A Fresh Approach} to {Numerical Computing}.''} \emph{SIAM
Review} 59 (1): 65--98. \url{https://doi.org/10.1137/141000671}.

\leavevmode\vadjust pre{\hypertarget{ref-Blanchet2020Cooccurrence}{}}%
Blanchet, F. Guillaume, Kevin Cazelles, and Dominique Gravel. 2020.
{``Co-Occurrence Is Not Evidence of Ecological Interactions.''}
\emph{Ecology Letters}.

\leavevmode\vadjust pre{\hypertarget{ref-Bohan2017Nextgeneration}{}}%
Bohan, David A., Corinne Vacher, Alireza Tamaddoni-Nezhad, Alan
Raybould, Alex J. Dumbrell, and Guy Woodward. 2017. {``Next-{Generation
Global Biomonitoring}: {Large-scale}, {Automated Reconstruction} of
{Ecological Networks}.''} \emph{Trends in Ecology \& Evolution}, March.
\url{https://doi.org/10.1016/j.tree.2017.03.001}.

\leavevmode\vadjust pre{\hypertarget{ref-Botella2022Appraisal}{}}%
Botella, Christophe, Stéphane Dray, Catherine Matias, Vincent Miele, and
Wilfried Thuiller. 2022. {``An Appraisal of Graph Embeddings for
Comparing Trophic Network Architectures.''} \emph{Methods in Ecology and
Evolution} 13 (1): 203--16.
\url{https://doi.org/10.1111/2041-210X.13738}.

\leavevmode\vadjust pre{\hypertarget{ref-Braga2019Spatial}{}}%
Braga, João, Laura J. Pollock, Ceres Barros, Núria Galiana, José M.
Montoya, Dominique Gravel, Luigi Maiorano, et al. 2019. {``Spatial
Analyses of Multi-Trophic Terrestrial Vertebrate Assemblages in
{Europe}.''} \emph{Global Ecology and Biogeography} 28 (11): 1636--48.
\url{https://doi.org/10.1111/geb.12981}.

\leavevmode\vadjust pre{\hypertarget{ref-Braga2021Phylogenetic}{}}%
Braga, Mariana P., Niklas Janz, Sören Nylin, Fredrik Ronquist, and
Michael J. Landis. 2021. {``Phylogenetic Reconstruction of Ancestral
Ecological Networks Through Time for Pierid Butterflies and Their Host
Plants.''} \emph{Ecology Letters} n/a (n/a).
\url{https://doi.org/10.1111/ele.13842}.

\leavevmode\vadjust pre{\hypertarget{ref-BramonMora2018Identifying}{}}%
Bramon Mora, Bernat, Dominique Gravel, Luis J. Gilarranz, Timothée
Poisot, and Daniel B. Stouffer. 2018. {``Identifying a Common Backbone
of Interactions Underlying Food Webs from Different Ecosystems.''}
\emph{Nature Communications} 9 (1): 2603.
\url{https://doi.org/10.1038/s41467-018-05056-0}.

\leavevmode\vadjust pre{\hypertarget{ref-Buxton2021Key}{}}%
Buxton, Rachel T., Joseph R. Bennett, Andrea J. Reid, Charles Shulman,
Steven J. Cooke, Charles M. Francis, Elizabeth A. Nyboer, et al. 2021.
{``Key Information Needs to Move from Knowledge to Action for
Biodiversity Conservation in {Canada}.''} \emph{Biological Conservation}
256 (April): 108983. \url{https://doi.org/10.1016/j.biocon.2021.108983}.

\leavevmode\vadjust pre{\hypertarget{ref-carlson2022}{}}%
Carlson, Colin J., Gregory F. Albery, Cory Merow, Christopher H. Trisos,
Casey M. Zipfel, Evan A. Eskew, Kevin J. Olival, Noam Ross, and Shweta
Bansal. 2022. {``Climate Change Increases Cross-Species Viral
Transmission Risk.''} \emph{Nature} 607 (7919): 555--62.
\url{https://doi.org/10.1038/s41586-022-04788-w}.

\leavevmode\vadjust pre{\hypertarget{ref-Catchen2023Missing}{}}%
Catchen, Michael, Timothée Poisot, Laura Pollock, and Andrew Gonzalez.
2023. {``The Missing Link: Discerning True from False Negatives When
Sampling Species Interaction Networks.''} Preprint. {EcoEvoRXiV}.
\url{https://doi.org/10.32942/X2DW22}.

\leavevmode\vadjust pre{\hypertarget{ref-Cazelles2016Theory}{}}%
Cazelles, Kévin, Miguel B. Araújo, Nicolas Mouquet, and Dominique
Gravel. 2016. {``A Theory for Species Co-Occurrence in Interaction
Networks.''} \emph{Theoretical Ecology} 9 (1): 39--48.
\url{https://doi.org/10.1007/s12080-015-0281-9}.

\leavevmode\vadjust pre{\hypertarget{ref-Chami2022Machine}{}}%
Chami, Ines, Sami Abu-El-Haija, Bryan Perozzi, Christopher Ré, and Kevin
Murphy. 2022. {``Machine {Learning} on {Graphs}: {A Model} and
{Comprehensive Taxonomy}.''} \emph{Journal of Machine Learning Research}
23 (89): 1--64. \url{http://jmlr.org/papers/v23/20-852.html}.

\leavevmode\vadjust pre{\hypertarget{ref-Chen2017Deep}{}}%
Chen, Di, Yexiang Xue, Daniel Fink, Shuo Chen, and Carla P. Gomes. 2017.
{``Deep {Multi-species Embedding},''} 3639--46.
\url{https://www.ijcai.org/proceedings/2017/509}.

\leavevmode\vadjust pre{\hypertarget{ref-Chen2017Harp}{}}%
Chen, Haochen, Bryan Perozzi, Yifan Hu, and Steven Skiena. 2017.
{``{HARP}: {Hierarchical Representation Learning} for {Networks}.''}
\url{http://arxiv.org/abs/1706.07845}.

\leavevmode\vadjust pre{\hypertarget{ref-Choudry2013Saving}{}}%
Choudry, Aziz. 2013. {``Saving Biodiversity, for Whom and for What?
{Conservation NGOs}, Complicity, Colonialism and Conquest in an Era of
Capitalist Globalization.''} In \emph{{NGOization}: {Complicity},
Contradictions and Prospects}, 24--44. {Bloomsbury Publishing}.

\leavevmode\vadjust pre{\hypertarget{ref-Cieslak2020Tdistributed}{}}%
Cieslak, Matthew C., Ann M. Castelfranco, Vittoria Roncalli, Petra H.
Lenz, and Daniel K. Hartline. 2020. {``T-{Distributed Stochastic
Neighbor Embedding} (t-{SNE}): {A} Tool for Eco-Physiological
Transcriptomic Analysis.''} \emph{Marine Genomics} 51 (June): 100723.
\url{https://doi.org/10.1016/j.margen.2019.100723}.

\leavevmode\vadjust pre{\hypertarget{ref-Csermely2004Strong}{}}%
Csermely, Peter. 2004. {``Strong Links Are Important, but Weak Links
Stabilize Them.''} \emph{Trends in Biochemical Sciences} 29 (7):
331--34. \url{https://doi.org/10.1016/j.tibs.2004.05.004}.

\leavevmode\vadjust pre{\hypertarget{ref-DallaRiva2016Exploring}{}}%
Dalla Riva, Giulio V., and Daniel B. Stouffer. 2016. {``Exploring the
Evolutionary Signature of Food Webs' Backbones Using Functional
Traits.''} \emph{Oikos} 125 (4): 446--56.
\url{https://doi.org/10.1111/oik.02305}.

\leavevmode\vadjust pre{\hypertarget{ref-Dallas2017Predicting}{}}%
Dallas, Tad, Andrew W. Park, and John M. Drake. 2017. {``Predicting
Cryptic Links in Host-Parasite Networks.''} \emph{PLOS Computational
Biology} 13 (5): e1005557.
\url{https://doi.org/10.1371/journal.pcbi.1005557}.

\leavevmode\vadjust pre{\hypertarget{ref-Danisch2021Makie}{}}%
Danisch, Simon, and Julius Krumbiegel. 2021. {``Makie.jl: {Flexible}
High-Performance Data Visualization for {Julia}.''} \emph{Journal of
Open Source Software} 6 (65): 3349.
\url{https://doi.org/10.21105/joss.03349}.

\leavevmode\vadjust pre{\hypertarget{ref-Dominguez2020Decolonising}{}}%
Domínguez, Lara, and Colin Luoma. 2020. {``Decolonising {Conservation
Policy}: {How Colonial Land} and {Conservation Ideologies Persist} and
{Perpetuate Indigenous Injustices} at the {Expense} of the
{Environment}.''} \emph{Land} 9 (3, 3): 65.
\url{https://doi.org/10.3390/land9030065}.

\leavevmode\vadjust pre{\hypertarget{ref-Dunne2006Network}{}}%
Dunne, Jennifer A. 2006. {``The {Network Structure} of {Food Webs}.''}
In \emph{Ecological Networks: {Linking} Structure and Dynamics}, edited
by Jennifer A Dunne and Mercedes Pascual, 27--86. {Oxford University
Press}.

\leavevmode\vadjust pre{\hypertarget{ref-Eero2021Use}{}}%
Eero, Margit, Jan Dierking, Christoph Humborg, Emma Undeman, Brian R
MacKenzie, Henn Ojaveer, Tiina Salo, and Friedrich Wilhelm Köster. 2021.
{``Use of Food Web Knowledge in Environmental Conservation and
Management of Living Resources in the {Baltic Sea}.''} \emph{ICES
Journal of Marine Science} 78 (8): 2645--63.
\url{https://doi.org/10.1093/icesjms/fsab145}.

\leavevmode\vadjust pre{\hypertarget{ref-Eichhorn2019Steps}{}}%
Eichhorn, Markus P., Kate Baker, and Mark Griffiths. 2019. {``Steps
Towards Decolonising Biogeography.''} \emph{Frontiers of Biogeography}
12 (1): 1--7. \url{https://doi.org/10.21425/F5FBG44795}.

\leavevmode\vadjust pre{\hypertarget{ref-Eklof2013Dimensionality}{}}%
Eklöf, Anna, Ute Jacob, Jason Kopp, Jordi Bosch, Rocío Castro-Urgal,
Natacha P. Chacoff, Bo Dalsgaard, et al. 2013. {``The Dimensionality of
Ecological Networks.''} \emph{Ecology Letters} 16 (5): 577--83.
\url{https://doi.org/10.1111/ele.12081}.

\leavevmode\vadjust pre{\hypertarget{ref-Eklof2016Phylogenetic}{}}%
Eklöf, Anna, and Daniel B. Stouffer. 2016. {``The Phylogenetic Component
of Food Web Structure and Intervality.''} \emph{Theoretical Ecology} 9
(1): 107--15. \url{https://doi.org/10.1007/s12080-015-0273-9}.

\leavevmode\vadjust pre{\hypertarget{ref-Fortin2021Network}{}}%
Fortin, Marie-Josée, Mark R. T. Dale, and Chris Brimacombe. 2021.
{``Network Ecology in Dynamic Landscapes.''} \emph{Proceedings of the
Royal Society B: Biological Sciences} 288 (1949): rspb.2020.1889,
20201889. \url{https://doi.org/10.1098/rspb.2020.1889}.

\leavevmode\vadjust pre{\hypertarget{ref-Fricke2022Effects}{}}%
Fricke, Evan C., Alejandro Ordonez, Haldre S. Rogers, and Jens-Christian
Svenning. 2022. {``The Effects of Defaunation on Plants' Capacity to
Track Climate Change.''} \emph{Science}, January.
\url{https://www.science.org/doi/abs/10.1126/science.abk3510}.

\leavevmode\vadjust pre{\hypertarget{ref-Galiana2022Ecological}{}}%
Galiana, Núria, Miguel Lurgi, Vinicius A. G. Bastazini, Jordi Bosch,
Luciano Cagnolo, Kevin Cazelles, Bernat Claramunt-López, et al. 2022.
{``Ecological Network Complexity Scales with Area.''} \emph{Nature
Ecology \& Evolution}, January, 1--8.
\url{https://doi.org/10.1038/s41559-021-01644-4}.

\leavevmode\vadjust pre{\hypertarget{ref-Galiana2018Spatial}{}}%
Galiana, Núria, Miguel Lurgi, Bernat Claramunt-López, Marie-Josée
Fortin, Shawn Leroux, Kevin Cazelles, Dominique Gravel, and José M.
Montoya. 2018. {``The Spatial Scaling of Species Interaction
Networks.''} \emph{Nature Ecology \& Evolution} 2 (5): 782--90.
\url{https://doi.org/10.1038/s41559-018-0517-3}.

\leavevmode\vadjust pre{\hypertarget{ref-Gaucher2021Outlier}{}}%
Gaucher, Solenne, Olga Klopp, and Geneviève Robin. 2021. {``Outlier
Detection in Networks with Missing Links.''} \emph{Computational
Statistics \& Data Analysis} 164 (December): 107308.
\url{https://doi.org/10.1016/j.csda.2021.107308}.

\leavevmode\vadjust pre{\hypertarget{ref-ghasemian2020}{}}%
Ghasemian, Amir, Homa Hosseinmardi, Aram Galstyan, Edoardo M. Airoldi,
and Aaron Clauset. 2020. {``Stacking Models for Nearly Optimal Link
Prediction in Complex Networks.''} \emph{Proceedings of the National
Academy of Sciences} 117 (38): 23393--400.
\url{https://doi.org/10.1073/pnas.1914950117}.

\leavevmode\vadjust pre{\hypertarget{ref-Gibb2021Data}{}}%
Gibb, Rory, Gregory F Albery, Daniel J Becker, Liam Brierley, Ryan
Connor, Tad A Dallas, Evan A Eskew, et al. 2021. {``Data
{Proliferation}, {Reconciliation}, and {Synthesis} in {Viral
Ecology}.''} \emph{BioScience} 71 (11): 1148--56.
\url{https://doi.org/10.1093/biosci/biab080}.

\leavevmode\vadjust pre{\hypertarget{ref-Goebel2023Body}{}}%
Goebel, Larissa Gabriela Araujo, Breno Dias Vitorino, Angélica Vilas
Boas Frota, and Manoel dos Santos-Filho. 2023. {``Body Mass Determines
the Role of Mammal Species in a Frugivore-Large Fruit Interaction
Network in a {Neotropical} Savanna.''} \emph{Journal of Tropical
Ecology} 39: e12. \url{https://doi.org/10.1017/S0266467422000505}.

\leavevmode\vadjust pre{\hypertarget{ref-Goodfellow2016Deep}{}}%
Goodfellow, Ian, Yoshua Bengio, and Aaron Courville. 2016. \emph{Deep
Learning}. {MIT Press}.

\leavevmode\vadjust pre{\hypertarget{ref-Goyal2018Graph}{}}%
Goyal, Palash, and Emilio Ferrara. 2018. {``Graph Embedding Techniques,
Applications, and Performance: {A} Survey.''} \emph{Knowledge-Based
Systems} 151 (July): 78--94.
\url{https://doi.org/10.1016/j.knosys.2018.03.022}.

\leavevmode\vadjust pre{\hypertarget{ref-Gravel2018Bringing}{}}%
Gravel, Dominique, Benjamin Baiser, Jennifer A. Dunne, Jens-Peter
Kopelke, Neo D. Martinez, Tommi Nyman, Timothée Poisot, et al. 2018.
{``Bringing {Elton} and {Grinnell} Together: A Quantitative Framework to
Represent the Biogeography of Ecological Interaction Networks.''}
\emph{Ecography} 0 (0). \url{https://doi.org/10.1111/ecog.04006}.

\leavevmode\vadjust pre{\hypertarget{ref-Gravel2013Inferring}{}}%
Gravel, Dominique, Timothée Poisot, Camille Albouy, Laure Velez, and
David Mouillot. 2013. {``Inferring Food Web Structure from Predator-Prey
Body Size Relationships.''} Edited by Robert Freckleton. \emph{Methods
in Ecology and Evolution} 4 (11): 1083--90.
\url{https://doi.org/10.1111/2041-210X.12103}.

\leavevmode\vadjust pre{\hypertarget{ref-Green2019Disparate}{}}%
Green, Ben, and Yiling Chen. 2019. {``Disparate {Interactions}: {An
Algorithm-in-the-Loop Analysis} of {Fairness} in {Risk Assessments}.''}
In \emph{Proceedings of the {Conference} on {Fairness},
{Accountability}, and {Transparency}}, 90--99. {FAT}* '19. {New York,
NY, USA}: {Association for Computing Machinery}.
\url{https://doi.org/10.1145/3287560.3287563}.

\leavevmode\vadjust pre{\hypertarget{ref-Grover2016Node2vec}{}}%
Grover, Aditya, and Jure Leskovec. 2016. {``Node2vec: {Scalable Feature
Learning} for {Networks}.''} In \emph{Proceedings of the 22nd {ACM
SIGKDD International Conference} on {Knowledge Discovery} and {Data
Mining}}, 855--64. {San Francisco California USA}: {ACM}.
\url{https://doi.org/10.1145/2939672.2939754}.

\leavevmode\vadjust pre{\hypertarget{ref-Grunig2020Crop}{}}%
Grünig, Marc, Dominique Mazzi, Pierluigi Calanca, Dirk Nikolaus Karger,
and Loïc Pellissier. 2020. {``Crop and Forest Pest Metawebs Shift
Towards Increased Linkage and Suitability Overlap Under Climate
Change.''} \emph{Communications Biology} 3 (1, 1): 1--10.
\url{https://doi.org/10.1038/s42003-020-0962-9}.

\leavevmode\vadjust pre{\hypertarget{ref-Gupta2022Simultaneously}{}}%
Gupta, Anubhav, Reinhard Furrer, and Owen L. Petchey. 2022.
{``Simultaneously Estimating Food Web Connectance and Structure with
Uncertainty.''} \emph{Ecology and Evolution} 12 (3): e8643.
\url{https://doi.org/10.1002/ece3.8643}.

\leavevmode\vadjust pre{\hypertarget{ref-Gupta2021Graph}{}}%
Gupta, Atika, Priya Matta, and Bhasker Pant. 2021. {``Graph Neural
Network: {Current} State of {Art}, Challenges and Applications.''}
\emph{Materials Today: Proceedings}, International {Conference} on
{Technological Advancements} in {Materials Science} and {Manufacturing},
46 (January): 10927--32.
\url{https://doi.org/10.1016/j.matpr.2021.01.950}.

\leavevmode\vadjust pre{\hypertarget{ref-Hadfield2014Tale}{}}%
Hadfield, Jarrod D., Boris R. Krasnov, Robert Poulin, and Shinichi
Nakagawa. 2014. {``A {Tale} of {Two Phylogenies}: {Comparative Analyses}
of {Ecological Interactions}.''} \emph{The American Naturalist} 183 (2):
174--87. \url{https://doi.org/10.1086/674445}.

\leavevmode\vadjust pre{\hypertarget{ref-Herbert1965Dune}{}}%
Herbert, Frank. 1965. \emph{Dune}. 1st ed. {Philadelphia}: {Chilton Book
Company}.

\leavevmode\vadjust pre{\hypertarget{ref-Hinton2002Stochastic}{}}%
Hinton, Geoffrey, and Sam T Roweis. 2002. {``Stochastic Neighbor
Embedding.''} In \emph{{NIPS}}, 15:833--40. {Citeseer}.

\leavevmode\vadjust pre{\hypertarget{ref-Hoffmann2019Machine}{}}%
Hoffmann, Jordan, Yohai Bar-Sinai, Lisa M. Lee, Jovana Andrejevic,
Shruti Mishra, Shmuel M. Rubinstein, and Chris H. Rycroft. 2019.
{``Machine Learning in a Data-Limited Regime: {Augmenting} Experiments
with Synthetic Data Uncovers Order in Crumpled Sheets.''} \emph{Science
Advances} 5 (4): eaau6792. \url{https://doi.org/10.1126/sciadv.aau6792}.

\leavevmode\vadjust pre{\hypertarget{ref-Hortal2015Seven}{}}%
Hortal, Joaquín, Francesco de Bello, José Alexandre F. Diniz-Filho,
Thomas M. Lewinsohn, Jorge M. Lobo, and Richard J. Ladle. 2015. {``Seven
{Shortfalls} That {Beset Large-Scale Knowledge} of {Biodiversity}.''}
\emph{Annual Review of Ecology, Evolution, and Systematics} 46 (1):
523--49. \url{https://doi.org/10.1146/annurev-ecolsys-112414-054400}.

\leavevmode\vadjust pre{\hypertarget{ref-Jones2009Pantheria}{}}%
Jones, Kate E., Jon Bielby, Marcel Cardillo, Susanne A. Fritz, Justin
O'Dell, C. David L. Orme, Kamran Safi, et al. 2009. {``{PanTHERIA}: A
Species‐level Database of Life History, Ecology, and Geography of Extant
and Recently Extinct Mammals: {Ecological Archives E090}‐184.''} Edited
by W. K. Michener. \emph{Ecology} 90 (9): 2648--48.
\url{https://doi.org/10.1890/08-1494.1}.

\leavevmode\vadjust pre{\hypertarget{ref-Jordano2016Sampling}{}}%
Jordano, Pedro. 2016. {``Sampling Networks of Ecological
Interactions.''} Edited by Daniel Stouffer. \emph{Functional Ecology} 30
(12): 1883--93. \url{https://doi.org/10.1111/1365-2435.12763}.

\leavevmode\vadjust pre{\hypertarget{ref-Lamba2019Deep}{}}%
Lamba, Aakash, Phillip Cassey, Ramesh Raja Segaran, and Lian Pin Koh.
2019. {``Deep Learning for Environmental Conservation.''} \emph{Current
Biology} 29 (19): R977--82.
\url{https://doi.org/10.1016/j.cub.2019.08.016}.

\leavevmode\vadjust pre{\hypertarget{ref-Lenzner2022Naturalized}{}}%
Lenzner, Bernd, Guillaume Latombe, Anna Schertler, Hanno Seebens, Qiang
Yang, Marten Winter, Patrick Weigelt, et al. 2022. {``Naturalized Alien
Floras Still Carry the Legacy of {European} Colonialism.''} \emph{Nature
Ecology \& Evolution}, October, 1--10.
\url{https://doi.org/10.1038/s41559-022-01865-1}.

\leavevmode\vadjust pre{\hypertarget{ref-Llewelyn2022Predicting}{}}%
Llewelyn, John, Giovanni Strona, Christopher R. Dickman, Aaron C.
Greenville, Glenda M. Wardle, Michael S. Y. Lee, Seamus Doherty, Farzin
Shabani, Frédérik Saltré, and Corey J. A. Bradshaw. 2022. {``Predicting
Predator-Prey Interactions in Terrestrial Endotherms Using Random
Forest.''} Preprint. {Ecology}.
\url{https://doi.org/10.1101/2022.09.02.506446}.

\leavevmode\vadjust pre{\hypertarget{ref-Maaten2009Learning}{}}%
Maaten, Laurens van der. 2009. {``Learning a {Parametric Embedding} by
{Preserving Local Structure}.''} In \emph{Proceedings of the {Twelth
International Conference} on {Artificial Intelligence} and
{Statistics}}, 384--91. {PMLR}.
\url{https://proceedings.mlr.press/v5/maaten09a.html}.

\leavevmode\vadjust pre{\hypertarget{ref-Machen2021Thinking}{}}%
Machen, Ruth, and Eric Nost. 2021. {``Thinking Algorithmically: {The}
Making of Hegemonic Knowledge in Climate Governance.''}
\emph{Transactions of the Institute of British Geographers} 46 (3):
555--69. \url{https://doi.org/10.1111/tran.12441}.

\leavevmode\vadjust pre{\hypertarget{ref-Malaterre2019Functional}{}}%
Malaterre, Christophe, Antoine C Dussault, Ely Mermans, Gillian Barker,
Beatrix E Beisner, Frédéric Bouchard, Eric Desjardins, et al. 2019.
{``Functional {Diversity}: {An Epistemic Roadmap}.''} \emph{BioScience}
69 (10): 800--811. \url{https://doi.org/10.1093/biosci/biz089}.

\leavevmode\vadjust pre{\hypertarget{ref-Martins2022Global}{}}%
Martins, Lucas P., Daniel B. Stouffer, Pedro G. Blendinger, Katrin
Böhning-Gaese, Galo Buitrón-Jurado, Marta Correia, José Miguel Costa, et
al. 2022. {``Global and Regional Ecological Boundaries Explain Abrupt
Spatial Discontinuities in Avian Frugivory Interactions.''} \emph{Nature
Communications} 13 (1, 1): 6943.
\url{https://doi.org/10.1038/s41467-022-34355-w}.

\leavevmode\vadjust pre{\hypertarget{ref-McLeod2021Sampling}{}}%
McLeod, Anne, Shawn J. Leroux, Dominique Gravel, Cindy Chu, Alyssa R.
Cirtwill, Marie-Josée Fortin, Núria Galiana, Timothée Poisot, and
Spencer A. Wood. 2021. {``Sampling and Asymptotic Network Properties of
Spatial Multi-Trophic Networks.''} \emph{Oikos} n/a (n/a).
\url{https://doi.org/10.1111/oik.08650}.

\leavevmode\vadjust pre{\hypertarget{ref-Melnyk2020Graphkke}{}}%
Melnyk, Kateryna, Stefan Klus, Grégoire Montavon, and Tim O. F. Conrad.
2020. {``{GraphKKE}: Graph {Kernel Koopman} Embedding for Human
Microbiome Analysis.''} \emph{Applied Network Science} 5 (1): 96.
\url{https://doi.org/10.1007/s41109-020-00339-2}.

\leavevmode\vadjust pre{\hypertarget{ref-Morales-Castilla2015Inferring}{}}%
Morales-Castilla, Ignacio, Miguel G. Matias, Dominique Gravel, and
Miguel B. Araújo. 2015. {``Inferring Biotic Interactions from
Proxies.''} \emph{Trends in Ecology \& Evolution} 30 (6): 347--56.
\url{https://doi.org/10.1016/j.tree.2015.03.014}.

\leavevmode\vadjust pre{\hypertarget{ref-morales-castilla2021}{}}%
Morales-Castilla, Ignacio, Paula Pappalardo, Maxwell J. Farrell, A.
Alonso Aguirre, Shan Huang, Alyssa-Lois M. Gehman, Tad Dallas, Dominique
Gravel, and T. Jonathan Davies. 2021. {``Forecasting Parasite Sharing
Under Climate Change.''} \emph{Philosophical Transactions of the Royal
Society B: Biological Sciences} 376 (1837): 20200360.
\url{https://doi.org/10.1098/rstb.2020.0360}.

\leavevmode\vadjust pre{\hypertarget{ref-Morand1998Density}{}}%
Morand, Serge, and Robert Poulin. 1998. {``Density, Body Mass and
Parasite Species Richness of Terrestrial Mammals.''} \emph{Evolutionary
Ecology} 12 (6): 717--27. \url{https://doi.org/10.1023/A:1006537600093}.

\leavevmode\vadjust pre{\hypertarget{ref-MoseboFernandes2020Machine}{}}%
Mosebo Fernandes, Ana Cristina, Rebeca Quintero Gonzalez, Marie Ann
Lenihan-Clarke, Ezra Francis Leslie Trotter, and Jamal Jokar Arsanjani.
2020. {``Machine {Learning} for {Conservation Planning} in a {Changing
Climate}.''} \emph{Sustainability} 12 (18, 18): 7657.
\url{https://doi.org/10.3390/su12187657}.

\leavevmode\vadjust pre{\hypertarget{ref-Murphy2022Probabilistic}{}}%
Murphy, Kevin P. 2022. \emph{Probabilistic Machine Learning: {An}
Introduction}. {MIT Press}. \href{https://probml.ai}{probml.ai}.

\leavevmode\vadjust pre{\hypertarget{ref-Naman2022Food}{}}%
Naman, Sean M., Seth M. White, J. Ryan Bellmore, Peter A. McHugh,
Matthew J. Kaylor, Colden V. Baxter, Robert J. Danehy, Robert J. Naiman,
and Amy L. Puls. 2022. {``Food Web Perspectives and Methods for Riverine
Fish Conservation.''} \emph{WIREs Water} n/a (n/a): e1590.
\url{https://doi.org/10.1002/wat2.1590}.

\leavevmode\vadjust pre{\hypertarget{ref-Narayanan2017Graph2vec}{}}%
Narayanan, Annamalai, Mahinthan Chandramohan, Rajasekar Venkatesan,
Lihui Chen, Yang Liu, and Shantanu Jaiswal. 2017. {``Graph2vec:
{Learning Distributed Representations} of {Graphs}.''}
\url{http://arxiv.org/abs/1707.05005}.

\leavevmode\vadjust pre{\hypertarget{ref-Neutel2002Stability}{}}%
Neutel, Anje-Margriet, Johan A. P. Heesterbeek, and Peter C. de Ruiter.
2002. {``Stability in {Real Food Webs}: {Weak Links} in {Long Loops}.''}
\emph{Science} 296 (5570): 1120--23.
\url{https://doi.org/10.1126/science.1068326}.

\leavevmode\vadjust pre{\hypertarget{ref-Nokmaq2021Awakening}{}}%
No'kmaq, M'sit, Albert Marshall, Karen F. Beazley, Jessica Hum, shalan
joudry, Anastasia Papadopoulos, Sherry Pictou, Janet Rabesca, Lisa
Young, and Melanie Zurba. 2021. {``{`{Awakening} the Sleeping Giant'}:
Re-{Indigenization} Principles for Transforming Biodiversity
Conservation in {Canada} and Beyond.''} \emph{FACETS} 6 (1): 839--69.

\leavevmode\vadjust pre{\hypertarget{ref-Nost2021Political}{}}%
Nost, Eric, and Jenny Elaine Goldstein. 2021. {``A Political Ecology of
Data.''} \emph{Environment and Planning E: Nature and Space}, September,
25148486211043503. \url{https://doi.org/10.1177/25148486211043503}.

\leavevmode\vadjust pre{\hypertarget{ref-OConnor2020Unveiling}{}}%
O'Connor, Louise M. J., Laura J. Pollock, João Braga, Gentile Francesco
Ficetola, Luigi Maiorano, Camille Martinez‐Almoyna, Alessandro
Montemaggiori, Marc Ohlmann, and Wilfried Thuiller. 2020. {``Unveiling
the Food Webs of Tetrapods Across {Europe} Through the Prism of the
{Eltonian} Niche.''} \emph{Journal of Biogeography} 47 (1): 181--92.
\url{https://doi.org/10.1111/jbi.13773}.

\leavevmode\vadjust pre{\hypertarget{ref-Pedersen2017Signatures}{}}%
Pedersen, Eric J., Patrick L. Thompson, R. Aaron Ball, Marie-Josée
Fortin, Tarik C. Gouhier, Heike Link, Charlotte Moritz, et al. 2017.
{``Signatures of the Collapse and Incipient Recovery of an Overexploited
Marine Ecosystem.''} \emph{Royal Society Open Science} 4 (7): 170215.
\url{https://doi.org/10.1098/rsos.170215}.

\leavevmode\vadjust pre{\hypertarget{ref-Perozzi2014Deepwalk}{}}%
Perozzi, Bryan, Rami Al-Rfou, and Steven Skiena. 2014. {``{DeepWalk}:
Online Learning of Social Representations.''} In \emph{Proceedings of
the 20th {ACM SIGKDD} International Conference on {Knowledge} Discovery
and Data Mining}, 701--10. {KDD} '14. {New York, NY, USA}: {Association
for Computing Machinery}. \url{https://doi.org/10.1145/2623330.2623732}.

\leavevmode\vadjust pre{\hypertarget{ref-Pichler2020Machine}{}}%
Pichler, Maximilian, Virginie Boreux, Alexandra-Maria Klein, Matthias
Schleuning, and Florian Hartig. 2020. {``Machine Learning Algorithms to
Infer Trait-Matching and Predict Species Interactions in Ecological
Networks.''} \emph{Methods in Ecology and Evolution} 11 (2): 281--93.
\url{https://doi.org/10.1111/2041-210X.13329}.

\leavevmode\vadjust pre{\hypertarget{ref-poisot2023}{}}%
Poisot, Timothée. 2023. {``Guidelines for the Prediction of Species
Interactions Through Binary Classification.''} \emph{Methods in Ecology
and Evolution} 14 (5): 1333--45.
\url{https://doi.org/10.1111/2041-210x.14071}.

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2019Ecologicalnetworks}{}}%
Poisot, Timothée, Zacharie Belisle, Laura Hoebeke, Michiel Stock, and
Piotr Szefer. 2019. {``{EcologicalNetworks}.jl - Analysing Ecological
Networks.''} \emph{Ecography}. \url{https://doi.org/10.1111/ecog.04310}.

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2012Dissimilarity}{}}%
Poisot, Timothée, Elsa Canard, David Mouillot, Nicolas Mouquet, and
Dominique Gravel. 2012. {``The Dissimilarity of Species Interaction
Networks.''} \emph{Ecology Letters} 15 (12): 1353--61.
\url{https://doi.org/10.1111/ele.12002}.

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2016Structure}{}}%
Poisot, Timothée, Alyssa R. Cirtwill, Kévin Cazelles, Dominique Gravel,
Marie-Josée Fortin, and Daniel B. Stouffer. 2016. {``The Structure of
Probabilistic Networks.''} \emph{Methods in Ecology and Evolution} 7
(3): 303--12. \url{https://doi.org/10.1111/2041-210X.12468}.

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2021Imputing}{}}%
Poisot, Timothée, Marie-Andrée Ouellet, Nardus Mollentze, Maxwell J.
Farrell, Daniel J. Becker, Gregory F. Albery, Rory J. Gibb, Stephanie N.
Seifert, and Colin J. Carlson. 2021. {``Imputing the Mammalian Virome
with Linear Filtering and Singular Value Decomposition.''}
\url{http://arxiv.org/abs/2105.14973}.

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2015Species}{}}%
Poisot, Timothée, Daniel B. Stouffer, and Dominique Gravel. 2015.
{``Beyond Species: Why Ecological Interaction Networks Vary Through
Space and Time.''} \emph{Oikos} 124 (3): 243--51.
\url{https://doi.org/10.1111/oik.01719}.

\leavevmode\vadjust pre{\hypertarget{ref-Raja2022Colonialism}{}}%
Raja, Nussaïbah B. 2022. {``Colonialism Shaped Today's Biodiversity.''}
\emph{Nature Ecology \& Evolution}, October, 1--2.
\url{https://doi.org/10.1038/s41559-022-01903-y}.

\leavevmode\vadjust pre{\hypertarget{ref-Ramasamy2015Compressive}{}}%
Ramasamy, Dinesh, and Upamanyu Madhow. 2015. {``Compressive Spectral
Embedding: Sidestepping the {SVD}.''} In \emph{Advances in Neural
Information Processing Systems}, edited by C. Cortes, N. Lawrence, D.
Lee, M. Sugiyama, and R. Garnett. Vol. 28. {Curran Associates, Inc.}
\url{https://proceedings.neurips.cc/paper/2015/file/4f6ffe13a5d75b2d6a3923922b3922e5-Paper.pdf}.

\leavevmode\vadjust pre{\hypertarget{ref-Ray2021Biodiversity}{}}%
Ray, Justina C., Jaime Grimm, and Andrea Olive. 2021. {``The
Biodiversity Crisis in {Canada}: Failures and Challenges of Federal and
Sub-National Strategic and Legal Frameworks.''} \emph{FACETS} 6
(January): 1044--68. \url{https://doi.org/10.1139/facets-2020-0075}.

\leavevmode\vadjust pre{\hypertarget{ref-Runghen2021Exploiting}{}}%
Runghen, Rogini, Daniel B Stouffer, and Giulio V Dalla Riva. 2021.
{``Exploiting Node Metadata to Predict Interactions in Large Networks
Using Graph Embedding and Neural Networks,''} June.
\url{https://doi.org/10.1101/2021.06.10.447991}.

\leavevmode\vadjust pre{\hypertarget{ref-Saravia2021Ecological}{}}%
Saravia, Leonardo A., Tomás I. Marina, Nadiah P. Kristensen, Marleen De
Troch, and Fernando R. Momo. 2021. {``Ecological Network Assembly: {How}
the Regional Metaweb Influences Local Food Webs.''} \emph{Journal of
Animal Ecology} n/a (n/a).
\url{https://doi.org/10.1111/1365-2656.13652}.

\leavevmode\vadjust pre{\hypertarget{ref-Schmidt2022Systemic}{}}%
Schmidt, Chloé, and Colin J. Garroway. 2022. {``Systemic Racism Alters
Wildlife Genetic Diversity.''} \emph{Proceedings of the National Academy
of Sciences} 119 (43): e2102860119.
\url{https://doi.org/10.1073/pnas.2102860119}.

\leavevmode\vadjust pre{\hypertarget{ref-Stevenson2021Algorithmic}{}}%
Stevenson, Megan T., and Jennifer L. Doleac. 2021. {``Algorithmic {Risk
Assessment} in the {Hands} of {Humans}.''} SSRN Scholarly Paper.
{Rochester, NY}. \url{https://doi.org/10.2139/ssrn.3489440}.

\leavevmode\vadjust pre{\hypertarget{ref-Stier2017Integrating}{}}%
Stier, Adrian C., Jameal F. Samhouri, Steven Gray, Rebecca G. Martone,
Megan E. Mach, Benjamin S. Halpern, Carrie V. Kappel, Courtney
Scarborough, and Phillip S. Levin. 2017. {``Integrating {Expert
Perceptions} into {Food Web Conservation} and {Management}.''}
\emph{Conservation Letters} 10 (1): 67--76.
\url{https://doi.org/10.1111/conl.12245}.

\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2007Evidence}{}}%
Stouffer, D. B, J. Camacho, W. Jiang, and L. A Nunes Amaral. 2007.
{``Evidence for the Existence of a Robust Pattern of Prey Selection in
Food Webs.''} \emph{Proceedings of the Royal Society B: Biological
Sciences} 274 (1621): 1931--40.
\url{https://doi.org/10.1098/rspb.2007.0571}.

\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2012Evolutionary}{}}%
Stouffer, D. B., M. Sales-Pardo, M. I. Sirer, and J. Bascompte. 2012.
{``Evolutionary {Conservation} of {Species}' {Roles} in {Food Webs}.''}
\emph{Science} 335 (6075): 1489--92.
\url{https://doi.org/10.1126/science.1216556}.

\leavevmode\vadjust pre{\hypertarget{ref-Strydom2022Food}{}}%
Strydom, Tanya, Salomé Bouskila, Francis Banville, Ceres Barros,
Dominique Caron, Maxwell J. Farrell, Marie-Josée Fortin, et al. 2022.
{``Food Web Reconstruction Through Phylogenetic Transfer of Low-Rank
Network Representation.''} \emph{Methods in Ecology and Evolution} n/a
(n/a). \url{https://doi.org/10.1111/2041-210X.13835}.

\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021Roadmap}{}}%
Strydom, Tanya, Michael D. Catchen, Francis Banville, Dominique Caron,
Gabriel Dansereau, Philippe Desjardins-Proulx, Norma R. Forero-Muñoz, et
al. 2021. {``A Roadmap Towards Predicting Species Interaction Networks
(Across Space and Time).''} \emph{Philosophical Transactions of the
Royal Society B: Biological Sciences} 376 (1837): 20210063.
\url{https://doi.org/10.1098/rstb.2021.0063}.

\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021Svd}{}}%
Strydom, Tanya, Giulio V. Dalla Riva, and Timothée Poisot. 2021. {``{SVD
Entropy Reveals} the {High Complexity} of {Ecological Networks}.''}
\emph{Frontiers in Ecology and Evolution} 9.
\url{https://doi.org/10.3389/fevo.2021.623141}.

\leavevmode\vadjust pre{\hypertarget{ref-Surendran2013Graph}{}}%
Surendran, Subu. 2013. {``Graph {Embedding} and {Dimensionality
Reduction} - {A Survey}.''} \emph{International Journal of Computer
Science \& Engineering Technology} 4 (1).
\url{https://www.semanticscholar.org/paper/Graph-Embedding-and-Dimensionality-Reduction-A-Surendran/3f413d591e4b2b876e033eeb9390e232ad4826ca}.

\leavevmode\vadjust pre{\hypertarget{ref-Tang2015Line}{}}%
Tang, Jian, Meng Qu, Mingzhe Wang, Ming Zhang, Jun Yan, and Qiaozhu Mei.
2015. {``{LINE}: {Large-scale Information Network Embedding}.''}
\emph{Proceedings of the 24th International Conference on World Wide
Web}, May, 1067--77. \url{https://doi.org/10.1145/2736277.2741093}.

\leavevmode\vadjust pre{\hypertarget{ref-Thurman2019Testing}{}}%
Thurman, Lindsey L., Allison K. Barner, Tiffany S. Garcia, and Tara
Chestnut. 2019. {``Testing the Link Between Species Interactions and
Co-Occurrence in a Trophic Network.''} \emph{Ecography} 0.
\url{https://doi.org/10.1111/ecog.04360}.

\leavevmode\vadjust pre{\hypertarget{ref-Torres2020Glee}{}}%
Torres, Leo, Kevin S Chan, and Tina Eliassi-Rad. 2020. {``{GLEE}:
{Geometric Laplacian Eigenmap Embedding}.''} \emph{Journal of Complex
Networks} 8 (2): cnaa007. \url{https://doi.org/10.1093/comnet/cnaa007}.

\leavevmode\vadjust pre{\hypertarget{ref-Turak2017Using}{}}%
Turak, Eren, James Brazill-Boast, Tim Cooney, Michael Drielsma, Jocelyn
DelaCruz, Gillian Dunkerley, Miguel Fernandez, et al. 2017. {``Using the
Essential Biodiversity Variables Framework to Measure Biodiversity
Change at National Scale.''} \emph{Biological Conservation},
{SI}:{Measures} of biodiversity, 213 (September): 264--71.
\url{https://doi.org/10.1016/j.biocon.2016.08.019}.

\leavevmode\vadjust pre{\hypertarget{ref-Wang2016Structural}{}}%
Wang, Daixin, Peng Cui, and Wenwu Zhu. 2016. {``Structural {Deep Network
Embedding}.''} In \emph{Proceedings of the 22nd {ACM SIGKDD
International Conference} on {Knowledge Discovery} and {Data Mining}},
1225--34. {San Francisco California USA}: {ACM}.
\url{https://doi.org/10.1145/2939672.2939753}.

\leavevmode\vadjust pre{\hypertarget{ref-Wang2021Joint}{}}%
Wang, Shangsi, Jesus Arroyo, Joshua T. Vogelstein, and Carey E. Priebe.
2021. {``Joint {Embedding} of {Graphs}.''} \emph{IEEE Transactions on
Pattern Analysis and Machine Intelligence} 43 (4): 1324--36.
\url{https://doi.org/10.1109/TPAMI.2019.2948619}.

\leavevmode\vadjust pre{\hypertarget{ref-Wardeh2021Predicting}{}}%
Wardeh, Maya, Matthew Baylis, and Marcus S. C. Blagrove. 2021.
{``Predicting Mammalian Hosts in Which Novel Coronaviruses Can Be
Generated.''} \emph{Nature Communications} 12 (1, 1): 780.
\url{https://doi.org/10.1038/s41467-021-21034-5}.

\leavevmode\vadjust pre{\hypertarget{ref-Weiskopf2022Increasing}{}}%
Weiskopf, Sarah R., Zuzana V. Harmáčková, Ciara G. Johnson, María
Cecilia Londoño-Murcia, Brian W. Miller, Bonnie J. E. Myers, Laura
Pereira, et al. 2022. {``Increasing the Uptake of Ecological Model
Results in Policy Decisions to Improve Biodiversity Outcomes.''}
\emph{Environmental Modelling \& Software} 149 (March): 105318.
\url{https://doi.org/10.1016/j.envsoft.2022.105318}.

\leavevmode\vadjust pre{\hypertarget{ref-Williams2000Simple}{}}%
Williams, Richard J., and Neo D. Martinez. 2000. {``Simple Rules Yield
Complex Food Webs.''} \emph{Nature} 404 (6774): 180--83.
\url{https://doi.org/10.1038/35004572}.

\leavevmode\vadjust pre{\hypertarget{ref-Wood2015Effects}{}}%
Wood, Spencer A., Roly Russell, Dieta Hanson, Richard J. Williams, and
Jennifer A. Dunne. 2015. {``Effects of Spatial Scale of Sampling on Food
Web Structure.''} \emph{Ecology and Evolution} 5 (17): 3769--82.
\url{https://doi.org/10.1002/ece3.1640}.

\leavevmode\vadjust pre{\hypertarget{ref-Wu2021Maximum}{}}%
Wu, David, David R. Palmer, and Daryl R. Deford. 2021. {``Maximum a
{Posteriori Inference} of {Random Dot Product Graphs} via {Conic
Programming}.''} {arXiv}. \url{http://arxiv.org/abs/2101.02180}.

\leavevmode\vadjust pre{\hypertarget{ref-Xu2021Understanding}{}}%
Xu, Mengjia. 2021. {``Understanding {Graph Embedding Methods} and {Their
Applications}.''} \emph{SIAM Review} 63 (4): 825--53.
\url{https://doi.org/10.1137/20M1386062}.

\leavevmode\vadjust pre{\hypertarget{ref-Yan2005Graph}{}}%
Yan, Shuicheng, Dong Xu, Benyu Zhang, and Hong-Jiang Zhang. 2005.
{``Graph Embedding: A General Framework for Dimensionality Reduction.''}
In \emph{2005 {IEEE Computer Society Conference} on {Computer Vision}
and {Pattern Recognition} ({CVPR}'05)}, 2:830--837 vol. 2.
\url{https://doi.org/10.1109/CVPR.2005.170}.

\leavevmode\vadjust pre{\hypertarget{ref-Young2007Random}{}}%
Young, Stephen J., and Edward R. Scheinerman. 2007. {``Random {Dot
Product Graph Models} for {Social Networks}.''} In \emph{Algorithms and
{Models} for the {Web-Graph}}, edited by Anthony Bonato and Fan R. K.
Chung, 138--49. Lecture {Notes} in {Computer Science}. {Berlin,
Heidelberg}: {Springer}.
\url{https://doi.org/10.1007/978-3-540-77004-6_11}.

\leavevmode\vadjust pre{\hypertarget{ref-Zhou2020Graph}{}}%
Zhou, Jie, Ganqu Cui, Shengding Hu, Zhengyan Zhang, Cheng Yang, Zhiyuan
Liu, Lifeng Wang, Changcheng Li, and Maosong Sun. 2020. {``Graph Neural
Networks: {A} Review of Methods and Applications.''} \emph{AI Open} 1
(January): 57--81. \url{https://doi.org/10.1016/j.aiopen.2021.01.001}.

\end{CSLReferences}

\end{document}

### 2023-09-07 index.tex

--- 2023-09-07 docs/_tex/index.tex
@@
 Banville \and Ceres Barros \and Dominique Caron \and Maxwell J.
-Farrell \and Marie-Josée Fortin \and Victoria Hemming \and Benjamin
-Mercier \and Laura J. Pollock \and Rogini Runghen \and Giulio V. Dalla
-Riva \and Timothée Poisot}
+Farrell \and Marie-Josée Fortin \and Benjamin Mercier \and Laura J.
+Pollock \and Rogini Runghen \and Giulio V. Dalla Riva \and Timothée
+Poisot}
 \date{}
@@
 \maketitle
-The ability to infer \emph{potential} interactions could serve as a
-significant breakthrough in our ability to conceptualize species
-interaction networks over large spatial scales (Hortal et al. 2015).
-Reliable inferences would not only boost our understanding of the
-structure of species interaction networks, but also increase the amount
-of information that can be used for biodiversity management. In a recent
-overview of the field of ecological network prediction, Strydom et al.
-(2021) identified two challenges of interest to the prediction of
-interactions at large scales. First, there is a relative scarcity of
-relevant data in most places globally -- which, due to the limitations
-in most predictive methods, restricts the ability to infer interactions
-to locations where it is least required (\emph{i.e.} regions where we
-already have interaction data) leaving us unable to make inference in
-data scarce regions (where we most need it); second, accurate predictors
-are important for accurate predictions, and the lack of methods that can
+\begin{abstract}
+\begin{itemize}
+\tightlist
+\item
+  Metawebs (networks of potential interactions within a species pool)
+  are a powerful abstraction to understand how large-scale species
+  interaction networks are structured.
+\item
+  Because metawebs are typically expressed at large spatial and
+  taxonomic scales, assembling them is a tedious and costly process;
+  predictive methods can help circumvent the limitations in data
+  deficiencies, by providing a first approximation of metawebs.''
+\item
+  One way to improve our ability to predict metawebs is to maximize
+  available information by using graph embeddings, as opposed to an
+  exhaustive list of species interactions. Graph embedding is an
+  emerging field in machine learning that holds great potential for
+  ecological problems.
+\item
+  Here, we outline how the challenges associated with inferring metawebs
+  line-up with the advantages of graph embeddings; followed by a
+  discussion as to how the choice of the species pool has consequences
+  on the reconstructed network, specifically as to the role of
+  human-made (or arbitrarily assigned) boundaries and how these may
+  influence ecological hypotheses.
+\end{itemize}
+\end{abstract}
+The ability to infer potential biotic interactions could serve as a
+significant breakthrough in our ability to conceptualize networks over
+large spatial scales (Hortal et al. 2015). Reliable inferences would not
+only boost our understanding of the structure of species interaction
+networks, but also increase the amount of information that can be used
+for biodiversity management. In a recent overview of the field of
+ecological network prediction, Strydom et al. (2021) identified two
+challenges of interest to the prediction of interactions at large
+scales. First, there is a relative scarcity of relevant data in most
+places globally -- which, due to the limitations in most predictive
+methods, restricts the ability to infer interactions to locations where
+it is least required (\emph{i.e.} regions where we already have
+interaction data) leaving us unable to make inference in data scarce
+regions (where we most need it); second, accurate predictors are
+important for accurate predictions, and the lack of methods that can
 leverage a small amount of \emph{accurate} data is a serious impediment
-to our predictive ability. In this contribution, we highlight the power
-of viewing (and constructing) metawebs as \emph{probabilistic} objects
-in the context of low-probability interactions, discuss how a family of
-machine learning tools (graph embeddings and transfer learning) can be
-used to overcome data limitations to metaweb inference, and highlight
-how the use of metawebs introduces important questions for the field of
-network ecology.
+to our predictive ability. In this contribution, we (i) highlight the
+power of viewing (and constructing) metawebs as \emph{probabilistic}
+objects in the context of low-probability interactions, (ii) discuss how
+a family of machine learning tools (graph embeddings and transfer
+learning) can be used to overcome data limitations to metaweb inference,
+and (iii) highlight how the use of metawebs introduces important
+questions for the field of network ecology.
 
@@
 However, inferring the potential interactions between these species
-still remains a challenge. And yet, because the metaweb represents the
-joint effect of functional, phylogenetic, and macroecological processes
-(Morales-Castilla et al. 2015; Carlson et al. 2022; Morales-Castilla et
-al. 2021), it holds valuable ecological information. Specifically, it
-represents the ``upper bounds'' on what the composition of the local
+still remains a challenge. And yet, the metaweb holds valuable
+ecological information: it represents the joint effect of functional,
+phylogenetic, and macroecological processes (Morales-Castilla et al.
+2015; Carlson et al. 2022; Morales-Castilla et al. 2021). Specifically,
+it represents the ``upper bounds'' on what the composition of the local
 networks, given a local species pool, can be (see \emph{e.g.} McLeod et
@@
 has been done for example for tree-galler-parasitoid systems (Gravel et
-al. 2018), fish trophic interactions (Albouy et al. 2019), tetrapod
-trophic interactions (J. Braga et al. 2019; O'Connor et al. 2020), and
-crop-pest networks (Grünig et al. 2020).
+al. 2018), fish trophic interactions (Albouy et al. 2019), terrestrial
+tetrapod trophic interactions (J. Braga et al. 2019; O'Connor et al.
+2020), and crop-pest networks (Grünig et al. 2020).
 
@@
 et al. 2015) and complexity (see \emph{e.g.} Galiana et al. 2022), than
-any of these local networks. These local networks (which capture the
+any of these local networks. Local networks (which capture the
 \(\alpha\) diversity of interactions) are a subset of the metaweb's
@@
 prevalent in networks than common or strong interactions (Csermely
-2004), compared to strong, persistent interactions; this is notably the
-case in food chains, wherein many weaker interactions are key to the
-stability of a system (Neutel, Heesterbeek, and de Ruiter 2002). In the
-light of these observations, we expect to see an over-representation of
-low-probability (hereafter rare) interactions under a model that
-accurately predicts interaction probabilities.
+2004); this is notably the case in food chains, wherein many weaker
+interactions are key to the stability of a system (Neutel, Heesterbeek,
+and de Ruiter 2002). In the light of these observations, we expect to
+see an over-representation of low-probability (hereafter rare)
+interactions under a model that accurately predicts interaction
+probabilities.
 
@@
 a specific network topology for link prediction (Gaucher, Klopp, and
-Robin 2021), but are able to work on generalizations of the network.
-These considerations emphasize why metaweb predictions should focus on
+Robin 2021), but are able to work on generalizations of the network that
+capture statistical processes giving it its structure. These
+considerations emphasize why metaweb predictions should focus on
 quantitative (preferentially probabilistic) predictions, and this should
@@
 Strydom et al. (2022) shows that t-SVD embedding is extremely robust to
-(and able to detect) the presence of false positives. In a sense, that
-most ecological interactions are elusive can call for a slightly
-different approach to sampling: once the common interactions are
-documented, the effort required in documenting each rare interaction
+(and able to detect) the presence of false positives. In a sense,
+because most ecological interactions are elusive, we should consider the
+direct consequences this has on sampling: once the common interactions
+are documented, the effort required in documenting each rare interaction
 will increase exponentially (Jordano 2016). Recent proposals in other
@@
 the original community (represented by the orange dashed arrows,
-\textbf{B}). Transfer learning (\textbf{D}) allows for the prediction
+\textbf{B}). Transfer learning (\textbf{D}) allows for the prediction of
 links (interactions) even when novel species (\textbf{C}) are included
-alongside the original community. This is achieved by learning using
-other relevant predictors (\emph{e.g.} traits) in conjunction with the
-known interactions to infer latent values (\textbf{E}). Ultimately this
-allows us to predict links (interactions) for species external from the
-original sample (blue dashed arrows) as well as missing within sample
-links (\textbf{F}). Within this context the predicted (and original)
-networks as well as the ecological predictors used (green boxes) are
-products that can be quantified through measurements in the field,
-whereas the embedded as well as imputed matrices (purple box) are
-representative of a decomposition of the interaction matrices onto the
-embedding space}
+alongside the original community. This is achieved with other
+ecologically relevant predictors (\emph{e.g.} traits) in conjunction
+with the known interactions to infer latent values (\textbf{E}).
+Ultimately this allows us to predict links (interactions) for species
+external from the original sample (blue dashed arrows) as well as
+missing within sample links (\textbf{F}). Within this context the
+predicted (and original) networks as well as the ecological predictors
+used (green boxes) are products that can be quantified through
+measurements in the field, whereas the embedded as well as imputed
+matrices (purple box) are representative of a decomposition of the
+interaction matrices onto the embedding space}
 
@@
 
-\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Box 1 - Graph Neural Networks}, colback=white, rightrule=.15mm, coltitle=black, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0, breakable, bottomtitle=1mm, titlerule=0mm, toptitle=1mm, arc=.35mm, toprule=.15mm, leftrule=.75mm, left=2mm, opacitybacktitle=0.6]
+\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Box 1 - Graph Neural Networks}, bottomtitle=1mm, colback=white, breakable, colbacktitle=quarto-callout-note-color!10!white, opacityback=0, left=2mm, arc=.35mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, leftrule=.75mm, rightrule=.15mm, titlerule=0mm, bottomrule=.15mm, toprule=.15mm, opacitybacktitle=0.6]
 
@@
 opposed to direct biotic interactions. Given the need to evaluate
-different methods on a problem-specific basis, the fact that a lot of
+different methods on a problem-specific basis, the fact that many
 methods have not been used on network problems is an opportunity for
@@
 applies to kernel/probabilistic PCA, which are variations on the more
-general method of SVD. Note further that tSNE has been included because
+general method of SVD. Note further that t-SNE has been included because
 it is frequently used to embed graphs, including of species
@@
 \endlastfoot
-tSNE & nodes & statistical divergence & Hinton and Roweis (2002) &
+t-SNE & nodes & statistical divergence & Hinton and Roweis (2002) &
 (Cieslak et al. 2020, species-environment responses \(^a\)) (Gibb et al.
@@
 at each rank, and visualize that using 39 ranks explains about 70\% of
-the variance in the empirical metaweb. This is a different information
-from the \(L_2\) loss (which is averaged across interactions), as it
-works on the eigenvalues of the embedding, and therefore captures
-higher-level features of the network. In panel \textbf{C}, we show
-positions of hosts and parasites on the first two dimensions of the left
-and right subspaces. Note that these values largely skew negative,
-because the first dimensions capture the coarse structure of the
-network: most pairs of species do not interact, and therefore have
-negative values. Finally in panel \textbf{D}, we show the predicted
-weight (\emph{i.e.} the result of the multiplication of the RDGP
-subspaces at a rank of 39) as a function of whether the interactions are
-observed, not-observed, or unknown due to lack of co-occurrence in the
-original dataset. This reveals that the observed interactions have
-higher predicted weights, although there is some overlap; the usual
-approach to identify potential interactions based on this information
-would be a thresholding analysis, which is outside the scope of this
-manuscript (and is done in the papers cited in this illustration).
-Because the values returned from RDPG are not bound to the unit
-interval, we performed a clamping of the weights to the unit space,
-showing a one-inflation in documented interactions, and a zero-inflation
-in other species pairs. This last figure shows that species pairs with
-no documented co-occurrence have weights that are not distinguishable
-from species pairs with no documented interactions; in other words,
-looking at the embedding, species that do not co-occur are not easily
-distinguished from species that do not interact. This suggests that (as
-befits a host-parasite model) the ability to interact is a strong
-predictor of co-occurrence.
+the variance in the empirical metaweb. This provides different
+information from the \(L_2\) loss (which is averaged across
+interactions), as it works on the eigenvalues of the embedding, and
+therefore captures higher-level features of the network. In panel
+\textbf{C}, we show positions of hosts and parasites on the first two
+dimensions of the left and right subspaces. Note that these values
+largely skew negative, because the first dimensions capture the coarse
+structure of the network: most pairs of species do not interact, and
+therefore have negative values. Finally in panel \textbf{D}, we show the
+predicted weight (\emph{i.e.} the result of the multiplication of the
+RDGP subspaces at a rank of 39) as a function of whether the
+interactions are observed, not-observed, or unknown due to lack of
+co-occurrence in the original dataset. This reveals that the observed
+interactions have higher predicted weights, although there is some
+overlap; the usual approach to identify potential interactions based on
+this information would be a thresholding analysis, which is outside the
+scope of this manuscript (and is done in the papers cited in this
+illustration). Because the values returned from RDPG are not bound to
+the unit interval, we performed a clamping of the weights to the unit
+space, showing a one-inflation in documented interactions, and a
+zero-inflation in other species pairs. Panel \textbf{D} specifically
+shows that species pairs with no documented co-occurrence have weights
+that are not distinguishable from species pairs with no documented
+interactions; in other words, looking at the embedding, species that do
+not co-occur are not easily distinguished from species that do not
+interact. This suggests that (as befits a host-parasite model) the
+ability to interact is a strong predictor of co-occurrence.
 
@@
 
-The results of Figure~\ref{fig-illustration-1} show that we can extract
-an embedding of the metaweb that captures enough variance to be
-relevant; specifically, this is true for both \(L_2\) loss (indicating
-that RDPG is able to capture pairwise processes) and the cumulative
-variance explained (indicating that RDPG is able to capture
-network-level structure). Therefore, in Figure~\ref{fig-illustration-2},
-we relate the values of latent variables for hosts to different
-ecologically-relevant data. In panel \textbf{A}, we show that host with
-a higher value on the first dimension have fewer parasites. This relates
-to the body size of hosts in the \emph{PanTHERIA} database (Jones et al.
-2009), as shown in panel \textbf{B}: interestingly, the position on the
-first axis is only weakly correlated to body mass of the host; this
-matches well established results showing that body size/mass is not
-always a direct predictor of parasite richness in terrestrial mammals
-(Morand and Poulin 1998), a result we observe in panel \textbf{C}.
-Finally, in panel \textbf{D}, we can see how different taxonomic
-families occupy different positions on the first axis, with \emph{e.g.}
-Sciuridae being biased towards higher values. These results show how we
-can look for ecological informations in the output of network
-embeddings, which can further be refined into the selection of
+In Figure~\ref{fig-illustration-2}, we relate the values of latent
+variables for hosts to different ecologically-relevant data; we can
+perform this additional step, because the results presented in
+Figure~\ref{fig-illustration-1} show that we can extract an embedding of
+the metaweb that captures enough variance to be relevant. Importantly,
+this is true for both \(L_2\) loss (indicating that RDPG is able to
+capture pairwise processes) and the cumulative variance explained
+(indicating that RDPG is able to capture network-level structure), which
+suggests that these approaches may allow to predict interactions
+\emph{and} network structure. In panel \textbf{A}, we show that host
+with a higher value on the first dimension have fewer parasites. This
+relates to the body size of hosts in the \emph{PanTHERIA} database
+(Jones et al. 2009), as shown in panel \textbf{B}: interestingly, the
+position on the first axis is only weakly correlated to body mass of the
+host; this matches well established results showing that body size/mass
+is not always a direct predictor of parasite richness in terrestrial
+mammals (Morand and Poulin 1998), a result we observe in panel
+\textbf{C}. Finally, in panel \textbf{D}, we can see how different
+taxonomic families occupy different positions on the first axis, with
+\emph{e.g.} Sciuridae being biased towards higher values. These results
+show how we can look for ecological informations in the output of
+network embeddings, which can further be refined into the selection of
 predictors for transfer learning.
@@
 interwoven, families of problems. In this section, we outline three that
-we think are particularly important, and can discuss how they may
+we think are particularly important, and discuss how they may be
 addressed with subsequent data analysis or simulations, and how they
@@
 If the initial metaweb is too narrow in scope, notably from a taxonomic
-point of view, the chances of finding another area with enough related
-species (through phylogenetic relatedness or similarity of functional
-traits) to make a reliable inference decreases. This is because transfer
-requires similarity (Figure~\ref{fig-embedding}). A diagnostic for the
-lack of similar species would likely be large confidence intervals
-during estimation of the values in the low-rank space. In other words,
-the representation of the original graph is difficult to transfer to the
-new problem. Alternatively, if the initial metaweb is too large
-(taxonomically), then the resulting embeddings would need to represent
-interactions between taxonomic groups that are not present in the new
-location. This would lead to a much higher variance in the starting
-dataset, and to under-dispersion in the target dataset, resulting in the
-potential under or over estimation of the strength of new predicted
-interactions. Llewelyn et al. (2022) provided compelling evidence for
-these situations by showing that, even at small spatial scales, the
-transfer of information about interactions becomes more challenging when
-areas rich with endemic species are considered. The lack of well
-documented metawebs is currently preventing the development of more
-concrete guidelines. The question of phylogenetic relatedness and
-distribution is notably relevant if the metaweb is assembled in an area
-with mostly endemic species (\emph{e.g.} a system that has undergone
-recent radiation or that has remained in isolation for a long period of
-time might not have an analogous system with which to draw knowledge
-from), and as with every predictive algorithm, there is room for the
-application of our best ecological judgement. Because this problem
-relates to distribution of species in the geographic or phylogenetic
-space, it can certainly be approached through assessing the performance
-of embedding transfer in simulated starting/target species pools.
+point of view, the chances decrease of finding another area with enough
+related species (through phylogenetic relatedness or similarity of
+functional traits) to make a reliable inference. This is because
+transfer requires similarity (Figure~\ref{fig-embedding}). A diagnostic
+for the lack of similar species would likely be large confidence
+intervals during estimation of the values in the low-rank space. In
+other words, the representation of the original graph is difficult to
+transfer to the new problem. Alternatively, if the initial metaweb is
+too large (taxonomically), then the resulting embeddings would need to
+represent interactions between taxonomic groups that are not present in
+the new location. This would lead to a much higher variance in the
+starting dataset, and to under-dispersion in the target dataset,
+resulting in the potential under or over estimation of the strength of
+new predicted interactions. Llewelyn et al. (2022) provided compelling
+evidence for these situations by showing that, even at small spatial
+scales, the transfer of information about interactions becomes more
+challenging when areas rich with endemic species are considered. The
+lack of well documented metawebs is currently preventing the development
+of more concrete guidelines. The question of phylogenetic relatedness
+and distribution is notably relevant if the metaweb is assembled in an
+area with mostly endemic species (\emph{e.g.} a system that has
+undergone recent radiation or that has remained in isolation for a long
+period of time might not have an analogous system with which to draw
+knowledge from), and as with every predictive algorithm, there is room
+for the application of our best ecological judgement. Because this
+problem relates to distribution of species in the geographic or
+phylogenetic space, it can certainly be approached through assessing the
+performance of embedding transfer in simulated starting/target species
+pools.
 
@@
 historical and contemporary biases that acted on these data, both
-because they shaped the ecological processes generating them, and the
-global processes leading to their measurement and publication. For a
-domain as vast as species interaction networks, these biases exist at
-multiple scales along the way, and a challenge for prediction is not
-only to develop (or adopt) new quantitative tools, but to assess the
-behavior of these tools in the proper context.
+because they shaped the ecological processes generating them (see Box
+2), and the global processes leading to their measurement and
+publication. For a domain as vast as species interaction networks, these
+biases exist at multiple scales along the way, and a challenge for
+prediction is not only to develop (or adopt) new quantitative tools, but
+to assess the behavior of these tools in the proper context.
 
@@
 Although promising, the application of embeddings to metaweb prediction
-will require to address several challenges. First, there is a need to
-understand how to define a metaweb as a single, cohesive, unit of
-ecological organisation. This is likely to admit very different answers
-based on the specific taxonomic group, temporal and spatial resolution,
-and question being investigated. Second, there is a need to understand
-the scale at which these predictions are relevant. Although we have
-documented many cases of using embedding to fill gaps in the metaweb,
-these techniques can likely be brought into a spatial (and possibly
-temporal) context. The validation of these predictions will have to
-proceed jointly with empirical sampling of interactions, but also with
-the design of downsampling methods. Finally, there is a need for a
-greater understanding of how biases in the data propagate to the
-predictions. Because the volume of metawebs is currently low, and
-because graph embeddings have not been commonly applied, we anticipate
-that this discussion will take place organically in the coming years.
-
-\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Box 2 - Minding legacies shaping ecological datasets}, colback=white, rightrule=.15mm, coltitle=black, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0, breakable, bottomtitle=1mm, titlerule=0mm, toptitle=1mm, arc=.35mm, toprule=.15mm, leftrule=.75mm, left=2mm, opacitybacktitle=0.6]
+still involved several challenges. First, there is a need to understand
+how to define a metaweb as a single, cohesive, unit of ecological
+organisation. This is likely to have very different answers based on the
+specific taxonomic group, temporal and spatial resolution, and question
+being investigated. Second, there is a need to understand the scale at
+which these predictions are relevant. Although we have documented many
+cases of using embedding to fill gaps in the metaweb, these techniques
+can likely be brought into a spatial (and possibly temporal) context.
+The validation of these predictions will have to proceed jointly with
+empirical sampling of interactions, but also with the design of
+downsampling methods. Finally, there is a need for a greater
+understanding of how biases in the data propagate to the predictions.
+Because the volume of metawebs is currently low, and because graph
+embeddings have not been commonly applied, we anticipate that this
+discussion will take place organically in the coming years.
+
+\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Box 2 - Minding legacies shaping ecological datasets}, bottomtitle=1mm, colback=white, breakable, colbacktitle=quarto-callout-note-color!10!white, opacityback=0, left=2mm, arc=.35mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, leftrule=.75mm, rightrule=.15mm, titlerule=0mm, bottomrule=.15mm, toprule=.15mm, opacitybacktitle=0.6]
 
 In large parts of the world, boundaries that delineate geographic
-regions are merely a reflection the legacy of settler colonialism, which
-drives global disparity in capacity to collect and publish ecological
-data. Applying any embedding to biased data does not debias them, but
-rather embeds these biases, propagating them to the models using
-embeddings to make predictions. Furthermore, the use of ecological data
-itself is not an apolitical act (Nost and Goldstein 2021): data
-infrastructures tend to be designed to answer questions within national
-boundaries (therefore placing contingencies on what is available to be
-embedded), their use often drawing upon, and reinforcing, territorial
-statecraft (see \emph{e.g.} Barrett 2005). As per Machen and Nost
-(2021), these biases are particularly important to consider when
-knowledge generated algorithmically is used to supplement or replace
-human decision-making, especially for governance (\emph{e.g.} enacting
-conservation decisions on the basis of model prediction). As information
-on networks is increasingly leveraged for conservation actions (see
-\emph{e.g.} Eero et al. 2021; Naman et al. 2022; Stier et al. 2017), the
-need to appraise and correct biases that are unwittingly propagated to
-algorithms when embedded from the original data is immense. These
-considerations are even more urgent in the specific context of
-biodiversity data. Long-term colonial legacies still shape taxonomic
-composition to this day (Lenzner et al. 2022; Raja 2022), and much
-shorter-term changes in taxonomic and genetic richness of wildlife
-emerged through environmental racism (Schmidt and Garroway 2022). Thus,
-the set of species found at a specific location is not only as the
-result of a response to ecological processes separate from human
-influence, but also the result of human-environment interaction as well
-as the result legislative/political histories.
+regions are a legacy of settler colonialism, which drives global
+disparity in capacity to collect and publish ecological data. Applying
+any embedding to biased data does not debias them, but rather embeds
+these biases, propagating them to the models using embeddings to make
+predictions. Furthermore, the use of ecological data itself is not an
+apolitical act (Nost and Goldstein 2021): data infrastructures tend to
+be designed to answer questions within national boundaries (therefore
+placing contingencies on what is available to be embedded), their use
+often drawing upon, and reinforcing, territorial statecraft (see
+\emph{e.g.} Barrett 2005). As per Machen and Nost (2021), these biases
+are particularly important to consider when knowledge generated
+algorithmically is used to supplement or replace human decision-making,
+especially for governance (\emph{e.g.} enacting conservation decisions
+on the basis of model prediction). As information on networks is
+increasingly leveraged for conservation actions (see \emph{e.g.} Eero et
+al. 2021; Naman et al. 2022; Stier et al. 2017), the need to appraise
+and correct biases that are unwittingly propagated to algorithms when
+embedded from the original data is immense. These considerations are
+even more urgent in the specific context of biodiversity data. Long-term
+colonial legacies still shape taxonomic composition to this day (Lenzner
+et al. 2022; Raja 2022), and much shorter-term changes in taxonomic and
+genetic richness of wildlife emerged through environmental racism
+(Schmidt and Garroway 2022). Thus, the set of species found at a
+specific location is not only as the result of a response to ecological
+processes separate from human influence, but also the result of
+human-environment interaction as well as the results of
+legislative/political histories.
 
@@
 Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak
-nations. TP, TS, DC, and LP received funding from the Canadian Institute
-for Ecology \& Evolution. FB is funded by the Institute for Data
-Valorization (IVADO). TS, SB, and TP are funded by a donation from the
-Courtois Foundation. CB was awarded a Mitacs Elevate Fellowship no.
-IT12391, in partnership with fRI Research, and also acknowledges funding
-from Alberta Innovates and the Forest Resources Improvement Association
-of Alberta. M-JF acknowledges funding from NSERC Discovery Grant and
+nations. We thank Victoria hemming for feedback on this manuscript. TP,
+TS, DC, and LP received funding from the Canadian Institute for Ecology
+\& Evolution. FB is funded by the Institute for Data Valorization
+(IVADO). TS, SB, and TP are funded by a donation from the Courtois
+Foundation. M-JF acknowledges funding from NSERC Discovery Grant and
 NSERC CRC. RR is funded by New Zealand's Biological Heritage Ngā Koiora
@@
 
-\textbf{Authors' contributions:} TS, and TP conceived the ideas
-discussed in the manuscript. All authors contributed to writing and
-editing the manuscript.
-
-\textbf{Data availability:} There is no data associated with this
+\textbf{Authors' contributions:} TS and TP conceived the ideas discussed
+in the manuscript. All authors contributed to writing and editing the
 manuscript.
+
+\textbf{Data availability:} The code to collect the data use in figures
+is distributed as part of the Supplementary Material.
 

### 2023-09-07 docs/_tex/index.tex
ready

@@
 \documentclass[
-  letterpaper,
-  DIV=11,
-  numbers=noendperiod]{scrartcl}
+]{article}
 
@@
     % xetex/luatex font selection
+  \setmainfont[]{IBM Plex Serif}
+  \setsansfont[]{IBM Plex Sans}
+  \setmonofont[]{IBM Plex Mono}
 \fi
@@
 
-\KOMAoption{captions}{tableheading}
 \makeatletter
@@
 species interaction networks despite data limitations}
-\author{Tanya Strydom \and Salomé Bouskila \and Francis
-Banville \and Ceres Barros \and Dominique Caron \and Maxwell J.
-Farrell \and Marie-Josée Fortin \and Victoria Hemming \and Benjamin
-Mercier \and Laura J. Pollock \and Rogini Runghen \and Giulio V. Dalla
-Riva \and Timothée Poisot}
+\author{Tanya Strydom %
+%
+\textsuperscript{%
+1,%
+2%
+}%
+; Salomé Bouskila %
+%
+\textsuperscript{%
+%
+1%
+}%
+; Francis Banville %
+%
+\textsuperscript{%
+1,2,%
+3%
+}%
+; Ceres Barros %
+%
+\textsuperscript{%
+%
+4%
+}%
+; Dominique Caron %
+%
+\textsuperscript{%
+5,%
+2%
+}%
+; Maxwell J. Farrell %
+%
+\textsuperscript{%
+%
+6%
+}%
+; Marie-Josée Fortin %
+%
+\textsuperscript{%
+%
+6%
+}%
+; Benjamin Mercier %
+%
+\textsuperscript{%
+3,%
+2%
+}%
+; Laura J. Pollock %
+%
+\textsuperscript{%
+5,%
+2%
+}%
+; Rogini Runghen %
+%
+\textsuperscript{%
+%
+7%
+}%
+; Giulio V. Dalla Riva %
+%
+\textsuperscript{%
+%
+7%
+}%
+; Timothée Poisot %
+%
+\textsuperscript{%
+1,%
+2%
+}%
+}
 \date{}
 
+\usepackage{setspace}
+\usepackage[left,pagewise]{lineno}
+\usepackage[letterpaper]{geometry}
+
+\usepackage[nolists,noheads,markers]{endfloat}
+\geometry{margin=2.5cm}
+
 \begin{document}
-\maketitle
-The ability to infer \emph{potential} interactions could serve as a
-significant breakthrough in our ability to conceptualize species
-interaction networks over large spatial scales (Hortal et al. 2015).
-Reliable inferences would not only boost our understanding of the
-structure of species interaction networks, but also increase the amount
-of information that can be used for biodiversity management. In a recent
-overview of the field of ecological network prediction, Strydom et al.
-(2021) identified two challenges of interest to the prediction of
-interactions at large scales. First, there is a relative scarcity of
-relevant data in most places globally -- which, due to the limitations
-in most predictive methods, restricts the ability to infer interactions
-to locations where it is least required (\emph{i.e.} regions where we
-already have interaction data) leaving us unable to make inference in
-data scarce regions (where we most need it); second, accurate predictors
-are important for accurate predictions, and the lack of methods that can
+
+\thispagestyle{empty}
+{\bfseries\sffamily\Large Graph embedding and transfer learning can help
+predict potential species interaction networks despite data limitations}
+\vfil
+Tanya Strydom %
+%
+\textsuperscript{%
+1,%
+2%
+}%
+; Salomé Bouskila %
+%
+\textsuperscript{%
+%
+1%
+}%
+; Francis Banville %
+%
+\textsuperscript{%
+1,2,%
+3%
+}%
+; Ceres Barros %
+%
+\textsuperscript{%
+%
+4%
+}%
+; Dominique Caron %
+%
+\textsuperscript{%
+5,%
+2%
+}%
+; Maxwell J. Farrell %
+%
+\textsuperscript{%
+%
+6%
+}%
+; Marie-Josée Fortin %
+%
+\textsuperscript{%
+%
+6%
+}%
+; Benjamin Mercier %
+%
+\textsuperscript{%
+3,%
+2%
+}%
+; Laura J. Pollock %
+%
+\textsuperscript{%
+5,%
+2%
+}%
+; Rogini Runghen %
+%
+\textsuperscript{%
+%
+7%
+}%
+; Giulio V. Dalla Riva %
+%
+\textsuperscript{%
+%
+7%
+}%
+; Timothée Poisot %
+%
+\textsuperscript{%
+1,%
+2%
+}%
+
+\vfil
+{\small
+\textbf{Abstract:} \begin{itemize}
+\tightlist
+\item
+  Metawebs (networks of potential interactions within a species pool)
+  are a powerful abstraction to understand how large-scale species
+  interaction networks are structured.
+\item
+  Because metawebs are typically expressed at large spatial and
+  taxonomic scales, assembling them is a tedious and costly process;
+  predictive methods can help circumvent the limitations in data
+  deficiencies, by providing a first approximation of metawebs.''
+\item
+  One way to improve our ability to predict metawebs is to maximize
+  available information by using graph embeddings, as opposed to an
+  exhaustive list of species interactions. Graph embedding is an
+  emerging field in machine learning that holds great potential for
+  ecological problems.
+\item
+  Here, we outline how the challenges associated with inferring metawebs
+  line-up with the advantages of graph embeddings; followed by a
+  discussion as to how the choice of the species pool has consequences
+  on the reconstructed network, specifically as to the role of
+  human-made (or arbitrarily assigned) boundaries and how these may
+  influence ecological hypotheses.
+\end{itemize}
+\vfil
+}
+\clearpage
+\setcounter{page}{1}
+\doublespacing
+\linenumbers
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+The ability to infer potential biotic interactions could serve as a
+significant breakthrough in our ability to conceptualize networks over
+large spatial scales (Hortal et al., 2015). Reliable inferences would
+not only boost our understanding of the structure of species interaction
+networks, but also increase the amount of information that can be used
+for biodiversity management. In a recent overview of the field of
+ecological network prediction, Strydom, Catchen, et al. (2021)
+identified two challenges of interest to the prediction of interactions
+at large scales. First, there is a relative scarcity of relevant data in
+most places globally -- which, due to the limitations in most predictive
+methods, restricts the ability to infer interactions to locations where
+it is least required (\emph{i.e.} regions where we already have
+interaction data) leaving us unable to make inference in data scarce
+regions (where we most need it); second, accurate predictors are
+important for accurate predictions, and the lack of methods that can
 leverage a small amount of \emph{accurate} data is a serious impediment
-to our predictive ability. In this contribution, we highlight the power
-of viewing (and constructing) metawebs as \emph{probabilistic} objects
-in the context of low-probability interactions, discuss how a family of
-machine learning tools (graph embeddings and transfer learning) can be
-used to overcome data limitations to metaweb inference, and highlight
-how the use of metawebs introduces important questions for the field of
-network ecology.
+to our predictive ability. In this contribution, we (i) highlight the
+power of viewing (and constructing) metawebs as \emph{probabilistic}
+objects in the context of low-probability interactions, (ii) discuss how
+a family of machine learning tools (graph embeddings and transfer
+learning) can be used to overcome data limitations to metaweb inference,
+and (iii) highlight how the use of metawebs introduces important
+questions for the field of network ecology.
 
@@
 However, inferring the potential interactions between these species
-still remains a challenge. And yet, because the metaweb represents the
-joint effect of functional, phylogenetic, and macroecological processes
-(Morales-Castilla et al. 2015; Carlson et al. 2022; Morales-Castilla et
-al. 2021), it holds valuable ecological information. Specifically, it
-represents the ``upper bounds'' on what the composition of the local
-networks, given a local species pool, can be (see \emph{e.g.} McLeod et
-al. 2021); this information can help evaluate the ability of ecological
-assemblages to withstand the effects of, for example, climate change
-(Fricke et al. 2022). These local networks may be reconstructed given an
-appropriate knowledge of local species composition and provide
-information on the structure of networks at finer spatial scales. This
-has been done for example for tree-galler-parasitoid systems (Gravel et
-al. 2018), fish trophic interactions (Albouy et al. 2019), tetrapod
-trophic interactions (J. Braga et al. 2019; O'Connor et al. 2020), and
-crop-pest networks (Grünig et al. 2020).
+still remains a challenge. And yet, the metaweb holds valuable
+ecological information: it represents the joint effect of functional,
+phylogenetic, and macroecological processes (Carlson et al., 2022;
+Morales-Castilla et al., 2015; Morales-Castilla et al., 2021).
+Specifically, it represents the ``upper bounds'' on what the composition
+of the local networks, given a local species pool, can be (see
+\emph{e.g.} McLeod et al., 2021); this information can help evaluate the
+ability of ecological assemblages to withstand the effects of, for
+example, climate change (Fricke et al., 2022). These local networks may
+be reconstructed given an appropriate knowledge of local species
+composition and provide information on the structure of networks at
+finer spatial scales. This has been done for example for
+tree-galler-parasitoid systems (Gravel et al., 2018), fish trophic
+interactions (Albouy et al., 2019), terrestrial tetrapod trophic
+interactions (J. Braga et al., 2019; O'Connor et al., 2020), and
+crop-pest networks (Grünig et al., 2020).
 
@@
 structure, notably by having a larger connectance (see \emph{e.g.} Wood
-et al. 2015) and complexity (see \emph{e.g.} Galiana et al. 2022), than
-any of these local networks. These local networks (which capture the
+et al., 2015) and complexity (see \emph{e.g.} Galiana et al., 2022),
+than any of these local networks. Local networks (which capture the
 \(\alpha\) diversity of interactions) are a subset of the metaweb's
 species and its realized interactions, and have been called ``metaweb
-realizations'' (Poisot, Stouffer, and Gravel 2015). Differences between
-local networks and their metawebs are due to chance, species abundance
-and co-occurrence, local environmental conditions, and local
-distribution of functional traits, among others. Specifically, although
-co-occurrence can be driven by interactions (Cazelles et al. 2016),
-co-occurrence alone is not a predictor of interactions (Blanchet,
-Cazelles, and Gravel 2020; Thurman et al. 2019), and therefore the lack
-of co-occurrence cannot be used to infer the lack of a feasible
-interaction. Yet, recent results by Saravia et al. (2021) strongly
-suggested that local (metaweb) realizations only respond weakly to local
-conditions: instead, they reflect constraints inherited by the structure
-of their metaweb. This sets up the core goal of predictive network
-ecology as the prediction of metaweb structure, as it is required to
-accurately produce downscaled, local predictions.
+realizations'' (Poisot et al., 2015). Differences between local networks
+and their metawebs are due to chance, species abundance and
+co-occurrence, local environmental conditions, and local distribution of
+functional traits, among others. Specifically, although co-occurrence
+can be driven by interactions (Cazelles et al., 2016), co-occurrence
+alone is not a predictor of interactions (Blanchet et al., 2020; Thurman
+et al., 2019), and therefore the lack of co-occurrence cannot be used to
+infer the lack of a feasible interaction. Yet, recent results by Saravia
+et al. (2021) strongly suggested that local (metaweb) realizations only
+respond weakly to local conditions: instead, they reflect constraints
+inherited by the structure of their metaweb. This sets up the core goal
+of predictive network ecology as the prediction of metaweb structure, as
+it is required to accurately produce downscaled, local predictions.
 
@@
 Treating interactions as probabilistic (as opposed to binary) events is
-a more nuanced and realistic way to represent them. Dallas, Park, and
-Drake (2017) suggested that most interactions (links) in ecological
-networks are cryptic, \emph{i.e.} uncommon or hard to observe. This
-argument echoes Jordano (2016): sampling ecological interactions is
-difficult because it requires first the joint observation of two
-species, and then the observation of their interaction. In addition, it
-is generally expected that weak or rare interactions will be more
-prevalent in networks than common or strong interactions (Csermely
-2004), compared to strong, persistent interactions; this is notably the
-case in food chains, wherein many weaker interactions are key to the
-stability of a system (Neutel, Heesterbeek, and de Ruiter 2002). In the
-light of these observations, we expect to see an over-representation of
-low-probability (hereafter rare) interactions under a model that
-accurately predicts interaction probabilities.
+a more nuanced and realistic way to represent them. Dallas et al. (2017)
+suggested that most interactions (links) in ecological networks are
+cryptic, \emph{i.e.} uncommon or hard to observe. This argument echoes
+Jordano (2016): sampling ecological interactions is difficult because it
+requires first the joint observation of two species, and then the
+observation of their interaction. In addition, it is generally expected
+that weak or rare interactions will be more prevalent in networks than
+common or strong interactions (Csermely, 2004); this is notably the case
+in food chains, wherein many weaker interactions are key to the
+stability of a system (Neutel et al., 2002). In the light of these
+observations, we expect to see an over-representation of low-probability
+(hereafter rare) interactions under a model that accurately predicts
+interaction probabilities.
 
@@
 towards \emph{probabilistic} metawebs, by representing interactions as
-Bernoulli events (see \emph{e.g.} Poisot et al. 2016), offers the
+Bernoulli events (see \emph{e.g.} Poisot et al., 2016), offers the
 opportunity to weigh these rare interactions appropriately. The inherent
@@
 documented instances of food webs undergoing rapid collapse/recovery
-cycles over short periods of time (\emph{e.g.} Pedersen et al. 2017).
+cycles over short periods of time (\emph{e.g.} Pedersen et al., 2017).
 Furthermore, because the structure of the metaweb cannot be known in
 advance, it is important to rely on predictive tools that do not assume
-a specific network topology for link prediction (Gaucher, Klopp, and
-Robin 2021), but are able to work on generalizations of the network.
-These considerations emphasize why metaweb predictions should focus on
-quantitative (preferentially probabilistic) predictions, and this should
-constrain the suite of models that are appropriate for prediction.
-Binary classifiers based on probabilities have an extremely robust
-methodology to validate them, and this applies naturally to the
-prediction of interactions (Poisot 2023).
+a specific network topology for link prediction (Gaucher et al., 2021),
+but are able to work on generalizations of the network that capture
+statistical processes giving it its structure. These considerations
+emphasize why metaweb predictions should focus on quantitative
+(preferentially probabilistic) predictions, and this should constrain
+the suite of models that are appropriate for prediction. Binary
+classifiers based on probabilities have an extremely robust methodology
+to validate them, and this applies naturally to the prediction of
+interactions (Poisot, 2023).
 
@@
 all potential (feasible) interactions, which is then filtered for a
-given application (Morales-Castilla et al. 2015). It is therefore
+given application (Morales-Castilla et al., 2015). It is therefore
 important to separate the interactions that happen ``almost surely''
@@
 \emph{e.g.} trait mis-match), and interactions with a probability that
-lays somewhere in between (Catchen et al. 2023). Although metawebs can
+lays somewhere in between (Catchen et al., 2023). Although metawebs can
 (and in practice likely do) include false positives, these are
@@
 Strydom et al. (2022) shows that t-SVD embedding is extremely robust to
-(and able to detect) the presence of false positives. In a sense, that
-most ecological interactions are elusive can call for a slightly
-different approach to sampling: once the common interactions are
-documented, the effort required in documenting each rare interaction
-will increase exponentially (Jordano 2016). Recent proposals in other
+(and able to detect) the presence of false positives. In a sense,
+because most ecological interactions are elusive, we should consider the
+direct consequences this has on sampling: once the common interactions
+are documented, the effort required in documenting each rare interaction
+will increase exponentially (Jordano, 2016). Recent proposals in other
 fields relying on machine learning approaches emphasize the idea that
@@
 approximate the process generating the data, can also act as data
-generators (Hoffmann et al. 2019). High quality observational data can
+generators (Hoffmann et al., 2019). High quality observational data can
 be used to infer core rules underpinning network structure, and be
@@
 on them, thereby increasing the volume of information available for
-analysis. Indeed, Strydom et al. (2021) suggested that knowing the
-metaweb may render the prediction of local networks easier, because it
-fixes an ``upper bound'' on which interactions can exist. In this
+analysis. Indeed, Strydom, Catchen, et al. (2021) suggested that knowing
+the metaweb may render the prediction of local networks easier, because
+it fixes an ``upper bound'' on which interactions can exist. In this
 context, a probabilistic metaweb represents an aggregation of
@@
 is usually hard to obtain yet has possibly the most potential to boost
-our predictive ability of local networks (Bartomeus 2013; Bartomeus et
-al. 2016). This would represent a departure from simple rules expressed
-at the network scale (\emph{e.g.} Williams and Martinez 2000) to a view
+our predictive ability of local networks (Bartomeus, 2013; Bartomeus et
+al., 2016). This would represent a departure from simple rules expressed
+at the network scale (\emph{e.g.} Williams \& Martinez, 2000) to a view
 of network prediction based on learning the rules that underpin
-interactions \emph{and} their variability (Anubhav Gupta, Furrer, and
-Petchey 2022).
+interactions \emph{and} their variability (Gupta et al., 2022).
 
@@
 machine learning techniques, whose main task is to learn a mapping
-function from a discrete graph to a continuous domain (Arsov and Mirceva
-2019; Chami et al. 2022). Their main goal is to learn a low dimensional
+function from a discrete graph to a continuous domain (Arsov \& Mirceva,
+2019; Chami et al., 2022). Their main goal is to learn a low dimensional
 vector representation of the graph (embeddings), such that its key
 properties (\emph{e.g.} local or global structures) are retained in the
-embedding space (Yan et al. 2005). The embedding space may, but will not
-necessarily, have lower dimensionality than the graph. Ecological
+embedding space (Yan et al., 2005). The embedding space may, but will
+not necessarily, have lower dimensionality than the graph. Ecological
 networks are promising candidates for the routine application of
 embeddings, as they tend to possess a shared structural backbone (see
-\emph{e.g.} Bramon Mora et al. 2018), which hints at structural
+\emph{e.g.} Bramon Mora et al., 2018), which hints at structural
 invariants in empirical data. Assuming that these structural invariants
@@
 Rather than directly predicting biological rules (see \emph{e.g.}
-Pichler et al. 2020 for an overview), which may be confounded by the
+Pichler et al., 2020 for an overview), which may be confounded by the
 sparse nature of graph data, learning embeddings works in the
@@
 represented by some graph embeddings {[}Random dot product graphs
-(RDPG); see Dalla Riva and Stouffer (2016){]}. In a recent publication,
+(RDPG); see Dalla Riva \& Stouffer (2016){]}. In a recent publication,
 Strydom et al. (2022) have used an embedding (based on RDPG) to project
@@
 Ecological networks are inherently low-dimensional objects, and can be
-adequately represented with less than ten dimensions (M. P. Braga et al.
-2021; Eklöf et al. 2013; J. Braga et al. 2019). Simulation results by
-Botella et al. (2022) suggested that there is no dominant method to
+adequately represented with less than ten dimensions (J. Braga et al.,
+2019; M. P. Braga et al., 2021; Eklöf et al., 2013). Simulation results
+by Botella et al. (2022) suggested that there is no dominant method to
 identify architectural similarities between networks: multiple
@@
 graph embedding, wherein different embedding algorithms yield different
-network embeddings (Goyal and Ferrara 2018), calling for a careful
+network embeddings (Goyal \& Ferrara, 2018), calling for a careful
 selection of the problem-specific approach to use. Additionally,
@@
 (\emph{i.e.} emergent properties). Nevertheless, some graph embedding
-techniques (like RDPG, see \emph{e.g.} Wu, Palmer, and Deford 2021) will
-provide high-quality node-level embeddings while also preserving network
+techniques (like RDPG, see \emph{e.g.} Wu et al., 2021) will provide
+high-quality node-level embeddings while also preserving network
 structure.
 
-\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Box 1 - Graph Neural Networks}, colback=white, rightrule=.15mm, coltitle=black, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0, breakable, bottomtitle=1mm, titlerule=0mm, toptitle=1mm, arc=.35mm, toprule=.15mm, leftrule=.75mm, left=2mm, opacitybacktitle=0.6]
+\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colback=white, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, titlerule=0mm, opacityback=0, rightrule=.15mm, bottomtitle=1mm, left=2mm, bottomrule=.15mm, breakable, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Box 1 - Graph Neural Networks}, toptitle=1mm, arc=.35mm, toprule=.15mm, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white]
 
@@
 belong to the family of deep learning methods, which has its own set of
-practices (see \emph{e.g.} Goodfellow, Bengio, and Courville 2016). An
-important issue with methods based on deep learning is that, because
-their parameter space is immense, the sample size of the data fed into
-them must be similarly large (typically thousands of instances). This is
-a requirement for the model to converge correctly during training, but
+practices (see \emph{e.g.} Goodfellow et al., 2016). An important issue
+with methods based on deep learning is that, because their parameter
+space is immense, the sample size of the data fed into them must be
+similarly large (typically thousands of instances). This is a
+requirement for the model to converge correctly during training, but
 this assumption is unlikely to be met given the size of datasets
@@
 challenges related to their shallow structure, and concerns related to
-scalability (see Atika Gupta, Matta, and Pant 2021 for a review), which
-are mostly absent from the methods listed in Table~\ref{tbl-methods}.
-Assuming that the uptake of next-generation biomonitoring techniques
-does indeed deliver larger datasets on species interactions (Bohan et
-al. 2017), there is nevertheless the potential for GNN to become an
-applicable embedding/predictive technique in the coming years.
+scalability (see Gupta et al., 2021 for a review), which are mostly
+absent from the methods listed in Table~\ref{tbl-methods}. Assuming that
+the uptake of next-generation biomonitoring techniques does indeed
+deliver larger datasets on species interactions (Bohan et al., 2017),
+there is nevertheless the potential for GNN to become an applicable
+embedding/predictive technique in the coming years.
 
@@
 Graph embeddings \emph{can} serve as a dimensionality reduction method.
-For example, RDPG (Strydom et al. 2022) and t-SVD {[}truncated Singular
+For example, RDPG (Strydom et al., 2022) and t-SVD {[}truncated Singular
 Value Decomposition; Poisot et al. (2021){]} typically embed networks
@@
 has as many dimensions as species, and as many informative dimensions as
-trophically unique species; Strydom, Dalla Riva, and Poisot (2021){]}.
+trophically unique species; Strydom, Dalla Riva, et al. (2021){]}.
 However, this is not necessarily the case -- indeed, one may perform a
@@
 embedding; Maaten (2009){]}. There are many dimensionality reductions
-(Anowar, Sadaoui, and Selim 2021) that can be applied to an embedded
-network should the need for dimensionality reduction (for example for
-data visualization) arise. In brief, many graph embeddings \emph{can}
-serve as dimensionality reduction steps, but not all do, neither do all
+(Anowar et al., 2021) that can be applied to an embedded network should
+the need for dimensionality reduction (for example for data
+visualization) arise. In brief, many graph embeddings \emph{can} serve
+as dimensionality reduction steps, but not all do, neither do all
 dimensionality reduction methods provide adequate graph embedding
@@
 applies to kernel/probabilistic PCA, which are variations on the more
-general method of SVD. Note further that tSNE has been included because
+general method of SVD. Note further that t-SNE has been included because
 it is frequently used to embed graphs, including of species
 associations/interactions, despite not being strictly speaking, a graph
-embedding technique (see \emph{e.g.} Chami et al. 2022).}\tabularnewline
+embedding technique (see \emph{e.g.} Chami et al.,
+2022).}\tabularnewline
 \toprule\noalign{}
@@
 \endlastfoot
-tSNE & nodes & statistical divergence & Hinton and Roweis (2002) &
-(Cieslak et al. 2020, species-environment responses \(^a\)) (Gibb et al.
-2021, host-virus network representation) \\
+t-SNE & nodes & statistical divergence & Hinton \& Roweis (2002) &
+(Cieslak et al., 2020, species-environment responses \(^a\)) (Gibb et
+al., 2021, host-virus network representation) \\
 LINE & nodes & stochastic gradient descent & Tang et al. (2015) & \\
-SDNE & nodes & gradient descent & D. Wang, Cui, and Zhu (2016) & \\
-node2vec & nodes & stochastic gradient descent & Grover and Leskovec
+SDNE & nodes & gradient descent & D. Wang et al. (2016) & \\
+node2vec & nodes & stochastic gradient descent & Grover \& Leskovec
 (2016) & \\
@@
 DMSE & joint nodes & deep neural network & D. Chen et al. (2017) & (D.
-Chen et al. 2017, species-environment interactions \(^b\)) \\
+Chen et al., 2017, species-environment interactions \(^b\)) \\
 graph2vec & sub-graph & skipgram network & Narayanan et al. (2017) & \\
-RDPG & graph & SVD & Young and Scheinerman (2007) & (Dalla Riva and
-Stouffer 2016, trophic interactions) (Poisot et al. 2021, host-virus
+RDPG & graph & SVD & Young \& Scheinerman (2007) & (Dalla Riva \&
+Stouffer, 2016, trophic interactions) (Poisot et al., 2021, host-virus
 network prediction) \\
-GLEE & graph & Laplacian eigenmap & Torres, Chan, and Eliassi-Rad (2020)
-& \\
-DeepWalk & graph & stochastic gradient descent & Perozzi, Al-Rfou, and
-Skiena (2014) & (Wardeh, Baylis, and Blagrove 2021, host-virus
-interactions) \\
+GLEE & graph & Laplacian eigenmap & Torres et al. (2020) & \\
+DeepWalk & graph & stochastic gradient descent & Perozzi et al. (2014) &
+(Wardeh et al., 2021, host-virus interactions) \\
 GraphKKE & graph & stochastic differential equation & Melnyk et al.
-(2020) & (Melnyk et al. 2020, microbiome species associations \(^a\)) \\
-FastEmbed & graph & eigen decomposition & Ramasamy and Madhow (2015)
-& \\
-PCA & graph & eigen decomposition & Surendran (2013) & (Strydom et al.
-2021, host-parasite interactions) \\
+(2020) & (Melnyk et al., 2020, microbiome species associations
+\(^a\)) \\
+FastEmbed & graph & eigen decomposition & Ramasamy \& Madhow (2015) & \\
+PCA & graph & eigen decomposition & Surendran (2013) & (Strydom,
+Catchen, et al., 2021, host-parasite interactions) \\
 Joint methods & multiple graphs & multiple strategies & S. Wang et al.
@@
 and machine learning techniques tend to handle continuous data better.
-Bringing a sparse graph into a continuous, dense vector space (Xu 2021)
+Bringing a sparse graph into a continuous, dense vector space (Xu, 2021)
 opens up a broader variety of predictive algorithms, notably of the sort
-that are able to predict events as probabilities (Murphy 2022).
+that are able to predict events as probabilities (Murphy, 2022).
 Furthermore, the projection of the graph itself is a representation that
-can be learned; Runghen, Stouffer, and Dalla Riva (2021), for example,
-used a neural network to learn the embedding of a network in which not
-all interactions were known, based on the nodes' metadata. This example
-has many parallels in ecology (see Figure~\ref{fig-embedding}
-\textbf{C}), in which node metadata can be represented by phylogeny,
-abundance, or functional traits. Using phylogeny as a source of
-information assumes (or strives to capture) the action of evolutionary
-processes on network structure, which at least for networks have been
-well documented (M. P. Braga et al. 2021; Dalla Riva and Stouffer 2016;
-Eklöf and Stouffer 2016; D. B. Stouffer et al. 2007; D. B. Stouffer et
-al. 2012); similarly, the use of functional traits assumes that
-interactions can be inferred from the knowledge of trait-matching rules,
-which is similarly well supported in the empirical literature (Bartomeus
-2013; Bartomeus et al. 2016; Goebel et al. 2023; Gravel et al. 2013).
-Relating this information to an embedding rather than a list of network
-measures would allow to capture their effect on the more fundamental
-aspects of network structure; conversely, the absence of a phylogenetic
-or functional signal may suggest that evolutionary/trait processes are
-not strong drivers of network structure, therefore opening a new way to
-perform hypothesis testing.
+can be learned; Runghen et al. (2021), for example, used a neural
+network to learn the embedding of a network in which not all
+interactions were known, based on the nodes' metadata. This example has
+many parallels in ecology (see Figure~\ref{fig-embedding} \textbf{C}),
+in which node metadata can be represented by phylogeny, abundance, or
+functional traits. Using phylogeny as a source of information assumes
+(or strives to capture) the action of evolutionary processes on network
+structure, which at least for networks have been well documented (M. P.
+Braga et al., 2021; Dalla Riva \& Stouffer, 2016; Eklöf \& Stouffer,
+2016; Stouffer et al., 2007; Stouffer et al., 2012); similarly, the use
+of functional traits assumes that interactions can be inferred from the
+knowledge of trait-matching rules, which is similarly well supported in
+the empirical literature (Bartomeus, 2013; Bartomeus et al., 2016;
+Goebel et al., 2023; Gravel et al., 2013). Relating this information to
+an embedding rather than a list of network measures would allow to
+capture their effect on the more fundamental aspects of network
+structure; conversely, the absence of a phylogenetic or functional
+signal may suggest that evolutionary/trait processes are not strong
+drivers of network structure, therefore opening a new way to perform
+hypothesis testing.
 
@@
 feature vectors, and provides good approximations of graphs with varied
-structures (Athreya et al. 2017). The code to reproduce this example is
+structures (Athreya et al., 2017). The code to reproduce this example is
 available as supplementary material (note, for the sake of comparison,
-that Strydom et al. 2021 have an example using embedding through PCA
-followed by prediction using a deep neural network on the same dataset).
-The resulting (binary) metaweb \(\mathcal{M}\) has 2131 interactions
-between 206 parasites and 121 hosts, and its adjacency matrix has full
-rank (\emph{i.e.} it represents a space with 121 dimensions). All
-analyses were done using Julia (Bezanson et al. 2017) version 1.7.2,
-\emph{Makie.jl} (Danisch and Krumbiegel 2021), and
-\emph{EcologicalNetworks.jl} (Poisot et al. 2019).
+that Strydom, Catchen, et al., 2021 have an example using embedding
+through PCA followed by prediction using a deep neural network on the
+same dataset). The resulting (binary) metaweb \(\mathcal{M}\) has 2131
+interactions between 206 parasites and 121 hosts, and its adjacency
+matrix has full rank (\emph{i.e.} it represents a space with 121
+dimensions). All analyses were done using Julia (Bezanson et al., 2017)
+version 1.7.2, \emph{Makie.jl} (Danisch \& Krumbiegel, 2021), and
+\emph{EcologicalNetworks.jl} (Poisot et al., 2019).
 
@@
 initially) according to the finite differences method. As discussed by
-Runghen, Stouffer, and Dalla Riva (2021), there is often a trade-off
-between the number of dimensions to use (more dimensions are more
-computationally demanding) and the quality of the representation. In
-panel \textbf{B}, we show the increase in cumulative variance explained
-at each rank, and visualize that using 39 ranks explains about 70\% of
-the variance in the empirical metaweb. This is a different information
-from the \(L_2\) loss (which is averaged across interactions), as it
-works on the eigenvalues of the embedding, and therefore captures
-higher-level features of the network. In panel \textbf{C}, we show
-positions of hosts and parasites on the first two dimensions of the left
-and right subspaces. Note that these values largely skew negative,
-because the first dimensions capture the coarse structure of the
-network: most pairs of species do not interact, and therefore have
-negative values. Finally in panel \textbf{D}, we show the predicted
-weight (\emph{i.e.} the result of the multiplication of the RDGP
-subspaces at a rank of 39) as a function of whether the interactions are
-observed, not-observed, or unknown due to lack of co-occurrence in the
-original dataset. This reveals that the observed interactions have
-higher predicted weights, although there is some overlap; the usual
-approach to identify potential interactions based on this information
-would be a thresholding analysis, which is outside the scope of this
-manuscript (and is done in the papers cited in this illustration).
-Because the values returned from RDPG are not bound to the unit
-interval, we performed a clamping of the weights to the unit space,
-showing a one-inflation in documented interactions, and a zero-inflation
-in other species pairs. This last figure shows that species pairs with
-no documented co-occurrence have weights that are not distinguishable
-from species pairs with no documented interactions; in other words,
-looking at the embedding, species that do not co-occur are not easily
-distinguished from species that do not interact. This suggests that (as
-befits a host-parasite model) the ability to interact is a strong
-predictor of co-occurrence.
+Runghen et al. (2021), there is often a trade-off between the number of
+dimensions to use (more dimensions are more computationally demanding)
+and the quality of the representation. In panel \textbf{B}, we show the
+increase in cumulative variance explained at each rank, and visualize
+that using 39 ranks explains about 70\% of the variance in the empirical
+metaweb. This provides different information from the \(L_2\) loss
+(which is averaged across interactions), as it works on the eigenvalues
+of the embedding, and therefore captures higher-level features of the
+network. In panel \textbf{C}, we show positions of hosts and parasites
+on the first two dimensions of the left and right subspaces. Note that
+these values largely skew negative, because the first dimensions capture
+the coarse structure of the network: most pairs of species do not
+interact, and therefore have negative values. Finally in panel
+\textbf{D}, we show the predicted weight (\emph{i.e.} the result of the
+multiplication of the RDGP subspaces at a rank of 39) as a function of
+whether the interactions are observed, not-observed, or unknown due to
+lack of co-occurrence in the original dataset. This reveals that the
+observed interactions have higher predicted weights, although there is
+some overlap; the usual approach to identify potential interactions
+based on this information would be a thresholding analysis, which is
+outside the scope of this manuscript (and is done in the papers cited in
+this illustration). Because the values returned from RDPG are not bound
+to the unit interval, we performed a clamping of the weights to the unit
+space, showing a one-inflation in documented interactions, and a
+zero-inflation in other species pairs. Panel \textbf{D} specifically
+shows that species pairs with no documented co-occurrence have weights
+that are not distinguishable from species pairs with no documented
+interactions; in other words, looking at the embedding, species that do
+not co-occur are not easily distinguished from species that do not
+interact. This suggests that (as befits a host-parasite model) the
+ability to interact is a strong predictor of co-occurrence.
 
@@
 
-The results of Figure~\ref{fig-illustration-1} show that we can extract
-an embedding of the metaweb that captures enough variance to be
-relevant; specifically, this is true for both \(L_2\) loss (indicating
-that RDPG is able to capture pairwise processes) and the cumulative
-variance explained (indicating that RDPG is able to capture
-network-level structure). Therefore, in Figure~\ref{fig-illustration-2},
-we relate the values of latent variables for hosts to different
-ecologically-relevant data. In panel \textbf{A}, we show that host with
-a higher value on the first dimension have fewer parasites. This relates
-to the body size of hosts in the \emph{PanTHERIA} database (Jones et al.
-2009), as shown in panel \textbf{B}: interestingly, the position on the
-first axis is only weakly correlated to body mass of the host; this
-matches well established results showing that body size/mass is not
-always a direct predictor of parasite richness in terrestrial mammals
-(Morand and Poulin 1998), a result we observe in panel \textbf{C}.
-Finally, in panel \textbf{D}, we can see how different taxonomic
-families occupy different positions on the first axis, with \emph{e.g.}
-Sciuridae being biased towards higher values. These results show how we
-can look for ecological informations in the output of network
-embeddings, which can further be refined into the selection of
+In Figure~\ref{fig-illustration-2}, we relate the values of latent
+variables for hosts to different ecologically-relevant data; we can
+perform this additional step, because the results presented in
+Figure~\ref{fig-illustration-1} show that we can extract an embedding of
+the metaweb that captures enough variance to be relevant. Importantly,
+this is true for both \(L_2\) loss (indicating that RDPG is able to
+capture pairwise processes) and the cumulative variance explained
+(indicating that RDPG is able to capture network-level structure), which
+suggests that these approaches may allow to predict interactions
+\emph{and} network structure. In panel \textbf{A}, we show that host
+with a higher value on the first dimension have fewer parasites. This
+relates to the body size of hosts in the \emph{PanTHERIA} database
+(Jones et al., 2009), as shown in panel \textbf{B}: interestingly, the
+position on the first axis is only weakly correlated to body mass of the
+host; this matches well established results showing that body size/mass
+is not always a direct predictor of parasite richness in terrestrial
+mammals (Morand \& Poulin, 1998), a result we observe in panel
+\textbf{C}. Finally, in panel \textbf{D}, we can see how different
+taxonomic families occupy different positions on the first axis, with
+\emph{e.g.} Sciuridae being biased towards higher values. These results
+show how we can look for ecological informations in the output of
+network embeddings, which can further be refined into the selection of
 predictors for transfer learning.
@@
 countries usually set conservation goals at the national level (Buxton
-et al. 2021), and as quantitative instruments are consequently designed
-to work at these scales (Turak et al. 2017); specific strategies are
-often enacted at smaller scales, nested within a specific country (Ray,
-Grimm, and Olive 2021). However, there is no guarantee that these
-arbitrary boundaries are meaningful. In fact, we do not have a
-satisfying answer to the question of ``where does an ecological network
-stop?'', the answer to which would dictate the spatial span to
-embed/predict. Recent results by Martins et al. (2022) suggested that
-networks are shaped within eco-regions, with abrupt structural
-transitions from an eco-region to the next. Should this trend hold
-generally, this would provide an ecologically-relevant scale at which
-metawebs can be downscaled and predicted. Other solutions could leverage
-network-area relationships to identify areas in which networks are
-structurally similar (see \emph{e.g.} Fortin, Dale, and Brimacombe 2021;
-Galiana et al. 2018, 2022). Both of these solutions require ample
-pre-existing information about the network in space. Nevertheless, the
-inclusion of species for which we have data but that are not in the
-right spatial extent \emph{may} improve the performance of approaches
-based on embedding and transfer, \emph{if} they increase the similarity
-between the target and destination network. This proposal can
-specifically be evaluated by adding nodes to the network to embed, and
-assessing the performance of predictive models (see \emph{e.g.} Llewelyn
-et al. 2022).
+et al., 2021), and as quantitative instruments are consequently designed
+to work at these scales (Turak et al., 2017); specific strategies are
+often enacted at smaller scales, nested within a specific country (Ray
+et al., 2021). However, there is no guarantee that these arbitrary
+boundaries are meaningful. In fact, we do not have a satisfying answer
+to the question of ``where does an ecological network stop?'', the
+answer to which would dictate the spatial span to embed/predict. Recent
+results by Martins et al. (2022) suggested that networks are shaped
+within eco-regions, with abrupt structural transitions from an
+eco-region to the next. Should this trend hold generally, this would
+provide an ecologically-relevant scale at which metawebs can be
+downscaled and predicted. Other solutions could leverage network-area
+relationships to identify areas in which networks are structurally
+similar (see \emph{e.g.} Fortin et al., 2021; Galiana et al., 2018,
+2022). Both of these solutions require ample pre-existing information
+about the network in space. Nevertheless, the inclusion of species for
+which we have data but that are not in the right spatial extent
+\emph{may} improve the performance of approaches based on embedding and
+transfer, \emph{if} they increase the similarity between the target and
+destination network. This proposal can specifically be evaluated by
+adding nodes to the network to embed, and assessing the performance of
+predictive models (see \emph{e.g.} Llewelyn et al., 2022).
 
@@
 are deployed and the intent of their deployment, originate in the
-framework that contributed to the ongoing biodiversity crisis (Adam
-2014) and reinforced environmental injustice (Choudry 2013; Domínguez
-and Luoma 2020). The risk of embedding this legacy in our models is
+framework that contributed to the ongoing biodiversity crisis (Adam,
+2014) and reinforced environmental injustice (Choudry, 2013; Domínguez
+\& Luoma, 2020). The risk of embedding this legacy in our models is
 real, especially when the impact of this legacy on species pools is
@@
 can be put to task in accompanying Indigenous principles of land
-management (Eichhorn, Baker, and Griffiths 2019; No'kmaq et al. 2021).
-The discussion of ``algorithm-in-the-loop'' approaches that is now
-pervasive in the machine learning community provides examples of why
-this is important. Human-algorithm interactions are notoriously
-difficult and can yield adverse effects (Green and Chen 2019; Stevenson
-and Doleac 2021), suggesting the need to systematically study them for
-the specific purpose of, here, biodiversity governance. Improving the
-algorithmic literacy of decision makers is part of the solution
-(\emph{e.g.} Lamba et al. 2019; Mosebo Fernandes et al. 2020), as we can
-reasonably expect that model outputs will be increasingly used to drive
-policy decisions (Weiskopf et al. 2022). Our discussion of these
-approaches need to go beyond the technical and statistical, and into the
-governance consequences they can have. To embed data also embeds
-historical and contemporary biases that acted on these data, both
-because they shaped the ecological processes generating them, and the
-global processes leading to their measurement and publication. For a
-domain as vast as species interaction networks, these biases exist at
-multiple scales along the way, and a challenge for prediction is not
-only to develop (or adopt) new quantitative tools, but to assess the
-behavior of these tools in the proper context.
+management (Eichhorn et al., 2019; No'kmaq et al., 2021). The discussion
+of ``algorithm-in-the-loop'' approaches that is now pervasive in the
+machine learning community provides examples of why this is important.
+Human-algorithm interactions are notoriously difficult and can yield
+adverse effects (Green \& Chen, 2019; Stevenson \& Doleac, 2021),
+suggesting the need to systematically study them for the specific
+purpose of, here, biodiversity governance. Improving the algorithmic
+literacy of decision makers is part of the solution (\emph{e.g.} Lamba
+et al., 2019; Mosebo Fernandes et al., 2020), as we can reasonably
+expect that model outputs will be increasingly used to drive policy
+decisions (Weiskopf et al., 2022). Our discussion of these approaches
+need to go beyond the technical and statistical, and into the governance
+consequences they can have. To embed data also embeds historical and
+contemporary biases that acted on these data, both because they shaped
+the ecological processes generating them (see Box 2), and the global
+processes leading to their measurement and publication. For a domain as
+vast as species interaction networks, these biases exist at multiple
+scales along the way, and a challenge for prediction is not only to
+develop (or adopt) new quantitative tools, but to assess the behavior of
+these tools in the proper context.
 
@@
 Although promising, the application of embeddings to metaweb prediction
-will require to address several challenges. First, there is a need to
-understand how to define a metaweb as a single, cohesive, unit of
-ecological organisation. This is likely to admit very different answers
-based on the specific taxonomic group, temporal and spatial resolution,
-and question being investigated. Second, there is a need to understand
-the scale at which these predictions are relevant. Although we have
-documented many cases of using embedding to fill gaps in the metaweb,
-these techniques can likely be brought into a spatial (and possibly
-temporal) context. The validation of these predictions will have to
-proceed jointly with empirical sampling of interactions, but also with
-the design of downsampling methods. Finally, there is a need for a
-greater understanding of how biases in the data propagate to the
-predictions. Because the volume of metawebs is currently low, and
-because graph embeddings have not been commonly applied, we anticipate
-that this discussion will take place organically in the coming years.
-
-\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Box 2 - Minding legacies shaping ecological datasets}, colback=white, rightrule=.15mm, coltitle=black, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0, breakable, bottomtitle=1mm, titlerule=0mm, toptitle=1mm, arc=.35mm, toprule=.15mm, leftrule=.75mm, left=2mm, opacitybacktitle=0.6]
+still involved several challenges. First, there is a need to understand
+how to define a metaweb as a single, cohesive, unit of ecological
+organisation. This is likely to have very different answers based on the
+specific taxonomic group, temporal and spatial resolution, and question
+being investigated. Second, there is a need to understand the scale at
+which these predictions are relevant. Although we have documented many
+cases of using embedding to fill gaps in the metaweb, these techniques
+can likely be brought into a spatial (and possibly temporal) context.
+The validation of these predictions will have to proceed jointly with
+empirical sampling of interactions, but also with the design of
+downsampling methods. Finally, there is a need for a greater
+understanding of how biases in the data propagate to the predictions.
+Because the volume of metawebs is currently low, and because graph
+embeddings have not been commonly applied, we anticipate that this
+discussion will take place organically in the coming years.
+
+\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colback=white, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, titlerule=0mm, opacityback=0, rightrule=.15mm, bottomtitle=1mm, left=2mm, bottomrule=.15mm, breakable, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Box 2 - Minding legacies shaping ecological datasets}, toptitle=1mm, arc=.35mm, toprule=.15mm, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white]
 
 In large parts of the world, boundaries that delineate geographic
-regions are merely a reflection the legacy of settler colonialism, which
-drives global disparity in capacity to collect and publish ecological
-data. Applying any embedding to biased data does not debias them, but
-rather embeds these biases, propagating them to the models using
-embeddings to make predictions. Furthermore, the use of ecological data
-itself is not an apolitical act (Nost and Goldstein 2021): data
-infrastructures tend to be designed to answer questions within national
-boundaries (therefore placing contingencies on what is available to be
-embedded), their use often drawing upon, and reinforcing, territorial
-statecraft (see \emph{e.g.} Barrett 2005). As per Machen and Nost
-(2021), these biases are particularly important to consider when
-knowledge generated algorithmically is used to supplement or replace
-human decision-making, especially for governance (\emph{e.g.} enacting
-conservation decisions on the basis of model prediction). As information
-on networks is increasingly leveraged for conservation actions (see
-\emph{e.g.} Eero et al. 2021; Naman et al. 2022; Stier et al. 2017), the
-need to appraise and correct biases that are unwittingly propagated to
-algorithms when embedded from the original data is immense. These
-considerations are even more urgent in the specific context of
-biodiversity data. Long-term colonial legacies still shape taxonomic
-composition to this day (Lenzner et al. 2022; Raja 2022), and much
-shorter-term changes in taxonomic and genetic richness of wildlife
-emerged through environmental racism (Schmidt and Garroway 2022). Thus,
-the set of species found at a specific location is not only as the
-result of a response to ecological processes separate from human
-influence, but also the result of human-environment interaction as well
-as the result legislative/political histories.
+regions are a legacy of settler colonialism, which drives global
+disparity in capacity to collect and publish ecological data. Applying
+any embedding to biased data does not debias them, but rather embeds
+these biases, propagating them to the models using embeddings to make
+predictions. Furthermore, the use of ecological data itself is not an
+apolitical act (Nost \& Goldstein, 2021): data infrastructures tend to
+be designed to answer questions within national boundaries (therefore
+placing contingencies on what is available to be embedded), their use
+often drawing upon, and reinforcing, territorial statecraft (see
+\emph{e.g.} Barrett, 2005). As per Machen \& Nost (2021), these biases
+are particularly important to consider when knowledge generated
+algorithmically is used to supplement or replace human decision-making,
+especially for governance (\emph{e.g.} enacting conservation decisions
+on the basis of model prediction). As information on networks is
+increasingly leveraged for conservation actions (see \emph{e.g.} Eero et
+al., 2021; Naman et al., 2022; Stier et al., 2017), the need to appraise
+and correct biases that are unwittingly propagated to algorithms when
+embedded from the original data is immense. These considerations are
+even more urgent in the specific context of biodiversity data. Long-term
+colonial legacies still shape taxonomic composition to this day (Lenzner
+et al., 2022; Raja, 2022), and much shorter-term changes in taxonomic
+and genetic richness of wildlife emerged through environmental racism
+(Schmidt \& Garroway, 2022). Thus, the set of species found at a
+specific location is not only as the result of a response to ecological
+processes separate from human influence, but also the result of
+human-environment interaction as well as the results of
+legislative/political histories.
 
@@
 Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak
-nations. TP, TS, DC, and LP received funding from the Canadian Institute
-for Ecology \& Evolution. FB is funded by the Institute for Data
-Valorization (IVADO). TS, SB, and TP are funded by a donation from the
-Courtois Foundation. CB was awarded a Mitacs Elevate Fellowship no.
-IT12391, in partnership with fRI Research, and also acknowledges funding
-from Alberta Innovates and the Forest Resources Improvement Association
-of Alberta. M-JF acknowledges funding from NSERC Discovery Grant and
+nations. We thank Victoria Hemming for feedback on this manuscript. TP,
+TS, DC, and LP received funding from the Canadian Institute for Ecology
+\& Evolution. FB is funded by the Institute for Data Valorization
+(IVADO). TS, SB, and TP are funded by a donation from the Courtois
+Foundation. M-JF acknowledges funding from NSERC Discovery Grant and
 NSERC CRC. RR is funded by New Zealand's Biological Heritage Ngā Koiora
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Adam2014Elephant}{}}%
-Adam, Rachelle. 2014. \emph{Elephant Treaties: {The Colonial} Legacy of
-the Biodiversity Crisis}. {UPNE}.
+Adam, R. (2014). \emph{Elephant treaties: {The Colonial} legacy of the
+biodiversity crisis}. {UPNE}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Albouy2019Marine}{}}%
-Albouy, Camille, Philippe Archambault, Ward Appeltans, Miguel B. Araújo,
-David Beauchesne, Kevin Cazelles, Alyssa R. Cirtwill, et al. 2019.
-{``The Marine Fish Food Web Is Globally Connected.''} \emph{Nature
-Ecology \& Evolution} 3 (8, 8): 1153--61.
-\url{https://doi.org/10.1038/s41559-019-0950-y}.
+Albouy, C., Archambault, P., Appeltans, W., Araújo, M. B., Beauchesne,
+D., Cazelles, K., Cirtwill, A. R., Fortin, M.-J., Galiana, N., Leroux,
+S. J., Pellissier, L., Poisot, T., Stouffer, D. B., Wood, S. A., \&
+Gravel, D. (2019). The marine fish food web is globally connected.
+\emph{Nature Ecology \& Evolution}, \emph{3}(8, 8), 1153--1161.
+\url{https://doi.org/10.1038/s41559-019-0950-y}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Anowar2021Conceptual}{}}%
-Anowar, Farzana, Samira Sadaoui, and Bassant Selim. 2021. {``Conceptual
-and Empirical Comparison of Dimensionality Reduction Algorithms ({PCA},
-{KPCA}, {LDA}, {MDS}, {SVD}, {LLE}, {ISOMAP}, {LE}, {ICA}, t-{SNE}).''}
-\emph{Computer Science Review} 40 (May): 100378.
-\url{https://doi.org/10.1016/j.cosrev.2021.100378}.
+Anowar, F., Sadaoui, S., \& Selim, B. (2021). Conceptual and empirical
+comparison of dimensionality reduction algorithms ({PCA}, {KPCA}, {LDA},
+{MDS}, {SVD}, {LLE}, {ISOMAP}, {LE}, {ICA}, t-{SNE}). \emph{Computer
+Science Review}, \emph{40}, 100378.
+\url{https://doi.org/10.1016/j.cosrev.2021.100378}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Arsov2019Network}{}}%
-Arsov, Nino, and Georgina Mirceva. 2019. {``Network {Embedding}: {An
-Overview}.''} \url{http://arxiv.org/abs/1911.11726}.
+Arsov, N., \& Mirceva, G. (2019). \emph{Network {Embedding}: {An
+Overview}}. \url{http://arxiv.org/abs/1911.11726}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Athreya2017Statistical}{}}%
-Athreya, Avanti, Donniell E. Fishkind, Keith Levin, Vince Lyzinski,
-Youngser Park, Yichen Qin, Daniel L. Sussman, Minh Tang, Joshua T.
-Vogelstein, and Carey E. Priebe. 2017. {``Statistical Inference on
-Random Dot Product Graphs: A Survey.''} {arXiv}.
-\url{http://arxiv.org/abs/1709.05454}.
+Athreya, A., Fishkind, D. E., Levin, K., Lyzinski, V., Park, Y., Qin,
+Y., Sussman, D. L., Tang, M., Vogelstein, J. T., \& Priebe, C. E.
+(2017). \emph{Statistical inference on random dot product graphs: A
+survey} (arXiv:1709.05454). {arXiv}.
+\url{http://arxiv.org/abs/1709.05454}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Barrett2005Environment}{}}%
-Barrett, Scott. 2005. \emph{Environment and {Statecraft}: {The Strategy}
-of {Environmental Treaty-Making}}. 1st ed. {Oxford University
-PressOxford}. \url{https://doi.org/10.1093/0199286094.001.0001}.
+Barrett, S. (2005). \emph{Environment and {Statecraft}: {The Strategy}
+of {Environmental Treaty-Making}} (1st ed.). {Oxford University
+PressOxford}. \url{https://doi.org/10.1093/0199286094.001.0001}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Bartomeus2013Understanding}{}}%
-Bartomeus, Ignasi. 2013. {``Understanding Linkage Rules in
-Plant-Pollinator Networks by Using Hierarchical Models That Incorporate
-Pollinator Detectability and Plant Traits.''} \emph{PloS One} 8 (7):
-e69200.
-\url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0069200}.
+Bartomeus, I. (2013). Understanding linkage rules in plant-pollinator
+networks by using hierarchical models that incorporate pollinator
+detectability and plant traits. \emph{PloS One}, \emph{8}(7), e69200.
+\url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0069200}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Bartomeus2016Common}{}}%
-Bartomeus, Ignasi, Dominique Gravel, Jason M. Tylianakis, Marcelo A.
-Aizen, Ian A. Dickie, and Maud Bernard-Verdier. 2016. {``A Common
-Framework for Identifying Linkage Rules Across Different Types of
-Interactions.''} \emph{Functional Ecology} 30 (12): 1894--1903.
-\url{http://onlinelibrary.wiley.com/doi/10.1111/1365-2435.12666/full}.
+Bartomeus, I., Gravel, D., Tylianakis, J. M., Aizen, M. A., Dickie, I.
+A., \& Bernard-Verdier, M. (2016). A common framework for identifying
+linkage rules across different types of interactions. \emph{Functional
+Ecology}, \emph{30}(12), 1894--1903.
+\url{http://onlinelibrary.wiley.com/doi/10.1111/1365-2435.12666/full}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Bezanson2017Julia}{}}%
-Bezanson, Jeff, Alan Edelman, Stefan Karpinski, and Viral B. Shah. 2017.
-{``Julia: {A Fresh Approach} to {Numerical Computing}.''} \emph{SIAM
-Review} 59 (1): 65--98. \url{https://doi.org/10.1137/141000671}.
+Bezanson, J., Edelman, A., Karpinski, S., \& Shah, V. B. (2017). Julia:
+{A Fresh Approach} to {Numerical Computing}. \emph{SIAM Review},
+\emph{59}(1), 65--98. \url{https://doi.org/10.1137/141000671}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Blanchet2020Cooccurrence}{}}%
-Blanchet, F. Guillaume, Kevin Cazelles, and Dominique Gravel. 2020.
-{``Co-Occurrence Is Not Evidence of Ecological Interactions.''}
-\emph{Ecology Letters}.
+Blanchet, F. G., Cazelles, K., \& Gravel, D. (2020). Co-occurrence is
+not evidence of ecological interactions. \emph{Ecology Letters}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Bohan2017Nextgeneration}{}}%
-Bohan, David A., Corinne Vacher, Alireza Tamaddoni-Nezhad, Alan
-Raybould, Alex J. Dumbrell, and Guy Woodward. 2017. {``Next-{Generation
-Global Biomonitoring}: {Large-scale}, {Automated Reconstruction} of
-{Ecological Networks}.''} \emph{Trends in Ecology \& Evolution}, March.
-\url{https://doi.org/10.1016/j.tree.2017.03.001}.
+Bohan, D. A., Vacher, C., Tamaddoni-Nezhad, A., Raybould, A., Dumbrell,
+A. J., \& Woodward, G. (2017). Next-{Generation Global Biomonitoring}:
+{Large-scale}, {Automated Reconstruction} of {Ecological Networks}.
+\emph{Trends in Ecology \& Evolution}.
+\url{https://doi.org/10.1016/j.tree.2017.03.001}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Botella2022Appraisal}{}}%
-Botella, Christophe, Stéphane Dray, Catherine Matias, Vincent Miele, and
-Wilfried Thuiller. 2022. {``An Appraisal of Graph Embeddings for
-Comparing Trophic Network Architectures.''} \emph{Methods in Ecology and
-Evolution} 13 (1): 203--16.
-\url{https://doi.org/10.1111/2041-210X.13738}.
+Botella, C., Dray, S., Matias, C., Miele, V., \& Thuiller, W. (2022). An
+appraisal of graph embeddings for comparing trophic network
+architectures. \emph{Methods in Ecology and Evolution}, \emph{13}(1),
+203--216. \url{https://doi.org/10.1111/2041-210X.13738}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Braga2019Spatial}{}}%
-Braga, João, Laura J. Pollock, Ceres Barros, Núria Galiana, José M.
-Montoya, Dominique Gravel, Luigi Maiorano, et al. 2019. {``Spatial
-Analyses of Multi-Trophic Terrestrial Vertebrate Assemblages in
-{Europe}.''} \emph{Global Ecology and Biogeography} 28 (11): 1636--48.
-\url{https://doi.org/10.1111/geb.12981}.
+Braga, J., Pollock, L. J., Barros, C., Galiana, N., Montoya, J. M.,
+Gravel, D., Maiorano, L., Montemaggiori, A., Ficetola, G. F., Dray, S.,
+\& Thuiller, W. (2019). Spatial analyses of multi-trophic terrestrial
+vertebrate assemblages in {Europe}. \emph{Global Ecology and
+Biogeography}, \emph{28}(11), 1636--1648.
+\url{https://doi.org/10.1111/geb.12981}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Braga2021Phylogenetic}{}}%
-Braga, Mariana P., Niklas Janz, Sören Nylin, Fredrik Ronquist, and
-Michael J. Landis. 2021. {``Phylogenetic Reconstruction of Ancestral
-Ecological Networks Through Time for Pierid Butterflies and Their Host
-Plants.''} \emph{Ecology Letters} n/a (n/a).
-\url{https://doi.org/10.1111/ele.13842}.
+Braga, M. P., Janz, N., Nylin, S., Ronquist, F., \& Landis, M. J.
+(2021). Phylogenetic reconstruction of ancestral ecological networks
+through time for pierid butterflies and their host plants. \emph{Ecology
+Letters}, \emph{n/a}(n/a). \url{https://doi.org/10.1111/ele.13842}
 
 \leavevmode\vadjust pre{\hypertarget{ref-BramonMora2018Identifying}{}}%
-Bramon Mora, Bernat, Dominique Gravel, Luis J. Gilarranz, Timothée
-Poisot, and Daniel B. Stouffer. 2018. {``Identifying a Common Backbone
-of Interactions Underlying Food Webs from Different Ecosystems.''}
-\emph{Nature Communications} 9 (1): 2603.
-\url{https://doi.org/10.1038/s41467-018-05056-0}.
+Bramon Mora, B., Gravel, D., Gilarranz, L. J., Poisot, T., \& Stouffer,
+D. B. (2018). Identifying a common backbone of interactions underlying
+food webs from different ecosystems. \emph{Nature Communications},
+\emph{9}(1), 2603. \url{https://doi.org/10.1038/s41467-018-05056-0}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Buxton2021Key}{}}%
-Buxton, Rachel T., Joseph R. Bennett, Andrea J. Reid, Charles Shulman,
-Steven J. Cooke, Charles M. Francis, Elizabeth A. Nyboer, et al. 2021.
-{``Key Information Needs to Move from Knowledge to Action for
-Biodiversity Conservation in {Canada}.''} \emph{Biological Conservation}
-256 (April): 108983. \url{https://doi.org/10.1016/j.biocon.2021.108983}.
+Buxton, R. T., Bennett, J. R., Reid, A. J., Shulman, C., Cooke, S. J.,
+Francis, C. M., Nyboer, E. A., Pritchard, G., Binley, A. D., Avery-Gomm,
+S., Ban, N. C., Beazley, K. F., Bennett, E., Blight, L. K., Bortolotti,
+L. E., Camfield, A. F., Gadallah, F., Jacob, A. L., Naujokaitis-Lewis,
+I., \ldots{} Smith, P. A. (2021). Key information needs to move from
+knowledge to action for biodiversity conservation in {Canada}.
+\emph{Biological Conservation}, \emph{256}, 108983.
+\url{https://doi.org/10.1016/j.biocon.2021.108983}
 
 \leavevmode\vadjust pre{\hypertarget{ref-carlson2022}{}}%
-Carlson, Colin J., Gregory F. Albery, Cory Merow, Christopher H. Trisos,
-Casey M. Zipfel, Evan A. Eskew, Kevin J. Olival, Noam Ross, and Shweta
-Bansal. 2022. {``Climate Change Increases Cross-Species Viral
-Transmission Risk.''} \emph{Nature} 607 (7919): 555--62.
-\url{https://doi.org/10.1038/s41586-022-04788-w}.
+Carlson, C. J., Albery, G. F., Merow, C., Trisos, C. H., Zipfel, C. M.,
+Eskew, E. A., Olival, K. J., Ross, N., \& Bansal, S. (2022). Climate
+change increases cross-species viral transmission risk. \emph{Nature},
+\emph{607}(7919), 555--562.
+\url{https://doi.org/10.1038/s41586-022-04788-w}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Catchen2023Missing}{}}%
-Catchen, Michael, Timothée Poisot, Laura Pollock, and Andrew Gonzalez.
-2023. {``The Missing Link: Discerning True from False Negatives When
-Sampling Species Interaction Networks.''} Preprint. {EcoEvoRXiV}.
-\url{https://doi.org/10.32942/X2DW22}.
+Catchen, M., Poisot, T., Pollock, L., \& Gonzalez, A. (2023). \emph{The
+missing link: Discerning true from false negatives when sampling species
+interaction networks} (Preprint 4929). {EcoEvoRXiV}.
+\url{https://doi.org/10.32942/X2DW22}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Cazelles2016Theory}{}}%
-Cazelles, Kévin, Miguel B. Araújo, Nicolas Mouquet, and Dominique
-Gravel. 2016. {``A Theory for Species Co-Occurrence in Interaction
-Networks.''} \emph{Theoretical Ecology} 9 (1): 39--48.
-\url{https://doi.org/10.1007/s12080-015-0281-9}.
+Cazelles, K., Araújo, M. B., Mouquet, N., \& Gravel, D. (2016). A theory
+for species co-occurrence in interaction networks. \emph{Theoretical
+Ecology}, \emph{9}(1), 39--48.
+\url{https://doi.org/10.1007/s12080-015-0281-9}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Chami2022Machine}{}}%
-Chami, Ines, Sami Abu-El-Haija, Bryan Perozzi, Christopher Ré, and Kevin
-Murphy. 2022. {``Machine {Learning} on {Graphs}: {A Model} and
-{Comprehensive Taxonomy}.''} \emph{Journal of Machine Learning Research}
-23 (89): 1--64. \url{http://jmlr.org/papers/v23/20-852.html}.
+Chami, I., Abu-El-Haija, S., Perozzi, B., Ré, C., \& Murphy, K. (2022).
+Machine {Learning} on {Graphs}: {A Model} and {Comprehensive Taxonomy}.
+\emph{Journal of Machine Learning Research}, \emph{23}(89), 1--64.
+\url{http://jmlr.org/papers/v23/20-852.html}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Chen2017Deep}{}}%
-Chen, Di, Yexiang Xue, Daniel Fink, Shuo Chen, and Carla P. Gomes. 2017.
-{``Deep {Multi-species Embedding},''} 3639--46.
-\url{https://www.ijcai.org/proceedings/2017/509}.
+Chen, D., Xue, Y., Fink, D., Chen, S., \& Gomes, C. P. (2017).
+\emph{Deep {Multi-species Embedding}}. 3639--3646.
+\url{https://www.ijcai.org/proceedings/2017/509}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Chen2017Harp}{}}%
-Chen, Haochen, Bryan Perozzi, Yifan Hu, and Steven Skiena. 2017.
-{``{HARP}: {Hierarchical Representation Learning} for {Networks}.''}
-\url{http://arxiv.org/abs/1706.07845}.
+Chen, H., Perozzi, B., Hu, Y., \& Skiena, S. (2017). \emph{{HARP}:
+{Hierarchical Representation Learning} for {Networks}}.
+\url{http://arxiv.org/abs/1706.07845}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Choudry2013Saving}{}}%
-Choudry, Aziz. 2013. {``Saving Biodiversity, for Whom and for What?
-{Conservation NGOs}, Complicity, Colonialism and Conquest in an Era of
-Capitalist Globalization.''} In \emph{{NGOization}: {Complicity},
-Contradictions and Prospects}, 24--44. {Bloomsbury Publishing}.
+Choudry, A. (2013). Saving biodiversity, for whom and for what?
+{Conservation NGOs}, complicity, colonialism and conquest in an era of
+capitalist globalization. In \emph{{NGOization}: {Complicity},
+contradictions and prospects} (pp. 24--44). {Bloomsbury Publishing}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Cieslak2020Tdistributed}{}}%
-Cieslak, Matthew C., Ann M. Castelfranco, Vittoria Roncalli, Petra H.
-Lenz, and Daniel K. Hartline. 2020. {``T-{Distributed Stochastic
-Neighbor Embedding} (t-{SNE}): {A} Tool for Eco-Physiological
-Transcriptomic Analysis.''} \emph{Marine Genomics} 51 (June): 100723.
-\url{https://doi.org/10.1016/j.margen.2019.100723}.
+Cieslak, M. C., Castelfranco, A. M., Roncalli, V., Lenz, P. H., \&
+Hartline, D. K. (2020). T-{Distributed Stochastic Neighbor Embedding}
+(t-{SNE}): {A} tool for eco-physiological transcriptomic analysis.
+\emph{Marine Genomics}, \emph{51}, 100723.
+\url{https://doi.org/10.1016/j.margen.2019.100723}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Csermely2004Strong}{}}%
-Csermely, Peter. 2004. {``Strong Links Are Important, but Weak Links
-Stabilize Them.''} \emph{Trends in Biochemical Sciences} 29 (7):
-331--34. \url{https://doi.org/10.1016/j.tibs.2004.05.004}.
+Csermely, P. (2004). Strong links are important, but weak links
+stabilize them. \emph{Trends in Biochemical Sciences}, \emph{29}(7),
+331--334. \url{https://doi.org/10.1016/j.tibs.2004.05.004}
 
 \leavevmode\vadjust pre{\hypertarget{ref-DallaRiva2016Exploring}{}}%
-Dalla Riva, Giulio V., and Daniel B. Stouffer. 2016. {``Exploring the
-Evolutionary Signature of Food Webs' Backbones Using Functional
-Traits.''} \emph{Oikos} 125 (4): 446--56.
-\url{https://doi.org/10.1111/oik.02305}.
+Dalla Riva, G. V., \& Stouffer, D. B. (2016). Exploring the evolutionary
+signature of food webs' backbones using functional traits. \emph{Oikos},
+\emph{125}(4), 446--456. \url{https://doi.org/10.1111/oik.02305}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Dallas2017Predicting}{}}%
-Dallas, Tad, Andrew W. Park, and John M. Drake. 2017. {``Predicting
-Cryptic Links in Host-Parasite Networks.''} \emph{PLOS Computational
-Biology} 13 (5): e1005557.
-\url{https://doi.org/10.1371/journal.pcbi.1005557}.
+Dallas, T., Park, A. W., \& Drake, J. M. (2017). Predicting cryptic
+links in host-parasite networks. \emph{PLOS Computational Biology},
+\emph{13}(5), e1005557.
+\url{https://doi.org/10.1371/journal.pcbi.1005557}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Danisch2021Makie}{}}%
-Danisch, Simon, and Julius Krumbiegel. 2021. {``Makie.jl: {Flexible}
-High-Performance Data Visualization for {Julia}.''} \emph{Journal of
-Open Source Software} 6 (65): 3349.
-\url{https://doi.org/10.21105/joss.03349}.
+Danisch, S., \& Krumbiegel, J. (2021). Makie.jl: {Flexible}
+high-performance data visualization for {Julia}. \emph{Journal of Open
+Source Software}, \emph{6}(65), 3349.
+\url{https://doi.org/10.21105/joss.03349}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Dominguez2020Decolonising}{}}%
-Domínguez, Lara, and Colin Luoma. 2020. {``Decolonising {Conservation
-Policy}: {How Colonial Land} and {Conservation Ideologies Persist} and
+Domínguez, L., \& Luoma, C. (2020). Decolonising {Conservation Policy}:
+{How Colonial Land} and {Conservation Ideologies Persist} and
 {Perpetuate Indigenous Injustices} at the {Expense} of the
-{Environment}.''} \emph{Land} 9 (3, 3): 65.
-\url{https://doi.org/10.3390/land9030065}.
+{Environment}. \emph{Land}, \emph{9}(3, 3), 65.
+\url{https://doi.org/10.3390/land9030065}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Dunne2006Network}{}}%
-Dunne, Jennifer A. 2006. {``The {Network Structure} of {Food Webs}.''}
-In \emph{Ecological Networks: {Linking} Structure and Dynamics}, edited
-by Jennifer A Dunne and Mercedes Pascual, 27--86. {Oxford University
-Press}.
+Dunne, J. A. (2006). The {Network Structure} of {Food Webs}. In J. A.
+Dunne \& M. Pascual (Eds.), \emph{Ecological networks: {Linking}
+structure and dynamics} (pp. 27--86). {Oxford University Press}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Eero2021Use}{}}%
-Eero, Margit, Jan Dierking, Christoph Humborg, Emma Undeman, Brian R
-MacKenzie, Henn Ojaveer, Tiina Salo, and Friedrich Wilhelm Köster. 2021.
-{``Use of Food Web Knowledge in Environmental Conservation and
-Management of Living Resources in the {Baltic Sea}.''} \emph{ICES
-Journal of Marine Science} 78 (8): 2645--63.
-\url{https://doi.org/10.1093/icesjms/fsab145}.
+Eero, M., Dierking, J., Humborg, C., Undeman, E., MacKenzie, B. R.,
+Ojaveer, H., Salo, T., \& Köster, F. W. (2021). Use of food web
+knowledge in environmental conservation and management of living
+resources in the {Baltic Sea}. \emph{ICES Journal of Marine Science},
+\emph{78}(8), 2645--2663. \url{https://doi.org/10.1093/icesjms/fsab145}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Eichhorn2019Steps}{}}%
-Eichhorn, Markus P., Kate Baker, and Mark Griffiths. 2019. {``Steps
-Towards Decolonising Biogeography.''} \emph{Frontiers of Biogeography}
-12 (1): 1--7. \url{https://doi.org/10.21425/F5FBG44795}.
+Eichhorn, M. P., Baker, K., \& Griffiths, M. (2019). Steps towards
+decolonising biogeography. \emph{Frontiers of Biogeography},
+\emph{12}(1), 1--7. \url{https://doi.org/10.21425/F5FBG44795}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Eklof2013Dimensionality}{}}%
-Eklöf, Anna, Ute Jacob, Jason Kopp, Jordi Bosch, Rocío Castro-Urgal,
-Natacha P. Chacoff, Bo Dalsgaard, et al. 2013. {``The Dimensionality of
-Ecological Networks.''} \emph{Ecology Letters} 16 (5): 577--83.
-\url{https://doi.org/10.1111/ele.12081}.
+Eklöf, A., Jacob, U., Kopp, J., Bosch, J., Castro-Urgal, R., Chacoff, N.
+P., Dalsgaard, B., de Sassi, C., Galetti, M., Guimarães, P. R.,
+Lomáscolo, S. B., Martín González, A. M., Pizo, M. A., Rader, R.,
+Rodrigo, A., Tylianakis, J. M., Vázquez, D. P., \& Allesina, S. (2013).
+The dimensionality of ecological networks. \emph{Ecology Letters},
+\emph{16}(5), 577--583. \url{https://doi.org/10.1111/ele.12081}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Eklof2016Phylogenetic}{}}%
-Eklöf, Anna, and Daniel B. Stouffer. 2016. {``The Phylogenetic Component
-of Food Web Structure and Intervality.''} \emph{Theoretical Ecology} 9
-(1): 107--15. \url{https://doi.org/10.1007/s12080-015-0273-9}.
+Eklöf, A., \& Stouffer, D. B. (2016). The phylogenetic component of food
+web structure and intervality. \emph{Theoretical Ecology}, \emph{9}(1),
+107--115. \url{https://doi.org/10.1007/s12080-015-0273-9}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Fortin2021Network}{}}%
-Fortin, Marie-Josée, Mark R. T. Dale, and Chris Brimacombe. 2021.
-{``Network Ecology in Dynamic Landscapes.''} \emph{Proceedings of the
-Royal Society B: Biological Sciences} 288 (1949): rspb.2020.1889,
-20201889. \url{https://doi.org/10.1098/rspb.2020.1889}.
+Fortin, M.-J., Dale, M. R. T., \& Brimacombe, C. (2021). Network ecology
+in dynamic landscapes. \emph{Proceedings of the Royal Society B:
+Biological Sciences}, \emph{288}(1949), rspb.2020.1889, 20201889.
+\url{https://doi.org/10.1098/rspb.2020.1889}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Fricke2022Effects}{}}%
-Fricke, Evan C., Alejandro Ordonez, Haldre S. Rogers, and Jens-Christian
-Svenning. 2022. {``The Effects of Defaunation on Plants' Capacity to
-Track Climate Change.''} \emph{Science}, January.
-\url{https://www.science.org/doi/abs/10.1126/science.abk3510}.
+Fricke, E. C., Ordonez, A., Rogers, H. S., \& Svenning, J.-C. (2022).
+The effects of defaunation on plants' capacity to track climate change.
+\emph{Science}.
+\url{https://www.science.org/doi/abs/10.1126/science.abk3510}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Galiana2022Ecological}{}}%
-Galiana, Núria, Miguel Lurgi, Vinicius A. G. Bastazini, Jordi Bosch,
-Luciano Cagnolo, Kevin Cazelles, Bernat Claramunt-López, et al. 2022.
-{``Ecological Network Complexity Scales with Area.''} \emph{Nature
-Ecology \& Evolution}, January, 1--8.
-\url{https://doi.org/10.1038/s41559-021-01644-4}.
+Galiana, N., Lurgi, M., Bastazini, V. A. G., Bosch, J., Cagnolo, L.,
+Cazelles, K., Claramunt-López, B., Emer, C., Fortin, M.-J., Grass, I.,
+Hernández-Castellano, C., Jauker, F., Leroux, S. J., McCann, K., McLeod,
+A. M., Montoya, D., Mulder, C., Osorio-Canadas, S., Reverté, S.,
+\ldots{} Montoya, J. M. (2022). Ecological network complexity scales
+with area. \emph{Nature Ecology \& Evolution}, 1--8.
+\url{https://doi.org/10.1038/s41559-021-01644-4}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Galiana2018Spatial}{}}%
-Galiana, Núria, Miguel Lurgi, Bernat Claramunt-López, Marie-Josée
-Fortin, Shawn Leroux, Kevin Cazelles, Dominique Gravel, and José M.
-Montoya. 2018. {``The Spatial Scaling of Species Interaction
-Networks.''} \emph{Nature Ecology \& Evolution} 2 (5): 782--90.
-\url{https://doi.org/10.1038/s41559-018-0517-3}.
+Galiana, N., Lurgi, M., Claramunt-López, B., Fortin, M.-J., Leroux, S.,
+Cazelles, K., Gravel, D., \& Montoya, J. M. (2018). The spatial scaling
+of species interaction networks. \emph{Nature Ecology \& Evolution},
+\emph{2}(5), 782--790. \url{https://doi.org/10.1038/s41559-018-0517-3}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Gaucher2021Outlier}{}}%
-Gaucher, Solenne, Olga Klopp, and Geneviève Robin. 2021. {``Outlier
-Detection in Networks with Missing Links.''} \emph{Computational
-Statistics \& Data Analysis} 164 (December): 107308.
-\url{https://doi.org/10.1016/j.csda.2021.107308}.
+Gaucher, S., Klopp, O., \& Robin, G. (2021). Outlier detection in
+networks with missing links. \emph{Computational Statistics \& Data
+Analysis}, \emph{164}, 107308.
+\url{https://doi.org/10.1016/j.csda.2021.107308}
 
 \leavevmode\vadjust pre{\hypertarget{ref-ghasemian2020}{}}%
-Ghasemian, Amir, Homa Hosseinmardi, Aram Galstyan, Edoardo M. Airoldi,
-and Aaron Clauset. 2020. {``Stacking Models for Nearly Optimal Link
-Prediction in Complex Networks.''} \emph{Proceedings of the National
-Academy of Sciences} 117 (38): 23393--400.
-\url{https://doi.org/10.1073/pnas.1914950117}.
+Ghasemian, A., Hosseinmardi, H., Galstyan, A., Airoldi, E. M., \&
+Clauset, A. (2020). Stacking models for nearly optimal link prediction
+in complex networks. \emph{Proceedings of the National Academy of
+Sciences}, \emph{117}(38), 23393--23400.
+\url{https://doi.org/10.1073/pnas.1914950117}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Gibb2021Data}{}}%
-Gibb, Rory, Gregory F Albery, Daniel J Becker, Liam Brierley, Ryan
-Connor, Tad A Dallas, Evan A Eskew, et al. 2021. {``Data
-{Proliferation}, {Reconciliation}, and {Synthesis} in {Viral
-Ecology}.''} \emph{BioScience} 71 (11): 1148--56.
-\url{https://doi.org/10.1093/biosci/biab080}.
+Gibb, R., Albery, G. F., Becker, D. J., Brierley, L., Connor, R.,
+Dallas, T. A., Eskew, E. A., Farrell, M. J., Rasmussen, A. L., Ryan, S.
+J., Sweeny, A., Carlson, C. J., \& Poisot, T. (2021). Data
+{Proliferation}, {Reconciliation}, and {Synthesis} in {Viral Ecology}.
+\emph{BioScience}, \emph{71}(11), 1148--1156.
+\url{https://doi.org/10.1093/biosci/biab080}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Goebel2023Body}{}}%
-Goebel, Larissa Gabriela Araujo, Breno Dias Vitorino, Angélica Vilas
-Boas Frota, and Manoel dos Santos-Filho. 2023. {``Body Mass Determines
-the Role of Mammal Species in a Frugivore-Large Fruit Interaction
-Network in a {Neotropical} Savanna.''} \emph{Journal of Tropical
-Ecology} 39: e12. \url{https://doi.org/10.1017/S0266467422000505}.
+Goebel, L. G. A., Vitorino, B. D., Frota, A. V. B., \& Santos-Filho, M.
+dos. (2023). Body mass determines the role of mammal species in a
+frugivore-large fruit interaction network in a {Neotropical} savanna.
+\emph{Journal of Tropical Ecology}, \emph{39}, e12.
+\url{https://doi.org/10.1017/S0266467422000505}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Goodfellow2016Deep}{}}%
-Goodfellow, Ian, Yoshua Bengio, and Aaron Courville. 2016. \emph{Deep
-Learning}. {MIT Press}.
+Goodfellow, I., Bengio, Y., \& Courville, A. (2016). \emph{Deep
+learning}. {MIT Press}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Goyal2018Graph}{}}%
-Goyal, Palash, and Emilio Ferrara. 2018. {``Graph Embedding Techniques,
-Applications, and Performance: {A} Survey.''} \emph{Knowledge-Based
-Systems} 151 (July): 78--94.
-\url{https://doi.org/10.1016/j.knosys.2018.03.022}.
+Goyal, P., \& Ferrara, E. (2018). Graph embedding techniques,
+applications, and performance: {A} survey. \emph{Knowledge-Based
+Systems}, \emph{151}, 78--94.
+\url{https://doi.org/10.1016/j.knosys.2018.03.022}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Gravel2018Bringing}{}}%
-Gravel, Dominique, Benjamin Baiser, Jennifer A. Dunne, Jens-Peter
-Kopelke, Neo D. Martinez, Tommi Nyman, Timothée Poisot, et al. 2018.
-{``Bringing {Elton} and {Grinnell} Together: A Quantitative Framework to
-Represent the Biogeography of Ecological Interaction Networks.''}
-\emph{Ecography} 0 (0). \url{https://doi.org/10.1111/ecog.04006}.
+Gravel, D., Baiser, B., Dunne, J. A., Kopelke, J.-P., Martinez, N. D.,
+Nyman, T., Poisot, T., Stouffer, D. B., Tylianakis, J. M., Wood, S. A.,
+\& Roslin, T. (2018). Bringing {Elton} and {Grinnell} together: A
+quantitative framework to represent the biogeography of ecological
+interaction networks. \emph{Ecography}, \emph{0}(0).
+\url{https://doi.org/10.1111/ecog.04006}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Gravel2013Inferring}{}}%
-Gravel, Dominique, Timothée Poisot, Camille Albouy, Laure Velez, and
-David Mouillot. 2013. {``Inferring Food Web Structure from Predator-Prey
-Body Size Relationships.''} Edited by Robert Freckleton. \emph{Methods
-in Ecology and Evolution} 4 (11): 1083--90.
-\url{https://doi.org/10.1111/2041-210X.12103}.
+Gravel, D., Poisot, T., Albouy, C., Velez, L., \& Mouillot, D. (2013).
+Inferring food web structure from predator-prey body size relationships.
+\emph{Methods in Ecology and Evolution}, \emph{4}(11), 1083--1090.
+\url{https://doi.org/10.1111/2041-210X.12103}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Green2019Disparate}{}}%
-Green, Ben, and Yiling Chen. 2019. {``Disparate {Interactions}: {An
-Algorithm-in-the-Loop Analysis} of {Fairness} in {Risk Assessments}.''}
-In \emph{Proceedings of the {Conference} on {Fairness},
-{Accountability}, and {Transparency}}, 90--99. {FAT}* '19. {New York,
-NY, USA}: {Association for Computing Machinery}.
-\url{https://doi.org/10.1145/3287560.3287563}.
+Green, B., \& Chen, Y. (2019). Disparate {Interactions}: {An
+Algorithm-in-the-Loop Analysis} of {Fairness} in {Risk Assessments}.
+\emph{Proceedings of the {Conference} on {Fairness}, {Accountability},
+and {Transparency}}, 90--99.
+\url{https://doi.org/10.1145/3287560.3287563}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Grover2016Node2vec}{}}%
-Grover, Aditya, and Jure Leskovec. 2016. {``Node2vec: {Scalable Feature
-Learning} for {Networks}.''} In \emph{Proceedings of the 22nd {ACM
-SIGKDD International Conference} on {Knowledge Discovery} and {Data
-Mining}}, 855--64. {San Francisco California USA}: {ACM}.
-\url{https://doi.org/10.1145/2939672.2939754}.
+Grover, A., \& Leskovec, J. (2016). Node2vec: {Scalable Feature
+Learning} for {Networks}. \emph{Proceedings of the 22nd {ACM SIGKDD
+International Conference} on {Knowledge Discovery} and {Data Mining}},
+855--864. \url{https://doi.org/10.1145/2939672.2939754}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Grunig2020Crop}{}}%
-Grünig, Marc, Dominique Mazzi, Pierluigi Calanca, Dirk Nikolaus Karger,
-and Loïc Pellissier. 2020. {``Crop and Forest Pest Metawebs Shift
-Towards Increased Linkage and Suitability Overlap Under Climate
-Change.''} \emph{Communications Biology} 3 (1, 1): 1--10.
-\url{https://doi.org/10.1038/s42003-020-0962-9}.
+Grünig, M., Mazzi, D., Calanca, P., Karger, D. N., \& Pellissier, L.
+(2020). Crop and forest pest metawebs shift towards increased linkage
+and suitability overlap under climate change. \emph{Communications
+Biology}, \emph{3}(1, 1), 1--10.
+\url{https://doi.org/10.1038/s42003-020-0962-9}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Gupta2022Simultaneously}{}}%
-Gupta, Anubhav, Reinhard Furrer, and Owen L. Petchey. 2022.
-{``Simultaneously Estimating Food Web Connectance and Structure with
-Uncertainty.''} \emph{Ecology and Evolution} 12 (3): e8643.
-\url{https://doi.org/10.1002/ece3.8643}.
+Gupta, A., Furrer, R., \& Petchey, O. L. (2022). Simultaneously
+estimating food web connectance and structure with uncertainty.
+\emph{Ecology and Evolution}, \emph{12}(3), e8643.
+\url{https://doi.org/10.1002/ece3.8643}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Gupta2021Graph}{}}%
-Gupta, Atika, Priya Matta, and Bhasker Pant. 2021. {``Graph Neural
-Network: {Current} State of {Art}, Challenges and Applications.''}
-\emph{Materials Today: Proceedings}, International {Conference} on
-{Technological Advancements} in {Materials Science} and {Manufacturing},
-46 (January): 10927--32.
-\url{https://doi.org/10.1016/j.matpr.2021.01.950}.
+Gupta, A., Matta, P., \& Pant, B. (2021). Graph neural network:
+{Current} state of {Art}, challenges and applications. \emph{Materials
+Today: Proceedings}, \emph{46}, 10927--10932.
+\url{https://doi.org/10.1016/j.matpr.2021.01.950}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Hadfield2014Tale}{}}%
-Hadfield, Jarrod D., Boris R. Krasnov, Robert Poulin, and Shinichi
-Nakagawa. 2014. {``A {Tale} of {Two Phylogenies}: {Comparative Analyses}
-of {Ecological Interactions}.''} \emph{The American Naturalist} 183 (2):
-174--87. \url{https://doi.org/10.1086/674445}.
+Hadfield, J. D., Krasnov, B. R., Poulin, R., \& Nakagawa, S. (2014). A
+{Tale} of {Two Phylogenies}: {Comparative Analyses} of {Ecological
+Interactions}. \emph{The American Naturalist}, \emph{183}(2), 174--187.
+\url{https://doi.org/10.1086/674445}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Herbert1965Dune}{}}%
-Herbert, Frank. 1965. \emph{Dune}. 1st ed. {Philadelphia}: {Chilton Book
-Company}.
+Herbert, F. (1965). \emph{Dune} (1st ed.). {Chilton Book Company}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Hinton2002Stochastic}{}}%
-Hinton, Geoffrey, and Sam T Roweis. 2002. {``Stochastic Neighbor
-Embedding.''} In \emph{{NIPS}}, 15:833--40. {Citeseer}.
+Hinton, G., \& Roweis, S. T. (2002). Stochastic neighbor embedding.
+\emph{{NIPS}}, \emph{15}, 833--840.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Hoffmann2019Machine}{}}%
-Hoffmann, Jordan, Yohai Bar-Sinai, Lisa M. Lee, Jovana Andrejevic,
-Shruti Mishra, Shmuel M. Rubinstein, and Chris H. Rycroft. 2019.
-{``Machine Learning in a Data-Limited Regime: {Augmenting} Experiments
-with Synthetic Data Uncovers Order in Crumpled Sheets.''} \emph{Science
-Advances} 5 (4): eaau6792. \url{https://doi.org/10.1126/sciadv.aau6792}.
+Hoffmann, J., Bar-Sinai, Y., Lee, L. M., Andrejevic, J., Mishra, S.,
+Rubinstein, S. M., \& Rycroft, C. H. (2019). Machine learning in a
+data-limited regime: {Augmenting} experiments with synthetic data
+uncovers order in crumpled sheets. \emph{Science Advances}, \emph{5}(4),
+eaau6792. \url{https://doi.org/10.1126/sciadv.aau6792}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Hortal2015Seven}{}}%
-Hortal, Joaquín, Francesco de Bello, José Alexandre F. Diniz-Filho,
-Thomas M. Lewinsohn, Jorge M. Lobo, and Richard J. Ladle. 2015. {``Seven
-{Shortfalls} That {Beset Large-Scale Knowledge} of {Biodiversity}.''}
-\emph{Annual Review of Ecology, Evolution, and Systematics} 46 (1):
-523--49. \url{https://doi.org/10.1146/annurev-ecolsys-112414-054400}.
+Hortal, J., de Bello, F., Diniz-Filho, J. A. F., Lewinsohn, T. M., Lobo,
+J. M., \& Ladle, R. J. (2015). Seven {Shortfalls} that {Beset
+Large-Scale Knowledge} of {Biodiversity}. \emph{Annual Review of
+Ecology, Evolution, and Systematics}, \emph{46}(1), 523--549.
+\url{https://doi.org/10.1146/annurev-ecolsys-112414-054400}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Jones2009Pantheria}{}}%
-Jones, Kate E., Jon Bielby, Marcel Cardillo, Susanne A. Fritz, Justin
-O'Dell, C. David L. Orme, Kamran Safi, et al. 2009. {``{PanTHERIA}: A
-Species‐level Database of Life History, Ecology, and Geography of Extant
-and Recently Extinct Mammals: {Ecological Archives E090}‐184.''} Edited
-by W. K. Michener. \emph{Ecology} 90 (9): 2648--48.
-\url{https://doi.org/10.1890/08-1494.1}.
+Jones, K. E., Bielby, J., Cardillo, M., Fritz, S. A., O'Dell, J., Orme,
+C. D. L., Safi, K., Sechrest, W., Boakes, E. H., Carbone, C., Connolly,
+C., Cutts, M. J., Foster, J. K., Grenyer, R., Habib, M., Plaster, C. A.,
+Price, S. A., Rigby, E. A., Rist, J., \ldots{} Purvis, A. (2009).
+{PanTHERIA}: A species‐level database of life history, ecology, and
+geography of extant and recently extinct mammals: {Ecological Archives
+E090}‐184. \emph{Ecology}, \emph{90}(9), 2648--2648.
+\url{https://doi.org/10.1890/08-1494.1}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Jordano2016Sampling}{}}%
-Jordano, Pedro. 2016. {``Sampling Networks of Ecological
-Interactions.''} Edited by Daniel Stouffer. \emph{Functional Ecology} 30
-(12): 1883--93. \url{https://doi.org/10.1111/1365-2435.12763}.
+Jordano, P. (2016). Sampling networks of ecological interactions.
+\emph{Functional Ecology}, \emph{30}(12), 1883--1893.
+\url{https://doi.org/10.1111/1365-2435.12763}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Lamba2019Deep}{}}%
-Lamba, Aakash, Phillip Cassey, Ramesh Raja Segaran, and Lian Pin Koh.
-2019. {``Deep Learning for Environmental Conservation.''} \emph{Current
-Biology} 29 (19): R977--82.
-\url{https://doi.org/10.1016/j.cub.2019.08.016}.
+Lamba, A., Cassey, P., Segaran, R. R., \& Koh, L. P. (2019). Deep
+learning for environmental conservation. \emph{Current Biology},
+\emph{29}(19), R977--R982.
+\url{https://doi.org/10.1016/j.cub.2019.08.016}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Lenzner2022Naturalized}{}}%
-Lenzner, Bernd, Guillaume Latombe, Anna Schertler, Hanno Seebens, Qiang
-Yang, Marten Winter, Patrick Weigelt, et al. 2022. {``Naturalized Alien
-Floras Still Carry the Legacy of {European} Colonialism.''} \emph{Nature
-Ecology \& Evolution}, October, 1--10.
-\url{https://doi.org/10.1038/s41559-022-01865-1}.
+Lenzner, B., Latombe, G., Schertler, A., Seebens, H., Yang, Q., Winter,
+M., Weigelt, P., van Kleunen, M., Pyšek, P., Pergl, J., Kreft, H.,
+Dawson, W., Dullinger, S., \& Essl, F. (2022). Naturalized alien floras
+still carry the legacy of {European} colonialism. \emph{Nature Ecology
+\& Evolution}, 1--10. \url{https://doi.org/10.1038/s41559-022-01865-1}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Llewelyn2022Predicting}{}}%
-Llewelyn, John, Giovanni Strona, Christopher R. Dickman, Aaron C.
-Greenville, Glenda M. Wardle, Michael S. Y. Lee, Seamus Doherty, Farzin
-Shabani, Frédérik Saltré, and Corey J. A. Bradshaw. 2022. {``Predicting
-Predator-Prey Interactions in Terrestrial Endotherms Using Random
-Forest.''} Preprint. {Ecology}.
-\url{https://doi.org/10.1101/2022.09.02.506446}.
+Llewelyn, J., Strona, G., Dickman, C. R., Greenville, A. C., Wardle, G.
+M., Lee, M. S. Y., Doherty, S., Shabani, F., Saltré, F., \& Bradshaw, C.
+J. A. (2022). \emph{Predicting predator-prey interactions in terrestrial
+endotherms using random forest} {[}Preprint{]}. {Ecology}.
+\url{https://doi.org/10.1101/2022.09.02.506446}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Maaten2009Learning}{}}%
-Maaten, Laurens van der. 2009. {``Learning a {Parametric Embedding} by
-{Preserving Local Structure}.''} In \emph{Proceedings of the {Twelth
+Maaten, L. van der. (2009). Learning a {Parametric Embedding} by
+{Preserving Local Structure}. \emph{Proceedings of the {Twelth
 International Conference} on {Artificial Intelligence} and
-{Statistics}}, 384--91. {PMLR}.
-\url{https://proceedings.mlr.press/v5/maaten09a.html}.
+{Statistics}}, 384--391.
+\url{https://proceedings.mlr.press/v5/maaten09a.html}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Machen2021Thinking}{}}%
-Machen, Ruth, and Eric Nost. 2021. {``Thinking Algorithmically: {The}
-Making of Hegemonic Knowledge in Climate Governance.''}
-\emph{Transactions of the Institute of British Geographers} 46 (3):
-555--69. \url{https://doi.org/10.1111/tran.12441}.
+Machen, R., \& Nost, E. (2021). Thinking algorithmically: {The} making
+of hegemonic knowledge in climate governance. \emph{Transactions of the
+Institute of British Geographers}, \emph{46}(3), 555--569.
+\url{https://doi.org/10.1111/tran.12441}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Malaterre2019Functional}{}}%
-Malaterre, Christophe, Antoine C Dussault, Ely Mermans, Gillian Barker,
-Beatrix E Beisner, Frédéric Bouchard, Eric Desjardins, et al. 2019.
-{``Functional {Diversity}: {An Epistemic Roadmap}.''} \emph{BioScience}
-69 (10): 800--811. \url{https://doi.org/10.1093/biosci/biz089}.
+Malaterre, C., Dussault, A. C., Mermans, E., Barker, G., Beisner, B. E.,
+Bouchard, F., Desjardins, E., Handa, I. T., Kembel, S. W., Lajoie, G.,
+Maris, V., Munson, A. D., Odenbaugh, J., Poisot, T., Shapiro, B. J., \&
+Suttle, C. A. (2019). Functional {Diversity}: {An Epistemic Roadmap}.
+\emph{BioScience}, \emph{69}(10), 800--811.
+\url{https://doi.org/10.1093/biosci/biz089}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Martins2022Global}{}}%
-Martins, Lucas P., Daniel B. Stouffer, Pedro G. Blendinger, Katrin
-Böhning-Gaese, Galo Buitrón-Jurado, Marta Correia, José Miguel Costa, et
-al. 2022. {``Global and Regional Ecological Boundaries Explain Abrupt
-Spatial Discontinuities in Avian Frugivory Interactions.''} \emph{Nature
-Communications} 13 (1, 1): 6943.
-\url{https://doi.org/10.1038/s41467-022-34355-w}.
+Martins, L. P., Stouffer, D. B., Blendinger, P. G., Böhning-Gaese, K.,
+Buitrón-Jurado, G., Correia, M., Costa, J. M., Dehling, D. M., Donatti,
+C. I., Emer, C., Galetti, M., Heleno, R., Jordano, P., Menezes, Í.,
+Morante-Filho, J. C., Muñoz, M. C., Neuschulz, E. L., Pizo, M. A.,
+Quitián, M., \ldots{} Tylianakis, J. M. (2022). Global and regional
+ecological boundaries explain abrupt spatial discontinuities in avian
+frugivory interactions. \emph{Nature Communications}, \emph{13}(1, 1),
+6943. \url{https://doi.org/10.1038/s41467-022-34355-w}
 
 \leavevmode\vadjust pre{\hypertarget{ref-McLeod2021Sampling}{}}%
-McLeod, Anne, Shawn J. Leroux, Dominique Gravel, Cindy Chu, Alyssa R.
-Cirtwill, Marie-Josée Fortin, Núria Galiana, Timothée Poisot, and
-Spencer A. Wood. 2021. {``Sampling and Asymptotic Network Properties of
-Spatial Multi-Trophic Networks.''} \emph{Oikos} n/a (n/a).
-\url{https://doi.org/10.1111/oik.08650}.
+McLeod, A., Leroux, S. J., Gravel, D., Chu, C., Cirtwill, A. R., Fortin,
+M.-J., Galiana, N., Poisot, T., \& Wood, S. A. (2021). Sampling and
+asymptotic network properties of spatial multi-trophic networks.
+\emph{Oikos}, \emph{n/a}(n/a). \url{https://doi.org/10.1111/oik.08650}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Melnyk2020Graphkke}{}}%
-Melnyk, Kateryna, Stefan Klus, Grégoire Montavon, and Tim O. F. Conrad.
-2020. {``{GraphKKE}: Graph {Kernel Koopman} Embedding for Human
-Microbiome Analysis.''} \emph{Applied Network Science} 5 (1): 96.
-\url{https://doi.org/10.1007/s41109-020-00339-2}.
+Melnyk, K., Klus, S., Montavon, G., \& Conrad, T. O. F. (2020).
+{GraphKKE}: Graph {Kernel Koopman} embedding for human microbiome
+analysis. \emph{Applied Network Science}, \emph{5}(1), 96.
+\url{https://doi.org/10.1007/s41109-020-00339-2}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Morales-Castilla2015Inferring}{}}%
-Morales-Castilla, Ignacio, Miguel G. Matias, Dominique Gravel, and
-Miguel B. Araújo. 2015. {``Inferring Biotic Interactions from
-Proxies.''} \emph{Trends in Ecology \& Evolution} 30 (6): 347--56.
-\url{https://doi.org/10.1016/j.tree.2015.03.014}.
+Morales-Castilla, I., Matias, M. G., Gravel, D., \& Araújo, M. B.
+(2015). Inferring biotic interactions from proxies. \emph{Trends in
+Ecology \& Evolution}, \emph{30}(6), 347--356.
+\url{https://doi.org/10.1016/j.tree.2015.03.014}
 
 \leavevmode\vadjust pre{\hypertarget{ref-morales-castilla2021}{}}%
-Morales-Castilla, Ignacio, Paula Pappalardo, Maxwell J. Farrell, A.
-Alonso Aguirre, Shan Huang, Alyssa-Lois M. Gehman, Tad Dallas, Dominique
-Gravel, and T. Jonathan Davies. 2021. {``Forecasting Parasite Sharing
-Under Climate Change.''} \emph{Philosophical Transactions of the Royal
-Society B: Biological Sciences} 376 (1837): 20200360.
-\url{https://doi.org/10.1098/rstb.2020.0360}.
+Morales-Castilla, I., Pappalardo, P., Farrell, M. J., Aguirre, A. A.,
+Huang, S., Gehman, A.-L. M., Dallas, T., Gravel, D., \& Davies, T. J.
+(2021). Forecasting parasite sharing under climate change.
+\emph{Philosophical Transactions of the Royal Society B: Biological
+Sciences}, \emph{376}(1837), 20200360.
+\url{https://doi.org/10.1098/rstb.2020.0360}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Morand1998Density}{}}%
-Morand, Serge, and Robert Poulin. 1998. {``Density, Body Mass and
-Parasite Species Richness of Terrestrial Mammals.''} \emph{Evolutionary
-Ecology} 12 (6): 717--27. \url{https://doi.org/10.1023/A:1006537600093}.
+Morand, S., \& Poulin, R. (1998). Density, body mass and parasite
+species richness of terrestrial mammals. \emph{Evolutionary Ecology},
+\emph{12}(6), 717--727. \url{https://doi.org/10.1023/A:1006537600093}
 
 \leavevmode\vadjust pre{\hypertarget{ref-MoseboFernandes2020Machine}{}}%
-Mosebo Fernandes, Ana Cristina, Rebeca Quintero Gonzalez, Marie Ann
-Lenihan-Clarke, Ezra Francis Leslie Trotter, and Jamal Jokar Arsanjani.
-2020. {``Machine {Learning} for {Conservation Planning} in a {Changing
-Climate}.''} \emph{Sustainability} 12 (18, 18): 7657.
-\url{https://doi.org/10.3390/su12187657}.
+Mosebo Fernandes, A. C., Quintero Gonzalez, R., Lenihan-Clarke, M. A.,
+Leslie Trotter, E. F., \& Jokar Arsanjani, J. (2020). Machine {Learning}
+for {Conservation Planning} in a {Changing Climate}.
+\emph{Sustainability}, \emph{12}(18, 18), 7657.
+\url{https://doi.org/10.3390/su12187657}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Murphy2022Probabilistic}{}}%
-Murphy, Kevin P. 2022. \emph{Probabilistic Machine Learning: {An}
-Introduction}. {MIT Press}. \href{https://probml.ai}{probml.ai}.
+Murphy, K. P. (2022). \emph{Probabilistic machine learning: {An}
+introduction}. {MIT Press}. \href{https://probml.ai}{probml.ai}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Naman2022Food}{}}%
-Naman, Sean M., Seth M. White, J. Ryan Bellmore, Peter A. McHugh,
-Matthew J. Kaylor, Colden V. Baxter, Robert J. Danehy, Robert J. Naiman,
-and Amy L. Puls. 2022. {``Food Web Perspectives and Methods for Riverine
-Fish Conservation.''} \emph{WIREs Water} n/a (n/a): e1590.
-\url{https://doi.org/10.1002/wat2.1590}.
+Naman, S. M., White, S. M., Bellmore, J. R., McHugh, P. A., Kaylor, M.
+J., Baxter, C. V., Danehy, R. J., Naiman, R. J., \& Puls, A. L. (2022).
+Food web perspectives and methods for riverine fish conservation.
+\emph{WIREs Water}, \emph{n/a}(n/a), e1590.
+\url{https://doi.org/10.1002/wat2.1590}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Narayanan2017Graph2vec}{}}%
-Narayanan, Annamalai, Mahinthan Chandramohan, Rajasekar Venkatesan,
-Lihui Chen, Yang Liu, and Shantanu Jaiswal. 2017. {``Graph2vec:
-{Learning Distributed Representations} of {Graphs}.''}
-\url{http://arxiv.org/abs/1707.05005}.
+Narayanan, A., Chandramohan, M., Venkatesan, R., Chen, L., Liu, Y., \&
+Jaiswal, S. (2017). \emph{Graph2vec: {Learning Distributed
+Representations} of {Graphs}}. \url{http://arxiv.org/abs/1707.05005}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Neutel2002Stability}{}}%
-Neutel, Anje-Margriet, Johan A. P. Heesterbeek, and Peter C. de Ruiter.
-2002. {``Stability in {Real Food Webs}: {Weak Links} in {Long Loops}.''}
-\emph{Science} 296 (5570): 1120--23.
-\url{https://doi.org/10.1126/science.1068326}.
+Neutel, A.-M., Heesterbeek, J. A. P., \& de Ruiter, P. C. (2002).
+Stability in {Real Food Webs}: {Weak Links} in {Long Loops}.
+\emph{Science}, \emph{296}(5570), 1120--1123.
+\url{https://doi.org/10.1126/science.1068326}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Nokmaq2021Awakening}{}}%
-No'kmaq, M'sit, Albert Marshall, Karen F. Beazley, Jessica Hum, shalan
-joudry, Anastasia Papadopoulos, Sherry Pictou, Janet Rabesca, Lisa
-Young, and Melanie Zurba. 2021. {``{`{Awakening} the Sleeping Giant'}:
-Re-{Indigenization} Principles for Transforming Biodiversity
-Conservation in {Canada} and Beyond.''} \emph{FACETS} 6 (1): 839--69.
+No'kmaq, M., Marshall, A., Beazley, K. F., Hum, J., joudry, shalan,
+Papadopoulos, A., Pictou, S., Rabesca, J., Young, L., \& Zurba, M.
+(2021). {``{Awakening} the sleeping giant''}: Re-{Indigenization}
+principles for transforming biodiversity conservation in {Canada} and
+beyond. \emph{FACETS}, \emph{6}(1), 839--869.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Nost2021Political}{}}%
-Nost, Eric, and Jenny Elaine Goldstein. 2021. {``A Political Ecology of
-Data.''} \emph{Environment and Planning E: Nature and Space}, September,
-25148486211043503. \url{https://doi.org/10.1177/25148486211043503}.
+Nost, E., \& Goldstein, J. E. (2021). A political ecology of data.
+\emph{Environment and Planning E: Nature and Space}, 25148486211043503.
+\url{https://doi.org/10.1177/25148486211043503}
 
 \leavevmode\vadjust pre{\hypertarget{ref-OConnor2020Unveiling}{}}%
-O'Connor, Louise M. J., Laura J. Pollock, João Braga, Gentile Francesco
-Ficetola, Luigi Maiorano, Camille Martinez‐Almoyna, Alessandro
-Montemaggiori, Marc Ohlmann, and Wilfried Thuiller. 2020. {``Unveiling
-the Food Webs of Tetrapods Across {Europe} Through the Prism of the
-{Eltonian} Niche.''} \emph{Journal of Biogeography} 47 (1): 181--92.
-\url{https://doi.org/10.1111/jbi.13773}.
+O'Connor, L. M. J., Pollock, L. J., Braga, J., Ficetola, G. F.,
+Maiorano, L., Martinez‐Almoyna, C., Montemaggiori, A., Ohlmann, M., \&
+Thuiller, W. (2020). Unveiling the food webs of tetrapods across
+{Europe} through the prism of the {Eltonian} niche. \emph{Journal of
+Biogeography}, \emph{47}(1), 181--192.
+\url{https://doi.org/10.1111/jbi.13773}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Pedersen2017Signatures}{}}%
-Pedersen, Eric J., Patrick L. Thompson, R. Aaron Ball, Marie-Josée
-Fortin, Tarik C. Gouhier, Heike Link, Charlotte Moritz, et al. 2017.
-{``Signatures of the Collapse and Incipient Recovery of an Overexploited
-Marine Ecosystem.''} \emph{Royal Society Open Science} 4 (7): 170215.
-\url{https://doi.org/10.1098/rsos.170215}.
+Pedersen, E. J., Thompson, P. L., Ball, R. A., Fortin, M.-J., Gouhier,
+T. C., Link, H., Moritz, C., Nenzen, H., Stanley, R. R. E., Taranu, Z.
+E., Gonzalez, A., Guichard, F., \& Pepin, P. (2017). Signatures of the
+collapse and incipient recovery of an overexploited marine ecosystem.
+\emph{Royal Society Open Science}, \emph{4}(7), 170215.
+\url{https://doi.org/10.1098/rsos.170215}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Perozzi2014Deepwalk}{}}%
-Perozzi, Bryan, Rami Al-Rfou, and Steven Skiena. 2014. {``{DeepWalk}:
-Online Learning of Social Representations.''} In \emph{Proceedings of
-the 20th {ACM SIGKDD} International Conference on {Knowledge} Discovery
-and Data Mining}, 701--10. {KDD} '14. {New York, NY, USA}: {Association
-for Computing Machinery}. \url{https://doi.org/10.1145/2623330.2623732}.
+Perozzi, B., Al-Rfou, R., \& Skiena, S. (2014). {DeepWalk}: Online
+learning of social representations. \emph{Proceedings of the 20th {ACM
+SIGKDD} International Conference on {Knowledge} Discovery and Data
+Mining}, 701--710. \url{https://doi.org/10.1145/2623330.2623732}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Pichler2020Machine}{}}%
-Pichler, Maximilian, Virginie Boreux, Alexandra-Maria Klein, Matthias
-Schleuning, and Florian Hartig. 2020. {``Machine Learning Algorithms to
-Infer Trait-Matching and Predict Species Interactions in Ecological
-Networks.''} \emph{Methods in Ecology and Evolution} 11 (2): 281--93.
-\url{https://doi.org/10.1111/2041-210X.13329}.
+Pichler, M., Boreux, V., Klein, A.-M., Schleuning, M., \& Hartig, F.
+(2020). Machine learning algorithms to infer trait-matching and predict
+species interactions in ecological networks. \emph{Methods in Ecology
+and Evolution}, \emph{11}(2), 281--293.
+\url{https://doi.org/10.1111/2041-210X.13329}
 
 \leavevmode\vadjust pre{\hypertarget{ref-poisot2023}{}}%
-Poisot, Timothée. 2023. {``Guidelines for the Prediction of Species
-Interactions Through Binary Classification.''} \emph{Methods in Ecology
-and Evolution} 14 (5): 1333--45.
-\url{https://doi.org/10.1111/2041-210x.14071}.
+Poisot, T. (2023). Guidelines for the prediction of species interactions
+through binary classification. \emph{Methods in Ecology and Evolution},
+\emph{14}(5), 1333--1345. \url{https://doi.org/10.1111/2041-210x.14071}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Poisot2019Ecologicalnetworks}{}}%
-Poisot, Timothée, Zacharie Belisle, Laura Hoebeke, Michiel Stock, and
-Piotr Szefer. 2019. {``{EcologicalNetworks}.jl - Analysing Ecological
-Networks.''} \emph{Ecography}. \url{https://doi.org/10.1111/ecog.04310}.
+Poisot, T., Belisle, Z., Hoebeke, L., Stock, M., \& Szefer, P. (2019).
+{EcologicalNetworks}.jl - analysing ecological networks.
+\emph{Ecography}. \url{https://doi.org/10.1111/ecog.04310}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Poisot2012Dissimilarity}{}}%
-Poisot, Timothée, Elsa Canard, David Mouillot, Nicolas Mouquet, and
-Dominique Gravel. 2012. {``The Dissimilarity of Species Interaction
-Networks.''} \emph{Ecology Letters} 15 (12): 1353--61.
-\url{https://doi.org/10.1111/ele.12002}.
+Poisot, T., Canard, E., Mouillot, D., Mouquet, N., \& Gravel, D. (2012).
+The dissimilarity of species interaction networks. \emph{Ecology
+Letters}, \emph{15}(12), 1353--1361.
+\url{https://doi.org/10.1111/ele.12002}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Poisot2016Structure}{}}%
-Poisot, Timothée, Alyssa R. Cirtwill, Kévin Cazelles, Dominique Gravel,
-Marie-Josée Fortin, and Daniel B. Stouffer. 2016. {``The Structure of
-Probabilistic Networks.''} \emph{Methods in Ecology and Evolution} 7
-(3): 303--12. \url{https://doi.org/10.1111/2041-210X.12468}.
+Poisot, T., Cirtwill, A. R., Cazelles, K., Gravel, D., Fortin, M.-J., \&
+Stouffer, D. B. (2016). The structure of probabilistic networks.
+\emph{Methods in Ecology and Evolution}, \emph{7}(3), 303--312.
+\url{https://doi.org/10.1111/2041-210X.12468}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Poisot2021Imputing}{}}%
-Poisot, Timothée, Marie-Andrée Ouellet, Nardus Mollentze, Maxwell J.
-Farrell, Daniel J. Becker, Gregory F. Albery, Rory J. Gibb, Stephanie N.
-Seifert, and Colin J. Carlson. 2021. {``Imputing the Mammalian Virome
-with Linear Filtering and Singular Value Decomposition.''}
-\url{http://arxiv.org/abs/2105.14973}.
+Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M. J., Becker, D.
+J., Albery, G. F., Gibb, R. J., Seifert, S. N., \& Carlson, C. J.
+(2021). \emph{Imputing the mammalian virome with linear filtering and
+singular value decomposition}. \url{http://arxiv.org/abs/2105.14973}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Poisot2015Species}{}}%
-Poisot, Timothée, Daniel B. Stouffer, and Dominique Gravel. 2015.
-{``Beyond Species: Why Ecological Interaction Networks Vary Through
-Space and Time.''} \emph{Oikos} 124 (3): 243--51.
-\url{https://doi.org/10.1111/oik.01719}.
+Poisot, T., Stouffer, D. B., \& Gravel, D. (2015). Beyond species: Why
+ecological interaction networks vary through space and time.
+\emph{Oikos}, \emph{124}(3), 243--251.
+\url{https://doi.org/10.1111/oik.01719}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Raja2022Colonialism}{}}%
-Raja, Nussaïbah B. 2022. {``Colonialism Shaped Today's Biodiversity.''}
-\emph{Nature Ecology \& Evolution}, October, 1--2.
-\url{https://doi.org/10.1038/s41559-022-01903-y}.
+Raja, N. B. (2022). Colonialism shaped today's biodiversity.
+\emph{Nature Ecology \& Evolution}, 1--2.
+\url{https://doi.org/10.1038/s41559-022-01903-y}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Ramasamy2015Compressive}{}}%
-Ramasamy, Dinesh, and Upamanyu Madhow. 2015. {``Compressive Spectral
-Embedding: Sidestepping the {SVD}.''} In \emph{Advances in Neural
-Information Processing Systems}, edited by C. Cortes, N. Lawrence, D.
-Lee, M. Sugiyama, and R. Garnett. Vol. 28. {Curran Associates, Inc.}
-\url{https://proceedings.neurips.cc/paper/2015/file/4f6ffe13a5d75b2d6a3923922b3922e5-Paper.pdf}.
+Ramasamy, D., \& Madhow, U. (2015). Compressive spectral embedding:
+Sidestepping the {SVD}. In C. Cortes, N. Lawrence, D. Lee, M. Sugiyama,
+\& R. Garnett (Eds.), \emph{Advances in neural information processing
+systems} (Vol. 28). {Curran Associates, Inc.}
+\url{https://proceedings.neurips.cc/paper/2015/file/4f6ffe13a5d75b2d6a3923922b3922e5-Paper.pdf}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Ray2021Biodiversity}{}}%
-Ray, Justina C., Jaime Grimm, and Andrea Olive. 2021. {``The
-Biodiversity Crisis in {Canada}: Failures and Challenges of Federal and
-Sub-National Strategic and Legal Frameworks.''} \emph{FACETS} 6
-(January): 1044--68. \url{https://doi.org/10.1139/facets-2020-0075}.
+Ray, J. C., Grimm, J., \& Olive, A. (2021). The biodiversity crisis in
+{Canada}: Failures and challenges of federal and sub-national strategic
+and legal frameworks. \emph{FACETS}, \emph{6}, 1044--1068.
+\url{https://doi.org/10.1139/facets-2020-0075}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Runghen2021Exploiting}{}}%
-Runghen, Rogini, Daniel B Stouffer, and Giulio V Dalla Riva. 2021.
-{``Exploiting Node Metadata to Predict Interactions in Large Networks
-Using Graph Embedding and Neural Networks,''} June.
-\url{https://doi.org/10.1101/2021.06.10.447991}.
+Runghen, R., Stouffer, D. B., \& Dalla Riva, G. V. (2021).
+\emph{Exploiting node metadata to predict interactions in large networks
+using graph embedding and neural networks}.
+\url{https://doi.org/10.1101/2021.06.10.447991}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Saravia2021Ecological}{}}%
-Saravia, Leonardo A., Tomás I. Marina, Nadiah P. Kristensen, Marleen De
-Troch, and Fernando R. Momo. 2021. {``Ecological Network Assembly: {How}
-the Regional Metaweb Influences Local Food Webs.''} \emph{Journal of
-Animal Ecology} n/a (n/a).
-\url{https://doi.org/10.1111/1365-2656.13652}.
+Saravia, L. A., Marina, T. I., Kristensen, N. P., De Troch, M., \& Momo,
+F. R. (2021). Ecological network assembly: {How} the regional metaweb
+influences local food webs. \emph{Journal of Animal Ecology},
+\emph{n/a}(n/a). \url{https://doi.org/10.1111/1365-2656.13652}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Schmidt2022Systemic}{}}%
-Schmidt, Chloé, and Colin J. Garroway. 2022. {``Systemic Racism Alters
-Wildlife Genetic Diversity.''} \emph{Proceedings of the National Academy
-of Sciences} 119 (43): e2102860119.
-\url{https://doi.org/10.1073/pnas.2102860119}.
+Schmidt, C., \& Garroway, C. J. (2022). Systemic racism alters wildlife
+genetic diversity. \emph{Proceedings of the National Academy of
+Sciences}, \emph{119}(43), e2102860119.
+\url{https://doi.org/10.1073/pnas.2102860119}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Stevenson2021Algorithmic}{}}%
-Stevenson, Megan T., and Jennifer L. Doleac. 2021. {``Algorithmic {Risk
-Assessment} in the {Hands} of {Humans}.''} SSRN Scholarly Paper.
-{Rochester, NY}. \url{https://doi.org/10.2139/ssrn.3489440}.
+Stevenson, M. T., \& Doleac, J. L. (2021). \emph{Algorithmic {Risk
+Assessment} in the {Hands} of {Humans}} (SSRN Scholarly Paper 3489440).
+\url{https://doi.org/10.2139/ssrn.3489440}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Stier2017Integrating}{}}%
-Stier, Adrian C., Jameal F. Samhouri, Steven Gray, Rebecca G. Martone,
-Megan E. Mach, Benjamin S. Halpern, Carrie V. Kappel, Courtney
-Scarborough, and Phillip S. Levin. 2017. {``Integrating {Expert
-Perceptions} into {Food Web Conservation} and {Management}.''}
-\emph{Conservation Letters} 10 (1): 67--76.
-\url{https://doi.org/10.1111/conl.12245}.
+Stier, A. C., Samhouri, J. F., Gray, S., Martone, R. G., Mach, M. E.,
+Halpern, B. S., Kappel, C. V., Scarborough, C., \& Levin, P. S. (2017).
+Integrating {Expert Perceptions} into {Food Web Conservation} and
+{Management}. \emph{Conservation Letters}, \emph{10}(1), 67--76.
+\url{https://doi.org/10.1111/conl.12245}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Stouffer2007Evidence}{}}%
-Stouffer, D. B, J. Camacho, W. Jiang, and L. A Nunes Amaral. 2007.
-{``Evidence for the Existence of a Robust Pattern of Prey Selection in
-Food Webs.''} \emph{Proceedings of the Royal Society B: Biological
-Sciences} 274 (1621): 1931--40.
-\url{https://doi.org/10.1098/rspb.2007.0571}.
+Stouffer, D. B., Camacho, J., Jiang, W., \& Nunes Amaral, L. A. (2007).
+Evidence for the existence of a robust pattern of prey selection in food
+webs. \emph{Proceedings of the Royal Society B: Biological Sciences},
+\emph{274}(1621), 1931--1940.
+\url{https://doi.org/10.1098/rspb.2007.0571}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Stouffer2012Evolutionary}{}}%
-Stouffer, D. B., M. Sales-Pardo, M. I. Sirer, and J. Bascompte. 2012.
-{``Evolutionary {Conservation} of {Species}' {Roles} in {Food Webs}.''}
-\emph{Science} 335 (6075): 1489--92.
-\url{https://doi.org/10.1126/science.1216556}.
+Stouffer, D. B., Sales-Pardo, M., Sirer, M. I., \& Bascompte, J. (2012).
+Evolutionary {Conservation} of {Species}' {Roles} in {Food Webs}.
+\emph{Science}, \emph{335}(6075), 1489--1492.
+\url{https://doi.org/10.1126/science.1216556}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Strydom2022Food}{}}%
-Strydom, Tanya, Salomé Bouskila, Francis Banville, Ceres Barros,
-Dominique Caron, Maxwell J. Farrell, Marie-Josée Fortin, et al. 2022.
-{``Food Web Reconstruction Through Phylogenetic Transfer of Low-Rank
-Network Representation.''} \emph{Methods in Ecology and Evolution} n/a
-(n/a). \url{https://doi.org/10.1111/2041-210X.13835}.
+Strydom, T., Bouskila, S., Banville, F., Barros, C., Caron, D., Farrell,
+M. J., Fortin, M.-J., Hemming, V., Mercier, B., Pollock, L. J., Runghen,
+R., Dalla Riva, G. V., \& Poisot, T. (2022). Food web reconstruction
+through phylogenetic transfer of low-rank network representation.
+\emph{Methods in Ecology and Evolution}, \emph{n/a}(n/a).
+\url{https://doi.org/10.1111/2041-210X.13835}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Strydom2021Roadmap}{}}%
-Strydom, Tanya, Michael D. Catchen, Francis Banville, Dominique Caron,
-Gabriel Dansereau, Philippe Desjardins-Proulx, Norma R. Forero-Muñoz, et
-al. 2021. {``A Roadmap Towards Predicting Species Interaction Networks
-(Across Space and Time).''} \emph{Philosophical Transactions of the
-Royal Society B: Biological Sciences} 376 (1837): 20210063.
-\url{https://doi.org/10.1098/rstb.2021.0063}.
+Strydom, T., Catchen, M. D., Banville, F., Caron, D., Dansereau, G.,
+Desjardins-Proulx, P., Forero-Muñoz, N. R., Higino, G., Mercier, B.,
+Gonzalez, A., Gravel, D., Pollock, L., \& Poisot, T. (2021). A roadmap
+towards predicting species interaction networks (across space and time).
+\emph{Philosophical Transactions of the Royal Society B: Biological
+Sciences}, \emph{376}(1837), 20210063.
+\url{https://doi.org/10.1098/rstb.2021.0063}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Strydom2021Svd}{}}%
-Strydom, Tanya, Giulio V. Dalla Riva, and Timothée Poisot. 2021. {``{SVD
-Entropy Reveals} the {High Complexity} of {Ecological Networks}.''}
-\emph{Frontiers in Ecology and Evolution} 9.
-\url{https://doi.org/10.3389/fevo.2021.623141}.
+Strydom, T., Dalla Riva, G. V., \& Poisot, T. (2021). {SVD Entropy
+Reveals} the {High Complexity} of {Ecological Networks}. \emph{Frontiers
+in Ecology and Evolution}, \emph{9}.
+\url{https://doi.org/10.3389/fevo.2021.623141}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Surendran2013Graph}{}}%
-Surendran, Subu. 2013. {``Graph {Embedding} and {Dimensionality
-Reduction} - {A Survey}.''} \emph{International Journal of Computer
-Science \& Engineering Technology} 4 (1).
-\url{https://www.semanticscholar.org/paper/Graph-Embedding-and-Dimensionality-Reduction-A-Surendran/3f413d591e4b2b876e033eeb9390e232ad4826ca}.
+Surendran, S. (2013). Graph {Embedding} and {Dimensionality Reduction} -
+{A Survey}. \emph{International Journal of Computer Science \&
+Engineering Technology}, \emph{4}(1).
+\url{https://www.semanticscholar.org/paper/Graph-Embedding-and-Dimensionality-Reduction-A-Surendran/3f413d591e4b2b876e033eeb9390e232ad4826ca}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Tang2015Line}{}}%
-Tang, Jian, Meng Qu, Mingzhe Wang, Ming Zhang, Jun Yan, and Qiaozhu Mei.
-2015. {``{LINE}: {Large-scale Information Network Embedding}.''}
-\emph{Proceedings of the 24th International Conference on World Wide
-Web}, May, 1067--77. \url{https://doi.org/10.1145/2736277.2741093}.
+Tang, J., Qu, M., Wang, M., Zhang, M., Yan, J., \& Mei, Q. (2015).
+{LINE}: {Large-scale Information Network Embedding}. \emph{Proceedings
+of the 24th International Conference on World Wide Web}, 1067--1077.
+\url{https://doi.org/10.1145/2736277.2741093}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Thurman2019Testing}{}}%
-Thurman, Lindsey L., Allison K. Barner, Tiffany S. Garcia, and Tara
-Chestnut. 2019. {``Testing the Link Between Species Interactions and
-Co-Occurrence in a Trophic Network.''} \emph{Ecography} 0.
-\url{https://doi.org/10.1111/ecog.04360}.
+Thurman, L. L., Barner, A. K., Garcia, T. S., \& Chestnut, T. (2019).
+Testing the link between species interactions and co-occurrence in a
+trophic network. \emph{Ecography}, \emph{0}.
+\url{https://doi.org/10.1111/ecog.04360}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Torres2020Glee}{}}%
-Torres, Leo, Kevin S Chan, and Tina Eliassi-Rad. 2020. {``{GLEE}:
-{Geometric Laplacian Eigenmap Embedding}.''} \emph{Journal of Complex
-Networks} 8 (2): cnaa007. \url{https://doi.org/10.1093/comnet/cnaa007}.
+Torres, L., Chan, K. S., \& Eliassi-Rad, T. (2020). {GLEE}: {Geometric
+Laplacian Eigenmap Embedding}. \emph{Journal of Complex Networks},
+\emph{8}(2), cnaa007. \url{https://doi.org/10.1093/comnet/cnaa007}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Turak2017Using}{}}%
-Turak, Eren, James Brazill-Boast, Tim Cooney, Michael Drielsma, Jocelyn
-DelaCruz, Gillian Dunkerley, Miguel Fernandez, et al. 2017. {``Using the
-Essential Biodiversity Variables Framework to Measure Biodiversity
-Change at National Scale.''} \emph{Biological Conservation},
-{SI}:{Measures} of biodiversity, 213 (September): 264--71.
-\url{https://doi.org/10.1016/j.biocon.2016.08.019}.
+Turak, E., Brazill-Boast, J., Cooney, T., Drielsma, M., DelaCruz, J.,
+Dunkerley, G., Fernandez, M., Ferrier, S., Gill, M., Jones, H., Koen,
+T., Leys, J., McGeoch, M., Mihoub, J.-B., Scanes, P., Schmeller, D., \&
+Williams, K. (2017). Using the essential biodiversity variables
+framework to measure biodiversity change at national scale.
+\emph{Biological Conservation}, \emph{213}, 264--271.
+\url{https://doi.org/10.1016/j.biocon.2016.08.019}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Wang2016Structural}{}}%
-Wang, Daixin, Peng Cui, and Wenwu Zhu. 2016. {``Structural {Deep Network
-Embedding}.''} In \emph{Proceedings of the 22nd {ACM SIGKDD
-International Conference} on {Knowledge Discovery} and {Data Mining}},
-1225--34. {San Francisco California USA}: {ACM}.
-\url{https://doi.org/10.1145/2939672.2939753}.
+Wang, D., Cui, P., \& Zhu, W. (2016). Structural {Deep Network
+Embedding}. \emph{Proceedings of the 22nd {ACM SIGKDD International
+Conference} on {Knowledge Discovery} and {Data Mining}}, 1225--1234.
+\url{https://doi.org/10.1145/2939672.2939753}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Wang2021Joint}{}}%
-Wang, Shangsi, Jesus Arroyo, Joshua T. Vogelstein, and Carey E. Priebe.
-2021. {``Joint {Embedding} of {Graphs}.''} \emph{IEEE Transactions on
-Pattern Analysis and Machine Intelligence} 43 (4): 1324--36.
-\url{https://doi.org/10.1109/TPAMI.2019.2948619}.
+Wang, S., Arroyo, J., Vogelstein, J. T., \& Priebe, C. E. (2021). Joint
+{Embedding} of {Graphs}. \emph{IEEE Transactions on Pattern Analysis and
+Machine Intelligence}, \emph{43}(4), 1324--1336.
+\url{https://doi.org/10.1109/TPAMI.2019.2948619}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Wardeh2021Predicting}{}}%
-Wardeh, Maya, Matthew Baylis, and Marcus S. C. Blagrove. 2021.
-{``Predicting Mammalian Hosts in Which Novel Coronaviruses Can Be
-Generated.''} \emph{Nature Communications} 12 (1, 1): 780.
-\url{https://doi.org/10.1038/s41467-021-21034-5}.
+Wardeh, M., Baylis, M., \& Blagrove, M. S. C. (2021). Predicting
+mammalian hosts in which novel coronaviruses can be generated.
+\emph{Nature Communications}, \emph{12}(1, 1), 780.
+\url{https://doi.org/10.1038/s41467-021-21034-5}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Weiskopf2022Increasing}{}}%
-Weiskopf, Sarah R., Zuzana V. Harmáčková, Ciara G. Johnson, María
-Cecilia Londoño-Murcia, Brian W. Miller, Bonnie J. E. Myers, Laura
-Pereira, et al. 2022. {``Increasing the Uptake of Ecological Model
-Results in Policy Decisions to Improve Biodiversity Outcomes.''}
-\emph{Environmental Modelling \& Software} 149 (March): 105318.
-\url{https://doi.org/10.1016/j.envsoft.2022.105318}.
+Weiskopf, S. R., Harmáčková, Z. V., Johnson, C. G., Londoño-Murcia, M.
+C., Miller, B. W., Myers, B. J. E., Pereira, L., Arce-Plata, M. I.,
+Blanchard, J. L., Ferrier, S., Fulton, E. A., Harfoot, M., Isbell, F.,
+Johnson, J. A., Mori, A. S., Weng, E., \& Rosa, I. M. D. (2022).
+Increasing the uptake of ecological model results in policy decisions to
+improve biodiversity outcomes. \emph{Environmental Modelling \&
+Software}, \emph{149}, 105318.
+\url{https://doi.org/10.1016/j.envsoft.2022.105318}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Williams2000Simple}{}}%
-Williams, Richard J., and Neo D. Martinez. 2000. {``Simple Rules Yield
-Complex Food Webs.''} \emph{Nature} 404 (6774): 180--83.
-\url{https://doi.org/10.1038/35004572}.
+Williams, R. J., \& Martinez, N. D. (2000). Simple rules yield complex
+food webs. \emph{Nature}, \emph{404}(6774), 180--183.
+\url{https://doi.org/10.1038/35004572}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Wood2015Effects}{}}%
-Wood, Spencer A., Roly Russell, Dieta Hanson, Richard J. Williams, and
-Jennifer A. Dunne. 2015. {``Effects of Spatial Scale of Sampling on Food
-Web Structure.''} \emph{Ecology and Evolution} 5 (17): 3769--82.
-\url{https://doi.org/10.1002/ece3.1640}.
+Wood, S. A., Russell, R., Hanson, D., Williams, R. J., \& Dunne, J. A.
+(2015). Effects of spatial scale of sampling on food web structure.
+\emph{Ecology and Evolution}, \emph{5}(17), 3769--3782.
+\url{https://doi.org/10.1002/ece3.1640}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Wu2021Maximum}{}}%
-Wu, David, David R. Palmer, and Daryl R. Deford. 2021. {``Maximum a
+Wu, D., Palmer, D. R., \& Deford, D. R. (2021). \emph{Maximum a
 {Posteriori Inference} of {Random Dot Product Graphs} via {Conic
-Programming}.''} {arXiv}. \url{http://arxiv.org/abs/2101.02180}.
+Programming}} (arXiv:2101.02180). {arXiv}.
+\url{http://arxiv.org/abs/2101.02180}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Xu2021Understanding}{}}%
-Xu, Mengjia. 2021. {``Understanding {Graph Embedding Methods} and {Their
-Applications}.''} \emph{SIAM Review} 63 (4): 825--53.
-\url{https://doi.org/10.1137/20M1386062}.
+Xu, M. (2021). Understanding {Graph Embedding Methods} and {Their
+Applications}. \emph{SIAM Review}, \emph{63}(4), 825--853.
+\url{https://doi.org/10.1137/20M1386062}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Yan2005Graph}{}}%
-Yan, Shuicheng, Dong Xu, Benyu Zhang, and Hong-Jiang Zhang. 2005.
-{``Graph Embedding: A General Framework for Dimensionality Reduction.''}
-In \emph{2005 {IEEE Computer Society Conference} on {Computer Vision}
-and {Pattern Recognition} ({CVPR}'05)}, 2:830--837 vol. 2.
-\url{https://doi.org/10.1109/CVPR.2005.170}.
+Yan, S., Xu, D., Zhang, B., \& Zhang, H.-J. (2005). Graph embedding: A
+general framework for dimensionality reduction. \emph{2005 {IEEE
+Computer Society Conference} on {Computer Vision} and {Pattern
+Recognition} ({CVPR}'05)}, \emph{2}, 830--837 vol. 2.
+\url{https://doi.org/10.1109/CVPR.2005.170}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Young2007Random}{}}%
-Young, Stephen J., and Edward R. Scheinerman. 2007. {``Random {Dot
-Product Graph Models} for {Social Networks}.''} In \emph{Algorithms and
-{Models} for the {Web-Graph}}, edited by Anthony Bonato and Fan R. K.
-Chung, 138--49. Lecture {Notes} in {Computer Science}. {Berlin,
-Heidelberg}: {Springer}.
-\url{https://doi.org/10.1007/978-3-540-77004-6_11}.
+Young, S. J., \& Scheinerman, E. R. (2007). Random {Dot Product Graph
+Models} for {Social Networks}. In A. Bonato \& F. R. K. Chung (Eds.),
+\emph{Algorithms and {Models} for the {Web-Graph}} (pp. 138--149).
+{Springer}. \url{https://doi.org/10.1007/978-3-540-77004-6_11}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Zhou2020Graph}{}}%
-Zhou, Jie, Ganqu Cui, Shengding Hu, Zhengyan Zhang, Cheng Yang, Zhiyuan
-Liu, Lifeng Wang, Changcheng Li, and Maosong Sun. 2020. {``Graph Neural
-Networks: {A} Review of Methods and Applications.''} \emph{AI Open} 1
-(January): 57--81. \url{https://doi.org/10.1016/j.aiopen.2021.01.001}.
+Zhou, J., Cui, G., Hu, S., Zhang, Z., Yang, C., Liu, Z., Wang, L., Li,
+C., \& Sun, M. (2020). Graph neural networks: {A} review of methods and
+applications. \emph{AI Open}, \emph{1}, 57--81.
+\url{https://doi.org/10.1016/j.aiopen.2021.01.001}
 

### 2023-09-07 reviews/compile.sh

@@ -1,1 +1,2 @@
-find . -type f -name "*.md" -exec bash -c 'pandoc {} -o {}.pdf --template=../.assets/templates/responses.tex' \;
+#find . -type f -name "*.md" -exec bash -c 'pandoc {} -o {}.pdf --template=../.assets/templates/responses.tex' \;
+find . -type f -name "*.md" -exec bash -c 'pandoc {} -o {}.pdf' \;

### 2023-09-19 index.qmd
ready
:pencil: updates for publication needs

@@
 ---
+
+# Introduction
 
@@
 **Acknowledgements:** We acknowledge that this study was conducted on land within the traditional unceded territory of the Saint Lawrence Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations.
-We thank Victoria hemming for feedback on this manuscript.
+We thank Victoria Hemming for feedback on this manuscript.
 TP, TS, DC, and LP received funding from the Canadian Institute for Ecology & Evolution.
@@
 
+**Data availability:** The code to collect the data used in figures is distributed as part of the Supplementary Material.
+
 **Conflict of interest:** The authors have no conflict of interests to disclose
 
-**Authors' contributions:** TS and TP conceived the ideas discussed in the manuscript. All authors contributed to writing and editing the manuscript.
-
-**Data availability:** The code to collect the data use in figures is distributed as part of the Supplementary Material.
+**Authors' contributions:** Tanya Strydom and Timothée Poisot conceived the ideas discussed in the manuscript.
+All authors contributed to writing and editing the manuscript and gave final approval for publication.
 
